### 2022-07-14 presentation.qmd
copy over from sports_viz

---
title: "Tactical Round-Based Games"
author: "Tony ElHabr"
format:
  revealjs:
    incremental: false
    theme: dark
execute: 
  include: false
  echo: false
---

```{r}
#| label: setup
library(dplyr)
library(tibble)
library(qs)
library(scales)

dir_proj <- '57-cod_snd'

rounds <- qs::qread(file.path('cod_rounds.qs'))
```

## What?

-   Call of Duty League (CDL)
    -   Search and Destroy
-   Valorant Pro League
    -   Plant/Defuse

## How do you win SnD?

Several ways to win a round:

1.  One team eliminate all members of the other team prior to a bomb plant.
2.  The offensive team wins if they eliminate all members of the defensive team after a bomb plant.
3.  The defensive team wins if they defuse the bomb after a bomb plant.[^1]
4.  The defensive team wins if the offensive team does not make a plant by the time the round timer ends.

[^1]: Often the defensive team will try to eliminate all offensive team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.

## Data set

```{r}
#| label: descriptive-cod-snd-stats
n_series <- rounds |> 
  distinct(year, sheet, series) |> 
  nrow() |> 
  scales::comma()

n_rounds <- rounds |> 
  distinct(year, sheet, series, round) |> 
  nrow() |> 
  scales::comma()

offensive_win_pct <- rounds |> 
  filter(is_offense) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop) |> 
  scales::percent(accuracy = 1)

plant_pct <- rounds |>
  filter(is_offense) |> 
  count(makes_plant = !is.na(plant)) |> 
  mutate(prop = n / sum(n)) |> 
  filter(makes_plant) |> 
  pull(prop) |> 
  scales::percent(accuracy = 1)

offensive_plant_and_win_pct <- rounds |> 
  filter(is_offense, !is.na(plant)) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop) |> 
  scales::percent(accuracy = 1)

offensive_first_blood_win_pct <- rounds |> 
  filter(!is.na(earned_fb)) |> 
  filter(earned_fb) |> 
  count(win_round) |> 
  mutate(prop = n / sum(n)) |> 
  filter(win_round) |> 
  pull(prop) |> 
  scales::percent(accuracy = 1)
```

-   Total series: **`r n_series`**
-   Total rounds: **`r n_rounds`**
-   Offensive win %: **`r offensive_win_pct`**
-   Offensive sides plant %: **`r plant_pct`**
-   Win % when planting: **`r offensive_plant_and_win_pct`**
-   Win % when earning first blood: **`r offensive_first_blood_win_pct`**

## How do teams play in an information-neutral setting (round 1)?

![](offensive_win_r1_prop.png)

### 2022-07-14 0-streaks.R

@@ -1,0 +1,43 @@
+
+library(tidyverse)
+
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+  
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+  
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 1000, ...) {
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+
+runs <- crossing(
+  n = 1:100,
+  k = 1:3
+) |> 
+  mutate(
+    p = map2_dbl(n, k, ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2))
+  )
+runs |>
+  arrange(n, k) |>
+  mutate(
+    across(k, factor)
+  ) |> 
+  ggplot() +
+  aes(x = n, y = p, color = k, group = k) +
+  geom_step() +
+  geom_hline(aes(yintercept = 0.5))

### 2022-07-14 1-scrape.R

@@ -1,0 +1,234 @@
+
+## Data from https://twitter.com/IOUTurtle
+library(tidyverse)
+library(googlesheets4)
+library(magrittr)
+library(qs)
+
+dir_proj <- '57-cod_snd'
+dir_data <- file.path(dir_proj, 'data')
+dir.create(dir_data, showWarnings = FALSE)
+
+sheets <- list(
+  '2022' = crossing(
+    s = c(1, 2, 3, 4),
+    raw_series = c(1, 2, 3, 4)
+  ) |> 
+    mutate(
+      label = sprintf('S%d %s', s, ifelse(raw_series == 4, 'Major', sprintf('Wk%d', raw_series)))
+    ) |> 
+    pull(label) %>%
+    .[1:14],
+  '2021' = c(
+    'Champs', 
+    crossing(
+      s = c(1, 2, 3, 4, 5),
+      raw_series = c(1, 2, 3, 4)
+    ) |> 
+      mutate(
+        label = sprintf('S%d %s', s, ifelse(raw_series == 4, 'Major', sprintf('HS%d', raw_series)))
+      ) |> 
+      pull(label)
+  ),
+  '2020' = sprintf(
+    '%s_SnD',
+    c('CHAMPS', 'LAUNCH', 'LON', 'ATL', 'LA', 'DAL', 'CHI', 'FLA', 'SEA', 'MIN', 'PAR', 'NY', 'LON2', 'TOR')
+  )
+) |> 
+  enframe('year', 'sheet') |> 
+  unnest(sheet) |> 
+  mutate(
+    across(year, as.integer),
+    event = sprintf('%s - %s', year, sheet) |> fct_inorder()
+  )
+
+read_snd_sheet <- function(year, sheet, overwrite = FALSE) {
+  
+  path <- file.path(dir_data, sprintf('snd-%s-%s.qs', year, sheet))
+  if(file.exists(path) & !overwrite) {
+    return(qs::qread(path))
+  }
+  
+  year <- as.character(year)
+  ss <- switch(
+    year,
+    '2020' = '1urYnnEjYdjC320Ua7ccZ3GC6-3Lmpudp_fybe2D3Xbs',
+    '2021' = '1tkxRiu5i4XUDkLqJxEZMrwD9-jiXVLTD56j9pdHGjzc',
+    '2022' = '10Ou2UbMtox3pVfrW9mziLkE9138SV281t6yGTg5IMXY'
+  )
+  
[…]

### 2022-07-14 2-visualize.R

@@ -1,0 +1,818 @@
+
+library(tidyverse)
+library(qs)
+library(scales)
+library(extrafont)
+library(ggtext)
+
+dir_proj <- '57-cod_snd'
+blackish_background <- '#1c1c1c'
+gray_points <- '#4d4d4d'
+gray_text <- '#999999'
+
+font <- 'Titillium Web' ## Karla
+extrafont::loadfonts(quiet = TRUE)
+theme_set(theme_minimal())
+theme_update(
+  text = element_text(family = font),
+  title = element_text(size = 20, color = 'white'),
+  plot.title = element_text(face = 'bold', size = 20, color = 'white'),
+  plot.title.position = 'plot',
+  plot.subtitle = element_text(size = 16, color = '#f1f1f1'),
+  axis.text = element_text(color = 'white', size = 14),
+  axis.title = element_text(size = 14, color = 'white', face = 'bold', hjust = 0.99),
+  axis.line = element_blank(),
+  panel.grid.major = element_line(color = gray_points),
+  panel.grid.minor = element_line(color = gray_points),
+  panel.grid.minor.x = element_blank(),
+  panel.grid.minor.y = element_blank(),
+  strip.text = element_text(color = 'white', size = 16, face = 'bold'),
+  plot.margin = margin(10, 10, 10, 10),
+  plot.background = element_rect(fill = blackish_background, color = blackish_background),
+  plot.caption = element_text(size = 12, color = 'white', hjust = 1),
+  plot.caption.position = 'plot',
+  plot.tag = ggtext::element_markdown(size = 12, color = 'white', hjust = 0),
+  plot.tag.position = c(0.01, 0.01),
+  panel.background = element_rect(fill = blackish_background, color = blackish_background)
+)
+# update_geom_defaults('text', list(colour = 'white', font = font))
+update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
+update_geom_defaults('point', list(color = 'white'))
+update_geom_defaults('segment', list(color = 'white'))
+
+game_mapping <- c(
+  '2022' = 'Vanguard',
+  '2021' = 'Cold War',
+  '2020' = 'MW'
+)
+
[…]

### 2022-07-14 1-scrape.R
update data

@@ -5,8 +5,7 @@ library(googlesheets4)
 library(magrittr)
 library(qs)
 
-dir_proj <- '57-cod_snd'
-dir_data <- file.path(dir_proj, 'data')
+dir_data <- 'data'
 dir.create(dir_data, showWarnings = FALSE)
 
 sheets <- list(
@@ -231,4 +230,4 @@ rounds <- series |>
     .before = 1
   )
 rounds
-qs::qsave(rounds, file.path(dir_proj, 'cod_rounds.qs'))
+qs::qsave(rounds, 'cod_rounds.qs')

### 2022-07-14 2-visualize.R
update first plot

@@ -5,8 +5,7 @@ library(scales)
 library(extrafont)
 library(ggtext)
 
-dir_proj <- '57-cod_snd'
-blackish_background <- '#1c1c1c'
+blackish_background <- '#191919' # '#1c1c1c'
 gray_points <- '#4d4d4d'
 gray_text <- '#999999'
 
@@ -46,7 +45,7 @@ game_mapping <- c(
   '2020' = 'MW'
 )
 
-rounds <- qs::qread(file.path(dir_proj, 'cod_rounds.qs'))
+rounds <- qs::qread('cod_rounds.qs')
 
 ## offensive win % in "neutral" rounds (1 and 2) ----
 calculate_offensive_round_win_prop <- function(df) {
@@ -94,17 +93,18 @@ summarize_offensive_round_win_prop <- function(.round) {
 
 offensive_win_r1_prop <- summarize_offensive_round_win_prop(1)|> 
   mutate(
-    diff_prop = win_round_prop - other_win_round_prop,
+    diff_prop = other_win_round_prop - win_round_prop,
     dir = factor(sign(diff_prop)),
     is_significant = p_value < 0.05,
     label = sprintf('%s - %s (%s)', map, game, year)
   )
 
-x1_label <- 'Post-Round 1\nOffensive Win%'
-x2_label <- 'Round 1\nOffensive Win%'
+x1_label <- 'Round 1<br/>Offensive Win%'
+x2_label <- 'Post-Round 1<br/>Offensive Win%'
 
 min_offensive_win_r1_prop <- offensive_win_r1_prop |> slice_min(diff_prop, n = 1)
 max_offensive_win_r1_prop <- offensive_win_r1_prop |> slice_max(diff_prop, n = 1)
+minmax_labels <- c(min_offensive_win_r1_prop$label, max_offensive_win_r1_prop$label)
 
 offensive_win_r1_prop_pal <- c(
   `-1` = '#ef426f',
@@ -114,32 +114,6 @@ arw <- arrow(length = unit(5, 'pt'), type = 'closed')
 
 p_offensive_win_r1_prop <- offensive_win_r1_prop |> 
   ggplot() +
-  geom_segment(
-    show.legend = FALSE,
-    aes(
-      x = 1,
-      xend = 2,
-      y = other_win_round_prop,
-      yend = win_round_prop,
-      color = dir,
-      size = is_significant,
-      group = label
-    )
-  ) +
-  geom_text(
[…]

### 2022-07-14 0-streaks.R
think about streaking again

@@ -32,6 +32,7 @@ runs <- crossing(
   mutate(
     p = map2_dbl(n, k, ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2))
   )
+
 runs |>
   arrange(n, k) |>
   mutate(
@@ -41,3 +42,7 @@ runs |>
   aes(x = n, y = p, color = k, group = k) +
   geom_step() +
   geom_hline(aes(yintercept = 0.5))
+
+simulate_post_streak_prob(sims = 1000, n = 11, k = 3, p = 0.6)
+simulate_post_streak_prob(sims = 1000, n = 6, k = 3, p = 0.5)
+simulate_post_streak_prob(sims = 1000, n = 100, k = 3, p = 0.5)

### 2022-07-14 presentation.qmd
make progress on pres

@@
 ---
-title: "Tactical Round-Based Games"
+title: "On Round-Based Games in First-Person-Shooter (FPS) E-Sports"
 author: "Tony ElHabr"
@@
     incremental: false
-    theme: dark
+    theme: [dark, theme.scss]
 execute: 
@@
 
-dir_proj <- '57-cod_snd'
-
 rounds <- qs::qread(file.path('cod_rounds.qs'))
@@
 -   Call of Duty League (CDL)
-    -   Search and Destroy
+    -   Search and Destroy (SnD)
 -   Valorant Pro League
@@
 
-## How do you win SnD?
+## How does a team win a round of SnD?
 
-Several ways to win a round:
+::: fragment
+1.  One team eliminates all members of the other team prior to a bomb plant.
+:::
 
-1.  One team eliminate all members of the other team prior to a bomb plant.
-2.  The offensive team wins if they eliminate all members of the defensive team after a bomb plant.
-3.  The defensive team wins if they defuse the bomb after a bomb plant.[^1]
-4.  The defensive team wins if the offensive team does not make a plant by the time the round timer ends.
+::: fragment
+2.  The offensive team eliminates all members of the defensive team after a bomb plant.
+:::
 
-[^1]: Often the defensive team will try to eliminate all offensive team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+::: fragment
+3.  The defensive team defuses the bomb after a bomb plant.
+:::
+
+::: fragment
+Often the defensive team will try to eliminate all offensive team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+:::
+
+::: fragment
+4.  The offensive team does not make a plant by the time the round timer ends.
+:::
 
@@
 
+::: fragment
 -   Total series: **`r n_series`**
+:::
+
+::: fragment
 -   Total rounds: **`r n_rounds`**
+:::
+
+::: fragment
+-   Offensive sides plant %: **`r plant_pct`**
+:::
+
+::: fragment
 -   Offensive win %: **`r offensive_win_pct`**
--   Offensive sides plant %: **`r plant_pct`**
+:::
+
+::: fragment
 -   Win % when planting: **`r offensive_plant_and_win_pct`**
+:::
+
+::: fragment
 -   Win % when earning first blood: **`r offensive_first_blood_win_pct`**
+:::
 
@@
 
-![](offensive_win_r1_prop.png)
+![](offensive_win_r1_prop.png){fig-align="center"}

### 2022-07-14 0-streaks.R
add some streaks stuff to 2

@@ -46,3 +46,27 @@ runs |>
 simulate_post_streak_prob(sims = 1000, n = 11, k = 3, p = 0.6)
 simulate_post_streak_prob(sims = 1000, n = 6, k = 3, p = 0.5)
 simulate_post_streak_prob(sims = 1000, n = 100, k = 3, p = 0.5)
+
+probs_n6_k2 <- tibble(
+  prob = seq(0.1, 0.9, by = 0.1)
+) |> 
+  mutate(
+    p = map_dbl(prob, ~simulate_post_streak_prob(sims = 10000, n = 6, k = 2, p = .x))
+  )
+probs_n6_k2
+
+probs_n6_k3 <- tibble(
+  prob = seq(0.1, 0.9, by = 0.1)
+) |> 
+  mutate(
+    p = map_dbl(prob, ~simulate_post_streak_prob(sims = 10000, n = 6, k = 5, p = .x))
+  )
+probs_n6_k3
+
+probs_n11_k3 <- tibble(
+  prob = seq(0.1, 0.9, by = 0.1)
+) |> 
+  mutate(
+    p = map_dbl(prob, ~simulate_post_streak_prob(sims = 10000, n = 11, k = 2, p = .x))
+  )
+probs_n11_k3

### 2022-07-14 2-visualize.R

@@ -266,6 +266,56 @@ ggsave(
   height = 7.5
 )
 
+## win prob after a streak of 2 within first 6 rounds? ----
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+  
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+  
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 1000, ...) {
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+
+probs_n6_k2 <- tibble(
+  prob = seq(0.25, 0.75, by = 0.05)
+) |> 
+  mutate(
+    p = map_dbl(prob, ~simulate_post_streak_prob(sims = 10000, n = 6, k = 2, p = .x))
+  )
+probs_n6_k2
+
+streaks_of_3 <- rounds |> 
+  filter(round <= 6) |> 
+  group_by(year, sheet, series, team) |> 
+  mutate(
+    won_prior_round2 = lag(win_round, n = 2, default = NA)
+  ) |> 
+  ungroup() |> 
+  select(year, sheet, series, team, win_round, won_prior_round, won_prior_round2) |> 
+  filter(!is.na(won_prior_round2)) |> 
+  count(win_round, won_prior_round, won_prior_round2, sort = TRUE)
+
+streaks_of_3 |> 
+  filter(won_prior_round, won_prior_round2) |> 
+  mutate(
+    prop = n / sum(n)
+  )
+
 ## comparing round playouts vs expected if each side has a pre-series win expectation of 50% ----
 prior_clinching_round_win_prop <- rounds |> 
   filter(round == (n_rounds - 1L)) |> 

### 2022-07-14 presentation.qmd
outline talking points

@@
 ---
-title: "On Round-Based Games in First-Person-Shooter (FPS) E-Sports"
+title: "Momentum in Round-Based First-Person-Shooter (FPS) E-Sports"
 author: "Tony ElHabr"
@@
 
-## How do teams play in an information-neutral setting (round 1)?
+## What are your chances of winning a round, given the series state?
+
+(This should hint at the 4-4 phenomenon.)
+
+## How does reality compare to expectation?
+
+(This should really highlight the 4-4 phenomenon.)
+
+## What are your chances of going on to win the series, given the series state?
+
+(More of the 4-4 phenomenon. Also should not win %s along the diagonal.)
+
+## Are offensive win %'s different in round 1 (i.e. an "information-neutral" setting)?
 
 ![](offensive_win_r1_prop.png){fig-align="center"}
+
+## Are offensive win %'s different in round 2?
+
+![](offensive_win_r2_prop.png){fig-align="center"}
+
+(Emperically, no)
+
+## What are the most common series winning states?
+
+## How do end states compare to expectation?
+
+(There should be evidence of 6-0's and 6-5's being more frequent than expected given 50-50% chances. Might need to exclude major matchups, so that series are basically random.)
+
+## Is there evidence for the "hot hand"?
+
+![](hot_hand.png){fig-align="center"}
+
+(Need to explain that this is sort of biased by the fact that teams end up winning series in 6 rounds more often than expected.)

### 2022-07-15 2-visualize.R
frequency of planting at sites

@@ -266,6 +266,97 @@ ggsave(
   height = 7.5
 )
 
+## x ----
+map_plant_win_props <- rounds |> 
+  filter(!is.na(plant)) |> 
+  filter(is_offense) |> 
+  group_by(year, game, map, plant) |> 
+  summarize(
+    n = n(),
+    wins = sum(win_round)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_prop = wins / n
+  ) |> 
+  group_by(year, game, map) |> 
+  mutate(
+    total = sum(n),
+    rnk = row_number(-n),
+    prop = n / total
+  ) |> 
+  ungroup()
+map_plant_win_props
+
+rounds |> 
+  filter(is_offense) |> 
+  left_join(
+    map_plant_win_props |> 
+      transmute(year, game, map, plant, play = ifelse(rnk == 1, 'pri', 'sec'))
+  ) |> 
+  mutate(
+    play = ifelse(is.na(plant), 'no', play)
+  ) |> 
+  count(play, sort = TRUE) |> 
+  mutate(prop = n / sum(n))
+
+summarize_map_plant_win_props <- function(i) {
+  map_plant_win_props |> 
+    group_by(year, game, map) |> 
+    filter(rnk == !!i) |> 
+    ungroup() |> 
+    summarize(
+      across(c(n, wins, total), sum)
+    ) |> 
+    ungroup() |> 
+    mutate(
+      win_prop = wins / n,
+      prop = n / total
+    )
+}
+
+pri_map_plant_win_props <- summarize_map_plant_win_props(1)
+sec_map_plant_win_props <- summarize_map_plant_win_props(2)
+
+map_plant_win_props |> 
+  ggplot() +
+  aes(x = prop, y = win_prop) +
+  geom_point(aes(color = factor(rnk), size = n)) +
+  geom_segment(
+    data = map_plant_win_props |> 
+      select(year, game, map, rnk, prop, win_prop) |> 
+      pivot_wider(
+        names_from = rnk,
+        values_from = c(prop, win_prop)
+      ),
+    aes(
+      x = prop_1,
+      xend = prop_2,
+      y = win_prop_1,
+      yend = win_prop_2
+    )
+  )
+
+rounds |> 
+  filter(is.na(plant)) |> 
+  filter(is_offense) |> 
+  group_by(year, game, map, plant) |> 
+  summarize(
+    n = n(),
+    wins = sum(win_round)
[…]

### 2022-07-15 x-streaks.R
rename streaks

@@ -39,34 +39,12 @@ runs |>
     across(k, factor)
   ) |> 
   ggplot() +
+  theme_minimal() +
   aes(x = n, y = p, color = k, group = k) +
   geom_step() +
-  geom_hline(aes(yintercept = 0.5))
+  geom_hline(aes(yintercept = 0.5)) +
+  geom_smooth()
 
 simulate_post_streak_prob(sims = 1000, n = 11, k = 3, p = 0.6)
 simulate_post_streak_prob(sims = 1000, n = 6, k = 3, p = 0.5)
 simulate_post_streak_prob(sims = 1000, n = 100, k = 3, p = 0.5)
-
-probs_n6_k2 <- tibble(
-  prob = seq(0.1, 0.9, by = 0.1)
-) |> 
-  mutate(
-    p = map_dbl(prob, ~simulate_post_streak_prob(sims = 10000, n = 6, k = 2, p = .x))
-  )
-probs_n6_k2
-
-probs_n6_k3 <- tibble(
-  prob = seq(0.1, 0.9, by = 0.1)
-) |> 
-  mutate(
-    p = map_dbl(prob, ~simulate_post_streak_prob(sims = 10000, n = 6, k = 5, p = .x))
-  )
-probs_n6_k3
-
-probs_n11_k3 <- tibble(
-  prob = seq(0.1, 0.9, by = 0.1)
-) |> 
-  mutate(
-    p = map_dbl(prob, ~simulate_post_streak_prob(sims = 10000, n = 11, k = 2, p = .x))
-  )
-probs_n11_k3

### 2022-07-15 2-visualize.R
old code

@@ -39,12 +39,6 @@ update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bo
 update_geom_defaults('point', list(color = 'white'))
 update_geom_defaults('segment', list(color = 'white'))
 
-game_mapping <- c(
-  '2022' = 'Vanguard',
-  '2021' = 'Cold War',
-  '2020' = 'MW'
-)
-
 rounds <- qs::qread('cod_rounds.qs')
 
 ## offensive win % in "neutral" rounds (1 and 2) ----

### 2022-07-15 presentation.qmd
game theory q
6 official plots

--- 2022-07-14 presentation.qmd
@@
   echo: false
+  eval: false
 ---
@@
 #| label: setup
+#| eval: true
 library(dplyr)
-library(tibble)
+library(dplyr)
 library(qs)
@@
 
-rounds <- qs::qread(file.path('cod_rounds.qs'))
+rounds <- qs::qread('cod_rounds.qs')
 ```
 
-## What?
+```{r}
+#| label: setup-eval
+library(tidyverse)
+library(extrafont)
+library(ggtext)
+library(ggsci)
+blackish_background <- '#191919' ## to match slide background
+gray_points <- '#4d4d4d'
+gray_text <- '#999999'
 
--   Call of Duty League (CDL)
-    -   Search and Destroy (SnD)
--   Valorant Pro League
-    -   Plant/Defuse
+font <- 'Titillium Web'
+extrafont::loadfonts(quiet = TRUE)
+theme_set(theme_minimal())
+theme_update(
+  text = element_text(family = font),
+  title = element_text(size = 14, color = 'white'),
+  plot.title = element_text(face = 'bold', size = 20, color = 'white'),
+  plot.title.position = 'plot',
+  plot.subtitle = element_text(size = 14, color = '#f1f1f1'),
+  axis.text = element_text(color = 'white', size = 14),
+  axis.title = element_text(size = 14, color = 'white', face = 'bold', hjust = 0.99),
+  axis.line = element_blank(),
+  panel.grid.major = element_line(color = gray_points),
+  panel.grid.minor = element_line(color = gray_points),
+  panel.grid.minor.x = element_blank(),
+  panel.grid.minor.y = element_blank(),
+  strip.text = element_text(color = 'white', size = 16, face = 'bold'),
+  plot.margin = margin(10, 10, 10, 10),
+  plot.background = element_rect(fill = blackish_background, color = blackish_background),
+  plot.caption = element_text(size = 12, color = 'white', hjust = 1),
+  plot.caption.position = 'plot',
+  plot.tag = ggtext::element_markdown(size = 12, color = 'white', hjust = 0),
+  plot.tag.position = c(0.01, 0.01),
+  panel.background = element_rect(fill = blackish_background, color = blackish_background)
+)
+update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
+update_geom_defaults('point', list(color = 'white'))
+update_geom_defaults('segment', list(color = 'white'))
+```
 
-## How does a team win a round of SnD?
+## Game types
+
+::: fragment
+-   Search and Destroy (SnD) in Call of Duty (COD)
+    -   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
+    -   4v4.
+    -   First to 6 round wins
+    -   Teams swap sides (offense and defense) after every round
+:::
+
+::: fragment
+-   Plant/Defuse in Valorant
+    -   Data from Valorant professional league, updated through January 1, 2022
+    -   5v5
+    -   First to 13 round wins
+    -   One team plays offense in 12 consecutive rounds before swapping sides
+    -   Must win by 2 rounds
+:::
+
+## How does a team win a round of COD SnD / Valorant plant/defuse?
 
@@
 ::: fragment
-Often the defensive team will try to eliminate all offensive team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+Often the defensive team will try to eliminate all o team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
 :::
@@
 
-## Data set
+## COD SnD data overview
 
@@
 #| label: descriptive-cod-snd-stats
+#| eval: true
 n_series <- rounds |> 
@@
 
-offensive_win_pct <- rounds |> 
+o_win_prop_const <- rounds |> 
   filter(is_offense) |> 
@@
   filter(win_round) |> 
-  pull(prop) |> 
-  scales::percent(accuracy = 1)
+  pull(prop)
+o_win_pct <- scales::percent(o_win_prop_const, accuracy = 1)
 
@@
 
-offensive_plant_and_win_pct <- rounds |> 
+o_plant_and_win_pct <- rounds |> 
   filter(is_offense, !is.na(plant)) |> 
@@
 
-offensive_first_blood_win_pct <- rounds |> 
+o_first_blood_win_pct <- rounds |> 
   filter(!is.na(earned_fb)) |> 
@@
 ::: fragment
--   Offensive sides plant %: **`r plant_pct`**
+-   Offensive plant %: **`r plant_pct`**
 :::
@@
 ::: fragment
--   Offensive win %: **`r offensive_win_pct`**
+-   Offensive win %: **`r o_win_pct`**
 :::
@@
 ::: fragment
--   Win % when planting: **`r offensive_plant_and_win_pct`**
+-   Win % when planting: **`r o_plant_and_win_pct`**
 :::
@@
 ::: fragment
--   Win % when earning first blood: **`r offensive_first_blood_win_pct`**
+-   Win % when earning first blood: **`r o_first_blood_win_pct`**
 :::
 
-## How do teams play in an information-neutral setting (round 1)?
+## What are your chances of winning a round, given the series state?
 
-![](offensive_win_r1_prop.png){fig-align="center"}
+```{r}
+#| label: cod_heatmap_prep
+summarize_rounds <- function(rounds, ...) {
+  rounds |> 
+    group_by(pre_cumu_w, pre_cumu_l, ...) |> 
+    summarize(
+      n = n(),
+      across(c(win_round, win_series), sum)
+    ) |> 
+    ungroup() |> 
+    mutate(
+      win_round_prop = win_round / n,
+      win_series_prop = win_series / n
+    )
+}
+
+n_rounds_side <- rounds |> summarize_rounds(is_offense)
+o_win_prop <- n_rounds_side |> 
+  filter(is_offense) |> 
+  mutate(
+    diff_win_round_prop = win_round_prop - !!o_win_prop_const
+  )
+
+e_o_win_series_prop <- crossing(
+  pre_cumu_w = 0:5,
+  pre_cumu_l = 0:5
+) |> 
+  mutate(
+    n_remain_max = 11 - (pre_cumu_w + pre_cumu_l),
+    n_remain_w = 6 - pre_cumu_w,
+    ## can i account for offense in this by rotating?
+    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
+  )
+
+o_win_prop <- o_win_prop |> 
+  inner_join(
+    e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
+    by = c('pre_cumu_w', 'pre_cumu_l')
+  ) |> 
+  mutate(
+    diff_win_series_prop = win_series_prop - e_win_series_prop
+  )
+
+common_heatmap_layers <- function(...) {
+  list(
+    ...,
+    guides(
+      fill = 'none'
+    ),
+    scale_x_continuous(
+      labels = 0:5,
+      breaks = seq(.5, 5.5, by = 1),
+      expand = c(0, 0)
+    ),
+    scale_y_continuous(
+      labels = 0:5,
+      breaks = seq(.5, 5.5, by = 1),
+      expand = c(0, 0),
+      sec.axis = sec_axis(
+        trans = I, 
+        name = ' ', 
+        breaks = seq(0.5, 5.5, by = 1), 
+        labels = rep('', 6)
+      )
+    ),
+    theme(
+      panel.grid.major = element_blank(),
+      axis.title = element_text(hjust = 0.5),
+      plot.title = ggtext::element_markdown(hjust = 0.5),
+      axis.text = element_text(size = 16, face = 'bold')
+    ),
+    labs(
+      caption = 'CDL SnD Major and Weekly matches, 2020 - present',
+      tag = '**Viz**: @TonyElHabr | **Data**: @IOUTurtle',
+      x = "Offensive Team's # of Pre-Round Wins",
+      y = "Defensive Team's # of Pre-Round Wins"
+    )
+  )
+}
+
+.dpi <- 300
+save_heatmap <- function(
+    p, 
+    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
+    width = 6, 
+    height = 6,
+    units = 'px',
+    dpi = .dpi,
+    ...
+) {
+  ggsave(
+    plot = p,
+    filename = filename,
+    width = width * dpi,
+    height = height * dpi,
+    units = units,
+    dpi = dpi,
+    ...
+  )
+}
+
+heatmap_tile <- function(..., .fill = '') {
+  list(
+    ...,
+    geom_rect(
+      color = blackish_background,
+      aes(
+        fill = .data[[.fill]],
+        xmin = pre_cumu_w, 
+        ymin = pre_cumu_l,
+        xmax = pre_cumu_w + 1,
+        ymax = pre_cumu_l + 1
+      )
+    )
+  )
+}
+
+heatmap_seq_labeller <- function(.data, .label) {
+  sprintf(
+    '%s\n(%s/%s)', 
+    scales::percent(.data[[.label]], accuracy = 1), 
+    scales::comma(.data$win_round), 
+    scales::comma(.data$n)
+  )
+}
+
+heatmap_text_layer <- function(..., .op, .data, .label, .color, .threshold, .labeller) {
+  list(
+    ...,
+    geom_text(
+      data = .data |> filter(`.op`(.data[[.label]], .threshold)),
+      # family = font,
+      color = .color,
+      size = 11 / .pt,
+      fontface = 'bold',
+      aes(
+        x = pre_cumu_w + 0.5, 
+        y = pre_cumu_l + 0.5,
+        label = .labeller(.data = .data, .label = .label)
+      )
+    )
+  )
+}
+
+add_text_layers <- function(..., .f) {
+  list(
+    ...,
+    .f(.emphasize = 'low'),
+    .f(.emphasize = 'high')
+  )
+}
+```
+
+```{r}
+#| label: p_o_round_win_prop
+add_o_round_win_text_layer <- function(..., .emphasize = 'low') {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- blackish_background
+  } else {
+    op <- `>=`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .data = o_win_prop,
+      .op = op,
+      .label = 'win_round_prop',
+      .color = .color,
+      .threshold = 0.52,
+      .labeller = heatmap_seq_labeller
+    )
+  )
+}
+
+p_o_round_win_prop <- o_win_prop |> 
+  ggplot() +
+  common_heatmap_layers() +
+  heatmap_tile(.fill = 'win_round_prop') +
+  add_text_layers(.f = add_o_round_win_text_layer) +
+  ggsci::scale_fill_material('teal') +
+  labs(
+    title = 'Offensive Round Win %'
+  )
+p_o_round_win_prop
+save_heatmap(p_o_round_win_prop, width = 7.5, height = 5)
+```
+
+::: notes
+-   This should hint at what I'm calling the "4-4" phenomenon, where the o round win % is dramatically higher than adjacent scenarios (3-4, 4-3, 5-4, 4-5, and even 3-3 or 5-5).
+-   Note that round win %s are lower than one might expect in 0-5 and 1-5 states.
+:::
+
+![](o_round_win_prop.png){fig-align="center"}
+
+## How do the empirical round results compare to expectation?
+
+```{r}
+#| label: p_o_round_win_prop_over_expected
+heatmap_div_labeller <- function(.data, .label) {
+  sprintf(
+    '%+.0f\n(%s/%s)', 
+    100 * .data[[.label]], 
+    scales::comma(.data$win_round), 
+    scales::comma(.data$n)
+  )
+}
+
+add_o_round_win_over_expected_text_layer <- function(..., .emphasize) {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- 'white'
+  } else {
+    op <- `>=`
+    .color <- blackish_background
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .data = o_win_prop,
+      .op = op,
+      .label = 'diff_win_round_prop',
+      .color = .color,
+      .threshold = -0.1,
+      .labeller = heatmap_div_labeller
+    )
+  )
+}
+
+extract_ggsci_mid_color <- function(palette) {
+  ggsci::pal_material(palette, n = 3)(2)[2]
+}
+
+max_diff_win_round_prop <- max(abs(o_win_prop$diff_win_round_prop))
+p_o_round_win_prop_over_expected <- o_win_prop |> 
+  ggplot() +
+  common_heatmap_layers() +
+  heatmap_tile(.fill = 'diff_win_round_prop') +
+  add_text_layers(.f = add_o_round_win_over_expected_text_layer) +
+  scale_fill_gradient2(
+    low = extract_ggsci_mid_color('purple'),
+    high = extract_ggsci_mid_color('green'),
+    mid = 'white',
+    midpoint = 0,
+    limits = c(
+      -max_diff_win_round_prop, 
+      +max_diff_win_round_prop
+    )
+  ) +
+  labs(
+    title = 'Offensive Round Win % Over Expected'
+  )
+p_o_round_win_prop_over_expected
+save_heatmap(p_o_round_win_prop_over_expected, width = 7.5, height = 5)
+```
+
+::: notes
+-   This should emphasize the ends of the spectrum seen on the previous graph.
+:::
+
+![](o_round_win_prop_over_expected.png){fig-align="center"}
+
+## What are your chances of winning the series, given the series state?
+
+```{r}
+#| label: p_o_series_win_prop
+add_o_series_win_text_layer <- function(..., .emphasize) {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- blackish_background
+  } else {
+    op <- `>=`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .data = o_win_prop,
+      .op = op,
+      .label = 'win_series_prop',
+      .color = .color,
+      .threshold = 0.52,
+      .labeller = heatmap_seq_labeller
+    )
+  )
+}
+
+p_o_series_win_prop <- o_win_prop |> 
+  ggplot() +
+  common_heatmap_layers() +
+  heatmap_tile(.fill = 'win_series_prop') +
+  add_text_layers(.f = add_o_series_win_text_layer) +
+  ggsci::scale_fill_material('deep-orange') +
+  labs(
+    title = 'Offensive Series Win %'
+  )
+p_o_series_win_prop
+save_heatmap(p_o_series_win_prop, width = 7.5, height = 5)
+```
+
+::: notes
+-   This is mostly just for reference. I think the next slide should have more insight, since it's harder to have a prior understanding about the probability of winning the series given a round state.
+:::
+
+![](o_series_win_prop.png){fig-align="center"}
+
+## How do the empirical series results compare to expectation?
+
+```{r}
+#| label: p_o_series_win_prop_over_expected
+add_o_series_win_over_expected_text_layer <- function(..., .emphasize) {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- blackish_background
+  } else {
+    op <- `>=`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .data = o_win_prop,
+      .op = op,
+      .label = 'diff_win_series_prop',
+      .color = .color,
+      .threshold = 0.08,
+      .labeller = heatmap_div_labeller
+    )
+  )
+}
+
+max_diff_win_series_prop <- max(abs(o_win_prop$diff_win_series_prop))
+p_o_series_win_prop_over_expected <- o_win_prop |> 
+  ggplot() +
+  common_heatmap_layers() +
+  heatmap_tile(.fill = 'diff_win_series_prop') +
+  add_text_layers(.f = add_o_series_win_over_expected_text_layer) +
+  scale_fill_gradient2(
+    low = extract_ggsci_mid_color('brown'),
+    high = extract_ggsci_mid_color('cyan'),
+    mid = 'white',
+    midpoint = 0,
+    limits = c(
+      -max_diff_win_series_prop, 
+      +max_diff_win_series_prop
+    )
+  ) +
+  labs(
+    title = 'Offensive Series Win % Over Expected'
+  )
+p_o_series_win_prop_over_expected
+save_heatmap(p_o_series_win_prop_over_expected, width = 7.5, height = 5)
+```
+
+::: notes
+-   Note the 4-4 and 2-4 series win percentages.
+:::
+
+![](o_series_win_prop_over_expected.png){fig-align="center"}
+
+## Are offensive win %'s different in round 1?
+
+```{r}
+#| label: p_o_win_r1_prop
+calculate_o_round_win_prop <- function(df) {
+  df |> 
+    count(year, game, map, is_offense, win_round) |> 
+    group_by(map, is_offense) |> 
+    mutate(total = sum(n), prop = n / total) |> 
+    ungroup() |>
+    filter(win_round, is_offense) |>
+    select(
+      year,
+      game,
+      map,
+      rounds_won = n,
+      total_rounds = total,
+      win_round_prop = prop
+    ) |>
+    arrange(desc(win_round_prop))
+}
+
+devtools::source_url('https://raw.githubusercontent.com/dgrtwo/splittestr/master/R/vectorized-prop-test.R')
+summarize_o_round_win_prop <- function(.round) {
+
+  specified_round <- rounds |> 
+    filter(round == .round) |> 
+    calculate_o_round_win_prop()
+
+  post_rounds <- rounds |> 
+    filter(round > .round) |> 
+    calculate_o_round_win_prop()
+
+  specified_round |> 
+    inner_join(
+      post_rounds |> rename_with(~sprintf('post_%s', .x), -c(year, game, map)),
+      by = c('year', 'game', 'map')
+    ) |> 
+    mutate(round = .round, .after = 'map') |> 
+    arrange(desc(win_round_prop)) |> 
+    mutate(
+      prop_test = vectorized_prop_test(rounds_won, total_rounds, post_rounds_won, post_total_rounds),
+      p_value = prop_test$p.value
+    ) |> 
+    arrange(p_value) |> 
+    mutate(
+      diff_prop = post_win_round_prop - win_round_prop,
+      dir = factor(sign(diff_prop)),
+      is_significant = p_value < 0.05,
+      label = sprintf('%s - %s (%s)', map, game, year)
+    )
+}
+
+o_win_rx_prop_pal <- c(
+  `-1` = extract_ggsci_mid_color('pink'),
+  `1` = extract_ggsci_mid_color('teal')
+)
+
+arw <- arrow(length = unit(5, 'pt'), type = 'closed')
+
+plot_round_vs_post_round_slope_chart <- function(.round) {
+  o_win_rx_prop <- summarize_o_round_win_prop(.round)
+  x1_label <- sprintf('Round %d<br/>o Win %%', .round)
+  x2_label <- sprintf('Post-Round %d<br/>o Win %%', .round)
+
+  min_o_win_rx_prop <- o_win_rx_prop |> slice_min(diff_prop, n = 1)
+  max_o_win_rx_prop <- o_win_rx_prop |> slice_max(diff_prop, n = 1)
+  minmax_labels <- c(min_o_win_rx_prop$label, max_o_win_rx_prop$label)
+
+  p <- o_win_rx_prop |> 
+    ggplot() +
+    geom_vline(
+      data = tibble(),
+      aes(xintercept = c(1, 2)), 
+      color = gray_points
+    ) +
+    geom_hline(
+      data = tibble(),
+      aes(yintercept = c(0.25, 0.5, 0.75)), 
+      linetype = 2,
+      color = gray_points
+    ) +
+    geom_segment(
+      data = o_win_rx_prop |> 
+        mutate(
+          big_segment = label %in% minmax_labels
+        ),
+      show.legend = FALSE,
+      aes(
+        x = 1,
+        xend = 2,
+        y = win_round_prop,
+        yend = post_win_round_prop,
+        color = dir,
+        size = big_segment,
+        group = label
+      )
+    ) +
+    geom_text(
+      data = tibble(
+        y = c(0.25, 0.75)
+      ) |> 
+        mutate(
+          lab = sprintf('%s%%', round(100 * y))
+        ),
+      aes(x = 2, y = y, label = lab), 
+      size = 12 / .pt,
+      hjust = -0.05,
+      vjust = -0.25,
+      fontface = 'bold',
+      color = 'white'
+    ) +
+    ggtext::geom_richtext(
+      fill = blackish_background, 
+      label.color = NA,
+      data = tibble(
+        x = c(1, 2),
+        y = rep(0.7, 2),
+        lab = c(x1_label, x2_label)
+      ),
+      aes(x = x, y = y, label = lab), 
+      size = 9 / .pt,
+      hjust = 0.5,
+      vjust = 0.5,
+      family = font,
+      fontface = 'bold',
+      color = 'white'
+    ) +
+    ggrepel::geom_text_repel(
+      data = o_win_rx_prop |> 
+        filter(label %in% !!minmax_labels),
+      aes(x = 1, y = win_round_prop, label = label),
+      family = font,
+      fontface = 'bold',
+      color = 'white',
+      size = 9 / .pt,
+      hjust = 'right', 
+      nudge_x = -0.1,
+      direction = 'y'
+    ) +
+    ggrepel::geom_text_repel(
+      data = o_win_rx_prop |> 
+        filter(!(label %in% !!minmax_labels)),
+      aes(x = 2, y = post_win_round_prop, label = label),
+      family = font,
+      color = gray_text,
+      size = 9 / .pt,
+      hjust = 'left', 
+      nudge_x = 0.1,
+      direction = 'y'
+    ) +
+    scale_x_continuous(
+      position = 'top',
+      breaks = c(1, 2),
+      expand = expansion(mult = 0.5)
+    ) +
+    scale_y_continuous(
+      limits = c(0.25, 0.75)
+    ) +
+    scale_size_manual(
+      values = c(
+        `FALSE` = 0.5,
+        `TRUE` = 2
+      )
+    ) +
+    scale_color_manual(
+      name = NULL,
+      values = o_win_rx_prop_pal
+    ) +
+    theme(
+      plot.title = element_text(hjust = 0.5),
+      panel.grid.major = element_blank(),
+      axis.text.x = element_blank(),
+      axis.text.y = element_blank()
+    ) +
+    labs(
+      x = NULL,
+      y = NULL
+    )
+  list(
+    plot = p,
+    data = o_win_rx_prop,
+    largest_neg_diff_prop = min_o_win_rx_prop$diff_prop,
+    largest_pos_diff_prop = max_o_win_rx_prop$diff_prop
+  )
+}
+
+res_r1 <- plot_round_vs_post_round_slope_chart(1)
+
+p_o_win_r1_vs_post_round_prop <- res_r1$plot +
+  geom_curve(
+    data = tibble(),
+    aes(x = 1.2, y = 0.65, xend = 1.1, yend = 0.63),
+    curvature = 0.2, 
+    color = o_win_rx_prop_pal[["-1"]], 
+    arrow = arw
+  ) +
+  geom_curve(
+    data = tibble(),
+    aes(x = 1.24, y = 0.27, xend = 1.1, yend = 0.27),
+    curvature = 0-.2, 
+    color = o_win_rx_prop_pal[["1"]], 
+    arrow = arw
+  ) +
+  geom_text(
+    data = tibble(
+      x = c(1.2, 1.24),
+      y = c(0.65, 0.27),
+      hjust = c(0, 0),
+      vjust = c(0.5, 0.5),
+      lab = c(
+        sprintf(
+          'Largest negative percent difference in round 1\nvs. all other round win percentages (%+.0f%%).', 
+          100 * res_r1$largest_neg_diff_prop
+        ),
+        sprintf(
+          'Largest positive percent difference (%+.0f%%).\nOnly significant difference (p value < 0.01).',
+          100 * res_r1$largest_pos_diff_prop
+        )
+      )
+    ),
+    color = 'white',
+    size = 9 / .pt,
+    aes(x = x, y = y, hjust = hjust, vjust = vjust, label = lab)
+  )
+p_o_win_r1_vs_post_round_prop
+
+save_slope_chart <- function(
+    p, 
+    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
+    width = 7.5, 
+    height = 5,
+    units = 'px',
+    dpi = .dpi,
+    ...
+) {
+
+  ggsave(
+    plot = p,
+    filename = filename,
+    width = 7.5 * .dpi,
+    height = 5 * .dpi,
+    units = units,
+    dpi = dpi,
+    ...
+  )
+}
+
+save_slope_chart(p_o_win_r1_vs_post_round_prop)
+```
+
+![](o_win_r1_vs_post_round_prop.png){fig-align="center"}
+
+::: notes
+-   This might be considered an "information-neutral" setting
+:::
+
+## Are offensive win %'s different in round 2?
+
+```{r}
+res_r2 <- plot_round_vs_post_round_slope_chart(2)
+res_r2$plot
+save_slope_chart(
+  res_r2$plot,
+  filename = 'o_win_r2_vs_post_round_prop.png'
+)
+```
+
+![](o_win_r2_vs_post_round_prop.png){fig-align="center"}
+
+::: notes
+-   no trend
+:::
+
+## What are the most common series winning states?
+
+## How do end states compare to expectation?
+
+::: notes
+-   There should be evidence of 6-0's and 6-5's being more frequent than expected given 50-50% chances. Might need to exclude major matchups, so that series are basically random.
+:::
+
+## Is there evidence for the "hot hand"?
+
+```{r}
+#| label: round_win_prop_after_b2b2b_wins
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 1000, ...) {
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+# prob_n6_k2 <- simulate_post_streak_prob(sims = 10000, n = 6, k = 2, p = 0.5)
+prob_n6_k3 <- simulate_post_streak_prob(sims = 10000, n = 6, k = 3, p = 0.5)
+
+round_streaks <- rounds |> 
+  filter(round <= 6) |> 
+  group_by(year, sheet, series, team) |> 
+  mutate(
+    won_prior_round2 = lag(win_round, n = 2, default = NA),
+    won_prior_round3 = lag(win_round, n = 3, default = NA)
+  ) |> 
+  ungroup() |>
+  select(
+    year,
+    sheet,
+    series,
+    team,
+    is_offense,
+    win_round,
+    won_prior_round,
+    won_prior_round2,
+    won_prior_round3
+  )
+
+round_streaks_after_b2b <- round_streaks |> 
+  filter(!is.na(won_prior_round2)) |> 
+  count(win_round, won_prior_round, won_prior_round2, sort = TRUE)
+
+round_win_prop_after_b2b_wins <- round_streaks_after_b2b |> 
+  filter(won_prior_round, won_prior_round2) |> 
+  mutate(
+    total = sum(n),
+    prop = n / total
+  ) |> 
+  filter(win_round) |> 
+  select(n, total, prop)
+
+round_streaks_after_b2b2b <- round_streaks |> 
+  filter(!is.na(won_prior_round2), !is.na(won_prior_round3)) |> 
+  count(win_round, won_prior_round, won_prior_round2, won_prior_round3, sort = TRUE)
+
+round_win_prop_after_b2b2b_wins <- round_streaks_after_b2b2b |> 
+  filter(won_prior_round, won_prior_round2, won_prior_round3) |> 
+  mutate(
+    total = sum(n),
+    prop = n / total
+  ) |> 
+  filter(win_round) |> 
+  select(n, total, prop)
+```
+
+```{r}
+#| label: round_win_prop_after_b2b2b_wins-eval
+#| eval: true
+prob_n6_k3 <- 0.3838163
+round_win_prop_after_b2b2b_wins <- tibble(
+  n = 352,
+  total = 632
+) |> 
+  mutate(prop = n / total)
+```
+
+::: fragment
+-   Round win % after a streak of 3 round wins:
+    -   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
+    -   Actual: **`r 100 * round(round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r round_win_prop_after_b2b2b_wins$n` / `r round_win_prop_after_b2b2b_wins$total` )
+:::
+
+::: notes
+-   Note this is sort of biased by the fact that teams end up winning series in 6 rounds more often than expected.
+:::
+
+## What is the optimal strategy?
+
+::: notes
+-   plant at most prevalent/winningest site? plant at other site? go for kills?
+:::

### 2022-07-15 x-streaks.R
add research

@@ -30,7 +30,7 @@ runs <- crossing(
   k = 1:3
 ) |> 
   mutate(
-    p = map2_dbl(n, k, ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2))
+    p = map2_dbl(n, k, ~simulate_post_streak_prob(sims = 10000, n = ..1, k = ..2))
   )
 
 runs |>
@@ -44,7 +44,3 @@ runs |>
   geom_step() +
   geom_hline(aes(yintercept = 0.5)) +
   geom_smooth()
-
-simulate_post_streak_prob(sims = 1000, n = 11, k = 3, p = 0.6)
-simulate_post_streak_prob(sims = 1000, n = 6, k = 3, p = 0.5)
-simulate_post_streak_prob(sims = 1000, n = 100, k = 3, p = 0.5)

### 2022-07-15 research/replicate-streaks.R
move streaks

@@ -27,20 +27,24 @@ simulate_post_streak_prob <- function(sims = 1000, ...) {
 
 runs <- crossing(
   n = 1:100,
-  k = 1:3
+  k = 1:5,
+  p = c(0.25, 0.5, 0.75)
 ) |> 
   mutate(
-    p = map2_dbl(n, k, ~simulate_post_streak_prob(sims = 10000, n = ..1, k = ..2))
+    next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 10000, n = ..1, k = ..2, p = ..3))
   )
 
-runs |>
+p_streaks <- runs |>
   arrange(n, k) |>
   mutate(
-    across(k, factor)
+    across(k, factor),
+    group = sprintf('%s-%s', p, k)
   ) |> 
   ggplot() +
   theme_minimal() +
-  aes(x = n, y = p, color = k, group = k) +
+  aes(x = n, y = next_p, color = k, group = group) +
   geom_step() +
-  geom_hline(aes(yintercept = 0.5)) +
-  geom_smooth()
+  # facet_wrap(~p, scales = 'free_y') +
+  geom_hline(aes( yintercept = p))
+p_streaks
+ggsave(p_streaks, filename = 'research/streaks.png', width = 12, height = 6)

### 2022-07-15 presentation.qmd
better pres name, start looking at b2b

@@
 ---
-title: "Momentum in Round-Based First-Person-Shooter (FPS) E-Sports"
+title: "Streaking and Clutching in Round-Based First Person Shooter (FPS) Esports"
 author: "Tony ElHabr"
@@
 
-heatmap_tile <- function(..., .fill = '') {
+heatmap_tile <- function(..., .xmin, .xmax, .ymin, .ymax, .fill) {
   list(
@@
         fill = .data[[.fill]],
-        xmin = pre_cumu_w, 
-        ymin = pre_cumu_l,
-        xmax = pre_cumu_w + 1,
-        ymax = pre_cumu_l + 1
-      )
-    )
+        xmin = .data[[.xmin]], 
+        ymin = .data[[.ymin]],
+        xmax = .data[[.xmin]], + 1,
+        ymax = .data[[.ymin]] + 1
+      )
+    )
+  )
+}
+
+pre_cumu_heatmap_tile <- function(..., .fill) {
+  heatmap_tile(
+    .xmin = 'pre_cumu_w',
+    .ymin = 'pre_cumu_l',
+    .fill = .fill,
+    ...
   )
@@
   common_heatmap_layers() +
-  heatmap_tile(.fill = 'win_round_prop') +
+  pre_cumu_heatmap_tile(.fill = 'win_round_prop') +
   add_text_layers(.f = add_o_round_win_text_layer) +
@@
   common_heatmap_layers() +
-  heatmap_tile(.fill = 'diff_win_round_prop') +
+  pre_cumu_heatmap_tile(.fill = 'diff_win_round_prop') +
   add_text_layers(.f = add_o_round_win_over_expected_text_layer) +
@@
   common_heatmap_layers() +
-  heatmap_tile(.fill = 'win_series_prop') +
+  pre_cumu_heatmap_tile(.fill = 'win_series_prop') +
   add_text_layers(.f = add_o_series_win_text_layer) +
@@
   common_heatmap_layers() +
-  heatmap_tile(.fill = 'diff_win_series_prop') +
+  pre_cumu_heatmap_tile(.fill = 'diff_win_series_prop') +
   add_text_layers(.f = add_o_series_win_over_expected_text_layer) +
@@
 
+```{r}
+#| label: series_outcomes
+prior_clinching_round_win_prop <- rounds |> 
+  filter(round == (n_rounds - 1L)) |> 
+  count(n_rounds, win_series, won_prior_round = win_round) |> 
+  mutate(
+    across(win_series, ~ifelse(.x, 'win', 'loss'))
+  ) |> 
+  pivot_wider(
+    names_from = win_series,
+    values_from = n,
+    values_fill = 0L
+  ) |> 
+  filter(won_prior_round) |> 
+  select(-won_prior_round) |> 
+  mutate(
+    win_series_prop = win / (win + loss),
+    e_win_series_prop = (6L - 1L) / (n_rounds - 1L)
+  )
+
+n_rounds_max <- 11
+n_sims <- 100000
+set.seed(42)
+w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE)
+
+sim_rounds <- tibble(
+  i = rep(1:n_sims, each = n_rounds_max),
+  r = rep(1:n_sims, times = n_rounds_max),
+  w = w
+) |> 
+  group_by(i) |> 
+  mutate(
+    cumu_w = cumsum(w),
+    cumu_l = cumsum(w == 0)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    cumu_wl_max = ifelse(cumu_w > cumu_l, cumu_w, cumu_l)
+  ) |> 
+  filter(cumu_wl_max <= 6)
+
+sim_rounds_to_drop <- anti_join(
+  sim_rounds |> 
+    filter(cumu_wl_max == 6L),
+  sim_rounds |> 
+    filter(cumu_wl_max == 6L) |> 
+    group_by(i) |> 
+    slice_min(r, n = 1) |> 
+    ungroup()
+)
+
+sim_rounds <- sim_rounds |> 
+  anti_join(
+    sim_rounds_to_drop
+  )
+
+## always from offensive perspective
+e_series_streaks <- sim_rounds |> 
+  inner_join(
+    sim_rounds |> 
+      filter(cumu_wl_max == 6) |> 
+      mutate(
+        zeros_win = cumu_l == cumu_wl_max
+      ) |> 
+      select(i, zeros_win)
+  ) |> 
+  mutate(
+    across(w, ~ifelse(zeros_win, abs(1 - .x), .x))
+  ) |> 
+  group_by(i) |> 
+  summarize(
+    cumu_w = max(cumu_w),
+    cumu_l = max(cumu_l),
+    ws = paste0(w, collapse = '')
+  ) |> 
+  ungroup() |> 
+  mutate(
+    wins = ifelse(cumu_w == 6, cumu_w, cumu_l),
+    losses = ifelse(cumu_w == 6, cumu_l, cumu_w)
+  ) |> 
+  unite(
+    record, wins, losses, sep = '-'
+  ) |> 
+  count(record, ws, sort = TRUE) |> 
+  mutate(prop = n / sum(n))
+
+actual_series_streaks <- rounds |> 
+  filter(win_series) |> 
+  mutate(across(win_round, as.integer)) |> 
+  group_by(year, event, series) |> 
+  summarize(
+    wins = max(cumu_w),
+    losses = max(cumu_l),
+    ws = paste0(win_round, collapse = '')
+  ) |> 
+  ungroup() |> 
+  unite(
+    record, wins, losses, sep = '-'
+  ) |> 
+  count(record, ws, sort = TRUE) |> 
+  mutate(prop = n / sum(n))
+
+series_streaks <- full_join(
+  actual_series_streaks |> 
+    rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+  e_series_streaks |> 
+    rename_with(~sprintf('%s_expected', .x), c(n, prop))
+) |> 
+  mutate(
+    prop_diff = prop_actual - prop_expected
+  ) |> 
+  arrange(desc(abs(prop_diff)))
+series_streaks |> filter(is.na(n_actual))
+
+## 6-0, 6-1, and some combos of 6-5 occur more often than expected
+series_streaks |> 
+  filter(!is.na(n_actual)) |> 
+  mutate(total_actual = sum(n_actual)) |> 
+  mutate(
+    p = vectorized_prop_test(n_actual, total_actual, n_expected, !!n_sims)
+  ) |> 
+  select(-total_actual) |> 
+  arrange(p$p.value)
+
+## 6-0 and 6-1 occur more often than expected
+series_outcomes <- full_join(
+  actual_series_streaks |> 
+    group_by(record) |> 
+    summarize(
+      across(n, sum)
+    ) |> 
+    mutate(prop = n / sum(n)) |> 
+    rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+  e_series_streaks |> 
+    group_by(record) |> 
+    summarize(
+      across(n, sum)
+    ) |> 
+    mutate(prop = n / sum(n)) |> 
+    rename_with(~sprintf('%s_expected', .x), c(n, prop))
+) |> 
+  mutate(
+    prop_diff = prop_actual - prop_expected
+  ) |> 
+  arrange(desc(abs(prop_diff))) |> 
+  mutate(total_actual = sum(n_actual)) |> 
+  mutate(
+    p = vectorized_prop_test(n_actual, total_actual, n_expected, !!n_sims)
+  ) |> 
+  select(-total_actual) |> 
+  arrange(p$p.value)
+
+series_outcomes |> 
+  select(record, actual = prop_actual, expected = prop_expected, diff = prop_diff) |> 
+  pivot_longer(
+    -record,
+    names_to = 'prop',
+    values_to = 'value'
+  ) |> 
+  mutate(
+    across(
+      prop,
+      factor, 
+      levels = c('actual', 'expected', 'diff')
+    )
+  ) |> 
+  ggplot() +
+  aes(x = record, y = prop) +
+  geom_tile(
+    show.legend = FALSE,
+    aes(fill = value)
+  ) +
+  scale_x_discrete(
+    position = 'top'
+  )
+
+```
+
 ::: notes
@@
 :::
+
+## When do back-to-back round wins occur?
+
+```{r}
+summarize_b2b_round_wins <- function(df, ...) {
+  df |> 
+    arrange(year, sheet, series, team, round) |> 
+    group_by(year, sheet, series, team) |> 
+    mutate(
+      b2b_round_wins = win_round & lag(win_round)
+    ) |> 
+    ungroup() |> 
+    filter(round > 1L) |> 
+    count(..., round, b2b_round_wins) |> 
+    group_by(..., round) |> 
+    mutate(total = sum(n), prop = n / total) |> 
+    ungroup() |> 
+    filter(b2b_round_wins) |> 
+    select(-b2b_round_wins)
+}
+
+pre_cumu_heatmap_tile <- function(..., .fill) {
+  heatmap_tile(
+    .xmin = 'n_rounds',
+    .ymin = 'round',
+    .fill = .fill,
+    ...
+  )
+}
+
+## now accounting for number of rounds that end up being played...
+## seems like there is interesting behavior in the last round, regardless `n_rounds`
+b2b_round_win_props <- rounds |> 
+  filter(n_rounds > 6L) |> 
+  summarize_b2b_round_wins(n_rounds)
+
+b2b_round_win_props |> 
+  ggplot() +
+  pre_cumu_heatmap_tile(.fill = 'prop')
+
+b2b_round_win_props |> 
+  filter(n_rounds > 6L) |> 
+  summarize_b2b_round_wins(n_rounds) |> 
+  group_by(n_rounds) |> 
+  mutate(
+    intra_prop = (n - mean(n)) / sd(n)
+  ) |> 
+  ggplot() +
+  aes(x = n_rounds, y = round) +
+  geom_tile(aes(fill = intra_prop))
+
+## now accounting for number of rounds that end up being played AND series winners...
+rounds |> 
+  filter(win_series, n_rounds > 6L) |> 
+  summarize_b2b_round_wins(n_rounds)
+
+## and the losers...
+rounds |> 
+  filter(!win_series) |> 
+  summarize_b2b_round_wins(n_rounds)
+```
 
@@
 ::: notes
--   plant at most prevalent/winningest site? plant at other site? go for kills?
-:::
+-   Should you plant at most prevalent/winningest site? plant at other site? Go for kills?
+:::

### 2022-07-16 presentation.qmd
add b2b win props

@@
 #| label: cod_heatmap_prep
-summarize_rounds <- function(rounds, ...) {
-  rounds |> 
-    group_by(pre_cumu_w, pre_cumu_l, ...) |> 
+n_rounds_side <- rounds |> 
+  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
   summarize(
@@
   )
-}
-
-n_rounds_side <- rounds |> summarize_rounds(is_offense)
+
 o_win_prop <- n_rounds_side |> 
@@
 
-common_heatmap_layers <- function(...) {
+common_cod_labs <- function(...) {
+  list(
+    ...,
+    labs(
+      caption = 'CDL SnD Major and Weekly matches, 2020 - present',
+      tag = '**Viz**: @TonyElHabr | **Data**: @IOUTurtle'
+    )
+  )
+}
+
+common_cod_heatmap_layers <- function(...) {
   list(
@@
       labels = 0:5,
-      breaks = seq(.5, 5.5, by = 1),
+      breaks = seq(0.5, 5.5, by = 1),
       expand = c(0, 0)
@@
       labels = 0:5,
-      breaks = seq(.5, 5.5, by = 1),
+      breaks = seq(0.5, 5.5, by = 1),
       expand = c(0, 0),
@@
     ),
+    common_cod_labs(),
     labs(
-      caption = 'CDL SnD Major and Weekly matches, 2020 - present',
-      tag = '**Viz**: @TonyElHabr | **Data**: @IOUTurtle',
       x = "Offensive Team's # of Pre-Round Wins",
@@
     filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
-    width = 6, 
-    height = 6,
+    width = 7.5, 
+    height = 5,
     units = 'px',
@@
 
-heatmap_tile <- function(..., .xmin, .xmax, .ymin, .ymax, .fill) {
+heatmap_tile <- function(..., .fill) {
   list(
@@
         fill = .data[[.fill]],
-        xmin = .data[[.xmin]], 
-        ymin = .data[[.ymin]],
-        xmax = .data[[.xmin]], + 1,
-        ymax = .data[[.ymin]] + 1
-      )
-    )
-  )
-}
-
-pre_cumu_heatmap_tile <- function(..., .fill) {
-  heatmap_tile(
-    .xmin = 'pre_cumu_w',
-    .ymin = 'pre_cumu_l',
-    .fill = .fill,
-    ...
+        xmin = pre_cumu_w, 
+        ymin = pre_cumu_l,
+        xmax = pre_cumu_w + 1,
+        ymax = pre_cumu_l + 1
+      )
+    )
   )
@@
 
-add_text_layers <- function(..., .f) {
+heatmap_text_layers <- function(..., .f) {
   list(
@@
 #| label: p_o_round_win_prop
-add_o_round_win_text_layer <- function(..., .emphasize = 'low') {
+o_round_win_text_layer <- function(..., .emphasize = 'low') {
   if(.emphasize == 'low') {
@@
   ggplot() +
-  common_heatmap_layers() +
-  pre_cumu_heatmap_tile(.fill = 'win_round_prop') +
-  add_text_layers(.f = add_o_round_win_text_layer) +
+  common_cod_heatmap_layers() +
+  heatmap_tile(.fill = 'win_round_prop') +
+  heatmap_text_layers(.f = o_round_win_text_layer) +
   ggsci::scale_fill_material('teal') +
@@
 p_o_round_win_prop
-save_heatmap(p_o_round_win_prop, width = 7.5, height = 5)
+save_heatmap(p_o_round_win_prop)
 ```
@@
 
-add_o_round_win_over_expected_text_layer <- function(..., .emphasize) {
+o_round_win_over_expected_text_layer <- function(..., .emphasize) {
   if(.emphasize == 'low') {
@@
   ggplot() +
-  common_heatmap_layers() +
+  common_cod_heatmap_layers() +
   pre_cumu_heatmap_tile(.fill = 'diff_win_round_prop') +
-  add_text_layers(.f = add_o_round_win_over_expected_text_layer) +
+  heatmap_text_layers(.f = o_round_win_over_expected_text_layer) +
   scale_fill_gradient2(
@@
 p_o_round_win_prop_over_expected
-save_heatmap(p_o_round_win_prop_over_expected, width = 7.5, height = 5)
+save_heatmap(p_o_round_win_prop_over_expected)
 ```
@@
   ggplot() +
-  common_heatmap_layers() +
+  common_cod_heatmap_layers() +
   pre_cumu_heatmap_tile(.fill = 'win_series_prop') +
-  add_text_layers(.f = add_o_series_win_text_layer) +
+  heatmap_text_layers(.f = add_o_series_win_text_layer) +
   ggsci::scale_fill_material('deep-orange') +
@@
 p_o_series_win_prop
-save_heatmap(p_o_series_win_prop, width = 7.5, height = 5)
+save_heatmap(p_o_series_win_prop)
 ```
@@
   ggplot() +
-  common_heatmap_layers() +
+  common_cod_heatmap_layers() +
   pre_cumu_heatmap_tile(.fill = 'diff_win_series_prop') +
-  add_text_layers(.f = add_o_series_win_over_expected_text_layer) +
+  heatmap_text_layers(.f = add_o_series_win_over_expected_text_layer) +
   scale_fill_gradient2(
@@
 p_o_series_win_prop_over_expected
-save_heatmap(p_o_series_win_prop_over_expected, width = 7.5, height = 5)
+save_heatmap(p_o_series_win_prop_over_expected)
 ```
@@
 ::: notes
--   There should be evidence of 6-0's and 6-5's being more frequent than expected given 50-50% chances. Might need to exclude major matchups, so that series are basically random.
+-   There should be evidence of 6-0's and 6-5's being more frequent than expected given 50-50% chances.
 :::
@@
 
-pre_cumu_heatmap_tile <- function(..., .fill) {
-  heatmap_tile(
-    .xmin = 'n_rounds',
-    .ymin = 'round',
-    .fill = .fill,
-    ...
-  )
-}
-
 ## now accounting for number of rounds that end up being played...
@@
   filter(n_rounds > 6L) |> 
-  summarize_b2b_round_wins(n_rounds)
-
-b2b_round_win_props |> 
-  ggplot() +
-  pre_cumu_heatmap_tile(.fill = 'prop')
-
-b2b_round_win_props |> 
-  filter(n_rounds > 6L) |> 
   summarize_b2b_round_wins(n_rounds) |> 
@@
   mutate(
-    intra_prop = (n - mean(n)) / sd(n)
-  ) |> 
+    z = (n - mean(n)) / sd(n),
+    rnk = row_number(desc(n))
+  ) |> 
+  ungroup()
+
+b2b_round_win_props_tile_layer <- function(..., .round, .palette, .is_new = TRUE) {
+
+  init <- if(!.is_new) {
+    list()
+  } else {
+    ggnewscale::new_scale_fill()
+  }
+
+  list(
+    ...,
+    init,
+    geom_tile(
+      data = b2b_round_win_props |> filter(n_rounds == .round),
+      color = blackish_background,
+      height = 0.8,
+      show.legend = FALSE,
+      aes(
+        fill = z,
+        x = round + 0.5, 
+        y = n_rounds + 0.5
+      )
+    ),
+    ggsci::scale_fill_material(palette = .palette) 
+  )
+}
+
+b2b_round_win_prop_text_layer <- function(..., .emphasize) {
+  if(.emphasize == 'low') {
+    op <- `>`
+    .color <- blackish_background
+  } else {
+    op <- `==`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    geom_text(
+      data = b2b_round_win_props |> filter(`op`(rnk, 1)),
+      color = .color,
+      size = 11 / .pt,
+      fontface = 'bold',
+      aes(
+        label = sprintf('%s\n(%s)', scales::percent(prop, accuracy = 1), scales::comma(n)),
+        x = round + 0.5, 
+        y = n_rounds + 0.5
+      )
+    )
+  )
+}
+
+b2b_round_win_prop_text_layers <- function(...) {
+  list(
+    ...,
+    b2b_round_win_prop_text_layer(.emphasize = 'low'),
+    b2b_round_win_prop_text_layer(.emphasize = 'high')
+  )
+}
+
+b2b_round_win_props_arws <- tibble(
+  x = c(9.3, 9.4, 9.75, 10),
+  y = c(8.25, 8.5, 8.75, 8.75),
+  xend = c(8.1, 9.1, 9.5, 10.5),
+  yend = c(7.5, 8.5, 9, 10),
+  curvature = c(-0.2, -0.1, 0.1, 0.2)
+) |> 
+  mutate(
+    rn = row_number()
+  )
+
+p_b2b_round_win_props <- b2b_round_win_props |> 
   ggplot() +
-  aes(x = n_rounds, y = round) +
-  geom_tile(aes(fill = intra_prop))
-
-## now accounting for number of rounds that end up being played AND series winners...
-rounds |> 
-  filter(win_series, n_rounds > 6L) |> 
-  summarize_b2b_round_wins(n_rounds)
-
-## and the losers...
-rounds |> 
-  filter(!win_series) |> 
-  summarize_b2b_round_wins(n_rounds)
-```
+  b2b_round_win_props_tile_layer(.round = 7, .palette = 'pink', .is_new = FALSE) +
+  b2b_round_win_props_tile_layer(.round = 8, .palette = 'light-blue') +
+  b2b_round_win_props_tile_layer(.round = 9, .palette = 'light-green') +
+  b2b_round_win_props_tile_layer(.round = 10, .palette = 'amber') +
+  b2b_round_win_props_tile_layer(.round = 11, .palette = 'deep-orange') +
+  b2b_round_win_prop_text_layers() +
+  scale_x_continuous(
+    labels = 2:11,
+    breaks = seq(2.5, 11.5, by = 1),
+    expand = c(0, 0.5)
+  ) +
+  scale_y_continuous(
+    labels = 7:11,
+    breaks = seq(7.5, 11.5, by = 1),
+    expand = c(0, 0)
+  ) +
+  theme(
+    panel.grid.major = element_blank(),
+    axis.title = element_text(hjust = 0.5),
+    plot.title = ggtext::element_markdown(hjust = 0.5),
+    axis.text = element_text(size = 16, face = 'bold')
+  ) +
+  common_cod_labs() +
+  labs(
+    title = 'Back-to-back round win %',
+    x = 'Round',
+    y = '# of Rounds in Complete Series'
+  ) + 
+  geom_text(
+    data = tibble(
+      label = 'Back-to-back wins occur most\nfrequently in the last round.',
+      x = 9.5,
+      y = 8.5
+    ),
+    size = 9 / .pt,
+    fontface = 'bold',
+    color = 'white',
+    hjust = 0,
+    vjust = 0.5,
+    aes(x = x, y = y, label = label)
+  ) +
+  map(
+    b2b_round_win_props_arws |> group_split(rn), 
+    function(.x) {
+      geom_curve(
+        data = data.frame(),
+        color = 'white',
+        arrow = arw,
+        aes(x = .x$x, y = .x$y, xend = .x$xend, yend = .x$yend),
+        curvature = .x$curvature
+      )
+    }
+  )
+save_heatmap(p_b2b_round_win_props)
+# ## now accounting for number of rounds that end up being played AND series winners...
+# rounds |> 
+#   filter(win_series, n_rounds > 6L) |> 
+#   summarize_b2b_round_wins(n_rounds)
+# 
+# ## and the losers...
+# rounds |> 
+#   filter(!win_series) |> 
+#   summarize_b2b_round_wins(n_rounds)
+```
+
+![](b2b_round_win_props.png){fig-align="center"}
 

### 2022-07-17 presentation.qmd
reformat bullets
make a good looking pdf with renderthis

@@
 ---
-title: "Streaking and Clutching in Round-Based First Person Shooter (FPS) Esports"
+title: "Streaking and Clutching in Round-Based First Person Shooter Esports"
 author: "Tony ElHabr"
@@
 library(ggsci)
+library(ggnewscale)
 blackish_background <- '#191919' ## to match slide background
@@
     labs(
-      caption = 'CDL SnD Major and Weekly matches, 2020 - present',
-      tag = '**Viz**: @TonyElHabr | **Data**: @IOUTurtle'
+      caption = 'CDL SnD Major and Weekly matches, 2020 - present'
     )
@@
 .dpi <- 300
-save_heatmap <- function(
+save_for_slide <- function(
     p, 
@@
     width = 7.5, 
-    height = 5,
+    height = width / 1.5,
     units = 'px',
@@
 p_o_round_win_prop
-save_heatmap(p_o_round_win_prop)
+save_for_slide(p_o_round_win_prop)
 ```
@@
   common_cod_heatmap_layers() +
-  pre_cumu_heatmap_tile(.fill = 'diff_win_round_prop') +
+  heatmap_tile(.fill = 'diff_win_round_prop') +
   heatmap_text_layers(.f = o_round_win_over_expected_text_layer) +
@@
 p_o_round_win_prop_over_expected
-save_heatmap(p_o_round_win_prop_over_expected)
+save_for_slide(p_o_round_win_prop_over_expected)
 ```
@@
   common_cod_heatmap_layers() +
-  pre_cumu_heatmap_tile(.fill = 'win_series_prop') +
+  heatmap_tile(.fill = 'win_series_prop') +
   heatmap_text_layers(.f = add_o_series_win_text_layer) +
@@
 p_o_series_win_prop
-save_heatmap(p_o_series_win_prop)
+save_for_slide(p_o_series_win_prop)
 ```
@@
   common_cod_heatmap_layers() +
-  pre_cumu_heatmap_tile(.fill = 'diff_win_series_prop') +
+  heatmap_tile(.fill = 'diff_win_series_prop') +
   heatmap_text_layers(.f = add_o_series_win_over_expected_text_layer) +
@@
 p_o_series_win_prop_over_expected
-save_heatmap(p_o_series_win_prop_over_expected)
+save_for_slide(p_o_series_win_prop_over_expected)
 ```
@@
 ```{r}
-#| label: p_o_win_r1_prop
+#| label: o_win_r1_vs_post_round_pro
 calculate_o_round_win_prop <- function(df) {
@@
 
-devtools::source_url('https://raw.githubusercontent.com/dgrtwo/splittestr/master/R/vectorized-prop-test.R')
+# https://raw.githubusercontent.com/dgrtwo/splittestr/master/R/vectorized-prop-test.R
+vectorized_prop_test_approx <- function(a, b, c, d) {
+  n1 <- a + b
+  n2 <- c + d
+  n <- n1 + n2
+  p <- (a + c) / n
+  E <- cbind(p * n1, (1 - p) * n1, p * n2, (1 - p) * n2)
+
+  x <- cbind(a, b, c, d)
+
+  DELTA <- a / n1 - c / n2
+  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
+
+  STATISTIC <- rowSums((abs(x - E) - YATES)^2 / E)
+  PVAL <- pchisq(STATISTIC, 1, lower.tail = FALSE)
+  PVAL
+}
+
+vectorized_prop_test_exact <- function(a, b, c, d) {
+  sapply(seq_along(a), function(i) {
+    fisher.test(cbind(c(a[i], c[i]), c(b[i], d[i])))$p.value
+  })
+}
+
+vectorized_prop_test <- function(x1, n1, x2, n2, conf.level = .95) {
+  a <- x1
+  b <- n1 - x1
+  c <- x2
+  d <- n2 - x2
+
+  # if any values are < 20, use Fisher's exact test
+  exact <- (a < 20 | b < 20 | c < 20 | d < 20)
+
+  pvalue <- rep(NA, length(a))
+
+  if (any(exact)) {
+    pvalue[exact] <- vectorized_prop_test_exact(a[exact], b[exact], c[exact], d[exact])
+  }
+  if (any(!exact)) {
+    pvalue[!exact] <- vectorized_prop_test_approx(a[!exact], b[!exact], c[!exact], d[!exact])
+  }
+
+  mu1 <- a / (a + b)
+  mu2 <- c / (c + d)
+
+  ## confidence interval
+  alpha2 <- (1 - conf.level) / 2
+  DELTA <- mu2 - mu1
+  WIDTH <- qnorm(alpha2)
+  alpha <- (a + .5) / (a + b + 1)
+  beta <- (c + .5) / (c + d + 1)
+
+  n <- n1 + n2
+  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
+
+  z <- qnorm((1 + conf.level) / 2)
+  WIDTH <- z * sqrt(mu1 * (1 - mu1) / n1 + mu2 * (1 - mu2) / n2)
+
+  tibble(
+    estimate = DELTA,
+    conf.low = pmax(DELTA - WIDTH, -1),
+    conf.high = pmin(DELTA + WIDTH, 1),
+    p.value = pvalue
+  )
+}
+
 summarize_o_round_win_prop <- function(.round) {
@@
 p_o_win_r1_vs_post_round_prop
-
-save_slope_chart <- function(
-    p, 
-    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
-    width = 7.5, 
-    height = 5,
-    units = 'px',
-    dpi = .dpi,
-    ...
-) {
-
-  ggsave(
-    plot = p,
-    filename = filename,
-    width = 7.5 * .dpi,
-    height = 5 * .dpi,
-    units = units,
-    dpi = dpi,
-    ...
-  )
-}
-
-save_slope_chart(p_o_win_r1_vs_post_round_prop)
+save_for_slide(p_o_win_r1_vs_post_round_prop)
 ```
@@
 ```{r}
+#| label: o_win_r2_vs_post_round_pro
 res_r2 <- plot_round_vs_post_round_slope_chart(2)
 res_r2$plot
-save_slope_chart(
+save_for_slide(
   res_r2$plot,
@@
 
-## How do end states compare to expectation?
-
 ```{r}
-#| label: series_outcomes
+#| label: p_series_outcome_prop_over_expected
 prior_clinching_round_win_prop <- rounds |> 
@@
   arrange(desc(abs(prop_diff)))
-series_streaks |> filter(is.na(n_actual))
+# series_streaks |> filter(is.na(n_actual))
 
 ## 6-0, 6-1, and some combos of 6-5 occur more often than expected
-series_streaks |> 
+series_streak_props <- series_streaks |> 
   filter(!is.na(n_actual)) |> 
@@
 ## 6-0 and 6-1 occur more often than expected
-series_outcomes <- full_join(
+series_outcome_prop <- full_join(
   actual_series_streaks |> 
@@
   mutate(
-    prop_diff = prop_actual - prop_expected
-  ) |> 
-  arrange(desc(abs(prop_diff))) |> 
-  mutate(total_actual = sum(n_actual)) |> 
-  mutate(
-    p = vectorized_prop_test(n_actual, total_actual, n_expected, !!n_sims)
+    prop_diff = prop_actual - prop_expected,
+    total_actual = sum(n_actual),
+    n_expected_downsampled = round(prop_expected * total_actual),
+    p = vectorized_prop_test(n_actual, total_actual, n_expected_downsampled, total_actual)
   ) |> 
@@
 
-series_outcomes |> 
-  select(record, actual = prop_actual, expected = prop_expected, diff = prop_diff) |> 
+long_series_outcome_prop <- series_outcome_prop |>
+  unnest(p) |>
+  select(
+    record,
+    n = n_actual,
+    `3` = prop_actual,
+    `2` = prop_expected,
+    `1` = prop_diff
+  ) |> 
   pivot_longer(
-    -record,
-    names_to = 'prop',
+    matches('[123]'),
+    names_to = 'outcome_idx',
     values_to = 'value'
   ) |> 
-  mutate(
-    across(
-      prop,
-      factor, 
-      levels = c('actual', 'expected', 'diff')
-    )
-  ) |> 
+  mutate(across(outcome_idx, as.integer))
+
+max_diff_series_outcome_prop <- long_series_outcome_prop |> 
+  filter(outcome_idx == 1) |> 
+  pull(value) |> 
+  abs() |> 
+  max()
+
+p_series_outcome_prop_over_expected <- long_series_outcome_prop |> 
   ggplot() +
-  aes(x = record, y = prop) +
+  aes(x = record, y = outcome_idx) +
   geom_tile(
+    data = long_series_outcome_prop |> filter(outcome_idx > 1),
     show.legend = FALSE,
+    # height = 0.8,
     aes(fill = value)
   ) +
+  ggsci::scale_fill_material(
+    palette = 'orange'
+  ) +
+  ggnewscale::new_scale_fill() +
+  geom_tile(
+    data = long_series_outcome_prop |> filter(outcome_idx == 1),
+    show.legend = FALSE,
+    height = 0.8,
+    aes(fill = value)
+  ) +
+  scale_fill_gradient2(
+    low = extract_ggsci_mid_color('purple'),
+    high = extract_ggsci_mid_color('green'),
+    mid = 'white',
+    midpoint = 0,
+    limits = c(
+      -max_diff_series_outcome_prop, 
+      +max_diff_series_outcome_prop
+    )
+  ) +
+  geom_text(
+    data = long_series_outcome_prop |> filter(outcome_idx == 3),
+    color = blackish_background,
+    size = 11 / .pt,
+    aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
+  ) +
+  geom_text(
+    data = long_series_outcome_prop |> filter(outcome_idx == 2),
+    color = blackish_background,
+    size = 11 / .pt,
+    aes(label = sprintf('%.1f%%', 100 * value))
+  ) +
+  geom_text(
+    data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
+    color = blackish_background,
+    size = 11 / .pt,
+    aes(label = sprintf('%+.1f%%', 100 * value))
+  ) +
+  geom_text(
+    data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
+    color = 'white',
+    size = 11 / .pt,
+
+    aes(label = sprintf('%+.1f%%', 100 * value))
+  ) +
   scale_x_discrete(
-    position = 'top'
-  )
-
+    position = 'top',
+    expand = c(0, 0)
+  ) +
+  scale_y_continuous(
+    labels = c('Diff.', 'Expected', 'Actual'),
+    breaks = 1:3,
+    expand = c(0, 0)
+  ) +
+  theme(
+    panel.grid.major = element_blank(),
+    axis.title = element_text(hjust = 0.5),
+    plot.title = ggtext::element_markdown(hjust = 0.5),
+    axis.text = element_text(size = 16, face = 'bold')
+  ) +
+  labs(
+    title = 'Series outcome %',
+    x = NULL,
+    y = NULL
+  ) +
+  common_cod_labs() 
+p_series_outcome_prop_over_expected
+save_for_slide(p_series_outcome_prop_over_expected)
 ```
 
+![](series_outcome_prop_over_expected.png){fig-align="center"}
+
 ::: notes
--   There should be evidence of 6-0's and 6-5's being more frequent than expected given 50-50% chances.
+-   There should be evidence of 6-0's and 6-1's are more frequent than expected given 50-50% chances.
+-   Notably 6-4's occur less frequently than expected
+-   p-values are not significant for any
 :::
@@
 ```{r}
+#| label: p_b2b_round_win_prop
 summarize_b2b_round_wins <- function(df, ...) {
@@
 ## seems like there is interesting behavior in the last round, regardless `n_rounds`
-b2b_round_win_props <- rounds |> 
+b2b_round_win_prop <- rounds |> 
   filter(n_rounds > 6L) |> 
@@
 
-b2b_round_win_props_tile_layer <- function(..., .round, .palette, .is_new = TRUE) {
+b2b_round_win_prop_tile_layer <- function(..., .round, .palette, .is_new = TRUE) {
 
@@
     geom_tile(
-      data = b2b_round_win_props |> filter(n_rounds == .round),
+      data = b2b_round_win_prop |> filter(n_rounds == .round),
       color = blackish_background,
@@
     geom_text(
-      data = b2b_round_win_props |> filter(`op`(rnk, 1)),
+      data = b2b_round_win_prop |> filter(`op`(rnk, 1)),
       color = .color,
@@
 
-b2b_round_win_props_arws <- tibble(
+b2b_round_win_prop_arws <- tibble(
   x = c(9.3, 9.4, 9.75, 10),
@@
 
-p_b2b_round_win_props <- b2b_round_win_props |> 
+p_b2b_round_win_prop <- b2b_round_win_prop |> 
   ggplot() +
-  b2b_round_win_props_tile_layer(.round = 7, .palette = 'pink', .is_new = FALSE) +
-  b2b_round_win_props_tile_layer(.round = 8, .palette = 'light-blue') +
-  b2b_round_win_props_tile_layer(.round = 9, .palette = 'light-green') +
-  b2b_round_win_props_tile_layer(.round = 10, .palette = 'amber') +
-  b2b_round_win_props_tile_layer(.round = 11, .palette = 'deep-orange') +
+  b2b_round_win_prop_tile_layer(.round = 7, .palette = 'pink', .is_new = FALSE) +
+  b2b_round_win_prop_tile_layer(.round = 8, .palette = 'light-blue') +
+  b2b_round_win_prop_tile_layer(.round = 9, .palette = 'light-green') +
+  b2b_round_win_prop_tile_layer(.round = 10, .palette = 'amber') +
+  b2b_round_win_prop_tile_layer(.round = 11, .palette = 'deep-orange') +
   b2b_round_win_prop_text_layers() +
@@
   map(
-    b2b_round_win_props_arws |> group_split(rn), 
+    b2b_round_win_prop_arws |> group_split(rn), 
     function(.x) {
@@
   )
-save_heatmap(p_b2b_round_win_props)
+save_for_slide(p_b2b_round_win_prop)
 # ## now accounting for number of rounds that end up being played AND series winners...
@@
 
-![](b2b_round_win_props.png){fig-align="center"}
+![](b2b_round_win_prop.png){fig-align="center"}
 
@@
 
+```{r}
+#| label: plant_win_prop_proj
+map_plant_win_prop <- rounds |> 
+  filter(!is.na(plant)) |> 
+  filter(is_offense) |> 
+  group_by(year, game, map, plant) |> 
+  summarize(
+    n = n(),
+    wins = sum(win_round)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_prop = wins / n
+  ) |> 
+  group_by(year, game, map) |> 
+  mutate(
+    total = sum(n),
+    rnk = row_number(-n),
+    prop = n / total
+  ) |> 
+  ungroup()
+
+plant_win_prop <- map_plant_win_prop |>
+  mutate(site = ifelse(rnk == 1, 'pri', 'sec')) |> 
+  group_by(site) |> 
+  summarize(
+    across(c(n, wins, total), sum)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_prop = wins / n,
+    prop = n / total
+  )
+
+plant_win_prop_proj <- plant_win_prop |> 
+  left_join(
+    rounds |> 
+      filter(is_offense) |> 
+      filter(is.na(plant)) |> 
+      summarize(
+        n_no_plant = n(),
+        wins_no_plant = sum(win_round)
+      ),
+    by = character()
+  ) |> 
+  mutate(
+    n_proj = round(n + prop * n_no_plant),
+    wins_proj = round(wins + prop * wins_no_plant),
+    win_prop_proj = wins_proj / n_proj
+  )
+
+plant_site_prop <- plant_win_prop_proj |> 
+  select(site, prop) |> 
+  deframe() |> 
+  scales::percent(accuracy = 0.1)
+
+plant_site_win_prop <- plant_win_prop_proj |> 
+  select(site, win_prop_proj) |> 
+  deframe() |> 
+  scales::percent(accuracy = 0.1)
+```
+
+```{r}
+#| label: plant_win_prop_proj-eval
+#| eval: true
+plant_site_prop <- c(
+  'pri' = '60.9%',
+  'sec' = '39.1%'
+)
+plant_site_win_prop <- c(
+  'pri' = '47.4%',
+  'sec' = '48.5%'
+)
+```
+
+::: columns
+::: {.column width="15%"}
+:::
+
+::: {.column width="30%"}
+| Plant side |                           \% |
+|------------|-----------------------------:|
+| Primary    | `r plant_site_prop[['pri']]` |
+| Secondary  | `r plant_site_prop[['sec']]` |
+:::
+
+::: {.column width="10%"}
+:::
+
+::: {.column width="30%"}
+| Plant side |                            Win % |
+|------------|---------------------------------:|
+| Primary    | `r plant_site_win_prop[['pri']]` |
+| Secondary  |     `r plant_site_prop[['sec']]` |
+:::
+
+::: {.column width="15%"}
+:::
+:::
+
 ::: notes

### 2022-07-17 research/game-5-series-frequency.R
coolio calc of game 5 freq

@@ -1,0 +1,90 @@
+# https://twitter.com/AstrosInMyAfro/status/1548108679563530241?s=20&t=xWhKd8dOWQ_fhJRmgMc--A
+n_rounds_max <- 5
+n_sims <- 100000
+set.seed(42)
+w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE)
+
+sim_rounds <- tibble(
+  i = rep(1:n_sims, each = n_rounds_max),
+  r = rep(1:n_sims, times = n_rounds_max),
+  w = w
+) |> 
+  group_by(i) |> 
+  mutate(
+    cumu_w = cumsum(w),
+    cumu_l = cumsum(w == 0)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    cumu_wl_max = ifelse(cumu_w > cumu_l, cumu_w, cumu_l)
+  ) |> 
+  filter(cumu_wl_max <= 3)
+
+sim_rounds_to_drop <- anti_join(
+  sim_rounds |> 
+    filter(cumu_wl_max == 3L),
+  sim_rounds |> 
+    filter(cumu_wl_max == 3L) |> 
+    group_by(i) |> 
+    slice_min(r, n = 1) |> 
+    ungroup()
+)
+
+sim_rounds <- sim_rounds |> 
+  anti_join(
+    sim_rounds_to_drop
+  )
+sim_rounds
+
+e_series_streaks <- sim_rounds |> 
+  inner_join(
+    sim_rounds |> 
+      filter(cumu_wl_max == 3) |> 
+      mutate(
+        zeros_win = cumu_l == cumu_wl_max
+      ) |> 
+      select(i, zeros_win)
+  ) |> 
+  mutate(
+    across(w, ~ifelse(zeros_win, abs(1 - .x), .x))
+  ) |> 
+  group_by(i) |> 
+  summarize(
+    cumu_w = max(cumu_w),
+    cumu_l = max(cumu_l),
+    ws = paste0(w, collapse = '')
+  ) |> 
+  ungroup() |> 
+  mutate(
+    wins = ifelse(cumu_w == 3, cumu_w, cumu_l),
+    losses = ifelse(cumu_w == 3, cumu_l, cumu_w)
+  ) |> 
+  unite(
+    record, wins, losses, sep = '-'
+  ) |> 
+  count(record, ws, sort = TRUE) |> 
+  mutate(prop = n / sum(n))
+
+e_series_streaks |> 
[…]

### 2022-07-17 presentation.qmd
add spacing to last slide
more formatting

@@
 
+<br/><br/>
+
 ::: fragment
@@
     -   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
--   Actual: **`r 100 * round(round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r round_win_prop_after_b2b2b_wins$n` / `r round_win_prop_after_b2b2b_wins$total` )
+    -   Actual: **`r 100 * round(round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r round_win_prop_after_b2b2b_wins$n` / `r round_win_prop_after_b2b2b_wins$total`)
 :::
@@
 
+<br/><br/>
+
 ::: columns
@@
 
-::: {.column width="30%"}
-| Plant side |                           \% |
+::: {.column .fragment width="30%"}
+| Plant site |                           \% |
 |------------|-----------------------------:|
@@
 
-::: {.column width="30%"}
-| Plant side |                            Win % |
+::: {.column .fragment width="30%"}
+| Plant site |                            Win % |
 |------------|---------------------------------:|
 | Primary    | `r plant_site_win_prop[['pri']]` |
-| Secondary  |     `r plant_site_prop[['sec']]` |
+| Secondary  | `r plant_site_win_prop[['sec']]` |
 :::

### 2022-07-17 presentation.qmd
analytic formulas for series outcomes and streaks

@@
 -   Plant/Defuse in Valorant
-    -   Data from Valorant professional league, updated through January 1, 2022
+    -   Valorant professional league, updated through January 1, 2022
     -   5v5
@@
 #| label: p_series_outcome_prop_over_expected
-prior_clinching_round_win_prop <- rounds |> 
-  filter(round == (n_rounds - 1L)) |> 
-  count(n_rounds, win_series, won_prior_round = win_round) |> 
-  mutate(
-    across(win_series, ~ifelse(.x, 'win', 'loss'))
-  ) |> 
-  pivot_wider(
-    names_from = win_series,
-    values_from = n,
-    values_fill = 0L
-  ) |> 
-  filter(won_prior_round) |> 
-  select(-won_prior_round) |> 
-  mutate(
-    win_series_prop = win / (win + loss),
-    e_win_series_prop = (6L - 1L) / (n_rounds - 1L)
-  )
-
-n_rounds_max <- 11
-n_sims <- 100000
-set.seed(42)
-w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE)
-
-sim_rounds <- tibble(
-  i = rep(1:n_sims, each = n_rounds_max),
-  r = rep(1:n_sims, times = n_rounds_max),
-  w = w
-) |> 
-  group_by(i) |> 
-  mutate(
-    cumu_w = cumsum(w),
-    cumu_l = cumsum(w == 0)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    cumu_wl_max = ifelse(cumu_w > cumu_l, cumu_w, cumu_l)
-  ) |> 
-  filter(cumu_wl_max <= 6)
-
-sim_rounds_to_drop <- anti_join(
-  sim_rounds |> 
-    filter(cumu_wl_max == 6L),
-  sim_rounds |> 
-    filter(cumu_wl_max == 6L) |> 
-    group_by(i) |> 
-    slice_min(r, n = 1) |> 
-    ungroup()
-)
-
-sim_rounds <- sim_rounds |> 
-  anti_join(
-    sim_rounds_to_drop
-  )
-
-## always from offensive perspective
-e_series_streaks <- sim_rounds |> 
-  inner_join(
-    sim_rounds |> 
-      filter(cumu_wl_max == 6) |> 
-      mutate(
-        zeros_win = cumu_l == cumu_wl_max
-      ) |> 
-      select(i, zeros_win)
-  ) |> 
-  mutate(
-    across(w, ~ifelse(zeros_win, abs(1 - .x), .x))
-  ) |> 
-  group_by(i) |> 
-  summarize(
-    cumu_w = max(cumu_w),
-    cumu_l = max(cumu_l),
-    ws = paste0(w, collapse = '')
-  ) |> 
-  ungroup() |> 
-  mutate(
-    wins = ifelse(cumu_w == 6, cumu_w, cumu_l),
-    losses = ifelse(cumu_w == 6, cumu_l, cumu_w)
-  ) |> 
-  unite(
-    record, wins, losses, sep = '-'
-  ) |> 
-  count(record, ws, sort = TRUE) |> 
-  mutate(prop = n / sum(n))
+# https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422
+prob_of_series_lasting_n_games <- function(n, p = 0.5, max_rounds = 11) {
+  s <- ceiling(max_rounds / 2)
+  (factorial(n - 1) / (factorial(s - 1) * factorial(n - s))) * (p^s * (1 - p)^(n - s) + p^(n - s) * (1 - p)^s)
+}
+
+possibilities_of_outcomes <- function(m, n) {
+  factorial(m + n) / (factorial(m) * factorial(n))
+}
 
@@
   ungroup() |> 
+  mutate(n_rounds = wins + losses) |> 
   unite(
@@
   ) |> 
-  count(record, ws, sort = TRUE) |> 
+  count(n_rounds, record, ws, sort = TRUE) |> 
   mutate(prop = n / sum(n))
 
-series_streaks <- full_join(
+possibilities <- tibble(
+  n_rounds = 6L:11L
+) |> 
+  mutate(
+    series_prop = map_dbl(n_rounds, prob_of_series_lasting_n_games),
+    possibilities = map2_dbl(6, n_rounds - 6, possibilities_of_outcomes)
+  ) |> 
+  transmute(
+    n_rounds,
+    series_prop,
+    record = sprintf('6-%d', n_rounds - 6),
+    prop = series_prop / possibilities
+  )
+
+series_streaks <- inner_join(
   actual_series_streaks |> 
     rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-  e_series_streaks |> 
-    rename_with(~sprintf('%s_expected', .x), c(n, prop))
+  possibilities |> 
+    rename_with(~sprintf('%s_expected', .x), prop),
+  by = 'n_rounds'
 ) |> 
@@
   filter(!is.na(n_actual)) |> 
-  mutate(total_actual = sum(n_actual)) |> 
-  mutate(
-    p = vectorized_prop_test(n_actual, total_actual, n_expected, !!n_sims)
+  mutate(
+    prop_diff = prop_actual - prop_expected,
+    total_actual = sum(n_actual),
+    n_expected = round(prop_expected * total_actual),
+    p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
   ) |> 
   select(-total_actual) |> 
-  arrange(p$p.value)
+  unnest_wider(p) |> 
+  arrange(p.value)
 
@@
     rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-  e_series_streaks |> 
-    group_by(record) |> 
-    summarize(
-      across(n, sum)
-    ) |> 
-    mutate(prop = n / sum(n)) |> 
-    rename_with(~sprintf('%s_expected', .x), c(n, prop))
+  possibilities |> 
+    select(record, prop_expected = series_prop),
+  by = 'record'
 ) |> 
@@
     total_actual = sum(n_actual),
-    n_expected_downsampled = round(prop_expected * total_actual),
-    p = vectorized_prop_test(n_actual, total_actual, n_expected_downsampled, total_actual)
+    n_expected = round(prop_expected * total_actual),
+    p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
   ) |> 
   select(-total_actual) |> 
-  arrange(p$p.value)
+  unnest_wider(p) |> 
+  arrange(p.value)
 
 long_series_outcome_prop <- series_outcome_prop |>
-  unnest(p) |>
   select(
@@
 
-::: fragment
 -   Round win % after a streak of 3 round wins:
@@
     -   Actual: **`r 100 * round(round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r round_win_prop_after_b2b2b_wins$n` / `r round_win_prop_after_b2b2b_wins$total`)
-:::
 
@@
 
-## What is the optimal strategy?
+## Is planting at one site better than the other?
 

### 2022-07-17 presentation.qmd
idk if i can stop the reformatting of bullets, tried looking at momentum from 2nd paper

@@
   revealjs:
+    slide-number: true
     incremental: false
+    logo: images/cdl_gray.png
     theme: [dark, theme.scss]
@@
 #| label: cod_heatmap_prep
-n_rounds_side <- rounds |> 
+round_and_series_win_prop_by_side <- rounds |> 
   group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
@@
 
-o_win_prop <- n_rounds_side |> 
+o_win_prop <- round_and_series_win_prop_by_side |> 
   filter(is_offense) |> 
@@
   )
+
+# round_and_series_win_prop <- rounds |> 
+#   group_by(pre_cumu_w, pre_cumu_l) |> 
+#   summarize(
+#     n = n(),
+#     across(c(win_round, win_series), sum)
+#   ) |> 
+#   ungroup() |> 
+#   mutate(
+#     win_round_prop = win_round / n,
+#     win_series_prop = win_series / n
+#   )
+# 
+# pluck_round_win_prop <- function(w = 0, l = 0) {
+#   round_and_series_win_prop |> 
+#     filter(pre_cumu_w == w, pre_cumu_l == l) |> 
+#     pull(win_round_prop)
+# }
+# 
+# compute_conditional_probs <- function(
+    #     p00 = 0.5,
+#     p10 = p00,
+#     p20 = p00,
+#     p30 = p00,
+#     p40 = p00,
+#     p50 = p00,
+#     p11 = p00, p21 = p00, p31 = p00, p41 = p00, p51 = p00,
+#     p52 = p00, p53 = p00, p54 = p00
+# ) {
+#   pr6 <- p10 * p20 * p30 * p40 * p50
+#   # pr7 <- p51 * (p10 * p20 * p30 * p40 * (1 - p50) + p10 * p20 * p30 * (1 - p40) * p41 + p10 * p20 * (1 - p30) * p41 + p10 * (1 - p20) * p31 * p41 + (1 - p10) * p21 * p31 * p41)
+#   pr7 <- (
+#     (p00 * p10 * p20 * p30 * p40 * (1 - p50) * p51) +   ## aaaaaba
+#     (p00 * p10 * p20 * p30 * (1 - p40) * p41 * p51) + ## aaaabaa
+#     (p00 * p10 * p20 * (1 - p30) * p31 * p41 * p51) + ## aaabaaa
+#     (p00 * p10 * (1 - p20) * p21 * p31 * p41 * p51) + ## aabaaaa
+#     (p00 * (1 - p10) * p11 * p21 * p31 * p41 * p51) + ## abaaaaa
+#     ((1 - p00) * (1 - p10) * p11 * p21 * p31 * p41 * p51) + ## baaaaaa
+#     
+#     ((1 - p00) * p10 * p20 * p30 * p40 * (1 - p50) * p51) + ## bbbbbab
+#     ((1 - p00) * p10 * p20 * p30 * (1 - p40) * p41 * p51) + ## bbbbabb
+#     ((1 - p00) * p10 * p20 * (1 - p30) * p31 * p41 * p51) + ## bbbabbb
+#     ((1 - p00) * p10 * (1 - p20) * p21 * p31 * p41 * p51) + ## bbabbbb
+#     ((1 - p00) * (1 - p10) * (1 - p11) * p21 * p31 * p41 * p51) + ## babbbbb
+#     (p00 * (1 - p10) * (1 - p11) * p21 * p31 * p41 * p51) ## abbbbbb
+# )
+#   
+#   ## NOTE: pr8 and pr9 are broken.
+although we can use the simple subtraction of other probabilities for pr10 and pr11 like pr6 and pr7 in a 7 game series, they aren't valid for pr8 and pr9 in an 11 game series.
+#   pr8 <- (1 - pr6 - pr7) * p52
+#   pr9 <- (1 - pr6 - pr7 - pr8) * p53
+#   pr10 <- (1 - pr6 - pr7 - pr8 - pr9) * p54
+#   pr11 <- 1 - pr6 - pr7 - pr8 - pr9 - pr10
+#   tibble(
+#     n_rounds = 6L:11L,
+#     p = c(pr6, pr7, pr8, pr9, pr10, pr11)
+#   )
+# }
+# 
+# ## pr6 and pr7 should match up with what we see later with `possibilities`
+# conditional_series_probs <- compute_conditional_probs(
+#   p00 = pluck_round_win_prop(0, 0),
+#   p10 = pluck_round_win_prop(1, 0),
+#   p20 = pluck_round_win_prop(2, 0),
+#   p30 = pluck_round_win_prop(3, 0),
+#   p40 = pluck_round_win_prop(4, 0),
+#   p50 = pluck_round_win_prop(5, 0),
+#   p11 = pluck_round_win_prop(1, 1),
+#   p21 = pluck_round_win_prop(2, 1),
+#   p31 = pluck_round_win_prop(3, 1),
+#   p41 = pluck_round_win_prop(4, 1),
+#   p51 = pluck_round_win_prop(5, 1),
+#   p52 = pluck_round_win_prop(5, 2),
+#   p53 = pluck_round_win_prop(5, 3),
+#   p54 = pluck_round_win_prop(5, 4)
+# )
 
@@
 
-heatmap_seq_labeller <- function(.data, .label) {
+heatmap_seq_labeller <- function(.data, .label, .num) {
   sprintf(
@@
     scales::percent(.data[[.label]], accuracy = 1), 
-    scales::comma(.data$win_round), 
+    scales::comma(.data[[.num]]), 
     scales::comma(.data$n)
@@
 
-heatmap_text_layer <- function(..., .op, .data, .label, .color, .threshold, .labeller) {
+heatmap_text_layer <- function(..., .op, .data, .label, .num, .color, .threshold, .labeller) {
   list(
@@
         y = pre_cumu_l + 0.5,
-        label = .labeller(.data = .data, .label = .label)
+        label = .labeller(.data = .data, .label = .label, .num)
       )
@@
 #| label: p_o_round_win_prop
-o_round_win_text_layer <- function(..., .emphasize = 'low') {
+o_round_win_text_layer <- function(..., .emphasize) {
   if(.emphasize == 'low') {
@@
       .label = 'win_round_prop',
+      .num = 'win_round',
       .color = .color,
@@
 
-## How do the empirical round results compare to expectation?
+## What are your chances of winning a round, given the series state?
 
@@
 #| label: p_o_round_win_prop_over_expected
-heatmap_div_labeller <- function(.data, .label) {
+# I have no idea why I need to add .num here... keeps erroring otherwise
+heatmap_div_labeller <- function(.data, .label, .num) {
   sprintf(
-    '%+.0f\n(%s/%s)', 
+    '%+.1f\n(%s)', 
     100 * .data[[.label]], 
-    scales::comma(.data$win_round), 
     scales::comma(.data$n)
@@
       .label = 'win_series_prop',
+      .num = 'win_series',
       .color = .color,
-      .threshold = 0.52,
+      .threshold = 0.8,
       .labeller = heatmap_seq_labeller
@@
   heatmap_text_layers(.f = add_o_series_win_text_layer) +
-  ggsci::scale_fill_material('deep-orange') +
+  ggsci::scale_fill_material('orange') +
   labs(
@@
 
-## How do the empirical series results compare to expectation?
+## What are your chances of winning the series, given the series state?
 
@@
   o_win_rx_prop <- summarize_o_round_win_prop(.round)
-  x1_label <- sprintf('Round %d<br/>o Win %%', .round)
-  x2_label <- sprintf('Post-Round %d<br/>o Win %%', .round)
+  x1_label <- sprintf('Round %d<br/>offensive win %%', .round)
+  x2_label <- sprintf('Post-round %d<br/>offensive win %%', .round)
 
@@
   ggsci::scale_fill_material(
-    palette = 'orange'
+    palette = 'deep-orange'
   ) +
@@
 prob_n6_k3 <- simulate_post_streak_prob(sims = 10000, n = 6, k = 3, p = 0.5)
+prob_n11_k3 <- simulate_post_streak_prob(sims = 10000, n = 8, k = 3, p = 0.5)
+prob_n11_k3 <- simulate_post_streak_prob(sims = 10000, n = 11, k = 3, p = 0.5)
+prob_n10_k1 <- simulate_post_streak_prob(sims = 10000, n = 10, k = 1, p = 0.5)
 
 round_streaks <- rounds |> 
-  filter(round <= 6) |> 
+  # filter(round <= 6) |> 
   group_by(year, sheet, series, team) |> 
@@
     is_offense,
+    round,
     win_round,
@@
   )
-
-round_streaks_after_b2b <- round_streaks |> 
-  filter(!is.na(won_prior_round2)) |> 
-  count(win_round, won_prior_round, won_prior_round2, sort = TRUE)
-
-round_win_prop_after_b2b_wins <- round_streaks_after_b2b |> 
-  filter(won_prior_round, won_prior_round2) |> 
-  mutate(
-    total = sum(n),
-    prop = n / total
-  ) |> 
-  filter(win_round) |> 
-  select(n, total, prop)
 
@@
   mutate(prop = n / total)
+```
+
+```{r}
+#| label: summarize_and_compare_win_prop_after_wins
+## https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422#app2 suggests that we should look at non-overlapping streaks.
+## "To avoid this problem, we examine only the frequency of winning game three after having won games one and two and the frequency of winning game six after having won games four and five".
+They sort of deduced that win %s > 50% in the third game might constitute momentum, but didn't make strong statements.
+summarize_win_prop_after_x_wins <- function(round, ...) {
+  round_streaks |> 
+    filter(round == !!round) |> 
+    count(win_round, won_prior_round, won_prior_round2, ..., sort = TRUE) |> 
+    relocate(n) |> 
+    drop_na(last_col()) |> 
+    filter(won_prior_round, won_prior_round2, ...) |> 
+    mutate(
+      total = sum(n),
+      prop = n / total
+    ) |> 
+    filter(win_round) |> 
+    transmute(round = !!round, n, total, prop)
+}
+
+summarize_win_prop_after_b2b_wins <- summarize_win_prop_after_x_wins
+summarize_win_prop_after_b2b2b_wins <- function(round) {
+  summarize_win_prop_after_x_wins(round = round, won_prior_round3)
+}
+
+summarize_and_compare_win_prop_after_wins <- function(ri, add, f) {
+  ra <- f(ri)
+  rb <- f(ri + add)
+  bind_rows(ra, rb)
+}
+
+summarize_and_compare_win_prop_after_b2b_wins <- partial(
+  summarize_and_compare_win_prop_after_wins,
+  add = 3,
+  f = summarize_win_prop_after_b2b_wins,
+  ... = 
+)
+
+summarize_and_compare_win_prop_after_b2b2b_wins <- partial(
+  summarize_and_compare_win_prop_after_wins,
+  add = 4,
+  f = summarize_win_prop_after_b2b2b_wins,
+  ... = 
+)
+
+win_prop_after_b2b_wins <- seq(3, 8, by = 1) |> 
+  map_dfr(
+    summarize_and_compare_win_prop_after_b2b_wins,
+    .id = 'pair_idx'
+  )
+
+win_prop_after_b2b2b_wins <- seq(4, 7, by = 1) |> 
+  map_dfr(
+    summarize_and_compare_win_prop_after_b2b2b_wins,
+    .id = 'pair_idx'
+  )
 ```

### 2022-07-17 valorant.R
rename val vars

@@ -46,13 +46,14 @@ teams <- bind_rows(
   distinct(team_id, team) |> 
   arrange(team_id)
 teams
-rounds |> 
+
+cumu_rounds <- rounds |> 
   mutate(
     across(
       score_after_round,
       list(
-        pre_cumu_w = ~str_remove(.x, '-.*$') |> as.integer(),
-        pre_cumu_l = ~str_remove(.x, '^.*-') |> as.integer()
+        cumu_w = ~str_remove(.x, '-.*$') |> as.integer(),
+        cumu_l = ~str_remove(.x, '^.*-') |> as.integer()
       ),
       .names = '{fn}'
     )
@@ -67,9 +68,10 @@ rounds |>
     game_id,
     team_1,
     team_2,
-    pre_cumu_w,
-    pre_cumu_l
+    cumu_w,
+    cumu_l
   )
+cumu_rounds
 
 rounds |> 
   count(score_after_round, sort = TRUE)

### 2022-07-17 presentation.qmd
more val processing, prefix cod vars

--- 2022-07-17 presentation.qmd
@@
   revealjs:
+    slide-number: true
     incremental: false
@@
 
-rounds <- qs::qread('cod_rounds.qs')
+cod_rounds <- qs::qread('cod_rounds.qs')
 ```
@@
 -   First to 13 round wins
-    -   One team plays offense in 12 consecutive rounds before swapping sides
-    -   Must win by 2 rounds
+-   One team plays offense in 12 consecutive cod_rounds before swapping sides
+-   Must win by 2 cod_rounds
 :::
@@
 #| eval: true
-n_series <- rounds |> 
+cod_n_series <- cod_rounds |> 
   distinct(year, sheet, series) |> 
@@
 
-n_rounds <- rounds |> 
+cod_n_rounds <- cod_rounds |> 
   distinct(year, sheet, series, round) |> 
@@
 
-o_win_prop_const <- rounds |> 
+cod_o_win_prop_const <- cod_rounds |> 
   filter(is_offense) |> 
@@
   pull(prop)
-o_win_pct <- scales::percent(o_win_prop_const, accuracy = 1)
-
-plant_pct <- rounds |>
+cod_o_win_pct <- scales::percent(cod_o_win_prop_const, accuracy = 1)
+
+cod_plant_pct <- cod_rounds |>
   filter(is_offense) |> 
@@
 
-o_plant_and_win_pct <- rounds |> 
+cod_o_plant_and_win_pct <- cod_rounds |> 
   filter(is_offense, !is.na(plant)) |> 
@@
 
-o_first_blood_win_pct <- rounds |> 
+cod_o_first_blood_win_pct <- cod_rounds |> 
   filter(!is.na(earned_fb)) |> 
@@
 ::: fragment
--   Total series: **`r n_series`**
+-   Total series: **`r cod_n_series`**
 :::
@@
 ::: fragment
--   Total rounds: **`r n_rounds`**
+-   Total cod_rounds: **`r cod_n_rounds`**
 :::
@@
 ::: fragment
--   Offensive plant %: **`r plant_pct`**
+-   Offensive plant %: **`r cod_plant_pct`**
 :::
@@
 ::: fragment
--   Offensive win %: **`r o_win_pct`**
+-   Offensive win %: **`r cod_o_win_pct`**
 :::
@@
 ::: fragment
--   Win % when planting: **`r o_plant_and_win_pct`**
+-   Win % when planting: **`r cod_o_plant_and_win_pct`**
 :::
@@
 ::: fragment
--   Win % when earning first blood: **`r o_first_blood_win_pct`**
+-   Win % when earning first blood: **`r cod_o_first_blood_win_pct`**
 :::
@@
 #| label: cod_heatmap_prep
-n_rounds_side <- rounds |> 
+cod_round_and_series_win_prop_by_side <- cod_rounds |> 
   group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
@@
 
-o_win_prop <- n_rounds_side |> 
+cod_o_win_prop <- cod_round_and_series_win_prop_by_side |> 
   filter(is_offense) |> 
   mutate(
-    diff_win_round_prop = win_round_prop - !!o_win_prop_const
-  )
-
-e_o_win_series_prop <- crossing(
+    diff_win_round_prop = win_round_prop - !!cod_o_win_prop_const
+  )
+
+cod_e_o_win_series_prop <- crossing(
   pre_cumu_w = 0:5,
@@
 
-o_win_prop <- o_win_prop |> 
+cod_o_win_prop <- cod_o_win_prop |> 
   inner_join(
-    e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
+    cod_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
     by = c('pre_cumu_w', 'pre_cumu_l')
@@
   )
+
+# round_and_series_win_prop <- cod_rounds |> 
+#   group_by(pre_cumu_w, pre_cumu_l) |> 
+#   summarize(
+#     n = n(),
+#     across(c(win_round, win_series), sum)
+#   ) |> 
+#   ungroup() |> 
+#   mutate(
+#     win_round_prop = win_round / n,
+#     win_series_prop = win_series / n
+#   )
+# 
+# pluck_round_win_prop <- function(w = 0, l = 0) {
+#   round_and_series_win_prop |> 
+#     filter(pre_cumu_w == w, pre_cumu_l == l) |> 
+#     pull(win_round_prop)
+# }
+# 
+# compute_conditional_probs <- function(
+    #     p00 = 0.5,
+#     p10 = p00,
+#     p20 = p00,
+#     p30 = p00,
+#     p40 = p00,
+#     p50 = p00,
+#     p11 = p00, p21 = p00, p31 = p00, p41 = p00, p51 = p00,
+#     p52 = p00, p53 = p00, p54 = p00
+# ) {
+#   pr6 <- p10 * p20 * p30 * p40 * p50
+#   # pr7 <- p51 * (p10 * p20 * p30 * p40 * (1 - p50) + p10 * p20 * p30 * (1 - p40) * p41 + p10 * p20 * (1 - p30) * p41 + p10 * (1 - p20) * p31 * p41 + (1 - p10) * p21 * p31 * p41)
+#   pr7 <- (
+#     (p00 * p10 * p20 * p30 * p40 * (1 - p50) * p51) +   ## aaaaaba
+#     (p00 * p10 * p20 * p30 * (1 - p40) * p41 * p51) + ## aaaabaa
+#     (p00 * p10 * p20 * (1 - p30) * p31 * p41 * p51) + ## aaabaaa
+#     (p00 * p10 * (1 - p20) * p21 * p31 * p41 * p51) + ## aabaaaa
+#     (p00 * (1 - p10) * p11 * p21 * p31 * p41 * p51) + ## abaaaaa
+#     ((1 - p00) * (1 - p10) * p11 * p21 * p31 * p41 * p51) + ## baaaaaa
+#     
+#     ((1 - p00) * p10 * p20 * p30 * p40 * (1 - p50) * p51) + ## bbbbbab
+#     ((1 - p00) * p10 * p20 * p30 * (1 - p40) * p41 * p51) + ## bbbbabb
+#     ((1 - p00) * p10 * p20 * (1 - p30) * p31 * p41 * p51) + ## bbbabbb
+#     ((1 - p00) * p10 * (1 - p20) * p21 * p31 * p41 * p51) + ## bbabbbb
+#     ((1 - p00) * (1 - p10) * (1 - p11) * p21 * p31 * p41 * p51) + ## babbbbb
+#     (p00 * (1 - p10) * (1 - p11) * p21 * p31 * p41 * p51) ## abbbbbb
+# )
+#   
+#   ## NOTE: pr8 and pr9 are broken.
+although we can use the simple subtraction of other probabilities for pr10 and pr11 like pr6 and pr7 in a 7 game series, they aren't valid for pr8 and pr9 in an 11 game series.
+#   pr8 <- (1 - pr6 - pr7) * p52
+#   pr9 <- (1 - pr6 - pr7 - pr8) * p53
+#   pr10 <- (1 - pr6 - pr7 - pr8 - pr9) * p54
+#   pr11 <- 1 - pr6 - pr7 - pr8 - pr9 - pr10
+#   tibble(
+#     n_rounds = 6L:11L,
+#     p = c(pr6, pr7, pr8, pr9, pr10, pr11)
+#   )
+# }
+# 
+# ## pr6 and pr7 should match up with what we see later with `possibilities`
+# conditional_series_probs <- compute_conditional_probs(
+#   p00 = pluck_round_win_prop(0, 0),
+#   p10 = pluck_round_win_prop(1, 0),
+#   p20 = pluck_round_win_prop(2, 0),
+#   p30 = pluck_round_win_prop(3, 0),
+#   p40 = pluck_round_win_prop(4, 0),
+#   p50 = pluck_round_win_prop(5, 0),
+#   p11 = pluck_round_win_prop(1, 1),
+#   p21 = pluck_round_win_prop(2, 1),
+#   p31 = pluck_round_win_prop(3, 1),
+#   p41 = pluck_round_win_prop(4, 1),
+#   p51 = pluck_round_win_prop(5, 1),
+#   p52 = pluck_round_win_prop(5, 2),
+#   p53 = pluck_round_win_prop(5, 3),
+#   p54 = pluck_round_win_prop(5, 4)
+# )
 
@@
 
-heatmap_seq_labeller <- function(.data, .label) {
+heatmap_seq_labeller <- function(.df, .label, .num) {
   sprintf(
     '%s\n(%s/%s)',
-    scales::percent(.data[[.label]], accuracy = 1), 
-    scales::comma(.data$win_round), 
-    scales::comma(.data$n)
-  )
-}
-
-heatmap_text_layer <- function(..., .op, .data, .label, .color, .threshold, .labeller) {
+    scales::percent(.df[[.label]], accuracy = 1),
+    scales::comma(.df[[.num]]),
+    scales::comma(.df$n)
+  )
+}
+
+heatmap_text_layer <- function(..., .op, .df, .label, .num, .color, .threshold, .labeller) {
+  .df_filt <- .df |> filter(`.op`(.df[[.label]], .threshold))
+  if(nrow(.df_filt) == 0) {
+    return(list(...))
+  }
   list(
@@
     geom_text(
-      data = .data |> filter(`.op`(.data[[.label]], .threshold)),
-      # family = font,
+      data = .df_filt,
       color = .color,
@@
       aes(
-        x = pre_cumu_w + 0.5, 
-        y = pre_cumu_l + 0.5,
-        label = .labeller(.data = .data, .label = .label)
-      )
-    )
-  )
-}
-
-heatmap_text_layers <- function(..., .f) {
+        label = .labeller(.df = .df_filt, .label = .label, .num = .num),
+        x = .data$pre_cumu_w + 0.5, 
+        y = .data$pre_cumu_l + 0.5
+      )
+    )
+  )
+}
+
+heatmap_text_layers <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller,
+    .f
+) {
   list(
     ...,
-    .f(.emphasize = 'low'),
-    .f(.emphasize = 'high')
-  )
-}
-```
-
-```{r}
-#| label: p_o_round_win_prop
-o_round_win_text_layer <- function(..., .emphasize = 'low') {
+    .f(.df = .df, .threshold = .threshold, .labeller = .labeller, .emphasize = 'low'),
+    .f(.df = .df, .threshold = .threshold, .labeller = .labeller, .emphasize = 'high')
+  )
+}
+
+o_round_win_text_layer <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller, 
+    .emphasize
+) {
   if(.emphasize == 'low') {
@@
     heatmap_text_layer(
-      .data = o_win_prop,
+      .df = .df,
       .op = op,
       .label = 'win_round_prop',
+      .num = 'win_round',
       .color = .color,
-      .threshold = 0.52,
-      .labeller = heatmap_seq_labeller
-    )
-  )
-}
-
-p_o_round_win_prop <- o_win_prop |> 
+      .threshold = .threshold,
+      .labeller = .labeller
+    )
+  )
+}
+
+p_cod_o_round_win_prop <- cod_o_win_prop |> 
   ggplot() +
@@
   heatmap_tile(.fill = 'win_round_prop') +
-  heatmap_text_layers(.f = o_round_win_text_layer) +
+  heatmap_text_layers(
+    .df = cod_o_win_prop,
+    .f = o_round_win_text_layer,
+    .threshold = 0.52,
+    .labeller = heatmap_seq_labeller
+  ) +
   ggsci::scale_fill_material('teal') +
@@
   )
-p_o_round_win_prop
-save_for_slide(p_o_round_win_prop)
+p_cod_o_round_win_prop
+save_for_slide(p_cod_o_round_win_prop)
 ```
@@
 
-![](o_round_win_prop.png){fig-align="center"}
-
-## How do the empirical round results compare to expectation?
+![](cod_o_round_win_prop.png){fig-align="center"}
+
+## What are your chances of winning a round, given the series state?
 
 ```{r}
-#| label: p_o_round_win_prop_over_expected
-heatmap_div_labeller <- function(.data, .label) {
+#| label: p_cod_o_round_win_prop_over_expected
+# I have no idea why I need to add .num here... keeps erroring otherwise
+heatmap_div_labeller <- function(.df, .label, .num) {
   sprintf(
-    '%+.0f\n(%s/%s)', 
-    100 * .data[[.label]], 
-    scales::comma(.data$win_round), 
-    scales::comma(.data$n)
-  )
-}
-
-o_round_win_over_expected_text_layer <- function(..., .emphasize) {
+    '%+.1f\n(%s)', 
+    100 * .df[[.label]], 
+    scales::comma(.df$n)
+  )
+}
+
+o_round_win_over_expected_text_layer <- function(
+    ..., 
+    .df, 
+    .threshold,
+    .labeller,
+    .emphasize
+) {
   if(.emphasize == 'low') {
@@
     heatmap_text_layer(
-      .data = o_win_prop,
+      .df = .df,
       .op = op,
       .label = 'diff_win_round_prop',
+      .num = 1,
       .color = .color,
-      .threshold = -0.1,
-      .labeller = heatmap_div_labeller
+      .threshold = .threshold,
+      .labeller = .labeller
     )
@@
 
-max_diff_win_round_prop <- max(abs(o_win_prop$diff_win_round_prop))
-p_o_round_win_prop_over_expected <- o_win_prop |> 
+cod_max_diff_win_round_prop <- max(abs(cod_o_win_prop$diff_win_round_prop))
+p_cod_o_round_win_prop_over_expected <- cod_o_win_prop |> 
   ggplot() +
@@
   heatmap_tile(.fill = 'diff_win_round_prop') +
-  heatmap_text_layers(.f = o_round_win_over_expected_text_layer) +
+  heatmap_text_layers(
+    .df = cod_o_win_prop, 
+    .f = o_round_win_over_expected_text_layer,
+    .threshold = -0.1,
+    .labeller = heatmap_div_labeller
+  ) +
   scale_fill_gradient2(
@@
     limits = c(
-      -max_diff_win_round_prop, 
-      +max_diff_win_round_prop
+      -cod_max_diff_win_round_prop, 
+      +cod_max_diff_win_round_prop
     )
@@
   )
-p_o_round_win_prop_over_expected
-save_for_slide(p_o_round_win_prop_over_expected)
+p_cod_o_round_win_prop_over_expected
+save_for_slide(p_cod_o_round_win_prop_over_expected)
 ```
@@
 
-![](o_round_win_prop_over_expected.png){fig-align="center"}
+![](cod_o_round_win_prop_over_expected.png){fig-align="center"}
 
@@
 ```{r}
-#| label: p_o_series_win_prop
-add_o_series_win_text_layer <- function(..., .emphasize) {
+#| label: p_cod_o_series_win_prop
+o_series_win_text_layer <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller, 
+    .emphasize
+) {
   if(.emphasize == 'low') {
@@
     heatmap_text_layer(
-      .data = o_win_prop,
+      .df = .df,
       .op = op,
       .label = 'win_series_prop',
+      .num = 'win_series',
       .color = .color,
-      .threshold = 0.52,
-      .labeller = heatmap_seq_labeller
-    )
-  )
-}
-
-p_o_series_win_prop <- o_win_prop |> 
+      .threshold = .threshold,
+      .labeller = .labeller
+    )
+  )
+}
+
+p_cod_o_series_win_prop <- cod_o_win_prop |> 
   ggplot() +
@@
   heatmap_tile(.fill = 'win_series_prop') +
-  heatmap_text_layers(.f = add_o_series_win_text_layer) +
-  ggsci::scale_fill_material('deep-orange') +
+  heatmap_text_layers(
+    .df = cod_o_win_prop, 
+    .f = o_series_win_text_layer,
+    .threshold = 0.8,
+    .labeller = heatmap_seq_labeller
+  ) +
+  ggsci::scale_fill_material('orange') +
   labs(
@@
   )
-p_o_series_win_prop
-save_for_slide(p_o_series_win_prop)
+p_cod_o_series_win_prop
+save_for_slide(p_cod_o_series_win_prop)
 ```
@@
 
-![](o_series_win_prop.png){fig-align="center"}
-
-## How do the empirical series results compare to expectation?
+![](cod_o_series_win_prop.png){fig-align="center"}
+
+## What are your chances of winning the series, given the series state?
 
 ```{r}
-#| label: p_o_series_win_prop_over_expected
-add_o_series_win_over_expected_text_layer <- function(..., .emphasize) {
+#| label: p_cod_o_series_win_prop_over_expected
+o_series_win_over_expected_text_layer <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller, 
+    .emphasize
+) {
   if(.emphasize == 'low') {
@@
     heatmap_text_layer(
-      .data = o_win_prop,
+      .df = .df,
       .op = op,
       .label = 'diff_win_series_prop',
+      .num = NULL,
       .color = .color,
+      .threshold = .threshold,
+      .labeller = .labeller
+    )
+  )
+}
+
+cod_max_diff_win_series_prop <- max(abs(cod_o_win_prop$diff_win_series_prop))
+p_cod_o_series_win_prop_over_expected <- cod_o_win_prop |> 
+  ggplot() +
+  common_cod_heatmap_layers() +
+  heatmap_tile(
+    .fill = 'diff_win_series_prop'
+  ) +
+  heatmap_text_layers(
+    .df = cod_o_win_prop, 
+    .f = o_series_win_over_expected_text_layer,
     .threshold = 0.08,
     .labeller = heatmap_div_labeller
-    )
-  )
-}
-
-max_diff_win_series_prop <- max(abs(o_win_prop$diff_win_series_prop))
-p_o_series_win_prop_over_expected <- o_win_prop |> 
-  ggplot() +
-  common_cod_heatmap_layers() +
-  heatmap_tile(.fill = 'diff_win_series_prop') +
-  heatmap_text_layers(.f = add_o_series_win_over_expected_text_layer) +
+  ) +
   scale_fill_gradient2(
@@
     limits = c(
-      -max_diff_win_series_prop, 
-      +max_diff_win_series_prop
+      -cod_max_diff_win_series_prop, 
+      +cod_max_diff_win_series_prop
     )
@@
   )
-p_o_series_win_prop_over_expected
-save_for_slide(p_o_series_win_prop_over_expected)
+p_cod_o_series_win_prop_over_expected
+save_for_slide(p_cod_o_series_win_prop_over_expected)
 ```
@@
 ```{r}
-#| label: o_win_r1_vs_post_round_pro
-calculate_o_round_win_prop <- function(df) {
+#| label: p_cod_o_win_r1_vs_post_round_prop
+calculate_cod_o_round_win_prop <- function(df) {
   df |> 
@@
 
-summarize_o_round_win_prop <- function(.round) {
-
-  specified_round <- rounds |> 
+summarize_cod_o_round_win_prop <- function(.round) {
+
+  specified_round <- cod_rounds |> 
     filter(round == .round) |> 
-    calculate_o_round_win_prop()
-
-  post_rounds <- rounds |> 
+    calculate_cod_o_round_win_prop()
+
+  post_rounds <- cod_rounds |> 
     filter(round > .round) |> 
-    calculate_o_round_win_prop()
+    calculate_cod_o_round_win_prop()
 
@@
 
-plot_round_vs_post_round_slope_chart <- function(.round) {
-  o_win_rx_prop <- summarize_o_round_win_prop(.round)
-  x1_label <- sprintf('Round %d<br/>o Win %%', .round)
-  x2_label <- sprintf('Post-Round %d<br/>o Win %%', .round)
+plot_cod_round_vs_post_round_slope_chart <- function(.round) {
+  o_win_rx_prop <- summarize_cod_o_round_win_prop(.round)
+  x1_label <- sprintf('Round %d<br/>offensive win %%', .round)
+  x2_label <- sprintf('Post-round %d<br/>offensive win %%', .round)
 
@@
 
-res_r1 <- plot_round_vs_post_round_slope_chart(1)
-
-p_o_win_r1_vs_post_round_prop <- res_r1$plot +
+cod_res_r1 <- plot_cod_round_vs_post_round_slope_chart(1)
+
+p_cod_o_win_r1_vs_post_round_prop <- cod_res_r1$plot +
   geom_curve(
@@
           'Largest negative percent difference in round 1\nvs. all other round win percentages (%+.0f%%).', 
-          100 * res_r1$largest_neg_diff_prop
+          100 * cod_res_r1$largest_neg_diff_prop
         ),
@@
           'Largest positive percent difference (%+.0f%%).\nOnly significant difference (p value < 0.01).',
-          100 * res_r1$largest_pos_diff_prop
+          100 * cod_res_r1$largest_pos_diff_prop
         )
@@
   )
-p_o_win_r1_vs_post_round_prop
-save_for_slide(p_o_win_r1_vs_post_round_prop)
+p_cod_o_win_r1_vs_post_round_prop
+save_for_slide(p_cod_o_win_r1_vs_post_round_prop)
 ```
 
-![](o_win_r1_vs_post_round_prop.png){fig-align="center"}
+![](cod_o_win_r1_vs_post_round_prop.png){fig-align="center"}
 
@@
 
-## Are offensive win %'s different in round 2?
+## What are the most common series winning states?
 
 ```{r}
-#| label: o_win_r2_vs_post_round_pro
-res_r2 <- plot_round_vs_post_round_slope_chart(2)
-res_r2$plot
-save_for_slide(
-  res_r2$plot,
-  filename = 'o_win_r2_vs_post_round_prop.png'
-)
-```
-
-![](o_win_r2_vs_post_round_prop.png){fig-align="center"}
-
-::: notes
--   no trend
-:::
-
-## What are the most common series winning states?
-
-```{r}
-#| label: p_series_outcome_prop_over_expected
+#| label: p_cod_series_outcome_prop_over_expected
 # https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422
@@
 
-actual_series_streaks <- rounds |> 
+cod_actual_series_streaks <- cod_rounds |> 
   filter(win_series) |> 
@@
 
-possibilities <- tibble(
+cod_possibilities <- tibble(
   n_rounds = 6L:11L
@@
 
-series_streaks <- inner_join(
-  actual_series_streaks |> 
+cod_series_streaks <- inner_join(
+  cod_actual_series_streaks |> 
     rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-  possibilities |> 
+  cod_possibilities |> 
     rename_with(~sprintf('%s_expected', .x), prop),
@@
 ## 6-0, 6-1, and some combos of 6-5 occur more often than expected
-series_streak_props <- series_streaks |> 
+cod_series_streak_props <- cod_series_streaks |> 
   filter(!is.na(n_actual)) |> 
@@
 ## 6-0 and 6-1 occur more often than expected
-series_outcome_prop <- full_join(
-  actual_series_streaks |> 
+cod_series_outcome_prop <- full_join(
+  cod_actual_series_streaks |> 
     group_by(record) |> 
@@
     rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-  possibilities |> 
+  cod_possibilities |> 
     select(record, prop_expected = series_prop),
@@
 
-long_series_outcome_prop <- series_outcome_prop |>
+cod_long_series_outcome_prop <- cod_series_outcome_prop |>
   select(
@@
 
-max_diff_series_outcome_prop <- long_series_outcome_prop |> 
+cod_max_diff_series_outcome_prop <- cod_long_series_outcome_prop |> 
   filter(outcome_idx == 1) |> 
@@
 
-p_series_outcome_prop_over_expected <- long_series_outcome_prop |> 
+p_cod_series_outcome_prop_over_expected <- cod_long_series_outcome_prop |> 
   ggplot() +
@@
   geom_tile(
-    data = long_series_outcome_prop |> filter(outcome_idx > 1),
+    data = cod_long_series_outcome_prop |> filter(outcome_idx > 1),
     show.legend = FALSE,
@@
   geom_tile(
-    data = long_series_outcome_prop |> filter(outcome_idx == 1),
+    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1),
     show.legend = FALSE,
@@
     limits = c(
-      -max_diff_series_outcome_prop, 
-      +max_diff_series_outcome_prop
+      -cod_max_diff_series_outcome_prop, 
+      +cod_max_diff_series_outcome_prop
     )
@@
   geom_text(
-    data = long_series_outcome_prop |> filter(outcome_idx == 3),
+    data = cod_long_series_outcome_prop |> filter(outcome_idx == 3),
     color = blackish_background,
@@
   geom_text(
-    data = long_series_outcome_prop |> filter(outcome_idx == 2),
+    data = cod_long_series_outcome_prop |> filter(outcome_idx == 2),
     color = blackish_background,
@@
   geom_text(
-    data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
+    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
     color = blackish_background,
@@
   geom_text(
-    data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
+    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
     color = 'white',
     size = 11 / .pt,
-
     aes(label = sprintf('%+.1f%%', 100 * value))
@@
   common_cod_labs() 
-p_series_outcome_prop_over_expected
-save_for_slide(p_series_outcome_prop_over_expected)
+p_cod_series_outcome_prop_over_expected
+save_for_slide(p_cod_series_outcome_prop_over_expected)
 ```
 
-![](series_outcome_prop_over_expected.png){fig-align="center"}
+![](cod_series_outcome_prop_over_expected.png){fig-align="center"}
 
@@
 ```{r}
-#| label: p_b2b_round_win_prop
-summarize_b2b_round_wins <- function(df, ...) {
+#| label: p_cod_b2b_round_win_prop
+summarize_cod_b2b_round_wins <- function(df, ...) {
   df |> 
@@
 
-## now accounting for number of rounds that end up being played...
+## now accounting for number of cod_rounds that end up being played...
 ## seems like there is interesting behavior in the last round, regardless `n_rounds`
-b2b_round_win_prop <- rounds |> 
+cod_b2b_round_win_prop <- cod_rounds |> 
   filter(n_rounds > 6L) |> 
-  summarize_b2b_round_wins(n_rounds) |> 
+  summarize_cod_b2b_round_wins(n_rounds) |> 
   group_by(n_rounds) |> 
@@
 
-b2b_round_win_prop_tile_layer <- function(..., .round, .palette, .is_new = TRUE) {
+b2b_round_win_prop_tile_layer <- function(..., .df, .round, .palette, .is_new = TRUE) {
 
@@
     geom_tile(
-      data = b2b_round_win_prop |> filter(n_rounds == .round),
+      data = .df |> filter(n_rounds == .round),
       color = blackish_background,
@@
 
-b2b_round_win_prop_text_layer <- function(..., .emphasize) {
+b2b_round_win_prop_text_layer <- function(..., .df, .emphasize) {
   if(.emphasize == 'low') {
@@
     geom_text(
-      data = b2b_round_win_prop |> filter(`op`(rnk, 1)),
+      data = .df |> filter(`op`(rnk, 1)),
       color = .color,
@@
 
-b2b_round_win_prop_text_layers <- function(...) {
+b2b_round_win_prop_text_layers <- function(..., .df) {
   list(
     ...,
-    b2b_round_win_prop_text_layer(.emphasize = 'low'),
-    b2b_round_win_prop_text_layer(.emphasize = 'high')
-  )
-}
-
-b2b_round_win_prop_arws <- tibble(
+    b2b_round_win_prop_text_layer(.df = .df, .emphasize = 'low'),
+    b2b_round_win_prop_text_layer(.df = .df, .emphasize = 'high')
+  )
+}
+
+cod_b2b_round_win_prop_arws <- tibble(
   x = c(9.3, 9.4, 9.75, 10),
@@
 
-p_b2b_round_win_prop <- b2b_round_win_prop |> 
+p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
   ggplot() +
-  b2b_round_win_prop_tile_layer(.round = 7, .palette = 'pink', .is_new = FALSE) +
-  b2b_round_win_prop_tile_layer(.round = 8, .palette = 'light-blue') +
-  b2b_round_win_prop_tile_layer(.round = 9, .palette = 'light-green') +
-  b2b_round_win_prop_tile_layer(.round = 10, .palette = 'amber') +
-  b2b_round_win_prop_tile_layer(.round = 11, .palette = 'deep-orange') +
-  b2b_round_win_prop_text_layers() +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 7, 
+    .palette = 'pink', 
+    .is_new = FALSE
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 8, 
+    .palette = 'light-blue'
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 9, 
+    .palette = 'light-green'
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 10, 
+    .palette = 'amber'
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 11, 
+    .palette = 'deep-orange
+  ') +
+  b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
   scale_x_continuous(
@@
     x = 'Round',
-    y = '# of Rounds in Complete Series'
+    y = '# of cod_rounds in Complete Series'
   ) + 
@@
   map(
-    b2b_round_win_prop_arws |> group_split(rn), 
+    cod_b2b_round_win_prop_arws |> group_split(rn), 
     function(.x) {
@@
   )
-save_for_slide(p_b2b_round_win_prop)
-# ## now accounting for number of rounds that end up being played AND series winners...
-# rounds |> 
+p_cod_b2b_round_win_prop
+save_for_slide(p_cod_b2b_round_win_prop)
+# ## now accounting for number of cod_rounds that end up being played AND series winners...
+# cod_rounds |> 
 #   filter(win_series, n_rounds > 6L) |> 
@@
 # ## and the losers...
-# rounds |> 
+# cod_rounds |> 
 #   filter(!win_series) |> 
@@
 
-![](b2b_round_win_prop.png){fig-align="center"}
+![](cod_b2b_round_win_prop.png){fig-align="center"}
 
@@
 ```{r}
-#| label: round_win_prop_after_b2b2b_wins
+#| label: cod_round_win_prop_after_b2b2b_wins
 ## http://keyonvafa.com/hot-hand/
@@
 prob_n6_k3 <- simulate_post_streak_prob(sims = 10000, n = 6, k = 3, p = 0.5)
-
-round_streaks <- rounds |> 
-  filter(round <= 6) |> 
+prob_n11_k3 <- simulate_post_streak_prob(sims = 10000, n = 8, k = 3, p = 0.5)
+prob_n11_k3 <- simulate_post_streak_prob(sims = 10000, n = 11, k = 3, p = 0.5)
+prob_n10_k1 <- simulate_post_streak_prob(sims = 10000, n = 10, k = 1, p = 0.5)
+
+cod_round_streaks <- cod_rounds |> 
+  # filter(round <= 6) |> 
   group_by(year, sheet, series, team) |> 
@@
 
-round_streaks_after_b2b <- round_streaks |> 
-  filter(!is.na(won_prior_round2)) |> 
-  count(win_round, won_prior_round, won_prior_round2, sort = TRUE)
-
-round_win_prop_after_b2b_wins <- round_streaks_after_b2b |> 
-  filter(won_prior_round, won_prior_round2) |> 
-  mutate(
-    total = sum(n),
-    prop = n / total
-  ) |> 
-  filter(win_round) |> 
-  select(n, total, prop)
-
-round_streaks_after_b2b2b <- round_streaks |> 
+cod_round_streaks_after_b2b2b <- cod_round_streaks |> 
   filter(!is.na(won_prior_round2), !is.na(won_prior_round3)) |> 
@@
 
-round_win_prop_after_b2b2b_wins <- round_streaks_after_b2b2b |> 
+cod_round_win_prop_after_b2b2b_wins <- cod_round_streaks_after_b2b2b |> 
   filter(won_prior_round, won_prior_round2, won_prior_round3) |> 
@@
 ```{r}
-#| label: round_win_prop_after_b2b2b_wins-eval
+#| label: cod_round_win_prop_after_b2b2b_wins-eval
 #| eval: true
 prob_n6_k3 <- 0.3838163
-round_win_prop_after_b2b2b_wins <- tibble(
-  n = 352,
-  total = 632
+cod_round_win_prop_after_b2b2b_wins <- tibble(
+  n = 621,
+  total = 1150
 ) |> 
@@
 
+```{r}
+#| label: summarize_and_compare_win_prop_after_wins
+## https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422#app2 suggests that we should look at non-overlapping streaks.
+## "To avoid this problem, we examine only the frequency of winning game three after having won games one and two and the frequency of winning game six after having won games four and five".
+They sort of deduced that win %s > 50% in the third game might constitute momentum, but didn't make strong statements.
+summarize_cod_win_prop_after_x_wins <- function(round, ...) {
+  cod_round_streaks |> 
+    filter(round == !!round) |> 
+    count(win_round, won_prior_round, won_prior_round2, ..., sort = TRUE) |> 
+    relocate(n) |> 
+    drop_na(last_col()) |> 
+    filter(won_prior_round, won_prior_round2, ...) |> 
+    mutate(
+      total = sum(n),
+      prop = n / total
+    ) |> 
+    filter(win_round) |> 
+    transmute(round = !!round, n, total, prop)
+}
+
+summarize_cod_win_prop_after_b2b_wins <- summarize_cod_win_prop_after_x_wins
+summarize_cod_win_prop_after_b2b2b_wins <- function(round) {
+  summarize_cod_win_prop_after_x_wins(round = round, won_prior_round3)
+}
+
+summarize_and_compare_cod_win_prop_after_wins <- function(ri, add, f) {
+  ra <- f(ri)
+  rb <- f(ri + add)
+  bind_rows(ra, rb)
+}
+
+summarize_and_compare_cod_win_prop_after_b2b_wins <- partial(
+  summarize_and_compare_cod_win_prop_after_wins,
+  add = 3,
+  f = summarize_cod_win_prop_after_b2b_wins,
+  ... = 
+)
+
+summarize_and_compare_cod_win_prop_after_b2b2b_wins <- partial(
+  summarize_and_compare_cod_win_prop_after_wins,
+  add = 4,
+  f = summarize_cod_win_prop_after_b2b2b_wins,
+  ... = 
+)
+
+cod_win_prop_after_b2b_wins <- seq(3, 8, by = 1) |> 
+  map_dfr(
+    summarize_and_compare_cod_win_prop_after_b2b_wins,
+    .id = 'pair_idx'
+  )
+
+cod_win_prop_after_b2b2b_wins <- seq(4, 7, by = 1) |> 
+  map_dfr(
+    summarize_and_compare_cod_win_prop_after_b2b2b_wins,
+    .id = 'pair_idx'
+  )
+```
+
 <br/><br/>
@@
 -   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
-    -   Actual: **`r 100 * round(round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r round_win_prop_after_b2b2b_wins$n` / `r round_win_prop_after_b2b2b_wins$total`)
+-   Actual: **`r 100 * round(cod_round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r cod_round_win_prop_after_b2b2b_wins$n` / `r cod_round_win_prop_after_b2b2b_wins$total`)
 
 ::: notes
--   Note this is sort of biased by the fact that teams end up winning series in 6 rounds more often than expected.
+-   Note this is sort of biased by the fact that teams end up winning series in 6 cod_rounds more often than expected.
 :::
@@
 ```{r}
-#| label: plant_win_prop_proj
-map_plant_win_prop <- rounds |> 
+#| label: cod_plant_win_prop_proj
+cod_map_plant_win_prop <- cod_rounds |> 
   filter(!is.na(plant)) |> 
@@
 
-plant_win_prop <- map_plant_win_prop |>
+cod_plant_win_prop <- cod_map_plant_win_prop |>
   mutate(site = ifelse(rnk == 1, 'pri', 'sec')) |> 
@@
 
-plant_win_prop_proj <- plant_win_prop |> 
+cod_plant_win_prop_proj <- cod_plant_win_prop |> 
   left_join(
-    rounds |> 
+    cod_rounds |> 
       filter(is_offense) |> 
@@
 
-plant_site_prop <- plant_win_prop_proj |> 
+cod_plant_site_prop <- cod_plant_win_prop_proj |> 
   select(site, prop) |> 
@@
 
-plant_site_win_prop <- plant_win_prop_proj |> 
+cod_plant_site_win_prop <- cod_plant_win_prop_proj |> 
   select(site, win_prop_proj) |> 
@@
 ```{r}
-#| label: plant_win_prop_proj-eval
+#| label: cod_plant_win_prop_proj-eval
 #| eval: true
-plant_site_prop <- c(
+cod_plant_site_prop <- c(
   'pri' = '60.9%',
@@
 )
-plant_site_win_prop <- c(
+cod_plant_site_win_prop <- c(
   'pri' = '47.4%',
@@
 | Plant site |                               \% |
-|------------|-----------------------------:|
-| Primary    | `r plant_site_prop[['pri']]` |
-| Secondary  | `r plant_site_prop[['sec']]` |
+|------------|---------------------------------:|
+| Primary    | `r cod_plant_site_prop[['pri']]` |
+| Secondary  | `r cod_plant_site_prop[['sec']]` |
 :::
@@
 | Plant site |                                Win % |
-|------------|---------------------------------:|
-| Primary    | `r plant_site_win_prop[['pri']]` |
-| Secondary  | `r plant_site_win_prop[['sec']]` |
+|------------|-------------------------------------:|
+| Primary    | `r cod_plant_site_win_prop[['pri']]` |
+| Secondary  | `r cod_plant_site_win_prop[['sec']]` |
 :::
@@
 :::
-
-::: notes
--   Should you plant at most prevalent/winningest site? plant at other site? Go for kills?
-:::

### 2022-07-17 valorant.R

@@ -11,19 +11,22 @@ query_db <- function(conn, statement) {
     janitor::clean_names()
 }
 
-games <- query_db(con, 'select * from Games')
-matches <- query_db(con, 'select * from Matches')
-scoreboard <- query_db(con, 'select * from Game_Scoreboard')
-raw_rounds <- query_db(con, 'select * from Game_Rounds')
-clean_json <- function(x) {
+## for some reason there is no mapping of team ids -> team_abbrv, which is needed to identify round winners properly.
+## we have to make it ourselves (see `team_mapping`)
+val_games <- query_db(con, 'select * from Games')
+val_matches <- query_db(con, 'select * from Matches')
+val_scoreboard <- query_db(con, 'select * from Game_Scoreboard')
+raw_val_rounds <- query_db(con, 'select * from Game_Rounds')
+
+clean_val_json <- function(x) {
   x |> 
     str_replace_all("\\'", '\\"') |> 
     str_replace_all('([A-z0-9]+)[:]', '"\\1":') |> 
     fromJSON()
 }
-possibly_clean_json <- possibly(clean_json, otherwise = NULL)
+possibly_clean_json <- possibly(clean_val_json, otherwise = NULL)
 
-rounds <- raw_rounds |> 
+init_val_rounds <- raw_val_rounds |> 
   mutate(
     round_history = map(round_history, possibly_clean_json)
   ) |> 
@@ -31,23 +34,39 @@ rounds <- raw_rounds |>
   unnest_wider(round_history) |> 
   clean_names() |> 
   mutate(
+    across(round_winner, str_squish)
+  ) |> 
+  mutate(
     round = as.integer(round_history_id),
     .before = 'round_winner'
   ) |> 
   select(-round_history_id) |> 
   filter(!is.na(round))
 
-teams <- bind_rows(
-  games |> 
-    distinct(team_id = team1id, team = team1), 
-  games |> 
-    distinct(team_id = team2id, team = team2)
-) |> 
-  distinct(team_id, team) |> 
-  arrange(team_id)
-teams
+val_team_abbrvs <- val_scoreboard |> 
+  distinct(game_id, team_abbrv = team_abbreviation) |> 
+  mutate(across(team_abbrv, ~toupper(.x) |> str_squish()))
 
-cumu_rounds <- rounds |> 
[…]

### 2022-07-18 valorant.R
val data

@@ -13,7 +13,7 @@ query_db <- function(conn, statement) {
 
 ## for some reason there is no mapping of team ids -> team_abbrv, which is needed to identify round winners properly.
 ## we have to make it ourselves (see `team_mapping`)
-val_games <- query_db(con, 'select * from Games')
+init_val_games <- query_db(con, 'select * from Games')
 val_matches <- query_db(con, 'select * from Matches')
 val_scoreboard <- query_db(con, 'select * from Game_Scoreboard')
 raw_val_rounds <- query_db(con, 'select * from Game_Rounds')
@@ -41,9 +41,48 @@ init_val_rounds <- raw_val_rounds |>
     .before = 'round_winner'
   ) |> 
   select(-round_history_id) |> 
-  filter(!is.na(round))
+  filter(!is.na(round)) |> 
+  mutate(
+    across(
+      score_after_round,
+      list(
+        cumu_w = ~str_remove(.x, '-.*$') |> as.integer(),
+        cumu_l = ~str_remove(.x, '^.*-') |> as.integer()
+      ),
+      .names = '{fn}'
+    )
+  )
+
+init_val_series_outcomes <- init_val_rounds |> 
+  group_by(game_id) |> 
+  slice_max(round, n = 1, with_ties = FALSE) |> 
+  ungroup() |> 
+  select(game_id, round, cumu_w, cumu_l) |> 
+  mutate(
+    max_cumu_wl = ifelse(cumu_w > cumu_l, cumu_w, cumu_l),
+    min_cumu_wl = ifelse(cumu_w > cumu_l, cumu_l, cumu_w)
+  )
+
+weird_val_series_outcomes <- init_val_series_outcomes |> 
+  filter(max_cumu_wl > 13 & (min_cumu_wl < (max_cumu_wl - 2)))
+
+val_series_outcomes <- init_val_series_outcomes |> 
+  anti_join(
+    weird_val_series_outcomes |> select(game_id),
+    by = 'game_id'
+  )
+
+val_games <- init_val_games |> 
+  inner_join(
+    val_series_outcomes |> select(game_id),
+    by = 'game_id'
+  )
 
 val_team_abbrvs <- val_scoreboard |> 
+  inner_join(
+    val_series_outcomes |> select(game_id),
+    by = 'game_id'
+  ) |> 
   distinct(game_id, team_abbrv = team_abbreviation) |> 
   mutate(across(team_abbrv, ~toupper(.x) |> str_squish()))
 
[…]

### 2022-07-18 presentation.qmd
cooler title

@@
 ---
-title: "Streaking and Clutching in Round-Based First Person Shooter Esports"
-author: "Tony ElHabr"
+title: '"Turned on!": Momentum in Round-Based First Person Shooter Esports'
+author: 'Tony ElHabr'
 format:

### 2022-07-18 presentation.qmd
rename and rerender stuff

@@
 cod_rounds <- qs::qread('cod_rounds.qs')
+val_rounds <- qs::qread('valorant_rounds.qs')
 ```
@@
 -   First to 13 round wins
--   One team plays offense in 12 consecutive cod_rounds before swapping sides
+-   One team plays offense in 12 consecutive rounds before swapping sides
 -   Must win by 2 cod_rounds
@@
 ::: fragment
--   Total cod_rounds: **`r cod_n_rounds`**
+-   Total rounds: **`r cod_n_rounds`**
 :::
@@
 
-## What are your chances of winning a round, given the series state?
+## Valorant data overview
+
+```{r}
+#| label: descriptive-val-snd-stats
+#| eval: true
+val_n_series <- val_rounds |> 
+  distinct(game_id) |> 
+  nrow() |> 
+  scales::comma()
+
+val_n_rounds <- val_rounds |> 
+  distinct(game_id, round) |> 
+  nrow() |> 
+  scales::comma()
+
+val_o_win_prop_const <- val_rounds |> 
+  filter(is_offense) |> 
+  count(win_round) |> 
+  mutate(prop = n / sum(n)) |> 
+  filter(win_round) |> 
+  pull(prop)
+val_o_win_pct <- scales::percent(val_o_win_prop_const, accuracy = 1)
+```
+
+::: fragment
+-   Total series: **`r val_n_series`**
+:::
+
+::: fragment
+-   Total rounds: **`r val_n_rounds`**
+:::
+
+::: fragment
+-   Offensive win %: **`r val_o_win_pct`**
+:::
+
+## What are your chances of winning a round, given the series state in COD SnD?
 
@@
 
-heatmap_seq_labeller <- function(.df, .label, .num) {
+cod_heatmap_seq_labeller <- function(.df, .label, .num) {
   sprintf(
@@
 }
-
+```
+
+```{r}
+#| label: p_cod_o_round_win_prop
 o_round_win_text_layer <- function(
@@
     .labeller,
+    .label = 'win_round_prop',
+    .num = 'win_round',
     .emphasize
@@
       .op = op,
-      .label = 'win_round_prop',
-      .num = 'win_round',
+      .label = .label,
+      .num = .num,
       .color = .color,
@@
     .threshold = 0.52,
-    .labeller = heatmap_seq_labeller
+    .labeller = cod_heatmap_seq_labeller
   ) +
@@
 
-## What are your chances of winning a round, given the series state?
+## What are your chances of winning a round, given the series state in COD SnD?
 
@@
 #| label: p_cod_o_round_win_prop_over_expected
-# I have no idea why I need to add .num here... keeps erroring otherwise
 heatmap_div_labeller <- function(.df, .label, .num) {
@@
 ![](cod_o_round_win_prop_over_expected.png){fig-align="center"}
+
+## What are your chances of winning a round, given the series state in Valorant?
+
+```{r}
+val_round_and_series_win_prop_by_side <- val_rounds |> 
+  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
+  summarize(
+    n = n(),
+    across(c(win_round, win_series), sum)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_round_prop = win_round / n,
+    win_series_prop = win_series / n
+  )
+
+val_o_win_prop <- val_round_and_series_win_prop_by_side |> 
+  filter(is_offense) |> 
+  mutate(
+    diff_win_round_prop = win_round_prop - !!val_o_win_prop_const
+  )
+
+# Joshua Broas, vlr.gg
+common_val_labs <- function(...) {
+  list(
+    ...,
+    labs(
+      caption = 'Pro Valorant matches, 2020 - Jan 1, 2022'
+    )
+  )
+}
+
+common_val_heatmap_layers <- function(...) {
+  list(
+    ...,
+    guides(
+      fill = 'none'
+    ),
+    scale_x_continuous(
+      labels = 0:12,
+      breaks = seq(0.5, 12.5, by = 1),
+      expand = c(0, 0)
+    ),
+    scale_y_continuous(
+      labels = 0:12,
+      breaks = seq(0.5, 12.5, by = 1),
+      expand = c(0, 0),
+      sec.axis = sec_axis(
+        trans = I, 
+        name = ' ', 
+        breaks = seq(0.5, 12.5, by = 1), 
+        labels = rep('', 13)
+      )
+    ),
+    theme(
+      panel.grid.major = element_blank(),
+      axis.title = element_text(hjust = 0.5),
+      plot.title = ggtext::element_markdown(hjust = 0.5),
+      axis.text = element_text(size = 16, face = 'bold')
+    ),
+    common_val_labs(),
+    labs(
+      x = "Offensive Team's # of Pre-Round Wins",
+      y = "Defensive Team's # of Pre-Round Wins"
+    )
+  )
+}
+
+val_heatmap_seq_labeller <- function(.df, .label, .num) {
+  sprintf(
+    '%s', 
+    scales::percent(.df[[.label]], accuracy = 1)
+  )
+}
+
+filt_val_o_win_prop <- val_o_win_prop |> 
+  filter(pre_cumu_w <= 12, pre_cumu_l <= 12)
+
+val_pre_swap_rounds <- filt_val_o_win_prop |> 
+  mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
+  filter(pre_cumu_wl == 12)
+
+val_pre_swap_round_segments <- val_pre_swap_rounds |> 
+  transmute(
+    pre_cumu_w,
+    across(pre_cumu_l, ~.x + 1),
+    i = row_number(),
+    n = 2
+  ) |> 
+  uncount(n) |> 
+  group_by(i) |> 
+  mutate(rn = row_number()) |> 
+  ungroup() |> 
+  mutate(
+    across(pre_cumu_w, ~ifelse(rn == 2, .x + 1, .x))
+  ) |> 
+  add_row(
+    pre_cumu_w = 13,
+    pre_cumu_l = 0
+  )
+
+p_val_o_round_win_prop <- filt_val_o_win_prop |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(.fill = 'win_round_prop') +
+  geom_path(
+    data = val_pre_swap_round_segments,
+    color = 'white',
+    size = 1.5,
+    aes(
+      x = pre_cumu_w, 
+      y = pre_cumu_l
+    )
+  ) +
+  heatmap_text_layers(
+    .df = filt_val_o_win_prop, 
+    .f = o_round_win_text_layer,
+    .num = NULL,
+    .threshold = 0.8,
+    .labeller = val_heatmap_seq_labeller
+  ) +
+  ggsci::scale_fill_material('teal') +
+  labs(
+    title = 'Offensive Round Win %'
+  )
+p_val_o_round_win_prop
+save_for_slide(p_val_o_round_win_prop)
+```
+
+::: notes
+-   Big difference compared to COD. Lower/higher percentages in the corners are probably more indicative of gaps in team skill.
+-   1-0, 1-1, 3-0, 3-1 seem to b e the biggest outliers.
+:::
+
+![](val_o_round_win_prop.png){fig-align="center"}
 
@@
     .threshold = 0.8,
-    .labeller = heatmap_seq_labeller
+    .labeller = cod_heatmap_seq_labeller
   ) +
@@
 
-![](o_series_win_prop_over_expected.png){fig-align="center"}
+![](cod_o_series_win_prop_over_expected.png){fig-align="center"}
 
@@
   ggsci::scale_fill_material(
-    palette = 'orange'
+    palette = 'light-blue'
   ) +

### 2022-07-18 1-scrape-valorant.R

@@ -1,10 +1,11 @@
 library(tidyverse)
+library(RSQLite)
 library(DBI)
 library(janitor)
 library(jsonlite)
 
 ## https://www.kaggle.com/datasets/visualize25/valorant-pro-matches-full-data?resource=download
-con <- dbConnect(RSQLite::SQLite(), 'c:/users/antho/downloads/valorant.sqlite')
+con <- dbConnect(RSQLite::SQLite(), 'data/valorant.sqlite')
 query_db <- function(conn, statement) {
   DBI::dbGetQuery(conn = conn, statement = statement) |> 
     tibble() |> 
@@ -199,108 +200,3 @@ val_rounds <- bind_rows(
 ) |> 
   arrange(game_id, round, is_offense)
 qs::qsave(val_rounds, 'valorant_rounds.qs')
-
-val_o_win_prop_const <- val_rounds |> 
-  filter(is_offense) |> 
-  count(win_round) |> 
-  mutate(prop = n / sum(n)) |> 
-  filter(win_round) |> 
-  pull(prop)
-
-val_round_and_series_win_prop_by_side <- val_rounds |> 
-  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
-  summarize(
-    n = n(),
-    across(c(win_round, win_series), sum)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    win_round_prop = win_round / n,
-    win_series_prop = win_series / n
-  )
-
-val_o_win_prop <- val_round_and_series_win_prop_by_side |> 
-  filter(is_offense) |> 
-  mutate(
-    diff_win_round_prop = win_round_prop - !!val_o_win_prop_const
-  )
-
-common_val_heatmap_layers <- function(...) {
-  list(
-    ...,
-    guides(
-      fill = 'none'
-    ),
-    scale_x_continuous(
-      labels = 0:12,
-      breaks = seq(0.5, 12.5, by = 1),
-      expand = c(0, 0)
-    ),
-    scale_y_continuous(
-      labels = 0:12,
-      breaks = seq(0.5, 12.5, by = 1),
-      expand = c(0, 0),
-      sec.axis = sec_axis(
-        trans = I, 
-        name = ' ', 
-        breaks = seq(0.5, 12.5, by = 1), 
-        labels = rep('', 13)
-      )
-    ),
-    theme(
-      panel.grid.major = element_blank(),
-      axis.title = element_text(hjust = 0.5),
[…]

### 2022-07-18 2-visualize.R

@@ -1,973 +1,0 @@
-
-library(tidyverse)
-library(qs)
-library(scales)
-library(extrafont)
-library(ggtext)
-
-blackish_background <- '#191919' # '#1c1c1c'
-gray_points <- '#4d4d4d'
-gray_text <- '#999999'
-
-font <- 'Titillium Web' ## Karla
-extrafont::loadfonts(quiet = TRUE)
-theme_set(theme_minimal())
-theme_update(
-  text = element_text(family = font),
-  title = element_text(size = 20, color = 'white'),
-  plot.title = element_text(face = 'bold', size = 20, color = 'white'),
-  plot.title.position = 'plot',
-  plot.subtitle = element_text(size = 16, color = '#f1f1f1'),
-  axis.text = element_text(color = 'white', size = 14),
-  axis.title = element_text(size = 14, color = 'white', face = 'bold', hjust = 0.99),
-  axis.line = element_blank(),
-  panel.grid.major = element_line(color = gray_points),
-  panel.grid.minor = element_line(color = gray_points),
-  panel.grid.minor.x = element_blank(),
-  panel.grid.minor.y = element_blank(),
-  strip.text = element_text(color = 'white', size = 16, face = 'bold'),
-  plot.margin = margin(10, 10, 10, 10),
-  plot.background = element_rect(fill = blackish_background, color = blackish_background),
-  plot.caption = element_text(size = 12, color = 'white', hjust = 1),
-  plot.caption.position = 'plot',
-  plot.tag = ggtext::element_markdown(size = 12, color = 'white', hjust = 0),
-  plot.tag.position = c(0.01, 0.01),
-  panel.background = element_rect(fill = blackish_background, color = blackish_background)
-)
-# update_geom_defaults('text', list(colour = 'white', font = font))
-update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
-update_geom_defaults('point', list(color = 'white'))
-update_geom_defaults('segment', list(color = 'white'))
-
-rounds <- qs::qread('cod_rounds.qs')
-
-## offensive win % in "neutral" rounds (1 and 2) ----
[…]

### 2022-07-18 presentation.qmd
add val css, and more val plots

@@
 
-## What are your chances of winning a round, given the series state in COD SnD?
+## What are your chances of winning a round, given the series state in [COD SnD]{.cod}?
 
@@
 #| label: p_cod_o_round_win_prop_over_expected
-heatmap_div_labeller <- function(.df, .label, .num) {
+cod_heatmap_div_labeller <- function(.df, .label, .num) {
   sprintf(
@@
     .threshold = -0.1,
-    .labeller = heatmap_div_labeller
+    .labeller = cod_heatmap_div_labeller
   ) +
@@
 
-## What are your chances of winning a round, given the series state in Valorant?
+## What are your chances of winning a round, given the series state in [Valorant]{.valorant}?
 
@@
   )
+
+drop_25th_round <- function(df) {
+  df |> 
+    filter(
+      !(pre_cumu_w == 12 & pre_cumu_l == 12)
+    )
+}
+
+val_e_o_win_series_prop <- crossing(
+  pre_cumu_w = 0:12,
+  pre_cumu_l = 0:12
+) |> 
+  drop_25th_round() |> 
+  mutate(
+    n_remain_max = 25 - (pre_cumu_w + pre_cumu_l),
+    n_remain_w = 13 - pre_cumu_w,
+    ## can i account for offense in this by rotating?
+    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
+  )
+
+val_o_win_prop <- val_o_win_prop |> 
+  inner_join(
+    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
+    by = c('pre_cumu_w', 'pre_cumu_l')
+  ) |> 
+  mutate(
+    diff_win_series_prop = win_series_prop - e_win_series_prop
+  ) |> 
+  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
+  drop_25th_round()
 
@@
 
-filt_val_o_win_prop <- val_o_win_prop |> 
-  filter(pre_cumu_w <= 12, pre_cumu_l <= 12)
-
-val_pre_swap_rounds <- filt_val_o_win_prop |> 
+val_pre_swap_rounds <- val_o_win_prop |> 
   mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
@@
 
-p_val_o_round_win_prop <- filt_val_o_win_prop |> 
+p_val_o_round_win_prop <- val_o_win_prop |> 
   ggplot() +
@@
   heatmap_text_layers(
-    .df = filt_val_o_win_prop, 
+    .df = val_o_win_prop, 
     .f = o_round_win_text_layer,
-    .num = NULL,
     .threshold = 0.8,
@@
 
-## What are your chances of winning the series, given the series state?
+## What are your chances of winning the series, given the series state in [COD SnD]{.cod}?
 
@@
     .threshold = 0.08,
-    .labeller = heatmap_div_labeller
+    .labeller = cod_heatmap_div_labeller
   ) +
@@
 ![](cod_o_series_win_prop_over_expected.png){fig-align="center"}
+
+## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?
+
+```{r}
+#| label: p_val_o_series_win_prop
+p_val_o_series_win_prop <- val_o_win_prop |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(.fill = 'win_series_prop') +
+  geom_path(
+    data = val_pre_swap_round_segments,
+    color = 'white',
+    size = 1.5,
+    aes(
+      x = pre_cumu_w, 
+      y = pre_cumu_l
+    )
+  ) +
+  heatmap_text_layers(
+    .df = val_o_win_prop, 
+    .f = o_series_win_text_layer,
+    .threshold = 0.8,
+    .labeller = val_heatmap_seq_labeller
+  ) +
+  ggsci::scale_fill_material('orange') +
+  labs(
+    title = 'Offensive Series Win %'
+  )
+p_val_o_series_win_prop
+save_for_slide(p_val_o_series_win_prop)
+```
+
+![](val_o_series_win_prop.png){fig-align="center"}
+
+## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?
+
+```{r}
+#| label: p_val_o_series_win_prop_over_expected
+val_heatmap_div_labeller <- function(.df, .label, .num) {
+  sprintf(
+    '%+.1f', 
+    100 * .df[[.label]]
+  )
+}
+
+val_max_diff_win_series_prop <- max(abs(val_o_win_prop$diff_win_series_prop))
+p_val_o_series_win_prop_over_expected <- val_o_win_prop |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(
+    .fill = 'diff_win_series_prop'
+  ) +
+  heatmap_text_layers(
+    .df = val_o_win_prop, 
+    .f = o_series_win_over_expected_text_layer,
+    .threshold = 0.2,
+    .labeller = val_heatmap_div_labeller
+  ) +
+  scale_fill_gradient2(
+    low = extract_ggsci_mid_color('brown'),
+    high = extract_ggsci_mid_color('cyan'),
+    mid = 'white',
+    limits = c(
+      -val_max_diff_win_series_prop,
+      +val_max_diff_win_series_prop
+    ),
+    midpoint = 0
+  ) +
+  labs(
+    title = 'Offensive Series Win % Over Expected'
+  )
+p_val_o_series_win_prop_over_expected
+save_for_slide(p_val_o_series_win_prop_over_expected)
+```
+
+![](val_o_series_win_prop_over_expected.png){fig-align="center"}
 

### 2022-07-18 presentation.qmd
add state graph

@@
 
+## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?
+
+```{r}
+#| label: p_filt_val_o_series_win_prop_over_expected
+filt_val_o_win_prop <- val_o_win_prop |> 
+  filter(
+    pre_cumu_w >= 3, pre_cumu_l >= 3
+  )
+filt_val_max_diff_win_series_prop <- max(abs(filt_val_o_win_prop$diff_win_series_prop))
+p_filt_val_o_series_win_prop_over_expected <- filt_val_o_win_prop |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(
+    .fill = 'diff_win_series_prop'
+  ) +
+  heatmap_text_layers(
+    .df = filt_val_o_win_prop, 
+    .f = o_series_win_over_expected_text_layer,
+    .threshold = 0.1,
+    .labeller = val_heatmap_div_labeller
+  ) +
+  scale_fill_gradient2(
+    low = extract_ggsci_mid_color('brown'),
+    high = extract_ggsci_mid_color('cyan'),
+    mid = 'white',
+    limits = c(
+      -filt_val_max_diff_win_series_prop,
+      +filt_val_max_diff_win_series_prop
+    ),
+    midpoint = 0
+  ) +
+  labs(
+    title = 'Offensive Series Win % Over Expected'
+  )
+p_filt_val_o_series_win_prop_over_expected
+save_for_slide(p_val_o_series_win_prop_over_expected)
+```
+
+![](val_o_series_win_prop_over_expected.png){fig-align="center"}
+
 ## Are offensive win %'s different in round 1?

### 2022-07-19 1-scrape-valorant.R
only 2021 vct matches and other val cleaning

@@ -14,10 +14,39 @@ query_db <- function(conn, statement) {
 
 ## for some reason there is no mapping of team ids -> team_abbrv, which is needed to identify round winners properly.
 ## we have to make it ourselves (see `team_mapping`)
-init_val_games <- query_db(con, 'select * from Games')
-val_matches <- query_db(con, 'select * from Matches')
-val_scoreboard <- query_db(con, 'select * from Game_Scoreboard')
-raw_val_rounds <- query_db(con, 'select * from Game_Rounds')
+val_games <- query_db(con, 'select * from Games') |> 
+  mutate(
+    across(c(game_id, match_id), as.integer)
+  )
+
+val_matches <- query_db(
+  con, 
+  "
+  select * from Matches
+  where eventName like '%Champions Tour%'
+  "
+) |> 
+  mutate(
+    across(c(match_id, event_id), as.integer),
+    across(date, ~lubridate::ymd_hms(.x) |> lubridate::date())
+  )
+
+val_scoreboard <- query_db(
+  con, 
+  'select * from Game_Scoreboard'
+) |> 
+  mutate(
+    across(c(game_id, player_id), as.integer)
+  )
+
+raw_val_rounds <- query_db(
+  con, 
+  'select * from Game_Rounds'
+) |> 
+  mutate(
+    across(game_id, as.integer)
+  )
+dbDisconnect(con)
 
 clean_val_json <- function(x) {
   x |> 
@@ -28,6 +57,14 @@ clean_val_json <- function(x) {
 possibly_clean_json <- possibly(clean_val_json, otherwise = NULL)
 
 init_val_rounds <- raw_val_rounds |> 
+  inner_join(
+    val_games |> distinct(game_id, match_id),
+    by = 'game_id'
+  ) |> 
+  semi_join(
+    val_matches |> distinct(match_id),
+    by = 'match_id'
+  ) |> 
   mutate(
     round_history = map(round_history, possibly_clean_json)
   ) |> 
@@ -54,36 +91,20 @@ init_val_rounds <- raw_val_rounds |>
     )
   )
 
-init_val_series_outcomes <- init_val_rounds |> 
-  group_by(game_id) |> 
-  slice_max(round, n = 1, with_ties = FALSE) |> 
-  ungroup() |> 
-  select(game_id, round, cumu_w, cumu_l) |> 
+val_series_outcomes <- init_val_rounds |>
+  group_by(game_id) |>
+  slice_max(round, n = 1, with_ties = FALSE) |>
+  ungroup() |>
[…]

### 2022-07-19 presentation.qmd
update val dates

@@
 -   Plant/Defuse in Valorant
--   Valorant professional league, updated through January 1, 2022
+-   Valorant Champions Tour (VCT) matches (qualifiers and majors), through November 11, 2021
 -   5v5
@@
     labs(
-      caption = 'Pro Valorant matches, 2020 - Jan 1, 2022'
+      caption = '2021 VCT matches'
     )

### 2022-07-20 presentation.qmd
fix val sample sizes

@@
   pull(prop)
-val_o_win_pct <- scales::percent(val_o_win_prop_const, accuracy = 1)
+val_o_win_pct <- scales::percent(val_o_win_prop_const, accuracy = 0.1)
 ```

### 2022-07-20 1-scrape-valorant.R

@@ -56,7 +56,7 @@ clean_val_json <- function(x) {
 }
 possibly_clean_json <- possibly(clean_val_json, otherwise = NULL)
 
-init_val_rounds <- raw_val_rounds |> 
+init_val_rounds_side <- raw_val_rounds |> 
   inner_join(
     val_games |> distinct(game_id, match_id),
     by = 'game_id'
@@ -91,7 +91,7 @@ init_val_rounds <- raw_val_rounds |>
     )
   )
 
-val_series_outcomes <- init_val_rounds |>
+val_series_outcomes <- init_val_rounds_side |>
   group_by(game_id) |>
   slice_max(round, n = 1, with_ties = FALSE) |>
   ungroup() |>
@@ -159,9 +159,9 @@ val_games |>
 ##   i'm relying on vlr.gg instead of liquepedia as the source of truth.
 ##   liquepedia (https://liquipedia.net/valorant/VALORANT_Champions_Tour/2021/Southeast_Asia/Stage_2/Challengers_3/Malaysia_and_Singapore) has this as ending in 17 rounds, as well as val_matches.
 ##   but vlr.gg (https://www.vlr.gg/14384/paper-rex-vs-team-smg-champions-tour-malaysia-singapore-stage-2-challengers-3-main-event-grand/?game=25724&tab=overview) has this as ending in 19 rounds, as well as val_rounds.
-# init_val_rounds |> filter(game_id == 25726)
+# init_val_rounds_side |> filter(game_id == 25726)
 
-init_val_rounds_side <- init_val_rounds |> 
+val_rounds_side <- init_val_rounds_side |> 
   inner_join(
     val_team_mapping |> select(team1id = team_id, team_1 = team_abbrv), 
     by = 'team1id'
@@ -228,9 +228,13 @@ init_val_rounds_side <- init_val_rounds |>
     pre_cumu_l = lag(cumu_l, default = 0L)
   ) |> 
   ungroup()
+val_rounds_side |> 
+  filter(!is_offense_1) |> 
+  filter(cumu_l == 1, cumu_w == 0) |> 
+  count(win_round_1)
 
 val_rounds <- bind_rows(
-  init_val_rounds_side |> 
+  val_rounds_side |> 
     select(
       game_id,
       match_id,
@@ -248,7 +252,7 @@ val_rounds <- bind_rows(
       team_series_w = team_1_series_w,
[…]

### 2022-07-20 presentation.qmd
remove notes

@@
 ::: fragment
--   Search and Destroy (SnD) in Call of Duty (COD)
+### Search and Destroy (SnD) in Call of Duty (COD)
+
 -   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
@@
 
+<br/>
+
 ::: fragment
--   Plant/Defuse in Valorant
--   Valorant Champions Tour (VCT) matches (qualifiers and majors), through November 11, 2021
+### A Plant/Defuse in Valorant
+
+-   2021 Valorant Champions Tour (VCT) matches (qualifiers and majors)
 -   5v5
@@
 
-::: notes
--   This should hint at what I'm calling the "4-4" phenomenon, where the o round win % is dramatically higher than adjacent scenarios (3-4, 4-3, 5-4, 4-5, and even 3-3 or 5-5).
--   Note that round win %s are lower than one might expect in 0-5 and 1-5 states.
-:::
-
 ![](cod_o_round_win_prop.png){fig-align="center"}
@@
 ```
-
-::: notes
--   This should emphasize the ends of the spectrum seen on the previous graph.
-:::
 
@@
 
-::: notes
--   Big difference compared to COD. Lower/higher percentages in the corners are probably more indicative of gaps in team skill.
--   1-0, 1-1, 3-0, 3-1 seem to b e the biggest outliers.
-:::
-
 ![](val_o_round_win_prop.png){fig-align="center"}
@@
 
-::: notes
--   This is mostly just for reference. I think the next slide should have more insight, since it's harder to have a prior understanding about the probability of winning the series given a round state.
-:::
-
 ![](cod_o_series_win_prop.png){fig-align="center"}
@@
 ```
-
-::: notes
--   Note the 4-4 and 2-4 series win percentages.
-:::
 
@@
 
-::: notes
--   This might be considered an "information-neutral" setting
-:::
-
 ## What are the most common series winning states?
@@
 ![](cod_series_outcome_prop_over_expected.png){fig-align="center"}
-
-::: notes
--   There should be evidence of 6-0's and 6-1's are more frequent than expected given 50-50% chances.
--   Notably 6-4's occur less frequently than expected
--   p-values are not significant for any
-:::
 
@@
 
--   Round win % after a streak of 3 round wins:
+Round win % after a streak of 3 round wins:
+
 -   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
 -   Actual: **`r 100 * round(cod_round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r cod_round_win_prop_after_b2b2b_wins$n` / `r cod_round_win_prop_after_b2b2b_wins$total`)
-
-::: notes
--   Note this is sort of biased by the fact that teams end up winning series in 6 cod_rounds more often than expected.
-:::
 

### 2022-07-20 presentation.qmd
remove old conditional prob stuff

@@
 
-# round_and_series_win_prop <- cod_rounds |> 
-#   group_by(pre_cumu_w, pre_cumu_l) |> 
-#   summarize(
-#     n = n(),
-#     across(c(win_round, win_series), sum)
-#   ) |> 
-#   ungroup() |> 
-#   mutate(
-#     win_round_prop = win_round / n,
-#     win_series_prop = win_series / n
-#   )
-# 
-# pluck_round_win_prop <- function(w = 0, l = 0) {
-#   round_and_series_win_prop |> 
-#     filter(pre_cumu_w == w, pre_cumu_l == l) |> 
-#     pull(win_round_prop)
-# }
-# 
-# compute_conditional_probs <- function(
-    #     p00 = 0.5,
-#     p10 = p00,
-#     p20 = p00,
-#     p30 = p00,
-#     p40 = p00,
-#     p50 = p00,
-#     p11 = p00, p21 = p00, p31 = p00, p41 = p00, p51 = p00,
-#     p52 = p00, p53 = p00, p54 = p00
-# ) {
-#   pr6 <- p10 * p20 * p30 * p40 * p50
-#   # pr7 <- p51 * (p10 * p20 * p30 * p40 * (1 - p50) + p10 * p20 * p30 * (1 - p40) * p41 + p10 * p20 * (1 - p30) * p41 + p10 * (1 - p20) * p31 * p41 + (1 - p10) * p21 * p31 * p41)
-#   pr7 <- (
-#     (p00 * p10 * p20 * p30 * p40 * (1 - p50) * p51) +   ## aaaaaba
-#     (p00 * p10 * p20 * p30 * (1 - p40) * p41 * p51) + ## aaaabaa
-#     (p00 * p10 * p20 * (1 - p30) * p31 * p41 * p51) + ## aaabaaa
-#     (p00 * p10 * (1 - p20) * p21 * p31 * p41 * p51) + ## aabaaaa
-#     (p00 * (1 - p10) * p11 * p21 * p31 * p41 * p51) + ## abaaaaa
-#     ((1 - p00) * (1 - p10) * p11 * p21 * p31 * p41 * p51) + ## baaaaaa
-#     
-#     ((1 - p00) * p10 * p20 * p30 * p40 * (1 - p50) * p51) + ## bbbbbab
-#     ((1 - p00) * p10 * p20 * p30 * (1 - p40) * p41 * p51) + ## bbbbabb
-#     ((1 - p00) * p10 * p20 * (1 - p30) * p31 * p41 * p51) + ## bbbabbb
-#     ((1 - p00) * p10 * (1 - p20) * p21 * p31 * p41 * p51) + ## bbabbbb
-#     ((1 - p00) * (1 - p10) * (1 - p11) * p21 * p31 * p41 * p51) + ## babbbbb
-#     (p00 * (1 - p10) * (1 - p11) * p21 * p31 * p41 * p51) ## abbbbbb
-# )
-#   
-#   ## NOTE: pr8 and pr9 are broken.
-although we can use the simple subtraction of other probabilities for pr10 and pr11 like pr6 and pr7 in a 7 game series, they aren't valid for pr8 and pr9 in an 11 game series.
-#   pr8 <- (1 - pr6 - pr7) * p52
-#   pr9 <- (1 - pr6 - pr7 - pr8) * p53
-#   pr10 <- (1 - pr6 - pr7 - pr8 - pr9) * p54
-#   pr11 <- 1 - pr6 - pr7 - pr8 - pr9 - pr10
-#   tibble(
-#     n_rounds = 6L:11L,
-#     p = c(pr6, pr7, pr8, pr9, pr10, pr11)
-#   )
-# }
-# 
-# ## pr6 and pr7 should match up with what we see later with `possibilities`
-# conditional_series_probs <- compute_conditional_probs(
-#   p00 = pluck_round_win_prop(0, 0),
-#   p10 = pluck_round_win_prop(1, 0),
-#   p20 = pluck_round_win_prop(2, 0),
-#   p30 = pluck_round_win_prop(3, 0),
-#   p40 = pluck_round_win_prop(4, 0),
-#   p50 = pluck_round_win_prop(5, 0),
-#   p11 = pluck_round_win_prop(1, 1),
-#   p21 = pluck_round_win_prop(2, 1),
-#   p31 = pluck_round_win_prop(3, 1),
-#   p41 = pluck_round_win_prop(4, 1),
-#   p51 = pluck_round_win_prop(5, 1),
-#   p52 = pluck_round_win_prop(5, 2),
-#   p53 = pluck_round_win_prop(5, 3),
-#   p54 = pluck_round_win_prop(5, 4)
-# )
-
 common_cod_labs <- function(...) {

### 2022-07-20 presentation.qmd
fix val plot and rm extra val chunk, render as pdf without notes

@@
 
-## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?
-
-```{r}
-#| label: p_filt_val_o_series_win_prop_over_expected
-filt_val_o_win_prop <- val_o_win_prop |> 
-  filter(
-    pre_cumu_w >= 3, pre_cumu_l >= 3
-  )
-filt_val_max_diff_win_series_prop <- max(abs(filt_val_o_win_prop$diff_win_series_prop))
-p_filt_val_o_series_win_prop_over_expected <- filt_val_o_win_prop |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(
-    .fill = 'diff_win_series_prop'
-  ) +
-  heatmap_text_layers(
-    .df = filt_val_o_win_prop, 
-    .f = o_series_win_over_expected_text_layer,
-    .threshold = 0.1,
-    .labeller = val_heatmap_div_labeller
-  ) +
-  scale_fill_gradient2(
-    low = extract_ggsci_mid_color('brown'),
-    high = extract_ggsci_mid_color('cyan'),
-    mid = 'white',
-    limits = c(
-      -filt_val_max_diff_win_series_prop,
-      +filt_val_max_diff_win_series_prop
-    ),
-    midpoint = 0
-  ) +
-  labs(
-    title = 'Offensive Series Win % Over Expected'
-  )
-p_filt_val_o_series_win_prop_over_expected
-save_for_slide(p_val_o_series_win_prop_over_expected)
-```
-
-![](val_o_series_win_prop_over_expected.png){fig-align="center"}
-
 ## Are offensive win %'s different in round 1?

### 2022-07-22 presentation.qmd
start trying logos

@@
 library(ggnewscale)
+library(magick)
+
 blackish_background <- '#191919' ## to match slide background
@@
 update_geom_defaults('segment', list(color = 'white'))
+
+add_logo <- function(
+    path,
+    path_logo,
+    idx_x,
+    idx_y,
+    logo_scale = 0.1,
+    adjust_x = TRUE,
+    adjust_y = TRUE,
+    path_suffix = '_w_logo',
+    delete = TRUE
+) {
+
+  plot <- magick::image_read(path)
+  logo_raw <- magick::image_read(path_logo)
+
+  plot_height <- magick::image_info(plot)$height
+  plot_width <- magick::image_info(plot)$width
+
+  logo <- magick::image_scale(logo_raw, as.character(round(plot_width * logo_scale)))
+
+  info <- magick::image_info(logo)
+  logo_width <- info$width
+  logo_height <- info$height
+
+  x_pos <- plot_width - idx_x * plot_width
+  y_pos <- plot_height - idx_y * plot_height
+
+  if (adjust_x) {
+    x_pos <- x_pos - logo_width
+  }
+
+  if (adjust_y) {
+    y_pos <- y_pos - logo_height
+  }
+
+  offset <- paste0('+', x_pos, '+', y_pos)
+
+  img <- magick::image_composite(plot, logo, offset = offset)
+  ext <- tools::file_ext(path)
+  rgx_ext <- sprintf('[.]%s$', ext)
+
+  res <- magick::image_write(
+    img,
+    gsub(rgx_ext, sprintf('%s.%s', path_suffix, ext), path)
+  )
+
+  if (!delete) {
+    return(res)
+  }
+  unlink(path, recursive = TRUE, force = TRUE)
+  res
+}
+
 ```
@@
 
-## What are your chances of winning a round, given the series state in [COD SnD]{.cod}?
+## What are your chances of winning the next round ([COD SnD]{.cod})?
 
@@
 .dpi <- 300
-save_for_slide <- function(
+save_plot_for_slide <- function(
     p, 
@@
     dpi = .dpi,
+    # game = c('cod', 'val'),
     ...
 ) {
-  ggsave(
+
+  path <- ggsave(
     plot = p,
@@
     ...
+  )
+  is_cod <- filename |> str_detect('cod_')
+  game <- ifelse(is_cod, 'cod', 'val')
+  logo_scale <- ifelse(is_cod, 0.15, 0.07)
+  add_logo(
+    path,
+    path_logo = file.path('images', sprintf('%s.png', game)),
+    delete = FALSE,
+    path_suffix = '',
+    logo_scale = logo_scale,
+    idx_x = 0.99,
+    idx_y = 0.01,
+    adjust_x = FALSE
   )
@@
 p_cod_o_round_win_prop
-save_for_slide(p_cod_o_round_win_prop)
+save_plot_for_slide(p_cod_o_round_win_prop)
 ```
@@
 p_cod_o_round_win_prop_over_expected
-save_for_slide(p_cod_o_round_win_prop_over_expected)
+save_plot_for_slide(p_cod_o_round_win_prop_over_expected)
 ```
@@
 
-## What are your chances of winning a round, given the series state in [Valorant]{.valorant}?
+## What are your chances of winning the next round ([Valorant]{.valorant})?
 
@@
 p_val_o_round_win_prop
-save_for_slide(p_val_o_round_win_prop)
+save_plot_for_slide(p_val_o_round_win_prop)
 ```
@@
 
-## What are your chances of winning the series, given the series state in [COD SnD]{.cod}?
+## What are your chances of winning the series ([COD SnD]{.cod})?
 
@@
 p_cod_o_series_win_prop
-save_for_slide(p_cod_o_series_win_prop)
+save_plot_for_slide(p_cod_o_series_win_prop)
 ```
@@
 p_cod_o_series_win_prop_over_expected
-save_for_slide(p_cod_o_series_win_prop_over_expected)
+save_plot_for_slide(p_cod_o_series_win_prop_over_expected)
 ```
@@
 
-## What are your chances of winning the series, given the series state in [Valorant]{.valorant}?
+## What are your chances of winning the series ([Valorant]{.valorant})?
 
@@
 p_val_o_series_win_prop
-save_for_slide(p_val_o_series_win_prop)
+save_plot_for_slide(p_val_o_series_win_prop)
 ```
@@
 p_val_o_series_win_prop_over_expected
-save_for_slide(p_val_o_series_win_prop_over_expected)
+save_plot_for_slide(p_val_o_series_win_prop_over_expected)
 ```
@@
 
-## Are offensive win %'s different in round 1?
+## Are offensive win %'s different in round 1 ([COD SnD]{.cod}?
 
@@
 p_cod_o_win_r1_vs_post_round_prop
-save_for_slide(p_cod_o_win_r1_vs_post_round_prop)
+save_plot_for_slide(p_cod_o_win_r1_vs_post_round_prop)
 ```
@@
 p_cod_series_outcome_prop_over_expected
-save_for_slide(p_cod_series_outcome_prop_over_expected)
+save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
 ```
@@
 p_cod_b2b_round_win_prop
-save_for_slide(p_cod_b2b_round_win_prop)
+save_plot_for_slide(p_cod_b2b_round_win_prop)
 # ## now accounting for number of cod_rounds that end up being played AND series winners...

### 2022-07-23 presentation.qmd
re-render pngs with logos, refactor streaks

@@
 val_n_series <- val_rounds |> 
-  distinct(game_id) |> 
+  distinct(series_id) |> 
   nrow() |> 
@@
 val_n_rounds <- val_rounds |> 
-  distinct(game_id, round) |> 
+  distinct(series_id, round) |> 
   nrow() |> 
@@
 
-p_val_o_round_win_prop <- val_o_win_prop |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(.fill = 'win_round_prop') +
+val_swap_path <- function(...) {
+  list(
+    ...,
     geom_path(
@@
       )
-  ) +
+    )
+  )
+}
+
+p_val_o_round_win_prop <- val_o_win_prop |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(.fill = 'win_round_prop') +
+  val_swap_path() +
   heatmap_text_layers(
@@
   heatmap_tile(.fill = 'win_series_prop') +
-  geom_path(
-    data = val_pre_swap_round_segments,
-    color = 'white',
-    size = 1.5,
-    aes(
-      x = pre_cumu_w, 
-      y = pre_cumu_l
-    )
-  ) +
+  val_swap_path() +
   heatmap_text_layers(
@@
   ) +
+  val_swap_path() +
   scale_fill_gradient2(
@@
 
+## What are your chances of winning the series ([Valorant]{.valorant})?
+
+```{r}
+#| label: p_filt_val_o_series_win_prop_over_expected
+filt_val_o_win_prop <- val_o_win_prop |> 
+  mutate(
+    across(
+      diff_win_series_prop,
+      ~case_when(
+        pre_cumu_w <= 3 & pre_cumu_l <= 3 ~ NA_real_,
+        TRUE ~ .x
+      )
+    )
+  )
+filt_val_max_diff_win_series_prop <- max(abs(filt_val_o_win_prop$diff_win_series_prop))
+
+p_filt_val_o_series_win_prop_over_expected <- filt_val_o_win_prop |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(
+    .fill = 'diff_win_series_prop'
+  ) +
+  # geom_abline(
+  #   color = 'white',
+  #   linetype = 2,
+  #   aes(
+  #     slope = 1,
+  #     intercept = 0
+  #   )
+  # ) +
+  heatmap_text_layers(
+    .df = filt_val_o_win_prop, 
+    .f = o_series_win_over_expected_text_layer,
+    .threshold = 0.1,
+    .labeller = val_heatmap_div_labeller
+  ) +
+  val_swap_path() +
+  scale_fill_gradient2(
+    low = extract_ggsci_mid_color('brown'),
+    high = extract_ggsci_mid_color('cyan'),
+    mid = 'white',
+    limits = c(
+      -filt_val_max_diff_win_series_prop,
+      +filt_val_max_diff_win_series_prop
+    ),
+    midpoint = 0
+  ) +
+  labs(
+    title = 'Offensive Series Win % Over Expected'
+  )
+p_filt_val_o_series_win_prop_over_expected
+save_plot_for_slide(p_val_o_series_win_prop_over_expected)
+```
+
 ## Are offensive win %'s different in round 1 ([COD SnD]{.cod}?
@@
 #| label: p_cod_o_win_r1_vs_post_round_prop
-calculate_cod_o_round_win_prop <- function(df) {
-  df |> 
-    count(year, game, map, is_offense, win_round) |> 
-    group_by(map, is_offense) |> 
-    mutate(total = sum(n), prop = n / total) |> 
-    ungroup() |>
-    filter(win_round, is_offense) |>
-    select(
-      year,
-      game,
-      map,
-      rounds_won = n,
-      total_rounds = total,
-      win_round_prop = prop
-    ) |>
-    arrange(desc(win_round_prop))
-}
-
 # https://raw.githubusercontent.com/dgrtwo/splittestr/master/R/vectorized-prop-test.R
@@
 
-summarize_cod_o_round_win_prop <- function(.round) {
-
-  specified_round <- cod_rounds |> 
+calculate_map_o_round_win_prop <- function(df) {
+  df |> 
+    count(map, is_offense, win_round) |> 
+    group_by(map, is_offense) |> 
+    mutate(total = sum(n), prop = n / total) |> 
+    ungroup() |>
+    filter(win_round, is_offense) |>
+    select(
+      map,
+      rounds_won = n,
+      total_rounds = total,
+      win_round_prop = prop
+    ) |>
+    arrange(desc(win_round_prop))
+}
+
+summarize_map_o_round_win_prop <- function(df, .round) {
+
+  specified_round <- df |> 
     filter(round == .round) |> 
-    calculate_cod_o_round_win_prop()
-
-  post_rounds <- cod_rounds |> 
+    calculate_map_o_round_win_prop()
+
+  post_rounds <- df |> 
     filter(round > .round) |> 
-    calculate_cod_o_round_win_prop()
+    calculate_map_o_round_win_prop()
 
@@
     inner_join(
-      post_rounds |> rename_with(~sprintf('post_%s', .x), -c(year, game, map)),
-      by = c('year', 'game', 'map')
+      post_rounds |> rename_with(~sprintf('post_%s', .x), -c(map)),
+      by = 'map'
     ) |> 
@@
       dir = factor(sign(diff_prop)),
-      is_significant = p_value < 0.05,
-      label = sprintf('%s - %s (%s)', map, game, year)
+      is_significant = p_value < 0.05
     )
@@
 
-plot_cod_round_vs_post_round_slope_chart <- function(.round) {
-  o_win_rx_prop <- summarize_cod_o_round_win_prop(.round)
+plot_round_vs_post_round_slope_chart <- function(df, .round, game = c('cod', 'val')) {
+  game <- match.arg(game)
+  o_win_rx_prop <- summarize_map_o_round_win_prop(df, .round)
   x1_label <- sprintf('Round %d<br/>offensive win %%', .round)
@@
   max_o_win_rx_prop <- o_win_rx_prop |> slice_max(diff_prop, n = 1)
-  minmax_labels <- c(min_o_win_rx_prop$label, max_o_win_rx_prop$label)
+  minmax_maps <- c(min_o_win_rx_prop$map, max_o_win_rx_prop$map)
+
+  is_cod <- game == 'cod'
+  if (is_cod) {
+    y_lo <- 0.25
+    y_hi <- 0.75
+  } else {
+    y_lo <- 0.45
+    y_hi <- 0.55
+  }
 
@@
       data = tibble(),
-      aes(yintercept = c(0.25, 0.5, 0.75)), 
+      aes(yintercept = c(y_lo, 0.5, y_hi)), 
       linetype = 2,
@@
         mutate(
-          big_segment = label %in% minmax_labels
+          big_segment = map %in% minmax_maps
         ),
@@
         size = big_segment,
-        group = label
+        group = map
       )
@@
       data = tibble(
-        y = c(0.25, 0.75)
+        y = c(y_lo, y_hi)
       ) |> 
@@
       data = o_win_rx_prop |> 
-        filter(label %in% !!minmax_labels),
-      aes(x = 1, y = win_round_prop, label = label),
+        filter(map %in% !!minmax_maps),
+      aes(x = 1, y = win_round_prop, label = map),
       family = font,
@@
       data = o_win_rx_prop |> 
-        filter(!(label %in% !!minmax_labels)),
-      aes(x = 2, y = post_win_round_prop, label = label),
+        filter(!(map %in% !!minmax_maps)),
+      aes(x = 2, y = post_win_round_prop, label = map),
       family = font,
@@
     scale_y_continuous(
-      limits = c(0.25, 0.75)
+      limits = c(y_lo, y_hi)
     ) +
@@
 
-cod_res_r1 <- plot_cod_round_vs_post_round_slope_chart(1)
+cod_res_r1 <- cod_rounds |> 
+  mutate(
+    map = sprintf('%s - %s (%s)', map, game, year)
+  ) |> 
+  plot_round_vs_post_round_slope_chart(1, game = 'cod')
 
@@
     aes(x = x, y = y, hjust = hjust, vjust = vjust, label = lab)
-  )
+  ) +
+  common_cod_labs()
 p_cod_o_win_r1_vs_post_round_prop
@@
 
+## Are offensive win %'s different in round 1 ([Valorant]{.valorant}?
+
+```{r}
+#| label: p_val_o_win_r1_vs_post_round_prop
+p_val_o_win_r1_vs_post_round_prop <- val_rounds |> 
+  plot_round_vs_post_round_slope_chart(1, game = 'val') |> 
+  pluck('plot') +
+  common_val_labs()
+save_plot_for_slide(p_val_o_win_r1_vs_post_round_prop)
+```
+
+![](val_o_win_r1_vs_post_round_prop.png){fig-align="center"}
+
 ## What are the most common series winning states?
@@
 # https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422
-prob_of_series_lasting_n_games <- function(n, p = 0.5, max_rounds = 11) {
-  s <- ceiling(max_rounds / 2)
+prob_of_series_lasting_n_games <- function(n, p = 0.5, max_round) {
+  s <- ceiling(max_round / 2)
   (factorial(n - 1) / (factorial(s - 1) * factorial(n - s))) * (p^s * (1 - p)^(n - s) + p^(n - s) * (1 - p)^s)
@@
 
-possibilities_of_outcomes <- function(m, n) {
+expected_series_streaks_of_outcomes <- function(m, n) {
   factorial(m + n) / (factorial(m) * factorial(n))
@@
 
-cod_actual_series_streaks <- cod_rounds |> 
+summarize_streaks <- function(rounds, game = c('cod', 'val')) {
+  rounds <- val_rounds
+  game = 'val'
+  .max_round <- ifelse(game == 'cod', 11, 25)
+
+  sudden_death_rounds <- rounds |> 
+    filter(max_round > .max_round)
+
+  rounds1 <- rounds
+  ## should only happen in val
+  if(nrow(sudden_death_rounds) > 0) {
+
+    sudden_death_series_ids <- sudden_death_rounds |> 
+      distinct(series_id)
+
+    imputed_suddent_death_rounds <- sudden_death_rounds |> 
+      mutate(
+        round = .max_round
+      ) |> 
+      select(series_id, round, is_offense) |> 
+      inner_join(
+        rounds,
+        by = c('series_id', 'round', 'is_offense')
+      )
+
+    rounds <- bind_rows(
+      rounds |> 
+        filter(max_round <= .max_round),
+      imputed_suddent_death_rounds
+    )
+  }
+
+  cutoff <- (.max_round + 1) / 2
+
+  actual_round_streaks <- rounds |> 
+    filter(round <= .max_round) |> 
     filter(win_series) |> 
     mutate(across(win_round, as.integer)) |> 
-  group_by(year, event, series) |> 
+    group_by(series_id) |> 
     summarize(
@@
     ) |>
-  count(n_rounds, record, ws, sort = TRUE) |> 
+    count(record, n_rounds, ws, sort = TRUE) |> 
     mutate(prop = n / sum(n))
 
-cod_possibilities <- tibble(
-  n_rounds = 6L:11L
-) |> 
-  mutate(
-    series_prop = map_dbl(n_rounds, prob_of_series_lasting_n_games),
-    possibilities = map2_dbl(6, n_rounds - 6, possibilities_of_outcomes)
+  expected_round_streaks <- tibble(
+    n_rounds = cutoff:.max_round
+  ) |> 
+    mutate(
+      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_n_games(.x, max_round = .max_round)),
+      n_expected_series_streaks = map2_dbl(cutoff, n_rounds - cutoff, expected_series_streaks_of_outcomes)
     ) |> 
@@
       series_prop,
-    record = sprintf('6-%d', n_rounds - 6),
-    prop = series_prop / possibilities
-  )
-
-cod_series_streaks <- inner_join(
-  cod_actual_series_streaks |> 
+      prop = series_prop / n_expected_series_streaks
+    )
+
+  round_streaks <- full_join(
+    actual_round_streaks |> 
       rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-  cod_possibilities |> 
+    expected_round_streaks |> 
       rename_with(~sprintf('%s_expected', .x), prop),
     by = 'n_rounds'
-) |> 
-  mutate(
-    prop_diff = prop_actual - prop_expected
-  ) |> 
-  arrange(desc(abs(prop_diff)))
-# series_streaks |> filter(is.na(n_actual))
-
-## 6-0, 6-1, and some combos of 6-5 occur more often than expected
-cod_series_streak_props <- cod_series_streaks |> 
-  filter(!is.na(n_actual)) |> 
+  )
+
+  round_streak_prop <- round_streaks |> 
+    drop_na() |> 
     mutate(
@@
 
-## 6-0 and 6-1 occur more often than expected
-cod_series_outcome_prop <- full_join(
-  cod_actual_series_streaks |> 
-    group_by(record) |> 
+  series_outcomes <- full_join(
+    actual_round_streaks |> 
+      group_by(record, n_rounds) |> 
       summarize(
@@
       ) |> 
+      ungroup() |> 
       mutate(prop = n / sum(n)) |> 
       rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-  cod_possibilities |> 
-    select(record, prop_expected = series_prop),
-  by = 'record'
-) |> 
+    expected_round_streaks |> 
+      select(n_rounds, prop_expected = series_prop),
+    by = 'n_rounds'
+  )
+
+  series_outcome_prop <- series_outcomes |> 
+    drop_na() |> 
     mutate(
@@
 
-cod_long_series_outcome_prop <- cod_series_outcome_prop |>
+  list(
+    rounds = series_streak_prop,
+    series = series_outcome_prop
+  )
+}
+
+cod_streaks_res <- cod_rounds |> summarize_streaks(game = 'cod')
+val_streaks_res <- val_rounds |> summarize_streaks(game = 'val')
+cod_long_series_outcome_prop <- cod_streaks_res$series |>
   select(

### 2022-07-23 1-scrape-cod.R
refactor cod scraping

@@ -8,27 +8,36 @@ library(qs)
 dir_data <- 'data'
 dir.create(dir_data, showWarnings = FALSE)
 
-sheets <- list(
-  '2022' = crossing(
-    s = c(1, 2, 3, 4),
-    raw_series = c(1, 2, 3, 4)
+generate_cod_sheets <- function(year = c('2021', '2022')) {
+  year <- match.arg(year)
+  is_2022 <- year == '2022'
+  if (is_2022) {
+    max_s <- 4
+    prefix <- 'Wk'
+  } else {
+    max_s <- 5
+    prefix <- 'HS'
+  }
+  
+  labs <- crossing(
+    s = 1:max_s,
+    series = 1:4
   ) |> 
     mutate(
-      label = sprintf('S%d %s', s, ifelse(raw_series == 4, 'Major', sprintf('Wk%d', raw_series)))
+      label = sprintf('S%d %s', s, ifelse(series == 4, 'Major', sprintf('%s%d', !!prefix, series)))
     ) |> 
-    pull(label) %>%
-    .[1:14],
-  '2021' = c(
-    'Champs', 
-    crossing(
-      s = c(1, 2, 3, 4, 5),
-      raw_series = c(1, 2, 3, 4)
-    ) |> 
-      mutate(
-        label = sprintf('S%d %s', s, ifelse(raw_series == 4, 'Major', sprintf('HS%d', raw_series)))
-      ) |> 
-      pull(label)
-  ),
+    pull(label)
+  
+  if(is_2022) {
+    return(labs)
+  }
+  
+  c('Champs', labs)
+}
+
+cod_sheets <- list(
+  '2022' = generate_cod_sheets('2022'),
+  '2021' =  generate_cod_sheets('2021'),
   '2020' = sprintf(
     '%s_SnD',
     c('CHAMPS', 'LAUNCH', 'LON', 'ATL', 'LA', 'DAL', 'CHI', 'FLA', 'SEA', 'MIN', 'PAR', 'NY', 'LON2', 'TOR')
@@ -147,13 +156,13 @@ read_snd_sheet <- function(year, sheet, overwrite = FALSE) {
   res
 }
 
-raw_series <- sheets |> 
+raw_cod_series <- cod_sheets |> 
   mutate(
-    data = map2(year, sheet, read_snd_sheet, overwrite = F)
+    data = map2(year, sheet, read_snd_sheet, overwrite = FALSE)
   ) |> 
[…]

### 2022-07-24 1-scrape-valorant.R
val cleanup

@@ -91,6 +91,10 @@ init_val_rounds_side <- raw_val_rounds |>
     )
   )
 
+## note that the notion of a series may be confusing. in valorant, we typically think
+##  of a match/game as the first to 13 round wins, and the series as the first to 2 match/game/map wins.
+##  however, i'm treating match/game/map as a "series" since we're not really interested in cumulative
+##  match/game/map wins between 2 teams.
 val_series_outcomes <- init_val_rounds_side |>
   group_by(game_id) |>
   slice_max(round, n = 1, with_ties = FALSE) |>
@@ -104,54 +108,20 @@ val_series_outcomes <- init_val_rounds_side |>
 weird_val_series_outcomes <- val_series_outcomes |>
   filter(max_cumu_wl > 13 & (min_cumu_wl < (max_cumu_wl - 2)))
 
-val_team_abbrvs <- val_scoreboard |> 
-  distinct(game_id, team_abbrv = team_abbreviation) |> 
-  mutate(across(team_abbrv, ~toupper(.x) |> str_squish()))
-
-raw_val_team_mapping <- bind_rows(
-  val_games |>
-    distinct(game_id, team_id = team1id, team = team1),
-  val_games |>
-    distinct(game_id, team_id = team2id, team = team2)
-) |>
-  distinct(game_id, team_id, team) |>
-  arrange(team_id) |> 
-  inner_join(val_team_abbrvs, by = 'game_id') |> 
-  distinct(game_id, team_id, team, team_abbrv) |> 
-  count(team_id, team, team_abbrv) |> 
-  group_by(team_id, team) |> 
-  slice_max(n, n = 1, with_ties = FALSE) |> 
-  ungroup() |> 
-  arrange(desc(n))
-
-# val_team_mapping <- raw_val_team_mapping |> 
-#   filter(team_abbrv != '', n >= 5)
-val_team_mapping <- raw_val_team_mapping
-
-val_games |> 
-  inner_join(
-    val_team_mapping |> distinct(winner = team, winner_abbrv = team_abbrv),
-    by = 'winner'
-  ) |> 
-  count(game_id, match_id, winner, winner_abbrv, sort = TRUE)
-
-val_games |> 
-  transmute(
-    game_id,
-    team1,
-    team2,
-    team1_side_first_half,
-    total_rounds = team1_total_rounds + team2_total_rounds
-  ) |> 
-  inner_join(
-    val_series_outcomes |> 
[…]

### 2022-07-25 presentation.qmd
more val cleaning, re-arrange plots

@@
 ---
-title: '"Turned on!": Momentum in Round-Based First Person Shooter Esports'
+title: "They're on Fire: Team Momentum in Round-Based First Person Shooter Esports"
 author: 'Tony ElHabr'
@@
     dpi = .dpi,
-    # game = c('cod', 'val'),
     ...
@@
     plot = p,
-    filename = filename,
+    filename = file.path('plots', filename),
     width = width * dpi,
@@
 
-![](cod_o_round_win_prop.png){fig-align="center"}
+![](plots/cod_o_round_win_prop.png){fig-align="center"}
 
@@
 
-![](cod_o_round_win_prop_over_expected.png){fig-align="center"}
+![](plots/cod_o_round_win_prop_over_expected.png){fig-align="center"}
 
@@
 
-![](val_o_round_win_prop.png){fig-align="center"}
+![](plots/val_o_round_win_prop.png){fig-align="center"}
 
@@
 
-![](cod_o_series_win_prop.png){fig-align="center"}
+![](plots/cod_o_series_win_prop.png){fig-align="center"}
 
@@
 
-![](cod_o_series_win_prop_over_expected.png){fig-align="center"}
+![](plots/cod_o_series_win_prop_over_expected.png){fig-align="center"}
 
@@
 
-![](val_o_series_win_prop.png){fig-align="center"}
+![](plots/val_o_series_win_prop.png){fig-align="center"}
 
@@
 
-![](val_o_series_win_prop_over_expected.png){fig-align="center"}
+![](plots/val_o_series_win_prop_over_expected.png){fig-align="center"}
 
@@
 
-## Are offensive win %'s different in round 1 ([COD SnD]{.cod}?
+## Are offensive win %'s different in round 1 ([COD SnD]{.cod})?
 
@@
 cod_res_r1 <- cod_rounds |> 
-  mutate(
-    map = sprintf('%s - %s (%s)', map, game, year)
-  ) |> 
   plot_round_vs_post_round_slope_chart(1, game = 'cod')
@@
 
-![](cod_o_win_r1_vs_post_round_prop.png){fig-align="center"}
-
-## Are offensive win %'s different in round 1 ([Valorant]{.valorant}?
+![](plots/cod_o_win_r1_vs_post_round_prop.png){fig-align="center"}
+
+## Are offensive win %'s different in round 1 ([Valorant]{.valorant})?
 
@@
 
-![](val_o_win_r1_vs_post_round_prop.png){fig-align="center"}
-
-## What are the most common series winning states?
+![](plots/val_o_win_r1_vs_post_round_prop.png){fig-align="center"}
+
+## What are the most common series winning states ([COD SnD]{.cod})?
 
@@
 summarize_streaks <- function(rounds, game = c('cod', 'val')) {
-  rounds <- val_rounds
-  game = 'val'
-  .max_round <- ifelse(game == 'cod', 11, 25)
-
-  sudden_death_rounds <- rounds |> 
-    filter(max_round > .max_round)
-
-  rounds1 <- rounds
-  ## should only happen in val
-  if(nrow(sudden_death_rounds) > 0) {
-
-    sudden_death_series_ids <- sudden_death_rounds |> 
-      distinct(series_id)
-
-    imputed_suddent_death_rounds <- sudden_death_rounds |> 
-      mutate(
-        round = .max_round
-      ) |> 
-      select(series_id, round, is_offense) |> 
-      inner_join(
-        rounds,
-        by = c('series_id', 'round', 'is_offense')
-      )
-
-    rounds <- bind_rows(
-      rounds |> 
-        filter(max_round <= .max_round),
-      imputed_suddent_death_rounds
-    )
+  if (game == 'cod') {
+    .max_round <- 11
+    .adj <- 0
+  } else {
+    .max_round <- 25
+    .adj <- 1
   }
@@
   actual_round_streaks <- rounds |> 
-    filter(round <= .max_round) |> 
+    filter(round <= (.max_round - .adj)) |> 
     filter(win_series) |> 
@@
   list(
-    rounds = series_streak_prop,
+    rounds = round_streak_prop,
     series = series_outcome_prop
@@
 
-cod_streaks_res <- cod_rounds |> summarize_streaks(game = 'cod')
-val_streaks_res <- val_rounds |> summarize_streaks(game = 'val')
-cod_long_series_outcome_prop <- cod_streaks_res$series |>
+plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
+  if (game == 'cod') {
+    .lvls <- sprintf('6-%d', 0:5)
+    .axis_x_text_size <- 14
+  } else {
+    .lvls <- c(sprintf('13-%d', 0:11), '12-12')
+    .axis_x_text_size <- 12
+  }
+
+  long_series_outcome_prop <- series_outcome_prop |>
     select(
@@
     ) |> 
-  mutate(across(outcome_idx, as.integer))
-
-cod_max_diff_series_outcome_prop <- cod_long_series_outcome_prop |> 
+    mutate(
+      across(outcome_idx, as.integer),
+      across(record, ~factor(.x, levels = .lvls))
+    )
+
+  max_diff_series_outcome_prop <- long_series_outcome_prop |> 
     filter(outcome_idx == 1) |> 
@@
 
-p_cod_series_outcome_prop_over_expected <- cod_long_series_outcome_prop |> 
+  long_series_outcome_prop |> 
     ggplot() +
@@
     geom_tile(
-    data = cod_long_series_outcome_prop |> filter(outcome_idx > 1),
+      data = long_series_outcome_prop |> filter(outcome_idx > 1),
       show.legend = FALSE,
@@
     geom_tile(
-    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1),
+      data = long_series_outcome_prop |> filter(outcome_idx == 1),
       show.legend = FALSE,
@@
       limits = c(
-      -cod_max_diff_series_outcome_prop, 
-      +cod_max_diff_series_outcome_prop
+        -max_diff_series_outcome_prop, 
+        +max_diff_series_outcome_prop
       )
@@
     geom_text(
-    data = cod_long_series_outcome_prop |> filter(outcome_idx == 3),
+      data = long_series_outcome_prop |> filter(outcome_idx == 3),
       color = blackish_background,
@@
     geom_text(
-    data = cod_long_series_outcome_prop |> filter(outcome_idx == 2),
+      data = long_series_outcome_prop |> filter(outcome_idx == 2),
       color = blackish_background,
@@
     geom_text(
-    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
+      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
       color = blackish_background,
@@
     geom_text(
-    data = cod_long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
+      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
       color = 'white',
@@
       plot.title = ggtext::element_markdown(hjust = 0.5),
-    axis.text = element_text(size = 16, face = 'bold')
+      axis.text = element_text(size = 14, face = 'bold'),
+      axis.text.x = element_text(size = .axis_x_text_size, face = 'bold')
     ) +
@@
       y = NULL
-  ) +
+    )
+}
+
+cod_streaks_res <- cod_rounds |> summarize_streaks('cod')
+
+p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
+  plot_series_outcome_prop_over_expected('cod') +
   common_cod_labs()
@@
 
-![](cod_series_outcome_prop_over_expected.png){fig-align="center"}
-
-## When do back-to-back round wins occur?
+![](plots/cod_series_outcome_prop_over_expected.png){fig-align="center"}
+
+## What are the most common series winning states ([Valorant]{.valorant})?
+
+```{r}
+#| label: p_val_series_outcome_prop_over_expected
+val_streaks_res <- val_rounds |> summarize_streaks('val')
+
+p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
+  plot_series_outcome_prop_over_expected('val') +
+  common_val_labs()
+p_val_series_outcome_prop_over_expected
+save_plot_for_slide(p_val_series_outcome_prop_over_expected)
+```
+
+![](plots/val_series_outcome_prop_over_expected.png)
+
+```{r}
+#| label: altnerative-to-p=0.5-method-1
+## p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
+theoretical_cod_series_length <- function(p) {
+  6 * prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11) +
+    7 * prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11) + 
+    8 * prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11) + 
+    9 * prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11) +
+    10 * prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11) +
+    11 * prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)
+}
+
+cod_ps <- tibble(p = seq(0.5, 0.7, by = 0.0025))
+
+cod_theoretical_series_lengths <- cod_ps |> 
+  mutate(
+    theoretical_series_length = map_dbl(p, theoretical_cod_series_length)
+  )
+
+cod_rounds_per_series <- cod_streaks_res$series |> 
+  summarize(
+    actual = sum(n_rounds * prop_actual),
+    expected = sum(n_rounds * prop_expected)
+  )
+
+cod_theoretical_constant_p <- cod_theoretical_series_lengths |> 
+  mutate(
+    diff = theoretical_series_length - cod_rounds_per_series$actual
+  ) |> 
+  slice_min(abs(diff), n = 1) |> 
+  pull(p)
+cod_theoretical_constant_p
+```
+
+```{r}
+#| label: altnerative-to-p=0.5-method-2
+pluck_cod_n <- function(.n_rounds) {
+  cod_streaks_res$series |>
+    filter(n_rounds == .n_rounds) |> 
+    pull(n_actual)
+}
+
+n6 <- pluck_cod_n(6)
+n7 <- pluck_cod_n(7)
+n8 <- pluck_cod_n(8)
+n9 <- pluck_cod_n(9)
+n10 <- pluck_cod_n(10)
+n11 <- pluck_cod_n(11)
+pm <- pmin(n6, n7, n8, n9, n10, n11)
+n6adj <- round(10 * n6 / pm)
+n7adj <- round(10 * n7 / pm)
+n8adj <- round(10 * n8 / pm)
+n9adj <- round(10 * n9 / pm)
+n10adj <- round(10 * n10 / pm)
+n11adj <- round(10 * n11 / pm)
+
+maximize_cod_series_p <- function(p) {
+  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^n6adj *
+    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^n7adj * 
+    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^n8adj * 
+    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^n9adj *
+    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^n10adj * 
+    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^n11adj
+}
+
+cod_theoretical_constant_p <- cod_ps |> 
+  mutate(
+    theoretical_series_length = map_dbl(p, maximize_cod_series_p)
+  )
+
+cod_theoretical_constant_p <- cod_theoretical_constant_p |> 
+  slice_max(theoretical_series_length, n = 1) |> 
+  pull(p)
+cod_theoretical_constant_p
+
+m <- matrix(c(cod_streaks_res$series$n_actual, cod_streaks_res$series$n_expected), ncol = 2)
+dimnames(m) <- list(n_rounds = as.character(6:11), kind = c('actual', 'expected'))
+ch <- chisq.test(m)
+# ch$expected
+# chance_numbers <- tibble(
+#   league = rep(c('mlb', 'nba', 'nhl'), each = 4),
+#   i = rep(4:7, 3),
+#   a = c(
+#     c(0.1894, 0.215, 0.215, 0.3895),
+#     c(0.1324, 0.25, 0.3382, 0.2794),
+#     c(0.2532, 0.2405, 0.3038, 0.2025)
+#   ),
+#   e = rep(c(0.125, 0.25, 0.3125, 0.3125), 3)
+# )
+# chance_numbers |> filter(league == 'mlb') |> select(a, e) |> chisq.test()
+```
+
+## When do back-to-back round wins occur ([COD SnD]{.cod})?
 
@@
     .round = 11, 
-    .palette = 'deep-orange
-  ') +
+    .palette = 'deep-orange'
+  ) +
   b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
@@
 
-![](cod_b2b_round_win_prop.png){fig-align="center"}
+![](plots/cod_b2b_round_win_prop.png){fig-align="center"}
 
@@
 :::
+
+## Winning a next game given the series state
+
+```{r}
+
+```

### 2022-07-25 1-scrape-valorant.R

@@ -105,8 +105,12 @@ val_series_outcomes <- init_val_rounds_side |>
     min_cumu_wl = ifelse(cumu_w > cumu_l, cumu_l, cumu_w)
   )
 
-weird_val_series_outcomes <- val_series_outcomes |>
-  filter(max_cumu_wl > 13 & (min_cumu_wl < (max_cumu_wl - 2)))
+init_weird_val_series_outcomes <- bind_rows(
+  val_series_outcomes |>
+    filter(max_cumu_wl > 13 & (min_cumu_wl < (max_cumu_wl - 2))),
+  val_series_outcomes |> 
+    filter(max_cumu_wl < 13)
+)
 
 val_team_mapping <- bind_rows(
   init_val_rounds_side |> 
@@ -202,7 +206,21 @@ val_rounds_side <- init_val_rounds_side |>
     pre_cumu_l = lag(cumu_l, default = 0L)
   ) |> 
   ungroup()
-val_rounds_side
+
+more_weird_val_series_outcomes <- bind_rows(
+  val_rounds_side |> 
+    filter(win_series_1) |> 
+    group_by(series_id, team_1) |> 
+    slice_max(round, n = 1) |> 
+    ungroup() |> 
+    filter(cumu_w <= cumu_l),
+  val_rounds_side |> 
+    filter(!win_series_1) |> 
+    group_by(series_id, team_1) |> 
+    slice_max(round, n = 1) |> 
+    ungroup() |> 
+    filter(cumu_w >= cumu_l)
+)
 
 val_rounds <- bind_rows(
   val_rounds_side |> 
@@ -312,11 +330,30 @@ val_rounds <- bind_rows(
     opponent_series_w
   ) |> 
   anti_join(
-    weird_val_series_outcomes,
-    by = c('round', 'cumu_w', 'cumu_l')
+    init_weird_val_series_outcomes |> distinct(series_id = game_id),
+    by = 'series_id'
+  ) |> 
+  anti_join(
+    more_weird_val_series_outcomes |> distinct(series_id),
+    by = 'series_id'
   )
 qs::qsave(val_rounds, 'valorant_rounds.qs')
 
+# val_rounds |> 
+#   group_by(team, series_id) |> 
+#   slice_max(round, n = 1) |> 
+#   ungroup() |> 
+#   select(
+#     series_id,
+#     team,
+#     opponent,
+#     cumu_w,
+#     cumu_l,
+#     win_series
[…]

### 2022-07-25 research/nba-chi-squared.R
add research

@@ -1,0 +1,38 @@
+
+seasons <- 2022
+f_q <- quietly(nbastatR::game_logs)
+logs <- seasons %>% 
+  map_dfr(
+    ~f_q(.x, result_types = 'team', season_types = 'Playoffs', assign_to_environment = FALSE) %>% 
+      pluck('result')
+  ) %>% 
+  janitor::clean_names() 
+logs
+
+slim_logs <- logs %>% 
+  # filter(slug_team == slug_team_winner) %>%
+  select(
+    year = year_season,
+    date = date_game,
+    id_game,
+    tm_w = slug_team_winner,
+    tm_l = slug_team_loser,
+    slug_matchup,
+    is_win,
+    outcome_game
+  )
+slim_logs
+
+sked |> 
+  filter(series_type == 'playoff', series_title == 'Playoff Series') |> 
+  select(game_id, season, home = home_abbreviation, away = away_abbreviation, series_summary) |> 
+  mutate(
+    across(
+      series_summary,
+      list(
+        team = ~str_sub(.x, 1, 3),
+        line = ~str_sub(.x, -3, -1)
+      ),
+      .names = '{fn}'
+    )
+  )

### 2022-07-25 research/nba-chi-squared.R
clean sked

@@ -23,7 +23,10 @@ slim_logs <- logs %>%
   )
 slim_logs
 
-sked |> 
+sked <- hoopR::nba_schedule(2021) |> 
+  janitor::clean_names()
+
+clean_sked <- sked |> 
   filter(series_type == 'playoff', series_title == 'Playoff Series') |> 
   select(game_id, season, home = home_abbreviation, away = away_abbreviation, series_summary) |> 
   mutate(
@@ -36,3 +39,9 @@ sked |>
       .names = '{fn}'
     )
   )
+first_games <- clean_sked |> 
+  filter(line == '1-0' | line == '0-1')
+first_games
+
+cod_rounds |> 
+  group_by(cumu_w, cumu_l)

### 2022-07-30 presentation.qmd
update presentation with nhl, nba, mlb table and analysis

@@
 library(magick)
+library(broom)
+library(knitr)
 
@@
 -   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
--   4v4.
+-   4v4
 -   First to 6 round wins
@@
 
+ggsci_cyan <- extract_ggsci_mid_color('cyan')
+ggsci_brown <- extract_ggsci_mid_color('brown')
 cod_max_diff_win_series_prop <- max(abs(cod_o_win_prop$diff_win_series_prop))
@@
   scale_fill_gradient2(
-    low = extract_ggsci_mid_color('brown'),
-    high = extract_ggsci_mid_color('cyan'),
+    low = ggsci_brown,
+    high = ggsci_cyan,
     mid = 'white',
@@
 
-## What are the most common series winning states ([Valorant]{.valorant})?
-
-```{r}
-#| label: p_val_series_outcome_prop_over_expected
-val_streaks_res <- val_rounds |> summarize_streaks('val')
-
-p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
-  plot_series_outcome_prop_over_expected('val') +
-  common_val_labs()
-p_val_series_outcome_prop_over_expected
-save_plot_for_slide(p_val_series_outcome_prop_over_expected)
-```
-
-![](plots/val_series_outcome_prop_over_expected.png)
-
-```{r}
-#| label: altnerative-to-p=0.5-method-1
+## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
+
+::: fragment
+[Chance (2019)](https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422) finds that probability of winning a game that the title series in the MLB and NHL is **not** constant (at 50%)
+:::
+
+```{r}
+#| label: chance-2019
+chance_2019_leagues <- c('MLB World Series', 'NBA Finals', 'NHL Stanley Cup')
+
+n_sports <- tibble(
+  league = chance_2019_leagues,
+  ## i think nba has to be 2019 instead of 2018 in order for the product of `n * prop_actual` to be a whole number
+  n = c(2018 - 1923, 2019 - 1951, 2018 - 1939)
+)
+
+chance_sports <- tibble(
+  league = rep(chance_2019_leagues, each = 4),
+  games = rep(4:7, 3),
+  prop_actual = c(
+    c(0.1895, 0.2105, 0.2105, 0.3895),
+    c(0.1324, 0.25, 0.3382, 0.2794),
+    c(0.2532, 0.2278, 0.3165, 0.2025)
+  ),
+  prop_expected = rep(c(0.125, 0.25, 0.3125, 0.3125), 3)
+)
+
+sports <- chance_sports |> 
+  inner_join(
+    n_sports,
+    by = 'league'
+  ) |> 
+  mutate(
+    n_actual = round(n * prop_actual)
+  )
+
+generate_chi_label <- function(statistic, p.value) {
+  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
+}
+
+chi_sports <- sports |> 
+  nest(data = -c(league)) |> 
+  mutate(
+    chi = map(data, ~chisq.test(.x$n_actual, p = .x$prop_expected) |> broom::tidy())
+  ) |> 
+  select(league, chi) |> 
+  unnest(chi) |> 
+  transmute(
+    league, 
+    label = generate_chi_label(statistic, p.value)
+  )
+
+sports |> 
+  select(league, games, prop_expected, prop_actual) |> 
+  mutate(
+    across(
+      starts_with('prop_'),
+      scales::percent
+    ),
+    across(games, as.character)
+  ) |> 
+  pivot_wider(names_from = league, values_from = prop_actual) |> 
+  bind_rows(
+    bind_cols(
+      tibble(games = 'Avg. # of games'),
+      sports |> 
+        distinct(games, prop_expected) |>
+        summarize(prop_expected = as.character(round(sum(games * prop_expected), 2))),
+      sports |> 
+        group_by(league) |>
+        summarize(z = as.character(round(sum(games * prop_actual), 2))) |> 
+        pivot_wider(names_from = league, values_from = z)
+    )
+  ) |> 
+  bind_rows(
+    chi_sports |> 
+      pivot_wider(names_from = league, values_from = label) |> 
+      mutate(
+        games = '$\\xi^2$ (p-value)'
+      )
+  ) |> 
+  relocate(
+    `Series ends in i games` = games,
+    `Expected` = prop_expected
+  ) |> 
+  knitr::kable()
+```
+
+::: fragment
+|         Series length | Expected | MLB World Series | NBA Finals | NHL Stanley Cup |
+|----------------------:|---------:|-----------------:|-----------:|----------------:|
+|                     4 |   12.50% |           18.95% |     13.24% |          25.32% |
+|                     5 |   25.00% |           21.05% |     25.00% |          22.78% |
+|                     6 |   31.25% |           21.05% |     33.82% |          31.65% |
+|                     7 |   31.25% |           38.95% |     27.94% |          20.25% |
+|                       |          |                  |            |                 |
+|  **Avg. \# of games** |     5.81 |              5.8 |       5.76 |            5.47 |
+| $\xi^2$ **(p-value)** |          |       8.7 (0.03) | 0.4 (0.94) |  13.6 (\<=0.01) |
+:::
+
+```{r}
+#| label: cod_series_outcomes_chi
+
+cod_rounds_per_series <- cod_streaks_res$series |>
+  summarize(
+    actual = sum(n_rounds * prop_actual),
+    expected = sum(n_rounds * prop_expected)
+  )
+avg_actual_cod_rounds_per_series <- round(cod_rounds_per_series$actual, 2)
+avg_expected_cod_rounds_per_series <- round(cod_rounds_per_series$expected, 2)
+
+cod_series_outcomes_chi <- chisq.test(
+  cod_streaks_res$series$n_actual, 
+  p = cod_streaks_res$series$prop_expected
+) |> 
+  broom::tidy() |> 
+  mutate(label = generate_chi_label(statistic, p.value)) |> 
+  pull(label)
+cod_series_outcomes_chi
+```
+
+```{r}
+#| label: cod_series_outcomes_chi-eval
+#| eval: true
+avg_actual_cod_rounds_per_series <- 9.15
+avg_expected_cod_rounds_per_series <- 9.29
+cod_series_outcomes_chi <- '15.4 (<=0.01)'
+```
+
+<br/>
+
+::: fragment
+-   In COD, the average number of rounds (**`r avg_actual_cod_rounds_per_series`**) is less than the expected value (**`r avg_expected_cod_rounds_per_series`**)
+:::
+
+::: fragment
+-   A $\xi^2$ test for CoD demonstrates evidence against the constant probability null hypothesis for winning a given round in an SnD series (**`r cod_series_outcomes_chi`**)
+:::
+
+## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
+
+```{r}
+#| label: alternative-to-p=0.5-method-1
 ## p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
@@
 
-cod_theoretical_series_lengths <- cod_ps |> 
-  mutate(
-    theoretical_series_length = map_dbl(p, theoretical_cod_series_length)
-  )
-
-cod_rounds_per_series <- cod_streaks_res$series |> 
-  summarize(
-    actual = sum(n_rounds * prop_actual),
-    expected = sum(n_rounds * prop_expected)
-  )
-
-cod_theoretical_constant_p <- cod_theoretical_series_lengths |> 
-  mutate(
+cod_theoretical_series_lengths1 <- cod_ps |> 
+  mutate(
+    theoretical_series_length = map_dbl(p, theoretical_cod_series_length),
     diff = theoretical_series_length - cod_rounds_per_series$actual
-  ) |> 
+  )
+
+cod_theoretical_constant_p1 <- cod_theoretical_series_lengths1 |> 
   slice_min(abs(diff), n = 1) |> 
   pull(p)
-cod_theoretical_constant_p
-```
-
-```{r}
-#| label: altnerative-to-p=0.5-method-2
+
+pretty_cod_theoretical_constant_p1 <- cod_theoretical_constant_p1 |> 
+  scales::percent(accuracy = 0.01)
+```
+
+```{r}
+#| label: alternative-to-p=0.5-method-1-eval
+#| eval: true
+pretty_cod_theoretical_constant_p1 <- '57.25%'
+```
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-2
 pluck_cod_n <- function(.n_rounds) {
@@
 
-n6 <- pluck_cod_n(6)
-n7 <- pluck_cod_n(7)
-n8 <- pluck_cod_n(8)
-n9 <- pluck_cod_n(9)
-n10 <- pluck_cod_n(10)
-n11 <- pluck_cod_n(11)
-pm <- pmin(n6, n7, n8, n9, n10, n11)
-n6adj <- round(10 * n6 / pm)
-n7adj <- round(10 * n7 / pm)
-n8adj <- round(10 * n8 / pm)
-n9adj <- round(10 * n9 / pm)
-n10adj <- round(10 * n10 / pm)
-n11adj <- round(10 * n11 / pm)
+cod_n6 <- pluck_cod_n(6)
+cod_n7 <- pluck_cod_n(7)
+cod_n8 <- pluck_cod_n(8)
+cod_n9 <- pluck_cod_n(9)
+cod_n10 <- pluck_cod_n(10)
+cod_n11 <- pluck_cod_n(11)
+
+## This adjustment is something that is not done in the paper. I do it here to reduce
+##   the magnitude of the exponents.
+cod_pm <- pmin(cod_n6, cod_n7, cod_n8, cod_n9, cod_n10, cod_n11)
+cod_n6adj <- round(10 * cod_n6 / cod_pm)
+cod_n7adj <- round(10 * cod_n7 / cod_pm)
+cod_n8adj <- round(10 * cod_n8 / cod_)
+cod_n9adj <- round(10 * cod_n9 / cod_pm)
+cod_n10adj <- round(10 * cod_n10 / cod_pm)
+cod_n11adj <- round(10 * cod_n11 / cod_pm)
 
 maximize_cod_series_p <- function(p) {
-  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^n6adj *
-    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^n7adj * 
-    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^n8adj * 
-    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^n9adj *
-    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^n10adj * 
-    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^n11adj
-}
-
-cod_theoretical_constant_p <- cod_ps |> 
+  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^cod_n6adj *
+    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^cod_n7adj * 
+    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^cod_n8adj * 
+    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^cod_n9adj *
+    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^cod_n10adj * 
+    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^cod_n11adj
+}
+
+cod_theoretical_series_lengths2 <- cod_ps |> 
   mutate(
@@
 
-cod_theoretical_constant_p <- cod_theoretical_constant_p |> 
+cod_theoretical_constant_p2 <- cod_theoretical_series_lengths2 |> 
   slice_max(theoretical_series_length, n = 1) |> 
   pull(p)
-cod_theoretical_constant_p
-
-m <- matrix(c(cod_streaks_res$series$n_actual, cod_streaks_res$series$n_expected), ncol = 2)
-dimnames(m) <- list(n_rounds = as.character(6:11), kind = c('actual', 'expected'))
-ch <- chisq.test(m)
-# ch$expected
-# chance_numbers <- tibble(
-#   league = rep(c('mlb', 'nba', 'nhl'), each = 4),
-#   i = rep(4:7, 3),
-#   a = c(
-#     c(0.1894, 0.215, 0.215, 0.3895),
-#     c(0.1324, 0.25, 0.3382, 0.2794),
-#     c(0.2532, 0.2405, 0.3038, 0.2025)
-#   ),
-#   e = rep(c(0.125, 0.25, 0.3125, 0.3125), 3)
-# )
-# chance_numbers |> filter(league == 'mlb') |> select(a, e) |> chisq.test()
-```
+
+pretty_cod_theoretical_constant_p2 <- cod_theoretical_constant_p2 |> 
+  scales::percent(accuracy = 0.01)
+
+best_cod_theoretical_series_lengths2 <- cod_theoretical_series_lengths2 |> 
+  filter(p == cod_theoretical_constant_p2)
+
+p_cod_theoretical_series_lengths2 <- cod_theoretical_series_lengths2 |> 
+  ggplot() +
+  aes(x = p, y = theoretical_series_length) +
+  geom_line(
+    size = 2,
+    color = 'white'
+  ) +
+  geom_point(
+    data = best_cod_theoretical_series_lengths2,
+    color = ggsci_cyan,
+    size = 6
+  ) +
+  geom_text(
+    data = best_cod_theoretical_series_lengths2,
+    color = ggsci_cyan,
+    size = 13 / .pt,
+    hjust = 0,
+    aes(
+      x = p + 0.02,
+      label = sprintf('Maximum likilihood estimate (MLE) of\nconstant probability of better team winning (%s)', !!pretty_cod_theoretical_constant_p2)
+    )
+  ) +
+  scale_x_continuous(labels = scales::percent) +
+  labs(
+    x = 'Constant probability of better team winning',
+    y = 'Kernel of the multinomial likelihood'
+  ) +
+  theme(
+    axis.text.y = element_blank(),
+    panel.grid.major = element_blank()
+  )
+p_cod_theoretical_series_lengths2
+save_plot_for_slide(p_cod_theoretical_series_lengths2)
+```
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-2-eval
+#| eval: true
+pretty_cod_theoretical_constant_p2 <- '53.25%'
+```
+
+::: fragment
+[Mosteller (1952)](https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf) suggests several ways to find the optimal constant probability of the "stronger" team winning each game in a series.
+:::
+
+::: fragment
+-   Using the method of moments approach (Mosteller's method 1), `r pretty_cod_theoretical_constant_p1`
+:::
+
+::: fragment
+-   Using the maximum likelihood approach (Mosteller's method 2), `r pretty_cod_theoretical_constant_p2`
+
+![](plots/cod_theoretical_series_lengths2.png){fig-align="center" width="65%"}
+:::
+
+## What are the most common series winning states ([Valorant]{.valorant})?
+
+```{r}
+#| label: p_val_series_outcome_prop_over_expected
+val_streaks_res <- val_rounds |> summarize_streaks('val')
+
+p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
+  plot_series_outcome_prop_over_expected('val') +
+  common_val_labs()
+p_val_series_outcome_prop_over_expected
+save_plot_for_slide(p_val_series_outcome_prop_over_expected)
+```
+
+![](plots/val_series_outcome_prop_over_expected.png)
 

### 2022-07-30 research/replicate-streaks.R
regen npk plot

@@ -27,7 +27,7 @@ simulate_post_streak_prob <- function(sims = 1000, ...) {
 
 runs <- crossing(
   n = 1:100,
-  k = 1:5,
+  k = 1:4,
   p = c(0.25, 0.5, 0.75)
 ) |> 
   mutate(
@@ -35,6 +35,8 @@ runs <- crossing(
   )
 
 p_streaks <- runs |>
+  filter(k != 5) |> 
+  filter(!is.nan(next_p)) |> 
   arrange(n, k) |>
   mutate(
     across(k, factor),
@@ -44,7 +46,11 @@ p_streaks <- runs |>
   theme_minimal() +
   aes(x = n, y = next_p, color = k, group = group) +
   geom_step() +
+  # eom_smooth(method = 'gam', formula = y ~ s(x, bs = 'cs'), se = FALSE) +
+  # geom_smooth(method = 'lm', formula = y ~ poly(x, 2)) +
+  # geom_smooth(method = 'loess', formula = y ~ x, se = FALSE) +
   # facet_wrap(~p, scales = 'free_y') +
-  geom_hline(aes( yintercept = p))
+  geom_hline(aes( yintercept = p)) +
+  labs(x = NULL, y = NULL)
 p_streaks
-ggsave(p_streaks, filename = 'research/streaks.png', width = 12, height = 6)
+ggsave(p_streaks, filename = 'research/npk_replicated.png', width = 12, height = 9)

### 2022-07-31 presentation.qmd
typos, re-organize

@@
 ---
-title: "They're on Fire: Team Momentum in Round-Based First Person Shooter Esports"
+title: "They're Clutching up! Team Momentum in Round-Based Esports"
 author: 'Tony ElHabr'
@@
 -   One team plays offense in 12 consecutive rounds before swapping sides
--   Must win by 2 cod_rounds
+-   Must win by 2 rounds
 :::
@@
 ::: fragment
-Often the defensive team will try to eliminate all o team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
 :::
@@
 ```{r}
-#| label: cod_heatmap_prep
-cod_round_and_series_win_prop_by_side <- cod_rounds |> 
-  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
-  summarize(
-    n = n(),
-    across(c(win_round, win_series), sum)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    win_round_prop = win_round / n,
-    win_series_prop = win_series / n
-  )
-
-cod_o_win_prop <- cod_round_and_series_win_prop_by_side |> 
-  filter(is_offense) |> 
-  mutate(
-    diff_win_round_prop = win_round_prop - !!cod_o_win_prop_const
-  )
-
-cod_e_o_win_series_prop <- crossing(
-  pre_cumu_w = 0:5,
-  pre_cumu_l = 0:5
-) |> 
-  mutate(
-    n_remain_max = 11 - (pre_cumu_w + pre_cumu_l),
-    n_remain_w = 6 - pre_cumu_w,
-    ## can i account for offense in this by rotating?
-    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
-  )
-
-cod_o_win_prop <- cod_o_win_prop |> 
-  inner_join(
-    cod_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
-    by = c('pre_cumu_w', 'pre_cumu_l')
-  ) |> 
-  mutate(
-    diff_win_series_prop = win_series_prop - e_win_series_prop
-  )
+#| label: cod-funcs
 
@@
 
-cod_heatmap_seq_labeller <- function(.df, .label, .num) {
-  sprintf(
-    '%s\n(%s/%s)',
-    scales::percent(.df[[.label]], accuracy = 1),
-    scales::comma(.df[[.num]]),
-    scales::comma(.df$n)
-  )
-}
-
-heatmap_text_layer <- function(..., .op, .df, .label, .num, .color, .threshold, .labeller) {
+heatmap_text_layer <- function(..., .op, .df, .label, .num, .color, .threshold, .labeller, .size = 11 / .pt) {
   .df_filt <- .df |> filter(`.op`(.df[[.label]], .threshold))
@@
       color = .color,
-      size = 11 / .pt,
+      size = .size,
       fontface = 'bold',
@@
 }
-```
-
-```{r}
-#| label: p_cod_o_round_win_prop
+
+cod_heatmap_seq_labeller <- function(.df, .label, .num) {
+  sprintf(
+    '%s\n(%s)',
+    scales::percent(.df[[.label]], accuracy = 1), 
+    scales::comma(.df$n)
+  )
+}
+
 o_round_win_text_layer <- function(
@@
       .threshold = .threshold,
-      .labeller = .labeller
-    )
-  )
-}
-
-p_cod_o_round_win_prop <- cod_o_win_prop |> 
-  ggplot() +
-  common_cod_heatmap_layers() +
-  heatmap_tile(.fill = 'win_round_prop') +
-  heatmap_text_layers(
-    .df = cod_o_win_prop,
-    .f = o_round_win_text_layer,
-    .threshold = 0.52,
-    .labeller = cod_heatmap_seq_labeller
-  ) +
-  ggsci::scale_fill_material('teal') +
-  labs(
-    title = 'Offensive Round Win %'
-  )
-p_cod_o_round_win_prop
-save_plot_for_slide(p_cod_o_round_win_prop)
-```
-
-![](plots/cod_o_round_win_prop.png){fig-align="center"}
-
-## What are your chances of winning the next round ([COD SnD]{.cod})?
-
-```{r}
-#| label: p_cod_o_round_win_prop_over_expected
+      .labeller = .labeller,
+      .size = 11 / .pt
+    )
+  )
+}
+
 cod_heatmap_div_labeller <- function(.df, .label, .num) {
@@
 
+ggsci_purple <- extract_ggsci_mid_color('purple')
+ggsci_green <- extract_ggsci_mid_color('green')
+ggsci_cyan <- extract_ggsci_mid_color('cyan')
+ggsci_brown <- extract_ggsci_mid_color('brown')
+```
+
+```{r}
+#| label: cod_rounds-calcs
+cod_round_and_series_win_prop_by_side <- cod_rounds |> 
+  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
+  summarize(
+    n = n(),
+    across(c(win_round, win_series), sum)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_round_prop = win_round / n,
+    win_series_prop = win_series / n
+  )
+
+cod_e_o_win_series_prop <- crossing(
+  pre_cumu_w = 0:5,
+  pre_cumu_l = 0:5
+) |> 
+  mutate(
+    n_remain_max = 11 - (pre_cumu_w + pre_cumu_l),
+    n_remain_w = 6 - pre_cumu_w,
+    ## can i account for offense in this by rotating?
+    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
+  )
+
+cod_o_win_prop <- cod_round_and_series_win_prop_by_side |> 
+  filter(is_offense) |> 
+  mutate(
+    diff_win_round_prop = win_round_prop - !!cod_o_win_prop_const
+  ) |> 
+  inner_join(
+    cod_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
+    by = c('pre_cumu_w', 'pre_cumu_l')
+  ) |> 
+  mutate(
+    diff_win_series_prop = win_series_prop - e_win_series_prop
+  )
+```
+
+```{r}
+#| label: p_cod_o_round_win_prop
+p_cod_o_round_win_prop <- cod_o_win_prop |> 
+  ggplot() +
+  common_cod_heatmap_layers() +
+  heatmap_tile(.fill = 'win_round_prop') +
+  heatmap_text_layers(
+    .df = cod_o_win_prop,
+    .f = o_round_win_text_layer,
+    .threshold = 0.52,
+    .labeller = cod_heatmap_seq_labeller
+  ) +
+  ggsci::scale_fill_material('teal') +
+  labs(
+    title = 'Offensive Round Win %'
+  )
+p_cod_o_round_win_prop
+save_plot_for_slide(p_cod_o_round_win_prop)
+```
+
+![](plots/cod_o_round_win_prop.png){fig-align="center"}
+
+## What are your chances of winning the next round ([COD SnD]{.cod})?
+
+```{r}
+#| label: p_cod_o_round_win_prop_over_expected
 cod_max_diff_win_round_prop <- max(abs(cod_o_win_prop$diff_win_round_prop))
@@
   scale_fill_gradient2(
-    low = extract_ggsci_mid_color('purple'),
-    high = extract_ggsci_mid_color('green'),
+    low = ggsci_purple,
+    high = ggsci_green,
     mid = 'white',
@@
 ```{r}
-val_round_and_series_win_prop_by_side <- val_rounds |> 
-  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
-  summarize(
-    n = n(),
-    across(c(win_round, win_series), sum)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    win_round_prop = win_round / n,
-    win_series_prop = win_series / n
-  )
-
-val_o_win_prop <- val_round_and_series_win_prop_by_side |> 
-  filter(is_offense) |> 
-  mutate(
-    diff_win_round_prop = win_round_prop - !!val_o_win_prop_const
-  )
-
+#| label: val-funcs
 drop_25th_round <- function(df) {
@@
 
-val_o_win_prop <- val_o_win_prop |> 
-  inner_join(
-    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
-    by = c('pre_cumu_w', 'pre_cumu_l')
-  ) |> 
-  mutate(
-    diff_win_series_prop = win_series_prop - e_win_series_prop
-  ) |> 
-  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
-  drop_25th_round()
-
-# Joshua Broas, vlr.gg
+## Joshua Broas, vlr.gg
 common_val_labs <- function(...) {
@@
   sprintf(
-    '%s', 
-    scales::percent(.df[[.label]], accuracy = 1)
-  )
-}
-
-val_pre_swap_rounds <- val_o_win_prop |> 
-  mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
-  filter(pre_cumu_wl == 12)
-
-val_pre_swap_round_segments <- val_pre_swap_rounds |> 
-  transmute(
-    pre_cumu_w,
-    across(pre_cumu_l, ~.x + 1),
-    i = row_number(),
-    n = 2
-  ) |> 
-  uncount(n) |> 
-  group_by(i) |> 
-  mutate(rn = row_number()) |> 
-  ungroup() |> 
-  mutate(
-    across(pre_cumu_w, ~ifelse(rn == 2, .x + 1, .x))
-  ) |> 
-  add_row(
-    pre_cumu_w = 13,
-    pre_cumu_l = 0
-  )
-
-val_swap_path <- function(...) {
-  list(
-    ...,
-    geom_path(
-      data = val_pre_swap_round_segments,
-      color = 'white',
-      size = 1.5,
-      aes(
-        x = pre_cumu_w, 
-        y = pre_cumu_l
-      )
-    )
-  )
-}
-
-p_val_o_round_win_prop <- val_o_win_prop |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(.fill = 'win_round_prop') +
-  val_swap_path() +
-  heatmap_text_layers(
-    .df = val_o_win_prop, 
-    .f = o_round_win_text_layer,
-    .threshold = 0.8,
-    .labeller = val_heatmap_seq_labeller
-  ) +
-  ggsci::scale_fill_material('teal') +
-  labs(
-    title = 'Offensive Round Win %'
-  )
-p_val_o_round_win_prop
-save_plot_for_slide(p_val_o_round_win_prop)
-```
-
-![](plots/val_o_round_win_prop.png){fig-align="center"}
-
-## What are your chances of winning the series ([COD SnD]{.cod})?
-
-```{r}
-#| label: p_cod_o_series_win_prop
+    '%s\n(%s)', 
+    scales::percent(.df[[.label]], accuracy = 1), 
+    scales::comma(.df$n)
+  )
+}
+
 o_series_win_text_layer <- function(
@@
       .threshold = .threshold,
-      .labeller = .labeller
-    )
-  )
-}
-
-p_cod_o_series_win_prop <- cod_o_win_prop |> 
-  ggplot() +
-  common_cod_heatmap_layers() +
-  heatmap_tile(.fill = 'win_series_prop') +
-  heatmap_text_layers(
-    .df = cod_o_win_prop, 
-    .f = o_series_win_text_layer,
-    .threshold = 0.8,
-    .labeller = cod_heatmap_seq_labeller
-  ) +
-  ggsci::scale_fill_material('orange') +
-  labs(
-    title = 'Offensive Series Win %'
-  )
-p_cod_o_series_win_prop
-save_plot_for_slide(p_cod_o_series_win_prop)
-```
-
-![](plots/cod_o_series_win_prop.png){fig-align="center"}
-
-## What are your chances of winning the series ([COD SnD]{.cod})?
-
-```{r}
-#| label: p_cod_o_series_win_prop_over_expected
+      .labeller = .labeller,
+      .size = 9 / .pt
+    )
+  )
+}
+
+val_heatmap_div_labeller <- function(.df, .label, .num) {
+  sprintf(
+    '%+.1f\n(%s)', 
+    100 * .df[[.label]], 
+    scales::comma(.df$n)
+  )
+}
+
 o_series_win_over_expected_text_layer <- function(
@@
       .threshold = .threshold,
-      .labeller = .labeller
-    )
-  )
-}
-
-ggsci_cyan <- extract_ggsci_mid_color('cyan')
-ggsci_brown <- extract_ggsci_mid_color('brown')
+      .labeller = .labeller,
+      .size = 9 / .pt
+    )
+  )
+}
+```
+
+```{r}
+#| label: val_rounds-calcs
+val_round_and_series_win_prop_by_side <- val_rounds |> 
+  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
+  summarize(
+    n = n(),
+    across(c(win_round, win_series), sum)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_round_prop = win_round / n,
+    win_series_prop = win_series / n
+  )
+
+val_o_win_prop <- val_round_and_series_win_prop_by_side |> 
+  filter(is_offense) |> 
+  mutate(
+    diff_win_round_prop = win_round_prop - !!val_o_win_prop_const
+  ) |> 
+  inner_join(
+    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
+    by = c('pre_cumu_w', 'pre_cumu_l')
+  ) |> 
+  mutate(
+    diff_win_series_prop = win_series_prop - e_win_series_prop
+  ) |> 
+  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
+  drop_25th_round()
+```
+
+```{r}
+#| label: val_rounds_bothbuy-calcs
+val_bothbuy_rounds <- val_rounds |> 
+  filter(
+    team_buy_type %in% c('semi-buy', 'full-buy'), 
+    opponent_buy_type  %in% c('semi-buy', 'full-buy')
+  )
+
+val_bothbuy_o_win_prop_const <- val_bothbuy_rounds |> 
+  filter(is_offense) |> 
+  count(win_round) |> 
+  mutate(prop = n / sum(n)) |> 
+  filter(win_round) |> 
+  pull(prop)
+
+val_round_and_series_win_prop_by_side_bothbuy <- val_bothbuy_rounds |> 
+  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
+  summarize(
+    n = n(),
+    across(c(win_round, win_series), sum)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_round_prop = win_round / n,
+    win_series_prop = win_series / n
+  )
+
+val_o_win_prop_bothbuy <- val_round_and_series_win_prop_by_side_bothbuy |> 
+  filter(is_offense) |> 
+  mutate(
+    diff_win_round_prop = win_round_prop - !!val_bothbuy_o_win_prop_const
+  ) |> 
+  inner_join(
+    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
+    by = c('pre_cumu_w', 'pre_cumu_l')
+  ) |> 
+  mutate(
+    diff_win_series_prop = win_series_prop - e_win_series_prop
+  ) |> 
+  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
+  drop_25th_round()
+```
+
+```{r}
+#| label: val-funcs-2
+val_pre_swap_rounds <- val_o_win_prop |> 
+  mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
+  filter(pre_cumu_wl == 12)
+
+val_pre_swap_round_segments <- val_pre_swap_rounds |> 
+  transmute(
+    pre_cumu_w,
+    across(pre_cumu_l, ~.x),
+    i = row_number(),
+    n = 2
+  ) |> 
+  uncount(n) |> 
+  group_by(i) |> 
+  mutate(rn = row_number()) |> 
+  ungroup() |> 
+  mutate(
+    across(pre_cumu_w, ~ifelse(rn == 2, .x + 1, .x))
+  ) |> 
+  add_row(
+    pre_cumu_w = 12,
+    pre_cumu_l = 0
+  )
+
+val_swap_path <- function(...) {
+  list(
+    ...,
+    geom_path(
+      data = val_pre_swap_round_segments,
+      color = 'white',
+      size = 1.5,
+      aes(
+        x = pre_cumu_w, 
+        y = pre_cumu_l
+      )
+    )
+  )
+}
+```
+
+```{r}
+#| label: p_val_o_round_win_prop
+p_val_o_round_win_prop <- val_o_win_prop |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(.fill = 'win_round_prop') +
+  val_swap_path() +
+  heatmap_text_layers(
+    .df = val_o_win_prop, 
+    .f = o_round_win_text_layer,
+    .threshold = 0.8,
+    .labeller = val_heatmap_seq_labeller
+  ) +
+  ggsci::scale_fill_material('teal') +
+  labs(
+    title = 'Offensive Round Win %'
+  )
+p_val_o_round_win_prop
+save_plot_for_slide(p_val_o_round_win_prop)
+
+p_val_o_round_win_prop_bothbuy <- val_o_win_prop_bothbuy |> 
+  ggplot() +
+  common_val_heatmap_layers() +
+  heatmap_tile(.fill = 'win_round_prop') +
+  val_swap_path() +
+  heatmap_text_layers(
+    .df = val_o_win_prop_bothbuy, 
+    .f = o_round_win_text_layer,
+    .threshold = 0.8,
+    .labeller = val_heatmap_seq_labeller
+  ) +
+  ggsci::scale_fill_material('teal') +
+  labs(
+    title = 'Offensive Round Win %'
+  )
+p_val_o_round_win_prop_bothbuy
+save_plot_for_slide(p_val_o_round_win_prop_bothbuy)
+```
+
+![](plots/val_o_round_win_prop.png){fig-align="center"}
+
+## What are your chances of winning the series ([COD SnD]{.cod})?
+
+```{r}
+#| label: p_cod_o_series_win_prop
+p_cod_o_series_win_prop <- cod_o_win_prop |> 
+  ggplot() +
+  common_cod_heatmap_layers() +
+  heatmap_tile(.fill = 'win_series_prop') +
+  heatmap_text_layers(
+    .df = cod_o_win_prop, 
+    .f = o_series_win_text_layer,
+    .threshold = 0.8,
+    .labeller = cod_heatmap_seq_labeller
+  ) +
+  ggsci::scale_fill_material('orange') +
+  labs(
+    title = 'Offensive Series Win %'
+  )
+p_cod_o_series_win_prop
+save_plot_for_slide(p_cod_o_series_win_prop)
+```
+
+![](plots/cod_o_series_win_prop.png){fig-align="center"}
+
+## What are your chances of winning the series ([COD SnD]{.cod})?
+
+```{r}
+#| label: p_cod_o_series_win_prop_over_expected
 cod_max_diff_win_series_prop <- max(abs(cod_o_win_prop$diff_win_series_prop))
@@
 #| label: p_val_o_series_win_prop_over_expected
-val_heatmap_div_labeller <- function(.df, .label, .num) {
-  sprintf(
-    '%+.1f', 
-    100 * .df[[.label]]
-  )
-}
-
 val_max_diff_win_series_prop <- max(abs(val_o_win_prop$diff_win_series_prop))
@@
   ) +
-  # geom_abline(
-  #   color = 'white',
-  #   linetype = 2,
-  #   aes(
-  #     slope = 1,
-  #     intercept = 0
-  #   )
-  # ) +
   heatmap_text_layers(
@@
 p_filt_val_o_series_win_prop_over_expected
-save_plot_for_slide(p_val_o_series_win_prop_over_expected)
-```
+save_plot_for_slide(p_filt_val_o_series_win_prop_over_expected)
+```
+
+![](plots/filt_val_o_series_win_prop_over_expected.png){fig-align="center"}
 
@@
 ::: fragment
-[Chance (2019)](https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422) finds that probability of winning a game that the title series in the MLB and NHL is **not** constant (at 50%)
+[Chance (2019)](https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422) finds that the probability of winning a game in the title series in the MLB and NHL is **not** constant (at 50%)
 :::
@@
 ```
-
-<br/>
 
@@
     x = 'Round',
-    y = '# of cod_rounds in Complete Series'
+    y = '# of rounds played in series'
   ) + 

### 2022-07-31 presentation.qmd
move round 1 win pct
formalize the momentum analysis

@@
 
+## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
+
+::: fragment
+[Chance (2019)](https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422) finds that the probability of winning a game in the title series in the MLB and NHL is **not** constant (at 50%)
+:::
+
+```{r}
+#| label: chance-2019
+chance_2019_leagues <- c('MLB World Series', 'NBA Finals', 'NHL Stanley Cup')
+
+n_sports <- tibble(
+  league = chance_2019_leagues,
+  ## i think nba has to be 2019 instead of 2018 in order for the product of `n * prop_actual` to be a whole number
+  n = c(2018 - 1923, 2019 - 1951, 2018 - 1939)
+)
+
+chance_sports <- tibble(
+  league = rep(chance_2019_leagues, each = 4),
+  games = rep(4:7, 3),
+  prop_actual = c(
+    c(0.1895, 0.2105, 0.2105, 0.3895),
+    c(0.1324, 0.25, 0.3382, 0.2794),
+    c(0.2532, 0.2278, 0.3165, 0.2025)
+  ),
+  prop_expected = rep(c(0.125, 0.25, 0.3125, 0.3125), 3)
+)
+
+sports <- chance_sports |> 
+  inner_join(
+    n_sports,
+    by = 'league'
+  ) |> 
+  mutate(
+    n_actual = round(n * prop_actual)
+  )
+
+generate_chi_label <- function(statistic, p.value) {
+  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
+}
+
+chi_sports <- sports |> 
+  nest(data = -c(league)) |> 
+  mutate(
+    chi = map(data, ~chisq.test(.x$n_actual, p = .x$prop_expected) |> broom::tidy())
+  ) |> 
+  select(league, chi) |> 
+  unnest(chi) |> 
+  transmute(
+    league, 
+    label = generate_chi_label(statistic, p.value)
+  )
+
+sports |> 
+  select(league, games, prop_expected, prop_actual) |> 
+  mutate(
+    across(
+      starts_with('prop_'),
+      scales::percent
+    ),
+    across(games, as.character)
+  ) |> 
+  pivot_wider(names_from = league, values_from = prop_actual) |> 
+  bind_rows(
+    bind_cols(
+      tibble(games = 'Avg. # of games'),
+      sports |> 
+        distinct(games, prop_expected) |>
+        summarize(prop_expected = as.character(round(sum(games * prop_expected), 2))),
+      sports |> 
+        group_by(league) |>
+        summarize(z = as.character(round(sum(games * prop_actual), 2))) |> 
+        pivot_wider(names_from = league, values_from = z)
+    )
+  ) |> 
+  bind_rows(
+    chi_sports |> 
+      pivot_wider(names_from = league, values_from = label) |> 
+      mutate(
+        games = '$\\xi^2$ (p-value)'
+      )
+  ) |> 
+  relocate(
+    `Series ends in i games` = games,
+    `Expected` = prop_expected
+  ) |> 
+  knitr::kable()
+```
+
+::: fragment
+|         Series length | Expected | MLB World Series | NBA Finals | NHL Stanley Cup |
+|----------------------:|---------:|-----------------:|-----------:|----------------:|
+|                     4 |   12.50% |           18.95% |     13.24% |          25.32% |
+|                     5 |   25.00% |           21.05% |     25.00% |          22.78% |
+|                     6 |   31.25% |           21.05% |     33.82% |          31.65% |
+|                     7 |   31.25% |           38.95% |     27.94% |          20.25% |
+|                       |          |                  |            |                 |
+|  **Avg. \# of games** |     5.81 |              5.8 |       5.76 |            5.47 |
+| $\xi^2$ **(p-value)** |          |       8.7 (0.03) | 0.4 (0.94) |  13.6 (\<=0.01) |
+:::
+
+```{r}
+#| label: cod_series_outcomes_chi
+
+cod_rounds_per_series <- cod_streaks_res$series |>
+  summarize(
+    actual = sum(n_rounds * prop_actual),
+    expected = sum(n_rounds * prop_expected)
+  )
+avg_actual_cod_rounds_per_series <- round(cod_rounds_per_series$actual, 2)
+avg_expected_cod_rounds_per_series <- round(cod_rounds_per_series$expected, 2)
+
+cod_series_outcomes_chi <- chisq.test(
+  cod_streaks_res$series$n_actual, 
+  p = cod_streaks_res$series$prop_expected
+) |> 
+  broom::tidy() |> 
+  mutate(label = generate_chi_label(statistic, p.value)) |> 
+  pull(label)
+cod_series_outcomes_chi
+```
+
+```{r}
+#| label: cod_series_outcomes_chi-eval
+#| eval: true
+avg_actual_cod_rounds_per_series <- 9.15
+avg_expected_cod_rounds_per_series <- 9.29
+cod_series_outcomes_chi <- '15.4 (<=0.01)'
+```
+
+::: fragment
+-   In COD, the average number of rounds (**`r avg_actual_cod_rounds_per_series`**) is less than the expected value (**`r avg_expected_cod_rounds_per_series`**)
+:::
+
+::: fragment
+-   A $\xi^2$ test for CoD demonstrates evidence against the constant probability null hypothesis for winning a given round in an SnD series (**`r cod_series_outcomes_chi`**)
+:::
+
+## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
+
+```{r}
+#| label: alternative-to-p=0.5-method-1
+## p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
+theoretical_cod_series_length <- function(p) {
+  6 * prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11) +
+    7 * prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11) + 
+    8 * prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11) + 
+    9 * prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11) +
+    10 * prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11) +
+    11 * prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)
+}
+
+cod_ps <- tibble(p = seq(0.5, 0.7, by = 0.0025))
+
+cod_theoretical_series_lengths1 <- cod_ps |> 
+  mutate(
+    theoretical_series_length = map_dbl(p, theoretical_cod_series_length),
+    diff = theoretical_series_length - cod_rounds_per_series$actual
+  )
+
+cod_theoretical_constant_p1 <- cod_theoretical_series_lengths1 |> 
+  slice_min(abs(diff), n = 1) |> 
+  pull(p)
+
+pretty_cod_theoretical_constant_p1 <- cod_theoretical_constant_p1 |> 
+  scales::percent(accuracy = 0.01)
+```
+
+```{r}
+#| label: alternative-to-p=0.5-method-1-eval
+#| eval: true
+pretty_cod_theoretical_constant_p1 <- '57.25%'
+```
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-2
+pluck_cod_n <- function(.n_rounds) {
+  cod_streaks_res$series |>
+    filter(n_rounds == .n_rounds) |> 
+    pull(n_actual)
+}
+
+cod_n6 <- pluck_cod_n(6)
+cod_n7 <- pluck_cod_n(7)
+cod_n8 <- pluck_cod_n(8)
+cod_n9 <- pluck_cod_n(9)
+cod_n10 <- pluck_cod_n(10)
+cod_n11 <- pluck_cod_n(11)
+
+## This adjustment is something that is not done in the paper. I do it here to reduce
+##   the magnitude of the exponents.
+cod_pm <- pmin(cod_n6, cod_n7, cod_n8, cod_n9, cod_n10, cod_n11)
+cod_n6adj <- round(10 * cod_n6 / cod_pm)
+cod_n7adj <- round(10 * cod_n7 / cod_pm)
+cod_n8adj <- round(10 * cod_n8 / cod_)
+cod_n9adj <- round(10 * cod_n9 / cod_pm)
+cod_n10adj <- round(10 * cod_n10 / cod_pm)
+cod_n11adj <- round(10 * cod_n11 / cod_pm)
+
+maximize_cod_series_p <- function(p) {
+  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^cod_n6adj *
+    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^cod_n7adj * 
+    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^cod_n8adj * 
+    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^cod_n9adj *
+    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^cod_n10adj * 
+    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^cod_n11adj
+}
+
+cod_theoretical_series_lengths2 <- cod_ps |> 
+  mutate(
+    theoretical_series_length = map_dbl(p, maximize_cod_series_p)
+  )
+
+cod_theoretical_constant_p2 <- cod_theoretical_series_lengths2 |> 
+  slice_max(theoretical_series_length, n = 1) |> 
+  pull(p)
+
+pretty_cod_theoretical_constant_p2 <- cod_theoretical_constant_p2 |> 
+  scales::percent(accuracy = 0.01)
+
+best_cod_theoretical_series_lengths2 <- cod_theoretical_series_lengths2 |> 
+  filter(p == cod_theoretical_constant_p2)
+
+p_cod_theoretical_series_lengths2 <- cod_theoretical_series_lengths2 |> 
+  ggplot() +
+  aes(x = p, y = theoretical_series_length) +
+  geom_line(
+    size = 2,
+    color = 'white'
+  ) +
+  geom_point(
+    data = best_cod_theoretical_series_lengths2,
+    color = ggsci_cyan,
+    size = 6
+  ) +
+  geom_text(
+    data = best_cod_theoretical_series_lengths2,
+    color = ggsci_cyan,
+    size = 13 / .pt,
+    hjust = 0,
+    aes(
+      x = p + 0.02,
+      label = sprintf('Maximum likilihood estimate (MLE) of\nconstant probability of better team winning (%s)', !!pretty_cod_theoretical_constant_p2)
+    )
+  ) +
+  scale_x_continuous(labels = scales::percent) +
+  labs(
+    x = 'Constant probability of better team winning',
+    y = 'Kernel of the multinomial likelihood'
+  ) +
+  theme(
+    axis.text.y = element_blank(),
+    panel.grid.major = element_blank()
+  )
+p_cod_theoretical_series_lengths2
+save_plot_for_slide(p_cod_theoretical_series_lengths2)
+```
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-2-eval
+#| eval: true
+pretty_cod_theoretical_constant_p2 <- '53.25%'
+```
+
+::: fragment
+[Mosteller (1952)](https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf) suggests several ways to find the optimal constant probability of the "stronger" team winning each game in a series.
+:::
+
+::: fragment
+-   Using the method of moments approach (Mosteller's method 1), `r pretty_cod_theoretical_constant_p1`
+:::
+
+::: fragment
+-   Using the maximum likelihood approach (Mosteller's method 2), `r pretty_cod_theoretical_constant_p2`
+
+![](plots/cod_theoretical_series_lengths2.png){fig-align="center" width="65%"}
+:::
+
+## What are the most common series winning states ([Valorant]{.valorant})?
+
+```{r}
+#| label: p_val_series_outcome_prop_over_expected
+val_streaks_res <- val_rounds |> summarize_streaks('val')
+
+p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
+  plot_series_outcome_prop_over_expected('val') +
+  common_val_labs()
+p_val_series_outcome_prop_over_expected
+save_plot_for_slide(p_val_series_outcome_prop_over_expected)
+```
+
+![](plots/val_series_outcome_prop_over_expected.png)
+
+## When do back-to-back round wins occur ([COD SnD]{.cod})?
+
+```{r}
+#| label: p_cod_b2b_round_win_prop
+summarize_cod_b2b_round_wins <- function(df, ...) {
+  df |> 
+    arrange(year, sheet, series, team, round) |> 
+    group_by(year, sheet, series, team) |> 
+    mutate(
+      b2b_round_wins = win_round & lag(win_round)
+    ) |> 
+    ungroup() |> 
+    filter(round > 1L) |> 
+    count(..., round, b2b_round_wins) |> 
+    group_by(..., round) |> 
+    mutate(total = sum(n), prop = n / total) |> 
+    ungroup() |> 
+    filter(b2b_round_wins) |> 
+    select(-b2b_round_wins)
+}
+
+## now accounting for number of cod_rounds that end up being played...
+## seems like there is interesting behavior in the last round, regardless `n_rounds`
+cod_b2b_round_win_prop <- cod_rounds |> 
+  filter(n_rounds > 6L) |> 
+  summarize_cod_b2b_round_wins(n_rounds) |> 
+  group_by(n_rounds) |> 
+  mutate(
+    z = (n - mean(n)) / sd(n),
+    rnk = row_number(desc(n))
+  ) |> 
+  ungroup()
+
+b2b_round_win_prop_tile_layer <- function(..., .df, .round, .palette, .is_new = TRUE) {
+
+  init <- if(!.is_new) {
+    list()
+  } else {
+    ggnewscale::new_scale_fill()
+  }
+
+  list(
+    ...,
+    init,
+    geom_tile(
+      data = .df |> filter(n_rounds == .round),
+      color = blackish_background,
+      height = 0.8,
+      show.legend = FALSE,
+      aes(
+        fill = z,
+        x = round + 0.5, 
+        y = n_rounds + 0.5
+      )
+    ),
+    ggsci::scale_fill_material(palette = .palette) 
+  )
+}
+
+b2b_round_win_prop_text_layer <- function(..., .df, .emphasize) {
+  if(.emphasize == 'low') {
+    op <- `>`
+    .color <- blackish_background
+  } else {
+    op <- `==`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    geom_text(
+      data = .df |> filter(`op`(rnk, 1)),
+      color = .color,
+      size = 11 / .pt,
+      fontface = 'bold',
+      aes(
+        label = sprintf('%s\n(%s)', scales::percent(prop, accuracy = 1), scales::comma(n)),
+        x = round + 0.5, 
+        y = n_rounds + 0.5
+      )
+    )
+  )
+}
+
+b2b_round_win_prop_text_layers <- function(..., .df) {
+  list(
+    ...,
+    b2b_round_win_prop_text_layer(.df = .df, .emphasize = 'low'),
+    b2b_round_win_prop_text_layer(.df = .df, .emphasize = 'high')
+  )
+}
+
+cod_b2b_round_win_prop_arws <- tibble(
+  x = c(9.3, 9.4, 9.75, 10),
+  y = c(8.25, 8.5, 8.75, 8.75),
+  xend = c(8.1, 9.1, 9.5, 10.5),
+  yend = c(7.5, 8.5, 9, 10),
+  curvature = c(-0.2, -0.1, 0.1, 0.2)
+) |> 
+  mutate(
+    rn = row_number()
+  )
+
+p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
+  ggplot() +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 7, 
+    .palette = 'pink', 
+    .is_new = FALSE
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 8, 
+    .palette = 'light-blue'
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 9, 
+    .palette = 'light-green'
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 10, 
+    .palette = 'amber'
+  ) +
+  b2b_round_win_prop_tile_layer(
+    .df = cod_b2b_round_win_prop, 
+    .round = 11, 
+    .palette = 'deep-orange'
+  ) +
+  b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
+  scale_x_continuous(
+    labels = 2:11,
+    breaks = seq(2.5, 11.5, by = 1),
+    expand = c(0, 0.5)
+  ) +
+  scale_y_continuous(
+    labels = 7:11,
+    breaks = seq(7.5, 11.5, by = 1),
+    expand = c(0, 0)
+  ) +
+  theme(
+    panel.grid.major = element_blank(),
+    axis.title = element_text(hjust = 0.5),
+    plot.title = ggtext::element_markdown(hjust = 0.5),
+    axis.text = element_text(size = 16, face = 'bold')
+  ) +
+  common_cod_labs() +
+  labs(
+    title = 'Back-to-back round win %',
+    x = 'Round',
+    y = '# of rounds played in series'
+  ) + 
+  geom_text(
+    data = tibble(
+      label = 'Back-to-back wins occur most\nfrequently in the last round.',
+      x = 9.5,
+      y = 8.5
+    ),
+    size = 9 / .pt,
+    fontface = 'bold',
+    color = 'white',
+    hjust = 0,
+    vjust = 0.5,
+    aes(x = x, y = y, label = label)
+  ) +
+  map(
+    cod_b2b_round_win_prop_arws |> group_split(rn), 
+    function(.x) {
+      geom_curve(
+        data = data.frame(),
+        color = 'white',
+        arrow = arw,
+        aes(x = .x$x, y = .x$y, xend = .x$xend, yend = .x$yend),
+        curvature = .x$curvature
+      )
+    }
+  )
+p_cod_b2b_round_win_prop
+save_plot_for_slide(p_cod_b2b_round_win_prop)
+# ## now accounting for number of cod_rounds that end up being played AND series winners...
+# cod_rounds |> 
+#   filter(win_series, n_rounds > 6L) |> 
+#   summarize_b2b_round_wins(n_rounds)
+# 
+# ## and the losers...
+# cod_rounds |> 
+#   filter(!win_series) |> 
+#   summarize_b2b_round_wins(n_rounds)
+```
+
+![](plots/cod_b2b_round_win_prop.png){fig-align="center"}
+
+## Is there evidence for the "hot hand"?
+
+::: fragment
+[Miller and Sanjurjo (2018)](https://papers.ssrn.com/sol3/papers.cfm?abstract_id=2627354) outline a framework for quantifying post-streak success
+:::
+
+::: fragment
+Looking at streaks of 3
+:::
+
+```{r}
+#| label: cod_round_win_prop_after_b2b2b_wins
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 10000, seed = 42, ...) {
+  withr::local_seed(seed)
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+
+summarize_cod_win_prop_after_x_wins <- function(kind = c('b2b', 'b2b2b')) {
+  kind <- match.arg(kind)
+  is_b2b <- kind == 'b2b'
+  if (is_b2b) {
+    k <- 2
+  } else {
+    k <- 3
+  }
+
+  probs_nx_k <- tibble(
+    n_rounds = 7L:11L
+  ) |> 
+    mutate(
+      trial_p = 6 / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, trial_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  cod_round_win_prop_after_x_wins <- if (is_b2b) {
+    cod_round_streaks_after_x <- cod_round_streaks |> 
+      filter(!is.na(won_prior_round2)) |> 
+      count(n_rounds, win_round, won_prior_round, won_prior_round2, sort = TRUE)
+
+     cod_round_streaks_after_x |> 
+      filter(won_prior_round, won_prior_round2) 
+  } else {
+    cod_round_streaks_after_x <- cod_round_streaks |> 
+      filter(!is.na(won_prior_round2), !is.na(won_prior_round3)) |> 
+      count(n_rounds, win_round, won_prior_round, won_prior_round2, won_prior_round3, sort = TRUE)
+
+     cod_round_streaks_after_x |> 
+      filter(won_prior_round, won_prior_round2, won_prior_round3) 
+  }
+
+  cod_round_win_prop_after_x_wins |> 
+    group_by(n_rounds) |> 
+    mutate(
+      total = sum(n),
+      prop = n / total
+    ) |> 
+    ungroup() |> 
+    filter(win_round) |> 
+    select(n_rounds, n, total, prop) |> 
+    arrange(n_rounds) |> 
+    inner_join(
+      probs_nx_k,
+      by = 'n_rounds'
+    ) |> 
+    nest(data = -c(n_rounds)) |> 
+    mutate(
+      gt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      lt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
+          broom::tidy() |>
+          pull(p.value)
+      )
+    ) |> 
+    unnest(data)
+}
+
+cod_round_win_prop_after_b2b_wins <- summarize_cod_win_prop_after_x_wins('b2b')
+cod_round_win_prop_after_b2b2b_wins <- summarize_cod_win_prop_after_x_wins('b2b2b')
+```
+
+```{r}
+#| label: cod_round_win_prop_after_b2b2b_wins-eval
+#| eval: true
+# cod_round_win_prop_after_b2b_wins |> clipr::write_clip() |> datapasta::tribble_paste()
+cod_round_win_prop_after_b2b_wins <- tibble::tribble(
+  ~n_rounds,   ~n, ~total,             ~prop,          ~trial_p, ~expected_poststreak_p,       ~gt_p_value,          ~lt_p_value,
+         7L, 262L,   328L, 0.798780487804878, 0.857142857142857,      0.786573045059608,   0.3220219536276,    0.725316732579212,
+         8L, 265L,   421L, 0.629453681710214,              0.75,      0.648791374811152, 0.811481245561487,    0.217078977854197,
+         9L, 275L,   577L, 0.476603119584055, 0.666666666666667,      0.557203226372085, 0.999956606998609, 6.11343021400038e-05,
+        10L, 257L,   628L, 0.409235668789809,               0.6,      0.483529268542724, 0.999920968231117, 0.000108871179188732,
+        11L, 317L,   807L, 0.392812887236679, 0.545454545454545,       0.42596043311709, 0.974133848646825,   0.0304921375685209
+  )
+# cod_round_win_prop_after_b2b2b_wins |> clipr::write_clip() |> datapasta::tribble_paste()
+cod_round_win_prop_after_b2b2b_wins <- tibble::tribble(
+  ~n_rounds,   ~n, ~total,             ~prop,          ~trial_p, ~expected_poststreak_p,       ~gt_p_value,         ~lt_p_value,
+         7L, 149L,   201L, 0.741293532338308, 0.857142857142857,      0.757307821042062, 0.732554638281868,   0.323308922871945,
+         8L, 126L,   203L, 0.620689655172414,              0.75,      0.618543392752532, 0.505988058731931,   0.551527754692743,
+         9L,  98L,   209L,   0.4688995215311, 0.666666666666667,      0.526500674199098, 0.958718294702725,   0.055063286515911,
+        10L,  74L,   208L, 0.355769230769231,               0.6,      0.446500557074851, 0.996786203815779, 0.00490308277112825,
+        11L,  90L,   276L, 0.326086956521739, 0.545454545454545,      0.387843835660101, 0.985650077371605,  0.0196488641002811
+  )
+```
+
+::: fragment
+There is no evidence for momentum, for both streaks of 2 and 3.
+In fact, for series that go to 9, 10, or 11 rounds, there is evidence that the streaking teams perform significantly worse than expected in the post-streak round.
+:::
+
+```{r}
+#| label: chance_summarize_and_compare_win_prop_after_wins
+#| eval: false
+## https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422#app2 suggests that we should look at non-overlapping streaks.
+## "To avoid this problem, we examine only the frequency of winning game three after having won games one and two and the frequency of winning game six after having won games four and five".
+They sort of deduced that win %s > 50% in the third game might constitute momentum, but didn't make strong statements.
+## Personally, I don't really like this approach. It needs to account for the number of games played.
+chance_summarize_cod_win_prop_after_x_wins <- function(round, ...) {
+  cod_round_streaks |> 
+    filter(round == !!round) |> 
+    count(win_round, won_prior_round, won_prior_round2, ..., sort = TRUE) |> 
+    relocate(n) |> 
+    drop_na(last_col()) |> 
+    filter(won_prior_round, won_prior_round2, ...) |> 
+    mutate(
+      total = sum(n),
+      prop = n / total
+    ) |> 
+    filter(win_round) |> 
+    transmute(round = !!round, n, total, prop)
+}
+
+chance_summarize_cod_win_prop_after_b2b_wins <- chance_summarize_cod_win_prop_after_x_wins
+chance_summarize_cod_win_prop_after_b2b2b_wins <- function(round) {
+  chance_summarize_cod_win_prop_after_x_wins(round = round, won_prior_round3)
+}
+
+chance_summarize_and_compare_cod_win_prop_after_wins <- function(ri, add, f) {
+  ra <- f(ri)
+  rb <- f(ri + add)
+  bind_rows(ra, rb)
+}
+
+chance_summarize_and_compare_cod_win_prop_after_b2b_wins <- partial(
+  chance_summarize_and_compare_cod_win_prop_after_wins,
+  add = 3,
+  f = summarize_cod_win_prop_after_b2b_wins,
+  ... = 
+)
+
+chance_summarize_and_compare_cod_win_prop_after_b2b2b_wins <- partial(
+  chance_summarize_and_compare_cod_win_prop_after_wins,
+  add = 4,
+  f = summarize_cod_win_prop_after_b2b2b_wins,
+  ... = 
+)
+
+chance_cod_win_prop_after_b2b_wins <- seq(3, 8, by = 1) |> 
+  map_dfr(
+    chance_summarize_and_compare_cod_win_prop_after_b2b_wins,
+    .id = 'pair_idx'
+  )
+
+chance_cod_win_prop_after_b2b2b_wins <- seq(4, 7, by = 1) |> 
+  map_dfr(
+    chance_summarize_and_compare_cod_win_prop_after_b2b2b_wins,
+    .id = 'pair_idx'
+  )
+```
+
+## Is planting at one site better than the other ([COD SnD]{.cod})?
+
+```{r}
+#| label: cod_plant_win_prop_proj
+cod_map_plant_win_prop <- cod_rounds |> 
+  filter(!is.na(plant)) |> 
+  filter(is_offense) |> 
+  group_by(year, game, map, plant) |> 
+  summarize(
+    n = n(),
+    wins = sum(win_round)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_prop = wins / n
+  ) |> 
+  group_by(year, game, map) |> 
+  mutate(
+    total = sum(n),
+    rnk = row_number(-n),
+    prop = n / total
+  ) |> 
+  ungroup()
+
+cod_plant_win_prop <- cod_map_plant_win_prop |>
+  mutate(site = ifelse(rnk == 1, 'pri', 'sec')) |> 
+  group_by(site) |> 
+  summarize(
+    across(c(n, wins, total), sum)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_prop = wins / n,
+    prop = n / total
+  )
+
+cod_plant_win_prop_proj <- cod_plant_win_prop |> 
+  left_join(
+    cod_rounds |> 
+      filter(is_offense) |> 
+      filter(is.na(plant)) |> 
+      summarize(
+        n_no_plant = n(),
+        wins_no_plant = sum(win_round)
+      ),
+    by = character()
+  ) |> 
+  mutate(
+    n_proj = round(n + prop * n_no_plant),
+    wins_proj = round(wins + prop * wins_no_plant),
+    win_prop_proj = wins_proj / n_proj
+  )
+
+cod_plant_site_prop <- cod_plant_win_prop_proj |> 
+  select(site, prop) |> 
+  deframe() |> 
+  scales::percent(accuracy = 0.1)
+
+cod_plant_site_win_prop <- cod_plant_win_prop_proj |> 
+  select(site, win_prop_proj) |> 
+  deframe() |> 
+  scales::percent(accuracy = 0.1)
+```
+
+```{r}
+#| label: cod_plant_win_prop_proj-eval
+#| eval: true
+cod_plant_site_prop <- c(
+  'pri' = '60.9%',
+  'sec' = '39.1%'
+)
+cod_plant_site_win_prop <- c(
+  'pri' = '47.4%',
+  'sec' = '48.5%'
+)
+```
+
+<br/><br/>
+
+::: columns
+::: {.column width="15%"}
+:::
+
+::: {.column .fragment width="30%"}
+| Plant site |                               \% |
+|------------|---------------------------------:|
+| Primary    | `r cod_plant_site_prop[['pri']]` |
+| Secondary  | `r cod_plant_site_prop[['sec']]` |
+:::
+
+::: {.column width="10%"}
+:::
+
+::: {.column .fragment width="30%"}
+| Plant site |                                Win % |
+|------------|-------------------------------------:|
+| Primary    | `r cod_plant_site_win_prop[['pri']]` |
+| Secondary  | `r cod_plant_site_win_prop[['sec']]` |
+:::
+
+::: {.column width="15%"}
+:::
+:::
+
 ## Are offensive win %'s different in round 1 ([COD SnD]{.cod})?
@@
 
-## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
-
-::: fragment
-[Chance (2019)](https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422) finds that the probability of winning a game in the title series in the MLB and NHL is **not** constant (at 50%)
-:::
-
-```{r}
-#| label: chance-2019
-chance_2019_leagues <- c('MLB World Series', 'NBA Finals', 'NHL Stanley Cup')
-
-n_sports <- tibble(
-  league = chance_2019_leagues,
-  ## i think nba has to be 2019 instead of 2018 in order for the product of `n * prop_actual` to be a whole number
-  n = c(2018 - 1923, 2019 - 1951, 2018 - 1939)
-)
-
-chance_sports <- tibble(
-  league = rep(chance_2019_leagues, each = 4),
-  games = rep(4:7, 3),
-  prop_actual = c(
-    c(0.1895, 0.2105, 0.2105, 0.3895),
-    c(0.1324, 0.25, 0.3382, 0.2794),
-    c(0.2532, 0.2278, 0.3165, 0.2025)
-  ),
-  prop_expected = rep(c(0.125, 0.25, 0.3125, 0.3125), 3)
-)
-
-sports <- chance_sports |> 
-  inner_join(
-    n_sports,
-    by = 'league'
-  ) |> 
-  mutate(
-    n_actual = round(n * prop_actual)
-  )
-
-generate_chi_label <- function(statistic, p.value) {
-  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
-}
-
-chi_sports <- sports |> 
-  nest(data = -c(league)) |> 
-  mutate(
-    chi = map(data, ~chisq.test(.x$n_actual, p = .x$prop_expected) |> broom::tidy())
-  ) |> 
-  select(league, chi) |> 
-  unnest(chi) |> 
-  transmute(
-    league, 
-    label = generate_chi_label(statistic, p.value)
-  )
-
-sports |> 
-  select(league, games, prop_expected, prop_actual) |> 
-  mutate(
-    across(
-      starts_with('prop_'),
-      scales::percent
-    ),
-    across(games, as.character)
-  ) |> 
-  pivot_wider(names_from = league, values_from = prop_actual) |> 
-  bind_rows(
-    bind_cols(
-      tibble(games = 'Avg. # of games'),
-      sports |> 
-        distinct(games, prop_expected) |>
-        summarize(prop_expected = as.character(round(sum(games * prop_expected), 2))),
-      sports |> 
-        group_by(league) |>
-        summarize(z = as.character(round(sum(games * prop_actual), 2))) |> 
-        pivot_wider(names_from = league, values_from = z)
-    )
-  ) |> 
-  bind_rows(
-    chi_sports |> 
-      pivot_wider(names_from = league, values_from = label) |> 
-      mutate(
-        games = '$\\xi^2$ (p-value)'
-      )
-  ) |> 
-  relocate(
-    `Series ends in i games` = games,
-    `Expected` = prop_expected
-  ) |> 
-  knitr::kable()
-```
-
-::: fragment
-|         Series length | Expected | MLB World Series | NBA Finals | NHL Stanley Cup |
-|----------------------:|---------:|-----------------:|-----------:|----------------:|
-|                     4 |   12.50% |           18.95% |     13.24% |          25.32% |
-|                     5 |   25.00% |           21.05% |     25.00% |          22.78% |
-|                     6 |   31.25% |           21.05% |     33.82% |          31.65% |
-|                     7 |   31.25% |           38.95% |     27.94% |          20.25% |
-|                       |          |                  |            |                 |
-|  **Avg. \# of games** |     5.81 |              5.8 |       5.76 |            5.47 |
-| $\xi^2$ **(p-value)** |          |       8.7 (0.03) | 0.4 (0.94) |  13.6 (\<=0.01) |
-:::
-
-```{r}
-#| label: cod_series_outcomes_chi
-
-cod_rounds_per_series <- cod_streaks_res$series |>
-  summarize(
-    actual = sum(n_rounds * prop_actual),
-    expected = sum(n_rounds * prop_expected)
-  )
-avg_actual_cod_rounds_per_series <- round(cod_rounds_per_series$actual, 2)
-avg_expected_cod_rounds_per_series <- round(cod_rounds_per_series$expected, 2)
-
-cod_series_outcomes_chi <- chisq.test(
-  cod_streaks_res$series$n_actual, 
-  p = cod_streaks_res$series$prop_expected
-) |> 
-  broom::tidy() |> 
-  mutate(label = generate_chi_label(statistic, p.value)) |> 
-  pull(label)
-cod_series_outcomes_chi
-```
-
-```{r}
-#| label: cod_series_outcomes_chi-eval
-#| eval: true
-avg_actual_cod_rounds_per_series <- 9.15
-avg_expected_cod_rounds_per_series <- 9.29
-cod_series_outcomes_chi <- '15.4 (<=0.01)'
-```
-
-::: fragment
--   In COD, the average number of rounds (**`r avg_actual_cod_rounds_per_series`**) is less than the expected value (**`r avg_expected_cod_rounds_per_series`**)
-:::
-
-::: fragment
--   A $\xi^2$ test for CoD demonstrates evidence against the constant probability null hypothesis for winning a given round in an SnD series (**`r cod_series_outcomes_chi`**)
-:::
-
-## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
-
-```{r}
-#| label: alternative-to-p=0.5-method-1
-## p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
-theoretical_cod_series_length <- function(p) {
-  6 * prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11) +
-    7 * prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11) + 
-    8 * prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11) + 
-    9 * prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11) +
-    10 * prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11) +
-    11 * prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)
-}
-
-cod_ps <- tibble(p = seq(0.5, 0.7, by = 0.0025))
-
-cod_theoretical_series_lengths1 <- cod_ps |> 
-  mutate(
-    theoretical_series_length = map_dbl(p, theoretical_cod_series_length),
-    diff = theoretical_series_length - cod_rounds_per_series$actual
-  )
-
-cod_theoretical_constant_p1 <- cod_theoretical_series_lengths1 |> 
-  slice_min(abs(diff), n = 1) |> 
-  pull(p)
-
-pretty_cod_theoretical_constant_p1 <- cod_theoretical_constant_p1 |> 
-  scales::percent(accuracy = 0.01)
-```
-
-```{r}
-#| label: alternative-to-p=0.5-method-1-eval
-#| eval: true
-pretty_cod_theoretical_constant_p1 <- '57.25%'
-```
-
-```{r}
-#| label: cod-alternative-to-p=0.5-method-2
-pluck_cod_n <- function(.n_rounds) {
-  cod_streaks_res$series |>
-    filter(n_rounds == .n_rounds) |> 
-    pull(n_actual)
-}
-
-cod_n6 <- pluck_cod_n(6)
-cod_n7 <- pluck_cod_n(7)
-cod_n8 <- pluck_cod_n(8)
-cod_n9 <- pluck_cod_n(9)
-cod_n10 <- pluck_cod_n(10)
-cod_n11 <- pluck_cod_n(11)
-
-## This adjustment is something that is not done in the paper. I do it here to reduce
-##   the magnitude of the exponents.
-cod_pm <- pmin(cod_n6, cod_n7, cod_n8, cod_n9, cod_n10, cod_n11)
-cod_n6adj <- round(10 * cod_n6 / cod_pm)
-cod_n7adj <- round(10 * cod_n7 / cod_pm)
-cod_n8adj <- round(10 * cod_n8 / cod_)
-cod_n9adj <- round(10 * cod_n9 / cod_pm)
-cod_n10adj <- round(10 * cod_n10 / cod_pm)
-cod_n11adj <- round(10 * cod_n11 / cod_pm)
-
-maximize_cod_series_p <- function(p) {
-  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^cod_n6adj *
-    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^cod_n7adj * 
-    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^cod_n8adj * 
-    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^cod_n9adj *
-    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^cod_n10adj * 
-    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^cod_n11adj
-}
-
-cod_theoretical_series_lengths2 <- cod_ps |> 
-  mutate(
-    theoretical_series_length = map_dbl(p, maximize_cod_series_p)
-  )
-
-cod_theoretical_constant_p2 <- cod_theoretical_series_lengths2 |> 
-  slice_max(theoretical_series_length, n = 1) |> 
-  pull(p)
-
-pretty_cod_theoretical_constant_p2 <- cod_theoretical_constant_p2 |> 
-  scales::percent(accuracy = 0.01)
-
-best_cod_theoretical_series_lengths2 <- cod_theoretical_series_lengths2 |> 
-  filter(p == cod_theoretical_constant_p2)
-
-p_cod_theoretical_series_lengths2 <- cod_theoretical_series_lengths2 |> 
-  ggplot() +
-  aes(x = p, y = theoretical_series_length) +
-  geom_line(
-    size = 2,
-    color = 'white'
-  ) +
-  geom_point(
-    data = best_cod_theoretical_series_lengths2,
-    color = ggsci_cyan,
-    size = 6
-  ) +
-  geom_text(
-    data = best_cod_theoretical_series_lengths2,
-    color = ggsci_cyan,
-    size = 13 / .pt,
-    hjust = 0,
-    aes(
-      x = p + 0.02,
-      label = sprintf('Maximum likilihood estimate (MLE) of\nconstant probability of better team winning (%s)', !!pretty_cod_theoretical_constant_p2)
-    )
-  ) +
-  scale_x_continuous(labels = scales::percent) +
-  labs(
-    x = 'Constant probability of better team winning',
-    y = 'Kernel of the multinomial likelihood'
-  ) +
-  theme(
-    axis.text.y = element_blank(),
-    panel.grid.major = element_blank()
-  )
-p_cod_theoretical_series_lengths2
-save_plot_for_slide(p_cod_theoretical_series_lengths2)
-```
-
-```{r}
-#| label: cod-alternative-to-p=0.5-method-2-eval
-#| eval: true
-pretty_cod_theoretical_constant_p2 <- '53.25%'
-```
-
-::: fragment
-[Mosteller (1952)](https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf) suggests several ways to find the optimal constant probability of the "stronger" team winning each game in a series.
-:::
-
-::: fragment
--   Using the method of moments approach (Mosteller's method 1), `r pretty_cod_theoretical_constant_p1`
-:::
-
-::: fragment
--   Using the maximum likelihood approach (Mosteller's method 2), `r pretty_cod_theoretical_constant_p2`
-
-![](plots/cod_theoretical_series_lengths2.png){fig-align="center" width="65%"}
-:::
-
-## What are the most common series winning states ([Valorant]{.valorant})?
-
-```{r}
-#| label: p_val_series_outcome_prop_over_expected
-val_streaks_res <- val_rounds |> summarize_streaks('val')
-
-p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
-  plot_series_outcome_prop_over_expected('val') +
-  common_val_labs()
-p_val_series_outcome_prop_over_expected
-save_plot_for_slide(p_val_series_outcome_prop_over_expected)
-```
-
-![](plots/val_series_outcome_prop_over_expected.png)
-
-## When do back-to-back round wins occur ([COD SnD]{.cod})?
-
-```{r}
-#| label: p_cod_b2b_round_win_prop
-summarize_cod_b2b_round_wins <- function(df, ...) {
-  df |> 
-    arrange(year, sheet, series, team, round) |> 
-    group_by(year, sheet, series, team) |> 
-    mutate(
-      b2b_round_wins = win_round & lag(win_round)
-    ) |> 
-    ungroup() |> 
-    filter(round > 1L) |> 
-    count(..., round, b2b_round_wins) |> 
-    group_by(..., round) |> 
-    mutate(total = sum(n), prop = n / total) |> 
-    ungroup() |> 
-    filter(b2b_round_wins) |> 
-    select(-b2b_round_wins)
-}
-
-## now accounting for number of cod_rounds that end up being played...
-## seems like there is interesting behavior in the last round, regardless `n_rounds`
-cod_b2b_round_win_prop <- cod_rounds |> 
-  filter(n_rounds > 6L) |> 
-  summarize_cod_b2b_round_wins(n_rounds) |> 
-  group_by(n_rounds) |> 
-  mutate(
-    z = (n - mean(n)) / sd(n),
-    rnk = row_number(desc(n))
-  ) |> 
-  ungroup()
-
-b2b_round_win_prop_tile_layer <- function(..., .df, .round, .palette, .is_new = TRUE) {
-
-  init <- if(!.is_new) {
-    list()
-  } else {
-    ggnewscale::new_scale_fill()
-  }
-
-  list(
-    ...,
-    init,
-    geom_tile(
-      data = .df |> filter(n_rounds == .round),
-      color = blackish_background,
-      height = 0.8,
-      show.legend = FALSE,
-      aes(
-        fill = z,
-        x = round + 0.5, 
-        y = n_rounds + 0.5
-      )
-    ),
-    ggsci::scale_fill_material(palette = .palette) 
-  )
-}
-
-b2b_round_win_prop_text_layer <- function(..., .df, .emphasize) {
-  if(.emphasize == 'low') {
-    op <- `>`
-    .color <- blackish_background
-  } else {
-    op <- `==`
-    .color <- 'white'
-  }
-  list(
-    ...,
-    geom_text(
-      data = .df |> filter(`op`(rnk, 1)),
-      color = .color,
-      size = 11 / .pt,
-      fontface = 'bold',
-      aes(
-        label = sprintf('%s\n(%s)', scales::percent(prop, accuracy = 1), scales::comma(n)),
-        x = round + 0.5, 
-        y = n_rounds + 0.5
-      )
-    )
-  )
-}
-
-b2b_round_win_prop_text_layers <- function(..., .df) {
-  list(
-    ...,
-    b2b_round_win_prop_text_layer(.df = .df, .emphasize = 'low'),
-    b2b_round_win_prop_text_layer(.df = .df, .emphasize = 'high')
-  )
-}
-
-cod_b2b_round_win_prop_arws <- tibble(
-  x = c(9.3, 9.4, 9.75, 10),
-  y = c(8.25, 8.5, 8.75, 8.75),
-  xend = c(8.1, 9.1, 9.5, 10.5),
-  yend = c(7.5, 8.5, 9, 10),
-  curvature = c(-0.2, -0.1, 0.1, 0.2)
-) |> 
-  mutate(
-    rn = row_number()
-  )
-
-p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
-  ggplot() +
-  b2b_round_win_prop_tile_layer(
-    .df = cod_b2b_round_win_prop, 
-    .round = 7, 
-    .palette = 'pink', 
-    .is_new = FALSE
-  ) +
-  b2b_round_win_prop_tile_layer(
-    .df = cod_b2b_round_win_prop, 
-    .round = 8, 
-    .palette = 'light-blue'
-  ) +
-  b2b_round_win_prop_tile_layer(
-    .df = cod_b2b_round_win_prop, 
-    .round = 9, 
-    .palette = 'light-green'
-  ) +
-  b2b_round_win_prop_tile_layer(
-    .df = cod_b2b_round_win_prop, 
-    .round = 10, 
-    .palette = 'amber'
-  ) +
-  b2b_round_win_prop_tile_layer(
-    .df = cod_b2b_round_win_prop, 
-    .round = 11, 
-    .palette = 'deep-orange'
-  ) +
-  b2b_round_win_prop_text_layers(.df = cod_b2b_round_win_prop) +
-  scale_x_continuous(
-    labels = 2:11,
-    breaks = seq(2.5, 11.5, by = 1),
-    expand = c(0, 0.5)
-  ) +
-  scale_y_continuous(
-    labels = 7:11,
-    breaks = seq(7.5, 11.5, by = 1),
-    expand = c(0, 0)
-  ) +
-  theme(
-    panel.grid.major = element_blank(),
-    axis.title = element_text(hjust = 0.5),
-    plot.title = ggtext::element_markdown(hjust = 0.5),
-    axis.text = element_text(size = 16, face = 'bold')
-  ) +
-  common_cod_labs() +
-  labs(
-    title = 'Back-to-back round win %',
-    x = 'Round',
-    y = '# of rounds played in series'
-  ) + 
-  geom_text(
-    data = tibble(
-      label = 'Back-to-back wins occur most\nfrequently in the last round.',
-      x = 9.5,
-      y = 8.5
-    ),
-    size = 9 / .pt,
-    fontface = 'bold',
-    color = 'white',
-    hjust = 0,
-    vjust = 0.5,
-    aes(x = x, y = y, label = label)
-  ) +
-  map(
-    cod_b2b_round_win_prop_arws |> group_split(rn), 
-    function(.x) {
-      geom_curve(
-        data = data.frame(),
-        color = 'white',
-        arrow = arw,
-        aes(x = .x$x, y = .x$y, xend = .x$xend, yend = .x$yend),
-        curvature = .x$curvature
-      )
-    }
-  )
-p_cod_b2b_round_win_prop
-save_plot_for_slide(p_cod_b2b_round_win_prop)
-# ## now accounting for number of cod_rounds that end up being played AND series winners...
-# cod_rounds |> 
-#   filter(win_series, n_rounds > 6L) |> 
-#   summarize_b2b_round_wins(n_rounds)
-# 
-# ## and the losers...
-# cod_rounds |> 
-#   filter(!win_series) |> 
-#   summarize_b2b_round_wins(n_rounds)
-```
-
-![](plots/cod_b2b_round_win_prop.png){fig-align="center"}
-
-## Is there evidence for the "hot hand"?
-
-```{r}
-#| label: cod_round_win_prop_after_b2b2b_wins
-## http://keyonvafa.com/hot-hand/
-get_post_streak_prob <- function(n, k, p = 0.5) {
-  tosses <- rbinom(n, 1, p)
-  runs <- rle(tosses)
-  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
-  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
-
-  ## edge case
-  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
-    n_neg_after <- n_neg_after - 1
-  }
-
-  n_pos_after / (n_pos_after + n_neg_after)
-}
-
-simulate_post_streak_prob <- function(sims = 1000, ...) {
-  rerun(
-    sims,
-    get_post_streak_prob(...)
-  ) |> 
-    flatten_dbl() |> 
-    mean(na.rm = TRUE)
-}
-# prob_n6_k2 <- simulate_post_streak_prob(sims = 10000, n = 6, k = 2, p = 0.5)
-prob_n6_k3 <- simulate_post_streak_prob(sims = 10000, n = 6, k = 3, p = 0.5)
-prob_n11_k3 <- simulate_post_streak_prob(sims = 10000, n = 8, k = 3, p = 0.5)
-prob_n11_k3 <- simulate_post_streak_prob(sims = 10000, n = 11, k = 3, p = 0.5)
-prob_n10_k1 <- simulate_post_streak_prob(sims = 10000, n = 10, k = 1, p = 0.5)
-
-cod_round_streaks <- cod_rounds |> 
-  # filter(round <= 6) |> 
-  group_by(year, sheet, series, team) |> 
-  mutate(
-    won_prior_round2 = lag(win_round, n = 2, default = NA),
-    won_prior_round3 = lag(win_round, n = 3, default = NA)
-  ) |> 
-  ungroup() |>
-  select(
-    year,
-    sheet,
-    series,
-    team,
-    is_offense,
-    round,
-    win_round,
-    won_prior_round,
-    won_prior_round2,
-    won_prior_round3
-  )
-
-cod_round_streaks_after_b2b2b <- cod_round_streaks |> 
-  filter(!is.na(won_prior_round2), !is.na(won_prior_round3)) |> 
-  count(win_round, won_prior_round, won_prior_round2, won_prior_round3, sort = TRUE)
-
-cod_round_win_prop_after_b2b2b_wins <- cod_round_streaks_after_b2b2b |> 
-  filter(won_prior_round, won_prior_round2, won_prior_round3) |> 
-  mutate(
-    total = sum(n),
-    prop = n / total
-  ) |> 
-  filter(win_round) |> 
-  select(n, total, prop)
-```
-
-```{r}
-#| label: cod_round_win_prop_after_b2b2b_wins-eval
-#| eval: true
-prob_n6_k3 <- 0.3838163
-cod_round_win_prop_after_b2b2b_wins <- tibble(
-  n = 621,
-  total = 1150
-) |> 
-  mutate(prop = n / total)
-```
-
-```{r}
-#| label: summarize_and_compare_win_prop_after_wins
-## https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422#app2 suggests that we should look at non-overlapping streaks.
-## "To avoid this problem, we examine only the frequency of winning game three after having won games one and two and the frequency of winning game six after having won games four and five".
-They sort of deduced that win %s > 50% in the third game might constitute momentum, but didn't make strong statements.
-summarize_cod_win_prop_after_x_wins <- function(round, ...) {
-  cod_round_streaks |> 
-    filter(round == !!round) |> 
-    count(win_round, won_prior_round, won_prior_round2, ..., sort = TRUE) |> 
-    relocate(n) |> 
-    drop_na(last_col()) |> 
-    filter(won_prior_round, won_prior_round2, ...) |> 
-    mutate(
-      total = sum(n),
-      prop = n / total
-    ) |> 
-    filter(win_round) |> 
-    transmute(round = !!round, n, total, prop)
-}
-
-summarize_cod_win_prop_after_b2b_wins <- summarize_cod_win_prop_after_x_wins
-summarize_cod_win_prop_after_b2b2b_wins <- function(round) {
-  summarize_cod_win_prop_after_x_wins(round = round, won_prior_round3)
-}
-
-summarize_and_compare_cod_win_prop_after_wins <- function(ri, add, f) {
-  ra <- f(ri)
-  rb <- f(ri + add)
-  bind_rows(ra, rb)
-}
-
-summarize_and_compare_cod_win_prop_after_b2b_wins <- partial(
-  summarize_and_compare_cod_win_prop_after_wins,
-  add = 3,
-  f = summarize_cod_win_prop_after_b2b_wins,
-  ... = 
-)
-
-summarize_and_compare_cod_win_prop_after_b2b2b_wins <- partial(
-  summarize_and_compare_cod_win_prop_after_wins,
-  add = 4,
-  f = summarize_cod_win_prop_after_b2b2b_wins,
-  ... = 
-)
-
-cod_win_prop_after_b2b_wins <- seq(3, 8, by = 1) |> 
-  map_dfr(
-    summarize_and_compare_cod_win_prop_after_b2b_wins,
-    .id = 'pair_idx'
-  )
-
-cod_win_prop_after_b2b2b_wins <- seq(4, 7, by = 1) |> 
-  map_dfr(
-    summarize_and_compare_cod_win_prop_after_b2b2b_wins,
-    .id = 'pair_idx'
-  )
-```
-
-<br/><br/>
-
-Round win % after a streak of 3 round wins:
-
--   Expected: **`r 100 * round(prob_n6_k3, 3)`%**
--   Actual: **`r 100 * round(cod_round_win_prop_after_b2b2b_wins$prop, 3)`%** (`r cod_round_win_prop_after_b2b2b_wins$n` / `r cod_round_win_prop_after_b2b2b_wins$total`)
-
-## Is planting at one site better than the other?
-
-```{r}
-#| label: cod_plant_win_prop_proj
-cod_map_plant_win_prop <- cod_rounds |> 
-  filter(!is.na(plant)) |> 
-  filter(is_offense) |> 
-  group_by(year, game, map, plant) |> 
-  summarize(
-    n = n(),
-    wins = sum(win_round)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    win_prop = wins / n
-  ) |> 
-  group_by(year, game, map) |> 
-  mutate(
-    total = sum(n),
-    rnk = row_number(-n),
-    prop = n / total
-  ) |> 
-  ungroup()
-
-cod_plant_win_prop <- cod_map_plant_win_prop |>
-  mutate(site = ifelse(rnk == 1, 'pri', 'sec')) |> 
-  group_by(site) |> 
-  summarize(
-    across(c(n, wins, total), sum)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    win_prop = wins / n,
-    prop = n / total
-  )
-
-cod_plant_win_prop_proj <- cod_plant_win_prop |> 
-  left_join(
-    cod_rounds |> 
-      filter(is_offense) |> 
-      filter(is.na(plant)) |> 
-      summarize(
-        n_no_plant = n(),
-        wins_no_plant = sum(win_round)
-      ),
-    by = character()
-  ) |> 
-  mutate(
-    n_proj = round(n + prop * n_no_plant),
-    wins_proj = round(wins + prop * wins_no_plant),
-    win_prop_proj = wins_proj / n_proj
-  )
-
-cod_plant_site_prop <- cod_plant_win_prop_proj |> 
-  select(site, prop) |> 
-  deframe() |> 
-  scales::percent(accuracy = 0.1)
-
-cod_plant_site_win_prop <- cod_plant_win_prop_proj |> 
-  select(site, win_prop_proj) |> 
-  deframe() |> 
-  scales::percent(accuracy = 0.1)
-```
-
-```{r}
-#| label: cod_plant_win_prop_proj-eval
-#| eval: true
-cod_plant_site_prop <- c(
-  'pri' = '60.9%',
-  'sec' = '39.1%'
-)
-cod_plant_site_win_prop <- c(
-  'pri' = '47.4%',
-  'sec' = '48.5%'
-)
-```
-
-<br/><br/>
-
-::: columns
-::: {.column width="15%"}
-:::
-
-::: {.column .fragment width="30%"}
-| Plant site |                               \% |
-|------------|---------------------------------:|
-| Primary    | `r cod_plant_site_prop[['pri']]` |
-| Secondary  | `r cod_plant_site_prop[['sec']]` |
-:::
-
-::: {.column width="10%"}
-:::
-
-::: {.column .fragment width="30%"}
-| Plant site |                                Win % |
-|------------|-------------------------------------:|
-| Primary    | `r cod_plant_site_win_prop[['pri']]` |
-| Secondary  | `r cod_plant_site_win_prop[['sec']]` |
-:::
-
-::: {.column width="15%"}
-:::
-:::
-
 ## Winning a next game given the series state

### 2022-07-31 1-scrape-valorant.R
resave val with max_round -> nrounds

@@ -287,7 +287,7 @@ val_rounds <- bind_rows(
       group_by(series_id, match_id) |> 
       slice_max(round, n = 1, with_ties = FALSE) |> 
       ungroup() |> 
-      select(series_id, match_id, max_round = round),
+      select(series_id, match_id, n_rounds = round),
     by = 'series_id'
   ) |> 
   inner_join(
@@ -314,7 +314,7 @@ val_rounds <- bind_rows(
     team,
     opponent,
     round,
-    max_round,
+    n_rounds,
     is_offense,
     team_buy_type,
     opponent_buy_type,

### 2022-07-31 presentation.qmd
rm chance's momentum analysis

@@
 
-```{r}
-#| label: chance_summarize_and_compare_win_prop_after_wins
-#| eval: false
-## https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422#app2 suggests that we should look at non-overlapping streaks.
-## "To avoid this problem, we examine only the frequency of winning game three after having won games one and two and the frequency of winning game six after having won games four and five".
-They sort of deduced that win %s > 50% in the third game might constitute momentum, but didn't make strong statements.
-## Personally, I don't really like this approach. It needs to account for the number of games played.
-chance_summarize_cod_win_prop_after_x_wins <- function(round, ...) {
-  cod_round_streaks |> 
-    filter(round == !!round) |> 
-    count(win_round, won_prior_round, won_prior_round2, ..., sort = TRUE) |> 
-    relocate(n) |> 
-    drop_na(last_col()) |> 
-    filter(won_prior_round, won_prior_round2, ...) |> 
-    mutate(
-      total = sum(n),
-      prop = n / total
-    ) |> 
-    filter(win_round) |> 
-    transmute(round = !!round, n, total, prop)
-}
-
-chance_summarize_cod_win_prop_after_b2b_wins <- chance_summarize_cod_win_prop_after_x_wins
-chance_summarize_cod_win_prop_after_b2b2b_wins <- function(round) {
-  chance_summarize_cod_win_prop_after_x_wins(round = round, won_prior_round3)
-}
-
-chance_summarize_and_compare_cod_win_prop_after_wins <- function(ri, add, f) {
-  ra <- f(ri)
-  rb <- f(ri + add)
-  bind_rows(ra, rb)
-}
-
-chance_summarize_and_compare_cod_win_prop_after_b2b_wins <- partial(
-  chance_summarize_and_compare_cod_win_prop_after_wins,
-  add = 3,
-  f = summarize_cod_win_prop_after_b2b_wins,
-  ... = 
-)
-
-chance_summarize_and_compare_cod_win_prop_after_b2b2b_wins <- partial(
-  chance_summarize_and_compare_cod_win_prop_after_wins,
-  add = 4,
-  f = summarize_cod_win_prop_after_b2b2b_wins,
-  ... = 
-)
-
-chance_cod_win_prop_after_b2b_wins <- seq(3, 8, by = 1) |> 
-  map_dfr(
-    chance_summarize_and_compare_cod_win_prop_after_b2b_wins,
-    .id = 'pair_idx'
-  )
-
-chance_cod_win_prop_after_b2b2b_wins <- seq(4, 7, by = 1) |> 
-  map_dfr(
-    chance_summarize_and_compare_cod_win_prop_after_b2b2b_wins,
-    .id = 'pair_idx'
-  )
-```
-
 ## Is planting at one site better than the other ([COD SnD]{.cod})?

### 2022-08-02 research/replicate-streaks.R
Update replicate-streaks.R

@@ -25,32 +25,45 @@ simulate_post_streak_prob <- function(sims = 1000, ...) {
     mean(na.rm = TRUE)
 }
 
-runs <- crossing(
-  n = 1:100,
-  k = 1:4,
-  p = c(0.25, 0.5, 0.75)
+set.seed(42)
+## 1.6 hours for 1k reruns and 100 sims
+runs <- rerun(
+  1000,
+  crossing(
+    n = 1:100,
+    k = 1:4,
+    p = c(0.25, 0.5, 0.75)
+  ) |> 
+    mutate(
+      next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 100, n = ..1, k = ..2, p = ..3))
+    )
 ) |> 
-  mutate(
-    next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 10000, n = ..1, k = ..2, p = ..3))
-  )
+  reduce(bind_rows)
 
-p_streaks <- runs |>
-  filter(k != 5) |> 
+agg_runs <- runs |> 
   filter(!is.nan(next_p)) |> 
-  arrange(n, k) |>
+  group_by(p, k, n) |> 
+  summarize(
+    across(next_p, mean)
+  ) |> 
+  ungroup() |>
+  arrange(p, k)
+
+p_streaks <- agg_runs |>
+  group_by(p, k) |> 
+  mutate(
+    avg_next_p = slider::slide_dbl(next_p, .f = mean, .before = 5, .after = 0)
+  ) |> 
+  ungroup() |> 
   mutate(
     across(k, factor),
     group = sprintf('%s-%s', p, k)
   ) |> 
   ggplot() +
   theme_minimal() +
-  aes(x = n, y = next_p, color = k, group = group) +
-  geom_step() +
-  # eom_smooth(method = 'gam', formula = y ~ s(x, bs = 'cs'), se = FALSE) +
-  # geom_smooth(method = 'lm', formula = y ~ poly(x, 2)) +
-  # geom_smooth(method = 'loess', formula = y ~ x, se = FALSE) +
-  # facet_wrap(~p, scales = 'free_y') +
-  geom_hline(aes( yintercept = p)) +
+  aes(x = n, y = avg_next_p, color = k, group = group) +
+  geom_line() +
+  geom_hline(aes(yintercept = p)) +
   labs(x = NULL, y = NULL)
 p_streaks
 ggsave(p_streaks, filename = 'research/npk_replicated.png', width = 12, height = 9)

### 2022-08-02 1-scrape-cod.R
rm won_prior_round col

@@ -208,7 +208,6 @@ cod_rounds <- cod_series |>
     cumu_l = round - cumu_w,
     pre_cumu_w = lag(cumu_w, default = 0L),
     pre_cumu_l = lag(cumu_l, default = 0L),
-    won_prior_round = lag(win_round, default = NA),
     max_cumu_w = max(cumu_w)
   ) |> 
   ungroup() |> 

### 2022-08-02 presentation.qmd
formalize streaking with some FUNctions, basic plotting code

@@
 
-## Is there evidence for the "hot hand"?
+## Is there evidence for the "hot hand" ([COD SnD]{.cod})?
 
@@
 
-::: fragment
-Looking at streaks of 3
-:::
-
-```{r}
-#| label: cod_round_win_prop_after_b2b2b_wins
+```{r}
+#| label: cod_round_win_prop_after_x_wins
 ## http://keyonvafa.com/hot-hand/
@@
 
-summarize_cod_win_prop_after_x_wins <- function(kind = c('b2b', 'b2b2b')) {
-  kind <- match.arg(kind)
-  is_b2b <- kind == 'b2b'
-  if (is_b2b) {
-    k <- 2
-  } else {
-    k <- 3
-  }
+cod_round_streaks <- cod_rounds |> 
+  group_by(series_id, team) |> 
+  mutate(
+    won_prior_round1 = lag(win_round, n = 1, default = NA),
+    won_prior_round2 = lag(win_round, n = 2, default = NA),
+    won_prior_round3 = lag(win_round, n = 3, default = NA),
+    won_prior_round4 = lag(win_round, n = 4, default = NA),
+    won_prior_round5 = lag(win_round, n = 5, default = NA)
+  ) |> 
+  ungroup() |>
+  select(
+    series_id,
+    team,
+    is_offense,
+    round,
+    n_rounds,
+    win_round,
+    starts_with('won_prior_round')
+  )
+
+summarize_cod_win_prop_after_x_wins <- function(k) {
+  stopifnot((k >= 2) & (k <= 5))
 
@@
     mutate(
-      trial_p = 6 / n_rounds,
+      prior_p = 6L / n_rounds,
       expected_poststreak_p = map2_dbl(
-        n_rounds, trial_p, 
+        n_rounds, prior_p, 
         ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
@@
 
-  cod_round_win_prop_after_x_wins <- if (is_b2b) {
+  cols <- sprintf('won_prior_round%d', 2:k)
+  col_syms <- syms(cols)
   cod_round_streaks_after_x <- cod_round_streaks |> 
-      filter(!is.na(won_prior_round2)) |> 
-      count(n_rounds, win_round, won_prior_round, won_prior_round2, sort = TRUE)
-
-     cod_round_streaks_after_x |> 
-      filter(won_prior_round, won_prior_round2) 
-  } else {
-    cod_round_streaks_after_x <- cod_round_streaks |> 
-      filter(!is.na(won_prior_round2), !is.na(won_prior_round3)) |> 
-      count(n_rounds, win_round, won_prior_round, won_prior_round2, won_prior_round3, sort = TRUE)
-
-     cod_round_streaks_after_x |> 
-      filter(won_prior_round, won_prior_round2, won_prior_round3) 
-  }
+    drop_na(!!!col_syms) |> 
+    count(n_rounds, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+
+  cod_round_win_prop_after_x_wins <- cod_round_streaks_after_x |> 
+    filter(won_prior_round1, !!!col_syms)
 
@@
 
-cod_round_win_prop_after_b2b_wins <- summarize_cod_win_prop_after_x_wins('b2b')
-cod_round_win_prop_after_b2b2b_wins <- summarize_cod_win_prop_after_x_wins('b2b2b')
-```
-
-```{r}
-#| label: cod_round_win_prop_after_b2b2b_wins-eval
+cod_round_win_prop_after_x_wins <- tibble(win_streak = 2L:4L) |> 
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins)
+  ) |> 
+  unnest(data)
+```
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins-eval
 #| eval: true
-# cod_round_win_prop_after_b2b_wins |> clipr::write_clip() |> datapasta::tribble_paste()
-cod_round_win_prop_after_b2b_wins <- tibble::tribble(
-  ~n_rounds,   ~n, ~total,             ~prop,          ~trial_p, ~expected_poststreak_p,       ~gt_p_value,          ~lt_p_value,
-         7L, 262L,   328L, 0.798780487804878, 0.857142857142857,      0.786573045059608,   0.3220219536276,    0.725316732579212,
-         8L, 265L,   421L, 0.629453681710214,              0.75,      0.648791374811152, 0.811481245561487,    0.217078977854197,
-         9L, 275L,   577L, 0.476603119584055, 0.666666666666667,      0.557203226372085, 0.999956606998609, 6.11343021400038e-05,
-        10L, 257L,   628L, 0.409235668789809,               0.6,      0.483529268542724, 0.999920968231117, 0.000108871179188732,
-        11L, 317L,   807L, 0.392812887236679, 0.545454545454545,       0.42596043311709, 0.974133848646825,   0.0304921375685209
-  )
-# cod_round_win_prop_after_b2b2b_wins |> clipr::write_clip() |> datapasta::tribble_paste()
-cod_round_win_prop_after_b2b2b_wins <- tibble::tribble(
-  ~n_rounds,   ~n, ~total,             ~prop,          ~trial_p, ~expected_poststreak_p,       ~gt_p_value,         ~lt_p_value,
-         7L, 149L,   201L, 0.741293532338308, 0.857142857142857,      0.757307821042062, 0.732554638281868,   0.323308922871945,
-         8L, 126L,   203L, 0.620689655172414,              0.75,      0.618543392752532, 0.505988058731931,   0.551527754692743,
-         9L,  98L,   209L,   0.4688995215311, 0.666666666666667,      0.526500674199098, 0.958718294702725,   0.055063286515911,
-        10L,  74L,   208L, 0.355769230769231,               0.6,      0.446500557074851, 0.996786203815779, 0.00490308277112825,
-        11L,  90L,   276L, 0.326086956521739, 0.545454545454545,      0.387843835660101, 0.985650077371605,  0.0196488641002811
-  )
-```
-
-::: fragment
-There is no evidence for momentum, for both streaks of 2 and 3.
+cod_round_win_prop_after_x_wins |> 
+  transmute(
+    `Win Streak` = win_streak,
+    `Rounds` = n_rounds,
+    `N` = scales::comma(total),
+    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
+    across(
+      ends_with('p_value'), 
+      ~case_when(
+        .x <= 0.01 ~ '<=0.01', 
+        round(.x, 2) == 1 ~ '1',
+        TRUE ~ as.character(round(.x, 2))
+      )
+    )
+  ) |>
+  rename(
+    `Actual post-streak win %` = prop,
+    `Expected post-streak win %` = expected_poststreak_p,
+    `Binom. > p-value` = gt_p_value,
+    `Binom. < p-value` = lt_p_value
+  ) |> 
+  knitr::kable()
+
+```
+
+::: fragment
+-   There is no evidence for momentum, for both streaks of 2 and 3.
 In fact, for series that go to 9, 10, or 11 rounds, there is evidence that the streaking teams perform significantly worse than expected in the post-streak round.
+And for streaks of 4, teams perform worse than expected in series ending in 7, 8, 10, and 11 rounds.
+:::
+
+## Is there evidence for the "hot hand" ([Valorant]{.valorant})?
+
+```{r}
+#| label: val_round_win_prop_after_x_wins-save
+#| eval: false
+val_round_streaks <- val_rounds |> 
+  group_by(series_id, team, is_offense) |> 
+  mutate(
+    won_prior_round1 = lag(win_round, n = 1, default = NA),
+    won_prior_round2 = lag(win_round, n = 2, default = NA),
+    won_prior_round3 = lag(win_round, n = 3, default = NA),
+    won_prior_round4 = lag(win_round, n = 4, default = NA),
+    won_prior_round5 = lag(win_round, n = 5, default = NA),
+    won_prior_round6 = lag(win_round, n = 6, default = NA),
+    won_prior_round7 = lag(win_round, n = 7, default = NA),
+    won_prior_round8 = lag(win_round, n = 8, default = NA),
+    won_prior_round9 = lag(win_round, n = 9, default = NA)
+  ) |> 
+  ungroup() |>
+  select(
+    series_id,
+    team,
+    is_offense,
+    cumu_w,
+    round,
+    n_rounds,
+    win_round,
+    starts_with('won_prior_round')
+  )
+
+summarize_val_win_prop_after_x_wins_first12r <- function(k) {
+  stopifnot((k >= 3) & (k <= 9))
+  probs_nx_k <- tibble(
+    cumu_w = 4L:11L,
+    n_rounds = 12L
+  ) |> 
+    mutate(
+      prior_p = cumu_w / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  cols <- sprintf('won_prior_round%d', 2:k)
+  col_syms <- syms(cols)
+  val_round_streaks_after_x <- val_round_streaks |> 
+    filter(round < 13) |> 
+    drop_na(!!!col_syms) |> 
+    count(cumu_w, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+
+  val_round_win_prop_after_x_wins <- val_round_streaks_after_x |> 
+    filter(won_prior_round1, !!!col_syms)
+
+  val_round_win_prop_after_x_wins |> 
+    group_by(cumu_w) |> 
+    mutate(
+      total = sum(n),
+      prop = n / total
+    ) |> 
+    ungroup() |> 
+    filter(win_round) |> 
+    select(cumu_w, n, total, prop) |> 
+    arrange(cumu_w) |> 
+    inner_join(
+      probs_nx_k,
+      by = 'cumu_w'
+    ) |> 
+    nest(data = -c(cumu_w)) |> 
+    mutate(
+      gt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
+          broom::tidy() |>
+          pull(p.value) |> 
+          round(3)
+      ),
+      lt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
+          broom::tidy() |>
+          pull(p.value) |> 
+          round(3)
+      )
+    ) |> 
+    unnest(data)
+}
+
+summarize_val_win_prop_after_x_wins_second12r <- function(k) {
+  stopifnot((k >= 3) & (k <= 9))
+  probs_nx_k <- crossing(
+    cumu_w = 0L:13L,
+    n_rounds = 13L:24L
+  ) |> 
+    mutate(
+      prior_p = cumu_w / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  cols <- sprintf('won_prior_round%d', 2:k)
+  col_syms <- syms(cols)
+  val_round_streaks_after_x <- val_round_streaks |> 
+    filter(round > 12) |> 
+    drop_na(!!!col_syms) |> 
+    count(n_rounds, cumu_w, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+
+  val_round_win_prop_after_x_wins <- val_round_streaks_after_x |> 
+    filter(won_prior_round1, !!!col_syms)
+
+  val_round_win_prop_after_x_wins |> 
+    group_by(n_rounds, cumu_w) |> 
+    mutate(
+      total = sum(n),
+      prop = n / total
+    ) |> 
+    ungroup() |> 
+    filter(win_round) |> 
+    select(n_rounds, cumu_w, n, total, prop) |> 
+    arrange(n_rounds, cumu_w) |> 
+    inner_join(
+      probs_nx_k,
+      by = c('n_rounds', 'cumu_w')
+    ) |> 
+    nest(data = -c(n_rounds, cumu_w)) |> 
+    mutate(
+      gt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
+          broom::tidy() |>
+          pull(p.value) |> 
+          round(3)
+      ),
+      lt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
+          broom::tidy() |>
+          pull(p.value) |> 
+          round(3)
+      )
+    ) |> 
+    unnest(data)
+}
+
+save_qs <- function(df, name = deparse(substitute(df))) {
+  qs::qsave(df, sprintf('data/%s.qs', name))
+}
+
+val_round_win_prop_after_x_wins_first12r <- tibble(win_streak = 3L:9L) |> 
+  mutate(
+    data = map(win_streak, summarize_val_win_prop_after_x_wins_first12r)
+  ) |> 
+  unnest(data)
+save_qs(val_round_win_prop_after_x_wins_first12r)
+
+val_round_win_prop_after_x_wins_second12r <- tibble(win_streak = 3L:9L) |> 
+  mutate(
+    data = map(win_streak, summarize_val_win_prop_after_x_wins_second12r)
+  ) |> 
+  unnest(data)
+save_qs(val_round_win_prop_after_x_wins_second12r)
+```
+
+```{r}
+#| label: val_round_win_prop_after_x_wins
+#| eval: false
+load_qs <- function(name) {
+  res <- qs::qread(sprintf('data/%s.qs', name))
+  assign(name, value = res, envir = .GlobalEnv)
+}
+load_qs('val_round_win_prop_after_x_wins_first12r')
+load_qs('val_round_win_prop_after_x_wins_second12r')
+val_round_win_prop_after_x_wins_first12r |> 
+  filter(n > 30) |> 
+  mutate(
+    gt_signif = gt_p_value <= 0.05
+  ) |> 
+  ggplot() +
+  aes(x = win_streak, y = cumu_w) +
+  geom_tile(
+    aes(fill = gt_signif)
+  ) +
+  geom_text(
+    aes(label = sprintf(
+      '%s | %s\n(%s)',
+      scales::percent(prop, accuracy = 1),
+      scales::percent(expected_poststreak_p, accuracy = 1),
+      scales::comma(total)
+      )
+    )
+  )
+
+val_round_win_prop_after_x_wins_second12r |> 
+  filter(n > 30) |> 
+  mutate(
+    gt_signif = gt_p_value <= 0.05
+  ) |> 
+  ggplot() +
+  aes(x = win_streak, y = cumu_w) +
+  geom_tile(
+    aes(fill = gt_signif)
+  ) +
+  geom_text(
+    aes(label = sprintf(
+      '%s | %s\n(%s)',
+      scales::percent(prop, accuracy = 1),
+      scales::percent(expected_poststreak_p, accuracy = 1),
+      scales::comma(total)
+      )
+    )
+  ) +
+  facet_wrap(~n_rounds)
+
+```
+
+```{r}
+#| label: cod_round_win_prop_after_xw-eval
+#| eval: true
+val_round_win_prop_after_xw |> 
+  transmute(
+    `Win Streak` = win_streak,
+    `# of Offensive Wins in First 12 Rounds` = cumu_w,
+    `N` = scales::comma(total),
+    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
+    across(
+      ends_with('p_value'), 
+      ~case_when(
+        .x <= 0.01 ~ '<=0.01', 
+        round(.x, 2) == 1 ~ '1',
+        TRUE ~ as.character(round(.x, 2))
+      )
+    )
+  ) |>
+  rename(
+    `Actual post-streak win %` = prop,
+    `Expected post-streak win %` = expected_poststreak_p,
+    `Binom. > p-value` = gt_p_value,
+    `Binom. < p-value` = lt_p_value
+  ) |> 
+  knitr::kable()
+
+```
+
+::: fragment
+First 12 rounds **only**
+:::
+
+::: fragment
+-   There is no evidence for momentum, for both streaks of 2 and 3.
+In fact, for series that go to 9, 10, or 11 rounds, there is evidence that the streaking teams perform significantly worse than expected in the post-streak round.
+And for streaks of 4, teams perform worse than expected in series ending in 7, 8, 10, and 11 rounds.
+:::
+
+::: fragment
+-   Given the nature of how economy is used in the game, perhaps this is not suprising at all.
 :::

### 2022-08-05 presentation.qmd
qs functions

@@
 ```{r}
+#| label: qs-funcs
+#| eval: true
+load_qs <- function(name) {
+  res <- qs::qread(sprintf('data/%s.qs', name))
+  assign(name, value = res, envir = .GlobalEnv)
+}
+save_qs <- function(df, name = deparse(substitute(df))) {
+  qs::qsave(df, sprintf('data/%s.qs', name))
+}
+
+```
+
+```{r}
 #| label: cod_round_win_prop_after_x_wins
@@
   unnest(data)
+save_qs(cod_round_win_prop_after_x_wins)
 ```
@@
 #| eval: true
+load_qs('cod_round_win_prop_after_x_wins')
 cod_round_win_prop_after_x_wins |> 
@@
 
-save_qs <- function(df, name = deparse(substitute(df))) {
-  qs::qsave(df, sprintf('data/%s.qs', name))
-}
-
 val_round_win_prop_after_x_wins_first12r <- tibble(win_streak = 3L:9L) |> 
@@
 #| eval: false
-load_qs <- function(name) {
-  res <- qs::qread(sprintf('data/%s.qs', name))
-  assign(name, value = res, envir = .GlobalEnv)
-}
 load_qs('val_round_win_prop_after_x_wins_first12r')
@@
 #| label: cod_round_win_prop_after_xw-eval
-#| eval: true
-val_round_win_prop_after_xw |> 
+#| eval: false
+load_qs('val_round_win_prop_after_x_wins_first12r')
+val_round_win_prop_after_x_wins_first12r |> 
   transmute(
@@
 First 12 rounds **only**
+
+TODO
 :::
@@
 ![](plots/cod_series_outcome_prop_over_expected.png){fig-align="center"}
-
-## Winning a next game given the series state
-
-```{r}
-
-```

### 2022-08-05 presentation.qmd
shift up cod win series prop

@@
 
+## What are the most common series winning states ([COD SnD]{.cod})?
+
+```{r}
+#| label: p_cod_series_outcome_prop_over_expected
+# https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422
+prob_of_series_lasting_n_games <- function(n, p = 0.5, max_round) {
+  s <- ceiling(max_round / 2)
+  (factorial(n - 1) / (factorial(s - 1) * factorial(n - s))) * (p^s * (1 - p)^(n - s) + p^(n - s) * (1 - p)^s)
+}
+
+expected_series_streaks_of_outcomes <- function(m, n) {
+  factorial(m + n) / (factorial(m) * factorial(n))
+}
+
+summarize_streaks <- function(rounds, game = c('cod', 'val')) {
+  if (game == 'cod') {
+    .max_round <- 11
+    .adj <- 0
+  } else {
+    .max_round <- 25
+    .adj <- 1
+  }
+
+  cutoff <- (.max_round + 1) / 2
+
+  actual_round_streaks <- rounds |> 
+    filter(round <= (.max_round - .adj)) |> 
+    filter(win_series) |> 
+    mutate(across(win_round, as.integer)) |> 
+    group_by(series_id) |> 
+    summarize(
+      wins = max(cumu_w),
+      losses = max(cumu_l),
+      ws = paste0(win_round, collapse = '')
+    ) |> 
+    ungroup() |> 
+    mutate(n_rounds = wins + losses) |> 
+    unite(
+      record, wins, losses, sep = '-'
+    ) |>
+    count(record, n_rounds, ws, sort = TRUE) |> 
+    mutate(prop = n / sum(n))
+
+  expected_round_streaks <- tibble(
+    n_rounds = cutoff:.max_round
+  ) |> 
+    mutate(
+      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_n_games(.x, max_round = .max_round)),
+      n_expected_series_streaks = map2_dbl(cutoff, n_rounds - cutoff, expected_series_streaks_of_outcomes)
+    ) |> 
+    transmute(
+      n_rounds,
+      series_prop,
+      prop = series_prop / n_expected_series_streaks
+    )
+
+  round_streaks <- full_join(
+    actual_round_streaks |> 
+      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+    expected_round_streaks |> 
+      rename_with(~sprintf('%s_expected', .x), prop),
+    by = 'n_rounds'
+  )
+
+  round_streak_prop <- round_streaks |> 
+    drop_na() |> 
+    mutate(
+      prop_diff = prop_actual - prop_expected,
+      total_actual = sum(n_actual),
+      n_expected = round(prop_expected * total_actual),
+      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
+    ) |> 
+    select(-total_actual) |> 
+    unnest_wider(p) |> 
+    arrange(p.value)
+
+  series_outcomes <- full_join(
+    actual_round_streaks |> 
+      group_by(record, n_rounds) |> 
+      summarize(
+        across(n, sum)
+      ) |> 
+      ungroup() |> 
+      mutate(prop = n / sum(n)) |> 
+      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+    expected_round_streaks |> 
+      select(n_rounds, prop_expected = series_prop),
+    by = 'n_rounds'
+  )
+
+  series_outcome_prop <- series_outcomes |> 
+    drop_na() |> 
+    mutate(
+      prop_diff = prop_actual - prop_expected,
+      total_actual = sum(n_actual),
+      n_expected = round(prop_expected * total_actual),
+      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
+    ) |> 
+    select(-total_actual) |> 
+    unnest_wider(p) |> 
+    arrange(p.value)
+
+  list(
+    rounds = round_streak_prop,
+    series = series_outcome_prop
+  )
+}
+
+plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
+  if (game == 'cod') {
+    .lvls <- sprintf('6-%d', 0:5)
+    .axis_x_text_size <- 14
+  } else {
+    .lvls <- c(sprintf('13-%d', 0:11), '12-12')
+    .axis_x_text_size <- 12
+  }
+
+  long_series_outcome_prop <- series_outcome_prop |>
+    select(
+      record,
+      n = n_actual,
+      `3` = prop_actual,
+      `2` = prop_expected,
+      `1` = prop_diff
+    ) |> 
+    pivot_longer(
+      matches('[123]'),
+      names_to = 'outcome_idx',
+      values_to = 'value'
+    ) |> 
+    mutate(
+      across(outcome_idx, as.integer),
+      across(record, ~factor(.x, levels = .lvls))
+    )
+
+  max_diff_series_outcome_prop <- long_series_outcome_prop |> 
+    filter(outcome_idx == 1) |> 
+    pull(value) |> 
+    abs() |> 
+    max()
+
+  long_series_outcome_prop |> 
+    ggplot() +
+    aes(x = record, y = outcome_idx) +
+    geom_tile(
+      data = long_series_outcome_prop |> filter(outcome_idx > 1),
+      show.legend = FALSE,
+      # height = 0.8,
+      aes(fill = value)
+    ) +
+    ggsci::scale_fill_material(
+      palette = 'light-blue'
+    ) +
+    ggnewscale::new_scale_fill() +
+    geom_tile(
+      data = long_series_outcome_prop |> filter(outcome_idx == 1),
+      show.legend = FALSE,
+      height = 0.8,
+      aes(fill = value)
+    ) +
+    scale_fill_gradient2(
+      low = extract_ggsci_mid_color('purple'),
+      high = extract_ggsci_mid_color('green'),
+      mid = 'white',
+      midpoint = 0,
+      limits = c(
+        -max_diff_series_outcome_prop, 
+        +max_diff_series_outcome_prop
+      )
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 3),
+      color = blackish_background,
+      size = 11 / .pt,
+      aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 2),
+      color = blackish_background,
+      size = 11 / .pt,
+      aes(label = sprintf('%.1f%%', 100 * value))
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
+      color = blackish_background,
+      size = 11 / .pt,
+      aes(label = sprintf('%+.1f%%', 100 * value))
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
+      color = 'white',
+      size = 11 / .pt,
+      aes(label = sprintf('%+.1f%%', 100 * value))
+    ) +
+    scale_x_discrete(
+      position = 'top',
+      expand = c(0, 0)
+    ) +
+    scale_y_continuous(
+      labels = c('Diff.', 'Expected', 'Actual'),
+      breaks = 1:3,
+      expand = c(0, 0)
+    ) +
+    theme(
+      panel.grid.major = element_blank(),
+      axis.title = element_text(hjust = 0.5),
+      plot.title = ggtext::element_markdown(hjust = 0.5),
+      axis.text = element_text(size = 14, face = 'bold'),
+      axis.text.x = element_text(size = .axis_x_text_size, face = 'bold')
+    ) +
+    labs(
+      title = 'Series outcome %',
+      x = NULL,
+      y = NULL
+    )
+}
+
+cod_streaks_res <- cod_rounds |> summarize_streaks('cod')
+
+p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
+  plot_series_outcome_prop_over_expected('cod') +
+  common_cod_labs()
+p_cod_series_outcome_prop_over_expected
+save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
+```
+
+![](plots/cod_series_outcome_prop_over_expected.png){fig-align="center"}
+
 ## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
@@
 
+```{r}
+summarize_cod_win_prop_after_x_wins_y_rounds <- function(k) {
+  stopifnot((k >= 2) & (k <= 5))
+
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    round = 1L:10L
+  ) |> 
+    filter(round <= n_rounds) |> 
+    mutate(
+      prior_p = 6L / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  cols <- sprintf('won_prior_round%d', 2:k)
+  col_syms <- syms(cols)
+  cod_round_streaks_after_x <- cod_round_streaks |> 
+    drop_na(!!!col_syms) |> 
+    count(n_rounds, round, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+
+  cod_round_win_prop_after_x_wins <- cod_round_streaks_after_x |> 
+    filter(won_prior_round1, !!!col_syms)
+
+  cod_round_win_prop_after_x_wins |> 
+    group_by(n_rounds, round) |> 
+    mutate(
+      total = sum(n),
+      prop = n / total
+    ) |> 
+    ungroup() |> 
+    filter(win_round) |> 
+    select(n_rounds, round, n, total, prop) |> 
+    arrange(n_rounds, round) |> 
+    inner_join(
+      probs_nx_k,
+      by = c('n_rounds', 'round')
+    ) |> 
+    nest(data = -c(n_rounds, round)) |> 
+    mutate(
+      gt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      lt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
+          broom::tidy() |>
+          pull(p.value)
+      )
+    ) |> 
+    unnest(data)
+}
+
+cod_round_win_prop_after_x_wins_y_rounds <- tibble(win_streak = 2L:4L) |> 
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins_y_rounds)
+  ) |> 
+  unnest(data)
+save_qs(cod_round_win_prop_after_x_wins_y_rounds)
+```
+
 ## Is there evidence for the "hot hand" ([Valorant]{.valorant})?
@@
 ![](plots/val_o_win_r1_vs_post_round_prop.png){fig-align="center"}
-
-## What are the most common series winning states ([COD SnD]{.cod})?
-
-```{r}
-#| label: p_cod_series_outcome_prop_over_expected
-# https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422
-prob_of_series_lasting_n_games <- function(n, p = 0.5, max_round) {
-  s <- ceiling(max_round / 2)
-  (factorial(n - 1) / (factorial(s - 1) * factorial(n - s))) * (p^s * (1 - p)^(n - s) + p^(n - s) * (1 - p)^s)
-}
-
-expected_series_streaks_of_outcomes <- function(m, n) {
-  factorial(m + n) / (factorial(m) * factorial(n))
-}
-
-summarize_streaks <- function(rounds, game = c('cod', 'val')) {
-  if (game == 'cod') {
-    .max_round <- 11
-    .adj <- 0
-  } else {
-    .max_round <- 25
-    .adj <- 1
-  }
-
-  cutoff <- (.max_round + 1) / 2
-
-  actual_round_streaks <- rounds |> 
-    filter(round <= (.max_round - .adj)) |> 
-    filter(win_series) |> 
-    mutate(across(win_round, as.integer)) |> 
-    group_by(series_id) |> 
-    summarize(
-      wins = max(cumu_w),
-      losses = max(cumu_l),
-      ws = paste0(win_round, collapse = '')
-    ) |> 
-    ungroup() |> 
-    mutate(n_rounds = wins + losses) |> 
-    unite(
-      record, wins, losses, sep = '-'
-    ) |>
-    count(record, n_rounds, ws, sort = TRUE) |> 
-    mutate(prop = n / sum(n))
-
-  expected_round_streaks <- tibble(
-    n_rounds = cutoff:.max_round
-  ) |> 
-    mutate(
-      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_n_games(.x, max_round = .max_round)),
-      n_expected_series_streaks = map2_dbl(cutoff, n_rounds - cutoff, expected_series_streaks_of_outcomes)
-    ) |> 
-    transmute(
-      n_rounds,
-      series_prop,
-      prop = series_prop / n_expected_series_streaks
-    )
-
-  round_streaks <- full_join(
-    actual_round_streaks |> 
-      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-    expected_round_streaks |> 
-      rename_with(~sprintf('%s_expected', .x), prop),
-    by = 'n_rounds'
-  )
-
-  round_streak_prop <- round_streaks |> 
-    drop_na() |> 
-    mutate(
-      prop_diff = prop_actual - prop_expected,
-      total_actual = sum(n_actual),
-      n_expected = round(prop_expected * total_actual),
-      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
-    ) |> 
-    select(-total_actual) |> 
-    unnest_wider(p) |> 
-    arrange(p.value)
-
-  series_outcomes <- full_join(
-    actual_round_streaks |> 
-      group_by(record, n_rounds) |> 
-      summarize(
-        across(n, sum)
-      ) |> 
-      ungroup() |> 
-      mutate(prop = n / sum(n)) |> 
-      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
-    expected_round_streaks |> 
-      select(n_rounds, prop_expected = series_prop),
-    by = 'n_rounds'
-  )
-
-  series_outcome_prop <- series_outcomes |> 
-    drop_na() |> 
-    mutate(
-      prop_diff = prop_actual - prop_expected,
-      total_actual = sum(n_actual),
-      n_expected = round(prop_expected * total_actual),
-      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
-    ) |> 
-    select(-total_actual) |> 
-    unnest_wider(p) |> 
-    arrange(p.value)
-
-  list(
-    rounds = round_streak_prop,
-    series = series_outcome_prop
-  )
-}
-
-plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
-  if (game == 'cod') {
-    .lvls <- sprintf('6-%d', 0:5)
-    .axis_x_text_size <- 14
-  } else {
-    .lvls <- c(sprintf('13-%d', 0:11), '12-12')
-    .axis_x_text_size <- 12
-  }
-
-  long_series_outcome_prop <- series_outcome_prop |>
-    select(
-      record,
-      n = n_actual,
-      `3` = prop_actual,
-      `2` = prop_expected,
-      `1` = prop_diff
-    ) |> 
-    pivot_longer(
-      matches('[123]'),
-      names_to = 'outcome_idx',
-      values_to = 'value'
-    ) |> 
-    mutate(
-      across(outcome_idx, as.integer),
-      across(record, ~factor(.x, levels = .lvls))
-    )
-
-  max_diff_series_outcome_prop <- long_series_outcome_prop |> 
-    filter(outcome_idx == 1) |> 
-    pull(value) |> 
-    abs() |> 
-    max()
-
-  long_series_outcome_prop |> 
-    ggplot() +
-    aes(x = record, y = outcome_idx) +
-    geom_tile(
-      data = long_series_outcome_prop |> filter(outcome_idx > 1),
-      show.legend = FALSE,
-      # height = 0.8,
-      aes(fill = value)
-    ) +
-    ggsci::scale_fill_material(
-      palette = 'light-blue'
-    ) +
-    ggnewscale::new_scale_fill() +
-    geom_tile(
-      data = long_series_outcome_prop |> filter(outcome_idx == 1),
-      show.legend = FALSE,
-      height = 0.8,
-      aes(fill = value)
-    ) +
-    scale_fill_gradient2(
-      low = extract_ggsci_mid_color('purple'),
-      high = extract_ggsci_mid_color('green'),
-      mid = 'white',
-      midpoint = 0,
-      limits = c(
-        -max_diff_series_outcome_prop, 
-        +max_diff_series_outcome_prop
-      )
-    ) +
-    geom_text(
-      data = long_series_outcome_prop |> filter(outcome_idx == 3),
-      color = blackish_background,
-      size = 11 / .pt,
-      aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
-    ) +
-    geom_text(
-      data = long_series_outcome_prop |> filter(outcome_idx == 2),
-      color = blackish_background,
-      size = 11 / .pt,
-      aes(label = sprintf('%.1f%%', 100 * value))
-    ) +
-    geom_text(
-      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
-      color = blackish_background,
-      size = 11 / .pt,
-      aes(label = sprintf('%+.1f%%', 100 * value))
-    ) +
-    geom_text(
-      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
-      color = 'white',
-      size = 11 / .pt,
-      aes(label = sprintf('%+.1f%%', 100 * value))
-    ) +
-    scale_x_discrete(
-      position = 'top',
-      expand = c(0, 0)
-    ) +
-    scale_y_continuous(
-      labels = c('Diff.', 'Expected', 'Actual'),
-      breaks = 1:3,
-      expand = c(0, 0)
-    ) +
-    theme(
-      panel.grid.major = element_blank(),
-      axis.title = element_text(hjust = 0.5),
-      plot.title = ggtext::element_markdown(hjust = 0.5),
-      axis.text = element_text(size = 14, face = 'bold'),
-      axis.text.x = element_text(size = .axis_x_text_size, face = 'bold')
-    ) +
-    labs(
-      title = 'Series outcome %',
-      x = NULL,
-      y = NULL
-    )
-}
-
-cod_streaks_res <- cod_rounds |> summarize_streaks('cod')
-
-p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
-  plot_series_outcome_prop_over_expected('cod') +
-  common_cod_labs()
-p_cod_series_outcome_prop_over_expected
-save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
-```
-
-![](plots/cod_series_outcome_prop_over_expected.png){fig-align="center"}

### 2022-08-07 paper/paper.qmd
init paper

---
title: "They're Clutching up! Team Momentum in Round-Based Esports"
format:
  arxiv-pdf:
    keep-tex: true  
  arxiv-html: default
author:
  - name: Tony ElHabr
    affiliations:
      - name: Georgia Institute of Technology
    email: anthonyelhabr@gmail.com
    url: https://tonyelhabr.rbind.io
abstract: |
  My research investigates patterns in round win percentages in professional matches (series) of two popular first-person shooter games, Call of Duty (Search and Destroy mode) and Valorant.

  First, I find evidence in Call of Duty (COD) defying the naive hypothesis that a series represents a sequence of independent events (rounds), with each team having a constant 50% probability of winning a given round.

  Second, I examine post-streak round win probability. For COD, in which teams play first to 6 round wins (maximum 11 rounds), I find that teams perform significantly worse than expected after streaks of 2, 3, and 4 wins when series end up going to 9, 10, or 11 rounds, even after accounting for the "hot-hand" phenomenon. In Valorant, which requires one side to win 13 rounds for the series victory, there is evidence of performing better than expected after streaks of up to 8 wins, which is perhaps not shocking given the economy aspect of the game.

  Third, I compare win percentages in round one versus all other rounds, hypothesizing that there may be some advantage on either side when there is no prior information about how the opponent intends to play a given map in either game. I find one COD map for which there seems to be a significant defensive advantage in round one, but none otherwise.

  Finally, I evaluate behavior when teams have two rounds left to win the series, observing a peak in COD offensive win percentages in the 4-4 state, and no such oddity in Valorant.
keywords: 
  - esports
bibliography: bibliography.bib  
---

Sit nunc at convallis fringilla semper! Penatibus vivamus eget malesuada cursus fames magnis potenti. Venenatis ligula enim conubia laoreet orci class ligula? Massa sem sed enim risus ut mattis inceptos nisl elementum mattis. Nostra ultricies habitant donec vitae luctus proin gravida placerat ac libero imperdiet. Auctor habitasse faucibus ultricies purus eget sociis ultrices habitasse nec ad aptent lectus rutrum proin potenti montes sodales posuere convallis tempor erat egestas magna lectus sociis mollis purus.

Dolor turpis euismod himenaeos interdum felis dictum tempus euismod tortor aliquam? Eget interdum vehicula laoreet quam. Mollis justo cursus ad blandit feugiat pulvinar sem sodales bibendum. Leo leo magna pulvinar metus lacinia nam fringilla maecenas duis dis suscipit aenean natoque sem metus quam risus sagittis convallis primis sociis id dictumst.

# Introduction

Amet ultricies dignissim varius potenti suscipit justo phasellus dui ullamcorper luctus suscipit vulputate. Sagittis enim volutpat ultrices diam curabitur potenti platea euismod vel libero primis feugiat. Nibh potenti habitant ultricies dictum sociis class at vehicula eu vestibulum. Curabitur iaculis.

Consectetur est eleifend turpis morbi magna porttitor bibendum ut blandit aliquet lacus. Nostra iaculis torquent parturient id fermentum montes at himenaeos. Magna congue blandit fames egestas at inceptos? Id maecenas blandit maecenas accumsan ridiculus mollis nullam justo pulvinar elementum inceptos habitant risus.

{{< pagebreak >}}

# References {.unnumbered}

::: {#refs}
:::

### 2022-08-07 paper/paper.tex
init paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
]{article}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmathfont[]{Latin Modern Math}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={They're Clutching up! Team Momentum in Round-Based Esports},
  pdfauthor={Tony ElHabr},
  pdfkeywords={esports},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{They're Clutching up! Team Momentum in Round-Based Esports}
\author{
Tony ElHabr\\\\Georgia Institute of
Technology\\\\\href{mailto:anthonyelhabr@gmail.com}{anthonyelhabr@gmail.com}}
\date{}
\begin{document}
\maketitle
\begin{abstract}
My research investigates patterns in round win percentages in
professional matches (series) of two popular first-person shooter games,
Call of Duty (Search and Destroy mode) and Valorant.

First, I find evidence in Call of Duty (COD) defying the naive
hypothesis that a series represents a sequence of independent events
(rounds), with each team having a constant 50\% probability of winning a
given round.

Second, I examine post-streak round win probability. For COD, in which
teams play first to 6 round wins (maximum 11 rounds), I find that teams
perform significantly worse than expected after streaks of 2, 3, and 4
wins when series end up going to 9, 10, or 11 rounds, even after
accounting for the ``hot-hand'' phenomenon. In Valorant, which requires
one side to win 13 rounds for the series victory, there is evidence of
performing better than expected after streaks of up to 8 wins, which is
perhaps not shocking given the economy aspect of the game.

Third, I compare win percentages in round one versus all other rounds,
hypothesizing that there may be some advantage on either side when there
is no prior information about how the opponent intends to play a given
map in either game. I find one COD map for which there seems to be a
significant defensive advantage in round one, but none otherwise.

Finally, I evaluate behavior when teams have two rounds left to win the
series, observing a peak in COD offensive win percentages in the 4-4
state, and no such oddity in Valorant.
\end{abstract}
{\bfseries \emph Keywords}
\def\sep{\textbullet\ }

esports

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi

Sit nunc at convallis fringilla semper! Penatibus vivamus eget malesuada
cursus fames magnis potenti. Venenatis ligula enim conubia laoreet orci
class ligula? Massa sem sed enim risus ut mattis inceptos nisl elementum
mattis. Nostra ultricies habitant donec vitae luctus proin gravida
placerat ac libero imperdiet. Auctor habitasse faucibus ultricies purus
eget sociis ultrices habitasse nec ad aptent lectus rutrum proin potenti
montes sodales posuere convallis tempor erat egestas magna lectus sociis
mollis purus.

Dolor turpis euismod himenaeos interdum felis dictum tempus euismod
tortor aliquam? Eget interdum vehicula laoreet quam. Mollis justo cursus
ad blandit feugiat pulvinar sem sodales bibendum. Leo leo magna pulvinar
metus lacinia nam fringilla maecenas duis dis suscipit aenean natoque
sem metus quam risus sagittis convallis primis sociis id dictumst.

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Amet ultricies dignissim varius potenti suscipit justo phasellus dui
ullamcorper luctus suscipit vulputate. Sagittis enim volutpat ultrices
diam curabitur potenti platea euismod vel libero primis feugiat. Nibh
potenti habitant ultricies dictum sociis class at vehicula eu
vestibulum. Curabitur iaculis.

Consectetur est eleifend turpis morbi magna porttitor bibendum ut
blandit aliquet lacus. Nostra iaculis torquent parturient id fermentum
montes at himenaeos. Magna congue blandit fames egestas at inceptos? Id
maecenas blandit maecenas accumsan ridiculus mollis nullam justo
pulvinar elementum inceptos habitant risus.

\newpage{}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{0}{0}
\end{CSLReferences}

\end{document}

### 2022-08-07 presentation.qmd
move vectorized_prop_test, p_cod_round_win_prop_after_x_wins_y_rounds

--- 2022-08-05 presentation.qmd
@@
 
+## What are the most common series winning states ([COD SnD]{.cod})?
+
+```{r}
+#| label: p_cod_series_outcome_prop_over_expected
+# https://content.iospress.com/articles/journal-of-sports-analytics/jsa200422
+prob_of_series_lasting_n_games <- function(n, p = 0.5, max_round) {
+  s <- ceiling(max_round / 2)
+  (factorial(n - 1) / (factorial(s - 1) * factorial(n - s))) * (p^s * (1 - p)^(n - s) + p^(n - s) * (1 - p)^s)
+}
+
+expected_series_streaks_of_outcomes <- function(m, n) {
+  factorial(m + n) / (factorial(m) * factorial(n))
+}
+
+# https://raw.githubusercontent.com/dgrtwo/splittestr/master/R/vectorized-prop-test.R
+vectorized_prop_test_approx <- function(a, b, c, d) {
+  n1 <- a + b
+  n2 <- c + d
+  n <- n1 + n2
+  p <- (a + c) / n
+  E <- cbind(p * n1, (1 - p) * n1, p * n2, (1 - p) * n2)
+
+  x <- cbind(a, b, c, d)
+
+  DELTA <- a / n1 - c / n2
+  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
+
+  STATISTIC <- rowSums((abs(x - E) - YATES)^2 / E)
+  PVAL <- pchisq(STATISTIC, 1, lower.tail = FALSE)
+  PVAL
+}
+
+vectorized_prop_test_exact <- function(a, b, c, d) {
+  sapply(seq_along(a), function(i) {
+    fisher.test(cbind(c(a[i], c[i]), c(b[i], d[i])))$p.value
+  })
+}
+
+vectorized_prop_test <- function(x1, n1, x2, n2, conf.level = .95) {
+  a <- x1
+  b <- n1 - x1
+  c <- x2
+  d <- n2 - x2
+
+  # if any values are < 20, use Fisher's exact test
+  exact <- (a < 20 | b < 20 | c < 20 | d < 20)
+
+  pvalue <- rep(NA, length(a))
+
+  if (any(exact)) {
+    pvalue[exact] <- vectorized_prop_test_exact(a[exact], b[exact], c[exact], d[exact])
+  }
+  if (any(!exact)) {
+    pvalue[!exact] <- vectorized_prop_test_approx(a[!exact], b[!exact], c[!exact], d[!exact])
+  }
+
+  mu1 <- a / (a + b)
+  mu2 <- c / (c + d)
+
+  ## confidence interval
+  alpha2 <- (1 - conf.level) / 2
+  DELTA <- mu2 - mu1
+  WIDTH <- qnorm(alpha2)
+  alpha <- (a + .5) / (a + b + 1)
+  beta <- (c + .5) / (c + d + 1)
+
+  n <- n1 + n2
+  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
+
+  z <- qnorm((1 + conf.level) / 2)
+  WIDTH <- z * sqrt(mu1 * (1 - mu1) / n1 + mu2 * (1 - mu2) / n2)
+
+  tibble(
+    estimate = DELTA,
+    conf.low = pmax(DELTA - WIDTH, -1),
+    conf.high = pmin(DELTA + WIDTH, 1),
+    p.value = pvalue
+  )
+}
+
+summarize_streaks <- function(rounds, game = c('cod', 'val')) {
+  if (game == 'cod') {
+    .max_round <- 11
+    .adj <- 0
+  } else {
+    .max_round <- 25
+    .adj <- 1
+  }
+
+  cutoff <- (.max_round + 1) / 2
+
+  actual_round_streaks <- rounds |> 
+    filter(round <= (.max_round - .adj)) |> 
+    filter(win_series) |> 
+    mutate(across(win_round, as.integer)) |> 
+    group_by(series_id) |> 
+    summarize(
+      wins = max(cumu_w),
+      losses = max(cumu_l),
+      ws = paste0(win_round, collapse = '')
+    ) |> 
+    ungroup() |> 
+    mutate(n_rounds = wins + losses) |> 
+    unite(
+      record, wins, losses, sep = '-'
+    ) |>
+    count(record, n_rounds, ws, sort = TRUE) |> 
+    mutate(prop = n / sum(n))
+
+  expected_round_streaks <- tibble(
+    n_rounds = cutoff:.max_round
+  ) |> 
+    mutate(
+      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_n_games(.x, max_round = .max_round)),
+      n_expected_series_streaks = map2_dbl(cutoff, n_rounds - cutoff, expected_series_streaks_of_outcomes)
+    ) |> 
+    transmute(
+      n_rounds,
+      series_prop,
+      prop = series_prop / n_expected_series_streaks
+    )
+
+  round_streaks <- full_join(
+    actual_round_streaks |> 
+      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+    expected_round_streaks |> 
+      rename_with(~sprintf('%s_expected', .x), prop),
+    by = 'n_rounds'
+  )
+
+  round_streak_prop <- round_streaks |> 
+    drop_na() |> 
+    mutate(
+      prop_diff = prop_actual - prop_expected,
+      total_actual = sum(n_actual),
+      n_expected = round(prop_expected * total_actual),
+      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
+    ) |> 
+    select(-total_actual) |> 
+    unnest_wider(p) |> 
+    arrange(p.value)
+
+  series_outcomes <- full_join(
+    actual_round_streaks |> 
+      group_by(record, n_rounds) |> 
+      summarize(
+        across(n, sum)
+      ) |> 
+      ungroup() |> 
+      mutate(prop = n / sum(n)) |> 
+      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+    expected_round_streaks |> 
+      select(n_rounds, prop_expected = series_prop),
+    by = 'n_rounds'
+  )
+
+  series_outcome_prop <- series_outcomes |> 
+    drop_na() |> 
+    mutate(
+      prop_diff = prop_actual - prop_expected,
+      total_actual = sum(n_actual),
+      n_expected = round(prop_expected * total_actual),
+      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
+    ) |> 
+    select(-total_actual) |> 
+    unnest_wider(p) |> 
+    arrange(p.value)
+
+  list(
+    rounds = round_streak_prop,
+    series = series_outcome_prop
+  )
+}
+
+plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
+  if (game == 'cod') {
+    .lvls <- sprintf('6-%d', 0:5)
+    .axis_x_text_size <- 14
+  } else {
+    .lvls <- c(sprintf('13-%d', 0:11), '12-12')
+    .axis_x_text_size <- 12
+  }
+
+  long_series_outcome_prop <- series_outcome_prop |>
+    select(
+      record,
+      n = n_actual,
+      `3` = prop_actual,
+      `2` = prop_expected,
+      `1` = prop_diff
+    ) |> 
+    pivot_longer(
+      matches('[123]'),
+      names_to = 'outcome_idx',
+      values_to = 'value'
+    ) |> 
+    mutate(
+      across(outcome_idx, as.integer),
+      across(record, ~factor(.x, levels = .lvls))
+    )
+
+  max_diff_series_outcome_prop <- long_series_outcome_prop |> 
+    filter(outcome_idx == 1) |> 
+    pull(value) |> 
+    abs() |> 
+    max()
+
+  long_series_outcome_prop |> 
+    ggplot() +
+    aes(x = record, y = outcome_idx) +
+    geom_tile(
+      data = long_series_outcome_prop |> filter(outcome_idx > 1),
+      show.legend = FALSE,
+      # height = 0.8,
+      aes(fill = value)
+    ) +
+    ggsci::scale_fill_material(
+      palette = 'light-blue'
+    ) +
+    ggnewscale::new_scale_fill() +
+    geom_tile(
+      data = long_series_outcome_prop |> filter(outcome_idx == 1),
+      show.legend = FALSE,
+      height = 0.8,
+      aes(fill = value)
+    ) +
+    scale_fill_gradient2(
+      low = extract_ggsci_mid_color('purple'),
+      high = extract_ggsci_mid_color('green'),
+      mid = 'white',
+      midpoint = 0,
+      limits = c(
+        -max_diff_series_outcome_prop, 
+        +max_diff_series_outcome_prop
+      )
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 3),
+      color = blackish_background,
+      size = 11 / .pt,
+      aes(label = sprintf('%.1f%%\n(%s)', 100 * value, scales::comma(n)))
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 2),
+      color = blackish_background,
+      size = 11 / .pt,
+      aes(label = sprintf('%.1f%%', 100 * value))
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) != max(abs(value))),
+      color = blackish_background,
+      size = 11 / .pt,
+      aes(label = sprintf('%+.1f%%', 100 * value))
+    ) +
+    geom_text(
+      data = long_series_outcome_prop |> filter(outcome_idx == 1) |> filter(abs(value) == max(abs(value))),
+      color = 'white',
+      size = 11 / .pt,
+      aes(label = sprintf('%+.1f%%', 100 * value))
+    ) +
+    scale_x_discrete(
+      position = 'top',
+      expand = c(0, 0)
+    ) +
+    scale_y_continuous(
+      labels = c('Diff.', 'Expected', 'Actual'),
+      breaks = 1:3,
+      expand = c(0, 0)
+    ) +
+    theme(
+      panel.grid.major = element_blank(),
+      axis.title = element_text(hjust = 0.5),
+      plot.title = ggtext::element_markdown(hjust = 0.5),
+      axis.text = element_text(size = 14, face = 'bold'),
+      axis.text.x = element_text(size = .axis_x_text_size, face = 'bold')
+    ) +
+    labs(
+      title = 'Series outcome %',
+      x = NULL,
+      y = NULL
+    )
+}
+
+cod_streaks_res <- cod_rounds |> summarize_streaks('cod')
+
+p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
+  plot_series_outcome_prop_over_expected('cod') +
+  common_cod_labs()
+p_cod_series_outcome_prop_over_expected
+save_plot_for_slide(p_cod_series_outcome_prop_over_expected)
+```
+
+![](plots/cod_series_outcome_prop_over_expected.png){fig-align="center"}
+
 ## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
@@
 #| label: cod_series_outcomes_chi
-
 cod_rounds_per_series <- cod_streaks_res$series |>
@@
 cod_n7adj <- round(10 * cod_n7 / cod_pm)
-cod_n8adj <- round(10 * cod_n8 / cod_)
+cod_n8adj <- round(10 * cod_n8 / cod_pm)
 cod_n9adj <- round(10 * cod_n9 / cod_pm)
@@
 ![](plots/val_series_outcome_prop_over_expected.png)
+
+There's a clear bias towards shorter series than expected.
 
@@
 
+arw <- arrow(length = unit(5, 'pt'), type = 'closed')
+
 p_cod_b2b_round_win_prop <- cod_b2b_round_win_prop |> 
@@
 }
-
 ```
@@
 
-summarize_cod_win_prop_after_x_wins <- function(k) {
-  stopifnot((k >= 2) & (k <= 5))
-
-  probs_nx_k <- tibble(
-    n_rounds = 7L:11L
-  ) |> 
-    mutate(
-      prior_p = 6L / n_rounds,
-      expected_poststreak_p = map2_dbl(
-        n_rounds, prior_p, 
-        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
-      )
-    )
+.postprocess_round_streaks <- function(k, round_streaks, probs_nx_k, ...) {
 
@@
   col_syms <- syms(cols)
-  cod_round_streaks_after_x <- cod_round_streaks |> 
+  round_streaks_after_x <- round_streaks |> 
     drop_na(!!!col_syms) |> 
-    count(n_rounds, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
-
-  cod_round_win_prop_after_x_wins <- cod_round_streaks_after_x |> 
+    count(n_rounds, ..., win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+
+  round_win_prop_after_x_wins <- round_streaks_after_x |> 
     filter(won_prior_round1, !!!col_syms)
 
-  cod_round_win_prop_after_x_wins |> 
-    group_by(n_rounds) |> 
+  round_win_prop_after_x_wins |> 
+    group_by(n_rounds, ...) |> 
     mutate(
@@
     filter(win_round) |> 
-    select(n_rounds, n, total, prop) |> 
-    arrange(n_rounds) |> 
+    select(n_rounds, ..., n, total, prop) |> 
+    arrange(n_rounds, ...) |> 
     inner_join(
-      probs_nx_k,
-      by = 'n_rounds'
-    ) |> 
-    nest(data = -c(n_rounds)) |> 
+      probs_nx_k
+    ) |> 
+    nest(data = -c(n_rounds, ...)) |> 
     mutate(
@@
           pull(p.value)
+      ),
+      gt_is_signif = gt_p_value <= 0.05,
+      lt_is_signif = lt_p_value <= 0.05,
+      is_signif = case_when(
+        gt_is_signif ~ 'Better',
+        lt_is_signif ~ 'Worse',
+        TRUE ~ 'Neither'
       )
@@
     unnest(data)
+}
+
+summarize_cod_win_prop_after_x_wins <- function(k) {
+  probs_nx_k <- tibble(
+    n_rounds = 7L:11L
+  ) |> 
+    mutate(
+      prior_p = 6L / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  .postprocess_round_streaks(
+    k = k,
+    round_streaks = cod_round_streaks,
+    probs_nx_k = probs_nx_k
+  )
 }
@@
 ```{r}
-#| label: cod_round_win_prop_after_x_wins-eval
-#| eval: true
+#| label: cod_round_win_prop_after_x_wins_and_rounds
+summarize_cod_win_prop_after_x_wins_y_rounds <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    round = 3L:11L
+  ) |> 
+    filter(round >= (k + 1L)) |> 
+    mutate(
+      prior_p = 6L / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  .postprocess_round_streaks(
+    k = k,
+    round_streaks = cod_round_streaks,
+    probs_nx_k = probs_nx_k,
+    round
+  )
+}
+
+cod_round_win_prop_after_x_wins_and_rounds <- tibble(win_streak = 2L:4L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins_and_rounds)
+  ) |>
+  unnest(data)
+save_qs(cod_round_win_prop_after_x_wins_and_rounds)
+```
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins-table
+#| eval: false
 load_qs('cod_round_win_prop_after_x_wins')
@@
   knitr::kable()
-
+```
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins-plot
+load_qs('cod_round_win_prop_after_x_wins')
+
+ggsci_grey <- extract_ggsci_mid_color('grey')
+p_cod_round_win_prop_after_x_wins <- cod_round_win_prop_after_x_wins |> 
+  ggplot() +
+  geom_tile(
+    color = blackish_background,
+    height = 0.8,
+    aes(
+      fill = lt_is_signif,
+      y = win_streak + 0.5, 
+      x = n_rounds + 0.5
+    )
+  ) +
+  geom_richtext(
+    fill = NA_character_,
+    label.color = NA_character_,
+    family = font,
+    color = blackish_background,
+    size = 11 / .pt,
+    fontface = 'bold',
+    aes(
+      label = sprintf(
+        '%s %s <span style="color:white">%s</span><br/>(%s)',
+        scales::percent(prop, accuracy = 1), 
+        case_when(
+          round(prop, 1) == round(expected_poststreak_p, 1) ~ '=',
+          prop >= expected_poststreak_p ~ '>=', 
+          TRUE ~ '<'
+        ),
+        scales::percent(expected_poststreak_p, accuracy = 1),
+        scales::comma(n)
+      ),
+      y = win_streak + 0.5, 
+      x = n_rounds + 0.5
+    )
+  ) +
+  guides(
+    fill = guide_legend(
+      'Significantly less than expected?'
+    )
+  ) +
+  scale_y_continuous(
+    labels = 2:4,
+    breaks = seq(2.5, 4.5, by = 1),
+    expand = c(0, 0.5)
+  ) +
+  scale_x_continuous(
+    labels = 7:11,
+    breaks = seq(7.5, 11.5, by = 1),
+    expand = c(0, 0)
+  ) +
+  scale_fill_manual(
+    values = c(ggsci_grey, ggsci_cyan),
+    labels = c('No', 'Yes')
+  ) +
+  theme(
+    legend.position = 'top',
+    legend.text = element_text(color = 'white', size = 12),
+    panel.grid.major = element_blank(),
+    axis.title = element_text(hjust = 0.5),
+    plot.title = ggtext::element_markdown(hjust = 0.5),
+    axis.text = element_text(size = 16, face = 'bold')
+  ) +
+  common_cod_labs() +
+  labs(
+    title = 'Post win streak round win %',
+    y = 'Win streak length',
+    x = '# of rounds played in series'
+  ) +
+  geom_curve(
+    data = data.frame(),
+    color = 'white',
+    arrow = arw,
+    curvature = 0.1,
+    aes(
+      x = 7.8,
+      y = 5.11,
+      xend = 7.7,
+      yend = 4.8
+    )
+  ) +
+  geom_text(
+    data = data.frame(),
+    hjust = 0,
+    vjust = 0.5,
+    color = 'white',
+    size = 12 / .pt,
+    aes(
+      label = 'Expected %',
+      x = 7.81,
+      y = 5.12
+    )
+  ) +
+  geom_curve(
+    data = data.frame(),
+    color = 'white',
+    arrow = arw,
+    curvature = 0.25,
+    aes(
+      x = 7.8,
+      y = 5.41,
+      xend = 7.3,
+      yend = 4.8
+    )
+  ) +
+  geom_text(
+    data = data.frame(),
+    hjust = 0,
+    vjust = 0.5,
+    color = 'white',
+    size = 12 / .pt,
+    aes(
+      label = 'Actual %',
+      x = 7.81,
+      y = 5.42
+    )
+  )
+p_cod_round_win_prop_after_x_wins
+save_plot_for_slide(p_cod_round_win_prop_after_x_wins)
 ```
@@
 ::: fragment
+![](plots/cod_round_win_prop_after_x_wins.png)
+
 -   There is no evidence for momentum, for both streaks of 2 and 3.
@@
 :::
+
+```{r}
+load_qs('cod_round_win_prop_after_x_wins')
+ggsci_orange <- extract_ggsci_mid_color('orange')
+p_cod_round_win_prop_after_x_wins_y_rounds <- cod_round_win_prop_after_x_wins_y_rounds |> 
+  mutate(
+    is_signif = case_when(
+      gt_is_signif ~ 'Better',
+      lt_is_signif ~ 'Worse',
+      TRUE ~ 'Neither'
+    )
+  ) |> 
+  # filter(win_streak %in% c(3, 4)) |> 
+  # filter(n >= 20) |> 
+  ggplot() +
+  geom_tile(
+    color = blackish_background,
+    height = 0.8,
+    aes(
+      fill = is_signif,
+      x = round + 0.5, 
+      y = n_rounds + 0.5
+    )
+  ) +
+  geom_richtext(
+    fill = NA_character_,
+    label.color = NA_character_,
+    family = font,
+    color = blackish_background,
+    size = 11 / .pt,
+    fontface = 'bold',
+    aes(
+      label = sprintf(
+        '%s %s <span style="color:white">%s</span><br/>(%s)',
+        scales::percent(prop, accuracy = 1), 
+        case_when(
+          round(prop, 1) == round(expected_poststreak_p, 1) ~ '=',
+          prop >= expected_poststreak_p ~ '>=', 
+          TRUE ~ '<'
+        ),
+        scales::percent(expected_poststreak_p, accuracy = 1),
+        scales::comma(n)
+      ),
+      x = round + 0.5, 
+      y = n_rounds + 0.5
+    )
+  ) +
+  guides(
+    fill = guide_legend(
+      'Significantly better/worse?'
+    )
+  ) +
+  scale_x_continuous(
+    labels = 4:11,
+    breaks = seq(4.5, 11.5, by = 1),
+    expand = c(0, 0.5)
+  ) +
+  scale_y_continuous(
+    labels = 7:11,
+    breaks = seq(7.5, 11.5, by = 1),
+    expand = c(0, 0)
+  ) +
+  scale_fill_manual(
+    values = c(ggsci_cyan, ggsci_grey, ggsci_orange),
+    labels = c('Better', 'Neither', 'Worse')
+  ) +
+  theme(
+    legend.position = 'top',
+    legend.text = element_text(color = 'white', size = 12),
+    panel.grid.major = element_blank(),
+    axis.title = element_text(hjust = 0.5),
+    plot.title = ggtext::element_markdown(hjust = 0.5),
+    axis.text = element_text(size = 16, face = 'bold')
+  ) +
+  common_cod_labs() +
+  labs(
+    title = 'Post win streak round win %',
+    x = 'Round',
+    y = '# of rounds played in series'
+  ) +
+  facet_wrap(~win_streak)
+p_cod_round_win_prop_after_x_wins_y_rounds
+```
 
@@
 #| label: p_cod_o_win_r1_vs_post_round_prop
-# https://raw.githubusercontent.com/dgrtwo/splittestr/master/R/vectorized-prop-test.R
-vectorized_prop_test_approx <- function(a, b, c, d) {
-  n1 <- a + b
-  n2 <- c + d
-  n <- n1 + n2
-  p <- (a + c) / n
-  E <- cbind(p * n1, (1 - p) * n1, p * n2, (1 - p) * n2)
-
-  x <- cbind(a, b, c, d)
-
-  DELTA <- a / n1 - c / n2
-  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
-
-  STATISTIC <- rowSums((abs(x - E) - YATES)^2 / E)
-  PVAL <- pchisq(STATISTIC, 1, lower.tail = FALSE)
-  PVAL
-}
-
-vectorized_prop_test_exact <- function(a, b, c, d) {
-  sapply(seq_along(a), function(i) {
-    fisher.test(cbind(c(a[i], c[i]), c(b[i], d[i])))$p.value
-  })
-}
-
-vectorized_prop_test <- function(x1, n1, x2, n2, conf.level = .95) {
-  a <- x1
-  b <- n1 - x1
-  c <- x2
-  d <- n2 - x2
-
-  # if any values are < 20, use Fisher's exact test
-  exact <- (a < 20 | b < 20 | c < 20 | d < 20)
-
-  pvalue <- rep(NA, length(a))
-
-  if (any(exact)) {
-    pvalue[exact] <- vectorized_prop_test_exact(a[exact], b[exact], c[exact], d[exact])
-  }
-  if (any(!exact)) {
-    pvalue[!exact] <- vectorized_prop_test_approx(a[!exact], b[!exact], c[!exact], d[!exact])
-  }
-
-  mu1 <- a / (a + b)
-  mu2 <- c / (c + d)
-
-  ## confidence interval
-  alpha2 <- (1 - conf.level) / 2
-  DELTA <- mu2 - mu1
-  WIDTH <- qnorm(alpha2)
-  alpha <- (a + .5) / (a + b + 1)
-  beta <- (c + .5) / (c + d + 1)
-
-  n <- n1 + n2
-  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
-
-  z <- qnorm((1 + conf.level) / 2)
-  WIDTH <- z * sqrt(mu1 * (1 - mu1) / n1 + mu2 * (1 - mu2) / n2)
-
-  tibble(
-    estimate = DELTA,
-    conf.low = pmax(DELTA - WIDTH, -1),
-    conf.high = pmin(DELTA + WIDTH, 1),
-    p.value = pvalue
-  )
-}
-
 calculate_map_o_round_win_prop <- function(df) {
@@
 )
-
-arw <- arrow(length = unit(5, 'pt'), type = 'closed')
 

### 2022-08-07 paper/paper.tex
do a test render

@@
   \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-  \setmathfont[]{Latin Modern Math}
 \fi
@@
   pdfauthor={Tony ElHabr},
-  pdfkeywords={esports},
   colorlinks=true,
@@
 \end{abstract}
-{\bfseries \emph Keywords}
-\def\sep{\textbullet\ }
-
-esports
-
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, frame hidden, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable, boxrule=0pt]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden]}{\end{tcolorbox}}\fi
 

### 2022-08-12 paper/paper.qmd
do a test render
paper

@@
 abstract: |
-  My research investigates patterns in round win percentages in professional matches (series) of two popular first-person shooter games, Call of Duty (Search and Destroy mode) and Valorant.
+  My research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).
 
-  First, I find evidence in Call of Duty (COD) defying the naive hypothesis that a series represents a sequence of independent events (rounds), with each team having a constant 50% probability of winning a given round.
+  First, I find evidence in CoD defying the naive hypothesis that a series represents a sequence of independent events (rounds), with each team having a constant 50% probability of winning a given round.
 
   Second, I examine post-streak round win probability.
-For COD, in which teams play first to 6 round wins (maximum 11 rounds), I find that teams perform significantly worse than expected after streaks of 2, 3, and 4 wins when series end up going to 9, 10, or 11 rounds, even after accounting for the "hot-hand" phenomenon.
-In Valorant, which requires one side to win 13 rounds for the series victory, there is evidence of performing better than expected after streaks of up to 8 wins, which is perhaps not shocking given the economy aspect of the game.
+I find that teams perform significantly worse than expected after streaks of 2, 3, and 4 wins when series end up going to 9, 10, or 11 (maximum) rounds, even after accounting for the "hot-hand" phenomenon.
 
   Third, I compare win percentages in round one versus all other rounds, hypothesizing that there may be some advantage on either side when there is no prior information about how the opponent intends to play a given map in either game.
-I find one COD map for which there seems to be a significant defensive advantage in round one, but none otherwise.
+I find only one instance for which there seems to be a significant defensive advantage in round one.
 
   Finally, I evaluate behavior when teams have two rounds left to win the series, observing a peak in COD offensive win percentages in the 4-4 state, and no such oddity in Valorant.
-keywords: 
-  - esports
-bibliography: bibliography.bib  
+bibliography: references.bib  
 ---
 
-Sit nunc at convallis fringilla semper!
-Penatibus vivamus eget malesuada cursus fames magnis potenti.
-Venenatis ligula enim conubia laoreet orci class ligula?
-Massa sem sed enim risus ut mattis inceptos nisl elementum mattis.
-Nostra ultricies habitant donec vitae luctus proin gravida placerat ac libero imperdiet.
-Auctor habitasse faucibus ultricies purus eget sociis ultrices habitasse nec ad aptent lectus rutrum proin potenti montes sodales posuere convallis tempor erat egestas magna lectus sociis mollis purus.
+# 1. Introduction
 
-Dolor turpis euismod himenaeos interdum felis dictum tempus euismod tortor aliquam?
-Eget interdum vehicula laoreet quam.
-Mollis justo cursus ad blandit feugiat pulvinar sem sodales bibendum.
-Leo leo magna pulvinar metus lacinia nam fringilla maecenas duis dis suscipit aenean natoque sem metus quam risus sagittis convallis primis sociis id dictumst.
+## 1.1 Description of Call of Duty Search and Destroy
 
-# Introduction
+Call of Duty (CoD), first released in 2003, is one of the most popular first-person shooter (FPS) video game franchises of all-time.
+Tthe most popular mode in the competitive scene is "Search and Destroy" (SnD), which bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in professional leagues.
+SnD is one-sided game mode in which one team, the offensive side, tries to destroy one of two designated bomb sites on the map.[^1]
 
-Amet ultricies dignissim varius potenti suscipit justo phasellus dui ullamcorper luctus suscipit vulputate.
-Sagittis enim volutpat ultrices diam curabitur potenti platea euismod vel libero primis feugiat.
-Nibh potenti habitant ultricies dictum sociis class at vehicula eu vestibulum.
-Curabitur iaculis.
+[^1]: as
 
-Consectetur est eleifend turpis morbi magna porttitor bibendum ut blandit aliquet lacus.
-Nostra iaculis torquent parturient id fermentum montes at himenaeos.
-Magna congue blandit fames egestas at inceptos?
-Id maecenas blandit maecenas accumsan ridiculus mollis nullam justo pulvinar elementum inceptos habitant risus.
+In professional CoD, a team must win six rounds of SnD to win the match.[^2] A round can end in one of four ways:
 
-{{< pagebreak >}}
+[^2]: A maximum of 11 even rounds can be played. There is no "sudden death" or "win by two" rule like there are for SnD equivalent in professional Counter-Strike and Valorant matches.
+
+1.  One team eliminates all members of the other team prior to a bomb plant. (Eliminating team wins.)
+2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^3] (Offense wins.)
+3.  The defensive team defuses the bomb after a bomb plant.[^4] (Defense wins.)
+4.  The offensive team does not make a plant by the time the round timer ends. (Defense wins.)
+
+[^3]:
+    -   The bomb can be picked up by any member of the offensive team.
+    -   The bomb carrier is not obstructed at all by carrying the bomb (i.e. movement is the same, weapon usage is the same).
+    -   The defense does not get any visual indication for who is carrying the bomb.
+    -   A bomb plant takes five seconds. The timer resets if the player stops planting site prior to completing it.
+    -   A bomb defuse takes seven seconds. The timer resets if the player "drops" the bomb.
+    -   The bomb takes 45 seconds to defuse after being planted.
+
+[^4]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+
+Teams take turns playing offense and defense every round.
+
+## 1.2 Data
+
+CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.
+The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era.
+Data was collected in spreadsheets by community member "IOUTurtle".[^5]
+
+[^5]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle
+
+I adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
+A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
+
+CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, where a new game is published every year under the same title.
+Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
+The data set denotes which CoD game a given CoD SnD series was played,
+
+## 1.3 My contribution
+
+# 2 Literature review
+
+Streaks and momentum is one of the most frequently published topics in sports analytics.
+We often use these interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+When considering
+
+Despite the plethora of existing research on momentum in sports, its yet to be investigated heavily in esports. [@article-journal]
 

### 2022-08-12 1-scrape-cod.R
cod champs data

@@ -27,11 +27,6 @@ generate_cod_sheets <- function(year = c('2021', '2022')) {
       label = sprintf('S%d %s', s, ifelse(series == 4, 'Major', sprintf('%s%d', !!prefix, series)))
     ) |> 
     pull(label)
-  
-  if(is_2022) {
-    return(labs)
-  }
-  
   c('Champs', labs)
 }
 

### 2022-08-12 presentation.qmd
rm val from pres

@@
 cod_rounds <- qs::qread('cod_rounds.qs')
-val_rounds <- qs::qread('valorant_rounds.qs')
 ```
@@
 update_geom_defaults('segment', list(color = 'white'))
-
-add_logo <- function(
-    path,
-    path_logo,
-    idx_x,
-    idx_y,
-    logo_scale = 0.1,
-    adjust_x = TRUE,
-    adjust_y = TRUE,
-    path_suffix = '_w_logo',
-    delete = TRUE
-) {
-
-  plot <- magick::image_read(path)
-  logo_raw <- magick::image_read(path_logo)
-
-  plot_height <- magick::image_info(plot)$height
-  plot_width <- magick::image_info(plot)$width
-
-  logo <- magick::image_scale(logo_raw, as.character(round(plot_width * logo_scale)))
-
-  info <- magick::image_info(logo)
-  logo_width <- info$width
-  logo_height <- info$height
-
-  x_pos <- plot_width - idx_x * plot_width
-  y_pos <- plot_height - idx_y * plot_height
-
-  if (adjust_x) {
-    x_pos <- x_pos - logo_width
-  }
-
-  if (adjust_y) {
-    y_pos <- y_pos - logo_height
-  }
-
-  offset <- paste0('+', x_pos, '+', y_pos)
-
-  img <- magick::image_composite(plot, logo, offset = offset)
-  ext <- tools::file_ext(path)
-  rgx_ext <- sprintf('[.]%s$', ext)
-
-  res <- magick::image_write(
-    img,
-    gsub(rgx_ext, sprintf('%s.%s', path_suffix, ext), path)
-  )
-
-  if (!delete) {
-    return(res)
-  }
-  unlink(path, recursive = TRUE, force = TRUE)
-  res
-}
-
-```
-
-## Game types
+```
+
+## Search and Destroy (SnD) in Call of Duty (CoD)
 
 ::: fragment
-### Search and Destroy (SnD) in Call of Duty (COD)
-
 -   2020-2022 Call of Duty League (CDL) matches (qualifiers and majors)
@@
 
-<br/>
-
-::: fragment
-### A Plant/Defuse in Valorant
-
--   2021 Valorant Champions Tour (VCT) matches (qualifiers and majors)
--   5v5
--   First to 13 round wins
--   One team plays offense in 12 consecutive rounds before swapping sides
--   Must win by 2 rounds
-:::
-
-## How does a team win a round of COD SnD / Valorant plant/defuse?
+## How does a team win a round of CoD SnD ?
 
@@
 
-## COD SnD data overview
+## CoD SnD data overview
 
@@
 
-## Valorant data overview
-
-```{r}
-#| label: descriptive-val-snd-stats
-#| eval: true
-val_n_series <- val_rounds |> 
-  distinct(series_id) |> 
-  nrow() |> 
-  scales::comma()
-
-val_n_rounds <- val_rounds |> 
-  distinct(series_id, round) |> 
-  nrow() |> 
-  scales::comma()
-
-val_o_win_prop_const <- val_rounds |> 
-  filter(is_offense) |> 
-  count(win_round) |> 
-  mutate(prop = n / sum(n)) |> 
-  filter(win_round) |> 
-  pull(prop)
-val_o_win_pct <- scales::percent(val_o_win_prop_const, accuracy = 0.1)
-```
-
-::: fragment
--   Total series: **`r val_n_series`**
-:::
-
-::: fragment
--   Total rounds: **`r val_n_rounds`**
-:::
-
-::: fragment
--   Offensive win %: **`r val_o_win_pct`**
-:::
-
-## What are your chances of winning the next round ([COD SnD]{.cod})?
+## What are your chances of winning the next round?
 
@@
 #| label: cod-funcs
-
 common_cod_labs <- function(...) {
@@
     labs(
-      caption = 'CDL SnD Major and Weekly matches, 2020 - present'
+      caption = 'CDL SnD major and qualifier series, 2020 - 2022'
     )
@@
 
-  path <- ggsave(
+  ggsave(
     plot = p,
@@
     ...
-  )
-  is_cod <- filename |> str_detect('cod_')
-  game <- ifelse(is_cod, 'cod', 'val')
-  logo_scale <- ifelse(is_cod, 0.15, 0.07)
-  add_logo(
-    path,
-    path_logo = file.path('images', sprintf('%s.png', game)),
-    delete = FALSE,
-    path_suffix = '',
-    logo_scale = logo_scale,
-    idx_x = 0.99,
-    idx_y = 0.01,
-    adjust_x = FALSE
   )
@@
 
-## What are your chances of winning the next round ([COD SnD]{.cod})?
+## What are your chances of winning the next round?
 
@@
 
-## What are your chances of winning the next round ([Valorant]{.valorant})?
-
-```{r}
-#| label: val-funcs
-drop_25th_round <- function(df) {
-  df |> 
-    filter(
-      !(pre_cumu_w == 12 & pre_cumu_l == 12)
-    )
-}
-
-val_e_o_win_series_prop <- crossing(
-  pre_cumu_w = 0:12,
-  pre_cumu_l = 0:12
-) |> 
-  drop_25th_round() |> 
-  mutate(
-    n_remain_max = 25 - (pre_cumu_w + pre_cumu_l),
-    n_remain_w = 13 - pre_cumu_w,
-    ## can i account for offense in this by rotating?
-    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
-  )
-
-## Joshua Broas, vlr.gg
-common_val_labs <- function(...) {
-  list(
-    ...,
-    labs(
-      caption = '2021 VCT matches'
-    )
-  )
-}
-
-common_val_heatmap_layers <- function(...) {
-  list(
-    ...,
-    guides(
-      fill = 'none'
-    ),
-    scale_x_continuous(
-      labels = 0:12,
-      breaks = seq(0.5, 12.5, by = 1),
-      expand = c(0, 0)
-    ),
-    scale_y_continuous(
-      labels = 0:12,
-      breaks = seq(0.5, 12.5, by = 1),
-      expand = c(0, 0),
-      sec.axis = sec_axis(
-        trans = I, 
-        name = ' ', 
-        breaks = seq(0.5, 12.5, by = 1), 
-        labels = rep('', 13)
-      )
-    ),
-    theme(
-      panel.grid.major = element_blank(),
-      axis.title = element_text(hjust = 0.5),
-      plot.title = ggtext::element_markdown(hjust = 0.5),
-      axis.text = element_text(size = 16, face = 'bold')
-    ),
-    common_val_labs(),
-    labs(
-      x = "Offensive Team's # of Pre-Round Wins",
-      y = "Defensive Team's # of Pre-Round Wins"
-    )
-  )
-}
-
-val_heatmap_seq_labeller <- function(.df, .label, .num) {
-  sprintf(
-    '%s\n(%s)', 
-    scales::percent(.df[[.label]], accuracy = 1), 
-    scales::comma(.df$n)
-  )
-}
-
-o_series_win_text_layer <- function(
-    ..., 
-    .df,
-    .threshold,
-    .labeller, 
-    .emphasize
-) {
-  if(.emphasize == 'low') {
-    op <- `<`
-    .color <- blackish_background
-  } else {
-    op <- `>=`
-    .color <- 'white'
-  }
-  list(
-    ...,
-    heatmap_text_layer(
-      .df = .df,
-      .op = op,
-      .label = 'win_series_prop',
-      .num = 'win_series',
-      .color = .color,
-      .threshold = .threshold,
-      .labeller = .labeller,
-      .size = 9 / .pt
-    )
-  )
-}
-
-val_heatmap_div_labeller <- function(.df, .label, .num) {
-  sprintf(
-    '%+.1f\n(%s)', 
-    100 * .df[[.label]], 
-    scales::comma(.df$n)
-  )
-}
-
-o_series_win_over_expected_text_layer <- function(
-    ..., 
-    .df,
-    .threshold,
-    .labeller, 
-    .emphasize
-) {
-  if(.emphasize == 'low') {
-    op <- `<`
-    .color <- blackish_background
-  } else {
-    op <- `>=`
-    .color <- 'white'
-  }
-  list(
-    ...,
-    heatmap_text_layer(
-      .df = .df,
-      .op = op,
-      .label = 'diff_win_series_prop',
-      .num = NULL,
-      .color = .color,
-      .threshold = .threshold,
-      .labeller = .labeller,
-      .size = 9 / .pt
-    )
-  )
-}
-```
-
-```{r}
-#| label: val_rounds-calcs
-val_round_and_series_win_prop_by_side <- val_rounds |> 
-  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
-  summarize(
-    n = n(),
-    across(c(win_round, win_series), sum)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    win_round_prop = win_round / n,
-    win_series_prop = win_series / n
-  )
-
-val_o_win_prop <- val_round_and_series_win_prop_by_side |> 
-  filter(is_offense) |> 
-  mutate(
-    diff_win_round_prop = win_round_prop - !!val_o_win_prop_const
-  ) |> 
-  inner_join(
-    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
-    by = c('pre_cumu_w', 'pre_cumu_l')
-  ) |> 
-  mutate(
-    diff_win_series_prop = win_series_prop - e_win_series_prop
-  ) |> 
-  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
-  drop_25th_round()
-```
-
-```{r}
-#| label: val_rounds_bothbuy-calcs
-val_bothbuy_rounds <- val_rounds |> 
-  filter(
-    team_buy_type %in% c('semi-buy', 'full-buy'), 
-    opponent_buy_type  %in% c('semi-buy', 'full-buy')
-  )
-
-val_bothbuy_o_win_prop_const <- val_bothbuy_rounds |> 
-  filter(is_offense) |> 
-  count(win_round) |> 
-  mutate(prop = n / sum(n)) |> 
-  filter(win_round) |> 
-  pull(prop)
-
-val_round_and_series_win_prop_by_side_bothbuy <- val_bothbuy_rounds |> 
-  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
-  summarize(
-    n = n(),
-    across(c(win_round, win_series), sum)
-  ) |> 
-  ungroup() |> 
-  mutate(
-    win_round_prop = win_round / n,
-    win_series_prop = win_series / n
-  )
-
-val_o_win_prop_bothbuy <- val_round_and_series_win_prop_by_side_bothbuy |> 
-  filter(is_offense) |> 
-  mutate(
-    diff_win_round_prop = win_round_prop - !!val_bothbuy_o_win_prop_const
-  ) |> 
-  inner_join(
-    val_e_o_win_series_prop |> select(pre_cumu_w, pre_cumu_l, e_win_series_prop),
-    by = c('pre_cumu_w', 'pre_cumu_l')
-  ) |> 
-  mutate(
-    diff_win_series_prop = win_series_prop - e_win_series_prop
-  ) |> 
-  filter(pre_cumu_w <= 12, pre_cumu_l <= 12) |> 
-  drop_25th_round()
-```
-
-```{r}
-#| label: val-funcs-2
-val_pre_swap_rounds <- val_o_win_prop |> 
-  mutate(pre_cumu_wl = pre_cumu_w + pre_cumu_l) |> 
-  filter(pre_cumu_wl == 12)
-
-val_pre_swap_round_segments <- val_pre_swap_rounds |> 
-  transmute(
-    pre_cumu_w,
-    across(pre_cumu_l, ~.x),
-    i = row_number(),
-    n = 2
-  ) |> 
-  uncount(n) |> 
-  group_by(i) |> 
-  mutate(rn = row_number()) |> 
-  ungroup() |> 
-  mutate(
-    across(pre_cumu_w, ~ifelse(rn == 2, .x + 1, .x))
-  ) |> 
-  add_row(
-    pre_cumu_w = 12,
-    pre_cumu_l = 0
-  )
-
-val_swap_path <- function(...) {
-  list(
-    ...,
-    geom_path(
-      data = val_pre_swap_round_segments,
-      color = 'white',
-      size = 1.5,
-      aes(
-        x = pre_cumu_w, 
-        y = pre_cumu_l
-      )
-    )
-  )
-}
-```
-
-```{r}
-#| label: p_val_o_round_win_prop
-p_val_o_round_win_prop <- val_o_win_prop |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(.fill = 'win_round_prop') +
-  val_swap_path() +
-  heatmap_text_layers(
-    .df = val_o_win_prop, 
-    .f = o_round_win_text_layer,
-    .threshold = 0.8,
-    .labeller = val_heatmap_seq_labeller
-  ) +
-  ggsci::scale_fill_material('teal') +
-  labs(
-    title = 'Offensive Round Win %'
-  )
-p_val_o_round_win_prop
-save_plot_for_slide(p_val_o_round_win_prop)
-
-p_val_o_round_win_prop_bothbuy <- val_o_win_prop_bothbuy |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(.fill = 'win_round_prop') +
-  val_swap_path() +
-  heatmap_text_layers(
-    .df = val_o_win_prop_bothbuy, 
-    .f = o_round_win_text_layer,
-    .threshold = 0.8,
-    .labeller = val_heatmap_seq_labeller
-  ) +
-  ggsci::scale_fill_material('teal') +
-  labs(
-    title = 'Offensive Round Win %'
-  )
-p_val_o_round_win_prop_bothbuy
-save_plot_for_slide(p_val_o_round_win_prop_bothbuy)
-```
-
-![](plots/val_o_round_win_prop.png){fig-align="center"}
-
-## What are your chances of winning the series ([COD SnD]{.cod})?
+## What are your chances of winning the series?
 
@@
 
-## What are your chances of winning the series ([COD SnD]{.cod})?
+## What are your chances of winning the series?
 
@@
 
-## What are your chances of winning the series ([Valorant]{.valorant})?
-
-```{r}
-#| label: p_val_o_series_win_prop
-p_val_o_series_win_prop <- val_o_win_prop |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(.fill = 'win_series_prop') +
-  val_swap_path() +
-  heatmap_text_layers(
-    .df = val_o_win_prop, 
-    .f = o_series_win_text_layer,
-    .threshold = 0.8,
-    .labeller = val_heatmap_seq_labeller
-  ) +
-  ggsci::scale_fill_material('orange') +
-  labs(
-    title = 'Offensive Series Win %'
-  )
-p_val_o_series_win_prop
-save_plot_for_slide(p_val_o_series_win_prop)
-```
-
-![](plots/val_o_series_win_prop.png){fig-align="center"}
-
-## What are your chances of winning the series ([Valorant]{.valorant})?
-
-```{r}
-#| label: p_val_o_series_win_prop_over_expected
-val_max_diff_win_series_prop <- max(abs(val_o_win_prop$diff_win_series_prop))
-p_val_o_series_win_prop_over_expected <- val_o_win_prop |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(
-    .fill = 'diff_win_series_prop'
-  ) +
-  heatmap_text_layers(
-    .df = val_o_win_prop, 
-    .f = o_series_win_over_expected_text_layer,
-    .threshold = 0.2,
-    .labeller = val_heatmap_div_labeller
-  ) +
-  val_swap_path() +
-  scale_fill_gradient2(
-    low = ggsci_brown,
-    high = ggsci_cyan,
-    mid = 'white',
-    limits = c(
-      -val_max_diff_win_series_prop,
-      +val_max_diff_win_series_prop
-    ),
-    midpoint = 0
-  ) +
-  labs(
-    title = 'Offensive Series Win % Over Expected'
-  )
-p_val_o_series_win_prop_over_expected
-save_plot_for_slide(p_val_o_series_win_prop_over_expected)
-```
-
-![](plots/val_o_series_win_prop_over_expected.png){fig-align="center"}
-
-## What are your chances of winning the series ([Valorant]{.valorant})?
-
-```{r}
-#| label: p_filt_val_o_series_win_prop_over_expected
-filt_val_o_win_prop <- val_o_win_prop |> 
-  mutate(
-    across(
-      diff_win_series_prop,
-      ~case_when(
-        pre_cumu_w <= 3 & pre_cumu_l <= 3 ~ NA_real_,
-        TRUE ~ .x
-      )
-    )
-  )
-filt_val_max_diff_win_series_prop <- max(abs(filt_val_o_win_prop$diff_win_series_prop))
-
-p_filt_val_o_series_win_prop_over_expected <- filt_val_o_win_prop |> 
-  ggplot() +
-  common_val_heatmap_layers() +
-  heatmap_tile(
-    .fill = 'diff_win_series_prop'
-  ) +
-  heatmap_text_layers(
-    .df = filt_val_o_win_prop, 
-    .f = o_series_win_over_expected_text_layer,
-    .threshold = 0.1,
-    .labeller = val_heatmap_div_labeller
-  ) +
-  val_swap_path() +
-  scale_fill_gradient2(
-    low = ggsci_brown,
-    high = ggsci_cyan,
-    mid = 'white',
-    limits = c(
-      -filt_val_max_diff_win_series_prop,
-      +filt_val_max_diff_win_series_prop
-    ),
-    midpoint = 0
-  ) +
-  labs(
-    title = 'Offensive Series Win % Over Expected'
-  )
-p_filt_val_o_series_win_prop_over_expected
-save_plot_for_slide(p_filt_val_o_series_win_prop_over_expected)
-```
-
-![](plots/filt_val_o_series_win_prop_over_expected.png){fig-align="center"}
-
-## What are the most common series winning states ([COD SnD]{.cod})?
+## What are the most common series winning states?
 
@@
 
-summarize_streaks <- function(rounds, game = c('cod', 'val')) {
-  if (game == 'cod') {
+summarize_streaks <- function(rounds) {
   .max_round <- 11
   .adj <- 0
-  } else {
-    .max_round <- 25
-    .adj <- 1
-  }
 
@@
 plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
-  if (game == 'cod') {
   .lvls <- sprintf('6-%d', 0:5)
   .axis_x_text_size <- 14
-  } else {
-    .lvls <- c(sprintf('13-%d', 0:11), '12-12')
-    .axis_x_text_size <- 12
-  }
 
@@
 
-cod_streaks_res <- cod_rounds |> summarize_streaks('cod')
+cod_streaks_res <- cod_rounds |> summarize_streaks()
 
 p_cod_series_outcome_prop_over_expected <- cod_streaks_res$series |> 
-  plot_series_outcome_prop_over_expected('cod') +
+  plot_series_outcome_prop_over_expected() +
   common_cod_labs()
@@
 
-## Should round win percentage in [COD SnD]{.cod} be modeled as constant?
+## Should round win percentage be modeled as constant?
 
@@
 ::: fragment
--   In COD, the average number of rounds (**`r avg_actual_cod_rounds_per_series`**) is less than the expected value (**`r avg_expected_cod_rounds_per_series`**)
+-   In CoD, the average number of rounds (**`r avg_actual_cod_rounds_per_series`**) is less than the expected value (**`r avg_expected_cod_rounds_per_series`**)
 :::
@@
 
-## What are the most common series winning states ([Valorant]{.valorant})?
-
-```{r}
-#| label: p_val_series_outcome_prop_over_expected
-val_streaks_res <- val_rounds |> summarize_streaks('val')
-
-p_val_series_outcome_prop_over_expected <- val_streaks_res$series |> 
-  plot_series_outcome_prop_over_expected('val') +
-  common_val_labs()
-p_val_series_outcome_prop_over_expected
-save_plot_for_slide(p_val_series_outcome_prop_over_expected)
-```
-
-![](plots/val_series_outcome_prop_over_expected.png)
-
-There's a clear bias towards shorter series than expected.
-
-## When do back-to-back round wins occur ([COD SnD]{.cod})?
+## When do back-to-back round wins occur?
 
@@
 
-## Is there evidence for the "hot hand" ([COD SnD]{.cod})?
+## Is there evidence for the "hot hand"?
 
@@
 
-## Is there evidence for the "hot hand" ([Valorant]{.valorant})?
-
-```{r}
-#| label: val_round_win_prop_after_x_wins-save
-#| eval: false
-val_round_streaks <- val_rounds |> 
-  group_by(series_id, team, is_offense) |> 
-  mutate(
-    won_prior_round1 = lag(win_round, n = 1, default = NA),
-    won_prior_round2 = lag(win_round, n = 2, default = NA),
-    won_prior_round3 = lag(win_round, n = 3, default = NA),
-    won_prior_round4 = lag(win_round, n = 4, default = NA),
-    won_prior_round5 = lag(win_round, n = 5, default = NA),
-    won_prior_round6 = lag(win_round, n = 6, default = NA),
-    won_prior_round7 = lag(win_round, n = 7, default = NA),
-    won_prior_round8 = lag(win_round, n = 8, default = NA),
-    won_prior_round9 = lag(win_round, n = 9, default = NA)
-  ) |> 
-  ungroup() |>
-  select(
-    series_id,
-    team,
-    is_offense,
-    cumu_w,
-    round,
-    n_rounds,
-    win_round,
-    starts_with('won_prior_round')
-  )
-
-summarize_val_win_prop_after_x_wins_first12r <- function(k) {
-  stopifnot((k >= 3) & (k <= 9))
-  probs_nx_k <- tibble(
-    cumu_w = 4L:11L,
-    n_rounds = 12L
-  ) |> 
-    mutate(
-      prior_p = cumu_w / n_rounds,
-      expected_poststreak_p = map2_dbl(
-        n_rounds, prior_p, 
-        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
-      )
-    )
-
-  cols <- sprintf('won_prior_round%d', 2:k)
-  col_syms <- syms(cols)
-  val_round_streaks_after_x <- val_round_streaks |> 
-    filter(round < 13) |> 
-    drop_na(!!!col_syms) |> 
-    count(cumu_w, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
-
-  val_round_win_prop_after_x_wins <- val_round_streaks_after_x |> 
-    filter(won_prior_round1, !!!col_syms)
-
-  val_round_win_prop_after_x_wins |> 
-    group_by(cumu_w) |> 
-    mutate(
-      total = sum(n),
-      prop = n / total
-    ) |> 
-    ungroup() |> 
-    filter(win_round) |> 
-    select(cumu_w, n, total, prop) |> 
-    arrange(cumu_w) |> 
-    inner_join(
-      probs_nx_k,
-      by = 'cumu_w'
-    ) |> 
-    nest(data = -c(cumu_w)) |> 
-    mutate(
-      gt_p_value = map_dbl(
-        data, 
-        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
-          broom::tidy() |>
-          pull(p.value) |> 
-          round(3)
-      ),
-      lt_p_value = map_dbl(
-        data, 
-        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
-          broom::tidy() |>
-          pull(p.value) |> 
-          round(3)
-      )
-    ) |> 
-    unnest(data)
-}
-
-summarize_val_win_prop_after_x_wins_second12r <- function(k) {
-  stopifnot((k >= 3) & (k <= 9))
-  probs_nx_k <- crossing(
-    cumu_w = 0L:13L,
-    n_rounds = 13L:24L
-  ) |> 
-    mutate(
-      prior_p = cumu_w / n_rounds,
-      expected_poststreak_p = map2_dbl(
-        n_rounds, prior_p, 
-        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
-      )
-    )
-
-  cols <- sprintf('won_prior_round%d', 2:k)
-  col_syms <- syms(cols)
-  val_round_streaks_after_x <- val_round_streaks |> 
-    filter(round > 12) |> 
-    drop_na(!!!col_syms) |> 
-    count(n_rounds, cumu_w, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
-
-  val_round_win_prop_after_x_wins <- val_round_streaks_after_x |> 
-    filter(won_prior_round1, !!!col_syms)
-
-  val_round_win_prop_after_x_wins |> 
-    group_by(n_rounds, cumu_w) |> 
-    mutate(
-      total = sum(n),
-      prop = n / total
-    ) |> 
-    ungroup() |> 
-    filter(win_round) |> 
-    select(n_rounds, cumu_w, n, total, prop) |> 
-    arrange(n_rounds, cumu_w) |> 
-    inner_join(
-      probs_nx_k,
-      by = c('n_rounds', 'cumu_w')
-    ) |> 
-    nest(data = -c(n_rounds, cumu_w)) |> 
-    mutate(
-      gt_p_value = map_dbl(
-        data, 
-        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
-          broom::tidy() |>
-          pull(p.value) |> 
-          round(3)
-      ),
-      lt_p_value = map_dbl(
-        data, 
-        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
-          broom::tidy() |>
-          pull(p.value) |> 
-          round(3)
-      )
-    ) |> 
-    unnest(data)
-}
-
-val_round_win_prop_after_x_wins_first12r <- tibble(win_streak = 3L:9L) |> 
-  mutate(
-    data = map(win_streak, summarize_val_win_prop_after_x_wins_first12r)
-  ) |> 
-  unnest(data)
-save_qs(val_round_win_prop_after_x_wins_first12r)
-
-val_round_win_prop_after_x_wins_second12r <- tibble(win_streak = 3L:9L) |> 
-  mutate(
-    data = map(win_streak, summarize_val_win_prop_after_x_wins_second12r)
-  ) |> 
-  unnest(data)
-save_qs(val_round_win_prop_after_x_wins_second12r)
-```
-
-```{r}
-#| label: val_round_win_prop_after_x_wins
-#| eval: false
-load_qs('val_round_win_prop_after_x_wins_first12r')
-load_qs('val_round_win_prop_after_x_wins_second12r')
-val_round_win_prop_after_x_wins_first12r |> 
-  filter(n > 30) |> 
-  mutate(
-    gt_signif = gt_p_value <= 0.05
-  ) |> 
-  ggplot() +
-  aes(x = win_streak, y = cumu_w) +
-  geom_tile(
-    aes(fill = gt_signif)
-  ) +
-  geom_text(
-    aes(label = sprintf(
-      '%s | %s\n(%s)',
-      scales::percent(prop, accuracy = 1),
-      scales::percent(expected_poststreak_p, accuracy = 1),
-      scales::comma(total)
-    )
-    )
-  )
-
-val_round_win_prop_after_x_wins_second12r |> 
-  filter(n > 30) |> 
-  mutate(
-    gt_signif = gt_p_value <= 0.05
-  ) |> 
-  ggplot() +
-  aes(x = win_streak, y = cumu_w) +
-  geom_tile(
-    aes(fill = gt_signif)
-  ) +
-  geom_text(
-    aes(label = sprintf(
-      '%s | %s\n(%s)',
-      scales::percent(prop, accuracy = 1),
-      scales::percent(expected_poststreak_p, accuracy = 1),
-      scales::comma(total)
-    )
-    )
-  ) +
-  facet_wrap(~n_rounds)
-
-```
-
-```{r}
-#| label: cod_round_win_prop_after_xw-eval
-#| eval: false
-load_qs('val_round_win_prop_after_x_wins_first12r')
-val_round_win_prop_after_x_wins_first12r |> 
-  transmute(
-    `Win Streak` = win_streak,
-    `# of Offensive Wins in First 12 Rounds` = cumu_w,
-    `N` = scales::comma(total),
-    across(c(prop, expected_poststreak_p), ~scales::percent(.x, accuracy = 0.1)),
-    across(
-      ends_with('p_value'), 
-      ~case_when(
-        .x <= 0.01 ~ '<=0.01', 
-        round(.x, 2) == 1 ~ '1',
-        TRUE ~ as.character(round(.x, 2))
-      )
-    )
-  ) |>
-  rename(
-    `Actual post-streak win %` = prop,
-    `Expected post-streak win %` = expected_poststreak_p,
-    `Binom. > p-value` = gt_p_value,
-    `Binom. < p-value` = lt_p_value
-  ) |> 
-  knitr::kable()
-
-```
-
-::: fragment
-First 12 rounds **only**
-
-TODO
-:::
-
-::: fragment
--   There is no evidence for momentum, for both streaks of 2 and 3.
-In fact, for series that go to 9, 10, or 11 rounds, there is evidence that the streaking teams perform significantly worse than expected in the post-streak round.
-And for streaks of 4, teams perform worse than expected in series ending in 7, 8, 10, and 11 rounds.
-:::
-
-::: fragment
--   Given the nature of how economy is used in the game, perhaps this is not suprising at all.
-:::
-
-## Is planting at one site better than the other ([COD SnD]{.cod})?
+## Is planting at one site better than the other?
 
@@
 
-## Are offensive win %'s different in round 1 ([COD SnD]{.cod})?
+## Are offensive win %'s different in round 1?
 
@@
 
-plot_round_vs_post_round_slope_chart <- function(df, .round, game = c('cod', 'val')) {
+plot_round_vs_post_round_slope_chart <- function(df, .roun) {
   game <- match.arg(game)
@@
 
-  is_cod <- game == 'cod'
-  if (is_cod) {
   y_lo <- 0.25
   y_hi <- 0.75
-  } else {
-    y_lo <- 0.45
-    y_hi <- 0.55
-  }
 
@@
 cod_res_r1 <- cod_rounds |> 
-  plot_round_vs_post_round_slope_chart(1, game = 'cod')
+  plot_round_vs_post_round_slope_chart(1)
 
@@
 ![](plots/cod_o_win_r1_vs_post_round_prop.png){fig-align="center"}
-
-## Are offensive win %'s different in round 1 ([Valorant]{.valorant})?
-
-```{r}
-#| label: p_val_o_win_r1_vs_post_round_prop
-p_val_o_win_r1_vs_post_round_prop <- val_rounds |> 
-  plot_round_vs_post_round_slope_chart(1, game = 'val') |> 
-  pluck('plot') +
-  common_val_labs()
-save_plot_for_slide(p_val_o_win_r1_vs_post_round_prop)
-```
-
-![](plots/val_o_win_r1_vs_post_round_prop.png){fig-align="center"}

### 2022-08-12 1-scrape-cod.R
export cod rounds to paper dir

@@ -240,4 +240,6 @@ cod_rounds <- cod_series |>
     map = sprintf('%s - %s (%s)', map, game, year)
   )
 cod_rounds
-qs::qsave(cod_rounds, 'cod_rounds.qs')
+filename <- 'cod_rounds.qs'
+sprintf('%s%s', c('', 'paper/'), filename) |> 
+  walk(~qs::qsave(cod_rounds, .x))

### 2022-08-12 paper/paper.qmd
render paper

@@
 title: "They're Clutching up! Team Momentum in Round-Based Esports"
+execute: 
+  include: false
+  echo: false
+  eval: false
 format:
@@
 ---
+
+```{r}
+#| label: setup
+#| eval: true
+library(dplyr)
+library(dplyr)
+library(qs)
+library(scales)
+
+cod_rounds <- qs::qread('../cod_rounds.qs')
+```
+
+```{r}
+#| label: setup-eval
+library(tidyverse)
+library(extrafont)
+library(ggtext)
+library(ggsci)
+library(ggnewscale)
+library(magick)
+library(broom)
+library(knitr)
+
+background_color <- '#000000' ## to match slide background
+text_color <- '#191919'
+
+font <- 'Titillium Web'
+extrafont::loadfonts(quiet = TRUE)
+theme_set(theme_minimal())
+theme_update(
+  text = element_text(family = font),
+  title = element_text(size = 14, color = text_color),
+  plot.title = element_text(face = 'bold', size = 20, color = text_color),
+  plot.title.position = 'plot',
+  plot.subtitle = element_text(size = 14, color = '#f1f1f1'),
+  axis.text = element_text(color = 'white', size = 14),
+  axis.title = element_text(size = 14, color = text_color, face = 'bold', hjust = 0.99),
+  axis.line = element_blank(),
+  panel.grid.major = element_line(color = text_color),
+  panel.grid.minor = element_line(color = text_color),
+  panel.grid.minor.x = element_blank(),
+  panel.grid.minor.y = element_blank(),
+  strip.text = element_text(color = text_color, size = 16, face = 'bold'),
+  plot.margin = margin(10, 10, 10, 10),
+  plot.background = element_rect(fill = background_color, color = background_color),
+  plot.caption = element_text(size = 12, color = text_color, hjust = 1),
+  plot.caption.position = 'plot',
+  plot.tag = ggtext::element_markdown(size = 12, color = text_color, hjust = 0),
+  plot.tag.position = c(0.01, 0.01),
+  panel.background = element_rect(fill = background, color = background_color)
+)
+update_geom_defaults('text', list(family = font, size = 10 / .pt, fontface = 'bold'))
+update_geom_defaults('point', list(color = text_color))
+update_geom_defaults('segment', list(color = text_color))
+```
+
+```{r}
+#| label: descriptive-cod-snd-stats
+#| eval: true
+cod_n_series <- cod_rounds |> 
+  distinct(series_id, team) |> 
+  nrow()
+
+cod_n_rounds <- cod_rounds |> 
+  distinct(series_id, team, round) |> 
+  nrow()
+cod_n_rounds / cod_n_series
+## mean(cod_rounds$n_rounds) ## should this be the same?
+
+cod_o_win_prop_const <- cod_rounds |> 
+  filter(is_offense) |> 
+  count(win_round) |> 
+  mutate(prop = n / sum(n)) |> 
+  filter(win_round) |> 
+  pull(prop)
+```
+
+```{r}
+#| label: cod-funcs
+common_cod_labs <- function(...) {
+  list(
+    ...,
+    labs(
+      caption = 'CDL SnD major and qualifier series, 2020 - 2022'
+    )
+  )
+}
+
+common_cod_heatmap_layers <- function(...) {
+  list(
+    ...,
+    guides(
+      fill = 'none'
+    ),
+    scale_x_continuous(
+      labels = 0:5,
+      breaks = seq(0.5, 5.5, by = 1),
+      expand = c(0, 0)
+    ),
+    scale_y_continuous(
+      labels = 0:5,
+      breaks = seq(0.5, 5.5, by = 1),
+      expand = c(0, 0),
+      sec.axis = sec_axis(
+        trans = I, 
+        name = ' ', 
+        breaks = seq(0.5, 5.5, by = 1), 
+        labels = rep('', 6)
+      )
+    ),
+    theme(
+      panel.grid.major = element_blank(),
+      axis.title = element_text(hjust = 0.5),
+      plot.title = ggtext::element_markdown(hjust = 0.5),
+      axis.text = element_text(size = 16, face = 'bold')
+    ),
+    common_cod_labs(),
+    labs(
+      x = "Offensive Team's # of Pre-Round Wins",
+      y = "Defensive Team's # of Pre-Round Wins"
+    )
+  )
+}
+
+.dpi <- 300
+save_plot_for_paper <- function(
+    p, 
+    filename = paste0(str_remove(deparse(substitute(p)), '^p_'), '.png'), 
+    width = 7.5, 
+    height = width / 1.5,
+    units = 'px',
+    dpi = .dpi,
+    ...
+) {
+
+  path <- ggsave(
+    plot = p,
+    filename = file.path('plots', filename),
+    width = width * dpi,
+    height = height * dpi,
+    units = units,
+    dpi = dpi,
+    ...
+  )
+  is_cod <- filename |> str_detect('cod_')
+}
+
+heatmap_tile <- function(..., .fill) {
+  list(
+    ...,
+    geom_rect(
+      color = background_color,
+      aes(
+        fill = .data[[.fill]],
+        xmin = pre_cumu_w, 
+        ymin = pre_cumu_l,
+        xmax = pre_cumu_w + 1,
+        ymax = pre_cumu_l + 1
+      )
+    )
+  )
+}
+
+heatmap_text_layer <- function(..., .op, .df, .label, .num, .color, .threshold, .labeller, .size = 11 / .pt) {
+  .df_filt <- .df |> filter(`.op`(.df[[.label]], .threshold))
+  if(nrow(.df_filt) == 0) {
+    return(list(...))
+  }
+  list(
+    ...,
+    geom_text(
+      data = .df_filt,
+      color = .color,
+      size = .size,
+      fontface = 'bold',
+      aes(
+        label = .labeller(.df = .df_filt, .label = .label, .num = .num),
+        x = .data$pre_cumu_w + 0.5, 
+        y = .data$pre_cumu_l + 0.5
+      )
+    )
+  )
+}
+
+heatmap_text_layers <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller,
+    .f
+) {
+  list(
+    ...,
+    .f(.df = .df, .threshold = .threshold, .labeller = .labeller, .emphasize = 'low'),
+    .f(.df = .df, .threshold = .threshold, .labeller = .labeller, .emphasize = 'high')
+  )
+}
+
+cod_heatmap_seq_labeller <- function(.df, .label, .num) {
+  sprintf(
+    '%s\n(%s)',
+    scales::percent(.df[[.label]], accuracy = 1), 
+    scales::comma(.df$n)
+  )
+}
+
+cod_heatmap_seq_labeller <- function(.df, .label, .num) {
+  sprintf(
+    '%s\n(%s)',
+    scales::percent(.df[[.label]], accuracy = 1), 
+    scales::comma(.df$n)
+  )
+}
+
+o_round_win_text_layer <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller,
+    .label = 'win_round_prop',
+    .num = 'win_round',
+    .emphasize
+) {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- background_color
+  } else {
+    op <- `>=`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .df = .df,
+      .op = op,
+      .label = .label,
+      .num = .num,
+      .color = .color,
+      .threshold = .threshold,
+      .labeller = .labeller,
+      .size = 11 / .pt
+    )
+  )
+}
+
+cod_heatmap_div_labeller <- function(.df, .label, .num) {
+  sprintf(
+    '%+.1f\n(%s)', 
+    100 * .df[[.label]], 
+    scales::comma(.df$n)
+  )
+}
+
+o_round_win_over_expected_text_layer <- function(
+    ..., 
+    .df, 
+    .threshold,
+    .labeller,
+    .emphasize
+) {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- 'white'
+  } else {
+    op <- `>=`
+    .color <- background_color
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .df = .df,
+      .op = op,
+      .label = 'diff_win_round_prop',
+      .num = 1,
+      .color = .color,
+      .threshold = .threshold,
+      .labeller = .labeller
+    )
+  )
+}
+
+extract_ggsci_mid_color <- function(palette) {
+  ggsci::pal_material(palette, n = 3)(2)[2]
+}
+
+ggsci_purple <- extract_ggsci_mid_color('purple')
+ggsci_green <- extract_ggsci_mid_color('green')
+ggsci_cyan <- extract_ggsci_mid_color('cyan')
+ggsci_brown <- extract_ggsci_mid_color('brown')
+```
+
+```{r}
+#| label: cod_rounds-calcs
+cod_round_and_series_win_prop_by_side <- cod_rounds |> 
+  group_by(pre_cumu_w, pre_cumu_l, is_offense) |> 
+  summarize(
+    n = n(),
+    across(c(win_round, win_series), sum)
+  ) |> 
+  ungroup() |> 
+  mutate(
+    win_round_prop = win_round / n,
+    win_series_prop = win_series / n
+  )
+
+cod_e_o_win_series_prop <- crossing(
+  pre_cumu_w = 0:5,
+  pre_cumu_l = 0:5
+) |> 
+  mutate(
+    n_remain_max = 11 - (pre_cumu_w + pre_cumu_l),
+    n_remain_w = 6 - pre_cumu_w,
+    ## can i account for offense in this by rotating?
+    e_win_series_prop = map2_dbl(n_remain_w, n_remain_max, ~sum(dbinom(..1:..2, ..2, 0.5)))
+  )
+```
 
@@
 
-CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.
-The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era.
-Data was collected in spreadsheets by community member "IOUTurtle".[^5]
+CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^5] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era.
+Data was collected in spreadsheets by community member "IOUTurtle".[^6]
 
-[^5]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle
+[^5]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
+Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
+During the CDL era, the games released have been Modern Warfare (2020), Cold War (2021) and Vanguard (2022).
+
+[^6]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle
 
@@
 A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
-
-CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, where a new game is published every year under the same title.
-Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
-The data set denotes which CoD game a given CoD SnD series was played,
 
@@
 
-Streaks and momentum is one of the most frequently published topics in sports analytics.
-We often use these interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
-When considering
+There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state.
+Observing that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p=0.5$, [@mosteller1952] proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$ in each case: (1) a "method of moments", an approach that solves for $p$ from the empirical average number of games won by the loser of the series; (2) maximum likelihood, and (3) maximum chi-square approach.
+[@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
+Chance applies Mosteller's method 1 and 2 and finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series.
+Chance outlines a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
 
-Despite the plethora of existing research on momentum in sports, its yet to be investigated heavily in esports. [@article-journal]
+Momentum is one of the most frequently published topics in sports analytics.
+We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+(sentence about negative recency, hinting at "hot hand"...
+[@miller2018] debunking findings from [@gilovich1985])
+
+Despite the plethora of existing research on games played and momentum in sports, these topics have yet to be investigated heavily in esports.
+Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD.
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^7]\[\^8\]
+
+[^7]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+
+# 3. Methodology
+
+# 4. Results and discussion
 

### 2022-08-12 paper/paper.tex
render paper

@@
 My research investigates patterns in round win percentages in
-professional matches (series) of two popular first-person shooter games,
-Call of Duty (Search and Destroy mode) and Valorant.
+professional Search and Destroy (SnD) matches of the popular
+first-person shooter game Call of Duty (CoD).
 
-First, I find evidence in Call of Duty (COD) defying the naive
-hypothesis that a series represents a sequence of independent events
-(rounds), with each team having a constant 50\% probability of winning a
-given round.
+First, I find evidence in CoD defying the naive hypothesis that a series
+represents a sequence of independent events (rounds), with each team
+having a constant 50\% probability of winning a given round.
 
-Second, I examine post-streak round win probability. For COD, in which
-teams play first to 6 round wins (maximum 11 rounds), I find that teams
+Second, I examine post-streak round win probability. I find that teams
 perform significantly worse than expected after streaks of 2, 3, and 4
-wins when series end up going to 9, 10, or 11 rounds, even after
-accounting for the ``hot-hand'' phenomenon. In Valorant, which requires
-one side to win 13 rounds for the series victory, there is evidence of
-performing better than expected after streaks of up to 8 wins, which is
-perhaps not shocking given the economy aspect of the game.
+wins when series end up going to 9, 10, or 11 (maximum) rounds, even
+after accounting for the ``hot-hand'' phenomenon.
 
@@
 is no prior information about how the opponent intends to play a given
-map in either game. I find one COD map for which there seems to be a
-significant defensive advantage in round one, but none otherwise.
+map in either game. I find only one instance for which there seems to be
+a significant defensive advantage in round one.
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, enhanced, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden]}{\end{tcolorbox}}\fi
-
-Sit nunc at convallis fringilla semper! Penatibus vivamus eget malesuada
-cursus fames magnis potenti. Venenatis ligula enim conubia laoreet orci
-class ligula? Massa sem sed enim risus ut mattis inceptos nisl elementum
-mattis. Nostra ultricies habitant donec vitae luctus proin gravida
-placerat ac libero imperdiet. Auctor habitasse faucibus ultricies purus
-eget sociis ultrices habitasse nec ad aptent lectus rutrum proin potenti
-montes sodales posuere convallis tempor erat egestas magna lectus sociis
-mollis purus.
-
-Dolor turpis euismod himenaeos interdum felis dictum tempus euismod
-tortor aliquam? Eget interdum vehicula laoreet quam. Mollis justo cursus
-ad blandit feugiat pulvinar sem sodales bibendum. Leo leo magna pulvinar
-metus lacinia nam fringilla maecenas duis dis suscipit aenean natoque
-sem metus quam risus sagittis convallis primis sociis id dictumst.
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
 
 \hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+\section{1. Introduction}\label{introduction}}
 
-Amet ultricies dignissim varius potenti suscipit justo phasellus dui
-ullamcorper luctus suscipit vulputate. Sagittis enim volutpat ultrices
-diam curabitur potenti platea euismod vel libero primis feugiat. Nibh
-potenti habitant ultricies dictum sociis class at vehicula eu
-vestibulum. Curabitur iaculis.
+\hypertarget{description-of-call-of-duty-search-and-destroy}{%
+\subsection{1.1 Description of Call of Duty Search and
+Destroy}\label{description-of-call-of-duty-search-and-destroy}}
 
-Consectetur est eleifend turpis morbi magna porttitor bibendum ut
-blandit aliquet lacus. Nostra iaculis torquent parturient id fermentum
-montes at himenaeos. Magna congue blandit fames egestas at inceptos? Id
-maecenas blandit maecenas accumsan ridiculus mollis nullam justo
-pulvinar elementum inceptos habitant risus.
+Call of Duty (CoD), first released in 2003, is one of the most popular
+first-person shooter (FPS) video game franchises of all-time. Tthe most
+popular mode in the competitive scene is ``Search and Destroy'' (SnD),
+which bears resemblance to ``Bomb Defusal'' in Counter-Strike and
+``Plant/Defuse'' in Valorant, two other FPS games played in professional
+leagues. SnD is one-sided game mode in which one team, the offensive
+side, tries to destroy one of two designated bomb sites on the
+map.\footnote{as}
 
-\newpage{}
+In professional CoD, a team must win six rounds of SnD to win the
+match.\footnote{A maximum of 11 even rounds can be played. There is no
+  ``sudden death'' or ``win by two'' rule like there are for SnD
+  equivalent in professional Counter-Strike and Valorant matches.} A
+round can end in one of four ways:
+
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  One team eliminates all members of the other team prior to a bomb
+  plant. (Eliminating team wins.)
+\item
+  The offensive team eliminates all members of the defensive team after
+  a bomb plant.\footnote{\begin{itemize}
+    \tightlist
+    \item
+      The bomb can be picked up by any member of the offensive team.
+    \item
+      The bomb carrier is not obstructed at all by carrying the bomb
+      (i.e.~movement is the same, weapon usage is the same).
+    \item
+      The defense does not get any visual indication for who is carrying
+      the bomb.
+    \item
+      A bomb plant takes five seconds. The timer resets if the player
+      stops planting site prior to completing it.
+    \item
+      A bomb defuse takes seven seconds. The timer resets if the player
+      ``drops'' the bomb.
+    \item
+      The bomb takes 45 seconds to defuse after being planted.
+    \end{itemize}} (Offense wins.)
+\item
+  The defensive team defuses the bomb after a bomb plant.\footnote{Often
+    the defensive team will try to eliminate all team members prior to
+    making the defuse, but in some cases, they may try to ``ninja''
+    defuse.} (Defense wins.)
+\item
+  The offensive team does not make a plant by the time the round timer
+  ends. (Defense wins.)
+\end{enumerate}
+
+Teams take turns playing offense and defense every round.
+
+\hypertarget{data}{%
+\subsection{1.2 Data}\label{data}}
+
+CoD has roughly gone through three eras of professional gaming: (1)
+Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
+League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
+(CDL), running since 2020 and completing three year-long ``seasons''
+completed as of August 2022.\footnote{CoD is fairly unique compared to
+  other esports in that it runs on an annual lifecycle (released coming
+  in the late fall), where a new game is published every year under the
+  same title. Each new game bears resemblance to past ones, often
+  introducing relatively small variations (``improvements'') to
+  graphics, game modes, and other facets of gameplay. During the CDL
+  era, the games released have been Modern Warfare (2020), Cold War
+  (2021) and Vanguard (2022).} The data set consists of all SnD matches
+played in tournaments and qualifiers during the CDL era. Data was
+collected in spreadsheets by community member ``IOUTurtle''.\footnote{Data:
+  https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle}
+
+I adopt the terminology ``series'' to refer to what CoD SnD players
+typically call a ``match'', so as to emulate the terminology of playoff
+series in professional leagues like the National Basketball Association,
+National Hockey League, and Major League Baseball. A ``game'' or a
+``match'' in such leagues is analogous to a ``round'' of CoD SnD.
+
+\hypertarget{my-contribution}{%
+\subsection{1.3 My contribution}\label{my-contribution}}
+
+\hypertarget{literature-review}{%
+\section{2 Literature review}\label{literature-review}}
+
+There have been only a handful of studies of the distribution of games
+played in a series, most of which assume a constant probability \(p\) of
+a given team winning a game in the series, regardless of the series
+state. Observing that the American League had dominated the National
+League in Major League Baseball's (MLB) World Series matchups, implying
+that matchups should not modeled with \(p=0.5\), (Mosteller 1952)
+proposed three approaches for identifying the optimal constant
+probability value of the stronger team in the World Series, finding
+\(p \approx 0.65\) in each case: (1) a ``method of moments'', an
+approach that solves for \(p\) from the empirical average number of
+games won by the loser of the series; (2) maximum likelihood, and (3)
+maximum chi-square approach. (Chance 2020) re-examines the constant
+probability notion in Major League Baseball's World Series (1923--2018),
+the National Basketball Association's Finals (1951--2018), and the
+National Hockey League's Stanley Cup (1939--2018). Chance applies
+Mosteller's method 1 and 2 and finds strong evidence against the null
+hypothesis of \(p = 0.5\) in the MLB and NHL championship series. Chance
+outlines a conditional probability framework (likelihood of winning a
+game given the series state) which can exactly explain the distribution
+of the number of games played.
+
+Momentum is one of the most frequently published topics in sports
+analytics. We often use use ``streaks'' and momentum interchangeably,
+but as (Steeger, Dulin, and Gonzalez 2021) note, momentum implies
+dependence between events, whereas streaking does not. (sentence about
+negative recency, hinting at ``hot hand''\ldots{} (Miller and Sanjurjo
+2018) debunking findings from (Gilovich, Vallone, and Tversky 1985))
+
+Despite the plethora of existing research on games played and momentum
+in sports, these topics have yet to be investigated heavily in esports.
+Work has been done to examine in-round win probability in other FPS
+titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva 2022))
+and Valorant ((DeRover 2021)), both of which are round-based like CoD
+SnD. However, research on round-level trends is spare, perhaps because
 
@@
 \hypertarget{refs}{}
-\begin{CSLReferences}{0}{0}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-chance2020}{}}%
+Chance, Don. 2020. {``Conditional Probability and the Length of a
+Championship Series in Baseball, Basketball, and Hockey.''}
+\emph{Journal of Sports Analytics} 6 (2): 111--27.
+\url{https://doi.org/10.3233/JSA-200422}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-derover2021}{}}%
+DeRover, DeMars. 2021. {``Round Win Probabilities Based on Who's Alive +
+Time.''}
+\url{https://www.reddit.com/r/VALORANT/comments/n3lpoo/round_win_probabilities_based_on_whos_alive_time/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gilovich1985}{}}%
+Gilovich, Thomas, Robert Vallone, and Amos Tversky. 1985. {``The Hot
+Hand in Basketball: On the Misperception of Random Sequences.''}
+\emph{Cognitive Psychology} 17 (3): 295314.
+
+\leavevmode\vadjust pre{\hypertarget{ref-miller2018}{}}%
+Miller, Joshua B., and Adam Sanjurjo. 2018. {``Surprised by the Hot Hand
+Fallacy? A Truth in the Law of Small Numbers.''} \emph{Econometrica} 86
+(6): 20192047.
+
+\leavevmode\vadjust pre{\hypertarget{ref-mosteller1952}{}}%
+Mosteller, Frederick. 1952. {``The World Series Competition.''}
+\emph{Journal of the American Statistical Association} 47 (259): 355380.
+
+\leavevmode\vadjust pre{\hypertarget{ref-steeger2021}{}}%
+Steeger, Gregory M., Johnathon L. Dulin, and Gerardo O. Gonzalez. 2021.
+{``Winning and Losing Streaks in the National Hockey League: Are Teams
+Experiencing Momentum or Are Games a Sequence of Random Events?''}
+\emph{Journal of Quantitative Analysis in Sports} 17 (3): 155170.
+
+\leavevmode\vadjust pre{\hypertarget{ref-xenopoulos2022}{}}%
+Xenopoulos, Peter, William Robert Freeman, and Claudio Silva. 2022.
+{``Analyzing the Differences Between Professional and Amateur Esports
+Through Win Probability.''} In, 34183427.
+
 \end{CSLReferences}

### 2022-08-12 presentation.qmd
don't run code in the paper

@@
   pull(prop)
-cod_o_win_pct <- scales::percent(cod_o_win_prop_const, accuracy = 1)
+cod_o_win_pct <- scales::percent(cod_o_win_prop_const, accuracy = 0.1)
 
@@
   pull(prop) |> 
-  scales::percent(accuracy = 1)
+  scales::percent(accuracy = 0.1)
 
@@
   pull(prop) |> 
-  scales::percent(accuracy = 1)
+  scales::percent(accuracy = 0.1)
 ```
@@
     '%s\n(%s)',
-    scales::percent(.df[[.label]], accuracy = 1), 
+    scales::percent(.df[[.label]], accuracy = 0.1), 
     scales::comma(.df$n)
@@
 }
-
+o_series_win_text_layer <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller, 
+    .emphasize
+) {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- blackish_background
+  } else {
+    op <- `>=`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .df = .df,
+      .op = op,
+      .label = 'win_series_prop',
+      .num = 'win_series',
+      .color = .color,
+      .threshold = .threshold,
+      .labeller = .labeller,
+      .size = 9 / .pt
+    )
+  )
+}
 cod_heatmap_div_labeller <- function(.df, .label, .num) {
@@
 
+o_series_win_over_expected_text_layer <- function(
+    ..., 
+    .df,
+    .threshold,
+    .labeller, 
+    .emphasize
+) {
+  if(.emphasize == 'low') {
+    op <- `<`
+    .color <- blackish_background
+  } else {
+    op <- `>=`
+    .color <- 'white'
+  }
+  list(
+    ...,
+    heatmap_text_layer(
+      .df = .df,
+      .op = op,
+      .label = 'diff_win_series_prop',
+      .num = NULL,
+      .color = .color,
+      .threshold = .threshold,
+      .labeller = .labeller,
+      .size = 9 / .pt
+    )
+  )
+}
+
 extract_ggsci_mid_color <- function(palette) {
@@
 
-  round_win_prop_after_x_wins |> 
+  suppressMessages(
+  round_win_prop_after_x_wins_w_probs <- round_win_prop_after_x_wins |> 
     group_by(n_rounds, ...) |> 
@@
       probs_nx_k
-    ) |> 
+    )
+  )
+
+  round_win_prop_after_x_wins_w_probs |> 
     nest(data = -c(n_rounds, ...)) |> 
@@
 
-cod_round_win_prop_after_x_wins_and_rounds <- tibble(win_streak = 2L:4L) |>
-  mutate(
-    data = map(win_streak, summarize_cod_win_prop_after_x_wins_and_rounds)
+cod_round_win_prop_after_x_wins_y_rounds <- tibble(win_streak = 2L:4L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins_y_rounds)
   ) |>
   unnest(data)
-save_qs(cod_round_win_prop_after_x_wins_and_rounds)
+save_qs(cod_round_win_prop_after_x_wins_y_rounds)
 ```
@@
 ```{r}
-load_qs('cod_round_win_prop_after_x_wins')
+load_qs('cod_round_win_prop_after_x_wins_y_rounds')
 ggsci_orange <- extract_ggsci_mid_color('orange')

### 2022-08-12 1-scrape-cod.R

@@ -240,6 +240,4 @@ cod_rounds <- cod_series |>
     map = sprintf('%s - %s (%s)', map, game, year)
   )
 cod_rounds
-filename <- 'cod_rounds.qs'
-sprintf('%s%s', c('', 'paper/'), filename) |> 
-  walk(~qs::qsave(cod_rounds, .x))
+qs::qsave(cod_rounds, 'cod_rounds.qs')

### 2022-08-13 research/run_tests.R
Create run_tests.R

@@ -1,0 +1,161 @@
+
+simulate_cod_round_arrangements <- function(n_sims = 10000, seed = 42) {
+  n_rounds_max <- 11
+  set.seed(seed)
+  w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE)
+  m <- matrix(w, nrow = n_sims, ncol = n_rounds_max)
+  # data.frame(x)
+  df <- as_tibble(m)
+  names(df) <- sprintf('%d', 1:n_rounds_max)
+  df$i <- 1:nrow(df)
+  
+  sim_rounds <- tibble(
+    i = rep(1:n_sims, each = n_rounds_max),
+    r = rep(1:n_sims, times = n_rounds_max),
+    w = w
+  ) |> 
+    group_by(i) |> 
+    mutate(
+      cumu_w = cumsum(w),
+      cumu_l = cumsum(w == 0)
+    ) |> 
+    ungroup() |> 
+    mutate(
+      cumu_wl_max = ifelse(cumu_w > cumu_l, cumu_w, cumu_l)
+    ) |> 
+    filter(cumu_wl_max <= 6)
+  
+  sim_rounds <- df |> 
+    pivot_longer(
+      -i,
+      names_to = 'r',
+      values_to = 'w'
+    ) |> 
+    mutate(
+      across(r, as.integer)
+    ) |> 
+    group_by(i) |> 
+    mutate(
+      cumu_w = cumsum(w),
+      cumu_l = cumsum(w == 0)
+    ) |> 
+    ungroup() |> 
+    mutate(
+      cumu_wl_max = ifelse(cumu_w > cumu_l, cumu_w, cumu_l)
+    ) |> 
+    filter(cumu_wl_max <= 6)
+  
+  sim_rounds_to_drop <- anti_join(
+    sim_rounds |> 
+      filter(cumu_wl_max == 6L),
+    sim_rounds |> 
+      filter(cumu_wl_max == 6L) |> 
+      group_by(i) |> 
+      slice_min(r, n = 1) |> 
+      ungroup(), 
+    by = c('i', 'r', 'w', 'cumu_w', 'cumu_l', 'cumu_wl_max')
+  )
+  
+  sim_rounds <- sim_rounds |> 
+    anti_join(
+      sim_rounds_to_drop, 
+      by = c('i', 'r', 'w', 'cumu_w', 'cumu_l', 'cumu_wl_max')
+    )
+  
+  ## always from offensive perspective
[…]

### 2022-08-13 presentation.qmd
re-render pres

@@
 cod_n_series <- cod_rounds |> 
-  distinct(year, sheet, series) |> 
+  distinct(series_id, team) |> 
   nrow() |> 
@@
 cod_n_rounds <- cod_rounds |> 
-  distinct(year, sheet, series, round) |> 
+  distinct(series_id, team, round) |> 
   nrow() |> 
@@
 cod_o_win_pct <- scales::percent(cod_o_win_prop_const, accuracy = 0.1)
+
+cod_rounds |> 
+  filter(is_offense) |> 
+  count(game, win_round) |> 
+  group_by(game) |> 
+  mutate(prop = n / sum(n)) |> 
+  ungroup() |> 
+  filter(win_round)
 
@@
 
+all_possible_outcomes <- tibble(
+  n_rounds = 6L:11L
+) |> 
+  mutate(
+    x = map_dbl(n_rounds, ~sample(c(0L, 1L), size = .x, replace = TRUE))
+  )
+
 cod_e_o_win_series_prop <- crossing(
@@
 
-summarize_streaks <- function(rounds) {
-  .max_round <- 11
-  .adj <- 0
-
-  cutoff <- (.max_round + 1) / 2
-
-  actual_round_streaks <- rounds |> 
+summarize_round_arrangements <- function(rounds, .max_round, .adj = 0) {
+  rounds |> 
     filter(round <= (.max_round - .adj)) |> 
@@
       losses = max(cumu_l),
-      ws = paste0(win_round, collapse = '')
+      ws = paste0(win_round, collapse = '-')
     ) |> 
@@
     mutate(prop = n / sum(n))
+}
+
+summarize_cod_round_arrangements <- partial(
+  summarize_round_arrangements,
+  .max_round = 11,
+  .adj = 0
+)
+
+summarize_streaks <- function(rounds) {
+  .max_round <- 11
+  .adj <- 0
+
+  cutoff <- (.max_round + 1) / 2
+
+  actual_round_streaks <- rounds |> 
+    summarize_round_arrangements(.max_round = .max_round, .adj = .adj)
 
@@
 p_cod_round_win_prop_after_x_wins_y_rounds <- cod_round_win_prop_after_x_wins_y_rounds |> 
+  filter(win_streak == 3) |> 
   mutate(
@@
 p_cod_round_win_prop_after_x_wins_y_rounds
+save_plot_for_slide(p_cod_round_win_prop_after_x_wins_y_rounds)
 ```
@@
 
-plot_round_vs_post_round_slope_chart <- function(df, .roun) {
-  game <- match.arg(game)
+plot_round_vs_post_round_slope_chart <- function(df, .round) {
   o_win_rx_prop <- summarize_map_o_round_win_prop(df, .round)

### 2022-08-13 1-scrape-cod.R
re-save cod rounds with factored game column

@@ -233,11 +233,13 @@ cod_rounds <- cod_series |>
     by = c('year', 'sheet', 'series', 'team')
   ) |> 
   mutate(
-    game = cod_game_mapping[as.character(year)],
+    game = sprintf('%s (%s)', cod_game_mapping[as.character(year)], year),
     .before = 1
   ) |> 
   mutate(
-    map = sprintf('%s - %s (%s)', map, game, year)
+    across(game, ~fct_reorder(.x, year)),
+    map = sprintf('%s - %s', map, game)
   )
-cod_rounds
-qs::qsave(cod_rounds, 'cod_rounds.qs')
+filename <- 'cod_rounds.qs'
+sprintf('%s%s', c('', 'paper/'), filename) |> 
+  walk(~qs::qsave(cod_rounds, .x))

### 2022-08-13 paper/paper.qmd
trying paper with inline code and first plot

@@
 
-# 1. Introduction
+```{r}
+#| label: setup
+#| eval: true
+library(dplyr)
+library(dplyr)
+library(qs)
+library(scales)
 
-## 1.1 Description of Call of Duty Search and Destroy
+cod_rounds <- qs::qread('cod_rounds.qs')
+```
+
+```{r}
+#| label: descriptive-cod-snd-stats
+#| eval: true
+cod_n_series <- cod_rounds |> 
+  distinct(series_id, team) |> 
+  nrow()
+
+cod_n_rounds <- cod_rounds |> 
+  distinct(series_id, team, round) |> 
+  nrow()
+
+cod_o_win_prop <- cod_rounds |> 
+  filter(is_offense) |> 
+  count(win_round) |> 
+  mutate(prop = n / sum(n)) |> 
+  filter(win_round) |> 
+  pull(prop)
+
+cod_o_win_prop_by_game <- cod_rounds |> 
+  filter(is_offense) |> 
+  count(game, win_round) |> 
+  group_by(game) |> 
+  mutate(prop = n / sum(n)) |> 
+  ungroup() |> 
+  filter(win_round) |> 
+  select(game, n, prop)
+
+pull_cod_o_win_prop_by_game <- function(.game) {
+  cod_o_win_prop_by_game |> 
+    filter(game == .game) |> 
+    pull(prop) |> 
+    scales::percent(accuracy = 0.1)
+}
+```
+
+# Introduction
+
+## 1 Description of Call of Duty Search and Destroy
 
@@
 Tthe most popular mode in the competitive scene is "Search and Destroy" (SnD), which bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in professional leagues.
-SnD is one-sided game mode in which one team, the offensive side, tries to destroy one of two designated bomb sites on the map.[^1]
+SnD is one-sided game mode in which one team, the offensive side, tries to destroy one of two designated bomb sites on the map.
 
-[^1]: as
+In professional CoD, a team must win six rounds of SnD to win the match.[^1] A round can end in one of four ways:
 
-In professional CoD, a team must win six rounds of SnD to win the match.[^2] A round can end in one of four ways:
-
-[^2]: A maximum of 11 even rounds can be played. There is no "sudden death" or "win by two" rule like there are for SnD equivalent in professional Counter-Strike and Valorant matches.
+[^1]: A maximum of 11 even rounds can be played. There is no "sudden death" or "win by two" rule like there are for SnD equivalent in professional Counter-Strike and Valorant matches.
 
 1.  One team eliminates all members of the other team prior to a bomb plant. (Eliminating team wins.)
-2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^3] (Offense wins.)
-3.  The defensive team defuses the bomb after a bomb plant.[^4] (Defense wins.)
+2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^2] (Offense wins.)
+3.  The defensive team defuses the bomb after a bomb plant.[^3] (Defense wins.)
 4.  The offensive team does not make a plant by the time the round timer ends. (Defense wins.)
 
-[^3]:
+[^2]:
     -   The bomb can be picked up by any member of the offensive team.
@@
 
-[^4]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+[^3]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
 
@@
 
-## 1.2 Data
+## 1. Data
 
-CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^5] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era.
-Data was collected in spreadsheets by community member "IOUTurtle".[^6]
+CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling `r scales::comma(cod_n_series)` series played, in which there were `r scales::comma(cod_n_rounds)` rounds played.
+Data was collected in spreadsheets by community member "IOUTurtle".[^5]
 
-[^5]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
+[^4]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
 Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
@@
 
-[^6]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle
+[^5]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle
 
@@
 
-## 1.3 My contribution
-
-# 2 Literature review
+# Literature review
 
@@
 Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^7]\[\^8\]
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^6]
 
-[^7]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+[^6]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
 
-# 3. Methodology
+# Methodology, results, and discussion
 
-# 4. Results and discussion
+The empirical offensive round win percentage across all rounds is `r scales::percent(cod_o_win_prop, accuracy = 0.1)`.[^7] @fig-cod-o-round-win-prop shows that offensive round win rate is not quite constant, although, on average, never veers more than 10% from this global average.
+
+[^7]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`
+
+::: {#fig-cod-o-round-win-prop}
+![](images/cod_o_round_win_prop.png){fig-align="center"}
+
+Offensive round win percentage by series state
+:::
 

### 2022-08-13 paper/paper.tex
trying paper with inline code and first plot

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, enhanced, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, boxrule=0pt, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, boxrule=0pt, breakable, interior hidden, frame hidden]}{\end{tcolorbox}}\fi
 
 \hypertarget{introduction}{%
-\section{1. Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}}
 
 \hypertarget{description-of-call-of-duty-search-and-destroy}{%
-\subsection{1.1 Description of Call of Duty Search and
+\subsection{1 Description of Call of Duty Search and
 Destroy}\label{description-of-call-of-duty-search-and-destroy}}
@@
 leagues. SnD is one-sided game mode in which one team, the offensive
-side, tries to destroy one of two designated bomb sites on the
-map.\footnote{as}
+side, tries to destroy one of two designated bomb sites on the map.
 
@@
 \hypertarget{data}{%
-\subsection{1.2 Data}\label{data}}
+\subsection{1. Data}\label{data}}
 
@@
   (2021) and Vanguard (2022).} The data set consists of all SnD matches
-played in tournaments and qualifiers during the CDL era. Data was
+played in tournaments and qualifiers during the CDL era, totaling 1,704
+series played, in which there were 15,584 rounds played. Data was
 collected in spreadsheets by community member ``IOUTurtle''.\footnote{Data:
@@
 
-\hypertarget{my-contribution}{%
-\subsection{1.3 My contribution}\label{my-contribution}}
-
 \hypertarget{literature-review}{%
-\section{2 Literature review}\label{literature-review}}
+\section{Literature review}\label{literature-review}}
 
@@
 and Valorant ((DeRover 2021)), both of which are round-based like CoD
-SnD. However, research on round-level trends is spare, perhaps because
+SnD. However, research on round-level trends is sparse, perhaps because
+games like Counter-Strike and Valorant both have economic aspects that
+can create clear advantages on side in a given round, given how prior
+rounds played out.\footnote{Additionally, both Counter-Strike and
+  Valorant have overtime rules and blocked offensive/defensive roles
+  (i.e.~playing either offense or defense for many consecutive rounds).}
+
+\hypertarget{methodology-results-and-discussion}{%
+\section{Methodology, results, and
+discussion}\label{methodology-results-and-discussion}}
+
+The empirical offensive round win percentage across all rounds is
+47.8\%.\footnote{Offensive round win percentage has been nearly constant
+  across the three games during the CDL era: MW (2020) 47.2\%, Cold War
+  (2021) 47.9\%, Vanguard (2022) 48.1\%}
+Figure~\ref{fig-cod-o-round-win-prop} shows that offensive round win
+rate is not quite constant, although, on average, never veers more than
+10\% from this global average.
+
+\begin{figure}
+
+{\centering
+
+\begin{figure}
+
+{\centering \includegraphics{images/cod_o_round_win_prop.png}
+
+}
+
+\end{figure}
+
+}
+
+\caption{\label{fig-cod-o-round-win-prop}Offensive round win percentage
+by series state}
+
+\end{figure}
 

### 2022-08-13 paper/paper.tex
render a plot without error

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, enhanced, boxrule=0pt, breakable, interior hidden, frame hidden]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi
 
@@
 
-{\centering
-
-\begin{figure}
-
 {\centering \includegraphics{images/cod_o_round_win_prop.png}
-
-}
-
-\end{figure}
 

### 2022-08-13 paper/paper.qmd
render a plot without error
more on the intro to the paper

@@
 
-[^2]:
+[^2]: Merchanics regarding the bomb:
+
     -   The bomb can be picked up by any member of the offensive team.
@@
 
-CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling `r scales::comma(cod_n_series)` series played, in which there were `r scales::comma(cod_n_rounds)` rounds played.
+CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling `r scales::comma(cod_n_rounds)` rounds across `r scales::comma(cod_n_series)` series.
 Data was collected in spreadsheets by community member "IOUTurtle".[^5]
@@
 There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state.
-Observing that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p=0.5$, [@mosteller1952] proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$ in each case: (1) a "method of moments", an approach that solves for $p$ from the empirical average number of games won by the loser of the series; (2) maximum likelihood, and (3) maximum chi-square approach.
+[@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with \$p=0.5\$..
+Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding \$p \\approx 0.65\$.
+in each case: (1) a "method of moments", an approach that solves for \$p\$.
+from the empirical average number of games won by the loser of the series; (2) maximum likelihood, and (3) maximum chi-square approach.
+
 [@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
-Chance applies Mosteller's method 1 and 2 and finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series.
-Chance outlines a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
+Chance applies finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^6] Chance's work is closely related to ours and, in fact, provides a guide for the first part of our investigation.
 
-Momentum is one of the most frequently published topics in sports analytics.
-We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
-(sentence about negative recency, hinting at "hot hand"...
-[@miller2018] debunking findings from [@gilovich1985])
+[^6]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
 
-Despite the plethora of existing research on games played and momentum in sports, these topics have yet to be investigated heavily in esports.
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^7] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
+Per \[@ayton2004\], negative recency is "the belief that, for random events, runs of a particular outcome ...
+will be balanced by a tendency for the opposite outcome", while positive recency is the expectation of observing future results that match recent results.
+
+[^7]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+
+Studying both player streaks and team streaks in basketball, in both observational and controlled settings.
+[@gilovich1985] do not find evidence for the hot hand phenomenon.
+Recently , [@miller2018] refute [@gilovich1985]'s conclusions, finding mathematical evidence that seems to support negative recency.
+Specifically, they find that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" (streak selection bias) that imply that, under i.i.d.
+conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success".
+We agree with Miller's findings, accounting for the streak selection bias in our study of momentum.
+
+Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily in esports.
 Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^6]
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^8]
 
-[^6]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+[^8]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
 
@@
 
-The empirical offensive round win percentage across all rounds is `r scales::percent(cod_o_win_prop, accuracy = 0.1)`.[^7] @fig-cod-o-round-win-prop shows that offensive round win rate is not quite constant, although, on average, never veers more than 10% from this global average.
+First, we investigate the constant probability assumption and the distribution of rounds played in a series.
+Afterwards, we investigate momentum, building on our learnings from the constant probability assumption analysis.
 
-[^7]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`
+## Distribution of rounds played
 
-::: {#fig-cod-o-round-win-prop}
-![](images/cod_o_round_win_prop.png){fig-align="center"}
+The general formula for the probability $P(i)$ that a best-of-$s$ series lasts $i$ rounds given constant probability $p$ of one team[^9] winning each round is
 
-Offensive round win percentage by series state
-:::
+[^9]: If $p > 0.5$, then we might say that this team is the better team (presumably known in hindsight)
+
+$$
+s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}
+$$
+$$
+P(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}(1 - p)^{i - s_2} + p^{i - s_2}(1 - p)^{s_2})
+$$
+
+resulting in @tbl-prob-series-lasting-i-rounds} for $s = 11$ and the naive assumption that $p = 0.5$.
+
+| Number of rounds ($i$) | $P(i)$ |
+|-----------------------:|-------:|
+|                      6 |   3.1% |
+|                      7 |   9.4% |
+|                      8 |  16.4% |
+|                      9 |  21.9% |
+|                     10 |  24.6% |
+|                     11 |  24.6% |
+
+: The probabilities that a best-of-11 series lasts $i$ rounds ($Pr(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each game {#tbl-prob-series-lasting-i-rounds}
+
+The empirical offensive round win percentage across all rounds is `r scales::percent(cod_o_win_prop, accuracy = 0.1)`.[^10] @fig-cod-o-round-win-prop shows that offensive round win rate is not quite constant, although never veers more than 10% from this global average.
+
+[^10]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`
+
+![Offensive round win percentage by series state](images/cod_o_round_win_prop.png){#fig-cod-o-round-win-prop fig-align="center"}
 

### 2022-08-13 paper/paper.tex
more on the intro to the paper

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, breakable]}{\end{tcolorbox}}\fi
 
@@
   The offensive team eliminates all members of the defensive team after
-  a bomb plant.\footnote{\begin{itemize}
+  a bomb plant.\footnote{Merchanics regarding the bomb:
+
+    \begin{itemize}
     \tightlist
@@
   (2021) and Vanguard (2022).} The data set consists of all SnD matches
-played in tournaments and qualifiers during the CDL era, totaling 1,704
-series played, in which there were 15,584 rounds played. Data was
-collected in spreadsheets by community member ``IOUTurtle''.\footnote{Data:
+played in tournaments and qualifiers during the CDL era, totaling 15,584
+rounds across 1,704 series. Data was collected in spreadsheets by
+community member ``IOUTurtle''.\footnote{Data:
   https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle}
@@
 a given team winning a game in the series, regardless of the series
-state. Observing that the American League had dominated the National
-League in Major League Baseball's (MLB) World Series matchups, implying
-that matchups should not modeled with \(p=0.5\), (Mosteller 1952)
-proposed three approaches for identifying the optimal constant
-probability value of the stronger team in the World Series, finding
-\(p \approx 0.65\) in each case: (1) a ``method of moments'', an
-approach that solves for \(p\) from the empirical average number of
+state. (Mosteller 1952) observed that the American League had dominated
+the National League in Major League Baseball's (MLB) World Series
+matchups, implying that matchups should not modeled with \$p=0.5\$..
+Mosteller proposed three approaches for identifying the optimal constant
+probability value of the stronger team in the World Series, finding \$p
+\textbackslash approx 0.65\$. in each case: (1) a ``method of moments'',
+an approach that solves for \$p\$. from the empirical average number of
 games won by the loser of the series; (2) maximum likelihood, and (3)
-maximum chi-square approach. (Chance 2020) re-examines the constant
-probability notion in Major League Baseball's World Series (1923--2018),
-the National Basketball Association's Finals (1951--2018), and the
-National Hockey League's Stanley Cup (1939--2018). Chance applies
-Mosteller's method 1 and 2 and finds strong evidence against the null
-hypothesis of \(p = 0.5\) in the MLB and NHL championship series. Chance
-outlines a conditional probability framework (likelihood of winning a
-game given the series state) which can exactly explain the distribution
-of the number of games played.
+maximum chi-square approach.
 
-Momentum is one of the most frequently published topics in sports
-analytics. We often use use ``streaks'' and momentum interchangeably,
-but as (Steeger, Dulin, and Gonzalez 2021) note, momentum implies
-dependence between events, whereas streaking does not. (sentence about
-negative recency, hinting at ``hot hand''\ldots{} (Miller and Sanjurjo
-2018) debunking findings from (Gilovich, Vallone, and Tversky 1985))
+(Chance 2020) re-examines the constant probability notion in Major
+League Baseball's World Series (1923--2018), the National Basketball
+Association's Finals (1951--2018), and the National Hockey League's
+Stanley Cup (1939--2018). Chance applies finds strong evidence against
+the null hypothesis of \(p = 0.5\) in the MLB and NHL championship
+series when applying Mosteller's first and second methods.\footnote{Chance
+  goes on to outline a conditional probability framework (likelihood of
+  winning a game given the series state) which can exactly explain the
+  distribution of the number of games played.} Chance's work is closely
+related to ours and, in fact, provides a guide for the first part of our
+investigation.
 
-Despite the plethora of existing research on games played and momentum
-in sports, these topics have yet to be investigated heavily in esports.
-Work has been done to examine in-round win probability in other FPS
-titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva 2022))
-and Valorant ((DeRover 2021)), both of which are round-based like CoD
-SnD. However, research on round-level trends is sparse, perhaps because
-games like Counter-Strike and Valorant both have economic aspects that
-can create clear advantages on side in a given round, given how prior
-rounds played out.\footnote{Additionally, both Counter-Strike and
-  Valorant have overtime rules and blocked offensive/defensive roles
+Momentum, one of most discussed topics in sports analytics, goes
+hand-in-hand with a discussion of the nature of series
+outcomes.\footnote{We often use use ``streaks'' and momentum
+  interchangeably, but as (Steeger, Dulin, and Gonzalez 2021) note,
+  momentum implies dependence between events, whereas streaking does
+  not.} Two opposing fallacies are observed in the context of momentum:
+the ``gambler's fallacy'' (negative recency) and ``hot hand fallacy''
+(positive recency). Per {[}Ayton and Fischer (2004){]}, negative recency
+is ``the belief that, for random events, runs of a particular outcome
+\ldots{} will be balanced by a tendency for the opposite outcome'',
+while positive recency is the expectation of observing future results
+that match recent results.
+
+Studying both player streaks and team streaks in basketball, in both
+observational and controlled settings. (Gilovich, Vallone, and Tversky
+1985) do not find evidence for the hot hand phenomenon. Recently ,
+(Miller and Sanjurjo 2018) refute (Gilovich, Vallone, and Tversky
+1985)'s conclusions, finding mathematical evidence that seems to support
+negative recency. Specifically, they find that a ``bias exists in a
+common measure of the conditional dependence of present outcomes on
+streaks of past outcomes in sequential data'' (streak selection bias)
+that imply that, under i.i.d. conditions, ``the proportion of successes
+among the outcomes that immediately follow a streak of consecutive
+successes is expected to be strictly less than the underlying
+(conditional) probability of success''. We agree with Miller's findings,
+accounting for the streak selection bias in our study of momentum.
+
+Despite the plethora of existing research on games played in a series
+and momentum in sports, these topics have yet to be investigated heavily
+in esports. Work has been done to examine in-round win probability in
+other FPS titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva
+2022)) and Valorant ((DeRover 2021)), both of which are round-based like
+CoD SnD. However, research on round-level trends is sparse, perhaps
+because games like Counter-Strike and Valorant both have economic
+aspects that can create clear advantages on side in a given round, given
+how prior rounds played out.\footnote{Additionally, both Counter-Strike
+  and Valorant have overtime rules and blocked offensive/defensive roles
   (i.e.~playing either offense or defense for many consecutive rounds).}
@@
 
+First, we investigate the constant probability assumption and the
+distribution of rounds played in a series. Afterwards, we investigate
+momentum, building on our learnings from the constant probability
+assumption analysis.
+
+\hypertarget{distribution-of-rounds-played}{%
+\subsection{Distribution of rounds
+played}\label{distribution-of-rounds-played}}
+
+The general formula for the probability \(P(i)\) that a best-of-\(s\)
+series lasts \(i\) rounds given constant probability \(p\) of one
+team\footnote{If \(p > 0.5\), then we might say that this team is the
+  better team (presumably known in hindsight)} winning each round is
+
+\[
+s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}
+\]
+
+\[
+P(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}(1 - p)^{i - s_2} + p^{i - s_2}(1 - p)^{s_2})
+\]
+
+resulting in Table~\ref{tbl-prob-series-lasting-i-rounds}\} for
+\(s = 11\) and the naive assumption that \(p = 0.5\).
+
+\hypertarget{tbl-prob-series-lasting-i-rounds}{}
+\begin{longtable}[]{@{}rr@{}}
+\caption{\label{tbl-prob-series-lasting-i-rounds}The probabilities that
+a best-of-11 series lasts \(i\) rounds (\(Pr(i)\), where
+\(i = {6, 7, 8, 9, 10, 11}\)) under the assumption that each team has a
+50\% probability (\(p = 0.5\)) of winning each game}\tabularnewline
+\toprule()
+Number of rounds (\(i\)) & \(P(i)\) \\
+\midrule()
+\endfirsthead
+\toprule()
+Number of rounds (\(i\)) & \(P(i)\) \\
+\midrule()
+\endhead
+6 & 3.1\% \\
+7 & 9.4\% \\
+8 & 16.4\% \\
+9 & 21.9\% \\
+10 & 24.6\% \\
+11 & 24.6\% \\
+\bottomrule()
+\end{longtable}
+
 The empirical offensive round win percentage across all rounds is
@@
 Figure~\ref{fig-cod-o-round-win-prop} shows that offensive round win
-rate is not quite constant, although, on average, never veers more than
-10\% from this global average.
+rate is not quite constant, although never veers more than 10\% from
+this global average.
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-ayton2004}{}}%
+Ayton, Peter, and Ilan Fischer. 2004. {``The Hot Hand Fallacy and the
+Gambler{'}s Fallacy: Two Faces of Subjective Randomness?''} \emph{Memory
+\& Cognition} 32 (8): 13691378.
+
 \leavevmode\vadjust pre{\hypertarget{ref-chance2020}{}}%

### 2022-08-13 presentation.qmd
more on the intro to the paper

@@
 
-all_possible_outcomes <- tibble(
-  n_rounds = 6L:11L
-) |> 
-  mutate(
-    x = map_dbl(n_rounds, ~sample(c(0L, 1L), size = .x, replace = TRUE))
-  )
-
 cod_e_o_win_series_prop <- crossing(
@@
 
-plot_series_outcome_prop_over_expected <- function(series_outcome_prop, game) {
+plot_series_outcome_prop_over_expected <- function(series_outcome_prop) {
   .lvls <- sprintf('6-%d', 0:5)
@@
 avg_expected_cod_rounds_per_series <- 9.29
-cod_series_outcomes_chi <- '15.4 (<=0.01)'
+cod_series_outcomes_chi <- '16.0 (<=0.01)'
 ```

### 2022-08-14 paper/paper.qmd
mostly done with series length analysis

@@
 library(dplyr)
-library(dplyr)
 library(qs)
+library(tidyr)
+# library(gt)
 library(scales)
@@
 cod_n_series <- cod_rounds |> 
-  distinct(series_id, team) |> 
+  distinct(series_id) |> 
   nrow()
@@
 cod_n_rounds <- cod_rounds |> 
-  distinct(series_id, team, round) |> 
+  distinct(series_id, round) |> 
   nrow()
@@
 
-## 1 Description of Call of Duty Search and Destroy
+## Description of Call of Duty Search and Destroy
 
@@
 
+[^3]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+
 -   The bomb can be picked up by any member of the offensive team.
@@
 
-[^3]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
-
 Teams take turns playing offense and defense every round.
 
-## 1. Data
+We adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
+A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
 
-CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling `r scales::comma(cod_n_rounds)` rounds across `r scales::comma(cod_n_series)` series.
+## Data
+
+CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
 Data was collected in spreadsheets by community member "IOUTurtle".[^5]
@@
 
-I adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
-A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
+The empirical offensive round win percentage across all rounds is 47.8%.[^6] To contextualize our subsequent discussion of series length and momentum, table 1 shows round win percentages by series "state" (i.e.
+the number of round wins by each team prior to an upcoming round).
+Offensive round win rate is not quite constant, although never veers more than 10% from this global average.
 
+[^6]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`
+
+```{r}
+#| label: cod_o_win_prop
+#| eval: false
+cod_round_and_series_win_prop_by_side <- cod_rounds |>
+  group_by(pre_cumu_w, pre_cumu_l, is_offense) |>
+  summarize(
+    n = n(),
+    across(c(win_round, win_series), sum)
+  ) |>
+  ungroup() |>
+  mutate(
+    win_round_prop = win_round / n,
+    win_series_prop = win_series / n
+  )
+
+cod_round_and_series_win_prop_by_side |>
+  filter(is_offense) |>
+  transmute(
+    pre_cumu_w,
+    pre_cumu_l,
+    lab = sprintf('%.1f%%\n(%s)', round(100 * win_round_prop, 1), n)
+  ) |>
+  pivot_wider(
+    names_from = pre_cumu_l,
+    values_from = lab
+  ) |>
+  arrange(pre_cumu_w) |>
+  gt::gt() |>
+  gt::cols_label(
+    pre_cumu_w = "Defensive team's round wins",
+  ) |>
+  gt::tab_spanner(
+    label = "Offensive team's round wins",
+    columns = `0`:`5`
+  ) |>
+  gt::as_latex()
+```
+
+```{=tex}
+\captionsetup[table]{labelformat=empty,skip=1pt}
+\begin{longtable}{rrrrrrr}
+\toprule
+ & \multicolumn{6}{c}{Offensive team's round wins} \\ 
+\cmidrule(lr){2-7}
+Defensive team's round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
+\midrule
+0 & 47.8\%
+(852) & 46.6\%
+(408) & 43.1\%
+(216) & 43.5\%
+(115) & 43.3\%
+(67) & 40.5\%
+(37) \\ 
+1 & 48.6\%
+(444) & 49.3\%
+(418) & 51.5\%
+(309) & 43.4\%
+(205) & 43.3\%
+(120) & 39.4\%
+(99) \\ 
+2 & 52.8\%
+(218) & 48.9\%
+(305) & 48.9\%
+(315) & 46.6\%
+(262) & 48.7\%
+(189) & 42.1\%
+(133) \\ 
+3 & 54.5\%
+(123) & 46.0\%
+(200) & 49.6\%
+(250) & 45.6\%
+(248) & 44.4\%
+(214) & 44.8\%
+(174) \\ 
+4 & 56.9\%
+(65) & 54.5\%
+(145) & 47.2\%
+(193) & 44.7\%
+(228) & 55.2\%
+(221) & 50.5\%
+(208) \\ 
+5 & 47.4\%
+(38) & 49.4\%
+(83) & 47.1\%
+(136) & 50.9\%
+(175) & 45.2\%
+(177) & 46.0\%
+(202) \\ 
+\bottomrule
+\end{longtable}
+```
 # Literature review
@@
 There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state.
-[@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with \$p=0.5\$..
-Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding \$p \\approx 0.65\$.
-in each case: (1) a "method of moments", an approach that solves for \$p\$.
-from the empirical average number of games won by the loser of the series; (2) maximum likelihood, and (3) maximum chi-square approach.
+[@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with \$p=0.5\$.
+Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$.
+in each case: (1) a "method of moments" approach in which one solves for $p$.
+from the empirical average number of games won by the loser of the series; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series, and (3) minimizing the chi-square goodness of fit estimate for $p$.
 
 [@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
-Chance applies finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^6] Chance's work is closely related to ours and, in fact, provides a guide for the first part of our investigation.
+Chance applies finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^7] Chance's work is closely related to ours and, in fact, provides a guide for the first part of our investigation.
 
-[^6]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
+[^7]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^7] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
-Per \[@ayton2004\], negative recency is "the belief that, for random events, runs of a particular outcome ...
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^8] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
+Per [@ayton2004], negative recency is "the belief that, for random events, runs of a particular outcome ...
 will be balanced by a tendency for the opposite outcome", while positive recency is the expectation of observing future results that match recent results.
 
-[^7]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^8]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^8]
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^9]
 
-[^8]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+[^9]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
 
@@
 
-The general formula for the probability $P(i)$ that a best-of-$s$ series lasts $i$ rounds given constant probability $p$ of one team[^9] winning each round is
+The general formula for the probability $P_E(i)$ that a best-of-$s$ series lasts $i$ rounds given constant probability $p$ of one team[^10] winning each round is
 
-[^9]: If $p > 0.5$, then we might say that this team is the better team (presumably known in hindsight)
+[^10]: If $p > 0.5$, then we might say that this team is the better team (presumably known in hindsight)
 
 $$
-s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}
-$$
-$$
-P(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}(1 - p)^{i - s_2} + p^{i - s_2}(1 - p)^{s_2})
+q = 1 - p, s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}, s_2^{'} = 1 - s_2
 $$
 
-resulting in @tbl-prob-series-lasting-i-rounds} for $s = 11$ and the naive assumption that $p = 0.5$.
+$$
+P_E(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
+$$ {#eq-series-length}
 
-| Number of rounds ($i$) | $P(i)$ |
-|-----------------------:|-------:|
-|                      6 |   3.1% |
-|                      7 |   9.4% |
-|                      8 |  16.4% |
-|                      9 |  21.9% |
-|                     10 |  24.6% |
-|                     11 |  24.6% |
+```{r}
+#| label: cod_series_outcome_prop
+#| eval: true
+.max_round <- 11
+.cutoff <- 6
+prob_of_series_lasting_n_games <- function(n, p = 0.5, max_round = .max_round) {
+  s <- ceiling(max_round / 2)
+  (factorial(n - 1) / (factorial(s - 1) * factorial(n - s))) * (p^s * (1 - p)^(n - s) + p^(n - s) * (1 - p)^s)
+}
 
-: The probabilities that a best-of-11 series lasts $i$ rounds ($Pr(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each game {#tbl-prob-series-lasting-i-rounds}
+expected_series_streaks_of_outcomes <- function(m, n) {
+  factorial(m + n) / (factorial(m) * factorial(n))
+}
 
-The empirical offensive round win percentage across all rounds is `r scales::percent(cod_o_win_prop, accuracy = 0.1)`.[^10] @fig-cod-o-round-win-prop shows that offensive round win rate is not quite constant, although never veers more than 10% from this global average.
+# https://raw.githubusercontent.com/dgrtwo/splittestr/master/R/vectorized-prop-test.R
+vectorized_prop_test_approx <- function(a, b, c, d) {
+  n1 <- a + b
+  n2 <- c + d
+  n <- n1 + n2
+  p <- (a + c) / n
+  E <- cbind(p * n1, (1 - p) * n1, p * n2, (1 - p) * n2)
 
-[^10]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`
+  x <- cbind(a, b, c, d)
 
-![Offensive round win percentage by series state](images/cod_o_round_win_prop.png){#fig-cod-o-round-win-prop fig-align="center"}
+  DELTA <- a / n1 - c / n2
+  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
+
+  STATISTIC <- rowSums((abs(x - E) - YATES)^2 / E)
+  PVAL <- pchisq(STATISTIC, 1, lower.tail = FALSE)
+  PVAL
+}
+
+vectorized_prop_test_exact <- function(a, b, c, d) {
+  sapply(seq_along(a), function(i) {
+    fisher.test(cbind(c(a[i], c[i]), c(b[i], d[i])))$p.value
+  })
+}
+
+vectorized_prop_test <- function(x1, n1, x2, n2, conf.level = 0.95) {
+  a <- x1
+  b <- n1 - x1
+  c <- x2
+  d <- n2 - x2
+
+  # if any values are < 20, use Fisher's exact test
+  exact <- (a < 20 | b < 20 | c < 20 | d < 20)
+
+  pvalue <- rep(NA, length(a))
+
+  if (any(exact)) {
+    pvalue[exact] <- vectorized_prop_test_exact(a[exact], b[exact], c[exact], d[exact])
+  }
+  if (any(!exact)) {
+    pvalue[!exact] <- vectorized_prop_test_approx(a[!exact], b[!exact], c[!exact], d[!exact])
+  }
+
+  mu1 <- a / (a + b)
+  mu2 <- c / (c + d)
+
+  ## confidence interval
+  alpha2 <- (1 - conf.level) / 2
+  DELTA <- mu2 - mu1
+  WIDTH <- qnorm(alpha2)
+  alpha <- (a + .5) / (a + b + 1)
+  beta <- (c + .5) / (c + d + 1)
+
+  n <- n1 + n2
+  YATES <- pmin(.5, abs(DELTA) / sum(1 / n1 + 1 / n2))
+
+  z <- qnorm((1 + conf.level) / 2)
+  WIDTH <- z * sqrt(mu1 * (1 - mu1) / n1 + mu2 * (1 - mu2) / n2)
+
+  tibble(
+    estimate = DELTA,
+    conf.low = pmax(DELTA - WIDTH, -1),
+    conf.high = pmin(DELTA + WIDTH, 1),
+    p.value = pvalue
+  )
+}
+
+cod_actual_round_streaks <- cod_rounds |> 
+  filter(round <= .max_round) |> 
+  filter(win_series) |> 
+  mutate(across(win_round, as.integer)) |> 
+  group_by(series_id) |> 
+  summarize(
+    wins = max(cumu_w),
+    losses = max(cumu_l),
+    ws = paste0(win_round, collapse = '-')
+  ) |> 
+  ungroup() |> 
+  mutate(n_rounds = wins + losses) |> 
+  unite(
+    record, wins, losses, sep = '-'
+  ) |>
+  count(record, n_rounds, ws, sort = TRUE) |> 
+  mutate(prop = n / sum(n))
+
+summarize_cod_streaks <- function(p = 0.5) {
+
+  expected_round_streaks <- tibble(
+    n_rounds = .cutoff:.max_round
+  ) |> 
+    mutate(
+      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_n_games(.x, max_round = .max_round, p = !!p)),
+      n_expected_series_streaks = map_dbl(n_rounds, ~expected_series_streaks_of_outcomes(.cutoff, .x - .cutoff))
+    ) |> 
+    transmute(
+      n_rounds,
+      series_prop,
+      prop = series_prop / n_expected_series_streaks
+    )
+
+  round_streaks <- full_join(
+    cod_actual_round_streaks |> 
+      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+    expected_round_streaks |> 
+      rename_with(~sprintf('%s_expected', .x), prop),
+    by = 'n_rounds'
+  )
+
+  round_streak_prop <- round_streaks |> 
+    drop_na() |> 
+    mutate(
+      prop_diff = prop_actual - prop_expected,
+      total_actual = sum(n_actual),
+      n_expected = round(prop_expected * total_actual),
+      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
+    ) |> 
+    select(-total_actual) |> 
+    unnest_wider(p) |> 
+    arrange(p.value)
+
+  series_outcomes <- full_join(
+    cod_actual_round_streaks |> 
+      group_by(record, n_rounds) |> 
+      summarize(
+        across(n, sum)
+      ) |> 
+      ungroup() |> 
+      mutate(prop = n / sum(n)) |> 
+      rename_with(~sprintf('%s_actual', .x), c(n, prop)),
+    expected_round_streaks |> 
+      select(n_rounds, prop_expected = series_prop),
+    by = 'n_rounds'
+  )
+
+  series_outcome_prop <- series_outcomes |> 
+    drop_na() |> 
+    mutate(
+      prop_diff = prop_actual - prop_expected,
+      total_actual = sum(n_actual),
+      n_expected = round(prop_expected * total_actual),
+      p = vectorized_prop_test(n_actual, total_actual, n_expected, total_actual)
+    ) |> 
+    select(-total_actual) |> 
+    unnest_wider(p) |> 
+    arrange(p.value)
+
+  list(
+    rounds = round_streak_prop,
+    series = series_outcome_prop
+  )
+}
+
+cod_streaks_naive_res <- summarize_cod_streaks(p = 0.5)
+```
+
+```{r}
+#| label: cod_series_outcome_prop-table
+cod_streaks_naive_res$series |>
+  select(
+    n_rounds,
+    prop_expected,
+    prop_actual,
+    n_actual
+  ) |>
+  arrange(n_rounds) |>
+  gt::gt() |>
+  gt::cols_label(
+    n_rounds = 'Series lasts\ni rounds',
+    prop_expected = 'P_{E}(i)',
+    prop_actual = 'P_{O}(i)',
+    n_actual = 'N_O'
+  ) |>
+  gt::fmt_percent(
+    decimals = 1,
+    columns = c('prop_expected', 'prop_actual')
+  ) |>
+  gt::tab_spanner(
+    label = 'Observed',
+    columns = c('prop_actual', 'n_actual')
+  ) |>
+  gt::as_latex()
+```
+
+Table 2 shows the expected proportion for $s = 11$ and the naive assumption that $p = 0.5$, along with the observed proportion $P_{O}(i)$ for CoD SnD.
+
+```{=tex}
+\captionsetup[table]{labelformat=empty,skip=1pt}
+\begin{longtable}{rrrr}
+\toprule
+&  & \multicolumn{2}{c}{Observed} \\ 
+\cmidrule(lr){3-4}
+Series lasts $i$ rounds & $P_E(i)$ & $P_O(i)$ & $N_O(i)$ \\ 
+\midrule
+6 & $3.1\%$ & $4.7\%$ & 40 \\ 
+7 & $9.4\%$ & $11.9\%$ & 101 \\ 
+8 & $16.4\%$ & $16.5\%$ & 141 \\ 
+9 & $21.9\%$ & $21.7\%$ & 185 \\ 
+10 & $24.6\%$ & $21.5\%$ & 183 \\ 
+11 & $24.6\%$ & $23.7\%$ & 202 \\ 
+\bottomrule
+\end{longtable}
+```
+The probabilities that a best-of-11 series lasts $i$ rounds ($P(i)$, where $i \in R = [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each game {#tbl-prob-series-lasting-i-rounds} along with the observed frequencies of series lasting $i$ rounds, expressed as a percentage $P_O(i)$ and as a count ($N_O$)
+
+```{r}
+#| label: cod_series_outcomes_chi
+#| eval: false
+generate_chi_label <- function(statistic, p.value) {
+  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
+}
+
+perform_series_chi_test <- function(series) {
+  chisq.test(
+    series$n_actual, 
+    p = series$prop_expected
+  ) |> 
+    broom::tidy()
+}
+
+cod_series_outcomes_naive_chi <- cod_streaks_naive_res$series |> 
+  perform_series_chi_test()
+```
+
+Calculating the chi-square goodness of fit statistic
+
+$$
+\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11]
+$$
+
+as `r scales::number(cod_series_outcomes_naive_chi$statistic, accuracy = 0.1)` (p-value of `r scales::number(cod_series_outcomes_naive_chi$p.value, accuracy = 0.0001)`), we can comfortably reject the constant probability null hypothesis, event at a confidence level of $\alpha = 0.01$.
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-prep
+#| eval: false
+min_p1 <- 0.5
+max_p1 <- 0.7
+interval_p1 <- 0.0025
+cod_ps <- tibble(p = seq(min_p1, max_p1, by = 0.0025))
+```
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-1
+#| eval: false
+# p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
+theoretical_cod_series_length <- function(p) {
+  6 * prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11) +
+    7 * prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11) +
+    8 * prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11) +
+    9 * prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11) +
+    10 * prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11) +
+    11 * prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)
+}
+cod_rounds_per_series <- cod_streaks_naive_res$series |>
+  summarize(
+    actual = sum(n_rounds * prop_actual),
+    expected = sum(n_rounds * prop_expected)
+  )
+
+cod_theoretical_series_lengths1 <- cod_ps |>
+  mutate(
+    theoretical_series_length = map_dbl(p, theoretical_cod_series_length),
+    diff = theoretical_series_length - cod_rounds_per_series$actual
+  )
+
+cod_theoretical_p1 <- cod_theoretical_series_lengths1 |>
+  slice_min(abs(diff), n = 1) |>
+  pull(p)
+```
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-2
+#| eval: false
+pluck_cod_n <- function(.n_rounds) {
+  cod_streaks_naive_res$series |>
+    filter(n_rounds == .n_rounds) |>
+    pull(n_actual)
+}
+
+cod_n6 <- pluck_cod_n(6)
+cod_n7 <- pluck_cod_n(7)
+cod_n8 <- pluck_cod_n(8)
+cod_n9 <- pluck_cod_n(9)
+cod_n10 <- pluck_cod_n(10)
+cod_n11 <- pluck_cod_n(11)
+
+## This adjustment is something that is not done in the paper. I do it here to reduce
+##   the magnitude of the exponents.
+cod_pm <- pmin(cod_n6, cod_n7, cod_n8, cod_n9, cod_n10, cod_n11)
+cod_n6adj <- round(10 * cod_n6 / cod_pm)
+cod_n7adj <- round(10 * cod_n7 / cod_pm)
+cod_n8adj <- round(10 * cod_n8 / cod_pm)
+cod_n9adj <- round(10 * cod_n9 / cod_pm)
+cod_n10adj <- round(10 * cod_n10 / cod_pm)
+cod_n11adj <- round(10 * cod_n11 / cod_pm)
+
+maximize_cod_series_p <- function(p) {
+  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^cod_n6adj *
+    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^cod_n7adj *
+    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^cod_n8adj *
+    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^cod_n9adj *
+    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^cod_n10adj *
+    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^cod_n11adj
+}
+
+cod_theoretical_series_lengths2 <- cod_ps |>
+  mutate(
+    theoretical_series_length = map_dbl(p, maximize_cod_series_p)
+  )
+
+cod_theoretical_p2 <- cod_theoretical_series_lengths2 |>
+  slice_max(theoretical_series_length, n = 1) |>
+  pull(p)
+```
+
+```{r}
+#| label: cod-alternative-to-p=0.5-method-3
+#| eval: false
+summarize_cod_series_chi <- function(p) {
+  summarize_cod_streaks(p) |> 
+    pluck('series') |> 
+    perform_series_chi_test()
+}
+
+cod_theoretical_series_lengths3 <- cod_ps |> 
+  filter(p >= 0.56, p < 0.585) |> 
+  mutate(
+    chi_squ = map_dbl(
+      p,
+      ~summarize_cod_series_chi(.x) |> 
+        pluck('statistic')
+    )
+  )
+
+cod_theoretical_p3 <- cod_theoretical_series_lengths3 |> 
+  slice_min(chi_squ, n = 1) |> 
+  pull(p)
+```
+
+```{r}
+#| label: cod-alternatives-to-p=0.5
+#| eval: false
+cod_streaks_other_res <- tibble(
+  p = c(0.5, cod_theoretical_p1, cod_theoretical_p2, cod_theoretical_p3),
+  idx = 0L:3L,
+  name = c('0. Naive', '1. Method of moments', '2. Maximum likelihood', '3. Minimum Chi-square')
+) |> 
+  mutate(
+    series_streaks = map(
+      p,
+      ~summarize_cod_streaks(.x) |> 
+        pluck('series') 
+    ),
+    chi_squ = map(
+      series_streaks,
+      ~.x |> 
+        perform_series_chi_test() |> 
+        select(statistic, p.value)
+    )
+  )
+
+cod_streaks_other_res |>
+  select(name, p, chi_squ) |>
+  unnest(chi_squ) |>
+  mutate(
+    lab = generate_chi_label(statistic, p.value)
+  ) |>
+  select(
+    `Method` = name,
+    `$p$` = p,
+    `$\\chi^2$ (p-value)` = lab
+  ) |>
+  knitr::kable()
+
+cod_streaks_other_res |>
+  mutate(
+    lab = sprintf('%s. p = %s', idx, p)
+  ) |>
+  select(lab, series_streaks) |>
+  unnest(series_streaks) |>
+  select(lab, n_rounds, prop_expected) |>
+  mutate(
+    across(prop_expected, ~scales::percent(.x, accuracy = 0.1))
+  ) |>
+  pivot_wider(
+    names_from = lab,
+    values_from = prop_expected
+  ) |>
+  inner_join(
+    cod_streaks_naive_res$series |>
+      transmute(n_rounds, `$P_O(i)$` = scales::percent(prop_actual, accuracy = 0.1)),
+    by = 'n_rounds'
+  ) |>
+  arrange(n_rounds) |>
+  rename(`Series lasts $i$ rounds` = n_rounds) |>
+  knitr::kable()
+```
+
+@tbl-mosteller-methods shows the alternate values for the constant round win probability $p$ for winning a given round in a CoD SnD that we find when applying the three methods suggested by [@mosteller1952].
+Each is approximately or equal to 0.575, and each results in a $chi^2$ value for which we cannot reject constant probability null hypothesis.
+
+| Method                 |    $p$ | $\chi^2$ (p-value) |
+|:-----------------------|-------:|-------------------:|
+| 0\. Naive              | 0.5000 |     16.0 (\<=0.01) |
+| 1\. Method of moments  | 0.5725 |          3.6 (0.6) |
+| 2\. Maximum likelihood | 0.5750 |         3.5 (0.62) |
+| 3\. Minimum $\chi^2$   | 0.5775 |         3.5 (0.62) |
+
+: Alternate estimates of the constant probability $p$ for winning a given round in a CoD SnD, applying the three methods suggested by [@mosteller1952], in addition to the naive $p = 0.5$.
+{#tbl-mosteller-methods}
+
+@tbl-expected-series-lengths-alternative-ps shows the new $P_E(i)$ when re-applying @eq-series-length for each new $p$.
+We observe that $P_E(i)$ is notably smaller for $p_{1,2,3}$ when $i \in [10, 11]$ and higher for $i \in [6, 7]$, more closely matching $P_O(i)$.
+
+| Series lasts $i$ rounds | 0\. $p$= 0.5 | 1\. $p$ = 0.5725 | 2\. $p$ = 0.575 | 3\. $p$ = 0.5775 | $P_O(i)$ |
+|------------------------:|-------------:|-----------------:|----------------:|-----------------:|---------:|
+|                       6 |         3.1% |             4.1% |            4.2% |             4.3% |     4.7% |
+|                       7 |         9.4% |            11.1% |           11.2% |            11.4% |    11.9% |
+|                       8 |        16.4% |            17.7% |           17.8% |            17.9% |    16.5% |
+|                       9 |        21.9% |            21.8% |           21.8% |            21.8% |    21.7% |
+|                      10 |        24.6% |            23.1% |           23.0% |            22.9% |    21.5% |
+|                      11 |        24.6% |            22.1% |           22.0% |            21.8% |    23.7% |
+
+: Caption {#tbl-expected-series-lengths-alternative-ps}
 

### 2022-08-14 paper/paper.tex
mostly done with series length analysis

@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, boxrule=0pt, enhanced, borderline west={3pt}{0pt}{shadecolor}, frame hidden, sharp corners, breakable]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, breakable, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 \hypertarget{description-of-call-of-duty-search-and-destroy}{%
-\subsection{1 Description of Call of Duty Search and
+\subsection{Description of Call of Duty Search and
 Destroy}\label{description-of-call-of-duty-search-and-destroy}}
@@
   The offensive team eliminates all members of the defensive team after
-  a bomb plant.\footnote{Merchanics regarding the bomb:
-
-    \begin{itemize}
-    \tightlist
-    \item
-      The bomb can be picked up by any member of the offensive team.
-    \item
-      The bomb carrier is not obstructed at all by carrying the bomb
-      (i.e.~movement is the same, weapon usage is the same).
-    \item
-      The defense does not get any visual indication for who is carrying
-      the bomb.
-    \item
-      A bomb plant takes five seconds. The timer resets if the player
-      stops planting site prior to completing it.
-    \item
-      A bomb defuse takes seven seconds. The timer resets if the player
-      ``drops'' the bomb.
-    \item
-      The bomb takes 45 seconds to defuse after being planted.
-    \end{itemize}} (Offense wins.)
+  a bomb plant.\footnote{Merchanics regarding the bomb:} (Offense wins.)
 \item
@@
 
+\begin{itemize}
+\tightlist
+\item
+  The bomb can be picked up by any member of the offensive team.
+\item
+  The bomb carrier is not obstructed at all by carrying the bomb
+  (i.e.~movement is the same, weapon usage is the same).
+\item
+  The defense does not get any visual indication for who is carrying the
+  bomb.
+\item
+  A bomb plant takes five seconds. The timer resets if the player stops
+  planting site prior to completing it.
+\item
+  A bomb defuse takes seven seconds. The timer resets if the player
+  ``drops'' the bomb.
+\item
+  The bomb takes 45 seconds to defuse after being planted.
+\end{itemize}
+
 Teams take turns playing offense and defense every round.
 
+We adopt the terminology ``series'' to refer to what CoD SnD players
+typically call a ``match'', so as to emulate the terminology of playoff
+series in professional leagues like the National Basketball Association,
+National Hockey League, and Major League Baseball. A ``game'' or a
+``match'' in such leagues is analogous to a ``round'' of CoD SnD.
+
 \hypertarget{data}{%
-\subsection{1. Data}\label{data}}
+\subsection{Data}\label{data}}
 
@@
 
-I adopt the terminology ``series'' to refer to what CoD SnD players
-typically call a ``match'', so as to emulate the terminology of playoff
-series in professional leagues like the National Basketball Association,
-National Hockey League, and Major League Baseball. A ``game'' or a
-``match'' in such leagues is analogous to a ``round'' of CoD SnD.
+The empirical offensive round win percentage across all rounds is
+47.8\%.\footnote{Offensive round win percentage has been nearly constant
+  across the three games during the CDL era: MW (2020) 47.2\%, Cold War
+  (2021) 47.9\%, Vanguard (2022) 48.1\%} To contextualize our subsequent
+discussion of series length and momentum, table 1 shows round win
+percentages by series ``state'' (i.e.~the number of round wins by each
+team prior to an upcoming round). Offensive round win rate is not quite
+constant, although never veers more than 10\% from this global average.
+
+\captionsetup[table]{labelformat=empty,skip=1pt}
+\begin{longtable}{rllllll}
+\toprule
+ & \multicolumn{6}{c}{Offensive team's round wins} \\ 
+\cmidrule(r){2-7}
+Defensive team's round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
+\midrule
+0 & 47.8\%
+(852) & 46.6\%
+(408) & 43.1\%
+(216) & 43.5\%
+(115) & 43.3\%
+(67) & 40.5\%
+(37) \\ 
+1 & 48.6\%
+(444) & 49.3\%
+(418) & 51.5\%
+(309) & 43.4\%
+(205) & 43.3\%
+(120) & 39.4\%
+(99) \\ 
+2 & 52.8\%
+(218) & 48.9\%
+(305) & 48.9\%
+(315) & 46.6\%
+(262) & 48.7\%
+(189) & 42.1\%
+(133) \\ 
+3 & 54.5\%
+(123) & 46.0\%
+(200) & 49.6\%
+(250) & 45.6\%
+(248) & 44.4\%
+(214) & 44.8\%
+(174) \\ 
+4 & 56.9\%
+(65) & 54.5\%
+(145) & 47.2\%
+(193) & 44.7\%
+(228) & 55.2\%
+(221) & 50.5\%
+(208) \\ 
+5 & 47.4\%
+(38) & 49.4\%
+(83) & 47.1\%
+(136) & 50.9\%
+(175) & 45.2\%
+(177) & 46.0\%
+(202) \\ 
+\bottomrule
+\end{longtable}
 
@@
 the National League in Major League Baseball's (MLB) World Series
-matchups, implying that matchups should not modeled with \$p=0.5\$..
+matchups, implying that matchups should not modeled with \$p=0.5\$.
 Mosteller proposed three approaches for identifying the optimal constant
-probability value of the stronger team in the World Series, finding \$p
-\textbackslash approx 0.65\$. in each case: (1) a ``method of moments'',
-an approach that solves for \$p\$. from the empirical average number of
-games won by the loser of the series; (2) maximum likelihood, and (3)
-maximum chi-square approach.
+probability value of the stronger team in the World Series, finding
+\(p \approx 0.65\). in each case: (1) a ``method of moments'' approach
+in which one solves for \(p\). from the empirical average number of
+games won by the loser of the series; (2) maximizing the likelihood that
+the sample would have been drawn from a population in which the
+probability of a team winning a game is constant across the series, and
+(3) minimizing the chi-square goodness of fit estimate for \(p\).
 
@@
 the ``gambler's fallacy'' (negative recency) and ``hot hand fallacy''
-(positive recency). Per {[}Ayton and Fischer (2004){]}, negative recency
-is ``the belief that, for random events, runs of a particular outcome
+(positive recency). Per (Ayton and Fischer 2004), negative recency is
+``the belief that, for random events, runs of a particular outcome
 \ldots{} will be balanced by a tendency for the opposite outcome'',
@@
 
-The general formula for the probability \(P(i)\) that a best-of-\(s\)
+The general formula for the probability \(P_E(i)\) that a best-of-\(s\)
 series lasts \(i\) rounds given constant probability \(p\) of one
@@
 \[
-s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}
+q = 1 - p, s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}, s_2^{'} = 1 - s_2
 \]
 
+\begin{equation}\protect\hypertarget{eq-series-length}{}{
+P_E(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
+}\label{eq-series-length}\end{equation}
+
+Table 1 shows the expected proportion for \(s = 11\) and the naive
+assumption that \(p = 0.5\), along with the observed proportion
+\(P_{O}(i)\) for CoD SnD.
+
+\begin{table}
+
+\caption{\label{tbl-panel}: The probabilities that a best-of-11 series
+lasts \(i\) rounds (\(P(i)\), where \(i \in R = [6, 7, 8, 9, 10, 11]\))
+under the assumption that each team has a 50\% probability (\(p = 0.5\))
+of winning each game \{\#tbl-prob-series-lasting-i-rounds\} along with
+the observed frequencies of series lasting \(i\) rounds, expressed as a
+percentage \(P_O(i)\) and as a count
+(\(N_O\))}\begin{minipage}[t]{\linewidth}
+\subcaption{\label{tbl-panel-1}}
+
+{\centering
+
+\captionsetup[table]{labelformat=empty,skip=1pt}
+\begin{longtable}{rrrr}
+\toprule
+&  & \multicolumn{2}{c}{Observed} \\ 
+\cmidrule(lr){3-4}
+Series lasts $i$ rounds & $P_E(i)$ & $P_O(i)$ & $N_O(i)$ \\ 
+\midrule
+6 & $3.1\%$ & $4.7\%$ & 40 \\ 
+7 & $9.4\%$ & $11.9\%$ & 101 \\ 
+8 & $16.4\%$ & $16.5\%$ & 141 \\ 
+9 & $21.9\%$ & $21.7\%$ & 185 \\ 
+10 & $24.6\%$ & $21.5\%$ & 183 \\ 
+11 & $24.6\%$ & $23.7\%$ & 202 \\ 
+\bottomrule
+\end{longtable}
+
+}
+
+\end{minipage}%
+
+\end{table}
+
+Calculating the chi-square goodness of fit statistic
+
 \[
-P(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}(1 - p)^{i - s_2} + p^{i - s_2}(1 - p)^{s_2})
+\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11]
 \]
 
-resulting in Table~\ref{tbl-prob-series-lasting-i-rounds}\} for
-\(s = 11\) and the naive assumption that \(p = 0.5\).
+as 16.0 (p-value of 0.0068), we can comfortably reject the constant
+probability null hypothesis, event at a confidence level of
+\(\alpha = 0.01\).
 
-\hypertarget{tbl-prob-series-lasting-i-rounds}{}
-\begin{longtable}[]{@{}rr@{}}
-\caption{\label{tbl-prob-series-lasting-i-rounds}The probabilities that
-a best-of-11 series lasts \(i\) rounds (\(Pr(i)\), where
-\(i = {6, 7, 8, 9, 10, 11}\)) under the assumption that each team has a
-50\% probability (\(p = 0.5\)) of winning each game}\tabularnewline
+Table~\ref{tbl-mosteller-methods} shows the alternate values for the
+constant round win probability \(p\) for winning a given round in a CoD
+SnD that we find when applying the three methods suggested by (Mosteller
+1952). Each is approximately or equal to 0.575, and each results in a
+\(chi^2\) value for which we cannot reject constant probability null
+hypothesis.
+
+\hypertarget{tbl-mosteller-methods}{}
+\begin{longtable}[]{@{}lrr@{}}
+\caption{\label{tbl-mosteller-methods}Alternate estimates of the
+constant probability \(p\) for winning a given round in a CoD SnD,
+applying the three methods suggested by (Mosteller 1952), in addition to
+the naive \(p = 0.5\).}\tabularnewline
 \toprule()
-Number of rounds (\(i\)) & \(P(i)\) \\
+Method & \(p\) & \(\chi^2\) (p-value) \\
 \midrule()
@@
 \toprule()
-Number of rounds (\(i\)) & \(P(i)\) \\
+Method & \(p\) & \(\chi^2\) (p-value) \\
 \midrule()
 \endhead
-6 & 3.1\% \\
-7 & 9.4\% \\
-8 & 16.4\% \\
-9 & 21.9\% \\
-10 & 24.6\% \\
-11 & 24.6\% \\
+0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
+1. Method of moments & 0.5725 & 3.6 (0.6) \\
+2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
+3. Minimum \(\chi^2\) & 0.5775 & 3.5 (0.62) \\
 \bottomrule()
@@
 
-The empirical offensive round win percentage across all rounds is
-47.8\%.\footnote{Offensive round win percentage has been nearly constant
-  across the three games during the CDL era: MW (2020) 47.2\%, Cold War
-  (2021) 47.9\%, Vanguard (2022) 48.1\%}
-Figure~\ref{fig-cod-o-round-win-prop} shows that offensive round win
-rate is not quite constant, although never veers more than 10\% from
-this global average.
+Table~\ref{tbl-expected-series-lengths-alternative-ps} shows the new
+\(P_E(i)\) when re-applying Equation~\ref{eq-series-length} for each new
+\(p\). We observe that \(P_E(i)\) is notably smaller for \(p_{1,2,3}\)
+when \(i \in [10, 11]\) and higher for \(i \in [6, 7]\), more closely
+matching \(P_O(i)\).
 
-\begin{figure}
-
-{\centering \includegraphics{images/cod_o_round_win_prop.png}
-
-}
-
-\caption{\label{fig-cod-o-round-win-prop}Offensive round win percentage
-by series state}
-
-\end{figure}
+\hypertarget{tbl-expected-series-lengths-alternative-ps}{}
+\begin{longtable}[]{@{}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2451}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1373}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1765}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1765}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0980}}@{}}
+\caption{\label{tbl-expected-series-lengths-alternative-ps}Caption}\tabularnewline
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedleft
+Series lasts \(i\) rounds
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+0. \(p\)= 0.5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+1. \(p\) = 0.5725
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+2. \(p\) = 0.575
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+3. \(p\) = 0.5775
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\(P_O(i)\)
+\end{minipage} \\
+\midrule()
+\endfirsthead
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedleft
+Series lasts \(i\) rounds
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+0. \(p\)= 0.5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+1. \(p\) = 0.5725
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+2. \(p\) = 0.575
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+3. \(p\) = 0.5775
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\(P_O(i)\)
+\end{minipage} \\
+\midrule()
+\endhead
+6 & 3.1\% & 4.1\% & 4.2\% & 4.3\% & 4.7\% \\
+7 & 9.4\% & 11.1\% & 11.2\% & 11.4\% & 11.9\% \\
+8 & 16.4\% & 17.7\% & 17.8\% & 17.9\% & 16.5\% \\
+9 & 21.9\% & 21.8\% & 21.8\% & 21.8\% & 21.7\% \\
+10 & 24.6\% & 23.1\% & 23.0\% & 22.9\% & 21.5\% \\
+11 & 24.6\% & 22.1\% & 22.0\% & 21.8\% & 23.7\% \\
+\bottomrule()
+\end{longtable}
 

### 2022-08-14 1-scrape-cod.R
re-do series_id

@@ -208,12 +208,15 @@ cod_rounds <- cod_series |>
   ungroup() |> 
   inner_join(
     cod_series |> 
-      filter(round == 1L) |> 
-      distinct(year, sheet, series, team, starts_as_offense = is_offense) |> 
+      distinct(year, sheet, series) |> 
       mutate(
-        series_id = row_number(),
-        .before = 1
-      ), 
+        series_id = row_number()
+      )
+  ) |> 
+  inner_join(
+    cod_series |> 
+      filter(round == 1L) |> 
+      distinct(year, sheet, series, team, starts_as_offense = is_offense), 
     by = c('year', 'sheet', 'series', 'team')
   ) |> 
   inner_join(
@@ -239,7 +242,8 @@ cod_rounds <- cod_series |>
   mutate(
     across(game, ~fct_reorder(.x, year)),
     map = sprintf('%s - %s', map, game)
-  )
+  ) |> 
+  relocate(series_id, .after = 'game')
 filename <- 'cod_rounds.qs'
 sprintf('%s%s', c('', 'paper/'), filename) |> 
   walk(~qs::qsave(cod_rounds, .x))

### 2022-08-14 paper2/paper2.Rmd
paper 2

--- 2022-08-14 paper/paper.qmd
@@
 title: "They're Clutching up! Team Momentum in Round-Based Esports"
-execute: 
-  include: false
-  echo: false
-  eval: false
-format:
-  arxiv-pdf:
-    keep-tex: true  
-  arxiv-html: default
-author:
+authors:
   - name: Tony ElHabr
@@
 I find that teams perform significantly worse than expected after streaks of 2, 3, and 4 wins when series end up going to 9, 10, or 11 (maximum) rounds, even after accounting for the "hot-hand" phenomenon.
-
-  Third, I compare win percentages in round one versus all other rounds, hypothesizing that there may be some advantage on either side when there is no prior information about how the opponent intends to play a given map in either game.
-I find only one instance for which there seems to be a significant defensive advantage in round one.
-
-  Finally, I evaluate behavior when teams have two rounds left to win the series, observing a peak in COD offensive win percentages in the 4-4 state, and no such oddity in Valorant.
 bibliography: references.bib  
+biblio-style: unsrt
+output: rticles::arxiv_article
 ---
@@
 #| label: setup
+#| include: false
+#| echo: false
 #| eval: true
+knitr::opts_chunk$set(
+  eval = FALSE,
+  echo = FALSE,
+  include = FALSE,
+  message = FALSE,
+  warning = FALSE
+)
+```
+
+```{r}
+#| label: setup-code
 library(dplyr)
@@
 library(tidyr)
-# library(gt)
+library(gt)
 library(scales)
@@
 #| label: descriptive-cod-snd-stats
-#| eval: true
 cod_n_series <- cod_rounds |> 
@@
 Call of Duty (CoD), first released in 2003, is one of the most popular first-person shooter (FPS) video game franchises of all-time.
-Tthe most popular mode in the competitive scene is "Search and Destroy" (SnD), which bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in professional leagues.
+The most popular mode in the competitive scene is "Search and Destroy" (SnD), which bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in professional leagues.
 SnD is one-sided game mode in which one team, the offensive side, tries to destroy one of two designated bomb sites on the map.
 
-In professional CoD, a team must win six rounds of SnD to win the match.[^1] A round can end in one of four ways:
+In professional CoD, a team must win six rounds of SnD to win the match.[^1] A round can end in one of fmy ways:
 
@@
 
-[^2]: Merchanics regarding the bomb:
-
-[^3]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
-
+[^2]:
     -   The bomb can be picked up by any member of the offensive team.
@@
 
+[^3]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+
 Teams take turns playing offense and defense every round.
 
-We adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
+I adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
 A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
@@
 
-CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
+CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tmynaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tmynaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
 Data was collected in spreadsheets by community member "IOUTurtle".[^5]
@@
 
-[^5]: Data: https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle
+[^5]: Data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>
 
-The empirical offensive round win percentage across all rounds is 47.8%.[^6] To contextualize our subsequent discussion of series length and momentum, table 1 shows round win percentages by series "state" (i.e.
+The empirical offensive round win percentage across all rounds is 47.8%.[^6] To contextualize my subsequent discussion of series length and momentum, table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
@@
 
-[^6]: Offensive round win percentage has been nearly constant across the three games during the CDL era: MW (2020) `r pull_cod_o_win_prop_by_game('MW (2020)')`, Cold War (2021) `r pull_cod_o_win_prop_by_game('Cold War (2021)')`, Vanguard (2022) `r pull_cod_o_win_prop_by_game('Vanguard (2022)')`
+[^6]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
 
@@
 #| label: cod_o_win_prop
-#| eval: false
 cod_round_and_series_win_prop_by_side <- cod_rounds |>
@@
   gt::cols_label(
-    pre_cumu_w = "Defensive team's round wins",
+    pre_cumu_w = "Defense round wins",
   ) |>
   gt::tab_spanner(
-    label = "Offensive team's round wins",
+    label = "Offense round wins",
     columns = `0`:`5`
@@
 ```{=tex}
-\captionsetup[table]{labelformat=empty,skip=1pt}
-\begin{longtable}{rrrrrrr}
+\begin{longtable}{crrrrrr}
+  \caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins}\label{tbl:cod-o-win-prop-by-series-state} \\
   \toprule
- & \multicolumn{6}{c}{Offensive team's round wins} \\ 
+   & \multicolumn{6}{c}{Offense round wins} \\ 
   \cmidrule(lr){2-7}
-Defensive team's round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
+  Defense round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
     \midrule
@@
 There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state.
-[@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with \$p=0.5\$.
+[@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p = 0.5$.
 Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$.
@@
 [@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
-Chance applies finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^7] Chance's work is closely related to ours and, in fact, provides a guide for the first part of our investigation.
+Chance applies finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^7] Chance's work is closely related to mys and, in fact, provides a guide for the first part of my investigation.
 
@@
 conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success".
-We agree with Miller's findings, accounting for the streak selection bias in our study of momentum.
+I agree with Miller's findings, accounting for the streak selection bias in my study of momentum.
 
@@
 
-First, we investigate the constant probability assumption and the distribution of rounds played in a series.
-Afterwards, we investigate momentum, building on our learnings from the constant probability assumption analysis.
+First, I investigate the constant probability assumption and the distribution of rounds played in a series.
+Afterwards, I investigate momentum, building on my learnings from the constant probability assumption analysis.
 
@@
 
-[^10]: If $p > 0.5$, then we might say that this team is the better team (presumably known in hindsight)
+[^10]: If $p > 0.5$, then I might say that this team is the better team (known omnisciently).
 
@@
 
-$$
+```{=tex}
+\begin{equation}\protect\hypertarget{eq-series-length}{}{
 P_E(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
-$$ {#eq-series-length}
-
+}\label{eq:series-length}\end{equation}
+```
 ```{r}
 #| label: cod_series_outcome_prop
-#| eval: true
 .max_round <- 11
@@
 
-Table 2 shows the expected proportion for $s = 11$ and the naive assumption that $p = 0.5$, along with the observed proportion $P_{O}(i)$ for CoD SnD.
+Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected proportion for $s = 11$ and the naive assumption that $p = 0.5$, along with the observed frequencies observed in CoD SnD, as both a count $N_O(i)$ (of series lasting $i$ rounds) and a proportion $P_O(i)$ of all series.
 
 ```{=tex}
-\captionsetup[table]{labelformat=empty,skip=1pt}
 \begin{longtable}{rrrr}
+  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($Pr(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each round.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
   \toprule
@@
 ```{r}
-#| label: cod_series_outcomes_chi
-#| eval: false
+#| label: cod_series_outcomes_naive_chi
 generate_chi_label <- function(statistic, p.value) {
@@
 
-$$
-\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11]
-$$
-
-as `r scales::number(cod_series_outcomes_naive_chi$statistic, accuracy = 0.1)` (p-value of `r scales::number(cod_series_outcomes_naive_chi$p.value, accuracy = 0.0001)`), we can comfortably reject the constant probability null hypothesis, event at a confidence level of $\alpha = 0.01$.
+```{=tex}
+\begin{equation}\protect\hypertarget{eq-series-length}{}{
+\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11].
+}\label{eq:chi-squ-test}\end{equation}
+```
+as 16.0 (p-value of 0.0068), I can comfortably reject the constant probability null hypothesis, event at a confidence level of $\alpha = 0.01$.
 
@@
 #| label: cod-alternative-to-p=0.5-method-prep
-#| eval: false
 min_p1 <- 0.5
@@
 #| label: cod-alternative-to-p=0.5-method-1
-#| eval: false
-# p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
+## p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
 theoretical_cod_series_length <- function(p) {
@@
 #| label: cod-alternative-to-p=0.5-method-2
-#| eval: false
 pluck_cod_n <- function(.n_rounds) {
@@
 #| label: cod-alternative-to-p=0.5-method-3
-#| eval: false
 summarize_cod_series_chi <- function(p) {
@@
 #| label: cod-alternatives-to-p=0.5
-#| eval: false
 cod_streaks_other_res <- tibble(
@@
 
-@tbl-mosteller-methods shows the alternate values for the constant round win probability $p$ for winning a given round in a CoD SnD that we find when applying the three methods suggested by [@mosteller1952].
-Each is approximately or equal to 0.575, and each results in a $chi^2$ value for which we cannot reject constant probability null hypothesis.
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability $p$ for winning a given round in a CoD SnD that I find when applying the three methods suggested by Mosteller [-@mosteller1952].
+Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ-test}, each results in a $\chi^2$ value for which I cannot reject the constant probability null hypothesis.
 
-| Method                 |    $p$ | $\chi^2$ (p-value) |
-|:-----------------------|-------:|-------------------:|
-| 0\. Naive              | 0.5000 |     16.0 (\<=0.01) |
-| 1\. Method of moments  | 0.5725 |          3.6 (0.6) |
-| 2\. Maximum likelihood | 0.5750 |         3.5 (0.62) |
-| 3\. Minimum $\chi^2$   | 0.5775 |         3.5 (0.62) |
+```{=tex}
+\begin{longtable}[]{@{}lrr@{}}
+  \caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
+  \toprule()
+    Method & \(p\) & \(\chi^2\) (p-value) \\
+    \midrule()
+    \endfirsthead
+    \toprule()
+    Method & \(p\) & \(\chi^2\) (p-value) \\
+    \midrule()
+  \endhead
+  0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
+  1. Method of moments & 0.5725 & 3.6 (0.6) \\
+  2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
+  3. Minimum \(\chi^2\) & 0.5775 & 3.5 (0.62) \\
+  \bottomrule()
+\end{longtable}
+```
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(i)$ when re-applying Equation \ref{eq:series-length} for each new $p$.
+I observe that $P_E(i)$ is notably smaller for $p_{1,2,3}$ when $i \in [10, 11]$ and higher for $i \in [6, 7]$, more closely matching $P_O(i)$.
 
-: Alternate estimates of the constant probability $p$ for winning a given round in a CoD SnD, applying the three methods suggested by [@mosteller1952], in addition to the naive $p = 0.5$.
-{#tbl-mosteller-methods}
-
-@tbl-expected-series-lengths-alternative-ps shows the new $P_E(i)$ when re-applying @eq-series-length for each new $p$.
-We observe that $P_E(i)$ is notably smaller for $p_{1,2,3}$ when $i \in [10, 11]$ and higher for $i \in [6, 7]$, more closely matching $P_O(i)$.
-
-| Series lasts $i$ rounds | 0\. $p$= 0.5 | 1\. $p$ = 0.5725 | 2\. $p$ = 0.575 | 3\. $p$ = 0.5775 | $P_O(i)$ |
-|------------------------:|-------------:|-----------------:|----------------:|-----------------:|---------:|
-|                       6 |         3.1% |             4.1% |            4.2% |             4.3% |     4.7% |
-|                       7 |         9.4% |            11.1% |           11.2% |            11.4% |    11.9% |
-|                       8 |        16.4% |            17.7% |           17.8% |            17.9% |    16.5% |
-|                       9 |        21.9% |            21.8% |           21.8% |            21.8% |    21.7% |
-|                      10 |        24.6% |            23.1% |           23.0% |            22.9% |    21.5% |
-|                      11 |        24.6% |            22.1% |           22.0% |            21.8% |    23.7% |
-
-: Caption {#tbl-expected-series-lengths-alternative-ps}
+```{=tex}
+\begin{longtable}[]{@{}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2427}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1456}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1650}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0971}}@{}}
+\caption{The probabilities that a best-of-11 series lasts $i$ rounds under various assumptions for $p$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedleft
+Series lasts \(i\) rounds
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+0. \(p\) = 0.5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+1. \(p\) = 0.5725
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+2. \(p\) = 0.575
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+3. \(p\) = 0.5775
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\(P_O(i)\)
+\end{minipage} \\
+\midrule()
+\endfirsthead
+\toprule()
+\begin{minipage}[b]{\linewidth}\raggedleft
+Series lasts \(i\) rounds
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+0. \(p\) = 0.5
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+1. \(p\) = 0.5725
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+2. \(p\) = 0.575
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+3. \(p\) = 0.5775
+\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
+\(P_O(i)\)
+\end{minipage} \\
+\midrule()
+\endhead
+6 & 3.1\% & 4.1\% & 4.2\% & 4.3\% & 4.7\% \\
+7 & 9.4\% & 11.1\% & 11.2\% & 11.4\% & 11.9\% \\
+8 & 16.4\% & 17.7\% & 17.8\% & 17.9\% & 16.5\% \\
+9 & 21.9\% & 21.8\% & 21.8\% & 21.8\% & 21.7\% \\
+10 & 24.6\% & 23.1\% & 23.0\% & 22.9\% & 21.5\% \\
+11 & 24.6\% & 22.1\% & 22.0\% & 21.8\% & 23.7\% \\
+\bottomrule()
+\end{longtable}
+```
+So I conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $p$ ($\approx 0.575$).
 

### 2022-08-14 paper2/paper2.tex
paper 2

--- 2022-08-14 paper/paper.tex
@@
-% Options for packages loaded elsewhere
-\PassOptionsToPackage{unicode}{hyperref}
-\PassOptionsToPackage{hyphens}{url}
-\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
-%
-\documentclass[
-]{article}
+\documentclass{article}
 
-\usepackage{amsmath,amssymb}
-\usepackage{lmodern}
-\usepackage{iftex}
-\ifPDFTeX
-  \usepackage[T1]{fontenc}
-  \usepackage[utf8]{inputenc}
-  \usepackage{textcomp} % provide euro and other symbols
-\else % if luatex or xetex
-  \usepackage{unicode-math}
-  \defaultfontfeatures{Scale=MatchLowercase}
-  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
-\fi
-% Use upquote if available, for straight quotes in verbatim environments
-\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
-\IfFileExists{microtype.sty}{% use microtype if available
-  \usepackage[]{microtype}
-  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
-}{}
-\makeatletter
-\@ifundefined{KOMAClassName}{% if non-KOMA class
-  \IfFileExists{parskip.sty}{%
-    \usepackage{parskip}
-  }{% else
-    \setlength{\parindent}{0pt}
-    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
-}{% if KOMA class
-  \KOMAoptions{parskip=half}}
-\makeatother
-\usepackage{xcolor}
-\setlength{\emergencystretch}{3em} % prevent overfull lines
-\setcounter{secnumdepth}{5}
-% Make \paragraph and \subparagraph free-standing
-\ifx\paragraph\undefined\else
-  \let\oldparagraph\paragraph
-  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
-\fi
-\ifx\subparagraph\undefined\else
-  \let\oldsubparagraph\subparagraph
-  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
-\fi
+\usepackage{arxiv}
 
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{lmodern}        % https://github.com/rstudio/rticles/issues/343
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
+\usepackage{amsfonts}       % blackboard math symbols
+\usepackage{nicefrac}       % compact symbols for 1/2, etc.
+\usepackage{microtype}      % microtypography
+\usepackage{graphicx}
+
+\title{They're Clutching up! Team Momentum in Round-Based Esports}
+
+\author{
+    Tony ElHabr
+   \\
+     \\
+   \\
+  \texttt{\href{mailto:anthonyelhabr@gmail.com}{\nolinkurl{anthonyelhabr@gmail.com}}} \\
+  }
+
+% tightlist command for lists without linebreak
 \providecommand{\tightlist}{%
-  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
-\usepackage{calc} % for calculating minipage widths
-% Correct order of tables after \paragraph or \subparagraph
-\usepackage{etoolbox}
-\makeatletter
-\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
-\makeatother
-% Allow footnotes in longtable head/foot
-\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
-\makesavenoteenv{longtable}
-\usepackage{graphicx}
-\makeatletter
-\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
-\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
-\makeatother
-% Scale images if necessary, so that they will not overflow the page
-% margins by default, and it is still possible to overwrite the defaults
-% using explicit options in \includegraphics[width, height, ...]{}
-\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-% Set default figure placement to htbp
-\makeatletter
-\def\fps@figure{htbp}
-\makeatother
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+% Pandoc citation processing
 \newlength{\cslhangindent}
@@
 \setlength{\cslentryspacingunit}{\parskip}
+% for Pandoc 2.8 to 2.10.1
+\newenvironment{cslreferences}%
+  {}%
+  {\par}
+% For Pandoc 2.11+
 \newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
@@
 
-\usepackage{arxiv}
-\usepackage{orcidlink}
-\usepackage{amsmath}
-\usepackage[T1]{fontenc}
-\makeatletter
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
-\makeatother
-\makeatletter
-\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
-\makeatother
-\makeatletter
-\makeatother
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={They're Clutching up! Team Momentum in Round-Based Esports},
-  pdfauthor={Tony ElHabr},
-  colorlinks=true,
-  linkcolor={blue},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
-
-\title{They're Clutching up! Team Momentum in Round-Based Esports}
-\author{
-Tony ElHabr\\\\Georgia Institute of
-Technology\\\\\href{mailto:anthonyelhabr@gmail.com}{anthonyelhabr@gmail.com}}
-\date{}
 \begin{document}
 \maketitle
+
 \begin{abstract}
@@
 after accounting for the ``hot-hand'' phenomenon.
-
-Third, I compare win percentages in round one versus all other rounds,
-hypothesizing that there may be some advantage on either side when there
-is no prior information about how the opponent intends to play a given
-map in either game. I find only one instance for which there seems to be
-a significant defensive advantage in round one.
-
-Finally, I evaluate behavior when teams have two rounds left to win the
-series, observing a peak in COD offensive win percentages in the 4-4
-state, and no such oddity in Valorant.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, breakable, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
 
@@
 Call of Duty (CoD), first released in 2003, is one of the most popular
-first-person shooter (FPS) video game franchises of all-time. Tthe most
+first-person shooter (FPS) video game franchises of all-time. The most
 popular mode in the competitive scene is ``Search and Destroy'' (SnD),
@@
   equivalent in professional Counter-Strike and Valorant matches.} A
-round can end in one of four ways:
+round can end in one of fmy ways:
 
@@
   The offensive team eliminates all members of the defensive team after
-  a bomb plant.\footnote{Merchanics regarding the bomb:} (Offense wins.)
+  a bomb plant.\footnote{\begin{itemize}
+    \tightlist
+    \item
+      The bomb can be picked up by any member of the offensive team.
+    \item
+      The bomb carrier is not obstructed at all by carrying the bomb
+      (i.e.~movement is the same, weapon usage is the same).
+    \item
+      The defense does not get any visual indication for who is carrying
+      the bomb.
+    \item
+      A bomb plant takes five seconds. The timer resets if the player
+      stops planting site prior to completing it.
+    \item
+      A bomb defuse takes seven seconds. The timer resets if the player
+      ``drops'' the bomb.
+    \item
+      The bomb takes 45 seconds to defuse after being planted.
+    \end{itemize}} (Offense wins.)
 \item
@@
 
-\begin{itemize}
-\tightlist
-\item
-  The bomb can be picked up by any member of the offensive team.
-\item
-  The bomb carrier is not obstructed at all by carrying the bomb
-  (i.e.~movement is the same, weapon usage is the same).
-\item
-  The defense does not get any visual indication for who is carrying the
-  bomb.
-\item
-  A bomb plant takes five seconds. The timer resets if the player stops
-  planting site prior to completing it.
-\item
-  A bomb defuse takes seven seconds. The timer resets if the player
-  ``drops'' the bomb.
-\item
-  The bomb takes 45 seconds to defuse after being planted.
-\end{itemize}
-
 Teams take turns playing offense and defense every round.
 
-We adopt the terminology ``series'' to refer to what CoD SnD players
+I adopt the terminology ``series'' to refer to what CoD SnD players
 typically call a ``match'', so as to emulate the terminology of playoff
@@
 CoD has roughly gone through three eras of professional gaming: (1)
-Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
+Major League Gaming (MLG) tmynaments prior to 2016; (2) the CoD World
 League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
@@
   (2021) and Vanguard (2022).} The data set consists of all SnD matches
-played in tournaments and qualifiers during the CDL era, totaling 15,584
-rounds across 1,704 series. Data was collected in spreadsheets by
+played in tmynaments and qualifiers during the CDL era, totaling 7,792
+rounds across 852 series. Data was collected in spreadsheets by
 community member ``IOUTurtle''.\footnote{Data:
-  https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle}
+  \url{https://linktr.ee/CDLArchive}. Author:
+  \url{https://twitter.com/IOUTurtle}}
 
@@
 47.8\%.\footnote{Offensive round win percentage has been nearly constant
-  across the three games during the CDL era: MW (2020) 47.2\%, Cold War
-  (2021) 47.9\%, Vanguard (2022) 48.1\%} To contextualize our subsequent
-discussion of series length and momentum, table 1 shows round win
+  across the three games during the CDL era: 1. 47.2\% in MW (2020) 2.
+  47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)} To
+contextualize my subsequent discussion of series length and momentum,
+table \ref{tbl:cod-o-win-prop-by-series-state} shows round win
 percentages by series ``state'' (i.e.~the number of round wins by each
@@
 
-\captionsetup[table]{labelformat=empty,skip=1pt}
-\begin{longtable}{rllllll}
+\begin{longtable}{crrrrrr}
+  \caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins}\label{tbl:cod-o-win-prop-by-series-state} \\
   \toprule
- & \multicolumn{6}{c}{Offensive team's round wins} \\ 
-\cmidrule(r){2-7}
-Defensive team's round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
+   & \multicolumn{6}{c}{Offense round wins} \\ 
+  \cmidrule(lr){2-7}
+  Defense round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
     \midrule
@@
 the National League in Major League Baseball's (MLB) World Series
-matchups, implying that matchups should not modeled with \$p=0.5\$.
+matchups, implying that matchups should not modeled with \(p = 0.5\).
 Mosteller proposed three approaches for identifying the optimal constant
@@
   distribution of the number of games played.} Chance's work is closely
-related to ours and, in fact, provides a guide for the first part of our
+related to mys and, in fact, provides a guide for the first part of my
 investigation.
@@
 successes is expected to be strictly less than the underlying
-(conditional) probability of success''. We agree with Miller's findings,
-accounting for the streak selection bias in our study of momentum.
+(conditional) probability of success''. I agree with Miller's findings,
+accounting for the streak selection bias in my study of momentum.
 
@@
 
-First, we investigate the constant probability assumption and the
-distribution of rounds played in a series. Afterwards, we investigate
-momentum, building on our learnings from the constant probability
+First, I investigate the constant probability assumption and the
+distribution of rounds played in a series. Afterwards, I investigate
+momentum, building on my learnings from the constant probability
 assumption analysis.
@@
 series lasts \(i\) rounds given constant probability \(p\) of one
-team\footnote{If \(p > 0.5\), then we might say that this team is the
-  better team (presumably known in hindsight)} winning each round is
+team\footnote{If \(p > 0.5\), then I might say that this team is the
+  better team (known omnisciently).} winning each round is
 
@@
 P_E(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
-}\label{eq-series-length}\end{equation}
+}\label{eq:series-length}\end{equation}
 
-Table 1 shows the expected proportion for \(s = 11\) and the naive
-assumption that \(p = 0.5\), along with the observed proportion
-\(P_{O}(i)\) for CoD SnD.
+Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected
+proportion for \(s = 11\) and the naive assumption that \(p = 0.5\),
+along with the observed frequencies observed in CoD SnD, as both a count
+\(N_O(i)\) (of series lasting \(i\) rounds) and a proportion \(P_O(i)\)
+of all series.
 
-\begin{table}
-
-\caption{\label{tbl-panel}: The probabilities that a best-of-11 series
-lasts \(i\) rounds (\(P(i)\), where \(i \in R = [6, 7, 8, 9, 10, 11]\))
-under the assumption that each team has a 50\% probability (\(p = 0.5\))
-of winning each game \{\#tbl-prob-series-lasting-i-rounds\} along with
-the observed frequencies of series lasting \(i\) rounds, expressed as a
-percentage \(P_O(i)\) and as a count
-(\(N_O\))}\begin{minipage}[t]{\linewidth}
-\subcaption{\label{tbl-panel-1}}
-
-{\centering
-
-\captionsetup[table]{labelformat=empty,skip=1pt}
 \begin{longtable}{rrrr}
+  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($Pr(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each round.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
   \toprule
@@
 
-}
-
-\end{minipage}%
-
-\end{table}
+The probabilities that a best-of-11 series lasts \(i\) rounds (\(P(i)\),
+where \(i \in R = [6, 7, 8, 9, 10, 11]\)) under the assumption that each
+team has a 50\% probability (\(p = 0.5\)) of winning each game
+\{\#tbl-prob-series-lasting-i-rounds\} along with the observed
+frequencies of series lasting \(i\) rounds, expressed as a percentage
+\(P_O(i)\) and as a count (\(N_O\))
 
@@
 
-\[
-\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11]
-\]
+\begin{equation}\protect\hypertarget{eq-series-length}{}{
+\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11].
+}\label{eq:chi-squ-test}\end{equation}
 
-as 16.0 (p-value of 0.0068), we can comfortably reject the constant
+as 16.0 (p-value of 0.0068), I can comfortably reject the constant
 probability null hypothesis, event at a confidence level of
@@
 
-Table~\ref{tbl-mosteller-methods} shows the alternate values for the
-constant round win probability \(p\) for winning a given round in a CoD
-SnD that we find when applying the three methods suggested by (Mosteller
-1952). Each is approximately or equal to 0.575, and each results in a
-\(chi^2\) value for which we cannot reject constant probability null
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for
+the constant round win probability \(p\) for winning a given round in a
+CoD SnD that I find when applying the three methods suggested by
+Mosteller (1952). Each is approximately or equal to 0.575, and, when
+applying Equation \ref{eq:chi-squ-test}, each results in a \(\chi^2\)
+value for which I cannot reject the constant probability null
 hypothesis.
 
-\hypertarget{tbl-mosteller-methods}{}
 \begin{longtable}[]{@{}lrr@{}}
-\caption{\label{tbl-mosteller-methods}Alternate estimates of the
-constant probability \(p\) for winning a given round in a CoD SnD,
-applying the three methods suggested by (Mosteller 1952), in addition to
-the naive \(p = 0.5\).}\tabularnewline
+  \caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
   \toprule()
@@
 
-Table~\ref{tbl-expected-series-lengths-alternative-ps} shows the new
-\(P_E(i)\) when re-applying Equation~\ref{eq-series-length} for each new
-\(p\). We observe that \(P_E(i)\) is notably smaller for \(p_{1,2,3}\)
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
+\(P_E(i)\) when re-applying Equation \ref{eq:series-length} for each new
+\(p\). I observe that \(P_E(i)\) is notably smaller for \(p_{1,2,3}\)
 when \(i \in [10, 11]\) and higher for \(i \in [6, 7]\), more closely
@@
 
-\hypertarget{tbl-expected-series-lengths-alternative-ps}{}
 \begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2451}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1373}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1765}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1667}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1765}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0980}}@{}}
-\caption{\label{tbl-expected-series-lengths-alternative-ps}Caption}\tabularnewline
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2427}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1456}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1650}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
+  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0971}}@{}}
+\caption{The probabilities that a best-of-11 series lasts $i$ rounds under various assumptions for $p$.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
@@
 \end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-0. \(p\)= 0.5
+0. \(p\) = 0.5
 \end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
@@
 \end{longtable}
+
+So I conclude that the constant round win probability assumption can be
+valid in CoD SnD series with the appropriate choice of \(p\)
+(\(\approx 0.575\)).
 
@@
 
+\bibliographystyle{unsrt}
+\bibliography{references.bib}
+
 \end{document}

### 2022-08-14 paper2/paper2.Rmd
try 2

@@
   My research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).
-
-  First, I find evidence in CoD defying the naive hypothesis that a series represents a sequence of independent events (rounds), with each team having a constant 50% probability of winning a given round.
-
-  Second, I examine post-streak round win probability.
-I find that teams perform significantly worse than expected after streaks of 2, 3, and 4 wins when series end up going to 9, 10, or 11 (maximum) rounds, even after accounting for the "hot-hand" phenomenon.
+I find evidence in CoD supprting the hypothesis that round win probability can be modeled as constant across the series, although not at a naive 50%.
+Second, I examine post-streak round win probability, in search of evidence positive recency (the "hot hand" fallacy) or negative recency (the "gambler's falacy").
+I find that teams perform significantly worse than expected after streaks of 2, 3, and 4 wins when series end up going to 9, 10, or 11 (maximum) rounds, suggesting the presence of negative recency.
 bibliography: references.bib  
-biblio-style: unsrt
-output: rticles::arxiv_article
+output:
+  rticles::arxiv_article:
+    includes:
+      in_header: preamble.tex
 ---
@@
 library(tidyr)
+library(purrr)
 library(gt)
@@
 
-The empirical offensive round win percentage across all rounds is 47.8%.[^6] To contextualize my subsequent discussion of series length and momentum, table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+The empirical offensive round win percentage across all rounds is 47.8%.[^6] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
@@
 Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily in esports.
-Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike ([@xenopoulos2022]) and Valorant ([@derover2021]), both of which are round-based like CoD SnD.
+Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
 However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^9]
@@
 
-Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected proportion for $s = 11$ and the naive assumption that $p = 0.5$, along with the observed frequencies observed in CoD SnD, as both a count $N_O(i)$ (of series lasting $i$ rounds) and a proportion $P_O(i)$ of all series.
+Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected probabilities for $s = 11$ under the naive assumption that $p_0 = 0.5$ for a given round, along with the observed frequencies observed in CoD SnD ($P_O(i)$, $N_O(i)$)).
 
@@
 \begin{longtable}{rrrr}
-  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($Pr(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each round.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
+  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p_0 = 0.5$) of winning each game.
+The observed frequencies observed are shown as a count $N_O(i)$ and as a proportion $P_O(i)$ of all series.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
   \toprule
@@
 ```
-The probabilities that a best-of-11 series lasts $i$ rounds ($P(i)$, where $i \in R = [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each game {#tbl-prob-series-lasting-i-rounds} along with the observed frequencies of series lasting $i$ rounds, expressed as a percentage $P_O(i)$ and as a count ($N_O$)
+The probabilities that a best-of-11 series lasts $i$ rounds ($P(i)$, where $i \in R = [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50% probability ($p_0 = 0.5$) of winning each game {#tbl-prob-series-lasting-i-rounds} along with the observed frequencies of series lasting $i$ rounds, expressed as a percentage $P_O(i)$ and as a count ($N_O$)
 
@@
 ```
-as 16.0 (p-value of 0.0068), I can comfortably reject the constant probability null hypothesis, event at a confidence level of $\alpha = 0.01$.
+as 16.0 (p-value of 0.0068), I can comfortably reject the constant probability null hypothesis for $p_0 = 0.5$, event at a confidence level of $\alpha = 0.01$.
 
@@
 cod_streaks_other_res |>
+  filter(idx %in% c(0L, 2L)) |> 
   mutate(
-    lab = sprintf('%s. p = %s', idx, p)
+    lab = sprintf('$p$ = %s', p)
   ) |>
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(i)$ when re-applying Equation \ref{eq:series-length} for each new $p$.
-I observe that $P_E(i)$ is notably smaller for $p_{1,2,3}$ when $i \in [10, 11]$ and higher for $i \in [6, 7]$, more closely matching $P_O(i)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(i)$ when re-applying Equation \ref{eq:series-length} for each the maximum likelihood estimate $p_2 = 0.575$.[^11] I observe that $P_E(i)$ is notably larger for $p_{2}$ when $i \in [6, 7]$, more closely matching $P_O(i)$.
+$p_{2}$ is also closer to $P_O(i)$ for $i \in [9, 10]$, although not for $i \in [8, 11]$.
+
+[^11]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$.
 
 ```{=tex}
-\begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2427}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1456}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1650}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0971}}@{}}
-\caption{The probabilities that a best-of-11 series lasts $i$ rounds under various assumptions for $p$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\begin{longtable}[]{@{}rrrr@{}}
+\caption{The probabilities that a best-of-11 series lasts $i$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
-\begin{minipage}[b]{\linewidth}\raggedleft
-Series lasts \(i\) rounds
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-0. \(p\) = 0.5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-1. \(p\) = 0.5725
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-2. \(p\) = 0.575
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-3. \(p\) = 0.5775
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-\(P_O(i)\)
-\end{minipage} \\
-\midrule()
-\endfirsthead
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedleft
-Series lasts \(i\) rounds
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-0. \(p\) = 0.5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-1. \(p\) = 0.5725
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-2. \(p\) = 0.575
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-3. \(p\) = 0.5775
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-\(P_O(i)\)
-\end{minipage} \\
+Series lasts \(i\) rounds & \(p_0\) = 0.5 & \(p_2\) = 0.575 & \(P_O(i)\) \\
 \midrule()
 \endhead
-6 & 3.1\% & 4.1\% & 4.2\% & 4.3\% & 4.7\% \\
-7 & 9.4\% & 11.1\% & 11.2\% & 11.4\% & 11.9\% \\
-8 & 16.4\% & 17.7\% & 17.8\% & 17.9\% & 16.5\% \\
-9 & 21.9\% & 21.8\% & 21.8\% & 21.8\% & 21.7\% \\
-10 & 24.6\% & 23.1\% & 23.0\% & 22.9\% & 21.5\% \\
-11 & 24.6\% & 22.1\% & 22.0\% & 21.8\% & 23.7\% \\
+6 & 3.1\% & 4.2\% & 4.7\% \\
+7 & 9.4\% & 11.2\% & 11.9\% \\
+8 & 16.4\% & 17.8\% & 16.5\% \\
+9 & 21.9\% & 21.8\% & 21.7\% \\
+10 & 24.6\% & 23.0\% & 21.5\% \\
+11 & 24.6\% & 22.0\% & 23.7\% \\
 \bottomrule()

### 2022-08-14 paper2/paper2.tex
try 2

@@
 
+\usepackage{longtable}
 \begin{document}
@@
 professional Search and Destroy (SnD) matches of the popular
-first-person shooter game Call of Duty (CoD).
-
-First, I find evidence in CoD defying the naive hypothesis that a series
-represents a sequence of independent events (rounds), with each team
-having a constant 50\% probability of winning a given round.
-
-Second, I examine post-streak round win probability. I find that teams
-perform significantly worse than expected after streaks of 2, 3, and 4
-wins when series end up going to 9, 10, or 11 (maximum) rounds, even
-after accounting for the ``hot-hand'' phenomenon.
+first-person shooter game Call of Duty (CoD). I find evidence in CoD
+supprting the hypothesis that round win probability can be modeled as
+constant across the series, although not at a naive 50\%. Second, I
+examine post-streak round win probability, in search of evidence
+positive recency (the ``hot hand'' fallacy) or negative recency (the
+``gambler's falacy''). I find that teams perform significantly worse
+than expected after streaks of 2, 3, and 4 wins when series end up going
+to 9, 10, or 11 (maximum) rounds, suggesting the presence of negative
+recency.
 \end{abstract}
@@
   across the three games during the CDL era: 1. 47.2\% in MW (2020) 2.
-  47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)} To
-contextualize my subsequent discussion of series length and momentum,
-table \ref{tbl:cod-o-win-prop-by-series-state} shows round win
-percentages by series ``state'' (i.e.~the number of round wins by each
-team prior to an upcoming round). Offensive round win rate is not quite
-constant, although never veers more than 10\% from this global average.
+  47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)} Table
+\ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by
+series ``state'' (i.e.~the number of round wins by each team prior to an
+upcoming round). Offensive round win rate is not quite constant,
+although never veers more than 10\% from this global average.
 
@@
 in esports. Work has been done to examine in-round win probability in
-other FPS titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva
-2022)) and Valorant ((DeRover 2021)), both of which are round-based like
+other FPS titles such as Counter-Strike (Xenopoulos, Freeman, and Silva
+2022) and Valorant (DeRover 2021), both of which are round-based like
 CoD SnD. However, research on round-level trends is sparse, perhaps
@@
 Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected
-proportion for \(s = 11\) and the naive assumption that \(p = 0.5\),
-along with the observed frequencies observed in CoD SnD, as both a count
-\(N_O(i)\) (of series lasting \(i\) rounds) and a proportion \(P_O(i)\)
-of all series.
+probabilities for \(s = 11\) under the naive assumption that
+\(p_0 = 0.5\) for a given round, along with the observed frequencies
+observed in CoD SnD (\(P_O(i)\), \(N_O(i)\))).
 
 \begin{longtable}{rrrr}
-  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($Pr(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p = 0.5$) of winning each round.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
+  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p_0 = 0.5$) of winning each game.
+The observed frequencies observed are shown as a count $N_O(i)$ and as a proportion $P_O(i)$ of all series.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
   \toprule
@@
 where \(i \in R = [6, 7, 8, 9, 10, 11]\)) under the assumption that each
-team has a 50\% probability (\(p = 0.5\)) of winning each game
+team has a 50\% probability (\(p_0 = 0.5\)) of winning each game
 \{\#tbl-prob-series-lasting-i-rounds\} along with the observed
@@
 as 16.0 (p-value of 0.0068), I can comfortably reject the constant
-probability null hypothesis, event at a confidence level of
-\(\alpha = 0.01\).
+probability null hypothesis for \(p_0 = 0.5\), event at a confidence
+level of \(\alpha = 0.01\).
 
@@
 Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
-\(P_E(i)\) when re-applying Equation \ref{eq:series-length} for each new
-\(p\). I observe that \(P_E(i)\) is notably smaller for \(p_{1,2,3}\)
-when \(i \in [10, 11]\) and higher for \(i \in [6, 7]\), more closely
-matching \(P_O(i)\).
+\(P_E(i)\) when re-applying Equation \ref{eq:series-length} for each the
+maximum likelihood estimate \(p_2 = 0.575\).\footnote{The method of
+  moments and minimum \(\chi^2\) estimates for \(p\) are omitted simply
+  because the results would be nearly identical to those for the maximum
+  likelihood estimate of \(p\) (since they are all \(\approx 0.575\).} I
+observe that \(P_E(i)\) is notably larger for \(p_{2}\) when
+\(i \in [6, 7]\), more closely matching \(P_O(i)\). \(p_{2}\) is also
+closer to \(P_O(i)\) for \(i \in [9, 10]\), although not for
+\(i \in [8, 11]\).
 
-\begin{longtable}[]{@{}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.2427}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1456}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1650}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.1748}}
-  >{\raggedleft\arraybackslash}p{(\columnwidth - 10\tabcolsep) * \real{0.0971}}@{}}
-\caption{The probabilities that a best-of-11 series lasts $i$ rounds under various assumptions for $p$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\begin{longtable}[]{@{}rrrr@{}}
+\caption{The probabilities that a best-of-11 series lasts $i$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
-\begin{minipage}[b]{\linewidth}\raggedleft
-Series lasts \(i\) rounds
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-0. \(p\) = 0.5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-1. \(p\) = 0.5725
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-2. \(p\) = 0.575
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-3. \(p\) = 0.5775
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-\(P_O(i)\)
-\end{minipage} \\
-\midrule()
-\endfirsthead
-\toprule()
-\begin{minipage}[b]{\linewidth}\raggedleft
-Series lasts \(i\) rounds
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-0. \(p\) = 0.5
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-1. \(p\) = 0.5725
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-2. \(p\) = 0.575
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-3. \(p\) = 0.5775
-\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedleft
-\(P_O(i)\)
-\end{minipage} \\
+Series lasts \(i\) rounds & \(p_0\) = 0.5 & \(p_2\) = 0.575 & \(P_O(i)\) \\
 \midrule()
 \endhead
-6 & 3.1\% & 4.1\% & 4.2\% & 4.3\% & 4.7\% \\
-7 & 9.4\% & 11.1\% & 11.2\% & 11.4\% & 11.9\% \\
-8 & 16.4\% & 17.7\% & 17.8\% & 17.9\% & 16.5\% \\
-9 & 21.9\% & 21.8\% & 21.8\% & 21.8\% & 21.7\% \\
-10 & 24.6\% & 23.1\% & 23.0\% & 22.9\% & 21.5\% \\
-11 & 24.6\% & 22.1\% & 22.0\% & 21.8\% & 23.7\% \\
+6 & 3.1\% & 4.2\% & 4.7\% \\
+7 & 9.4\% & 11.2\% & 11.9\% \\
+8 & 16.4\% & 17.8\% & 16.5\% \\
+9 & 21.9\% & 21.8\% & 21.7\% \\
+10 & 24.6\% & 23.0\% & 21.5\% \\
+11 & 24.6\% & 22.0\% & 23.7\% \\
 \bottomrule()

### 2022-08-14 paper2/paper2.Rmd
rendered p2

@@
   My research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).
-I find evidence in CoD supprting the hypothesis that round win probability can be modeled as constant across the series, although not at a naive 50%.
+First, I find evidence supprting the hypothesis that round win probability can be modeled as a constant across the series, although not at the naive 50%.
 Second, I examine post-streak round win probability, in search of evidence positive recency (the "hot hand" fallacy) or negative recency (the "gambler's falacy").
@@
 Call of Duty (CoD), first released in 2003, is one of the most popular first-person shooter (FPS) video game franchises of all-time.
-The most popular mode in the competitive scene is "Search and Destroy" (SnD), which bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in professional leagues.
-SnD is one-sided game mode in which one team, the offensive side, tries to destroy one of two designated bomb sites on the map.
+The most popular mode in the competitive scene is "Search and Destroy" (SnD).[^1] SnD is a one-sided game mode in which one team, the offensive side, tries to destroy one of two designated bomb sites on the map.
 
-In professional CoD, a team must win six rounds of SnD to win the match.[^1] A round can end in one of fmy ways:
+[^1]: SnD bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in more popular professional leagues.
 
-[^1]: A maximum of 11 even rounds can be played. There is no "sudden death" or "win by two" rule like there are for SnD equivalent in professional Counter-Strike and Valorant matches.
+In professional CoD SnD, a team take turns playing offense and defense every round. They must win six rounds to win the series.[^2] A round can end in one of five ways:
+
+[^2]: A maximum of 11 even rounds can be played. There is no "sudden death" or "win by two" rule like there are for SnD equivalent in professional Counter-Strike and Valorant matches.
 
 1.  One team eliminates all members of the other team prior to a bomb plant. (Eliminating team wins.)
-2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^2] (Offense wins.)
-3.  The defensive team defuses the bomb after a bomb plant.[^3] (Defense wins.)
+2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^3] (Offense wins.)
+3.  The defensive team defuses the bomb after a bomb plant.[^4] (Defense wins.)
 4.  The offensive team does not make a plant by the time the round timer ends. (Defense wins.)
 
-[^2]:
+[^3]:
     -   The bomb can be picked up by any member of the offensive team.
@@
 
-[^3]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
-
-Teams take turns playing offense and defense every round.
+[^4]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
 
@@
 
-CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tmynaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), running since 2020 and completing three year-long "seasons" completed as of August 2022.[^4] The data set consists of all SnD matches played in tmynaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
-Data was collected in spreadsheets by community member "IOUTurtle".[^5]
+CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), operating since 2020.
+The CDL has completed three year-long "seasons" as of August 2022.[^5]
 
-[^4]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
+[^5]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
 Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
@@
 
-[^5]: Data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>
+The data set consists of all SnD matches played in tournanaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
+Data was collected in spreadsheets by community member "IOUTurtle".[^6]
 
-The empirical offensive round win percentage across all rounds is 47.8%.[^6] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+[^6]: Data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>
+
+The empirical offensive round win percentage across all rounds is 47.8%.[^7] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
@@
 
-[^6]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
+[^7]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
 
@@
 
-There have been only a handful of studies of the distribution of games played in a series, most of which assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state.
-[@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p = 0.5$.
+There have been a handful of studies of the distribution of games played in a series of a professional sport.
+Most assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state.
+Mosteller [-@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p = 0.5$.
 Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$.
-in each case: (1) a "method of moments" approach in which one solves for $p$.
-from the empirical average number of games won by the loser of the series; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series, and (3) minimizing the chi-square goodness of fit estimate for $p$.
+in each case: (1) solving for $p$ from the empirical average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
+maximum likelihood), and (3) minimizing the chi-square goodness of fit statistic for $p$.
 
-[@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
-Chance applies finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^7] Chance's work is closely related to mys and, in fact, provides a guide for the first part of my investigation.
+Chance [-@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
+Chance finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^8] Chance's work is closely related to mine, and, in fact, provides a guide for the first part of my investigation.
 
-[^7]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
+[^8]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^8] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
-Per [@ayton2004], negative recency is "the belief that, for random events, runs of a particular outcome ...
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^9] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
+Per Ayton et al.
+[-@ayton2004], negative recency is "the belief that, for random events, runs of a particular outcome ...
 will be balanced by a tendency for the opposite outcome", while positive recency is the expectation of observing future results that match recent results.
 
-[^8]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^9]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
 Studying both player streaks and team streaks in basketball, in both observational and controlled settings.
-[@gilovich1985] do not find evidence for the hot hand phenomenon.
-Recently , [@miller2018] refute [@gilovich1985]'s conclusions, finding mathematical evidence that seems to support negative recency.
+Gilovich et al.
+[-@gilovich1985] do not find evidence for the hot hand phenomenon.
+Recently, Miller et al.
+[-@miller2018] refuted the conclusions of Gilovich et al.
+, finding mathematical evidence that seems to support negative recency.
 Specifically, they find that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" (streak selection bias) that imply that, under i.i.d.
@@
 Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^9]
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^10]
 
-[^9]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+[^10]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
 
@@
 
-The general formula for the probability $P_E(i)$ that a best-of-$s$ series lasts $i$ rounds given constant probability $p$ of one team[^10] winning each round is
+The general formula for the probability $P_E(i)$ that a best-of-$s$ series lasts $i$ rounds given constant probability $p$ of one team[^11] winning each round is
 
-[^10]: If $p > 0.5$, then I might say that this team is the better team (known omnisciently).
+[^11]: If $p > 0.5$, then I might say that this team is the better team (known omnisciently).
 
 $$
-q = 1 - p, s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}, s_2^{'} = 1 - s_2
+q = 1 - p, s_1 = \frac{s_1 - 1}{2}, s_2 = \frac{s_1 + 1}{2}, s_2^{'} = 1 - s_2
 $$
@@
 
-Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected probabilities for $s = 11$ under the naive assumption that $p_0 = 0.5$ for a given round, along with the observed frequencies observed in CoD SnD ($P_O(i)$, $N_O(i)$)).
+Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected probabilities for $s = 11$ under the naive assumption that $p_0 = 0.5$ for a given round, along with the observed proportions $P_O(i)$ in CoD SnD.
 
@@
 \begin{longtable}{rrrr}
-  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p_0 = 0.5$) of winning each game.
+  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
 The observed frequencies observed are shown as a count $N_O(i)$ and as a proportion $P_O(i)$ of all series.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
@@
 ```
-The probabilities that a best-of-11 series lasts $i$ rounds ($P(i)$, where $i \in R = [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50% probability ($p_0 = 0.5$) of winning each game {#tbl-prob-series-lasting-i-rounds} along with the observed frequencies of series lasting $i$ rounds, expressed as a percentage $P_O(i)$ and as a count ($N_O$)
-
 ```{r}
@@
 
-Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability $p$ for winning a given round in a CoD SnD that I find when applying the three methods suggested by Mosteller [-@mosteller1952].
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability $p$ that I find when applying the three methods suggested by Mosteller [-@mosteller1952].
 Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ-test}, each results in a $\chi^2$ value for which I cannot reject the constant probability null hypothesis.
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(i)$ when re-applying Equation \ref{eq:series-length} for each the maximum likelihood estimate $p_2 = 0.575$.[^11] I observe that $P_E(i)$ is notably larger for $p_{2}$ when $i \in [6, 7]$, more closely matching $P_O(i)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(i)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^12] I observe that $P_E(i)$ is notably larger for $p_{2}$ when $i \in [6, 7]$, more closely matching $P_O(i)$.
 $p_{2}$ is also closer to $P_O(i)$ for $i \in [9, 10]$, although not for $i \in [8, 11]$.
 
-[^11]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$.
+[^12]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$.
 
@@
 ```
-So I conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $p$ ($\approx 0.575$).
+It is fair to conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $p$ ($\approx 0.575$).
 

### 2022-08-14 paper2/paper2.tex
rendered p2

@@
 professional Search and Destroy (SnD) matches of the popular
-first-person shooter game Call of Duty (CoD). I find evidence in CoD
-supprting the hypothesis that round win probability can be modeled as
-constant across the series, although not at a naive 50\%. Second, I
+first-person shooter game Call of Duty (CoD). First, I find evidence
+supprting the hypothesis that round win probability can be modeled as a
+constant across the series, although not at the naive 50\%. Second, I
 examine post-streak round win probability, in search of evidence
@@
 first-person shooter (FPS) video game franchises of all-time. The most
-popular mode in the competitive scene is ``Search and Destroy'' (SnD),
-which bears resemblance to ``Bomb Defusal'' in Counter-Strike and
-``Plant/Defuse'' in Valorant, two other FPS games played in professional
-leagues. SnD is one-sided game mode in which one team, the offensive
-side, tries to destroy one of two designated bomb sites on the map.
+popular mode in the competitive scene is ``Search and Destroy''
+(SnD).\footnote{SnD bears resemblance to ``Bomb Defusal'' in
+  Counter-Strike and ``Plant/Defuse'' in Valorant, two other FPS games
+  played in more popular professional leagues.} SnD is a one-sided game
+mode in which one team, the offensive side, tries to destroy one of two
+designated bomb sites on the map.
 
-In professional CoD, a team must win six rounds of SnD to win the
-match.\footnote{A maximum of 11 even rounds can be played. There is no
-  ``sudden death'' or ``win by two'' rule like there are for SnD
-  equivalent in professional Counter-Strike and Valorant matches.} A
-round can end in one of fmy ways:
+In professional CoD SnD, a team take turns playing offense and defense
+every round. They must win six rounds to win the series.\footnote{A
+  maximum of 11 even rounds can be played. There is no ``sudden death''
+  or ``win by two'' rule like there are for SnD equivalent in
+  professional Counter-Strike and Valorant matches.} A round can end in
+one of five ways:
 
@@
 
-Teams take turns playing offense and defense every round.
-
 I adopt the terminology ``series'' to refer to what CoD SnD players
@@
 CoD has roughly gone through three eras of professional gaming: (1)
-Major League Gaming (MLG) tmynaments prior to 2016; (2) the CoD World
+Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
 League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
-(CDL), running since 2020 and completing three year-long ``seasons''
-completed as of August 2022.\footnote{CoD is fairly unique compared to
+(CDL), operating since 2020. The CDL has completed three year-long
+``seasons'' as of August 2022.\footnote{CoD is fairly unique compared to
   other esports in that it runs on an annual lifecycle (released coming
@@
   era, the games released have been Modern Warfare (2020), Cold War
-  (2021) and Vanguard (2022).} The data set consists of all SnD matches
-played in tmynaments and qualifiers during the CDL era, totaling 7,792
-rounds across 852 series. Data was collected in spreadsheets by
-community member ``IOUTurtle''.\footnote{Data:
-  \url{https://linktr.ee/CDLArchive}. Author:
-  \url{https://twitter.com/IOUTurtle}}
+  (2021) and Vanguard (2022).}
+
+The data set consists of all SnD matches played in tournanaments and
+qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
+Data was collected in spreadsheets by community member
+``IOUTurtle''.\footnote{Data: \url{https://linktr.ee/CDLArchive}.
+  Author: \url{https://twitter.com/IOUTurtle}}
 
@@
 
-There have been only a handful of studies of the distribution of games
-played in a series, most of which assume a constant probability \(p\) of
-a given team winning a game in the series, regardless of the series
-state. (Mosteller 1952) observed that the American League had dominated
-the National League in Major League Baseball's (MLB) World Series
-matchups, implying that matchups should not modeled with \(p = 0.5\).
-Mosteller proposed three approaches for identifying the optimal constant
-probability value of the stronger team in the World Series, finding
-\(p \approx 0.65\). in each case: (1) a ``method of moments'' approach
-in which one solves for \(p\). from the empirical average number of
-games won by the loser of the series; (2) maximizing the likelihood that
-the sample would have been drawn from a population in which the
-probability of a team winning a game is constant across the series, and
-(3) minimizing the chi-square goodness of fit estimate for \(p\).
+There have been a handful of studies of the distribution of games played
+in a series of a professional sport. Most assume a constant probability
+\(p\) of a given team winning a game in the series, regardless of the
+series state. Mosteller (1952) observed that the American League had
+dominated the National League in Major League Baseball's (MLB) World
+Series matchups, implying that matchups should not modeled with
+\(p = 0.5\). Mosteller proposed three approaches for identifying the
+optimal constant probability value of the stronger team in the World
+Series, finding \(p \approx 0.65\). in each case: (1) solving for \(p\)
+from the empirical average number of games won by the loser of the
+series, which he called the ``method of moments'' approach; (2)
+maximizing the likelihood that the sample would have been drawn from a
+population in which the probability of a team winning a game is constant
+across the series (i.e.~maximum likelihood), and (3) minimizing the
+chi-square goodness of fit statistic for \(p\).
 
-(Chance 2020) re-examines the constant probability notion in Major
+Chance (2020) re-examines the constant probability notion in Major
 League Baseball's World Series (1923--2018), the National Basketball
 Association's Finals (1951--2018), and the National Hockey League's
-Stanley Cup (1939--2018). Chance applies finds strong evidence against
-the null hypothesis of \(p = 0.5\) in the MLB and NHL championship
-series when applying Mosteller's first and second methods.\footnote{Chance
-  goes on to outline a conditional probability framework (likelihood of
-  winning a game given the series state) which can exactly explain the
+Stanley Cup (1939--2018). Chance finds strong evidence against the null
+hypothesis of \(p = 0.5\) in the MLB and NHL championship series when
+applying Mosteller's first and second methods.\footnote{Chance goes on
+  to outline a conditional probability framework (likelihood of winning
+  a game given the series state) which can exactly explain the
   distribution of the number of games played.} Chance's work is closely
-related to mys and, in fact, provides a guide for the first part of my
+related to mine, and, in fact, provides a guide for the first part of my
 investigation.
@@
 the ``gambler's fallacy'' (negative recency) and ``hot hand fallacy''
-(positive recency). Per (Ayton and Fischer 2004), negative recency is
-``the belief that, for random events, runs of a particular outcome
-\ldots{} will be balanced by a tendency for the opposite outcome'',
-while positive recency is the expectation of observing future results
-that match recent results.
+(positive recency). Per Ayton et al. (2004), negative recency is ``the
+belief that, for random events, runs of a particular outcome \ldots{}
+will be balanced by a tendency for the opposite outcome'', while
+positive recency is the expectation of observing future results that
+match recent results.
 
 Studying both player streaks and team streaks in basketball, in both
-observational and controlled settings. (Gilovich, Vallone, and Tversky
-1985) do not find evidence for the hot hand phenomenon. Recently ,
-(Miller and Sanjurjo 2018) refute (Gilovich, Vallone, and Tversky
-1985)'s conclusions, finding mathematical evidence that seems to support
-negative recency. Specifically, they find that a ``bias exists in a
-common measure of the conditional dependence of present outcomes on
-streaks of past outcomes in sequential data'' (streak selection bias)
-that imply that, under i.i.d. conditions, ``the proportion of successes
-among the outcomes that immediately follow a streak of consecutive
-successes is expected to be strictly less than the underlying
-(conditional) probability of success''. I agree with Miller's findings,
-accounting for the streak selection bias in my study of momentum.
+observational and controlled settings. Gilovich et al. (1985) do not
+find evidence for the hot hand phenomenon. Recently, Miller et al.
+(2018) refuted the conclusions of Gilovich et al.~, finding mathematical
+evidence that seems to support negative recency. Specifically, they find
+that a ``bias exists in a common measure of the conditional dependence
+of present outcomes on streaks of past outcomes in sequential data''
+(streak selection bias) that imply that, under i.i.d. conditions, ``the
+proportion of successes among the outcomes that immediately follow a
+streak of consecutive successes is expected to be strictly less than the
+underlying (conditional) probability of success''. I agree with Miller's
+findings, accounting for the streak selection bias in my study of
+momentum.
 
@@
 \[
-q = 1 - p, s_1 = \frac{s - 1}{2}, s_2 = \frac{s + 1}{2}, s_2^{'} = 1 - s_2
+q = 1 - p, s_1 = \frac{s_1 - 1}{2}, s_2 = \frac{s_1 + 1}{2}, s_2^{'} = 1 - s_2
 \]
@@
 probabilities for \(s = 11\) under the naive assumption that
-\(p_0 = 0.5\) for a given round, along with the observed frequencies
-observed in CoD SnD (\(P_O(i)\), \(N_O(i)\))).
+\(p_0 = 0.5\) for a given round, along with the observed proportions
+\(P_O(i)\) in CoD SnD.
 
 \begin{longtable}{rrrr}
-  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i = {6, 7, 8, 9, 10, 11}$) under the assumption that each team has a 50% probability ($p_0 = 0.5$) of winning each game.
+  \caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
 The observed frequencies observed are shown as a count $N_O(i)$ and as a proportion $P_O(i)$ of all series.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
@@
 
-The probabilities that a best-of-11 series lasts \(i\) rounds (\(P(i)\),
-where \(i \in R = [6, 7, 8, 9, 10, 11]\)) under the assumption that each
-team has a 50\% probability (\(p_0 = 0.5\)) of winning each game
-\{\#tbl-prob-series-lasting-i-rounds\} along with the observed
-frequencies of series lasting \(i\) rounds, expressed as a percentage
-\(P_O(i)\) and as a count (\(N_O\))
-
 Calculating the chi-square goodness of fit statistic
@@
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for
-the constant round win probability \(p\) for winning a given round in a
-CoD SnD that I find when applying the three methods suggested by
-Mosteller (1952). Each is approximately or equal to 0.575, and, when
-applying Equation \ref{eq:chi-squ-test}, each results in a \(\chi^2\)
-value for which I cannot reject the constant probability null
-hypothesis.
+the constant round win probability \(p\) that I find when applying the
+three methods suggested by Mosteller (1952). Each is approximately or
+equal to 0.575, and, when applying Equation \ref{eq:chi-squ-test}, each
+results in a \(\chi^2\) value for which I cannot reject the constant
+probability null hypothesis.
 
@@
 Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
-\(P_E(i)\) when re-applying Equation \ref{eq:series-length} for each the
+\(P_E(i)\) when re-applying Equation \ref{eq:series-length} for the
 maximum likelihood estimate \(p_2 = 0.575\).\footnote{The method of
@@
 
-So I conclude that the constant round win probability assumption can be
-valid in CoD SnD series with the appropriate choice of \(p\)
-(\(\approx 0.575\)).
+It is fair to conclude that the constant round win probability
+assumption can be valid in CoD SnD series with the appropriate choice of
+\(p\) (\(\approx 0.575\)).
 

### 2022-08-14 presentation/presentation.qmd
replace paper/ with paper2/. move presentation, data, and scripts to dirs

--- 2022-08-13 presentation.qmd
@@
 ```{r}
+#| label: cod_streak_series
+cod_streaks_res$series |> 
+  arrange(n_rounds) |> 
+  transmute(
+    `# of rounds (i)` = n_rounds, 
+    `P(i)` = scales::percent(prop_expected, accuracy = 0.1)
+  ) |> 
+  knitr::kable()
+
+cod_streaks_res$series |> 
+  select(
+    n_rounds,
+    prop_expected,
+    prop_actual,
+    n_actual
+  ) |> 
+  arrange(n_rounds) |> 
+  gt::gt() |> 
+  gt::cols_label(
+    n_rounds = '# of rounds (i)', 
+    prop_expected = 'P(i)',
+    prop_actual = '%',
+    n_actual = 'N'
+  ) |> 
+  gt::fmt_percent(
+    decimals = 1,
+    columns = c('prop_expected', 'prop_actual')
+  ) |> 
+  gt::cols_align(
+    align = 'right',
+    columns = c('prop_expected', 'prop_actual')
+  ) |> 
+  gt::tab_spanner(
+    label = 'Observed',
+    columns = c('prop_actual', 'n_actual')
+  ) |> 
+  gt::as_latex() |> 
+  pluck(1)
+```
+
+```{r}
 #| label: chance-2019
@@
 cod_theoretical_constant_p2 <- cod_theoretical_series_lengths2 |> 
-  slice_max(theoretical_series_length, n = 1) |> 
+  slice_max(theoretical_series_length, n = 1, with_ties = FALSE) |> 
   pull(p)

### 2022-08-14 scripts/1-scrape-cod.R
data paths

@@ -245,5 +245,5 @@ cod_rounds <- cod_series |>
   ) |> 
   relocate(series_id, .after = 'game')
 filename <- 'cod_rounds.qs'
-sprintf('%s%s', c('', 'paper/'), filename) |> 
+sprintf('%s%s', c('data/', 'paper/'), filename) |> 
   walk(~qs::qsave(cod_rounds, .x))

### 2022-08-14 scripts/1-scrape-valorant.R

@@ -337,7 +337,7 @@ val_rounds <- bind_rows(
     more_weird_val_series_outcomes |> distinct(series_id),
     by = 'series_id'
   )
-qs::qsave(val_rounds, 'valorant_rounds.qs')
+qs::qsave(val_rounds, 'data/valorant_rounds.qs')
 
 # val_rounds |> 
 #   group_by(team, series_id) |> 

### 2022-08-14 scripts/1-scrape-cod.R
data paths

@@ -245,5 +245,5 @@ cod_rounds <- cod_series |>
   ) |> 
   relocate(series_id, .after = 'game')
 filename <- 'cod_rounds.qs'
-sprintf('%s%s', c('data/', 'paper/'), filename) |> 
+sprintf('%s/%s', c('data', 'paper', 'presentation'), filename) |> 
   walk(~qs::qsave(cod_rounds, .x))

### 2022-08-14 paper/paper.Rmd
data paths
add init streak blocks of code

--- 2022-08-14 paper2/paper2.Rmd
@@
 
-cod_rounds <- qs::qread('cod_rounds.qs')
+cod_rounds <- qs::qread('data/cod_rounds.qs')
 ```
@@
 
+# Momentum
+
+```{r}
+#| label: qs-funcs
+#| eval: true
+load_qs <- function(name) {
+  res <- qs::qread(sprintf('../data/%s.qs', name))
+  assign(name, value = res, envir = .GlobalEnv)
+}
+save_qs <- function(df, name = deparse(substitute(df))) {
+  qs::qsave(df, sprintf('../data/%s.qs', name))
+}
+```
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 10000, seed = 42, ...) {
+  withr::local_seed(seed)
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+
+cod_round_streaks <- cod_rounds |> 
+  group_by(series_id, team) |> 
+  mutate(
+    won_prior_round1 = lag(win_round, n = 1, default = NA),
+    won_prior_round2 = lag(win_round, n = 2, default = NA),
+    won_prior_round3 = lag(win_round, n = 3, default = NA),
+    won_prior_round4 = lag(win_round, n = 4, default = NA),
+    won_prior_round5 = lag(win_round, n = 5, default = NA)
+  ) |> 
+  ungroup() |>
+  select(
+    series_id,
+    team,
+    is_offense,
+    round,
+    n_rounds,
+    win_round,
+    starts_with('won_prior_round')
+  )
+
+.postprocess_round_streaks <- function(k, round_streaks, probs_nx_k, ...) {
+
+  cols <- sprintf('won_prior_round%d', 2:k)
+  col_syms <- syms(cols)
+  round_streaks_after_x <- round_streaks |> 
+    drop_na(!!!col_syms) |> 
+    count(n_rounds, ..., win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+
+  round_win_prop_after_x_wins <- round_streaks_after_x |> 
+    filter(won_prior_round1, !!!col_syms)
+
+  suppressMessages(
+    round_win_prop_after_x_wins_w_probs <- round_win_prop_after_x_wins |> 
+      group_by(n_rounds, ...) |> 
+      mutate(
+        total = sum(n),
+        prop = n / total
+      ) |> 
+      ungroup() |> 
+      filter(win_round) |> 
+      select(n_rounds, ..., n, total, prop) |> 
+      arrange(n_rounds, ...) |> 
+      inner_join(
+        probs_nx_k
+      )
+  )
+
+  round_win_prop_after_x_wins_w_probs |> 
+    nest(data = -c(n_rounds, ...)) |> 
+    mutate(
+      gt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      lt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      gt_is_signif = gt_p_value <= 0.05,
+      lt_is_signif = lt_p_value <= 0.05,
+      is_signif = case_when(
+        gt_is_signif ~ 'Better',
+        lt_is_signif ~ 'Worse',
+        TRUE ~ 'Neither'
+      )
+    ) |> 
+    unnest(data)
+}
+
+summarize_cod_win_prop_after_x_wins <- function(k) {
+  probs_nx_k <- tibble(
+    n_rounds = 7L:11L
+  ) |> 
+    mutate(
+      prior_p = 6L / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  .postprocess_round_streaks(
+    k = k,
+    round_streaks = cod_round_streaks,
+    probs_nx_k = probs_nx_k
+  )
+}
+
+cod_round_win_prop_after_x_wins <- tibble(win_streak = 2L:4L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins)
+  ) |>
+  unnest(data)
+save_qs(cod_round_win_prop_after_x_wins)
+```
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins_and_rounds
+summarize_cod_win_prop_after_x_wins_y_rounds <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    round = 3L:11L
+  ) |> 
+    filter(round >= (k + 1L)) |> 
+    mutate(
+      prior_p = 6L / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  .postprocess_round_streaks(
+    k = k,
+    round_streaks = cod_round_streaks,
+    probs_nx_k = probs_nx_k,
+    round
+  )
+}
+
+cod_round_win_prop_after_x_wins_y_rounds <- tibble(win_streak = 2L:4L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins_y_rounds)
+  ) |>
+  unnest(data)
+save_qs(cod_round_win_prop_after_x_wins_y_rounds)
+```
+
+Despite the implication that one can model team round win probability in CoD SnD as a constant, anecdotally many believe in momentum and positive recency, i.e. the "hot hand".
+
+Miller et al. [-@miller2018]
+
 # References {.unnumbered}

### 2022-08-15 paper/paper.Rmd
start momentum section

--- 2022-08-14 paper2/paper2.Rmd
@@
 
-## Distribution of rounds played
+## Distribution of rounds played {#sec:analysis-1}
 
@@
 ```{=tex}
-\begin{equation}\protect\hypertarget{eq-series-length}{}{
+\begin{equation}\protect\hypertarget{eq:series-length}{}{
 \chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11].
@@
 
+## Momentum {#sec:analysis-2}
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 10000, seed = 42, ...) {
+  withr::local_seed(seed)
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+
+cod_round_streaks <- cod_rounds |> 
+  group_by(series_id, team) |> 
+  mutate(
+    won_prior_round1 = lag(win_round, n = 1, default = NA),
+    won_prior_round2 = lag(win_round, n = 2, default = NA),
+    won_prior_round3 = lag(win_round, n = 3, default = NA),
+    won_prior_round4 = lag(win_round, n = 4, default = NA),
+    won_prior_round5 = lag(win_round, n = 5, default = NA)
+  ) |> 
+  ungroup() |>
+  select(
+    series_id,
+    team,
+    is_offense,
+    round,
+    n_rounds,
+    win_series,
+    win_round,
+    starts_with('won_prior_round')
+  )
+
+postprocess_round_streaks <- function(k, probs_nx_k, ...) {
+
+  cols <- sprintf('won_prior_round%d', 2:k)
+  col_syms <- syms(cols)
+  cod_round_streaks_after_x <- cod_round_streaks |> 
+    drop_na(!!!col_syms) |> 
+    count(n_rounds, ..., win_series, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+
+  cod_round_win_prop_after_z <- cod_round_streaks_after_x |> 
+    filter(won_prior_round1, !!!col_syms)
+
+  suppressMessages(
+    cod_round_win_prop_after_z_with_probs <- cod_round_win_prop_after_z |> 
+      group_by(win_series, n_rounds) |> 
+      mutate(
+        total = sum(n),
+        prop = n / total
+      ) |> 
+      ungroup() |> 
+      filter(win_round) |> 
+      select(n_rounds, ..., win_series, n, total, prop) |> 
+      arrange(n_rounds, ...) |> 
+      inner_join(
+        probs_nx_k
+      )
+  )
+
+  cod_round_win_prop_after_z_with_probs |> 
+    nest(data = -c(n_rounds, win_series, ...)) |> 
+    mutate(
+      gt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$prior_p, alternative = 'greater') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      lt_p_value = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$prior_p, alternative = 'less') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      gt_p_value_adj = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      lt_p_value_adj = map_dbl(
+        data, 
+        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
+          broom::tidy() |>
+          pull(p.value)
+      ),
+      gt_is_signif = gt_p_value <= 0.05,
+      lt_is_signif = lt_p_value <= 0.05,
+      gt_is_signif_adj = gt_p_value_adj <= 0.05,
+      lt_is_signif_adj = lt_p_value_adj <= 0.05
+    ) |> 
+    unnest(data)
+}
+
+summarize_cod_win_prop_after_x_wins <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    win_series = c(TRUE, FALSE)
+  ) |> 
+    mutate(
+      is_valid = case_when(
+        win_series ~ TRUE,
+        (n_rounds - !!k - 6L) > 0L ~ TRUE,
+        TRUE ~ FALSE
+      )
+    ) |> 
+    filter(is_valid) |> 
+    select(-is_valid) |> 
+    mutate(
+      prior_p = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  postprocess_round_streaks(
+    k = k,
+    probs_nx_k = probs_nx_k
+  )
+}
+
+cod_round_win_prop_after_x_wins <- tibble(win_streak = 2L:4L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins)
+  ) |>
+  unnest(data)
+```
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins-table
+cod_round_win_prop_after_x_wins |> 
+  mutate(
+    across(
+      matches('p_value'), 
+      ~case_when(
+        .x <= 0.01 ~ '<=0.01', 
+        round(.x, 2) == 1 ~ '1',
+        TRUE ~ as.character(round(.x, 2))
+      )
+    )
+  ) |>
+  # filter(win_streak == 3) |> 
+  select(
+    win_streak,
+    win_series,
+    n_rounds,
+    total,
+    prop,
+    prior_p,
+    expected_poststreak_p,
+    gt_p_value,
+    gt_p_value_adj
+  ) |> 
+  gt::gt() |> 
+  gt::fmt_percent(
+    decimals = 0,
+    columns = c(prop, prior_p, expected_poststreak_p)
+  ) |> 
+  gt::cols_label(
+    win_streak = 'Streak',
+    win_series = 'Win Series?',
+    n_rounds = 'Series lasts $i$ rounds',
+    total = 'N',
+    prop = 'Obs.',
+    prior_p = 'Naive',
+    expected_poststreak_p = 'Discounted',
+    gt_p_value = 'Naive',
+    gt_p_value_adj = 'Discounted'
+  ) |> 
+  gt::tab_spanner(
+    label = '%s',
+    columns = c(prop, prior_p, expected_poststreak_p)
+  ) |> 
+  gt::tab_spanner(
+    label = 'Binom. > p-value',
+    columns = c(gt_p_value, gt_p_value_adj)
+  )
+```
+
+Despite the implication that one can model team round win probability in CoD SnD as a constant, anecdotally many believe in momentum i.e.
+streaks not due to random chance.
+I now evaluate win frequency in rounds following a streak of length $k$.
+I account for the length of the series ($i$ rounds), modeling the expected round win probability after a streak of length $k$ as
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:pki}{}{
+  \hat{P}(\text{win round | k-round winning streak, series lasting i rounds})=\{
+  \begin{array}{cl}
+    \frac{6 - k}{i - k}, & \text{team wins series} \\
+    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
+  \end{array}.
+}\label{eq:pki}\end{equation}
+```
+Miller et al. [-@miller2018] provide evidence for negative recency suggesting that
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:pkid}{}{
+  \begin{array}{rcl}
+  \hat{P}_{ki,\text{diff}} & = & \hat{P}(\text{win round | k-round winning streak, series lasting i rounds}) -  \\
+    & & \hat{P}(\text{lose round | k-round losing streak, series lasting i rounds}) \\
+    E[\hat{P}_{ki,\text{diff}}] & \neq & 0
+  \end{array}
+}\label{eq:pkid}\end{equation}
+```
+given a deterministic i.i.d. Bernoulli probability $\hat{p}(\text{win round | k-round winning streak, series lasting i rounds)}$ (Equation \ref{eq:pki}.[^13]
+
+[^13]: Note that these probabilites are separate from those in Section \\ref{sec:analysis-1}.
+
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins, $k = 3$.[^14]
+
+[^14]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+
+```{r}
+#| label: cod_round_win_prop_after_x_wins_and_rounds
+summarize_cod_win_prop_after_x_wins_y_rounds <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    round = 3L:11L
+  ) |> 
+    filter(round >= (k + 1L)) |> 
+    mutate(
+      prior_p = 6L / n_rounds,
+      expected_poststreak_p = map2_dbl(
+        n_rounds, prior_p, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      )
+    )
+
+  postprocess_round_streaks(
+    k = k,
+    probs_nx_k = probs_nx_k,
+    round
+  )
+}
+
+cod_round_win_prop_after_x_wins_y_rounds <- tibble(win_streak = 2L:4L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_x_wins_y_rounds)
+  ) |>
+  unnest(data)
+```
+
 # References {.unnumbered}

### 2022-08-15 paper/paper.tex
start momentum section

--- 2022-08-13 paper/paper.tex
@@
 
-\usepackage{arxiv}
-\usepackage{orcidlink}
+\usepackage{longtable}
 \usepackage{amsmath}
-\usepackage[T1]{fontenc}
-\makeatletter
-\makeatother
-\makeatletter
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\AtBeginDocument{%
-\ifdefined\contentsname
-  \renewcommand*\contentsname{Table of contents}
-\else
-  \newcommand\contentsname{Table of contents}
-\fi
-\ifdefined\listfigurename
-  \renewcommand*\listfigurename{List of Figures}
-\else
-  \newcommand\listfigurename{List of Figures}
-\fi
-\ifdefined\listtablename
-  \renewcommand*\listtablename{List of Tables}
-\else
-  \newcommand\listtablename{List of Tables}
-\fi
-\ifdefined\figurename
-  \renewcommand*\figurename{Figure}
-\else
-  \newcommand\figurename{Figure}
-\fi
-\ifdefined\tablename
-  \renewcommand*\tablename{Table}
-\else
-  \newcommand\tablename{Table}
-\fi
-}
-\@ifpackageloaded{float}{}{\usepackage{float}}
-\floatstyle{ruled}
-\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
-\floatname{codelisting}{Listing}
-\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{caption}{}{\usepackage{caption}}
-\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
-\makeatother
-\makeatletter
-\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
-\makeatother
-\makeatletter
-\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
-\makeatother
-\makeatletter
-\makeatother
-\ifLuaTeX
-  \usepackage{selnolig}  % disable illegal ligatures
-\fi
-\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
-\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
-\urlstyle{same} % disable monospaced font for URLs
-\hypersetup{
-  pdftitle={They're Clutching up! Team Momentum in Round-Based Esports},
-  pdfauthor={Tony ElHabr},
-  colorlinks=true,
-  linkcolor={blue},
-  filecolor={Maroon},
-  citecolor={Blue},
-  urlcolor={Blue},
-  pdfcreator={LaTeX via pandoc}}
-
-\title{They're Clutching up! Team Momentum in Round-Based Esports}
-\author{
-Tony ElHabr\\\\Georgia Institute of
-Technology\\\\\href{mailto:anthonyelhabr@gmail.com}{anthonyelhabr@gmail.com}}
-\date{}
 \begin{document}
 \maketitle
+
 \begin{abstract}
@@
 professional Search and Destroy (SnD) matches of the popular
-first-person shooter game Call of Duty (CoD).
-
-First, I find evidence in CoD defying the naive hypothesis that a series
-represents a sequence of independent events (rounds), with each team
-having a constant 50\% probability of winning a given round.
-
-Second, I examine post-streak round win probability. I find that teams
-perform significantly worse than expected after streaks of 2, 3, and 4
-wins when series end up going to 9, 10, or 11 (maximum) rounds, even
-after accounting for the ``hot-hand'' phenomenon.
-
-Third, I compare win percentages in round one versus all other rounds,
-hypothesizing that there may be some advantage on either side when there
-is no prior information about how the opponent intends to play a given
-map in either game. I find only one instance for which there seems to be
-a significant defensive advantage in round one.
-
-Finally, I evaluate behavior when teams have two rounds left to win the
-series, observing a peak in COD offensive win percentages in the 4-4
-state, and no such oddity in Valorant.
+first-person shooter game Call of Duty (CoD). First, I find evidence
+supprting the hypothesis that round win probability can be modeled as a
+constant across the series, although not at the naive 50\%. Second, I
+examine post-streak round win probability, in search of evidence
+positive recency (the ``hot hand'' fallacy) or negative recency (the
+``gambler's falacy''). I find that teams perform significantly worse
+than expected after streaks of 2, 3, and 4 wins when series end up going
+to 9, 10, or 11 (maximum) rounds, suggesting the presence of negative
+recency.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, breakable]}{\end{tcolorbox}}\fi
 
@@
 Call of Duty (CoD), first released in 2003, is one of the most popular
-first-person shooter (FPS) video game franchises of all-time. Tthe most
-popular mode in the competitive scene is ``Search and Destroy'' (SnD),
-which bears resemblance to ``Bomb Defusal'' in Counter-Strike and
-``Plant/Defuse'' in Valorant, two other FPS games played in professional
-leagues. SnD is one-sided game mode in which one team, the offensive
-side, tries to destroy one of two designated bomb sites on the map.
+first-person shooter (FPS) video game franchises of all-time. The most
+popular mode in the competitive scene is ``Search and Destroy''
+(SnD).\footnote{SnD bears resemblance to ``Bomb Defusal'' in
+  Counter-Strike and ``Plant/Defuse'' in Valorant, two other FPS games
+  played in more popular professional leagues.} SnD is a one-sided game
+mode in which one team, the offensive side, tries to destroy one of two
+designated bomb sites on the map.
 
-In professional CoD, a team must win six rounds of SnD to win the
-match.\footnote{A maximum of 11 even rounds can be played. There is no
-  ``sudden death'' or ``win by two'' rule like there are for SnD
-  equivalent in professional Counter-Strike and Valorant matches.} A
-round can end in one of four ways:
+In professional CoD SnD, a team take turns playing offense and defense
+every round. They must win six rounds to win the series.\footnote{A
+  maximum of 11 even rounds can be played. There is no ``sudden death''
+  or ``win by two'' rule like there are for SnD equivalent in
+  professional Counter-Strike and Valorant matches.} A round can end in
+one of five ways:
 
@@
 
-Teams take turns playing offense and defense every round.
+I adopt the terminology ``series'' to refer to what CoD SnD players
+typically call a ``match'', so as to emulate the terminology of playoff
+series in professional leagues like the National Basketball Association,
+National Hockey League, and Major League Baseball. A ``game'' or a
+``match'' in such leagues is analogous to a ``round'' of CoD SnD.
 
 \hypertarget{data}{%
-\subsection{1. Data}\label{data}}
+\subsection{Data}\label{data}}
 
@@
 League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
-(CDL), running since 2020 and completing three year-long ``seasons''
-completed as of August 2022.\footnote{CoD is fairly unique compared to
+(CDL), operating since 2020. The CDL has completed three year-long
+``seasons'' as of August 2022.\footnote{CoD is fairly unique compared to
   other esports in that it runs on an annual lifecycle (released coming
@@
   era, the games released have been Modern Warfare (2020), Cold War
-  (2021) and Vanguard (2022).} The data set consists of all SnD matches
-played in tournaments and qualifiers during the CDL era, totaling 1,704
-series played, in which there were 15,584 rounds played. Data was
-collected in spreadsheets by community member ``IOUTurtle''.\footnote{Data:
-  https://linktr.ee/CDLArchive. Author: https://twitter.com/IOUTurtle}
+  (2021) and Vanguard (2022).}
 
-I adopt the terminology ``series'' to refer to what CoD SnD players
-typically call a ``match'', so as to emulate the terminology of playoff
-series in professional leagues like the National Basketball Association,
-National Hockey League, and Major League Baseball. A ``game'' or a
-``match'' in such leagues is analogous to a ``round'' of CoD SnD.
+The data set consists of all SnD matches played in tournanaments and
+qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
+Data was collected in spreadsheets by community member
+``IOUTurtle''.\footnote{Data: \url{https://linktr.ee/CDLArchive}.
+  Author: \url{https://twitter.com/IOUTurtle}}
+
+The empirical offensive round win percentage across all rounds is
+47.8\%.\footnote{Offensive round win percentage has been nearly constant
+  across the three games during the CDL era: 1. 47.2\% in MW (2020) 2.
+  47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)} Table
+\ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by
+series ``state'' (i.e.~the number of round wins by each team prior to an
+upcoming round). Offensive round win rate is not quite constant,
+although never veers more than 10\% from this global average.
+
+\begin{longtable}{crrrrrr}
+\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins}\label{tbl:cod-o-win-prop-by-series-state} \\
+\toprule
+& \multicolumn{6}{c}{Offense round wins} \\ 
+\cmidrule(lr){2-7}
+Defense round wins & 0 & 1 & 2 & 3 & 4 & 5 \\ 
+\midrule
+0 & 47.8\%
+(852) & 46.6\%
+(408) & 43.1\%
+(216) & 43.5\%
+(115) & 43.3\%
+(67) & 40.5\%
+(37) \\ 
+1 & 48.6\%
+(444) & 49.3\%
+(418) & 51.5\%
+(309) & 43.4\%
+(205) & 43.3\%
+(120) & 39.4\%
+(99) \\ 
+2 & 52.8\%
+(218) & 48.9\%
+(305) & 48.9\%
+(315) & 46.6\%
+(262) & 48.7\%
+(189) & 42.1\%
+(133) \\ 
+3 & 54.5\%
+(123) & 46.0\%
+(200) & 49.6\%
+(250) & 45.6\%
+(248) & 44.4\%
+(214) & 44.8\%
+(174) \\ 
+4 & 56.9\%
+(65) & 54.5\%
+(145) & 47.2\%
+(193) & 44.7\%
+(228) & 55.2\%
+(221) & 50.5\%
+(208) \\ 
+5 & 47.4\%
+(38) & 49.4\%
+(83) & 47.1\%
+(136) & 50.9\%
+(175) & 45.2\%
+(177) & 46.0\%
+(202) \\ 
+\bottomrule
+\end{longtable}
 
@@
 
-There have been only a handful of studies of the distribution of games
-played in a series, most of which assume a constant probability \(p\) of
-a given team winning a game in the series, regardless of the series
-state. Observing that the American League had dominated the National
-League in Major League Baseball's (MLB) World Series matchups, implying
-that matchups should not modeled with \(p=0.5\), (Mosteller 1952)
-proposed three approaches for identifying the optimal constant
-probability value of the stronger team in the World Series, finding
-\(p \approx 0.65\) in each case: (1) a ``method of moments'', an
-approach that solves for \(p\) from the empirical average number of
-games won by the loser of the series; (2) maximum likelihood, and (3)
-maximum chi-square approach. (Chance 2020) re-examines the constant
-probability notion in Major League Baseball's World Series (1923--2018),
-the National Basketball Association's Finals (1951--2018), and the
-National Hockey League's Stanley Cup (1939--2018). Chance applies
-Mosteller's method 1 and 2 and finds strong evidence against the null
-hypothesis of \(p = 0.5\) in the MLB and NHL championship series. Chance
-outlines a conditional probability framework (likelihood of winning a
-game given the series state) which can exactly explain the distribution
-of the number of games played.
+There have been a handful of studies of the distribution of games played
+in a series of a professional sport. Most assume a constant probability
+\(p\) of a given team winning a game in the series, regardless of the
+series state. Mosteller (1952) observed that the American League had
+dominated the National League in Major League Baseball's (MLB) World
+Series matchups, implying that matchups should not modeled with
+\(p = 0.5\). Mosteller proposed three approaches for identifying the
+optimal constant probability value of the stronger team in the World
+Series, finding \(p \approx 0.65\). in each case: (1) solving for \(p\)
+from the empirical average number of games won by the loser of the
+series, which he called the ``method of moments'' approach; (2)
+maximizing the likelihood that the sample would have been drawn from a
+population in which the probability of a team winning a game is constant
+across the series (i.e.~maximum likelihood), and (3) minimizing the
+chi-square goodness of fit statistic for \(p\).
 
-Momentum is one of the most frequently published topics in sports
-analytics. We often use use ``streaks'' and momentum interchangeably,
-but as (Steeger, Dulin, and Gonzalez 2021) note, momentum implies
-dependence between events, whereas streaking does not. (sentence about
-negative recency, hinting at ``hot hand''\ldots{} (Miller and Sanjurjo
-2018) debunking findings from (Gilovich, Vallone, and Tversky 1985))
+Chance (2020) re-examines the constant probability notion in Major
+League Baseball's World Series (1923--2018), the National Basketball
+Association's Finals (1951--2018), and the National Hockey League's
+Stanley Cup (1939--2018). Chance finds strong evidence against the null
+hypothesis of \(p = 0.5\) in the MLB and NHL championship series when
+applying Mosteller's first and second methods.\footnote{Chance goes on
+  to outline a conditional probability framework (likelihood of winning
+  a game given the series state) which can exactly explain the
+  distribution of the number of games played.} Chance's work is closely
+related to mine, and, in fact, provides a guide for the first part of my
+investigation.
 
-Despite the plethora of existing research on games played and momentum
-in sports, these topics have yet to be investigated heavily in esports.
-Work has been done to examine in-round win probability in other FPS
-titles such as Counter-Strike ((Xenopoulos, Freeman, and Silva 2022))
-and Valorant ((DeRover 2021)), both of which are round-based like CoD
-SnD. However, research on round-level trends is sparse, perhaps because
-games like Counter-Strike and Valorant both have economic aspects that
-can create clear advantages on side in a given round, given how prior
-rounds played out.\footnote{Additionally, both Counter-Strike and
-  Valorant have overtime rules and blocked offensive/defensive roles
+Momentum, one of most discussed topics in sports analytics, goes
+hand-in-hand with a discussion of the nature of series
+outcomes.\footnote{We often use use ``streaks'' and momentum
+  interchangeably, but as (Steeger, Dulin, and Gonzalez 2021) note,
+  momentum implies dependence between events, whereas streaking does
+  not.} Two opposing fallacies are observed in the context of momentum:
+the ``gambler's fallacy'' (negative recency) and ``hot hand fallacy''
+(positive recency). Per Ayton et al. (2004), negative recency is ``the
+belief that, for random events, runs of a particular outcome \ldots{}
+will be balanced by a tendency for the opposite outcome'', while
+positive recency is the expectation of observing future results that
+match recent results.
+
+Studying both player streaks and team streaks in basketball, in both
+observational and controlled settings. Gilovich et al. (1985) do not
+find evidence for the hot hand phenomenon. Recently, Miller et al.
+(2018) refuted the conclusions of Gilovich et al.~, finding mathematical
+evidence that seems to support negative recency. Specifically, they find
+that a ``bias exists in a common measure of the conditional dependence
+of present outcomes on streaks of past outcomes in sequential data''
+(streak selection bias) that imply that, under i.i.d. conditions, ``the
+proportion of successes among the outcomes that immediately follow a
+streak of consecutive successes is expected to be strictly less than the
+underlying (conditional) probability of success''. I agree with Miller's
+findings, accounting for the streak selection bias in my study of
+momentum.
+
+Despite the plethora of existing research on games played in a series
+and momentum in sports, these topics have yet to be investigated heavily
+in esports. Work has been done to examine in-round win probability in
+other FPS titles such as Counter-Strike (Xenopoulos, Freeman, and Silva
+2022) and Valorant (DeRover 2021), both of which are round-based like
+CoD SnD. However, research on round-level trends is sparse, perhaps
+because games like Counter-Strike and Valorant both have economic
+aspects that can create clear advantages on side in a given round, given
+how prior rounds played out.\footnote{Additionally, both Counter-Strike
+  and Valorant have overtime rules and blocked offensive/defensive roles
   (i.e.~playing either offense or defense for many consecutive rounds).}
@@
 
-The empirical offensive round win percentage across all rounds is
-47.8\%.\footnote{Offensive round win percentage has been nearly constant
-  across the three games during the CDL era: MW (2020) 47.2\%, Cold War
-  (2021) 47.9\%, Vanguard (2022) 48.1\%}
-Figure~\ref{fig-cod-o-round-win-prop} shows that offensive round win
-rate is not quite constant, although, on average, never veers more than
-10\% from this global average.
+First, I investigate the constant probability assumption and the
+distribution of rounds played in a series. Afterwards, I investigate
+momentum, building on my learnings from the constant probability
+assumption analysis.
 
-\begin{figure}
+\hypertarget{sec:analysis-1}{%
+\subsection{Distribution of rounds played}\label{sec:analysis-1}}
 
-{\centering \includegraphics{images/cod_o_round_win_prop.png}
+The general formula for the probability \(P_E(i)\) that a best-of-\(s\)
+series lasts \(i\) rounds given constant probability \(p\) of one
+team\footnote{If \(p > 0.5\), then I might say that this team is the
+  better team (known omnisciently).} winning each round is
 
-}
+\[
+q = 1 - p, s_1 = \frac{s_1 - 1}{2}, s_2 = \frac{s_1 + 1}{2}, s_2^{'} = 1 - s_2
+\]
 
-\caption{\label{fig-cod-o-round-win-prop}Offensive round win percentage
-by series state}
+\begin{equation}\protect\hypertarget{eq-series-length}{}{
+P_E(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
+}\label{eq:series-length}\end{equation}
 
-\end{figure}
+Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected
+probabilities for \(s = 11\) under the naive assumption that
+\(p_0 = 0.5\) for a given round, along with the observed proportions
+\(P_O(i)\) in CoD SnD.
+
+\begin{longtable}{rrrr}
+\caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
+The observed frequencies observed are shown as a count $N_O(i)$ and as a proportion $P_O(i)$ of all series.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
+\toprule
+&  & \multicolumn{2}{c}{Observed} \\ 
+\cmidrule(lr){3-4}
+Series lasts $i$ rounds & $P_E(i)$ & $P_O(i)$ & $N_O(i)$ \\ 
+\midrule
+6 & $3.1\%$ & $4.7\%$ & 40 \\ 
+7 & $9.4\%$ & $11.9\%$ & 101 \\ 
+8 & $16.4\%$ & $16.5\%$ & 141 \\ 
+9 & $21.9\%$ & $21.7\%$ & 185 \\ 
+10 & $24.6\%$ & $21.5\%$ & 183 \\ 
+11 & $24.6\%$ & $23.7\%$ & 202 \\ 
+\bottomrule
+\end{longtable}
+
+Calculating the chi-square goodness of fit statistic
+
+\begin{equation}\protect\hypertarget{eq:series-length}{}{
+\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11].
+}\label{eq:chi-squ-test}\end{equation}
+
+as 16.0 (p-value of 0.0068), I can comfortably reject the constant
+probability null hypothesis for \(p_0 = 0.5\), event at a confidence
+level of \(\alpha = 0.01\).
+
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for
+the constant round win probability \(p\) that I find when applying the
+three methods suggested by Mosteller (1952). Each is approximately or
+equal to 0.575, and, when applying Equation \ref{eq:chi-squ-test}, each
+results in a \(\chi^2\) value for which I cannot reject the constant
+probability null hypothesis.
+
+\begin{longtable}[]{@{}lrr@{}}
+\caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
+\toprule()
+Method & \(p\) & \(\chi^2\) (p-value) \\
+\midrule()
+\endfirsthead
+\toprule()
+Method & \(p\) & \(\chi^2\) (p-value) \\
+\midrule()
+\endhead
+0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
+1. Method of moments & 0.5725 & 3.6 (0.6) \\
+2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
+3. Minimum \(\chi^2\) & 0.5775 & 3.5 (0.62) \\
+\bottomrule()
+\end{longtable}
+
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
+\(P_E(i)\) when re-applying Equation \ref{eq:series-length} for the
+maximum likelihood estimate \(p_2 = 0.575\).\footnote{The method of
+  moments and minimum \(\chi^2\) estimates for \(p\) are omitted simply
+  because the results would be nearly identical to those for the maximum
+  likelihood estimate of \(p\) (since they are all \(\approx 0.575\).} I
+observe that \(P_E(i)\) is notably larger for \(p_{2}\) when
+\(i \in [6, 7]\), more closely matching \(P_O(i)\). \(p_{2}\) is also
+closer to \(P_O(i)\) for \(i \in [9, 10]\), although not for
+\(i \in [8, 11]\).
+
+\begin{longtable}[]{@{}rrrr@{}}
+\caption{The probabilities that a best-of-11 series lasts $i$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\toprule()
+Series lasts \(i\) rounds & \(p_0\) = 0.5 & \(p_2\) = 0.575 & \(P_O(i)\) \\
+\midrule()
+\endhead
+6 & 3.1\% & 4.2\% & 4.7\% \\
+7 & 9.4\% & 11.2\% & 11.9\% \\
+8 & 16.4\% & 17.8\% & 16.5\% \\
+9 & 21.9\% & 21.8\% & 21.7\% \\
+10 & 24.6\% & 23.0\% & 21.5\% \\
+11 & 24.6\% & 22.0\% & 23.7\% \\
+\bottomrule()
+\end{longtable}
+
+It is fair to conclude that the constant round win probability
+assumption can be valid in CoD SnD series with the appropriate choice of
+\(p\) (\(\approx 0.575\)).
+
+\hypertarget{sec:analysis-2}{%
+\subsection{Momentum}\label{sec:analysis-2}}
+
+Despite the implication that one can model team round win probability in
+CoD SnD as a constant, anecdotally many believe in momentum i.e.~streaks
+not due to random chance. I now evaluate win frequency in rounds
+following a streak of length \(k\). I account for the length of the
+series (\(i\) rounds), modeling the expected round win probability after
+a streak of length \(k\) as
+
+\begin{equation}\protect\hypertarget{eq:pki}{}{
+  \hat{P}(\text{win round | k-round winning streak, series lasting i rounds})=\{
+  \begin{array}{cl}
+    \frac{6 - k}{i - k}, & \text{team wins series} \\
+    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
+  \end{array}.
+}\label{eq:pki}\end{equation}
+
+Miller et al. (2018) provide evidence for negative recency suggesting
+that
+
+\begin{equation}\protect\hypertarget{eq:pkid}{}{
+  \begin{array}{rcl}
+  \hat{P}_{ki,\text{diff}} & = & \hat{P}(\text{win round | k-round winning streak, series lasting i rounds}) -  \\
+    & & \hat{P}(\text{lose round | k-round losing streak, series lasting i rounds}) \\
+    E[\hat{P}_{ki,\text{diff}}] & \neq & 0
+  \end{array}
+}\label{eq:pkid}\end{equation}
+
+given a deterministic i.i.d. Bernoulli probability
+\(\hat{p}(\text{win round | k-round winning streak, series lasting i rounds)}\)
+(Equation \ref{eq:pki}.\footnote{Note that these probabilites are
+  separate from those in Section \textbackslash ref\{sec:analysis-1\}.}
+
+Given that people typically perceive streaks as beginning after the
+third success (or failure) at minimum (Carlson and Shu 2007), I focus on
+round win percentages in rounds immediately following streaks of three
+wins, \(k = 3\).\footnote{Three happens to also be a reasonable number
+  for series that lasts at maximum 11 rounds.}
 
@@
 \begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-ayton2004}{}}%
+Ayton, Peter, and Ilan Fischer. 2004. {``The Hot Hand Fallacy and the
+Gambler{'}s Fallacy: Two Faces of Subjective Randomness?''} \emph{Memory
+\& Cognition} 32 (8): 13691378.
+
+\leavevmode\vadjust pre{\hypertarget{ref-carlson2007}{}}%
+Carlson, Kurt A., and Suzanne B. Shu. 2007. {``The Rule of Three: How
+the Third Event Signals the Emergence of a Streak.''}
+\emph{Organizational Behavior and Human Decision Processes} 104 (1):
+113121.
+
 \leavevmode\vadjust pre{\hypertarget{ref-chance2020}{}}%

### 2022-08-15 paper/paper.Rmd
rm little p
more prose

@@
 ```{r}
-#| label: cod_round_win_prop_after_x_wins
+#| label: cod_round_win_prop_after_k_wins
 ## http://keyonvafa.com/hot-hand/
@@
 
-summarize_cod_win_prop_after_x_wins <- function(k) {
+summarize_cod_win_prop_after_k_wins <- function(k) {
   probs_nx_k <- crossing(
@@
 
-cod_round_win_prop_after_x_wins <- tibble(win_streak = 2L:4L) |>
+cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:4L) |>
   mutate(
-    data = map(win_streak, summarize_cod_win_prop_after_x_wins)
+    data = map(win_streak, summarize_cod_win_prop_after_k_wins)
   ) |>
@@
 ```{r}
-#| label: cod_round_win_prop_after_x_wins-table
-cod_round_win_prop_after_x_wins |> 
+#| label: cod_round_win_prop_after_k_wins-table
+cod_round_win_prop_after_k_wins |> 
   mutate(
@@
 \begin{equation}\protect\hypertarget{eq:pki}{}{
-  \hat{P}(\text{win round | k-round winning streak, series lasting i rounds})=\{
+  \hat{P}_{wki} = \hat{P}(\text{win round | k-round winning streak, series lasting i rounds})=\{
   \begin{array}{cl}
@@
 ```
+$\hat{P}_{lki} = \hat{P}(\text{lose round | k-round losing streak, series lasting i rounds})$ can be formulated symmetrically.
+
 Miller et al. [-@miller2018] provide evidence for negative recency suggesting that
@@
 ```
-given a deterministic i.i.d. Bernoulli probability $\hat{p}(\text{win round | k-round winning streak, series lasting i rounds)}$ (Equation \ref{eq:pki}.[^13]
+given a deterministic i.i.d. Bernoulli probability (Equation \ref{eq:pki}.[^13]
 
-[^13]: Note that these probabilites are separate from those in Section \\ref{sec:analysis-1}.
+[^13]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins, $k = 3$.[^14]
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}_{wki}$ for $k = 3$ winning streaks, for both teams that empirically won and lost the series.
+(Some combinations of $i$ and $\text{team loses series}$ are irrelevant, such as the case when $i \in [7, 8, 9]$, so these combinations are excluded.)
 
 [^14]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
-
-```{r}
-#| label: cod_round_win_prop_after_x_wins_and_rounds
-summarize_cod_win_prop_after_x_wins_y_rounds <- function(k) {
-  probs_nx_k <- crossing(
-    n_rounds = 7L:11L,
-    round = 3L:11L
-  ) |> 
-    filter(round >= (k + 1L)) |> 
-    mutate(
-      prior_p = 6L / n_rounds,
-      expected_poststreak_p = map2_dbl(
-        n_rounds, prior_p, 
-        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
-      )
-    )
-
-  postprocess_round_streaks(
-    k = k,
-    probs_nx_k = probs_nx_k,
-    round
-  )
-}
-
-cod_round_win_prop_after_x_wins_y_rounds <- tibble(win_streak = 2L:4L) |>
-  mutate(
-    data = map(win_streak, summarize_cod_win_prop_after_x_wins_y_rounds)
-  ) |>
-  unnest(data)
-```
 

### 2022-08-15 paper/paper.Rmd
i -> r, new table

@@
 
-The general formula for the probability $P_E(i)$ that a best-of-$s$ series lasts $i$ rounds given constant probability $p$ of one team[^11] winning each round is
+The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^11] winning each round is
 
@@
 \begin{equation}\protect\hypertarget{eq-series-length}{}{
-P_E(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
+P_E(r) = \frac{(r - 1)!}{s_1!(r - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
 }\label{eq:series-length}\end{equation}
@@
   gt::cols_label(
-    n_rounds = 'Series lasts\ni rounds',
-    prop_expected = 'P_{E}(i)',
-    prop_actual = 'P_{O}(i)',
+    n_rounds = 'Series lasts\nr rounds',
+    prop_expected = 'P_{E}(r)',
+    prop_actual = 'P_{O}(r)',
     n_actual = 'N_O'
@@
 
-Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected probabilities for $s = 11$ under the naive assumption that $p_0 = 0.5$ for a given round, along with the observed proportions $P_O(i)$ in CoD SnD.
+Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected probabilities for $s = 11$ under the naive assumption that $p_0 = 0.5$ for a given round, along with the observed proportions $P_O(r)$ in CoD SnD.
 
@@
 \begin{longtable}{rrrr}
-\caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
-The observed frequencies observed are shown as a count $N_O(i)$ and as a proportion $P_O(i)$ of all series.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
+\caption{The probabilities that a best-of-11 series lasts $r$ rounds ($P_E(r)$, where $r \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
+The observed frequencies observed are shown as a count $N_O(r)$ and as a proportion $P_O(r)$ of all series.}\label{tbl:cod-prob-series-lasting-r-rounds} \\
 \toprule
@@
 \cmidrule(lr){3-4}
-Series lasts $i$ rounds & $P_E(i)$ & $P_O(i)$ & $N_O(i)$ \\ 
+Series lasts $r$ rounds & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
 \midrule
@@
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
-\chi^2 = \sum^{11}_{i=6} \frac{(P_O(i) - P_E(i))^2}{P_E(i)}, i \in R = [6, 7, 8, 9, 10, 11].
+\chi^2 = \sum^{11}_{i=6} \frac{(P_O(r) - P_E(r))^2}{P_E(r)}, r \in R = [6, 7, 8, 9, 10, 11].
 }\label{eq:chi-squ-test}\end{equation}
@@
     cod_streaks_naive_res$series |>
-      transmute(n_rounds, `$P_O(i)$` = scales::percent(prop_actual, accuracy = 0.1)),
+      transmute(n_rounds, `$P_O(r)$` = scales::percent(prop_actual, accuracy = 0.1)),
     by = 'n_rounds'
@@
   arrange(n_rounds) |>
-  rename(`Series lasts $i$ rounds` = n_rounds) |>
+  rename(`Series lasts $r$ rounds` = n_rounds) |>
   knitr::kable()
@@
 \toprule()
-Method & \(p\) & \(\chi^2\) (p-value) \\
+Method & \(p(r)\) & \(\chi^2\) (p-value) \\
 \midrule()
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(i)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^12] I observe that $P_E(i)$ is notably larger for $p_{2}$ when $i \in [6, 7]$, more closely matching $P_O(i)$.
-$p_{2}$ is also closer to $P_O(i)$ for $i \in [9, 10]$, although not for $i \in [8, 11]$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^12] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
+$p_{2}$ is also closer to $P_O(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
@@
 \begin{longtable}[]{@{}rrrr@{}}
-\caption{The probabilities that a best-of-11 series lasts $i$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\caption{The probabilities that a best-of-11 series lasts $r$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
-Series lasts \(i\) rounds & \(p_0\) = 0.5 & \(p_2\) = 0.575 & \(P_O(i)\) \\
+Series lasts \(r\) rounds & \(p_0(r)\) = 0.5 & \(p_2(r)\) = 0.575 & \(P_O(r)\) \\
 \midrule()
@@
   ) |>
-  # filter(win_streak == 3) |> 
-  select(
-    win_streak,
-    win_series,
+  filter(win_streak == 3) |> 
+  arrange(win_streak, n_rounds, win_series) |> 
+  transmute(
+    # win_streak,
     n_rounds,
+    across(win_series, ~ifelse(.x, 'win', 'lose')),
     total,
@@
   gt::cols_label(
-    win_streak = 'Streak',
+    # win_streak = 'Streak',
     win_series = 'Win Series?',
-    n_rounds = 'Series lasts $i$ rounds',
+    n_rounds = 'Series lasts r rounds',
     total = 'N',
-    prop = 'Obs.',
-    prior_p = 'Naive',
-    expected_poststreak_p = 'Discounted',
-    gt_p_value = 'Naive',
-    gt_p_value_adj = 'Discounted'
+    prop = 'O',
+    prior_p = 'a',
+    expected_poststreak_p = 'b',
+    gt_p_value = 'a',
+    gt_p_value_adj = 'b'
   ) |> 
   gt::tab_spanner(
-    label = '%s',
+    label = 'x',
     columns = c(prop, prior_p, expected_poststreak_p)
@@
   gt::tab_spanner(
-    label = 'Binom. > p-value',
+    label = 'y',
     columns = c(gt_p_value, gt_p_value_adj)
-  )
+  ) |> 
+  gt::tab_footnote(
+    footnote = 'Binom',
+    locations = gt::cells_column_labels(columns = c(gt_p_value))
+  ) |> 
+  gt::as_latex()
 ```
@@
 I now evaluate win frequency in rounds following a streak of length $k$.
-I account for the length of the series ($i$ rounds), modeling the expected round win probability after a streak of length $k$ as
+I account for the length of the series ($r$ rounds), modeling the expected round win probability after a streak of length $k$ as
 
 ```{=tex}
-\begin{equation}\protect\hypertarget{eq:pki}{}{
-  \hat{P}_{wki} = \hat{P}(\text{win round | k-round winning streak, series lasting i rounds})=\{
+\begin{equation}\protect\hypertarget{eq:pwkr}{}{
+  \hat{p}^{kr,\text{win}}_E = \hat{p}(\text{win round | k-round winning streak, series lasting r rounds})=\{
     \begin{array}{cl}
@@
     \end{array}.
-}\label{eq:pki}\end{equation}
+  }\label{eq:pwkr}
+\end{equation}
 ```
-$\hat{P}_{lki} = \hat{P}(\text{lose round | k-round losing streak, series lasting i rounds})$ can be formulated symmetrically.
+$\hat{p}^{kr,loss}_E = \hat{p}(\text{lose round | k-round losing streak, series lasting r rounds})$ can be formulated symmetrically.
 
-Miller et al. [-@miller2018] provide evidence for negative recency suggesting that
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:pkid}{}{
-  \begin{array}{rcl}
-  \hat{P}_{ki,\text{diff}} & = & \hat{P}(\text{win round | k-round winning streak, series lasting i rounds}) -  \\
-    & & \hat{P}(\text{lose round | k-round losing streak, series lasting i rounds}) \\
-    E[\hat{P}_{ki,\text{diff}}] & \neq & 0
-  \end{array}
-}\label{eq:pkid}\end{equation}
-```
-given a deterministic i.i.d. Bernoulli probability (Equation \ref{eq:pki}.[^13]
+While one might think that $E[\hat{p}^{kr,\text{win}} - \hat{p}^{kr,\text{loss}}] = 0$, Miller et al.
+[-@miller2018] suggest that, given a deterministic i.i.d.
+Bernoulli probability (Equation \ref{pwkr}, this is not true due to streak-selection bias.[^13][^14]
 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}_{wki}$ for $k = 3$ winning streaks, for both teams that empirically won and lost the series.
-(Some combinations of $i$ and $\text{team loses series}$ are irrelevant, such as the case when $i \in [7, 8, 9]$, so these combinations are excluded.)
-
 [^14]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
 
+I don't attempt to measure this expectation like Miller et al.
+[-@miller2018], who perform their analysis longitudinally per study participant; nonetheless, I apply their formulation for applying the "downward bias" on post-streak success to come up with estimates $\hat{P}_{kr,\text{win}}^{\text{adj.}}$, specifying $r$ as the number of trials.
+
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^15] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}_{kr,\text{win}}$ for $k = 3$ winning streaks, for both teams that empirically won and lost the series.
+(Some combinations of $r$ and $\text{team loses series}$ are irrelevant, such as the case when $r \in [7, 8, 9]$, so these combinations are excluded.)
+
+[^15]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+
+```{=tex}
+\begin{longtable}{rrrrrrrr}
+\toprule
+&  &  & \multicolumn{3}{c}{$\hat{p}^{kr,\text{win}}$} & \multicolumn{2}{c}{$p$-value} \\
+\cmidrule(lr){4-6} \cmidrule(lr){7-8}
+Series lasts $r$ rounds & Win Series? & $N^{kr,\text{win}}_O$ & $O$ & $E$ & $\text{adj.}$ & $E$ & $\text{adj.}$ \\ 
+\midrule
+7 & win & 209 & $75\%$ & $75\%$ & $61\%$ & 0.58 & <=0.01 \\ 
+8 & win & 209 & $62\%$ & $60\%$ & $45\%$ & 0.28 & <=0.01 \\ 
+9 & win & 193 & $52\%$ & $50\%$ & $35\%$ & 0.33 & <=0.01 \\ 
+10 & lose & 60 & $13\%$ & $14\%$ & $10\%$ & 0.64 & 0.26 \\ 
+10 & win & 151 & $44\%$ & $43\%$ & $29\%$ & 0.45 & <=0.01 \\ 
+11 & lose & 129 & $24\%$ & $25\%$ & $16\%$ & 0.63 & <=0.01 \\ 
+11 & win & 150 & $40\%$ & $38\%$ & $25\%$ & 0.29 & <=0.01 \\ 
+\bottomrule
+\end{longtable}
+```
 # References {.unnumbered}

### 2022-08-15 paper/paper.tex
i -> r, new table

@@
 
-The general formula for the probability \(P_E(i)\) that a best-of-\(s\)
-series lasts \(i\) rounds given constant probability \(p\) of one
+The general formula for the probability \(P_E(r)\) that a best-of-\(s\)
+series lasts \(r\) rounds given constant probability \(p\) of one
 team\footnote{If \(p > 0.5\), then I might say that this team is the
@@
 \begin{equation}\protect\hypertarget{eq-series-length}{}{
-P_E(i) = \frac{(i - 1)!}{s_1!(i - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
+P_E(r) = \frac{(r - 1)!}{s_1!(r - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
 }\label{eq:series-length}\end{equation}
 
-Table \ref{tbl:cod-prob-series-lasting-i-rounds} shows the expected
+Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected
 probabilities for \(s = 11\) under the naive assumption that
 \(p_0 = 0.5\) for a given round, along with the observed proportions
-\(P_O(i)\) in CoD SnD.
+\(P_O(r)\) in CoD SnD.
 
 \begin{longtable}{rrrr}
-\caption{The probabilities that a best-of-11 series lasts $i$ rounds ($P_E(i)$, where $i \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
-The observed frequencies observed are shown as a count $N_O(i)$ and as a proportion $P_O(i)$ of all series.}\label{tbl:cod-prob-series-lasting-i-rounds} \\
+\caption{The probabilities that a best-of-11 series lasts $r$ rounds ($P_E(r)$, where $r \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
+The observed frequencies observed are shown as a count $N_O(r)$ and as a proportion $P_O(r)$ of all series.}\label{tbl:cod-prob-series-lasting-r-rounds} \\
 \toprule
@@
 Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
-\(P_E(i)\) when re-applying Equation \ref{eq:series-length} for the
+\(P_E(r)\) when re-applying Equation \ref{eq:series-length} for the
 maximum likelihood estimate \(p_2 = 0.575\).\footnote{The method of
@@
   likelihood estimate of \(p\) (since they are all \(\approx 0.575\).} I
-observe that \(P_E(i)\) is notably larger for \(p_{2}\) when
-\(i \in [6, 7]\), more closely matching \(P_O(i)\). \(p_{2}\) is also
-closer to \(P_O(i)\) for \(i \in [9, 10]\), although not for
-\(i \in [8, 11]\).
+observe that \(P_E(r)\) is notably larger for \(p_{2}\) when
+\(r \in [6, 7]\), more closely matching \(P_O(r)\). \(p_{2}\) is also
+closer to \(P_O(r)\) for \(r \in [9, 10]\), although not for
+\(r \in [8, 11]\).
 
 \begin{longtable}[]{@{}rrrr@{}}
-\caption{The probabilities that a best-of-11 series lasts $i$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\caption{The probabilities that a best-of-11 series lasts $r$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
-Series lasts \(i\) rounds & \(p_0\) = 0.5 & \(p_2\) = 0.575 & \(P_O(i)\) \\
+Series lasts \(r\) rounds & \(p_0(r)\) = 0.5 & \(p_2(r)\) = 0.575 & \(P_O(r)\) \\
 \midrule()
@@
 following a streak of length \(k\). I account for the length of the
-series (\(i\) rounds), modeling the expected round win probability after
+series (\(r\) rounds), modeling the expected round win probability after
 a streak of length \(k\) as
 
-\begin{equation}\protect\hypertarget{eq:pki}{}{
-  \hat{P}(\text{win round | k-round winning streak, series lasting i rounds})=\{
+\begin{equation}\protect\hypertarget{eq:pwkr}{}{
+  \hat{p}^{kr,\text{win}} = \hat{p}(\text{win round | k-round winning streak, series lasting r rounds})=\{
     \begin{array}{cl}
@@
     \end{array}.
-}\label{eq:pki}\end{equation}
+  }\label{eq:pwkr}
+\end{equation}
+
+\(\hat{p}^{kr,loss} = \hat{p}(\text{lose round | k-round losing streak, series lasting r rounds})\)
+can be formulated symmetrically.
 
 Miller et al. (2018) provide evidence for negative recency suggesting
-that
+that, given a deterministic i.i.d. Bernoulli probability (Equation
+\ref{eq:pki},
 
-\begin{equation}\protect\hypertarget{eq:pkid}{}{
-  \begin{array}{rcl}
-  \hat{P}_{ki,\text{diff}} & = & \hat{P}(\text{win round | k-round winning streak, series lasting i rounds}) -  \\
-    & & \hat{P}(\text{lose round | k-round losing streak, series lasting i rounds}) \\
-    E[\hat{P}_{ki,\text{diff}}] & \neq & 0
-  \end{array}
-}\label{eq:pkid}\end{equation}
+\begin{equation}\protect\hypertarget{eq:pkrd}{}{
+E[\hat{P}^{kr,\text{win}} - \hat{P}^{kr,\text{loss}}] = 0
+}\label{eq:pkrd}\end{equation}
 
-given a deterministic i.i.d. Bernoulli probability
-\(\hat{p}(\text{win round | k-round winning streak, series lasting i rounds)}\)
-(Equation \ref{eq:pki}.\footnote{Note that these probabilites are
-  separate from those in Section \textbackslash ref\{sec:analysis-1\}.}
+is not true due to streak-selection bias.\footnote{Note that these
+  probabilities are separate from those in Section \ref{sec:analysis-1}.}
+I don't attempt to measure this expectation like Miller et al. (2018),
+who perform their analysis longitudinally per study participant;
+nonetheless, I apply their formulation for applying the ``downward
+bias'' on post-streak success to come up with estimates
+\(\hat{P}_{kr,\text{win}}^{\text{adj.}}\), specifying \(r\) as the
+number of trials.
 
@@
 round win percentages in rounds immediately following streaks of three
-wins, \(k = 3\).\footnote{Three happens to also be a reasonable number
-  for series that lasts at maximum 11 rounds.}
+wins.\footnote{Three happens to also be a reasonable number for series
+  that lasts at maximum 11 rounds.} Table
+\ref{tbl:cod-round-win-prop-after-k-wins} shows
+\(\hat{P}_{kr,\text{win}}\) for \(k = 3\) winning streaks, for both
+teams that empirically won and lost the series. (Some combinations of
+\(r\) and \(\text{team loses series}\) are irrelevant, such as the case
+when \(r \in [7, 8, 9]\), so these combinations are excluded.)
+
+\begin{longtable}{rrrrrrrr}
+\toprule
+&  &  & \multicolumn{3}{c}{$\hat{p}^{kr,\text{win}}$} & \multicolumn{2}{c}{$p$-value} \\
+\cmidrule(lr){4-6} \cmidrule(lr){7-8}
+Series lasts $r$ rounds & Win Series? & $N^{kr,\text{win}}_O$ & $O$ & $E$ & $\text{adj.}$ & $E$ & $\text{adj.}$ \\ 
+\midrule
+7 & win & 209 & $75\%$ & $75\%$ & $61\%$ & 0.58 & <=0.01 \\ 
+8 & win & 209 & $62\%$ & $60\%$ & $45\%$ & 0.28 & <=0.01 \\ 
+9 & win & 193 & $52\%$ & $50\%$ & $35\%$ & 0.33 & <=0.01 \\ 
+10 & lose & 60 & $13\%$ & $14\%$ & $10\%$ & 0.64 & 0.26 \\ 
+10 & win & 151 & $44\%$ & $43\%$ & $29\%$ & 0.45 & <=0.01 \\ 
+11 & lose & 129 & $24\%$ & $25\%$ & $16\%$ & 0.63 & <=0.01 \\ 
+11 & win & 150 & $40\%$ & $38\%$ & $25\%$ & 0.29 & <=0.01 \\ 
+\bottomrule
+\end{longtable}
 

### 2022-08-16 paper/paper.Rmd
some re-writing

@@
 Chance [-@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
-Chance finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[^8] Chance's work is closely related to mine, and, in fact, provides a guide for the first part of my investigation.
+Chance finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[\^8] [\^8]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
 
-[^8]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
-
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^9] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^8] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^9]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^8]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 [-@gilovich1985] do not find evidence for the hot hand phenomenon.
-Recently, Miller et al.
-[-@miller2018] refuted the conclusions of Gilovich et al.
-, finding mathematical evidence that seems to support negative recency.
-Specifically, they find that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" (streak selection bias) that imply that, under i.i.d.
+However, Miller and Sanjurjo [-@miller2018] refuted the conclusions of Gilovich et al., proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy.
+Specifically, Miller and Sanjurjo say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
 conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success".
-I agree with Miller's findings, accounting for the streak selection bias in my study of momentum.
+When applying streak selection bias to Giloveih et al.'s data, Miller and Sanjurjo come to the opposite conclusions as Giloveih et al.
 
@@
 Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^10]
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^9]
 
-[^10]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+[^9]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
 
-# Methodology, results, and discussion
+# Methodology and results
 
 First, I investigate the constant probability assumption and the distribution of rounds played in a series.
-Afterwards, I investigate momentum, building on my learnings from the constant probability assumption analysis.
+Chance's [-@chance2020] work is closely related to mine, and, in fact, provides a guide for this investigation.
+
+Afterwards, I investigate post-streak win rates, building on my learnings from the constant probability assumption analysis.
+I agree with Miller and Sanjurjo's [-@miller2018] framework for streak selection bias, accounting for it in when analyzing momentum.
 
@@
 
-The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^11] winning each round is
+The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^10] winning each round is
 
-[^11]: If $p > 0.5$, then I might say that this team is the better team (known omnisciently).
+[^10]: If $p > 0.5$, then I might say that this team is the better team (known omnisciently).
 
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^12] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^11] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
 $p_{2}$ is also closer to $P_O(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^12]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$.
+[^11]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$.
 
@@
 
-While one might think that $E[\hat{p}^{kr,\text{win}} - \hat{p}^{kr,\text{loss}}] = 0$, Miller et al.
-[-@miller2018] suggest that, given a deterministic i.i.d.
-Bernoulli probability (Equation \ref{pwkr}, this is not true due to streak-selection bias.[^13][^14]
+While one might think that $E[\hat{p}^{kr,\text{win}} - \hat{p}^{kr,\text{loss}}] = 0$, Miller and Sanjurjo [-@miller2018] suggest that, given a deterministic i.i.d.
+Bernoulli probability (Equation \ref{pwkr}, this is not true due to streak-selection bias.[^12][^13]
 
-[^13]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.
+[^12]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.
+
+[^13]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+
+I apply their formulation for "downward bias" to post-streak success to come up with estimates $\hat{P}_{kr,\text{win}}^{\text{adj.}}$, specifying $r$ as the number of trials.
+
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}_{kr,\text{win}}$ for $k = 3$ winning streaks, for both teams that empirically won and lost the series.
+(Some combinations of $r$ and $\text{team loses series}$ are irrelevant, such as the case when $r \in [7, 8, 9]$, so these combinations are excluded.)
 
 [^14]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
-
-I don't attempt to measure this expectation like Miller et al.
-[-@miller2018], who perform their analysis longitudinally per study participant; nonetheless, I apply their formulation for applying the "downward bias" on post-streak success to come up with estimates $\hat{P}_{kr,\text{win}}^{\text{adj.}}$, specifying $r$ as the number of trials.
-
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^15] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}_{kr,\text{win}}$ for $k = 3$ winning streaks, for both teams that empirically won and lost the series.
-(Some combinations of $r$ and $\text{team loses series}$ are irrelevant, such as the case when $r \in [7, 8, 9]$, so these combinations are excluded.)
-
-[^15]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
 
@@
 :::
+
+# Appendix {.unnumbered}

### 2022-08-16 research/jqas_headers.R
jqas headers

@@ -1,0 +1,51 @@
+library(rvest)
+library(tidyverse)
+main_url <- 'https://www.degruyter.com/journal/key/jqas/html?lang=en'
+main_page <- main_url |> read_html()
+nodes <- main_page |> 
+  html_elements('.metadataInfoFont > p > a')
+info <- tibble(
+  name = nodes |> html_text2(),
+  href = nodes |> html_attr('href')
+)
+
+parse_jqas_html_paper_headers <- function(href) {
+  page <- href |> read_html()
+  list(
+    'h2' = page |> html_elements('h2.subheading') |> html_text2(),
+    'h3' = page |> html_elements('h3.subheading') |> html_text2()
+  ) |> 
+    enframe('level', 'title') |> 
+    unnest(title)
+}
+
+possibly_parse_jqas_html_paper_headers <- possibly(
+  parse_jqas_html_paper_headers,
+  otherwise = tibble(),
+  quiet = FALSE
+)
+
+headers <- info |> 
+  mutate(
+    headers = map(href, possibly_parse_jqas_html_paper_headers)
+  )
+
+headers <- headers |> 
+  unnest(headers) |> 
+  mutate(
+    index = title |> str_replace_all('(^[0-9.]+)\\s+(.*$)', '\\1'),
+    h2 = index |> str_remove('[.].*$'),
+    h3 = index |> str_remove('^[0-9+][.]'),
+    across(h3, ~ifelse(index == h2, NA_character_, .x)),
+    across(c(h2, h3), as.integer),
+    title = title |> str_replace_all('(^[0-9.]+)\\s+(.*$)', '\\2')
+  )
+write_csv(headers, 'research/jqas_headers.csv', na = '')
+
+headers |> 
+  count(title, sort = TRUE)
+headers |> 
+  count(h2, title, sort = TRUE)
+headers |> 
+  drop_na(h3) |> 
+  count(h3, title, sort = TRUE)

### 2022-08-16 paper/paper.Rmd
tables 5 and 6, capital Ps

@@
 [-@gilovich1985] do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo [-@miller2018] refuted the conclusions of Gilovich et al., proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy.
+However, Miller and Sanjurjo [-@miller2018] refuted the conclusions of Gilovich et al., proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^9].
 Specifically, Miller and Sanjurjo say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
@@
 
+[^9]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
+provides a novel structural candidate explanationfor the persistence of gambler's fallacy beliefs", per Miller and Sanjurjo [-@miller2018].
+
 Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily in esports.
 Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^9]
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^10]
 
-[^9]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+[^10]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
 
@@
 
-The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^10] winning each round is
+The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^11] winning each round is
 
-[^10]: If $p > 0.5$, then I might say that this team is the better team (known omnisciently).
+[^11]: If $p > 0.5$, then one might say that this team is the better team (known in hindsight).
 
@@
   gt::cols_label(
-    n_rounds = 'Series lasts\nr rounds',
+    n_rounds = 'r',
     prop_expected = 'P_{E}(r)',
@@
 \cmidrule(lr){3-4}
-Series lasts $r$ rounds & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
+$r$ & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
 \midrule
@@
   arrange(n_rounds) |>
-  rename(`Series lasts $r$ rounds` = n_rounds) |>
+  rename(`$r$` = n_rounds) |>
   knitr::kable()
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^11] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^12] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
 $p_{2}$ is also closer to $P_O(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^11]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$.
+[^12]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$).
 
@@
 \toprule()
-Series lasts \(r\) rounds & \(p_0(r)\) = 0.5 & \(p_2(r)\) = 0.575 & \(P_O(r)\) \\
+$r$ & $p_0(r)$ = 0.5 & $p_2(r)$ = 0.575 & $P_O(r)$ \\
 \midrule()
@@
   ) |>
-  filter(win_streak == 3) |> 
+  filter(win_streak == 3, !win_series) |> 
   arrange(win_streak, n_rounds, win_series) |> 
@@
     n_rounds,
-    across(win_series, ~ifelse(.x, 'win', 'lose')),
+    # across(win_series, ~ifelse(.x, 'win', 'lose')),
     total,
@@
     # win_streak = 'Streak',
-    win_series = 'Win Series?',
-    n_rounds = 'Series lasts r rounds',
+    n_rounds = 'r',
     total = 'N',
@@
     expected_poststreak_p = 'b',
-    gt_p_value = 'a',
-    gt_p_value_adj = 'b'
+    gt_p_value = 'c',
+    gt_p_value_adj = 'd'
   ) |> 
@@
     label = 'x',
-    columns = c(prop, prior_p, expected_poststreak_p)
+    columns = c(prior_p, gt_p_value)
   ) |> 
@@
     label = 'y',
-    columns = c(gt_p_value, gt_p_value_adj)
-  ) |> 
-  gt::tab_footnote(
-    footnote = 'Binom',
-    locations = gt::cells_column_labels(columns = c(gt_p_value))
+    columns = c(expected_poststreak_p, gt_p_value_adj)
   ) |> 
@@
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-  \hat{p}^{kr,\text{win}}_E = \hat{p}(\text{win round | k-round winning streak, series lasting r rounds})=\{
+  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}(\text{win round | k-round winning streak, series lasting r rounds})=\{
     \begin{array}{cl}
@@
 ```
-$\hat{p}^{kr,loss}_E = \hat{p}(\text{lose round | k-round losing streak, series lasting r rounds})$ can be formulated symmetrically.
+$\hat{P}^{kr,loss}_{E,\text{unadj.}} = \hat{P}(\text{lose round | k-round losing streak, series lasting r rounds})$ can be formulated symmetrically.
 
-While one might think that $E[\hat{p}^{kr,\text{win}} - \hat{p}^{kr,\text{loss}}] = 0$, Miller and Sanjurjo [-@miller2018] suggest that, given a deterministic i.i.d.
-Bernoulli probability (Equation \ref{pwkr}, this is not true due to streak-selection bias.[^12][^13]
+While one might think that $E[\hat{P}^{kr,\text{win}} - \hat{P}^{kr,\text{loss}}] = 0$, Miller and Sanjurjo [-@miller2018] suggest that, given a deterministic i.i.d.
+Bernoulli probability (Equation \ref{eq:pwkr}, this is not true due to streak-selection bias.[^13] As proved by Miller and Sanjurjo, TODO: Combine these two sentences
 
-[^12]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.
+[^13]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.
 
-[^13]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < p < 1$*.
+Let* $\hat{P}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
+\hat{P}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
+In particular,* $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.$
 
-I apply their formulation for "downward bias" to post-streak success to come up with estimates $\hat{P}_{kr,\text{win}}^{\text{adj.}}$, specifying $r$ as the number of trials.
+TODO: Descripe the Appendix E.1.
+I apply their formulation for "downward bias" to post-streak success to come up with estimates $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$, specifying $r$ as the number of trials.
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}_{kr,\text{win}}$ for $k = 3$ winning streaks, for both teams that empirically won and lost the series.
-(Some combinations of $r$ and $\text{team loses series}$ are irrelevant, such as the case when $r \in [7, 8, 9]$, so these combinations are excluded.)
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} and table \ref{tbl:cod-round-loss-prop-after-k-losses} shows $\hat{P}^{kr,\text{win}}_O$ and $\hat{P}^{kr,\text{loss}}_O$ for $k = 3$ streaks respectively.
 
@@
 
+TODO: Put p-value in parentheses
+
 ```{=tex}
-\begin{longtable}{rrrrrrrr}
+\begin{longtable}{rrrrrrr}
+\caption{Observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round-win streak, for a series lasting $r$ rounds.}\label{tbl:cod-round-win-prop-after-k-wins} \\
 \toprule
-&  &  & \multicolumn{3}{c}{$\hat{p}^{kr,\text{win}}$} & \multicolumn{2}{c}{$p$-value} \\
-\cmidrule(lr){4-6} \cmidrule(lr){7-8}
-Series lasts $r$ rounds & Win Series? & $N^{kr,\text{win}}_O$ & $O$ & $E$ & $\text{adj.}$ & $E$ & $\text{adj.}$ \\ 
+ &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
+\cmidrule(lr){4-5} \cmidrule(lr){6-7}
+$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ & $p$-value \\ 
 \midrule
-7 & win & 209 & $75\%$ & $75\%$ & $61\%$ & 0.58 & <=0.01 \\ 
-8 & win & 209 & $62\%$ & $60\%$ & $45\%$ & 0.28 & <=0.01 \\ 
-9 & win & 193 & $52\%$ & $50\%$ & $35\%$ & 0.33 & <=0.01 \\ 
-10 & lose & 60 & $13\%$ & $14\%$ & $10\%$ & 0.64 & 0.26 \\ 
-10 & win & 151 & $44\%$ & $43\%$ & $29\%$ & 0.45 & <=0.01 \\ 
-11 & lose & 129 & $24\%$ & $25\%$ & $16\%$ & 0.63 & <=0.01 \\ 
-11 & win & 150 & $40\%$ & $38\%$ & $25\%$ & 0.29 & <=0.01 \\ 
+7 & 209 & $75\%$ & $75\%$ & 0.58 & $61\%$ & <=0.01 \\ 
+8 & 209 & $62\%$ & $60\%$ & 0.28 & $45\%$ & <=0.01 \\ 
+9 & 193 & $52\%$ & $50\%$ & 0.33 & $35\%$ & <=0.01 \\ 
+10 & 151 & $44\%$ & $43\%$ & 0.45 & $29\%$ & <=0.01 \\ 
+11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
+\bottomrule
+\end{longtable}
+```
+```{=tex}
+\begin{longtable}{rrrrrrr}
+\caption{Observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round-loss streak, for a series lasting $r$ rounds.
+$r \in [7, 8, 9]$ are invalid.}\label{tbl:cod-round-loss-prop-after-k-losses} \\
+\toprule
+ &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
+\cmidrule(lr){4-5} \cmidrule(lr){6-7}
+$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ & $p$-value \\ 
+\midrule
+10 & 60 & $13\%$ & $14\%$ & 0.64 & $10\%$ & 0.26 \\ 
+11 & 129 & $24\%$ & $25\%$ & 0.63 & $16\%$ & <=0.01 \\ 
 \bottomrule

### 2022-08-16 paper/paper.tex
tables 5 and 6, capital Ps

@@
 hypothesis of \(p = 0.5\) in the MLB and NHL championship series when
-applying Mosteller's first and second methods.\footnote{Chance goes on
-  to outline a conditional probability framework (likelihood of winning
-  a game given the series state) which can exactly explain the
-  distribution of the number of games played.} Chance's work is closely
-related to mine, and, in fact, provides a guide for the first part of my
-investigation.
+applying Mosteller's first and second methods.{[}\^{}8{]} {[}\^{}8{]}:
+Chance goes on to outline a conditional probability framework
+(likelihood of winning a game given the series state) which can exactly
+explain the distribution of the number of games played.
 
@@
 observational and controlled settings. Gilovich et al. (1985) do not
-find evidence for the hot hand phenomenon. Recently, Miller et al.
-(2018) refuted the conclusions of Gilovich et al.~, finding mathematical
-evidence that seems to support negative recency. Specifically, they find
+find evidence for the hot hand phenomenon. However, Miller and Sanjurjo
+(2018) refuted the conclusions of Gilovich et al., proving a framework
+for quantifying streak selection bias, which effectively works in the
+manner posited by the gambler's fallacy\footnote{Streak selection bias,
+  ``in conjunction with a quasi-Bayesian model of decision making under
+  sample size neglect\ldots{} provides a novel structural candidate
+  explanationfor the persistence of gambler's fallacy beliefs'', per
+  Miller and Sanjurjo (2018).}. Specifically, Miller and Sanjurjo say
 that a ``bias exists in a common measure of the conditional dependence
 of present outcomes on streaks of past outcomes in sequential data''
-(streak selection bias) that imply that, under i.i.d. conditions, ``the
-proportion of successes among the outcomes that immediately follow a
-streak of consecutive successes is expected to be strictly less than the
-underlying (conditional) probability of success''. I agree with Miller's
-findings, accounting for the streak selection bias in my study of
-momentum.
+implying that, under i.i.d. conditions, ``the proportion of successes
+among the outcomes that immediately follow a streak of consecutive
+successes is expected to be strictly less than the underlying
+(conditional) probability of success''. When applying streak selection
+bias to Giloveih et al.'s data, Miller and Sanjurjo come to the opposite
+conclusions as Giloveih et al.
 
@@
 
-\hypertarget{methodology-results-and-discussion}{%
-\section{Methodology, results, and
-discussion}\label{methodology-results-and-discussion}}
+\hypertarget{methodology-and-results}{%
+\section{Methodology and results}\label{methodology-and-results}}
 
 First, I investigate the constant probability assumption and the
-distribution of rounds played in a series. Afterwards, I investigate
-momentum, building on my learnings from the constant probability
-assumption analysis.
+distribution of rounds played in a series. Chance's (2020) work is
+closely related to mine, and, in fact, provides a guide for this
+investigation.
+
+Afterwards, I investigate post-streak win rates, building on my
+learnings from the constant probability assumption analysis. I agree
+with Miller and Sanjurjo's (2018) framework for streak selection bias,
+accounting for it in when analyzing momentum.
 
@@
 series lasts \(r\) rounds given constant probability \(p\) of one
-team\footnote{If \(p > 0.5\), then I might say that this team is the
-  better team (known omnisciently).} winning each round is
+team\footnote{If \(p > 0.5\), then one might say that this team is the
+  better team (known in hindsight).} winning each round is
 
@@
   because the results would be nearly identical to those for the maximum
-  likelihood estimate of \(p\) (since they are all \(\approx 0.575\).} I
-observe that \(P_E(r)\) is notably larger for \(p_{2}\) when
+  likelihood estimate of \(p\) (since they are all \(\approx 0.575\)).}
+I observe that \(P_E(r)\) is notably larger for \(p_{2}\) when
 \(r \in [6, 7]\), more closely matching \(P_O(r)\). \(p_{2}\) is also
@@
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-  \hat{p}^{kr,\text{win}} = \hat{p}(\text{win round | k-round winning streak, series lasting r rounds})=\{
+  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}(\text{win round | k-round winning streak, series lasting r rounds})=\{
     \begin{array}{cl}
@@
 
-\(\hat{p}^{kr,loss} = \hat{p}(\text{lose round | k-round losing streak, series lasting r rounds})\)
+\(\hat{P}^{kr,loss}_{E,\text{unadj.}} = \hat{P}(\text{lose round | k-round losing streak, series lasting r rounds})\)
 can be formulated symmetrically.
 
-Miller et al. (2018) provide evidence for negative recency suggesting
-that, given a deterministic i.i.d. Bernoulli probability (Equation
-\ref{eq:pki},
+While one might think that
+\(E[\hat{P}^{kr,\text{win}} - \hat{P}^{kr,\text{loss}}] = 0\), Miller
+and Sanjurjo (2018) suggest that, given a deterministic i.i.d. Bernoulli
+probability (Equation \ref{eq:pwkr}, this is not true due to
+streak-selection bias.\footnote{Note that these probabilities are
+  separate from those in Section \ref{sec:analysis-1}.} As proved by
+Miller and Sanjurjo, TODO: Combine these two sentences
 
-\begin{equation}\protect\hypertarget{eq:pkrd}{}{
-E[\hat{P}^{kr,\text{win}} - \hat{P}^{kr,\text{loss}}] = 0
-}\label{eq:pkrd}\end{equation}
+\begin{quote}
+Theorem 1: \emph{Let}
+\(\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3\)\emph{, be a sequence of
+independent Bernoulli trials, each with probability of success}
+\(0 < p < 1\)\emph{. Let} \(\hat{P}_k(\mathbf{X})\) \emph{be the
+proportion of successes on the subset of trials} \(I_k(\mathbf{X})\)
+\emph{that immediately follow} \(k\) consecutive successes, that is,
+\(\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |. \hat{P}_k\)
+\emph{is a biased estimate of}
+\(\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p\) \emph{for
+all} \(k\) \emph{such that} \(1 \leq k \leq n - 2\)\emph{. In
+particular,}
+\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.\)
+\end{quote}
 
-is not true due to streak-selection bias.\footnote{Note that these
-  probabilities are separate from those in Section \ref{sec:analysis-1}.}
-I don't attempt to measure this expectation like Miller et al. (2018),
-who perform their analysis longitudinally per study participant;
-nonetheless, I apply their formulation for applying the ``downward
-bias'' on post-streak success to come up with estimates
-\(\hat{P}_{kr,\text{win}}^{\text{adj.}}\), specifying \(r\) as the
+TODO: Descripe the Appendix E.1. I apply their formulation for
+``downward bias'' to post-streak success to come up with estimates
+\(\hat{P}^{kr,\text{win}}_{E,\text{adj.}}\), specifying \(r\) as the
 number of trials.
@@
   that lasts at maximum 11 rounds.} Table
-\ref{tbl:cod-round-win-prop-after-k-wins} shows
-\(\hat{P}_{kr,\text{win}}\) for \(k = 3\) winning streaks, for both
-teams that empirically won and lost the series. (Some combinations of
-\(r\) and \(\text{team loses series}\) are irrelevant, such as the case
-when \(r \in [7, 8, 9]\), so these combinations are excluded.)
+\ref{tbl:cod-round-win-prop-after-k-wins} and table
+\ref{tbl:cod-round-loss-prop-after-k-losses} shows
+\(\hat{P}^{kr,\text{win}}_O\) and \(\hat{P}^{kr,\text{loss}}_O\) for
+\(k = 3\) streaks respectively.
 
-\begin{longtable}{rrrrrrrr}
+TODO: Put p-value in parentheses
+
+\begin{longtable}{rrrrrrr}
+\caption{Observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round-win streak, for a series lasting $r$ rounds.}\label{tbl:cod-round-win-prop-after-k-wins} \\
 \toprule
-&  &  & \multicolumn{3}{c}{$\hat{p}^{kr,\text{win}}$} & \multicolumn{2}{c}{$p$-value} \\
-\cmidrule(lr){4-6} \cmidrule(lr){7-8}
-Series lasts $r$ rounds & Win Series? & $N^{kr,\text{win}}_O$ & $O$ & $E$ & $\text{adj.}$ & $E$ & $\text{adj.}$ \\ 
+ &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
+\cmidrule(lr){4-5} \cmidrule(lr){6-7}
+$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ & $p$-value \\ 
 \midrule
-7 & win & 209 & $75\%$ & $75\%$ & $61\%$ & 0.58 & <=0.01 \\ 
-8 & win & 209 & $62\%$ & $60\%$ & $45\%$ & 0.28 & <=0.01 \\ 
-9 & win & 193 & $52\%$ & $50\%$ & $35\%$ & 0.33 & <=0.01 \\ 
-10 & lose & 60 & $13\%$ & $14\%$ & $10\%$ & 0.64 & 0.26 \\ 
-10 & win & 151 & $44\%$ & $43\%$ & $29\%$ & 0.45 & <=0.01 \\ 
-11 & lose & 129 & $24\%$ & $25\%$ & $16\%$ & 0.63 & <=0.01 \\ 
-11 & win & 150 & $40\%$ & $38\%$ & $25\%$ & 0.29 & <=0.01 \\ 
+7 & 209 & $75\%$ & $75\%$ & 0.58 & $61\%$ & <=0.01 \\ 
+8 & 209 & $62\%$ & $60\%$ & 0.28 & $45\%$ & <=0.01 \\ 
+9 & 193 & $52\%$ & $50\%$ & 0.33 & $35\%$ & <=0.01 \\ 
+10 & 151 & $44\%$ & $43\%$ & 0.45 & $29\%$ & <=0.01 \\ 
+11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
+\bottomrule
+\end{longtable}
+
+\begin{longtable}{rrrrrrr}
+\caption{Observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round-loss streak, for a series lasting $r$ rounds.
+$r \in [7, 8, 9]$ are invalid.}\label{tbl:cod-round-loss-prop-after-k-losses} \\
+\toprule
+ &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
+\cmidrule(lr){4-5} \cmidrule(lr){6-7}
+$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ & $p$-value \\ 
+\midrule
+10 & 60 & $13\%$ & $14\%$ & 0.64 & $10\%$ & 0.26 \\ 
+11 & 129 & $24\%$ & $25\%$ & 0.63 & $16\%$ & <=0.01 \\ 
 \bottomrule
@@
 
+\hypertarget{appendix}{%
+\section*{Appendix}\label{appendix}}
+\addcontentsline{toc}{section}{Appendix}
+
 \bibliographystyle{unsrt}

### 2022-08-17 paper/paper.Rmd
better table 6

@@
       )
-    )
+    ),
+    unadj_lab = sprintf('%.0f%%', round(100 * prior_p), gt_p_value),
+    adj_lab = sprintf('%.0f%%', round(100 * expected_poststreak_p), gt_p_value_adj)
   ) |>
@@
     prop,
-    prior_p,
-    expected_poststreak_p,
-    gt_p_value,
-    gt_p_value_adj
+    unadj_lab,
+    adj_lab
   ) |> 
   gt::gt() |> 
-  gt::fmt_percent(
-    decimals = 0,
-    columns = c(prop, prior_p, expected_poststreak_p)
-  ) |> 
   gt::cols_label(
@@
     prop = 'O',
-    prior_p = 'a',
-    expected_poststreak_p = 'b',
-    gt_p_value = 'c',
-    gt_p_value_adj = 'd'
+    unadj_lab = 'a',
+    adj_lab = 'b'
   ) |> 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} and table \ref{tbl:cod-round-loss-prop-after-k-losses} shows $\hat{P}^{kr,\text{win}}_O$ and $\hat{P}^{kr,\text{loss}}_O$ for $k = 3$ streaks respectively.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}^{kr,\text{win}}_O$ and $\hat{P}^{kr,\text{loss}}_O$ for $k = 3$ streaks respectively.
 
@@
 \begin{longtable}{rrrrrrr}
-\caption{Observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round-win streak, for a series lasting $r$ rounds.}\label{tbl:cod-round-win-prop-after-k-wins} \\
+\caption{First, observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round win streak, for a series lasting $r$ rounds.
+Second, observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round loss streak}\label{tbl:cod-round-win-prop-after-k-wins} \\
 \toprule
+\multicolumn{7}{c}{\text{3 round win streak}} \\
  &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
@@
 11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
-\bottomrule
-\end{longtable}
-```
-```{=tex}
-\begin{longtable}{rrrrrrr}
-\caption{Observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round-loss streak, for a series lasting $r$ rounds.
-$r \in [7, 8, 9]$ are invalid.}\label{tbl:cod-round-loss-prop-after-k-losses} \\
 \toprule
+\multicolumn{7}{c}{\text{3 round loss streak}} \\
  &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 

### 2022-08-17 paper/paper.tex
better table 6

@@
   that lasts at maximum 11 rounds.} Table
-\ref{tbl:cod-round-win-prop-after-k-wins} and table
-\ref{tbl:cod-round-loss-prop-after-k-losses} shows
+\ref{tbl:cod-round-win-prop-after-k-wins} shows
 \(\hat{P}^{kr,\text{win}}_O\) and \(\hat{P}^{kr,\text{loss}}_O\) for
@@
 11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
-\bottomrule
-\end{longtable}
-
-\begin{longtable}{rrrrrrr}
-\caption{Observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round-loss streak, for a series lasting $r$ rounds.
-$r \in [7, 8, 9]$ are invalid.}\label{tbl:cod-round-loss-prop-after-k-losses} \\
 \toprule
+\multicolumn{7}{c}{\text{3 round loss streak}} \\
  &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 

### 2022-08-17 paper/paper.tex
reduce long eq 3

@@
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}(\text{win round | k-round winning streak, series lasting r rounds})=\{
+  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}_{E,\text{unadj.}}(\text{win | k, r})=\{
     \begin{array}{cl}
@@
 
-\(\hat{P}^{kr,loss}_{E,\text{unadj.}} = \hat{P}(\text{lose round | k-round losing streak, series lasting r rounds})\)
-can be formulated symmetrically.
+\(\hat{P}^{kr,loss}_{E,\text{unadj.}}\) can be formulated symmetrically.
 
@@
 
+\begin{tabbing}
 \begin{longtable}{rrrrrrr}
@@
 \end{longtable}
+\end{tabbing}
 

### 2022-08-18 paper/paper.Rmd
reduce long eq 3
splitting up methodology and results

@@
 
-# Methodology and results
+# Methodology
+
+## Distribution of rounds played {#sec:method-rounds-played}
+
+The general formula for the probability $P_E(r)$ that a best-of-$s$ series ($s = 11$ for CoD SnD) lasts $r$ rounds given constant probability $p$ of one team[^11] winning each round is
+
+[^11]: If $p > 0.5$, then one might say that this team is the better team (known in hindsight).
+
+$$
+m = \frac{s + 1}{2}
+$$
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:series-length}{}{
+P_E(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(p^{m}(1 - p)^{r - m} + p^{r - m}(1 - p)^m).
+}\label{eq:series-length}\end{equation}
+```
+The chi-square goodness of fit statistic can be used to test the constant found probability hypothesis for $0 \leq p \leq 1$.
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:chi-squ}{}{
+\chi^2 = \sum^R \frac{(P_O(r) - P_E(r))^2}{P_E(r)}
+}\label{eq:chi-squ}\end{equation}
+```
+For CoD SnD, $r \in R [6, 7, 8, 9, 10, 11]$.
+
+## Momentum {#sec:method-momentum}
+
+Without accounting for the streak selection bias described by Miller and Sanjurjo [-@miller2018], the round win probability after a streak of $k$ round wins for a best-of-$s$ series ($s = 11$ for CoD SnD), accounting for the series lasting $r$ rounds known in hindsight, is
+
+$$
+m = \frac{s + 1}{2}
+$$
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:pwkr}{}{
+  p^{w|kr} = p(\text{win | k, r})=\{
+    \begin{array}{cl}
+    \frac{m - k}{i - k}, & \text{team wins series} \\
+    \frac{s - m - k}{i - k}, & \text{team loses series}
+    \end{array}.
+  }
+\label{eq:pwkr}
+\end{equation}
+```
+The "hindsight" round loss probability after a streak of $k$ round losses for a series lasting $r$ rounds, $p^{l|kr}$, can be formulated symmetrically.[^12]
+
+[^12]: Note that these probabilities are separate from the constant round probabilities in Sections \ref{sec:method-rounds-played} and \ref{sec:results-rounds-played}.
+
+However, as shown by Miller and Sanjurjo, we should expect the observed proportion of rounds wins after a streak $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}$, to be strictly less than $p^{w|kr}$.[^13]
+
+[^13]: See Appendix A of Miller and Sanjurjo [-@miller2018] for the proof.
+
+> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < p < 1$*.
+Let* $\hat{P}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
+\hat{P}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
+In particular,* $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.$
+
+Miller and Sanjurjo [-@miller2018] note that there does not exists a closed form representation for $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ ($\hat{P}^{w|kr}$ for CoD SnD) for $k > 1$.
+Figure \ref{fig:npk} shows this.[^14]
+
+[^14]: I've adapted the code from Vafa [-@vafa2017].
+
+![The expected value](images/npk_replicated.png)
+
+The expected value of the proportion of successes on trials that immediately follow k consecutive successes, Pˆk(X), as a function of the total number of trials n,for different values of k and probabilities of success p,
+
+# Results
 
@@
 
+## Distribution of rounds played {#sec:results-rounds-played}
+
+Using Equation \ref{eq:chi-squ}, $\chi^2 = 16.0$ (p-value of 0.0068) for a naive constant round win probability $p_0 = 0.5$.
+Thus, I can comfortably reject the constant probability null hypothesis for $p_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
 Afterwards, I investigate post-streak win rates, building on my learnings from the constant probability assumption analysis.
@@
 
-## Distribution of rounds played {#sec:analysis-1}
-
-The general formula for the probability $P_E(r)$ that a best-of-$s$ series lasts $r$ rounds given constant probability $p$ of one team[^11] winning each round is
-
-[^11]: If $p > 0.5$, then one might say that this team is the better team (known in hindsight).
-
-$$
-q = 1 - p, s_1 = \frac{s_1 - 1}{2}, s_2 = \frac{s_1 + 1}{2}, s_2^{'} = 1 - s_2
-$$
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq-series-length}{}{
-P_E(r) = \frac{(r - 1)!}{s_1!(r - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
-}\label{eq:series-length}\end{equation}
-```
 ```{r}
@@
 .cutoff <- 6
-prob_of_series_lasting_n_games <- function(n, p = 0.5, max_round = .max_round) {
-  s <- ceiling(max_round / 2)
-  (factorial(n - 1) / (factorial(s - 1) * factorial(n - s))) * (p^s * (1 - p)^(n - s) + p^(n - s) * (1 - p)^s)
+prob_of_series_lasting_r_rounds <- function(r, p = 0.5, s = .max_round) {
+  m <- as.integer((s + 1) / 2)
+  (factorial(r - 1) / (factorial(m - 1) * factorial(r - s))) * (p^m * (1 - p)^(r - m) + p^(r - m) * (1 - p)^m)
 }
@@
     mutate(
-      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_n_games(.x, max_round = .max_round, p = !!p)),
+      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_r_rounds(.x, max_round = .max_round, p = !!p)),
       n_expected_series_streaks = map_dbl(n_rounds, ~expected_series_streaks_of_outcomes(.cutoff, .x - .cutoff))
@@
 
-Calculating the chi-square goodness of fit statistic
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:series-length}{}{
-\chi^2 = \sum^{11}_{i=6} \frac{(P_O(r) - P_E(r))^2}{P_E(r)}, r \in R = [6, 7, 8, 9, 10, 11].
-}\label{eq:chi-squ-test}\end{equation}
-```
-as 16.0 (p-value of 0.0068), I can comfortably reject the constant probability null hypothesis for $p_0 = 0.5$, event at a confidence level of $\alpha = 0.01$.
-
 ```{r}
@@
 theoretical_cod_series_length <- function(p) {
-  6 * prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11) +
-    7 * prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11) +
-    8 * prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11) +
-    9 * prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11) +
-    10 * prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11) +
-    11 * prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)
+  6 * prob_of_series_lasting_r_rounds(n = 6, p = p, max_round = 11) +
+    7 * prob_of_series_lasting_r_rounds(n = 7, p = p, max_round = 11) +
+    8 * prob_of_series_lasting_r_rounds(n = 8, p = p, max_round = 11) +
+    9 * prob_of_series_lasting_r_rounds(n = 9, p = p, max_round = 11) +
+    10 * prob_of_series_lasting_r_rounds(n = 10, p = p, max_round = 11) +
+    11 * prob_of_series_lasting_r_rounds(n = 11, p = p, max_round = 11)
 }
@@
 maximize_cod_series_p <- function(p) {
-  prob_of_series_lasting_n_games(n = 6, p = p, max_round = 11)^cod_n6adj *
-    prob_of_series_lasting_n_games(n = 7, p = p, max_round = 11)^cod_n7adj *
-    prob_of_series_lasting_n_games(n = 8, p = p, max_round = 11)^cod_n8adj *
-    prob_of_series_lasting_n_games(n = 9, p = p, max_round = 11)^cod_n9adj *
-    prob_of_series_lasting_n_games(n = 10, p = p, max_round = 11)^cod_n10adj *
-    prob_of_series_lasting_n_games(n = 11, p = p, max_round = 11)^cod_n11adj
+  prob_of_series_lasting_r_rounds(n = 6, p = p, max_round = 11)^cod_n6adj *
+    prob_of_series_lasting_r_rounds(n = 7, p = p, max_round = 11)^cod_n7adj *
+    prob_of_series_lasting_r_rounds(n = 8, p = p, max_round = 11)^cod_n8adj *
+    prob_of_series_lasting_r_rounds(n = 9, p = p, max_round = 11)^cod_n9adj *
+    prob_of_series_lasting_r_rounds(n = 10, p = p, max_round = 11)^cod_n10adj *
+    prob_of_series_lasting_r_rounds(n = 11, p = p, max_round = 11)^cod_n11adj
 }
@@
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability $p$ that I find when applying the three methods suggested by Mosteller [-@mosteller1952].
-Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ-test}, each results in a $\chi^2$ value for which I cannot reject the constant probability null hypothesis.
+Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which I cannot reject the constant probability null hypothesis.
 
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^12] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^15] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
 $p_{2}$ is also closer to $P_O(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^12]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$).
+[^15]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$).
 
@@
 
-## Momentum {#sec:analysis-2}
+## Momentum {#sec:results-momentum}
 
@@
 
-Despite the implication that one can model team round win probability in CoD SnD as a constant, anecdotally many believe in momentum i.e.
-streaks not due to random chance.
-I now evaluate win frequency in rounds following a streak of length $k$.
-I account for the length of the series ($r$ rounds), modeling the expected round win probability after a streak of length $k$ as
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^16] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}^{kr,\text{win}}_O$ and $\hat{P}^{kr,\text{loss}}_O$ for $k = 3$ streaks respectively.
 
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:pwkr}{}{
-  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}(\text{win round | k-round winning streak, series lasting r rounds})=\{
-    \begin{array}{cl}
-    \frac{6 - k}{i - k}, & \text{team wins series} \\
-    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
-    \end{array}.
-  }\label{eq:pwkr}
-\end{equation}
-```
-$\hat{P}^{kr,loss}_{E,\text{unadj.}} = \hat{P}(\text{lose round | k-round losing streak, series lasting r rounds})$ can be formulated symmetrically.
-
-While one might think that $E[\hat{P}^{kr,\text{win}} - \hat{P}^{kr,\text{loss}}] = 0$, Miller and Sanjurjo [-@miller2018] suggest that, given a deterministic i.i.d.
-Bernoulli probability (Equation \ref{eq:pwkr}, this is not true due to streak-selection bias.[^13] As proved by Miller and Sanjurjo, TODO: Combine these two sentences
-
-[^13]: Note that these probabilities are separate from those in Section \ref{sec:analysis-1}.
-
-> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < p < 1$*.
-Let* $\hat{P}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
-\hat{P}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
-In particular,* $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.$
-
-TODO: Descripe the Appendix E.1.
-I apply their formulation for "downward bias" to post-streak success to come up with estimates $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$, specifying $r$ as the number of trials.
-
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^14] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}^{kr,\text{win}}_O$ and $\hat{P}^{kr,\text{loss}}_O$ for $k = 3$ streaks respectively.
-
-[^14]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+[^16]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
 

### 2022-08-18 paper/paper.tex
splitting up methodology and results

@@
 
-\hypertarget{methodology-and-results}{%
-\section{Methodology and results}\label{methodology-and-results}}
+\hypertarget{methodology}{%
+\section{Methodology}\label{methodology}}
+
+\hypertarget{sec:method-rounds-played}{%
+\subsection{Distribution of rounds
+played}\label{sec:method-rounds-played}}
+
+The general formula for the probability \(P_E(r)\) that a best-of-\(s\)
+series (\(s = 11\) for CoD SnD) lasts \(r\) rounds given constant
+probability \(p\) of one team\footnote{If \(p > 0.5\), then one might
+  say that this team is the better team (known in hindsight).} winning
+each round is
+
+\[
+m = \frac{s + 1}{2}
+\]
+
+\begin{equation}\protect\hypertarget{eq:series-length}{}{
+P_E(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(p^{m}(1 - p)^{r - m} + p^{r - m}(1 - p)^m).
+}\label{eq:series-length}\end{equation}
+
+The chi-square goodness of fit statistic can be used to test the
+constant found probability hypothesis for \(0 \leq p \leq 1\).
+
+\begin{equation}\protect\hypertarget{eq:chi-squ}{}{
+\chi^2 = \sum^R \frac{(P_O(r) - P_E(r))^2}{P_E(r)}
+}\label{eq:chi-squ}\end{equation}
+
+For CoD SnD, \(r \in R [6, 7, 8, 9, 10, 11]\).
+
+\hypertarget{sec:method-momentum}{%
+\subsection{Momentum}\label{sec:method-momentum}}
+
+Without accounting for the streak selection bias described by Miller and
+Sanjurjo (2018), the round win probability after a streak of \(k\) round
+wins for a best-of-\(s\) series (\(s = 11\) for CoD SnD), accounting for
+the series lasting \(r\) rounds known in hindsight, is
+
+\[
+m = \frac{s + 1}{2}
+\]
+
+\begin{equation}\protect\hypertarget{eq:pwkr}{}{
+  p^{w|kr} = p(\text{win | k, r})=\{
+    \begin{array}{cl}
+    \frac{m - k}{i - k}, & \text{team wins series} \\
+    \frac{s - m - k}{i - k}, & \text{team loses series}
+    \end{array}.
+  }
+\label{eq:pwkr}
+\end{equation}
+
+The ``hindsight'' round loss probability after a streak of \(k\) round
+losses for a series lasting \(r\) rounds, \(p^{l|kr}\), can be
+formulated symmetrically.\footnote{Note that these probabilities are
+  separate from the constant round probabilities in Sections
+  \ref{sec:method-rounds-played} and \ref{sec:results-rounds-played}.}
+
+However, as shown by Miller and Sanjurjo, we should expect the observed
+proportion of rounds wins after a streak \(k\) rounds wins for a series
+lasting \(r\) rounds, \(\hat{P}_{w|kr}\), to be strictly less than
+\(p^{w|kr}\).
+
+\begin{quote}
+Theorem 1: \emph{Let}
+\(\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3\)\emph{, be a sequence of
+independent Bernoulli trials, each with probability of success}
+\(0 < p < 1\)\emph{. Let} \(\hat{P}_k(\mathbf{X})\) \emph{be the
+proportion of successes on the subset of trials} \(I_k(\mathbf{X})\)
+\emph{that immediately follow} \(k\) consecutive successes, that is,
+\(\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |. \hat{P}_k\)
+\emph{is a biased estimate of}
+\(\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p\) \emph{for
+all} \(k\) \emph{such that} \(1 \leq k \leq n - 2\)\emph{. In
+particular,}
+\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.\)
+\end{quote}
+
+Miller and Sanjurjo (2018) note that there does not exists a closed form
+representation for
+\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\) for
+\(k > 1\).
+
+\hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
 
+\hypertarget{sec:results-rounds-played}{%
+\subsection{Distribution of rounds
+played}\label{sec:results-rounds-played}}
+
+Using Equation \ref{eq:chi-squ}, \(\chi^2 = 16.0\) (p-value of 0.0068)
+for a naive constant round win probability \(p_0 = 0.5\). Thus, I can
+comfortably reject the constant probability null hypothesis for
+\(p_0 = 0.5\), even at a confidence level of \(\alpha = 0.01\).
 Afterwards, I investigate post-streak win rates, building on my
@@
 accounting for it in when analyzing momentum.
-
-\hypertarget{sec:analysis-1}{%
-\subsection{Distribution of rounds played}\label{sec:analysis-1}}
-
-The general formula for the probability \(P_E(r)\) that a best-of-\(s\)
-series lasts \(r\) rounds given constant probability \(p\) of one
-team\footnote{If \(p > 0.5\), then one might say that this team is the
-  better team (known in hindsight).} winning each round is
-
-\[
-q = 1 - p, s_1 = \frac{s_1 - 1}{2}, s_2 = \frac{s_1 + 1}{2}, s_2^{'} = 1 - s_2
-\]
-
-\begin{equation}\protect\hypertarget{eq-series-length}{}{
-P_E(r) = \frac{(r - 1)!}{s_1!(r - s_2)!}(p^{s_2}q^{s_2^{'}} + p^{s_2^{'}}q^{s_2}).
-}\label{eq:series-length}\end{equation}
 
@@
 
-Calculating the chi-square goodness of fit statistic
-
-\begin{equation}\protect\hypertarget{eq:series-length}{}{
-\chi^2 = \sum^{11}_{i=6} \frac{(P_O(r) - P_E(r))^2}{P_E(r)}, r \in R = [6, 7, 8, 9, 10, 11].
-}\label{eq:chi-squ-test}\end{equation}
-
-as 16.0 (p-value of 0.0068), I can comfortably reject the constant
-probability null hypothesis for \(p_0 = 0.5\), event at a confidence
-level of \(\alpha = 0.01\).
-
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for
@@
 three methods suggested by Mosteller (1952). Each is approximately or
-equal to 0.575, and, when applying Equation \ref{eq:chi-squ-test}, each
+equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each
 results in a \(\chi^2\) value for which I cannot reject the constant
@@
 
-\hypertarget{sec:analysis-2}{%
-\subsection{Momentum}\label{sec:analysis-2}}
-
-Despite the implication that one can model team round win probability in
-CoD SnD as a constant, anecdotally many believe in momentum i.e.~streaks
-not due to random chance. I now evaluate win frequency in rounds
-following a streak of length \(k\). I account for the length of the
-series (\(r\) rounds), modeling the expected round win probability after
-a streak of length \(k\) as
-
-\begin{equation}\protect\hypertarget{eq:pwkr}{}{
-  \hat{P}^{kr,\text{win}}_{E,\text{unadj.}} = \hat{P}_{E,\text{unadj.}}(\text{win | k, r})=\{
-    \begin{array}{cl}
-    \frac{6 - k}{i - k}, & \text{team wins series} \\
-    \frac{11 - 6 - k}{i - k}, & \text{team loses series}
-    \end{array}.
-  }\label{eq:pwkr}
-\end{equation}
-
-\(\hat{P}^{kr,loss}_{E,\text{unadj.}}\) can be formulated symmetrically.
-
-While one might think that
-\(E[\hat{P}^{kr,\text{win}} - \hat{P}^{kr,\text{loss}}] = 0\), Miller
-and Sanjurjo (2018) suggest that, given a deterministic i.i.d. Bernoulli
-probability (Equation \ref{eq:pwkr}, this is not true due to
-streak-selection bias.\footnote{Note that these probabilities are
-  separate from those in Section \ref{sec:analysis-1}.} As proved by
-Miller and Sanjurjo, TODO: Combine these two sentences
-
-\begin{quote}
-Theorem 1: \emph{Let}
-\(\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3\)\emph{, be a sequence of
-independent Bernoulli trials, each with probability of success}
-\(0 < p < 1\)\emph{. Let} \(\hat{P}_k(\mathbf{X})\) \emph{be the
-proportion of successes on the subset of trials} \(I_k(\mathbf{X})\)
-\emph{that immediately follow} \(k\) consecutive successes, that is,
-\(\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |. \hat{P}_k\)
-\emph{is a biased estimate of}
-\(\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p\) \emph{for
-all} \(k\) \emph{such that} \(1 \leq k \leq n - 2\)\emph{. In
-particular,}
-\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.\)
-\end{quote}
-
-TODO: Descripe the Appendix E.1. I apply their formulation for
-``downward bias'' to post-streak success to come up with estimates
-\(\hat{P}^{kr,\text{win}}_{E,\text{adj.}}\), specifying \(r\) as the
-number of trials.
+\hypertarget{sec:results-momentum}{%
+\subsection{Momentum}\label{sec:results-momentum}}
 
@@
 
-\begin{tabbing}
 \begin{longtable}{rrrrrrr}
@@
 \end{longtable}
-\end{tabbing}
 

### 2022-08-18 research/replicate-streaks.R
messing with streaks code

@@ -30,15 +30,16 @@ set.seed(42)
 runs <- rerun(
   1000,
   crossing(
-    n = 1:100,
+    n = 1:50,
     k = 1:4,
     p = c(0.25, 0.5, 0.75)
   ) |> 
     mutate(
-      next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 100, n = ..1, k = ..2, p = ..3))
+      next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2, p = ..3))
     )
 ) |> 
   reduce(bind_rows)
+qs::qsave(runs, 'data/runs_1000x1000.qs')
 
 agg_runs <- runs |> 
   filter(!is.nan(next_p)) |> 
@@ -49,20 +50,37 @@ agg_runs <- runs |>
   ungroup() |>
   arrange(p, k)
 
-p_streaks <- agg_runs |>
-  group_by(p, k) |> 
-  mutate(
-    avg_next_p = slider::slide_dbl(next_p, .f = mean, .before = 5, .after = 0)
+agg_runs <- runs |> 
+  filter(!is.nan(next_p)) |> 
+  slice_sample(prop = 10, replace = TRUE) |> 
+  group_by(p, k, n) |> 
+  summarize(
+    across(next_p, mean)
   ) |> 
-  ungroup() |> 
+  ungroup() |>
+  arrange(p, k)
+
+p_streaks <- bind_rows(
+  agg_runs |> 
+    distinct(p, k) |> 
+    mutate(n = 1, next_p = p),
+  agg_runs,
+) |> 
+  arrange(p, k, n) |> 
+  # group_by(p, k) |> 
+  # mutate(
+  #   avg_next_p = slider::slide_dbl(next_p, .f = mean, .before = 5, .after = 0)
+  # ) |> 
+  # ungroup() |> 
   mutate(
     across(k, factor),
     group = sprintf('%s-%s', p, k)
   ) |> 
   ggplot() +
   theme_minimal() +
-  aes(x = n, y = avg_next_p, color = k, group = group) +
+  aes(x = n, y = next_p, color = k, group = group) +
   geom_line() +
+  geom_smooth() +
   geom_hline(aes(yintercept = p)) +
   labs(x = NULL, y = NULL)
 p_streaks

### 2022-08-19 research/replicate-streaks.R
npkd plot

@@ -26,7 +26,6 @@ simulate_post_streak_prob <- function(sims = 1000, ...) {
 }
 
 set.seed(42)
-## 1.6 hours for 1k reruns and 100 sims
 runs <- rerun(
   1000,
   crossing(
@@ -50,28 +49,8 @@ agg_runs <- runs |>
   ungroup() |>
   arrange(p, k)
 
-agg_runs <- runs |> 
-  filter(!is.nan(next_p)) |> 
-  slice_sample(prop = 10, replace = TRUE) |> 
-  group_by(p, k, n) |> 
-  summarize(
-    across(next_p, mean)
-  ) |> 
-  ungroup() |>
-  arrange(p, k)
-
-p_streaks <- bind_rows(
-  agg_runs |> 
-    distinct(p, k) |> 
-    mutate(n = 1, next_p = p),
-  agg_runs,
-) |> 
+p_streaks <- agg_runs |> 
   arrange(p, k, n) |> 
-  # group_by(p, k) |> 
-  # mutate(
-  #   avg_next_p = slider::slide_dbl(next_p, .f = mean, .before = 5, .after = 0)
-  # ) |> 
-  # ungroup() |> 
   mutate(
     across(k, factor),
     group = sprintf('%s-%s', p, k)
@@ -80,8 +59,44 @@ p_streaks <- bind_rows(
   theme_minimal() +
   aes(x = n, y = next_p, color = k, group = group) +
   geom_line() +
-  geom_smooth() +
+  # geom_smooth() +
   geom_hline(aes(yintercept = p)) +
   labs(x = NULL, y = NULL)
 p_streaks
 ggsave(p_streaks, filename = 'research/npk_replicated.png', width = 12, height = 9)
+
+font <- 'Latin Modern Roman 10'
+extrafont::loadfonts(quiet = TRUE)
+theme_set(theme_classic())
+theme_update(
+  text = element_text(family = font)
+)
+  
+p <- agg_runs |> 
+  filter(p == 0.5, k >= 2, k <= 4, n <= 50) |> 
+  arrange(p, k, n) |> 
+  mutate(
+    across(k, factor)
+  ) |> 
+  ggplot() +
+  aes(x = n, y = next_p, color = k, group = k) +
+  guides(
+    color = guide_legend(
+      title.hjust = 0.5,
+      nrow = 1, override.aes = list(size = 3)
+    )
+  ) +
+  geom_line() +
[…]

### 2022-08-19 research/replicate-streaks.R
cleaner npkd

@@ -25,53 +25,55 @@ simulate_post_streak_prob <- function(sims = 1000, ...) {
     mean(na.rm = TRUE)
 }
 
-set.seed(42)
-runs <- rerun(
-  1000,
-  crossing(
-    n = 1:50,
-    k = 1:4,
-    p = c(0.25, 0.5, 0.75)
-  ) |> 
-    mutate(
-      next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2, p = ..3))
-    )
-) |> 
-  reduce(bind_rows)
-qs::qsave(runs, 'data/runs_1000x1000.qs')
+# set.seed(42)
+# runs <- rerun(
+#   1000,
+#   crossing(
+#     n = 1:50,
+#     k = 1:4,
+#     p = c(0.25, 0.5, 0.75)
+#   ) |> 
+#     mutate(
+#       next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2, p = ..3))
+#     )
+# ) |> 
+#   reduce(bind_rows)
+# qs::qsave(runs, 'data/runs_1000x1000.qs')
+runs <- qs::qread('data/runs_1000x1000.qs')
 
-agg_runs <- runs |> 
-  filter(!is.nan(next_p)) |> 
-  group_by(p, k, n) |> 
+agg_runs <- runs |>
+  filter(!is.nan(next_p)) |>
+  group_by(p, k, n) |>
   summarize(
     across(next_p, mean)
-  ) |> 
+  ) |>
   ungroup() |>
   arrange(p, k)
 
-p_streaks <- agg_runs |> 
-  arrange(p, k, n) |> 
-  mutate(
-    across(k, factor),
-    group = sprintf('%s-%s', p, k)
-  ) |> 
-  ggplot() +
-  theme_minimal() +
-  aes(x = n, y = next_p, color = k, group = group) +
-  geom_line() +
-  # geom_smooth() +
-  geom_hline(aes(yintercept = p)) +
-  labs(x = NULL, y = NULL)
-p_streaks
-ggsave(p_streaks, filename = 'research/npk_replicated.png', width = 12, height = 9)
+# p_streaks <- agg_runs |> 
+#   arrange(p, k, n) |> 
+#   mutate(
+#     across(k, factor),
+#     group = sprintf('%s-%s', p, k)
+#   ) |> 
+#   ggplot() +
+#   theme_minimal() +
[…]

### 2022-08-19 paper/paper.Rmd
ALL THE SYMBOL CHANGES

@@
 There have been a handful of studies of the distribution of games played in a series of a professional sport.
-Most assume a constant probability $p$ of a given team winning a game in the series, regardless of the series state.
-Mosteller [-@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $p = 0.5$.
-Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $p \approx 0.65$.
+Most assume a constant probability $\phi$ of a given team winning a game in the series, regardless of the series state.
+Mosteller [-@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $\phi = 0.5$.
+Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\phi \approx 0.65$.
 in each case: (1) solving for $p$ from the empirical average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
-maximum likelihood), and (3) minimizing the chi-square goodness of fit statistic for $p$.
-
-Chance [-@chance2020] re-examines the constant probability notion in Major League Baseball's World Series (1923--2018), the National Basketball Association's Finals (1951--2018), and the National Hockey League's Stanley Cup (1939--2018).
-Chance finds strong evidence against the null hypothesis of $p = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.[\^8] [\^8]: Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
+maximum likelihood), and (3) minimizing the chi-square goodness of fit statistic for $\phi$.
+
+Chance [-@chance2020] re-examines the constant probability notion in Major League Baseball's (MLB) World Series (1923--2018), the National Basketball Association's (NBA) Finals (1951--2018), and the National Hockey League's (NHL) Stanley Cup (1939--2018).
+Chance finds strong evidence against the null hypothesis of $\phi = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.
+Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
 
@@
 Gilovich et al.
-[-@gilovich1985] do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo [-@miller2018] refuted the conclusions of Gilovich et al., proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^9].
-Specifically, Miller and Sanjurjo say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
+[-@gilovich1985], henceforth GVT, do not find evidence for the hot hand phenomenon.
+However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^9].
+Specifically, MS say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
 conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success".
-When applying streak selection bias to Giloveih et al.'s data, Miller and Sanjurjo come to the opposite conclusions as Giloveih et al.
+When applying streak selection bias to GVT.'s data, MS come to the opposite conclusions as GVT.
 
 [^9]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
-provides a novel structural candidate explanationfor the persistence of gambler's fallacy beliefs", per Miller and Sanjurjo [-@miller2018].
+provides a novel structural candidate explanation for the persistence of gambler's fallacy beliefs", per MS.
 
@@
 Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.[^10]
-
-[^10]: Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e. playing either offense or defense for many consecutive rounds).
+However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.
+
+Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e.
+playing either offense or defense for many consecutive rounds).
+On the other hand, teams in CoD SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^10] While theoretically one might be able to account for any kind of balanced rotation, such as a "blocky" on like a 5-5-1, the rotation of team sides every round is convenient, particularly for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+Bernoulli trials.
+
+[^10]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
 
@@
 
-The general formula for the probability $P_E(r)$ that a best-of-$s$ series ($s = 11$ for CoD SnD) lasts $r$ rounds given constant probability $p$ of one team[^11] winning each round is
-
-[^11]: If $p > 0.5$, then one might say that this team is the better team (known in hindsight).
+The formula for the expected proportion of seriesn a best-of-$s$ format ($s = 11$ rounds for CoD SnD), ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^11] is
+
+[^11]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
 
@@
 ```{=tex}
+\begin{equation}\protect\hypertarget{eq:m}{}{
+m = \frac{s + 1}{2}
+}\label{eq:m}\end{equation}
+```
+```{=tex}
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
-P_E(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(p^{m}(1 - p)^{r - m} + p^{r - m}(1 - p)^m).
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m).
 }\label{eq:series-length}\end{equation}
 ```
-The chi-square goodness of fit statistic can be used to test the constant found probability hypothesis for $0 \leq p \leq 1$.
+To evaluate the constant round win probability hypothesis--that is, that the expected and observed round win rates, $\hat{\Phi}(r)$ and $\Phi(r)$ respectively, are equal to one another--we can compute the chi-square goodness of fit statistic, $\chi^2$.
 
@@
 \begin{equation}\protect\hypertarget{eq:chi-squ}{}{
-\chi^2 = \sum^R \frac{(P_O(r) - P_E(r))^2}{P_E(r)}
+\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
 }\label{eq:chi-squ}\end{equation}
 ```
-For CoD SnD, $r \in R [6, 7, 8, 9, 10, 11]$.
+For CoD SnD, $r \in R = [6, 7, 8, 9, 10, 11]$.
 
@@
 
-Without accounting for the streak selection bias described by Miller and Sanjurjo [-@miller2018], the round win probability after a streak of $k$ round wins for a best-of-$s$ series ($s = 11$ for CoD SnD), accounting for the series lasting $r$ rounds known in hindsight, is
-
-$$
-m = \frac{s + 1}{2}
-$$
+The hindsight Bernoulli round loss probability after a streak of $k$ round wins, $p^{l|kr}_0$, can be formulated symmetrically. We might consider these as a reference when considering the
+
+Removing our knowledge of a streak, we might model the Bernoulli round win probability as
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:pwr}{}{
+  p^{w|r} = p(\text{win | r})=\{
+    \begin{array}{cl}
+    \frac{m}{r}, & \text{team wins series} \\
+    \frac{r - m}{r}, & \text{team loses series}
+    \end{array}.
+  }
+\label{eq:pwr}
+\end{equation}
+```
+As shown by MS, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^12]
+
+[^12]: See Appendix E.1 of MS for details on the proof that follows.
+
+> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < p < 1$*.
+Let* $\hat{P}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
+\hat{P}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
+In particular,* $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.$
+
+MS note that there does not exists a closed form representation for $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ for $k > 1$.
+($\hat{P}_k(\mathbf{X})$ is the analogue for $\hat{P}^{w|kr}_{MS}$ in my notation for CoD SnD.) Figure 1 shows how the expected value varies as a function of the total number of trials $n$, given $p$ and $k > 1$.[^13]
+
+[^13]: I've adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+```{r}
+#| label: npkd
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 10000, seed = 42, ...) {
+  withr::local_seed(seed)
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+
+# library(extrafont)
+# library(ggplot2)
+# set.seed(42)
+# runs <- rerun(
+#   1000,
+#   crossing(
+#     n = 1:50,
+#     k = 2:4,
+#     p = 0.5
+#   ) |>
+#     mutate(
+#       next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2, p = ..3))
+#     )
+# ) |>
+#   reduce(bind_rows)
+# 
+# agg_runs <- runs |>
+#   filter(!is.nan(next_p)) |>
+#   group_by(p, k, n) |>
+#   summarize(
+#     across(next_p, mean)
+#   ) |>
+#   ungroup() |>
+#   arrange(p, k)
+# 
+# extrafont::loadfonts(quiet = TRUE)
+# theme_set(theme_classic())
+# theme_update(
+#   text = element_text(family = 'CMU Typewriter Text')
+# )
+# p <- agg_runs |> 
+#   arrange(p, k, n) |> 
+#   mutate(
+#     across(k, factor)
+#   ) |> 
+#   ggplot() +
+#   aes(x = n, y = next_p, color = k, group = k) +
+#   guides(
+#     color = guide_legend(
+#       title.hjust = 0.5,
+#       nrow = 1, override.aes = list(size = 3)
+#     )
+#   ) +
+#   geom_line() +
+#   geom_hline(aes(yintercept = p)) +
+#   labs(x = 'n', y = 'p') +
+#   theme(
+#     legend.position = c(0.5, 0.8)
+#   )
+# 
+# ggsave(
+#   p, 
+#   filename = 'paper/images/npkd.png', 
+#   width = 5.5, 
+#   height = 3
+# )
+```
+
+```{=tex}
+\begin{figure}
+\centering
+\includegraphics{images/npkd.png}
+\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $p = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
+\end{figure}
+```
+My context is fundamentally different from that of GVT and MS, both of whom focus on longitudinal data in controlled settings.
+GVT also perform statistical tests on shots from players in live games, i.e.
+"observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
+The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series, as shown in Equation \ref{eq:pwr}.
+The Bernoulli trial success probability, i.e.
+a round win in CoD SnD, is not independent of the opponent.
+
+Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{l|kr}$, as performed by GVT and MS to evaluate their respective hypothesis regarding $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ (Theorem 1), is not appropriate.
+
+Let us consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "hindsight" proportion $\hat{P}^{w|kr}_0$.
+The Bernoulli round win probability underlying $\hat{P}^{w|kr}_0$ is
+
+~~When considering momentum in consecutive rounds wins, I use the descriptor "hindsight" because I account for the length of the series (~~$r$ rounds).
 
@@
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-  p^{w|kr} = p(\text{win | k, r})=\{
+  p_0^{w|kr} = p_0(\text{win | k, r})=\{
     \begin{array}{cl}
@@
 ```
-The "hindsight" round loss probability after a streak of $k$ round losses for a series lasting $r$ rounds, $p^{l|kr}$, can be formulated symmetrically.[^12]
-
-[^12]: Note that these probabilities are separate from the constant round probabilities in Sections \ref{sec:method-rounds-played} and \ref{sec:results-rounds-played}.
-
-However, as shown by Miller and Sanjurjo, we should expect the observed proportion of rounds wins after a streak $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}$, to be strictly less than $p^{w|kr}$.[^13]
-
-[^13]: See Appendix A of Miller and Sanjurjo [-@miller2018] for the proof.
-
-> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < p < 1$*.
-Let* $\hat{P}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
-\hat{P}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
-In particular,* $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.$
-
-Miller and Sanjurjo [-@miller2018] note that there does not exists a closed form representation for $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ ($\hat{P}^{w|kr}$ for CoD SnD) for $k > 1$.
-Figure \ref{fig:npk} shows this.[^14]
-
-[^14]: I've adapted the code from Vafa [-@vafa2017].
-
-![The expected value](images/npk_replicated.png)
-
-The expected value of the proportion of successes on trials that immediately follow k consecutive successes, Pˆk(X), as a function of the total number of trials n,for different values of k and probabilities of success p,
+A binomial test for the observed proportion of round wins following streaks of $k$ round wins in a series lasting $r$ rounds, $P^{w|kr}$, assuming $p_0^{w|kr}$ as the probability of success, can be used to verify that $p_0^{w|kr}$ is reasonable as a reference.
+
+A proportion test of $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ can tell us whether the momentum exists in CoD SnD.
+A null result means we cannot say that there is a difference between the hindsight expected proportion $\hat{P}^{w|kr}_0$ and the expected proportion adjusted for streak-selection bias, $\hat{P}^{w|kr}_0$.
 
@@
 Chance's [-@chance2020] work is closely related to mine, and, in fact, provides a guide for this investigation.
+Afterwards, I investigate post-streak win rates and the context of momentum, leveraging MS's [-@miller2018] framework for streak selection bias.
 
@@
 
-Using Equation \ref{eq:chi-squ}, $\chi^2 = 16.0$ (p-value of 0.0068) for a naive constant round win probability $p_0 = 0.5$.
-Thus, I can comfortably reject the constant probability null hypothesis for $p_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
-Afterwards, I investigate post-streak win rates, building on my learnings from the constant probability assumption analysis.
-I agree with Miller and Sanjurjo's [-@miller2018] framework for streak selection bias, accounting for it in when analyzing momentum.
+Using Equation \ref{eq:chi-squ}, I find that $\chi^2 = 16.0$ (p-value of 0.0068) for the naive constant round win probability $\phi_0 = 0.5$.
+Thus, I can comfortably reject the constant probability null hypothesis for $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
 
@@
 .cutoff <- 6
-prob_of_series_lasting_r_rounds <- function(r, p = 0.5, s = .max_round) {
+prob_of_series_lasting_r_rounds <- function(r, p = 0.5, s) {
   m <- as.integer((s + 1) / 2)
-  (factorial(r - 1) / (factorial(m - 1) * factorial(r - s))) * (p^m * (1 - p)^(r - m) + p^(r - m) * (1 - p)^m)
+  (factorial(r - 1) / (factorial(m - 1) * factorial(r - m))) * (p^m * (1 - p)^(r - m) + p^(r - m) * (1 - p)^m)
 }
@@
     mutate(
-      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_r_rounds(.x, max_round = .max_round, p = !!p)),
+      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_r_rounds(.x, s = .max_round, p = !!p)),
       n_expected_series_streaks = map_dbl(n_rounds, ~expected_series_streaks_of_outcomes(.cutoff, .x - .cutoff))
@@
 
-```{r}
-#| label: cod_series_outcome_prop-table
-cod_streaks_naive_res$series |>
-  select(
-    n_rounds,
-    prop_expected,
-    prop_actual,
-    n_actual
-  ) |>
-  arrange(n_rounds) |>
-  gt::gt() |>
-  gt::cols_label(
-    n_rounds = 'r',
-    prop_expected = 'P_{E}(r)',
-    prop_actual = 'P_{O}(r)',
-    n_actual = 'N_O'
-  ) |>
-  gt::fmt_percent(
-    decimals = 1,
-    columns = c('prop_expected', 'prop_actual')
-  ) |>
-  gt::tab_spanner(
-    label = 'Observed',
-    columns = c('prop_actual', 'n_actual')
-  ) |>
-  gt::as_latex()
-```
-
-Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected probabilities for $s = 11$ under the naive assumption that $p_0 = 0.5$ for a given round, along with the observed proportions $P_O(r)$ in CoD SnD.
+Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected series lasting $r$ rounds, $\hat{\Phi}_0(r)$ (under the assumption $\phi_0 = 0.5$), for $s = 11$, along with the observed proportions, $\Phi(r)$, in CoD SnD.
 
@@
 \begin{longtable}{rrrr}
-\caption{The probabilities that a best-of-11 series lasts $r$ rounds ($P_E(r)$, where $r \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
-The observed frequencies observed are shown as a count $N_O(r)$ and as a proportion $P_O(r)$ of all series.}\label{tbl:cod-prob-series-lasting-r-rounds} \\
+\caption{The expected proportion of series lasting $r$ rounds ($\hat{\Phi}_0(r)$) in a best-of-11 format, wehre $r \in R = [6, 7, 8, 9, 10, 11]$ under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
+The observed frequencies for CoD SnD are shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^R N(r)$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
 \toprule
-&  & \multicolumn{2}{c}{Observed} \\ 
-\cmidrule(lr){3-4}
-$r$ & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
+$r$ & $\hat{\Phi}_0(r)$ & $\Phi(r)$ & $N(r)$ \\ 
 \midrule
@@
 ## p. 365 on https://math.mit.edu/classes/18.095/2016IAP/lec9/Sports_Mosteller1952_WorldSeries.pdf
+cod_prob_of_series_lasting_r_rounds <- function(r, p) {
+  prob_of_series_lasting_r_rounds(r = r, p = p, s = 11)
+}
+
 theoretical_cod_series_length <- function(p) {
-  6 * prob_of_series_lasting_r_rounds(n = 6, p = p, max_round = 11) +
-    7 * prob_of_series_lasting_r_rounds(n = 7, p = p, max_round = 11) +
-    8 * prob_of_series_lasting_r_rounds(n = 8, p = p, max_round = 11) +
-    9 * prob_of_series_lasting_r_rounds(n = 9, p = p, max_round = 11) +
-    10 * prob_of_series_lasting_r_rounds(n = 10, p = p, max_round = 11) +
-    11 * prob_of_series_lasting_r_rounds(n = 11, p = p, max_round = 11)
-}
+  6 * cod_prob_of_series_lasting_r_rounds(r = 6, p = p) +
+    7 * cod_prob_of_series_lasting_r_rounds(r = 7, p = p) +
+    8 * cod_prob_of_series_lasting_r_rounds(r = 8, p = p) +
+    9 * cod_prob_of_series_lasting_r_rounds(r = 9, p = p) +
+    10 * cod_prob_of_series_lasting_r_rounds(r = 10, p = p) +
+    11 * cod_prob_of_series_lasting_r_rounds(r = 11, p = p)
+}
+
 cod_rounds_per_series <- cod_streaks_naive_res$series |>
@@
 maximize_cod_series_p <- function(p) {
-  prob_of_series_lasting_r_rounds(n = 6, p = p, max_round = 11)^cod_n6adj *
-    prob_of_series_lasting_r_rounds(n = 7, p = p, max_round = 11)^cod_n7adj *
-    prob_of_series_lasting_r_rounds(n = 8, p = p, max_round = 11)^cod_n8adj *
-    prob_of_series_lasting_r_rounds(n = 9, p = p, max_round = 11)^cod_n9adj *
-    prob_of_series_lasting_r_rounds(n = 10, p = p, max_round = 11)^cod_n10adj *
-    prob_of_series_lasting_r_rounds(n = 11, p = p, max_round = 11)^cod_n11adj
+  cod_prob_of_series_lasting_r_rounds(r = 6, p = p)^cod_n6adj *
+    cod_prob_of_series_lasting_r_rounds(r = 7, p = p)^cod_n7adj *
+    cod_prob_of_series_lasting_r_rounds(r = 8, p = p)^cod_n8adj *
+    cod_prob_of_series_lasting_r_rounds(r = 9, p = p)^cod_n9adj *
+    cod_prob_of_series_lasting_r_rounds(r = 10, p = p)^cod_n10adj *
+    cod_prob_of_series_lasting_r_rounds(r = 11, p = p)^cod_n11adj
 }
@@
   )
-
-cod_streaks_other_res |>
-  select(name, p, chi_squ) |>
-  unnest(chi_squ) |>
-  mutate(
-    lab = generate_chi_label(statistic, p.value)
-  ) |>
-  select(
-    `Method` = name,
-    `$p$` = p,
-    `$\\chi^2$ (p-value)` = lab
-  ) |>
-  knitr::kable()
-
-cod_streaks_other_res |>
-  filter(idx %in% c(0L, 2L)) |> 
-  mutate(
-    lab = sprintf('$p$ = %s', p)
-  ) |>
-  select(lab, series_streaks) |>
-  unnest(series_streaks) |>
-  select(lab, n_rounds, prop_expected) |>
-  mutate(
-    across(prop_expected, ~scales::percent(.x, accuracy = 0.1))
-  ) |>
-  pivot_wider(
-    names_from = lab,
-    values_from = prop_expected
-  ) |>
-  inner_join(
-    cod_streaks_naive_res$series |>
-      transmute(n_rounds, `$P_O(r)$` = scales::percent(prop_actual, accuracy = 0.1)),
-    by = 'n_rounds'
-  ) |>
-  arrange(n_rounds) |>
-  rename(`$r$` = n_rounds) |>
-  knitr::kable()
-```
-
-Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability $p$ that I find when applying the three methods suggested by Mosteller [-@mosteller1952].
+```
+
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that I find when applying the three methods suggested by Mosteller [-@mosteller1952].
 Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which I cannot reject the constant probability null hypothesis.
@@
 \begin{longtable}[]{@{}lrr@{}}
-\caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
+\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
 \toprule()
-Method & \(p(r)\) & \(\chi^2\) (p-value) \\
+Method & $\phi$ & $\chi^2$ (p-value) \\
 \midrule()
@@
 \toprule()
-Method & \(p(r)\) & \(\chi^2\) (p-value) \\
+Method & $\phi(r)$ & $\chi^2$ (p-value) \\
 \midrule()
@@
 2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
-3. Minimum \(\chi^2\) & 0.5775 & 3.5 (0.62) \\
+3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
 \bottomrule()
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $P_E(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $p_2 = 0.575$.[^15] I observe that $P_E(r)$ is notably larger for $p_{2}$ when $r \in [6, 7]$, more closely matching $P_O(r)$.
-$p_{2}$ is also closer to $P_O(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
-
-[^15]: The method of moments and minimum $\chi^2$ estimates for $p$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $p$ (since they are all $\approx 0.575$).
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^14] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+$\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
+
+[^14]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 \begin{longtable}[]{@{}rrrr@{}}
-\caption{The probabilities that a best-of-11 series lasts $r$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\caption{The observed proportion of series $\Phi(r)$ ending in $r$ rounds in CoD SnD's best-of-11 format, compared to the expected proportion $\hat{\Phi}_0(r)$ the naive assumption $\phi_0 = 0.5$ and the expected proportion $\hat{\Phi}_2(r)$ under the maximum likelihood estimate $\phi_2 = 0.575$ for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
-$r$ & $p_0(r)$ = 0.5 & $p_2(r)$ = 0.575 & $P_O(r)$ \\
+$r$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 & $\Phi(r)$ \\
 \midrule()
@@
 ```
-It is fair to conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $p$ ($\approx 0.575$).
+Observing that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (especially in comparison to $\hat{\Phi}_0(r)$), along with the null hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results}, it is fair to conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
 
@@
 #| label: cod_round_win_prop_after_k_wins
-## http://keyonvafa.com/hot-hand/
-get_post_streak_prob <- function(n, k, p = 0.5) {
-  tosses <- rbinom(n, 1, p)
-  runs <- rle(tosses)
-  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
-  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
-
-  ## edge case
-  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
-    n_neg_after <- n_neg_after - 1
-  }
-
-  n_pos_after / (n_pos_after + n_neg_after)
-}
-
-simulate_post_streak_prob <- function(sims = 10000, seed = 42, ...) {
-  withr::local_seed(seed)
-  rerun(
-    sims,
-    get_post_streak_prob(...)
-  ) |> 
-    flatten_dbl() |> 
-    mean(na.rm = TRUE)
-}
-
 cod_round_streaks <- cod_rounds |> 
@@
     drop_na(!!!col_syms) |> 
-    count(n_rounds, ..., win_series, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+    count(n_rounds, win_series, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
 
@@
       ungroup() |> 
-      filter(win_round) |> 
-      select(n_rounds, ..., win_series, n, total, prop) |> 
-      arrange(n_rounds, ...) |> 
+      # filter(win_round) |> 
+      select(n_rounds, win_round, win_series, n, total, prop) |> 
+      arrange(n_rounds, win_round) |> 
       inner_join(
@@
   cod_round_win_prop_after_z_with_probs |> 
-    nest(data = -c(n_rounds, win_series, ...)) |> 
+    nest(data = -c(n_rounds, win_series, win_round)) |> 
     mutate(
@@
         ~binom.test(.x$n, .x$total, .x$prior_p, alternative = 'greater') |> 
-          broom::tidy() |>
-          pull(p.value)
-      ),
-      lt_p_value = map_dbl(
-        data, 
-        ~binom.test(.x$n, .x$total, .x$prior_p, alternative = 'less') |> 
           broom::tidy() |>
@@
       ),
-      lt_p_value_adj = map_dbl(
-        data, 
-        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'less') |> 
-          broom::tidy() |>
-          pull(p.value)
-      ),
       gt_is_signif = gt_p_value <= 0.05,
-      lt_is_signif = lt_p_value <= 0.05,
-      gt_is_signif_adj = gt_p_value_adj <= 0.05,
-      lt_is_signif_adj = lt_p_value_adj <= 0.05
+      gt_is_signif_adj = gt_p_value_adj <= 0.05
     ) |> 
@@
     n_rounds = 7L:11L,
-    win_series = c(TRUE, FALSE)
+    win_series = c(TRUE, FALSE),
+    win_round = c(TRUE, FALSE)
   ) |> 
@@
     mutate(
+      naive_p = ifelse(win_series, 6L / n_rounds, (n_rounds - 6L) / n_rounds),
       prior_p = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
+      across(c(naive_p, prior_p), ~ifelse(win_round, .x, 1 - .x)),
       expected_poststreak_p = map2_dbl(
-        n_rounds, prior_p, 
+        n_rounds, naive_p, 
         ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on round win percentages in rounds immediately following streaks of three wins.[^16] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $\hat{P}^{kr,\text{win}}_O$ and $\hat{P}^{kr,\text{loss}}_O$ for $k = 3$ streaks respectively.
-
-[^16]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
-
-TODO: Put p-value in parentheses
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^15] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $P^{w,kr}$ and $P^{l,kr}$ for round win rate and loss rate following $k = 3$ round win streaks respectively.
+
+[^15]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
 
@@
 \multicolumn{7}{c}{\text{3 round win streak}} \\
- &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
-\cmidrule(lr){4-5} \cmidrule(lr){6-7}
-$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ & $p$-value \\ 
+$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ \\ 
 \midrule
-7 & 209 & $75\%$ & $75\%$ & 0.58 & $61\%$ & <=0.01 \\ 
-8 & 209 & $62\%$ & $60\%$ & 0.28 & $45\%$ & <=0.01 \\ 
-9 & 193 & $52\%$ & $50\%$ & 0.33 & $35\%$ & <=0.01 \\ 
-10 & 151 & $44\%$ & $43\%$ & 0.45 & $29\%$ & <=0.01 \\ 
-11 & 150 & $40\%$ & $38\%$ & 0.29 & $25\%$ & <=0.01 \\ 
+7 & 209 & $75\%$ & $75\%$ (0.58) & $61\%$ (<=0.01) \\
+8 & 209 & $62\%$ & $60\%$ (0.28) & $45\%$ (<=0.01) \\
+9 & 193 & $52\%$ & $50\%$ (0.33) & $35\%$ (<=0.01) \\
+10 & 151 & $44\%$ & $43\%$ (0.45) & $29\%$ (<=0.01) \\
+11 & 150 & $40\%$ & $38\%$ (0.29) & $25\%$ (<=0.01) \\
 \toprule
 \multicolumn{7}{c}{\text{3 round loss streak}} \\
- &  &  & \multicolumn{2}{c}{\text{Unadjusted}} & \multicolumn{2}{c}{\text{Adjusted}} \\ 
-\cmidrule(lr){4-5} \cmidrule(lr){6-7}
-$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ &  $p$-value & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ & $p$-value \\ 
+$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ \\ 
 \midrule
-10 & 60 & $13\%$ & $14\%$ & 0.64 & $10\%$ & 0.26 \\ 
-11 & 129 & $24\%$ & $25\%$ & 0.63 & $16\%$ & <=0.01 \\ 
+10 & 60 & $13\%$ & $14\%$ (0.64) & $10\%$ (0.26) \\ 
+11 & 129 & $24\%$ & $25\%$ (0.63) & $16\%$ (<=0.01) \\ 
 \bottomrule

### 2022-08-19 paper/paper.tex
ALL THE SYMBOL CHANGES

@@
 in a series of a professional sport. Most assume a constant probability
-\(p\) of a given team winning a game in the series, regardless of the
+\(\phi\) of a given team winning a game in the series, regardless of the
 series state. Mosteller (1952) observed that the American League had
@@
 Series matchups, implying that matchups should not modeled with
-\(p = 0.5\). Mosteller proposed three approaches for identifying the
+\(\phi = 0.5\). Mosteller proposed three approaches for identifying the
 optimal constant probability value of the stronger team in the World
-Series, finding \(p \approx 0.65\). in each case: (1) solving for \(p\)
-from the empirical average number of games won by the loser of the
+Series, finding \(\phi \approx 0.65\). in each case: (1) solving for
+\(p\) from the empirical average number of games won by the loser of the
 series, which he called the ``method of moments'' approach; (2)
@@
 across the series (i.e.~maximum likelihood), and (3) minimizing the
-chi-square goodness of fit statistic for \(p\).
+chi-square goodness of fit statistic for \(\phi\).
 
 Chance (2020) re-examines the constant probability notion in Major
-League Baseball's World Series (1923--2018), the National Basketball
-Association's Finals (1951--2018), and the National Hockey League's
-Stanley Cup (1939--2018). Chance finds strong evidence against the null
-hypothesis of \(p = 0.5\) in the MLB and NHL championship series when
-applying Mosteller's first and second methods.{[}\^{}8{]} {[}\^{}8{]}:
-Chance goes on to outline a conditional probability framework
+League Baseball's (MLB) World Series (1923--2018), the National
+Basketball Association's (NBA) Finals (1951--2018), and the National
+Hockey League's (NHL) Stanley Cup (1939--2018). Chance finds strong
+evidence against the null hypothesis of \(\phi = 0.5\) in the MLB and
+NHL championship series when applying Mosteller's first and second
+methods. Chance goes on to outline a conditional probability framework
 (likelihood of winning a game given the series state) which can exactly
@@
 Studying both player streaks and team streaks in basketball, in both
-observational and controlled settings. Gilovich et al. (1985) do not
-find evidence for the hot hand phenomenon. However, Miller and Sanjurjo
-(2018) refuted the conclusions of Gilovich et al., proving a framework
-for quantifying streak selection bias, which effectively works in the
-manner posited by the gambler's fallacy\footnote{Streak selection bias,
-  ``in conjunction with a quasi-Bayesian model of decision making under
-  sample size neglect\ldots{} provides a novel structural candidate
-  explanationfor the persistence of gambler's fallacy beliefs'', per
-  Miller and Sanjurjo (2018).}. Specifically, Miller and Sanjurjo say
-that a ``bias exists in a common measure of the conditional dependence
-of present outcomes on streaks of past outcomes in sequential data''
-implying that, under i.i.d. conditions, ``the proportion of successes
-among the outcomes that immediately follow a streak of consecutive
-successes is expected to be strictly less than the underlying
-(conditional) probability of success''. When applying streak selection
-bias to Giloveih et al.'s data, Miller and Sanjurjo come to the opposite
-conclusions as Giloveih et al.
+observational and controlled settings. Gilovich et al. (1985),
+henceforth GVT, do not find evidence for the hot hand phenomenon.
+However, Miller and Sanjurjo (2018), henceforth MS, refuted the
+conclusions of GVT, proving a framework for quantifying streak selection
+bias, which effectively works in the manner posited by the gambler's
+fallacy\footnote{Streak selection bias, ``in conjunction with a
+  quasi-Bayesian model of decision making under sample size
+  neglect\ldots{} provides a novel structural candidate explanation for
+  the persistence of gambler's fallacy beliefs'', per MS (2018).}.
+Specifically, MS say that a ``bias exists in a common measure of the
+conditional dependence of present outcomes on streaks of past outcomes
+in sequential data'' implying that, under i.i.d. conditions, ``the
+proportion of successes among the outcomes that immediately follow a
+streak of consecutive successes is expected to be strictly less than the
+underlying (conditional) probability of success''. When applying streak
+selection bias to GVT.'s data, MS come to the opposite conclusions as
+GVT.
 
@@
 aspects that can create clear advantages on side in a given round, given
-how prior rounds played out.\footnote{Additionally, both Counter-Strike
-  and Valorant have overtime rules and blocked offensive/defensive roles
-  (i.e.~playing either offense or defense for many consecutive rounds).}
+how prior rounds played out.
+
+Additionally, both Counter-Strike and Valorant have overtime rules and
+blocked offensive/defensive roles (i.e.~playing either offense or
+defense for many consecutive rounds). On the other hand, teams in CoD
+SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for
+home advantage in best-of-seven series for professional sports like the
+MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1 is not used today in these
+  leagues, but it was at least one in each league.} While theoretically
+one might be able to account for any kind of balanced rotation, such as
+a ``blocky'' on like a 5-5-1, the rotation of team sides every round is
+convenient, particularly for convincing ourselves that rounds could
+reasonably be modeled as i.i.d. Bernoulli trials.
 
@@
 
-The general formula for the probability \(P_E(r)\) that a best-of-\(s\)
-series (\(s = 11\) for CoD SnD) lasts \(r\) rounds given constant
-probability \(p\) of one team\footnote{If \(p > 0.5\), then one might
-  say that this team is the better team (known in hindsight).} winning
-each round is
+The formula for the expected proportion of seriesn a best-of-\(s\)
+format (\(s = 11\) rounds for CoD SnD), ending in \(r\) rounds
+(\(r \leq s\)), \(\hat{\Phi}(r)\), for a constant round win probability
+\(\phi\) (\(0 \leq \phi \leq 1\)) for one team\footnote{If
+  \(\phi > 0.5\), then one might say that this team is the better team
+  (known in hindsight).} is
 
@@
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
-P_E(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(p^{m}(1 - p)^{r - m} + p^{r - m}(1 - p)^m).
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m).
 }\label{eq:series-length}\end{equation}
 
-The chi-square goodness of fit statistic can be used to test the
-constant found probability hypothesis for \(0 \leq p \leq 1\).
+To evaluate the constant round win probability hypothesis--that is, that
+the expected and observed round win rates, \(\hat{\Phi}(r)\) and
+\(\Phi(r)\) respectively, are equal to one another--we can compute the
+chi-square goodness of fit statistic, \(\chi^2\).
 
 \begin{equation}\protect\hypertarget{eq:chi-squ}{}{
-\chi^2 = \sum^R \frac{(P_O(r) - P_E(r))^2}{P_E(r)}
+\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
 }\label{eq:chi-squ}\end{equation}
 
-For CoD SnD, \(r \in R [6, 7, 8, 9, 10, 11]\).
+For CoD SnD, \(r \in R = [6, 7, 8, 9, 10, 11]\).
 
@@
 
-Without accounting for the streak selection bias described by Miller and
-Sanjurjo (2018), the round win probability after a streak of \(k\) round
-wins for a best-of-\(s\) series (\(s = 11\) for CoD SnD), accounting for
-the series lasting \(r\) rounds known in hindsight, is
+When considering momentum in consecutive rounds wins, I use the
+descriptor ``hindsight'' because I account for the length of the series
+(\(r\) rounds). Without accounting for the streak selection bias
+described by MS (2018), the ``hindsight'' Bernoulli round win
+probability immediately following a streak of \(k\) round wins for a
+best-of-\(s\) series, \(p^{w|kr}\), is
 
@@
 
-The ``hindsight'' round loss probability after a streak of \(k\) round
-losses for a series lasting \(r\) rounds, \(p^{l|kr}\), can be
-formulated symmetrically.\footnote{Note that these probabilities are
-  separate from the constant round probabilities in Sections
-  \ref{sec:method-rounds-played} and \ref{sec:results-rounds-played}.}
+The hindsight Bernoulli round loss probability after a streak of \(k\)
+round wins, \(p^{l|kr}\), can be formulated symmetrically.
 
-However, as shown by Miller and Sanjurjo, we should expect the observed
-proportion of rounds wins after a streak \(k\) rounds wins for a series
-lasting \(r\) rounds, \(\hat{P}_{w|kr}\), to be strictly less than
-\(p^{w|kr}\).
+However, as shown by MS, we should expect the proportion of rounds wins
+immediately following a streak \(k\) rounds wins for a series lasting
+\(r\) rounds, \(\hat{P}^{w|kr}\), to be strictly less than
+\(p^{w|kr}\).\footnote{See Appendix E.1 of MS (2018) for details on the
+  proof that follows.}
 
@@
 
-Miller and Sanjurjo (2018) note that there does not exists a closed form
-representation for
-\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\) for
-\(k > 1\).
+MS (2018) note that there does not exists a closed form representation
+for \(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\)
+(\(\hat{P}_k(\mathbf{X})\) is the analogue for \(\hat{P}^{w|kr}\) in my
+CoD SnD notation), for \(k > 1\). Figure 1 shows how the expected value
+varies as a function of the total number of trials \(n\), given \(p\)
+and \(k > 1\).\footnote{I've adapted the code from Vafa (2017), which
+  implements MS's framework (2018).}
+
+\begin{figure}
+\centering
+\includegraphics{images/npkd.png}
+\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $p = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
+\end{figure}
 
@@
 closely related to mine, and, in fact, provides a guide for this
-investigation.
+investigation. Afterwards, I investigate post-streak win rates and the
+context of momentum, leveraging MS's (2018) framework for streak
+selection bias.
 
@@
 
-Using Equation \ref{eq:chi-squ}, \(\chi^2 = 16.0\) (p-value of 0.0068)
-for a naive constant round win probability \(p_0 = 0.5\). Thus, I can
-comfortably reject the constant probability null hypothesis for
-\(p_0 = 0.5\), even at a confidence level of \(\alpha = 0.01\).
-Afterwards, I investigate post-streak win rates, building on my
-learnings from the constant probability assumption analysis. I agree
-with Miller and Sanjurjo's (2018) framework for streak selection bias,
-accounting for it in when analyzing momentum.
+Using Equation \ref{eq:chi-squ}, I find that \(\chi^2 = 16.0\) (p-value
+of 0.0068) for the naive constant round win probability
+\(\phi_0 = 0.5\). Thus, I can comfortably reject the constant
+probability null hypothesis for \(\phi_0 = 0.5\), even at a confidence
+level of \(\alpha = 0.01\).
 
 Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected
-probabilities for \(s = 11\) under the naive assumption that
-\(p_0 = 0.5\) for a given round, along with the observed proportions
-\(P_O(r)\) in CoD SnD.
+series lasting \(r\) rounds, \(\hat{\Phi}_0(r)\) (under the assumption
+\(\phi_0 = 0.5\)), for \(s = 11\), along with the observed proportions,
+\(\Phi(r)\), in CoD SnD.
 
 \begin{longtable}{rrrr}
-\caption{The probabilities that a best-of-11 series lasts $r$ rounds ($P_E(r)$, where $r \in [6, 7, 8, 9, 10, 11]$) under the assumption that each team has a 50\% probability ($p_0 = 0.5$) of winning each game.
-The observed frequencies observed are shown as a count $N_O(r)$ and as a proportion $P_O(r)$ of all series.}\label{tbl:cod-prob-series-lasting-r-rounds} \\
+\caption{The expected proportion of series lasting $r$ rounds ($\hat{\Phi}_0(r)$) in a best-of-11 format, wehre $r \in R = [6, 7, 8, 9, 10, 11]$ under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
+The observed frequencies for CoD SnD are shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^R N(r)$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
 \toprule
-&  & \multicolumn{2}{c}{Observed} \\ 
-\cmidrule(lr){3-4}
-$r$ & $P_E(r)$ & $P_O(r)$ & $N_O(r)$ \\ 
+$r$ & $\hat{\Phi}_0(r)$ & $\Phi(r)$ & $N(r)$ \\ 
 \midrule
@@
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for
-the constant round win probability \(p\) that I find when applying the
-three methods suggested by Mosteller (1952). Each is approximately or
-equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each
-results in a \(\chi^2\) value for which I cannot reject the constant
-probability null hypothesis.
+the constant round win probability that I find when applying the three
+methods suggested by Mosteller (1952). Each is approximately or equal to
+0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a
+\(\chi^2\) value for which I cannot reject the constant probability null
+hypothesis.
 
 \begin{longtable}[]{@{}lrr@{}}
-\caption{Alternate estimates of the constant probability \(p\) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive \(p = 0.5\).}\label{tbl:mosteller-methods-results} \\
+\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
 \toprule()
-Method & \(p(r)\) & \(\chi^2\) (p-value) \\
+Method & $\phi$ & $\chi^2$ (p-value) \\
 \midrule()
@@
 Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
-\(P_E(r)\) when re-applying Equation \ref{eq:series-length} for the
-maximum likelihood estimate \(p_2 = 0.575\).\footnote{The method of
-  moments and minimum \(\chi^2\) estimates for \(p\) are omitted simply
-  because the results would be nearly identical to those for the maximum
-  likelihood estimate of \(p\) (since they are all \(\approx 0.575\)).}
-I observe that \(P_E(r)\) is notably larger for \(p_{2}\) when
-\(r \in [6, 7]\), more closely matching \(P_O(r)\). \(p_{2}\) is also
-closer to \(P_O(r)\) for \(r \in [9, 10]\), although not for
-\(r \in [8, 11]\).
+\(\hat{\Phi}(r)\) when re-applying Equation \ref{eq:series-length} for
+the maximum likelihood estimate \(\phi_2 = 0.575\), resulting in a new
+set of expected proportions of series lasting \(r\) rounds
+\(\hat{\Phi}_2(r)\).\footnote{The method of moments and minimum
+  \(\chi^2\) estimates for \(\phi\) are omitted simply because the
+  results would be nearly identical to those for the maximum likelihood
+  estimate of \(\phi\) (since they are all \(\approx 0.575\)).} I
+observe that \(\hat{\Phi}_2(r)\) is larger than \(\hat{\Phi}_0(r)\) for
+\(r \in [6, 7]\), more closely matching \(\Phi(r)\). \(\hat{\Phi}_2(r)\)
+is also closer to the observed \(\Phi(r)\) for \(r \in [9, 10]\),
+although not for \(r \in [8, 11]\).
 
 \begin{longtable}[]{@{}rrrr@{}}
-\caption{The probabilities that a best-of-11 series lasts $r$ rounds under the naive assumption $p_0 = 0.5$ and the maximum likelihood estimation $p_2 = 0.575$.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\caption{The observed proportion of series $\Phi(r)$ ending in $r$ rounds in CoD SnD's best-of-11 format, compared to the expected proportion $\hat{\Phi}_0(r)$ the naive assumption $\phi_0 = 0.5$ and the expected proportion $\hat{\Phi}_2(r)$ under the maximum likelihood estimate $\phi_2 = 0.575$ for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
-$r$ & $p_0(r)$ = 0.5 & $p_2(r)$ = 0.575 & $P_O(r)$ \\
+$r$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 & $\Phi(r)$ \\
 \midrule()
@@
 
-It is fair to conclude that the constant round win probability
+Observing that \(\hat{\Phi}_2(r)\) reasonably matches \(\Phi(r)\)
+(especially in comparison to \(\hat{\Phi}_0(r)\)), along with the null
+hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results},
+it is fair to conclude that the constant round win probability
 assumption can be valid in CoD SnD series with the appropriate choice of
-\(p\) (\(\approx 0.575\)).
+\(\phi\) (\(\approx 0.575\)).
 
@@
 third success (or failure) at minimum (Carlson and Shu 2007), I focus on
-round win percentages in rounds immediately following streaks of three
-wins.\footnote{Three happens to also be a reasonable number for series
-  that lasts at maximum 11 rounds.} Table
-\ref{tbl:cod-round-win-prop-after-k-wins} shows
-\(\hat{P}^{kr,\text{win}}_O\) and \(\hat{P}^{kr,\text{loss}}_O\) for
-\(k = 3\) streaks respectively.
-
-TODO: Put p-value in parentheses
+streaks of three round wins.\footnote{Three happens to also be a
+  reasonable number for series that lasts at maximum 11 rounds.} Table
+\ref{tbl:cod-round-win-prop-after-k-wins} shows \(P^{w,kr}\) and
+\(P^{l,kr}\) for round win rate and loss rate following \(k = 3\) round
+win streaks respectively.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-vafa2017}{}}%
+Vafa, Keyon. 2017. {``Is the Hot Hand Fallacy a Fallacy?''}
+\url{https://keyonvafa.github.io/hot-hand/}.
+
 \leavevmode\vadjust pre{\hypertarget{ref-xenopoulos2022}{}}%

### 2022-08-20 paper/paper.Rmd
working thru p_ms

@@
 
-The hindsight Bernoulli round loss probability after a streak of $k$ round wins, $p^{l|kr}_0$, can be formulated symmetrically. We might consider these as a reference when considering the
-
 Removing our knowledge of a streak, we might model the Bernoulli round win probability as
@@
 ```
+The Bernoulli round loss probability after a streak of $k$ round wins, $p^{\ell|kr}_0$, can be formulated symmetrically.
+
 As shown by MS, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^12]
@@
 
-> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < p < 1$*.
-Let* $\hat{P}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
-\hat{P}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
-In particular,* $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.$
-
-MS note that there does not exists a closed form representation for $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ for $k > 1$.
-($\hat{P}_k(\mathbf{X})$ is the analogue for $\hat{P}^{w|kr}_{MS}$ in my notation for CoD SnD.) Figure 1 shows how the expected value varies as a function of the total number of trials $n$, given $p$ and $k > 1$.[^13]
+> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < \pi < 1$*.
+Let* $\hat{\Pi}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{\Pi}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
+\hat{\Pi}_k$ *is a biased estimate of* $\mathbb{\Pi}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
+In particular,* $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < \pi.$
+
+MS note that there does not exists a closed form representation for $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ for $k > 1$.
+($\hat{\Pi}_k(\mathbf{X})$ is the analogue for $\hat{P}^{w|kr}_{MS}$ in my notation for CoD SnD.) Figure 1 shows how the expected value varies as a function of the total number of trials $n$, given $\pi$ and $k > 1$.[^13]
 
@@
 # library(ggplot2)
-# set.seed(42)
-# runs <- rerun(
-#   1000,
-#   crossing(
-#     n = 1:50,
-#     k = 2:4,
-#     p = 0.5
-#   ) |>
-#     mutate(
-#       next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2, p = ..3))
-#     )
-# ) |>
-#   reduce(bind_rows)
+# library(latex2exp)
+# # set.seed(42)
+# # runs <- rerun(
+# #   1000,
+# #   crossing(
+# #     n = 1:50,
+# #     k = 2:4,
+# #     p = 0.5
+# #   ) |>
+# #     mutate(
+# #       next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2, p = ..3))
+# #     )
+# # ) |>
+# #   reduce(bind_rows)
+# # qs::qsave(runs, 'data/runs_1000x1000_nkp.qs')
+# runs <- qs::qread('data/runs_1000x1000_nkp.qs')
 # 
@@
 # )
+# 
 # p <- agg_runs |>
@@
 #     color = guide_legend(
+#       title = 'streak length (k)',
 #       title.hjust = 0.5,
@@
 #   geom_hline(aes(yintercept = p)) +
-#   labs(x = 'n', y = 'p') +
+#   labs(x = 'number of trials (n)', y = expression('post-streak probability of success'~(pi))) +
 #   theme(
@@
 #   )
+# p
 # 
@@
 #   p,
-#   filename = 'paper/images/npkd.png', 
+#   filename = 'paper/images/pwkr_ms.png',
 #   width = 5.5,
@@
 \centering
-\includegraphics{images/npkd.png}
-\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $p = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
+\includegraphics{images/pwkr_ms.png}
+\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $\pi = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
 \end{figure}
@@
 
-Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{l|kr}$, as performed by GVT and MS to evaluate their respective hypothesis regarding $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ (Theorem 1), is not appropriate.
+Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{\ell|kr}$, as performed by GVT and MS to evaluate their respective hypothesis regarding $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ (Theorem 1), is not appropriate.
 
@@
 The Bernoulli round win probability underlying $\hat{P}^{w|kr}_0$ is
-
-~~When considering momentum in consecutive rounds wins, I use the descriptor "hindsight" because I account for the length of the series (~~$r$ rounds).
 
@@
 ```
-A binomial test for the observed proportion of round wins following streaks of $k$ round wins in a series lasting $r$ rounds, $P^{w|kr}$, assuming $p_0^{w|kr}$ as the probability of success, can be used to verify that $p_0^{w|kr}$ is reasonable as a reference.
+A binomial test for the expected proportion of round wins following streaks of $k$ round wins in a series lasting $r$ rounds, $\hat{P}^{w|kr}_0$, assuming $p^{w|kr}_0$ as the probability of success, can be used to verify that $\hat{P}^{w|kr}_0$ is reasonable as to use as a baseline with which to compare $\hat{P}^{w|kr}_{MS}$.
+If the binomial test shows that we cannot reject the null hypothesis that the expected $\hat{P}^{w|kr}_0$ is different from the observed proportion $P^{w|kr}$.
 
@@
       ungroup() |> 
-      # filter(win_round) |> 
       select(n_rounds, win_round, win_series, n, total, prop) |> 
@@
 
+  suppressMessages(
+    full_join(
       cod_round_win_prop_after_z_with_probs |> 
@@
         mutate(
-      gt_p_value = map_dbl(
+          ## TODO: Vectorize this.
+          binom_p_value = map_dbl(
             data, 
-        ~binom.test(.x$n, .x$total, .x$prior_p, alternative = 'greater') |> 
+            ~binom.test(.x$n, .x$total, .x$notional_prop, alternative = 'greater') |> 
               broom::tidy() |>
@@
           ),
-      gt_p_value_adj = map_dbl(
-        data, 
-        ~binom.test(.x$n, .x$total, .x$expected_poststreak_p, alternative = 'greater') |> 
-          broom::tidy() |>
-          pull(p.value)
-      ),
-      gt_is_signif = gt_p_value <= 0.05,
-      gt_is_signif_adj = gt_p_value_adj <= 0.05
-    ) |> 
-    unnest(data)
+          binom_is_signif = binom_p_value <= 0.05
+        ) |> 
+        unnest(data),
+      cod_round_win_prop_after_z_with_probs |> 
+        select(n_rounds, win_round, win_series, n, total, prop, notional_prop) |> 
+        mutate(
+          notional_n = as.integer(n * notional_prop / prop),
+          notional_total = as.integer(total * notional_prop / prop), 
+          compared_p_value = vectorized_prop_test(n, total, notional_n, notional_total)$p.value,
+          compared_is_signif = compared_p_value <= 0.05
+        )
+    )
+  )
 }
@@
         win_series ~ TRUE,
-        (n_rounds - !!k - 6L) > 0L ~ TRUE,
+        (n_rounds - !!k - 6L) >= 0L ~ TRUE,
         TRUE ~ FALSE
@@
     mutate(
-      naive_p = ifelse(win_series, 6L / n_rounds, (n_rounds - 6L) / n_rounds),
-      prior_p = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
-      across(c(naive_p, prior_p), ~ifelse(win_round, .x, 1 - .x)),
-      expected_poststreak_p = map2_dbl(
-        n_rounds, naive_p, 
+      naive_prop = ifelse(win_series, 6L / n_rounds, (n_rounds - 6L) / n_rounds),
+      notional_prop = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
+      across(c(naive_prop, notional_prop), ~ifelse(win_round, .x, 1 - .x)),
+      ms_prop = map2_dbl(
+        n_rounds, naive_prop, 
         ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
-      )
-    )
+      ),
+      diff_prop = notional_prop - ms_prop
+    ) |> 
+    filter(notional_prop > 0, notional_prop < 1)
 
@@
 
-cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:4L) |>
+cod_round_win_prop_after_k_wins <- tibble(win_streak = 3L) |>
   mutate(
@@
         .x <= 0.01 ~ '<=0.01', 
-        round(.x, 2) == 1 ~ '1',
+        round(.x, 2) == 1 ~ '1.00',
         TRUE ~ as.character(round(.x, 2))
@@
     ),
-    unadj_lab = sprintf('%.0f%%', round(100 * prior_p), gt_p_value),
-    adj_lab = sprintf('%.0f%%', round(100 * expected_poststreak_p), gt_p_value_adj)
-  ) |>
-  filter(win_streak == 3, !win_series) |> 
+    prop_lab = scales::percent(prop, accuracy = 0.1),
+    binom_lab = sprintf('%.1f%% (%s)', round(100 * notional_prop, 1), binom_p_value),
+    compared_lab = scales::percent(ms_prop, accuracy = 0.1),
+    diff_lab = sprintf('%.1f%% (%s)', round(100 * diff_prop, 1), compared_p_value)
+  ) |>
   arrange(win_streak, n_rounds, win_series) |> 
   transmute(
-    # win_streak,
+    win_series,
+    win_round,
     n_rounds,
-    # across(win_series, ~ifelse(.x, 'win', 'lose')),
     total,
-    prop,
-    unadj_lab,
-    adj_lab
+    prop_lab,
+    binom_lab,
+    compared_lab,
+    diff_lab
+  ) |>
+  group_split(win_series, win_round) |> 
+  walk(
+    function(df) {
+      message(sprintf('win_round=%s, win_series=%s', df$win_round[[1]], df$win_series[[1]]))
+      df <- df |> 
+        select(
+          -c(win_series, win_round)
         ) |> 
@@
           total = 'N',
-    prop = 'O',
-    unadj_lab = 'a',
-    adj_lab = 'b'
-  ) |> 
-  gt::tab_spanner(
-    label = 'x',
-    columns = c(prior_p, gt_p_value)
-  ) |> 
-  gt::tab_spanner(
-    label = 'y',
-    columns = c(expected_poststreak_p, gt_p_value_adj)
-  ) |> 
-  gt::as_latex()
-```
-
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^15] Table \ref{tbl:cod-round-win-prop-after-k-wins} shows $P^{w,kr}$ and $P^{l,kr}$ for round win rate and loss rate following $k = 3$ round win streaks respectively.
+          prop_lab = 'O',
+          binom_lab = 'a',
+          compared_lab = 'b',
+          diff_lab = 'c'
+        ) |> 
+        gt::as_latex() |> 
+        cat()
+    }
+  )
+
+```
+
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^15] Table \ref{tbl:cod-pw3r-pl3r} shows $P^{w,kr}$ and $P^{l,kr}$ for round win rate and loss rate following $k = 3$ round win streaks respectively.
 
 [^15]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+
+First,
 
@@
 \begin{longtable}{rrrrrrr}
-\caption{First, observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round win streak, for a series lasting $r$ rounds.
-Second, observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round loss streak}\label{tbl:cod-round-win-prop-after-k-wins} \\
+\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, in series lasting $r$ rounds.
+Additionally, notional expected proportion, $\hat{P}^{w|kr}_0$ and binomial test p-value, assuming notional round probability $p^{w|kr}$ and using observed counts; MS expected proportion $\hat{P}^{w|kr}_{MS}$; and $\hat{D}^{w|kr} = \hat{P}^{w|kr}_{MS} - \hat{P}^{w|kr}_0$ and proportion test p-value.
+Fields presented in groups, split by whether the team won the round immediately following the 3-round win streak, and whether the team won the series.
+The post-streak loss analogues are presented as $N^{\ell|kr}$, $P^{\ell|kr}$, $\hat{P}^{\ell|kr}_0$, $\hat{P}^{\ell|kr}_{MS}$, and $\hat{D}^{\ell|kr}$.}
+\label{tbl:cod-pw3r-pl3r} \\
 \toprule
-\multicolumn{7}{c}{\text{3 round win streak}} \\
-$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ \\ 
+\multicolumn{6}{c}{\text{win series, win after 3-round win streak}} \\
 \midrule
-7 & 209 & $75\%$ & $75\%$ (0.58) & $61\%$ (<=0.01) \\
-8 & 209 & $62\%$ & $60\%$ (0.28) & $45\%$ (<=0.01) \\
-9 & 193 & $52\%$ & $50\%$ (0.33) & $35\%$ (<=0.01) \\
-10 & 151 & $44\%$ & $43\%$ (0.45) & $29\%$ (<=0.01) \\
-11 & 150 & $40\%$ & $38\%$ (0.29) & $25\%$ (<=0.01) \\
+$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
+\midrule
+7 & 209 & 74.6\% & 75.0\% (0.58) & 75.7\% & -0.7\% (0.94) \\ 
+8 & 209 & 62.2\% & 60.0\% (0.28) & 61.9\% & -1.9\% (1.00) \\ 
+9 & 193 & 51.8\% & 50.0\% (0.33) & 52.7\% & -2.7\% (0.97) \\ 
+10 & 151 & 43.7\% & 42.9\% (0.45) & 44.7\% & -1.8\% (0.94) \\ 
+11 & 150 & 40.0\% & 37.5\% (0.29) & 38.8\% & -1.3\% (1.00) \\ 
 \toprule
-\multicolumn{7}{c}{\text{3 round loss streak}} \\
-$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ \\ 
+\toprule
+\multicolumn{6}{c}{\text{lose series, win after 3-round win streak}} \\
 \midrule
-10 & 60 & $13\%$ & $14\%$ (0.64) & $10\%$ (0.26) \\ 
-11 & 129 & $24\%$ & $25\%$ (0.63) & $16\%$ (<=0.01) \\ 
+$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
+\midrule
+10 & 60 & 13.3\% & 14.3\% (0.64) & 26.7\% & -12.4\% (1.00) \\ 
+11 & 129 & 24.0\% & 25.0\% (0.63) & 30.8\% & -5.8\% (0.98) \\ 
+\toprule
+\toprule
+\multicolumn{6}{c}{\text{win series, lose after 3-round win streak}} \\
+\midrule
+$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
+\midrule
+7 & 209 & 25.4\% & 25.0\% (0.48) & 6.4\% & 18.6\% (0.98) \\ 
+8 & 209 & 37.8\% & 40.0\% (0.76) & 14.7\% & 25.3\% (0.96) \\ 
+9 & 193 & 48.2\% & 50.0\% (0.72) & 22.2\% & 27.8\% (0.97) \\ 
+10 & 151 & 56.3\% & 57.1\% (0.62) & 26.7\% & 30.5\% (0.99) \\ 
+11 & 150 & 60.0\% & 62.5\% (0.76) & 30.8\% & 31.7\% (0.95) \\ 
+\toprule
+\toprule
+\multicolumn{6}{c}{\text{lose series, lose after 3-round win streak}} \\
+\midrule
+$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
+\midrule
+10 & 60 & 86.7\% & 85.7\% (0.51) & 44.7\% & 41.1\% (1.00) \\ 
+11 & 129 & 76.0\% & 75.0\% (0.45) & 38.8\% & 36.2\% (0.95) \\ 
 \bottomrule
@@
 :::
-
-# Appendix {.unnumbered}

### 2022-08-20 paper/paper.tex
working thru p_ms

@@
   neglect\ldots{} provides a novel structural candidate explanation for
-  the persistence of gambler's fallacy beliefs'', per MS (2018).}.
+  the persistence of gambler's fallacy beliefs'', per MS.}.
 Specifically, MS say that a ``bias exists in a common measure of the
@@
 
+\begin{equation}\protect\hypertarget{eq:m}{}{
+m = \frac{s + 1}{2}
+}\label{eq:m}\end{equation}
+
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
@@
 
-When considering momentum in consecutive rounds wins, I use the
-descriptor ``hindsight'' because I account for the length of the series
-(\(r\) rounds). Without accounting for the streak selection bias
-described by MS (2018), the ``hindsight'' Bernoulli round win
-probability immediately following a streak of \(k\) round wins for a
-best-of-\(s\) series, \(p^{w|kr}\), is
+Removing our knowledge of a streak, we might model the Bernoulli round
+win probability as
 
-\[
-m = \frac{s + 1}{2}
-\]
+\begin{equation}\protect\hypertarget{eq:pwr}{}{
+p^{w|r} = p(\text{win | r})=\{
+\begin{array}{cl}
+\frac{m}{r}, & \text{team wins series} \\
+\frac{r - m}{r}, & \text{team loses series}
+\end{array}.
+}
+\label{eq:pwr}
+\end{equation}
+
+The Bernoulli round loss probability after a streak of \(k\) round wins,
+\(p^{\ell|kr}_0\), can be formulated symmetrically.
+
+As shown by MS, we should expect the proportion of rounds wins
+immediately following a streak of \(k\) rounds wins for a series lasting
+\(r\) rounds, \(\hat{P}^{w|kr}_{MS}\), to be strictly less than
+\(p^{w|r}\).\footnote{See Appendix E.1 of MS for details on the proof
+  that follows.}
+
+\begin{quote}
+Theorem 1: \emph{Let}
+\(\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3\)\emph{, be a sequence of
+independent Bernoulli trials, each with probability of success}
+\(0 < \pi < 1\)\emph{. Let} \(\hat{\Pi}_k(\mathbf{X})\) \emph{be the
+proportion of successes on the subset of trials} \(I_k(\mathbf{X})\)
+\emph{that immediately follow} \(k\) consecutive successes, that is,
+\(\hat{\Pi}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |. \hat{\Pi}_k\)
+\emph{is a biased estimate of}
+\(\mathbb{\Pi}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p\)
+\emph{for all} \(k\) \emph{such that} \(1 \leq k \leq n - 2\)\emph{. In
+particular,}
+\(E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < \pi.\)
+\end{quote}
+
+MS note that there does not exists a closed form representation for
+\(E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\) for
+\(k > 1\). (\(\hat{\Pi}_k(\mathbf{X})\) is the analogue for
+\(\hat{P}^{w|kr}_{MS}\) in my notation for CoD SnD.) Figure 1 shows how
+the expected value varies as a function of the total number of trials
+\(n\), given \(\pi\) and \(k > 1\).\footnote{I've adapted the code from
+  Vafa (2017), which implements MS's framework (2018).}
+
+\begin{figure}
+\centering
+\includegraphics{images/pwkr_ms.png}
+\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $\pi = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
+\end{figure}
+
+My context is fundamentally different from that of GVT and MS, both of
+whom focus on longitudinal data in controlled settings. GVT also perform
+statistical tests on shots from players in live games,
+i.e.~``observational'' data, but they note that their findings are
+likely affected player shot selection in the face of defensive strategy
+by the opposing team. The number of trials is fixed in their
+experimental designs, but in CoD SnD, the number of rounds played is
+determined as a function of the max number of possible rounds (\(s\))
+and whether or not the team wins the series, as shown in Equation
+\ref{eq:pwr}. The Bernoulli trial success probability, i.e.~a round win
+in CoD SnD, is not independent of the opponent.
+
+Consequently, a statistical test of the difference in \(\hat{P}^{w|kr}\)
+and \(\hat{P}^{\ell|kr}\), as performed by GVT and MS to evaluate their
+respective hypothesis regarding
+\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\) (Theorem
+1), is not appropriate.
+
+Let us consider another form of the expected proportion of rounds won
+immediately after a streak of \(k\) round wins in a best-of-\(s\) series
+given the length of the series (\(r\) rounds), the ``hindsight''
+proportion \(\hat{P}^{w|kr}_0\). The Bernoulli round win probability
+underlying \(\hat{P}^{w|kr}_0\) is
 
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-  p^{w|kr} = p(\text{win | k, r})=\{
+p_0^{w|kr} = p_0(\text{win | k, r})=\{
 \begin{array}{cl}
@@
 
-The hindsight Bernoulli round loss probability after a streak of \(k\)
-round wins, \(p^{l|kr}\), can be formulated symmetrically.
+A binomial test for the expected proportion of round wins following
+streaks of \(k\) round wins in a series lasting \(r\) rounds,
+\(\hat{P}^{w|kr}_0\), assuming \(p^{w|kr}_0\) as the probability of
+success, can be used to verify that \(\hat{P}^{w|kr}_0\) is reasonable
+as to use as a baseline with which to compare \(\hat{P}^{w|kr}_{MS}\).
+If the binomial test shows that we cannot reject the null hypothesis
+that the expected \(\hat{P}^{w|kr}_0\) is different from the observed
+proportion \(P^{w|kr}\).
 
-However, as shown by MS, we should expect the proportion of rounds wins
-immediately following a streak \(k\) rounds wins for a series lasting
-\(r\) rounds, \(\hat{P}^{w|kr}\), to be strictly less than
-\(p^{w|kr}\).\footnote{See Appendix E.1 of MS (2018) for details on the
-  proof that follows.}
-
-\begin{quote}
-Theorem 1: \emph{Let}
-\(\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3\)\emph{, be a sequence of
-independent Bernoulli trials, each with probability of success}
-\(0 < p < 1\)\emph{. Let} \(\hat{P}_k(\mathbf{X})\) \emph{be the
-proportion of successes on the subset of trials} \(I_k(\mathbf{X})\)
-\emph{that immediately follow} \(k\) consecutive successes, that is,
-\(\hat{P}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |. \hat{P}_k\)
-\emph{is a biased estimate of}
-\(\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p\) \emph{for
-all} \(k\) \emph{such that} \(1 \leq k \leq n - 2\)\emph{. In
-particular,}
-\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < p.\)
-\end{quote}
-
-MS (2018) note that there does not exists a closed form representation
-for \(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\)
-(\(\hat{P}_k(\mathbf{X})\) is the analogue for \(\hat{P}^{w|kr}\) in my
-CoD SnD notation), for \(k > 1\). Figure 1 shows how the expected value
-varies as a function of the total number of trials \(n\), given \(p\)
-and \(k > 1\).\footnote{I've adapted the code from Vafa (2017), which
-  implements MS's framework (2018).}
-
-\begin{figure}
-\centering
-\includegraphics{images/npkd.png}
-\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $p = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
-\end{figure}
+A proportion test of \(\hat{P}^{w|kr}_0\) and \(\hat{P}^{w|kr}_{MS}\)
+can tell us whether the momentum exists in CoD SnD. A null result means
+we cannot say that there is a difference between the hindsight expected
+proportion \(\hat{P}^{w|kr}_0\) and the expected proportion adjusted for
+streak-selection bias, \(\hat{P}^{w|kr}_0\).
 
@@
   reasonable number for series that lasts at maximum 11 rounds.} Table
-\ref{tbl:cod-round-win-prop-after-k-wins} shows \(P^{w,kr}\) and
-\(P^{l,kr}\) for round win rate and loss rate following \(k = 3\) round
-win streaks respectively.
+\ref{tbl:cod-pw3r-pl3r} shows \(P^{w,kr}\) and \(P^{l,kr}\) for round
+win rate and loss rate following \(k = 3\) round win streaks
+respectively.
+
+First,
 
 \begin{longtable}{rrrrrrr}
-\caption{First, observed proportion of wins ($\hat{P}^{kr,\text{win}}_O$) and expected proportion of wins, both un-adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$), after 3-round win streak, for a series lasting $r$ rounds.
-Second, observed proportion of losses ($\hat{P}^{kr,\text{loss}}_O$) and expected proportion of losses, both un-adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$) and adjusted ($\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$), after 3-round loss streak}\label{tbl:cod-round-win-prop-after-k-wins} \\
+\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, in series lasting $r$ rounds.
+Additionally, notional expected proportion, $\hat{P}^{w|kr}_0$ and binomial test p-value, assuming notional round probability $p^{w|kr}$ and using observed counts; MS expected proportion $\hat{P}^{w|kr}_{MS}$; and $\hat{D}^{w|kr} = \hat{P}^{w|kr}_{MS} - \hat{P}^{w|kr}_0$ and proportion test p-value.
+Fields presented in groups, split by whether the team won the round immediately following the 3-round win streak, and whether the team won the series.
+The post-streak loss analogues are presented as $N^{\ell|kr}$, $P^{\ell|kr}$, $\hat{P}^{\ell|kr}_0$, $\hat{P}^{\ell|kr}_{MS}$, and $\hat{D}^{\ell|kr}$.}
+\label{tbl:cod-pw3r-pl3r} \\
 \toprule
-\multicolumn{7}{c}{\text{3 round win streak}} \\
-$r$ & $N^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_O$ & $\hat{P}^{kr,\text{win}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{win}}_{E,\text{adj.}}$ \\ 
+\multicolumn{6}{c}{\text{win series, win after 3-round win streak}} \\
 \midrule
-7 & 209 & $75\%$ & $75\%$ (0.58) & $61\%$ (<=0.01) \\
-8 & 209 & $62\%$ & $60\%$ (0.28) & $45\%$ (<=0.01) \\
-9 & 193 & $52\%$ & $50\%$ (0.33) & $35\%$ (<=0.01) \\
-10 & 151 & $44\%$ & $43\%$ (0.45) & $29\%$ (<=0.01) \\
-11 & 150 & $40\%$ & $38\%$ (0.29) & $25\%$ (<=0.01) \\
+$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
+\midrule
+7 & 209 & 74.6\% & 75.0\% (0.58) & 75.7\% & -0.7\% (0.94) \\ 
+8 & 209 & 62.2\% & 60.0\% (0.28) & 61.9\% & -1.9\% (1.00) \\ 
+9 & 193 & 51.8\% & 50.0\% (0.33) & 52.7\% & -2.7\% (0.97) \\ 
+10 & 151 & 43.7\% & 42.9\% (0.45) & 44.7\% & -1.8\% (0.94) \\ 
+11 & 150 & 40.0\% & 37.5\% (0.29) & 38.8\% & -1.3\% (1.00) \\ 
 \toprule
-\multicolumn{7}{c}{\text{3 round loss streak}} \\
-$r$ & $N^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_O$ & $\hat{P}^{kr,\text{loss}}_{E,\text{unadj.}}$ & $\hat{P}^{kr,\text{loss}}_{E,\text{adj.}}$ \\ 
+\toprule
+\multicolumn{6}{c}{\text{lose series, win after 3-round win streak}} \\
 \midrule
-10 & 60 & $13\%$ & $14\%$ (0.64) & $10\%$ (0.26) \\ 
-11 & 129 & $24\%$ & $25\%$ (0.63) & $16\%$ (<=0.01) \\ 
+$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
+\midrule
+10 & 60 & 13.3\% & 14.3\% (0.64) & 26.7\% & -12.4\% (1.00) \\ 
+11 & 129 & 24.0\% & 25.0\% (0.63) & 30.8\% & -5.8\% (0.98) \\ 
+\toprule
+\toprule
+\multicolumn{6}{c}{\text{win series, lose after 3-round win streak}} \\
+\midrule
+$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
+\midrule
+7 & 209 & 25.4\% & 25.0\% (0.48) & 6.4\% & 18.6\% (0.98) \\ 
+8 & 209 & 37.8\% & 40.0\% (0.76) & 14.7\% & 25.3\% (0.96) \\ 
+9 & 193 & 48.2\% & 50.0\% (0.72) & 22.2\% & 27.8\% (0.97) \\ 
+10 & 151 & 56.3\% & 57.1\% (0.62) & 26.7\% & 30.5\% (0.99) \\ 
+11 & 150 & 60.0\% & 62.5\% (0.76) & 30.8\% & 31.7\% (0.95) \\ 
+\toprule
+\toprule
+\multicolumn{6}{c}{\text{lose series, lose after 3-round win streak}} \\
+\midrule
+$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
+\midrule
+10 & 60 & 86.7\% & 85.7\% (0.51) & 44.7\% & 41.1\% (1.00) \\ 
+11 & 129 & 76.0\% & 75.0\% (0.45) & 38.8\% & 36.2\% (0.95) \\ 
 \bottomrule
@@
 
-\hypertarget{appendix}{%
-\section*{Appendix}\label{appendix}}
-\addcontentsline{toc}{section}{Appendix}
-
 \bibliographystyle{unsrt}

### 2022-08-20 paper/paper.Rmd
more methodology writing

@@
 
-The formula for the expected proportion of seriesn a best-of-$s$ format ($s = 11$ rounds for CoD SnD), ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^11] is
+The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^11] is
 
 [^11]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
-
-$$
-m = \frac{s + 1}{2}
-$$
 
@@
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
-\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m).
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
 }\label{eq:series-length}\end{equation}
 ```
-To evaluate the constant round win probability hypothesis--that is, that the expected and observed round win rates, $\hat{\Phi}(r)$ and $\Phi(r)$ respectively, are equal to one another--we can compute the chi-square goodness of fit statistic, $\chi^2$.
+$s = 11$ rounds for CoD SnD.[^12]
+
+[^12]: $\phi$ and other symbols are selected so as to avoid reserve symbols, like $p$ for usage in other contexts, without risking confusion.
+Upper-case symbol, e.g.
+$\Phi$, are consistently used in this paper to represent proportions, while lower-case symbols corresponding to proportions represent probabilities.
+"Hats", e.g.
+$\hat{\Phi}$, are used to convey expectations, while "bare" symbols mirroring hat-ed symbols convey observational data.
+
+To evaluate the constant round win probability null hypothesis---that is, that the expected and observed round win rates, $\hat{\Phi}(r)$ and $\Phi(r)$ respectively, are equal to one another---we can compute the chi-square goodness of fit statistic, $\chi^2$,
 
@@
 \begin{equation}\protect\hypertarget{eq:chi-squ}{}{
-\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
+\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}.
 }\label{eq:chi-squ}\end{equation}
 ```
-For CoD SnD, $r \in R = [6, 7, 8, 9, 10, 11]$.
+$r \in R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
 
@@
 
+Let us now consider round win rate immediately following a streak of $k$ wins, given that the series lasts $r$ rounds.
 Removing our knowledge of a streak, we might model the Bernoulli round win probability as
@@
 \begin{equation}\protect\hypertarget{eq:pwr}{}{
-p^{w|r} = p(\text{win | r})=\{
-\begin{array}{cl}
-\frac{m}{r}, & \text{team wins series} \\
-\frac{r - m}{r}, & \text{team loses series}
-\end{array}.
+p_0(\text{win} | r) = p^{w|r}_0 = \{
+\begin{array}{rcll}
+p^{w|r_W} & = & \frac{m}{r}, & \text{team wins series} \\
+p^{w|r_L} & = & \frac{r - m}{r}, & \text{team loses series}
+\end{array}
 }
@@
 ```
-The Bernoulli round loss probability after a streak of $k$ round wins, $p^{\ell|kr}_0$, can be formulated symmetrically.
-
-As shown by MS, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^12]
-
-[^12]: See Appendix E.1 of MS for details on the proof that follows.
-
-> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < \pi < 1$*.
+using $m$ from Equation \ref{eq:m}. The Bernoulli round loss probability for a series lasting $r$ rounds, $p^{\ell|kr}_0$ (i.e. $\ell = 1 - w, w \in [0, 1]$), can be formulated symmetrically.
+
+As shown by MS, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^13][^14]
+
+[^13]: See Appendix E.1 of MS for details on the proof that follows.
+
+[^14]: Here, I choose symbols, e.g.
+$\pi$, $x$, etc.
+that mostly do not conflict with syntax in other places.
+The exceptions are $k$ and $r$, which are used to represent streak length and number of trials globally.
+
+> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{r}_{i=1}, r \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < \pi < 1$*.
 Let* $\hat{\Pi}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{\Pi}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
-\hat{\Pi}_k$ *is a biased estimate of* $\mathbb{\Pi}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p$ *for all* $k$ *such that* $1 \leq k \leq n - 2$*.
+\hat{\Pi}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv \pi$ *for all* $k$ *such that* $1 \leq k \leq r - 2$*.
 In particular,* $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < \pi.$
 
-MS note that there does not exists a closed form representation for $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ for $k > 1$.
-($\hat{\Pi}_k(\mathbf{X})$ is the analogue for $\hat{P}^{w|kr}_{MS}$ in my notation for CoD SnD.) Figure 1 shows how the expected value varies as a function of the total number of trials $n$, given $\pi$ and $k > 1$.[^13]
-
-[^13]: I've adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+MS notes that there does not exists a closed form representation for $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, henceforth $E^\Pi$, for $k \> 1$.
+One may recursively build a collection of dictionaries to quantify $E^\Pi$ analytically, or, more reasonably for large values of $n$, one may run simulations to estimate the expected value.
+Indeed, Figure 1 uses simulation to estimate $E^\Pi$ as a function of the total number of trials $r$, given $\pi$ and $k$.[^15][^16]
+
+[^15]: I've adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+[^16]: Note that $\pi$ and $\hat{\Pi}_k(\mathbf{X})$ are analogues for $p_0^{w|r}$ and $\hat{P}^{w|kr}_{MS}$ in my notation for CoD SnD.
 
@@
 
-# library(extrafont)
-# library(ggplot2)
-# library(latex2exp)
 # # set.seed(42)
@@
 # # qs::qsave(runs, 'data/runs_1000x1000_nkp.qs')
+# 
+# library(ggplot2)
+# library(latex2exp)
 # runs <- qs::qread('data/runs_1000x1000_nkp.qs')
@@
 # 
-# extrafont::loadfonts(quiet = TRUE)
-# theme_set(theme_classic())
-# theme_update(
-#   text = element_text(family = 'CMU Typewriter Text')
-# )
+# # theme_set(theme_classic())
 # 
@@
 #     color = guide_legend(
-#       title = 'streak length (k)',
+#       title = 'k',
 #       title.hjust = 0.5,
@@
 #   geom_hline(aes(yintercept = p)) +
-#   labs(x = 'number of trials (n)', y = expression('post-streak probability of success'~(pi))) +
+#   labs(x = 'r', y = expression(pi)) +
+#   theme_classic() +
 #   theme(
@@
 \includegraphics{images/pwkr_ms.png}
-\caption{The expected value of the proportion of successes on trials that immediately follow $k$ consecutive successes, $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, for Bernoulli trial success $\pi = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $n.$}
+\caption{The expected value of the proportion of successes on trials, $E^\Pi$, that immediately follow $k$ consecutive successes for Bernoulli trial success $\pi = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $r$.}
 \end{figure}
@@
 My context is fundamentally different from that of GVT and MS, both of whom focus on longitudinal data in controlled settings.
-GVT also perform statistical tests on shots from players in live games, i.e.
+GVT also performs statistical tests on shots from players in live games, i.e.
 "observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
@@
 a round win in CoD SnD, is not independent of the opponent.
-
-Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{\ell|kr}$, as performed by GVT and MS to evaluate their respective hypothesis regarding $E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$ (Theorem 1), is not appropriate.
-
-Let us consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "hindsight" proportion $\hat{P}^{w|kr}_0$.
+Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{\ell|kr}$, as performed by GVT and MS to evaluate their respective hypothesis regarding post-streak success rates is not appropriate.
+
+One might consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{w|kr}_0$.
 The Bernoulli round win probability underlying $\hat{P}^{w|kr}_0$ is
@@
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-p_0^{w|kr} = p_0(\text{win | k, r})=\{
-\begin{array}{cl}
-\frac{m - k}{i - k}, & \text{team wins series} \\
-\frac{s - m - k}{i - k}, & \text{team loses series}
-\end{array}.
+p_0(\text{win} | k, r) = p^{w|kr}_0 =\{
+\begin{array}{rcll}
+p_0^{w|kr_W} & = & \frac{m - k}{i - k}, & \text{team wins series} \\
+p_0^{w|kr_L} & = & \frac{s - m - k}{i - k}, & \text{team loses series}
+\end{array}
 }
@@
 ```
-A binomial test for the expected proportion of round wins following streaks of $k$ round wins in a series lasting $r$ rounds, $\hat{P}^{w|kr}_0$, assuming $p^{w|kr}_0$ as the probability of success, can be used to verify that $\hat{P}^{w|kr}_0$ is reasonable as to use as a baseline with which to compare $\hat{P}^{w|kr}_{MS}$.
-If the binomial test shows that we cannot reject the null hypothesis that the expected $\hat{P}^{w|kr}_0$ is different from the observed proportion $P^{w|kr}$.
-
-A proportion test of $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ can tell us whether the momentum exists in CoD SnD.
-A null result means we cannot say that there is a difference between the hindsight expected proportion $\hat{P}^{w|kr}_0$ and the expected proportion adjusted for streak-selection bias, $\hat{P}^{w|kr}_0$.
+using $m$ from Equation \ref{eq:m}.
+We can perform a binomial test to test the null hypothesis $H_0 : \omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^17]
+
+[^17]: $\omega$ and other symbols are chosen so as to not conflict with symbols already used elsewhere for in other equations, either generic or for CoD SnD specifically.
+
+If there are $\sigma$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of getting this expected number of successes is
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:binom}{}{
+\Pr(\sigma) = {\binom {r}{\sigma}} \omega^{\sigma}(1-\omega)^{r-\sigma}.
+}\label{eq:binom}\end{equation}
+```
+Plugging in the notional probability $p^{w|kr}_0$ for the null $\omega_0$ and the observed probability $p^{w|kr} = \frac{N^{w|kr}}{P^{w|kr}}$, where $N^{w|kr}$ is the observed number of instances where a teams wins the round immediately following a $k$-round winning streak in a series lasting $r$ rounds, for the observed $\omega$, we can evaluate whether the observed probability is not significantly different from the notional probability.
+If we reject this hypothesis, then we might consider team momentum, represented by post-streak success, plausible.
+
+Returning to the streak-selection adjustment framework proposed by MS, one can perform the same binomial test, swapping out $p^{w|kr}_0$ with $p^{w|kr}_{MS}$.
+Of course, given the caveats mentioned before, the results should be heeded with caution.
 
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^14] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^18] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^14]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+[^18]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^15] Table \ref{tbl:cod-pw3r-pl3r} shows $P^{w,kr}$ and $P^{l,kr}$ for round win rate and loss rate following $k = 3$ round win streaks respectively.
-
-[^15]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^19] Table \ref{tbl:cod-pw3r-pl3r} shows $P^{w,kr}$ and $P^{l,kr}$ for round win rate and loss rate following $k = 3$ round win streaks respectively.
+
+[^19]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
 

### 2022-08-20 paper/paper.tex
more methodology writing

@@
 
-The formula for the expected proportion of seriesn a best-of-\(s\)
-format (\(s = 11\) rounds for CoD SnD), ending in \(r\) rounds
-(\(r \leq s\)), \(\hat{\Phi}(r)\), for a constant round win probability
-\(\phi\) (\(0 \leq \phi \leq 1\)) for one team\footnote{If
-  \(\phi > 0.5\), then one might say that this team is the better team
-  (known in hindsight).} is
-
-\[
-m = \frac{s + 1}{2}
-\]
+The formula for the expected proportion of series a best-of-\(s\) format
+ending in \(r\) rounds (\(r \leq s\)), \(\hat{\Phi}(r)\), for a constant
+round win probability \(\phi\) (\(0 \leq \phi \leq 1\)) for one
+team\footnote{If \(\phi > 0.5\), then one might say that this team is
+  the better team (known in hindsight).} is
 
@@
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
-\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m).
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
 }\label{eq:series-length}\end{equation}
 
-To evaluate the constant round win probability hypothesis--that is, that
-the expected and observed round win rates, \(\hat{\Phi}(r)\) and
-\(\Phi(r)\) respectively, are equal to one another--we can compute the
-chi-square goodness of fit statistic, \(\chi^2\).
+\(s = 11\) rounds for CoD SnD.\footnote{\(\phi\) and other symbols are
+  selected so as to avoid reserve symbols, like \(p\) for usage in other
+  contexts, without risking confusion. Upper-case symbol, e.g.~\(\Phi\),
+  are consistently used in this paper to represent proportions, while
+  lower-case symbols corresponding to proportions represent
+  probabilities. ``Hats'', e.g.~\(\hat{\Phi}\), are used to convey
+  expectations, while ``bare'' symbols mirroring hat-ed symbols convey
+  observational data.}
+
+To evaluate the constant round win probability null hypothesis---that
+is, that the expected and observed round win rates, \(\hat{\Phi}(r)\)
+and \(\Phi(r)\) respectively, are equal to one another---we can compute
+the chi-square goodness of fit statistic, \(\chi^2\),
 
 \begin{equation}\protect\hypertarget{eq:chi-squ}{}{
-\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
+\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}.
 }\label{eq:chi-squ}\end{equation}
 
-For CoD SnD, \(r \in R = [6, 7, 8, 9, 10, 11]\).
+\(r \in R = [6, 7, 8, 9, 10, 11]\) for CoD SnD.
 
@@
 
-Removing our knowledge of a streak, we might model the Bernoulli round
-win probability as
+Let us now consider round win rate immediately following a streak of
+\(k\) wins, given that the series lasts \(r\) rounds. Removing our
+knowledge of a streak, we might model the Bernoulli round win
+probability as
 
 \begin{equation}\protect\hypertarget{eq:pwr}{}{
-p^{w|r} = p(\text{win | r})=\{
-\begin{array}{cl}
-\frac{m}{r}, & \text{team wins series} \\
-\frac{r - m}{r}, & \text{team loses series}
-\end{array}.
+p_0(\text{win} | r) = p^{w|r}_0 = \{
+\begin{array}{rcll}
+p^{w|r_W} & = & \frac{m}{r}, & \text{team wins series} \\
+p^{w|r_L} & = & \frac{r - m}{r}, & \text{team loses series}
+\end{array}
 }
@@
 
-The Bernoulli round loss probability after a streak of \(k\) round wins,
-\(p^{\ell|kr}_0\), can be formulated symmetrically.
+using \(m\) from Equation \ref{eq:m}. The Bernoulli round loss
+probability for a series lasting \(r\) rounds, \(p^{\ell|kr}_0\)
+(i.e.~\(\ell = 1 - w, w \in [0, 1]\)), can be formulated symmetrically.
 
@@
 \(p^{w|r}\).\footnote{See Appendix E.1 of MS for details on the proof
-  that follows.}
+  that follows.}\footnote{Here, I choose symbols, e.g.~\(\pi\), \(x\),
+  etc. that mostly do not conflict with syntax in other places. The
+  exceptions are \(k\) and \(r\), which are used to represent streak
+  length and number of trials globally.}
 
@@
 Theorem 1: \emph{Let}
-\(\mathbf{X} = \{X_i\}^{n}_{i=1}, n \geq 3\)\emph{, be a sequence of
+\(\mathbf{X} = \{X_i\}^{r}_{i=1}, r \geq 3\)\emph{, be a sequence of
 independent Bernoulli trials, each with probability of success}
@@
 \emph{is a biased estimate of}
-\(\mathbb{\Pi}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv p\)
-\emph{for all} \(k\) \emph{such that} \(1 \leq k \leq n - 2\)\emph{. In
+\(\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv \pi\)
+\emph{for all} \(k\) \emph{such that} \(1 \leq k \leq r - 2\)\emph{. In
 particular,}
@@
 
-MS note that there does not exists a closed form representation for
-\(E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\) for
-\(k > 1\). (\(\hat{\Pi}_k(\mathbf{X})\) is the analogue for
-\(\hat{P}^{w|kr}_{MS}\) in my notation for CoD SnD.) Figure 1 shows how
-the expected value varies as a function of the total number of trials
-\(n\), given \(\pi\) and \(k > 1\).\footnote{I've adapted the code from
-  Vafa (2017), which implements MS's framework (2018).}
+MS notes that there does not exists a closed form representation for
+\(E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\),
+henceforth \(E^\Pi\), for \(k \> 1\). One may recursively build a
+collection of dictionaries to quantify \(E^\Pi\) analytically, or, more
+reasonably for large values of \(n\), one may run simulations to
+estimate the expected value. Indeed, Figure 1 uses simulation to
+estimate \(E^\Pi\) as a function of the total number of trials \(r\),
+given \(\pi\) and \(k\).\footnote{I've adapted the code from Vafa
+  (2017), which implements MS's framework (2018).}\footnote{Note that
+  \(\pi\) and \(\hat{\Pi}_k(\mathbf{X})\) are analogues for
+  \(p_0^{w|r}\) and \(\hat{P}^{w|kr}_{MS}\) in my notation for CoD SnD.}
 
@@
 My context is fundamentally different from that of GVT and MS, both of
-whom focus on longitudinal data in controlled settings. GVT also perform
-statistical tests on shots from players in live games,
+whom focus on longitudinal data in controlled settings. GVT also
+performs statistical tests on shots from players in live games,
 i.e.~``observational'' data, but they note that their findings are
@@
 \ref{eq:pwr}. The Bernoulli trial success probability, i.e.~a round win
-in CoD SnD, is not independent of the opponent.
+in CoD SnD, is not independent of the opponent. Consequently, a
+statistical test of the difference in \(\hat{P}^{w|kr}\) and
+\(\hat{P}^{\ell|kr}\), as performed by GVT and MS to evaluate their
+respective hypothesis regarding post-streak success rates is not
+appropriate.
 
-Consequently, a statistical test of the difference in \(\hat{P}^{w|kr}\)
-and \(\hat{P}^{\ell|kr}\), as performed by GVT and MS to evaluate their
-respective hypothesis regarding
-\(E[\hat{P}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\) (Theorem
-1), is not appropriate.
-
-Let us consider another form of the expected proportion of rounds won
+One might consider another form of the expected proportion of rounds won
 immediately after a streak of \(k\) round wins in a best-of-\(s\) series
-given the length of the series (\(r\) rounds), the ``hindsight''
+given the length of the series (\(r\) rounds), the ``notional''
 proportion \(\hat{P}^{w|kr}_0\). The Bernoulli round win probability
@@
 
-A binomial test for the expected proportion of round wins following
-streaks of \(k\) round wins in a series lasting \(r\) rounds,
-\(\hat{P}^{w|kr}_0\), assuming \(p^{w|kr}_0\) as the probability of
-success, can be used to verify that \(\hat{P}^{w|kr}_0\) is reasonable
-as to use as a baseline with which to compare \(\hat{P}^{w|kr}_{MS}\).
-If the binomial test shows that we cannot reject the null hypothesis
-that the expected \(\hat{P}^{w|kr}_0\) is different from the observed
-proportion \(P^{w|kr}\).
+using \(m\) from Equation \ref{eq:m}. We can perform a binomial test to
+test the null hypothesis \(H_0 : \omega = \omega_0\) for the observed
+probability of success \(\omega\) and a user-specified \(\omega_0\),
+where \(0 \leq \omega_0 \leq 1\).\footnote{\(\omega\) and other symbols
+  are chosen so as to not conflict with symbols already used elsewhere
+  for in other equations, either generic or for CoD SnD specifically.}
 
-A proportion test of \(\hat{P}^{w|kr}_0\) and \(\hat{P}^{w|kr}_{MS}\)
-can tell us whether the momentum exists in CoD SnD. A null result means
-we cannot say that there is a difference between the hindsight expected
-proportion \(\hat{P}^{w|kr}_0\) and the expected proportion adjusted for
-streak-selection bias, \(\hat{P}^{w|kr}_0\).
+If there are \(\sigma\) observed successes in a sample of \(r\) trials
+and we expect that there should be \(r * \omega_0\), the probability of
+getting this expected number of successes is
+
+\begin{equation}\protect\hypertarget{eq:binom}{}{
+\Pr(\sigma) = {\binom {r}{\sigma}} \omega^{\sigma}(1-\omega)^{r-\sigma}.
+}\label{eq:binom}\end{equation}
+
+Plugging in the notional probability \(p^{w|kr}_0\) for the null
+\(\omega_0\) and the observed probability
+\(p^{w|kr} = \frac{N^{w|kr}}{P^{w|kr}}\), where \(N^{w|kr}\) is the
+observed number of instances where a teams wins the round immediately
+following a \(k\)-round winning streak in a series lasting \(r\) rounds,
+for the observed \(\omega\), we can evaluate whether the observed
+probability is not significantly different from the notional
+probability. If we reject this hypothesis, then we might consider team
+momentum, represented by post-streak success, plausible.
+
+Returning to the streak-selection adjustment framework proposed by MS,
+one can perform the same binomial test, swapping out \(p^{w|kr}_0\) with
+\(p^{w|kr}_{MS}\). Of course, given the caveats mentioned before, the
+results should be heeded with caution.
 

### 2022-08-20 paper/paper.Rmd
better last table

@@
 First, I find evidence supprting the hypothesis that round win probability can be modeled as a constant across the series, although not at the naive 50%.
-Second, I examine post-streak round win probability, in search of evidence positive recency (the "hot hand" fallacy) or negative recency (the "gambler's falacy").
-I find that teams perform significantly worse than expected after streaks of 2, 3, and 4 wins when series end up going to 9, 10, or 11 (maximum) rounds, suggesting the presence of negative recency.
+Second, I examine post-streak round win probability, given the series outcome.
+I find no evidence that post-streak win rate is significantly different than expected for combinations of streak length, series length, and series winner, suggesting that the perception of momentum at the team level is deceiving.
 bibliography: references.bib  
@@
 ```
-Plugging in the notional probability $p^{w|kr}_0$ for the null $\omega_0$ and the observed probability $p^{w|kr} = \frac{N^{w|kr}}{P^{w|kr}}$, where $N^{w|kr}$ is the observed number of instances where a teams wins the round immediately following a $k$-round winning streak in a series lasting $r$ rounds, for the observed $\omega$, we can evaluate whether the observed probability is not significantly different from the notional probability.
+Plugging in the notional probability $p^{w|kr}_0$ for the null $\omega_0$ and the observed probability $p^{w|kr} = N^{w|kr} \times P^{w|kr}$, where $N^{w|kr}$ is the observed number of instances where a teams wins the round immediately following a $k$-round winning streak in a series lasting $r$ rounds, for the observed $\omega$, we can evaluate whether the observed probability is not significantly different from the notional probability.
 If we reject this hypothesis, then we might consider team momentum, represented by post-streak success, plausible.
@@
 #| label: cod_round_win_prop_after_k_wins
+vectorized_binom_test <- function(x, n, p, ...) {
+  map_dfr(
+    seq_along(x), 
+    function(i) {
+      res <- binom.test(x[i], n[i], p = p[i], ...)
+      tibble(
+        estimate = res$estimate,
+        conf.low = res$conf.int[[1]],
+        conf.high = res$conf.int[[2]],
+        p.value = res$p.value
+      )
+    }
+  )
+}
+
 cod_round_streaks <- cod_rounds |> 
@@
     drop_na(!!!col_syms) |> 
-    count(n_rounds, win_series, win_round, won_prior_round1, !!!col_syms, sort = TRUE)
+    count(n_rounds, win_series, ..., win_round, won_prior_round1, !!!col_syms, sort = TRUE)
 
@@
     cod_round_win_prop_after_z_with_probs <- cod_round_win_prop_after_z |> 
-      group_by(win_series, n_rounds) |> 
+      group_by(win_series, n_rounds, ...) |> 
       mutate(
@@
       ungroup() |> 
-      select(n_rounds, win_round, win_series, n, total, prop) |> 
-      arrange(n_rounds, win_round) |> 
+      select(n_rounds, win_round, win_series, ..., n, total, prop) |> 
+      # filter(!win_round) |> 
+      arrange(n_rounds, win_round, ...) |> 
       inner_join(
@@
 
-  suppressMessages(
-    full_join(
   cod_round_win_prop_after_z_with_probs |> 
-        nest(data = -c(n_rounds, win_series, win_round)) |> 
-        mutate(
-          ## TODO: Vectorize this.
-          binom_p_value = map_dbl(
-            data, 
-            ~binom.test(.x$n, .x$total, .x$notional_prop, alternative = 'greater') |> 
-              broom::tidy() |>
-              pull(p.value)
-          ),
-          binom_is_signif = binom_p_value <= 0.05
-        ) |> 
-        unnest(data),
-      cod_round_win_prop_after_z_with_probs |> 
-        select(n_rounds, win_round, win_series, n, total, prop, notional_prop) |> 
-        mutate(
-          notional_n = as.integer(n * notional_prop / prop),
-          notional_total = as.integer(total * notional_prop / prop), 
-          compared_p_value = vectorized_prop_test(n, total, notional_n, notional_total)$p.value,
-          compared_is_signif = compared_p_value <= 0.05
-        )
-    )
-  )
-}
-
-summarize_cod_win_prop_after_k_wins <- function(k) {
+    mutate(
+      notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value,
+      ms_p_value = vectorized_binom_test(n, total, p = ms_prop)$p.value
+    )
+}
+
+summarize_cod_win_prop_after_k_wins <- function(k, ...) {
   probs_nx_k <- crossing(
@@
       ),
-      diff_prop = notional_prop - ms_prop
-    ) |> 
-    filter(notional_prop > 0, notional_prop < 1)
+      across(
+        ms_prop,
+        ~ifelse(win_round, .x, naive_prop + (naive_prop - .x))
+      ),
+      across(
+        ms_prop,
+        ~ifelse(is.nan(ms_prop), naive_prop, .x)
+      )
+    )
 
@@
 
-cod_round_win_prop_after_k_wins <- tibble(win_streak = 3L) |>
+summarize_cod_win_prop_after_k_wins_i_rounds <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    round = 3L:11L,
+    win_series = c(TRUE, FALSE),
+    win_round = c(TRUE, FALSE)
+  ) |> 
+    filter(round >= (!!k + 1L)) |> 
+    mutate(
+      is_valid = case_when(
+        win_series ~ TRUE,
+        (n_rounds - !!k - 6L) >= 0L ~ TRUE,
+        TRUE ~ FALSE
+      )
+    ) |> 
+    filter(is_valid) |> 
+    select(-is_valid) |> 
+    mutate(
+      naive_prop = ifelse(win_series, 6L / n_rounds, (n_rounds - 6L) / n_rounds),
+      notional_prop = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
+      across(c(naive_prop, notional_prop), ~ifelse(win_round, .x, 1 - .x)),
+      ms_prop = map2_dbl(
+        n_rounds, naive_prop, 
+        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
+      ),
+      across(
+        ms_prop,
+        ~ifelse(win_round, .x, naive_prop + (naive_prop - .x))
+      )
+    )
+
+  postprocess_round_streaks(
+    k = k,
+    probs_nx_k = probs_nx_k,
+    round
+  )
+}
+
+cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
   mutate(
@@
   unnest(data)
+cod_round_win_prop_after_k_wins |> filter(win_round, notional_p_value < 0.05)
+cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value < 0.05)
+
+cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 2L:3L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
+  ) |>
+  unnest(data)
+cod_round_win_prop_after_k_wins_i_rounds |> filter(win_round, notional_p_value < 0.05)
 ```
@@
 cod_round_win_prop_after_k_wins |> 
+  filter(win_streak == 2L) |> 
   mutate(
@@
         .x <= 0.01 ~ '<=0.01', 
-        round(.x, 2) == 1 ~ '1.00',
-        TRUE ~ as.character(round(.x, 2))
+        TRUE ~ sprintf('%.2f', .x)
       )
@@
     prop_lab = scales::percent(prop, accuracy = 0.1),
-    binom_lab = sprintf('%.1f%% (%s)', round(100 * notional_prop, 1), binom_p_value),
-    compared_lab = scales::percent(ms_prop, accuracy = 0.1),
-    diff_lab = sprintf('%.1f%% (%s)', round(100 * diff_prop, 1), compared_p_value)
-  ) |>
-  arrange(win_streak, n_rounds, win_series) |> 
+    notional_lab = sprintf('%.1f%% (%s)', round(100 * notional_prop, 1), notional_p_value),
+    ms_lab = sprintf('%.1f%% (%s)', round(100 * ms_prop, 1), ms_p_value)
+  ) |>
+  arrange(n_rounds, win_series, win_round) |> 
   transmute(
-    win_series,
+    n_rounds,
+    across(win_series, ~ifelse(.x, 'yes', 'no')),
     win_round,
-    n_rounds,
     total,
     prop_lab,
-    binom_lab,
-    compared_lab,
-    diff_lab
-  ) |>
-  group_split(win_series, win_round) |> 
+    notional_lab,
+    ms_lab
+  ) |>
+  group_split(win_round) |> 
   walk(
@@
         select(
-          -c(win_series, win_round)
+          -c(win_round)
         ) |> 
@@
         gt::cols_label(
-          # win_streak = 'Streak',
           n_rounds = 'r',
+          win_series = 'Win series?',
           total = 'N',
           prop_lab = 'O',
-          binom_lab = 'a',
-          compared_lab = 'b',
-          diff_lab = 'c'
+          notional_lab = 'a',
+          ms_lab = 'b'
         ) |> 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^19] Table \ref{tbl:cod-pw3r-pl3r} shows $P^{w,kr}$ and $P^{l,kr}$ for round win rate and loss rate following $k = 3$ round win streaks respectively.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^19] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively.
 
@@
 
-First,
-
 ```{=tex}
-\begin{longtable}{rrrrrrr}
-\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, in series lasting $r$ rounds.
-Additionally, notional expected proportion, $\hat{P}^{w|kr}_0$ and binomial test p-value, assuming notional round probability $p^{w|kr}$ and using observed counts; MS expected proportion $\hat{P}^{w|kr}_{MS}$; and $\hat{D}^{w|kr} = \hat{P}^{w|kr}_{MS} - \hat{P}^{w|kr}_0$ and proportion test p-value.
-Fields presented in groups, split by whether the team won the round immediately following the 3-round win streak, and whether the team won the series.
-The post-streak loss analogues are presented as $N^{\ell|kr}$, $P^{\ell|kr}$, $\hat{P}^{\ell|kr}_0$, $\hat{P}^{\ell|kr}_{MS}$, and $\hat{D}^{\ell|kr}$.}
+\begin{longtable}{rrrrrr}
+\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, given the length of the series ($r$ rounds) and the series winner.
+Additionally, the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively, and the $p$-values of binomial tests comparing the underlying notional and MS round win probabilities, $p^{w|kr}_0$ and $p^{w|kr}_{MS}$, to the probability implied by the observed proportion $p^{w|kr} = N^{w|kr} \times P^{w|kr}$.}
 \label{tbl:cod-pw3r-pl3r} \\
 \toprule
-\multicolumn{6}{c}{\text{win series, win after 3-round win streak}} \\
+$r$ & \text{Win series?} & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ ($p$-value) \\ 
 \midrule
-$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
-\midrule
-7 & 209 & 74.6\% & 75.0\% (0.58) & 75.7\% & -0.7\% (0.94) \\ 
-8 & 209 & 62.2\% & 60.0\% (0.28) & 61.9\% & -1.9\% (1.00) \\ 
-9 & 193 & 51.8\% & 50.0\% (0.33) & 52.7\% & -2.7\% (0.97) \\ 
-10 & 151 & 43.7\% & 42.9\% (0.45) & 44.7\% & -1.8\% (0.94) \\ 
-11 & 150 & 40.0\% & 37.5\% (0.29) & 38.8\% & -1.3\% (1.00) \\ 
-\toprule
-\toprule
-\multicolumn{6}{c}{\text{lose series, win after 3-round win streak}} \\
-\midrule
-$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
-\midrule
-10 & 60 & 13.3\% & 14.3\% (0.64) & 26.7\% & -12.4\% (1.00) \\ 
-11 & 129 & 24.0\% & 25.0\% (0.63) & 30.8\% & -5.8\% (0.98) \\ 
-\toprule
-\toprule
-\multicolumn{6}{c}{\text{win series, lose after 3-round win streak}} \\
-\midrule
-$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
-\midrule
-7 & 209 & 25.4\% & 25.0\% (0.48) & 6.4\% & 18.6\% (0.98) \\ 
-8 & 209 & 37.8\% & 40.0\% (0.76) & 14.7\% & 25.3\% (0.96) \\ 
-9 & 193 & 48.2\% & 50.0\% (0.72) & 22.2\% & 27.8\% (0.97) \\ 
-10 & 151 & 56.3\% & 57.1\% (0.62) & 26.7\% & 30.5\% (0.99) \\ 
-11 & 150 & 60.0\% & 62.5\% (0.76) & 30.8\% & 31.7\% (0.95) \\ 
-\toprule
-\toprule
-\multicolumn{6}{c}{\text{lose series, lose after 3-round win streak}} \\
-\midrule
-$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
-\midrule
-10 & 60 & 86.7\% & 85.7\% (0.51) & 44.7\% & 41.1\% (1.00) \\ 
-11 & 129 & 76.0\% & 75.0\% (0.45) & 38.8\% & 36.2\% (0.95) \\ 
+7 & yes & 209 & 74.6\% & 75.0\% (0.94) & 75.7\% (0.69) \\ 
+8 & yes & 209 & 62.2\% & 60.0\% (0.53) & 61.9\% (0.94) \\ 
+9 & yes & 193 & 51.8\% & 50.0\% (0.67) & 52.7\% (0.83) \\ 
+10 & no & 60 & 13.3\% & 14.3\% (1.00) & 26.7\% (0.02) \\ 
+10 & yes & 151 & 43.7\% & 42.9\% (0.87) & 44.7\% (0.87) \\ 
+11 & no & 129 & 24.0\% & 25.0\% (0.84) & 30.8\% (0.11) \\ 
+11 & yes & 150 & 40.0\% & 37.5\% (0.56) & 38.8\% (0.80) \\
+
 \bottomrule
@@
 ```
+We observe that, with the exception of $\hat{P}^{w|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^20], all binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
+As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
+
+[^20]: This implies that the opponent, th eventual series winner, goes on to win the series 6-4 after going down 0-4.
+This is the only scenario in which one team wins four rounds consecutively but loses a best-of-11 series in 10 rounds.
+
+When performing the same tests for streaks of two, four, and five, there is no case in which I can reject the binomial null hypothesis for the expected notional probability $p^{w|kr}_0$.
+The null hypothesis can be rejected for expected MS probability $p^{w|kr}_{MS}$ when $k = 4, r = [7, 8, 10]$ and $k = 5, r = [7, 8]$.
+Nonetheless, the usefulness of $p^{w|kr}_{MS}$ is questionable, as described before, and the sample sizes are smaller for these conditions (all under 20 instances, with the exception of $k = 4, r = [7, 8]$ with 70 and 39 observations respectively).
+
 # References {.unnumbered}

### 2022-08-20 paper/paper.tex
better last table

@@
 constant across the series, although not at the naive 50\%. Second, I
-examine post-streak round win probability, in search of evidence
-positive recency (the ``hot hand'' fallacy) or negative recency (the
-``gambler's falacy''). I find that teams perform significantly worse
-than expected after streaks of 2, 3, and 4 wins when series end up going
-to 9, 10, or 11 (maximum) rounds, suggesting the presence of negative
-recency.
+examine post-streak round win probability, given the series outcome. I
+find no evidence that post-streak win rate is significantly different
+than expected for combinations of streak length, series length, and
+series winner, suggesting that the perception of momentum at the team
+level is deceiving.
 \end{abstract}
@@
 \(\omega_0\) and the observed probability
-\(p^{w|kr} = \frac{N^{w|kr}}{P^{w|kr}}\), where \(N^{w|kr}\) is the
+\(p^{w|kr} = N^{w|kr} \times P^{w|kr}\), where \(N^{w|kr}\) is the
 observed number of instances where a teams wins the round immediately
@@
   reasonable number for series that lasts at maximum 11 rounds.} Table
-\ref{tbl:cod-pw3r-pl3r} shows \(P^{w,kr}\) and \(P^{l,kr}\) for round
-win rate and loss rate following \(k = 3\) round win streaks
+\ref{tbl:cod-pw3r-pl3r} compares the observed round win rate
+\(P^{w,kr}\) following streaks of \(k=3\) round wins given the series
+outcome (\(r\) rounds and winner) with the notional and MS expected
+proportions, \(\hat{P}^{w|kr}_0\) and \(\hat{P}^{w|kr}_{MS}\)
 respectively.
 
-First,
-
-\begin{longtable}{rrrrrrr}
-\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, in series lasting $r$ rounds.
-Additionally, notional expected proportion, $\hat{P}^{w|kr}_0$ and binomial test p-value, assuming notional round probability $p^{w|kr}$ and using observed counts; MS expected proportion $\hat{P}^{w|kr}_{MS}$; and $\hat{D}^{w|kr} = \hat{P}^{w|kr}_{MS} - \hat{P}^{w|kr}_0$ and proportion test p-value.
-Fields presented in groups, split by whether the team won the round immediately following the 3-round win streak, and whether the team won the series.
-The post-streak loss analogues are presented as $N^{\ell|kr}$, $P^{\ell|kr}$, $\hat{P}^{\ell|kr}_0$, $\hat{P}^{\ell|kr}_{MS}$, and $\hat{D}^{\ell|kr}$.}
+\begin{longtable}{rrrrrr}
+\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, given the length of the series ($r$ rounds) and the series winner.
+Additionally, the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively, and the $p$-values of binomial tests comparing the underlying notional and MS round win probabilities, $p^{w|kr}_0$ and $p^{w|kr}_{MS}$, to the probability implied by the observed proportion $p^{w|kr} = N^{w|kr} \times P^{w|kr}$.}
 \label{tbl:cod-pw3r-pl3r} \\
 \toprule
-\multicolumn{6}{c}{\text{win series, win after 3-round win streak}} \\
+$r$ & \text{Win series?} & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ ($p$-value) \\ 
 \midrule
-$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
-\midrule
-7 & 209 & 74.6\% & 75.0\% (0.58) & 75.7\% & -0.7\% (0.94) \\ 
-8 & 209 & 62.2\% & 60.0\% (0.28) & 61.9\% & -1.9\% (1.00) \\ 
-9 & 193 & 51.8\% & 50.0\% (0.33) & 52.7\% & -2.7\% (0.97) \\ 
-10 & 151 & 43.7\% & 42.9\% (0.45) & 44.7\% & -1.8\% (0.94) \\ 
-11 & 150 & 40.0\% & 37.5\% (0.29) & 38.8\% & -1.3\% (1.00) \\ 
-\toprule
-\toprule
-\multicolumn{6}{c}{\text{lose series, win after 3-round win streak}} \\
-\midrule
-$r$ & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ & $\hat{D}^{w|kr}$ ($p$-value) \\ 
-\midrule
-10 & 60 & 13.3\% & 14.3\% (0.64) & 26.7\% & -12.4\% (1.00) \\ 
-11 & 129 & 24.0\% & 25.0\% (0.63) & 30.8\% & -5.8\% (0.98) \\ 
-\toprule
-\toprule
-\multicolumn{6}{c}{\text{win series, lose after 3-round win streak}} \\
-\midrule
-$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
-\midrule
-7 & 209 & 25.4\% & 25.0\% (0.48) & 6.4\% & 18.6\% (0.98) \\ 
-8 & 209 & 37.8\% & 40.0\% (0.76) & 14.7\% & 25.3\% (0.96) \\ 
-9 & 193 & 48.2\% & 50.0\% (0.72) & 22.2\% & 27.8\% (0.97) \\ 
-10 & 151 & 56.3\% & 57.1\% (0.62) & 26.7\% & 30.5\% (0.99) \\ 
-11 & 150 & 60.0\% & 62.5\% (0.76) & 30.8\% & 31.7\% (0.95) \\ 
-\toprule
-\toprule
-\multicolumn{6}{c}{\text{lose series, lose after 3-round win streak}} \\
-\midrule
-$r$ & $N^{\ell|kr}$ & $P^{\ell|kr}$ & $\hat{P}^{\ell|kr}_0$ ($p$-value) & $\hat{P}^{\ell|kr}_{MS}$ & $\hat{D}^{\ell|kr}$ ($p$-value) \\ 
-\midrule
-10 & 60 & 86.7\% & 85.7\% (0.51) & 44.7\% & 41.1\% (1.00) \\ 
-11 & 129 & 76.0\% & 75.0\% (0.45) & 38.8\% & 36.2\% (0.95) \\ 
+7 & yes & 209 & 74.6\% & 75.0\% (0.94) & 75.7\% (0.69) \\ 
+8 & yes & 209 & 62.2\% & 60.0\% (0.53) & 61.9\% (0.94) \\ 
+9 & yes & 193 & 51.8\% & 50.0\% (0.67) & 52.7\% (0.83) \\ 
+10 & no & 60 & 13.3\% & 14.3\% (1.00) & 26.7\% (0.02) \\ 
+10 & yes & 151 & 43.7\% & 42.9\% (0.87) & 44.7\% (0.87) \\ 
+11 & no & 129 & 24.0\% & 25.0\% (0.84) & 30.8\% (0.11) \\ 
+11 & yes & 150 & 40.0\% & 37.5\% (0.56) & 38.8\% (0.80) \\
+
 \bottomrule
 \end{longtable}
+
+We observe that, with the exception of \(\hat{P}^{w|kr}_{MS}\) when
+\(r = 10\) and the eventual series loser is the team that wins after a
+streak of three round wins\footnote{This implies that the opponent, th
+  eventual series winner, goes on to win the series 6-4 after going down
+  0-4. This is the only scenario in which one team wins four rounds
+  consecutively but loses a best-of-11 series in 10 rounds.}, all
+binomial test \(p\)-values are greater than the typical
+\(\alpha = 0.05\) threshold, implying that we cannot reject the null
+hypothesis that the expected notional and MS post-streak round win rates
+are different than the observed proportion. As noted before, the MS
+expectations may be unreliable for CoD SnD, so one is inclined to prefer
+the results of the notional binomial tests.
+
+When performing the same tests for streaks of two, four, and five, there
+is no case in which I can reject the binomial null hypothesis for the
+expected notional probability \(p^{w|kr}_0\). The null hypothesis can be
+rejected for expected MS probability \(p^{w|kr}_{MS}\) when
+\(k = 4, r = [7, 8, 10]\) and \(k = 5, r = [7, 8]\). Nonetheless, the
+usefulness of \(p^{w|kr}_{MS}\) is questionable, as described before,
+and the sample sizes are smaller for these conditions (all under 20
+instances, with the exception of \(k = 4, r = [7, 8]\) with 70 and 39
+observations respectively).
 

### 2022-08-21 paper/paper.Rmd
start paper discussion

@@
   pull(prop)
+cod_o_win_prop^2 * (1 - cod_o_win_prop)
+cod_o_win_prop * (1 - cod_o_win_prop)^2
 
@@
 
-The empirical offensive round win percentage across all rounds is 47.8%.[^7] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+The empirical offensive round win percentage across all rounds is $\phi_O$ = 47.8%.[^7] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
@@
 
-cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 2L:3L) |>
+tibble(win_streak = 1L) |>
   mutate(
@@
   ) |>
+  unnest(data) |> 
+  filter(win_round, notional_p_value < 0.05)
+
+cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 1L:3L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
+  ) |>
   unnest(data)
-cod_round_win_prop_after_k_wins_i_rounds |> filter(win_round, notional_p_value < 0.05)
+cod_round_win_prop_after_k_wins_i_rounds |> 
+  filter(notional_prop < prop, notional_p_value < 0.05) |> 
+  filter(n_rounds == round) |> 
+  filter(win_streak == 1) |> 
+  group_by(n_rounds, round) |> 
+  mutate(
+    total = sum(n),
+    prop = n / total
+  )
 ```
@@
 
+# Discussion
+
+For the sake of brevity, I did not delve into win rates and streaks split by offensive or defensive role.
+For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak winning as the offensive team.
+This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average.
+On the other hand, streaks of three starting with an offensive round win---theoretically, given $\phi_O$ = 47.7% the expected frequency is $\phi_O^2 \times (1 - \phi_O) \approx 0.119$---are likely to occur less frequently than such streaks starting with a defensive win---$\phi_O \times (1 - \phi_O)^2 \approx 0.130$---so I would want to account for sample size differences.
+
+# Acknowledgements {.unnumbered}
+
+I would like to thank my brother Andrew for giving me feedback on early iterations of this paper, and for requiring me to mention him.
+
 # References {.unnumbered}

### 2022-08-21 research/run_tests.R
functionalize run tests

@@ -1,8 +1,13 @@
 
-simulate_cod_round_arrangements <- function(n_sims = 10000, seed = 42) {
+library(tidyverse)
+library(qs)
+library(randtests)
+
+cod_rounds <- qs::qread('data/cod_rounds.qs')
+simulate_cod_round_arrangements <- function(p = 0.5, n_sims = 10000, seed = 42) {
   n_rounds_max <- 11
   set.seed(seed)
-  w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE)
+  w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE, prob = c(1 - p, p))
   m <- matrix(w, nrow = n_sims, ncol = n_rounds_max)
   # data.frame(x)
   df <- as_tibble(m)
@@ -96,7 +101,8 @@ simulate_cod_round_arrangements <- function(n_sims = 10000, seed = 42) {
     mutate(prop = n / sum(n))
 }
 
-cod_expected_round_arrangements <- simulate_cod_round_arrangements()
+cod_expected_round_arrangements_naive <- simulate_cod_round_arrangements(0.5)
+cod_expected_round_arrangements_mle <- simulate_cod_round_arrangements(0.575)
 
 cod_actual_round_arrangements <- cod_rounds |> 
   filter(win_series) |> 
@@ -114,48 +120,76 @@ cod_actual_round_arrangements <- cod_rounds |>
   count(record, ws, sort = TRUE) |> 
   mutate(prop = n / sum(n))
 
-suppressWarnings(
-  cod_run_tests <- cod_expected_round_arrangements |> 
-    select(record, ws) |> 
-    separate(ws, into = as.character(1:11), remove = FALSE) |> 
-    pivot_longer(
-      -c(record, ws),
-      names_to = 'round',
-      values_to = 'w',
-      values_drop_na = TRUE
+perform_run_tests <- function(cod_expected_round_arrangements) {
+  suppressWarnings(
+    cod_run_tests <- cod_expected_round_arrangements |> 
+      select(record, ws) |> 
+      separate(ws, into = as.character(1:11), remove = FALSE) |> 
+      pivot_longer(
+        -c(record, ws),
+        names_to = 'round',
+        values_to = 'w',
+        values_drop_na = TRUE
+      ) |> 
+      mutate(
+        across(c(round, w), as.integer)
+      ) |> 
+      # filter(record != '6-0') |> 
+      select(-round) |> 
[…]

### 2022-08-21 paper/paper.Rmd
incorporate some andy feedback, start writing ww run streak stuff

@@
 }
+
+cod_n_series_lan <- cod_rounds |> 
+  filter(event |> stringr::str_detect('C[Hh][Aa][Mm][Pp]|Major')) |> 
+  distinct(series_id) |> 
+  nrow()
 ```
@@
 
-The data set consists of all SnD matches played in tournanaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
-Data was collected in spreadsheets by community member "IOUTurtle".[^6]
-
-[^6]: Data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>
-
-The empirical offensive round win percentage across all rounds is $\phi_O$ = 47.8%.[^7] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^6] Data was collected in spreadsheets by community member "IOUTurtle".[^7]
+
+[^6]: 288 of the series occur in major tournaments, which are considered to be more "competitive" than the qualifiers since they are played in person (COVID-permitting), whereas the qualifiers are played online.
+
+[^7]: Data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>
+
+The empirical offensive round win percentage across all rounds is $\phi_O$ = 47.8%.[^8] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
@@
 
-[^7]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
+[^8]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
 
@@
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^8] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^9] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^8]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^9]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 [-@gilovich1985], henceforth GVT, do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^9].
+However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^10].
 Specifically, MS say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
@@
 
-[^9]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
+[^10]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
 provides a novel structural candidate explanation for the persistence of gambler's fallacy beliefs", per MS.
@@
 playing either offense or defense for many consecutive rounds).
-On the other hand, teams in CoD SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^10] While theoretically one might be able to account for any kind of balanced rotation, such as a "blocky" on like a 5-5-1, the rotation of team sides every round is convenient, particularly for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+On the other hand, teams in CoD SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^11] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
 Bernoulli trials.
 
-[^10]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
+[^11]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
 
@@
 
-The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^11] is
-
-[^11]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
+The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^12] is
+
+[^12]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
 
@@
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
-\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
 }\label{eq:series-length}\end{equation}
 ```
-$s = 11$ rounds for CoD SnD.[^12]
-
-[^12]: $\phi$ and other symbols are selected so as to avoid reserve symbols, like $p$ for usage in other contexts, without risking confusion.
+$s = 11$ rounds for CoD SnD.[^13]
+
+[^13]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
 Upper-case symbol, e.g.
@@
 p_0(\text{win} | r) = p^{w|r}_0 = \{
-\begin{array}{rcll}
-p^{w|r_W} & = & \frac{m}{r}, & \text{team wins series} \\
-p^{w|r_L} & = & \frac{r - m}{r}, & \text{team loses series}
+\begin{array}{rl}
+\frac{m}{r}, & \text{team wins series} \\
+\frac{r - m}{r}, & \text{team loses series}
 \end{array}
@@
 ```
-using $m$ from Equation \ref{eq:m}. The Bernoulli round loss probability for a series lasting $r$ rounds, $p^{\ell|kr}_0$ (i.e. $\ell = 1 - w, w \in [0, 1]$), can be formulated symmetrically.
-
-As shown by MS, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^13][^14]
-
-[^13]: See Appendix E.1 of MS for details on the proof that follows.
-
-[^14]: Here, I choose symbols, e.g.
-$\pi$, $x$, etc.
-that mostly do not conflict with syntax in other places.
-The exceptions are $k$ and $r$, which are used to represent streak length and number of trials globally.
-
-> Theorem 1: *Let* $\mathbf{X} = \{X_i\}^{r}_{i=1}, r \geq 3$*, be a sequence of independent Bernoulli trials, each with probability of success* $0 < \pi < 1$*.
-Let* $\hat{\Pi}_k(\mathbf{X})$ *be the proportion of successes on the subset of trials* $I_k(\mathbf{X})$ *that immediately follow* $k$ consecutive successes, that is, $\hat{\Pi}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |.
-\hat{\Pi}_k$ *is a biased estimate of* $\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv \pi$ *for all* $k$ *such that* $1 \leq k \leq r - 2$*.
-In particular,* $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < \pi.$
-
-MS notes that there does not exists a closed form representation for $E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]$, henceforth $E^\Pi$, for $k \> 1$.
-One may recursively build a collection of dictionaries to quantify $E^\Pi$ analytically, or, more reasonably for large values of $n$, one may run simulations to estimate the expected value.
-Indeed, Figure 1 uses simulation to estimate $E^\Pi$ as a function of the total number of trials $r$, given $\pi$ and $k$.[^15][^16]
+using $m$ from Equation \ref{eq:m}.
+
+As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^14] Unfortunately, there does not exist a closed form representation for the expectation for $\hat{P}^{w|kr}_{MS}$ for $k > 1$.
+Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value.[^15]
+
+[^14]: See Appendix E.1 of MS for details on the proof that follows.
 
@@
 
-[^16]: Note that $\pi$ and $\hat{\Pi}_k(\mathbf{X})$ are analogues for $p_0^{w|r}$ and $\hat{P}^{w|kr}_{MS}$ in my notation for CoD SnD.
-
-```{r}
-#| label: npkd
-## http://keyonvafa.com/hot-hand/
-get_post_streak_prob <- function(n, k, p = 0.5) {
-  tosses <- rbinom(n, 1, p)
-  runs <- rle(tosses)
-  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
-  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
-
-  ## edge case
-  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
-    n_neg_after <- n_neg_after - 1
-  }
-
-  n_pos_after / (n_pos_after + n_neg_after)
-}
-
-simulate_post_streak_prob <- function(sims = 10000, seed = 42, ...) {
-  withr::local_seed(seed)
-  rerun(
-    sims,
-    get_post_streak_prob(...)
-  ) |> 
-    flatten_dbl() |> 
-    mean(na.rm = TRUE)
-}
-
-# # set.seed(42)
-# # runs <- rerun(
-# #   1000,
-# #   crossing(
-# #     n = 1:50,
-# #     k = 2:4,
-# #     p = 0.5
-# #   ) |>
-# #     mutate(
-# #       next_p = pmap_dbl(list(n, k, p), ~simulate_post_streak_prob(sims = 1000, n = ..1, k = ..2, p = ..3))
-# #     )
-# # ) |>
-# #   reduce(bind_rows)
-# # qs::qsave(runs, 'data/runs_1000x1000_nkp.qs')
-# 
-# library(ggplot2)
-# library(latex2exp)
-# runs <- qs::qread('data/runs_1000x1000_nkp.qs')
-# 
-# agg_runs <- runs |>
-#   filter(!is.nan(next_p)) |>
-#   group_by(p, k, n) |>
-#   summarize(
-#     across(next_p, mean)
-#   ) |>
-#   ungroup() |>
-#   arrange(p, k)
-# 
-# # theme_set(theme_classic())
-# 
-# p <- agg_runs |>
-#   arrange(p, k, n) |>
-#   mutate(
-#     across(k, factor)
-#   ) |>
-#   ggplot() +
-#   aes(x = n, y = next_p, color = k, group = k) +
-#   guides(
-#     color = guide_legend(
-#       title = 'k',
-#       title.hjust = 0.5,
-#       nrow = 1, override.aes = list(size = 3)
-#     )
-#   ) +
-#   geom_line() +
-#   geom_hline(aes(yintercept = p)) +
-#   labs(x = 'r', y = expression(pi)) +
-#   theme_classic() +
-#   theme(
-#     legend.position = c(0.5, 0.8)
-#   )
-# p
-# 
-# ggsave(
-#   p,
-#   filename = 'paper/images/pwkr_ms.png',
-#   width = 5.5,
-#   height = 3
-# )
-```
-
-```{=tex}
-\begin{figure}
-\centering
-\includegraphics{images/pwkr_ms.png}
-\caption{The expected value of the proportion of successes on trials, $E^\Pi$, that immediately follow $k$ consecutive successes for Bernoulli trial success $\pi = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $r$.}
-\end{figure}
-```
-My context is fundamentally different from that of GVT and MS, both of whom focus on longitudinal data in controlled settings.
-GVT also performs statistical tests on shots from players in live games, i.e.
-"observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
-The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series, as shown in Equation \ref{eq:pwr}.
+Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^16] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series, as shown in Equation \ref{eq:pwr}.
 The Bernoulli trial success probability, i.e.
 a round win in CoD SnD, is not independent of the opponent.
-Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{\ell|kr}$, as performed by GVT and MS to evaluate their respective hypothesis regarding post-streak success rates is not appropriate.
+Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{\ell|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rates is not completely appropriate, although useful as a reference.
+
+[^16]: GVT also performs statistical tests on shots from players in live games, i.e.
+"observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
 
@@
 p_0(\text{win} | k, r) = p^{w|kr}_0 =\{
-\begin{array}{rcll}
-p_0^{w|kr_W} & = & \frac{m - k}{i - k}, & \text{team wins series} \\
-p_0^{w|kr_L} & = & \frac{s - m - k}{i - k}, & \text{team loses series}
+\begin{array}{rl}
+\frac{m - k}{i - k}, & \text{team wins series} \\
+\frac{s - m - k}{i - k}, & \text{team loses series}
 \end{array}
@@
 
-If there are $\sigma$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of getting this expected number of successes is
+If there are $r_+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
 
@@
 \begin{equation}\protect\hypertarget{eq:binom}{}{
-\Pr(\sigma) = {\binom {r}{\sigma}} \omega^{\sigma}(1-\omega)^{r-\sigma}.
+\Pr(r_+) = {\binom {r}{r_+}} \omega^{r_+}(1-\omega)^{r-r+}.
 }\label{eq:binom}\end{equation}
 ```
-Plugging in the notional probability $p^{w|kr}_0$ for the null $\omega_0$ and the observed probability $p^{w|kr} = N^{w|kr} \times P^{w|kr}$, where $N^{w|kr}$ is the observed number of instances where a teams wins the round immediately following a $k$-round winning streak in a series lasting $r$ rounds, for the observed $\omega$, we can evaluate whether the observed probability is not significantly different from the notional probability.
-If we reject this hypothesis, then we might consider team momentum, represented by post-streak success, plausible.
-
-Returning to the streak-selection adjustment framework proposed by MS, one can perform the same binomial test, swapping out $p^{w|kr}_0$ with $p^{w|kr}_{MS}$.
-Of course, given the caveats mentioned before, the results should be heeded with caution.
-
+Plugging in the notional probability $p^{w|kr}_0$ for the null $\omega_0$ and the observed probability $p^{w|kr} = N^{w|kr} \times P^{w|kr}$, for the observed $\omega$, where $N^{w|kr}$ is the observed number of instances where a teams wins the round immediately following a $k$-round winning streak in a series lasting $r$ rounds, we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
+If we reject this null hypothesis, then we might consider team momentum, represented by post-streak success, plausible.
+
+One can perform the same binomial test for the MS probability adjusting for streak-selection bias, $p^{w|kr}_{MS}$. Given the caveats mentioned before, the results should be heeded with caution.
+
+Stepping back from the one-sided perspective of a single team's probability of winning and their streakiness, I can attempt to detect the "hot hand" more broadly with the Wald-Wolfowitz runs test, a common tool used in the field of quality control.
+Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable with the following mean $\mu$ and variance $\sigma^2$.
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:ww}{}{
+\mu = \frac{2r_+r_-}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
+}\label{eq:ww}\end{equation}
+```
 # Results
@@
 #| label: cod_round_win_prop_after_k_wins
+## http://keyonvafa.com/hot-hand/
+get_post_streak_prob <- function(n, k, p = 0.5) {
+  tosses <- rbinom(n, 1, p)
+  runs <- rle(tosses)
+  n_neg_after <- length(which(runs$values == 1 & runs$lengths >= k))
+  n_pos_after <- sum(runs$lengths[which(runs$values == 1 & runs$lengths >= k)] - k)
+
+  ## edge case
+  if (n %in% cumsum(runs$lengths)[which(runs$values == 1 & runs$lengths >= k)]) {
+    n_neg_after <- n_neg_after - 1
+  }
+
+  n_pos_after / (n_pos_after + n_neg_after)
+}
+
+simulate_post_streak_prob <- function(sims = 10000, seed = 42, ...) {
+  withr::local_seed(seed)
+  rerun(
+    sims,
+    get_post_streak_prob(...)
+  ) |> 
+    flatten_dbl() |> 
+    mean(na.rm = TRUE)
+}
+
 vectorized_binom_test <- function(x, n, p, ...) {
@@
 
+Regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^21] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+
+[^21]: <https://twitter.com/R11stats>
+
 # Acknowledgements {.unnumbered}

### 2022-08-21 paper/paper.tex
incorporate some andy feedback, start writing ww run streak stuff

@@
 
-The data set consists of all SnD matches played in tournanaments and
-qualifiers during the CDL era, totaling 7,792 rounds across 852 series.
-Data was collected in spreadsheets by community member
+The data set consists of all SnD matches played in major tournaments and
+qualifiers during the CDL era, totaling 7,792 rounds across 852
+series.\footnote{288 of the series occur in major tournaments, which are
+  considered to be more ``competitive'' than the qualifiers since they
+  are played in person (COVID-permitting), whereas the qualifiers are
+  played online.} Data was collected in spreadsheets by community member
 ``IOUTurtle''.\footnote{Data: \url{https://linktr.ee/CDLArchive}.
@@
 The empirical offensive round win percentage across all rounds is
-47.8\%.\footnote{Offensive round win percentage has been nearly constant
-  across the three games during the CDL era: 1. 47.2\% in MW (2020) 2.
-  47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)} Table
-\ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by
-series ``state'' (i.e.~the number of round wins by each team prior to an
-upcoming round). Offensive round win rate is not quite constant,
-although never veers more than 10\% from this global average.
+\(\phi_O\) = 47.8\%.\footnote{Offensive round win percentage has been
+  nearly constant across the three games during the CDL era: 1. 47.2\%
+  in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)}
+Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win
+percentages by series ``state'' (i.e.~the number of round wins by each
+team prior to an upcoming round). Offensive round win rate is not quite
+constant, although never veers more than 10\% from this global average.
 
@@
   leagues, but it was at least one in each league.} While theoretically
-one might be able to account for any kind of balanced rotation, such as
-a ``blocky'' on like a 5-5-1, the rotation of team sides every round is
-convenient, particularly for convincing ourselves that rounds could
-reasonably be modeled as i.i.d. Bernoulli trials.
+one might be able to account for any kind of format, such as a 5-5-1,
+the rotation of team sides every round is convenient for convincing
+ourselves that rounds could reasonably be modeled as i.i.d. Bernoulli
+trials.
 
@@
 \begin{equation}\protect\hypertarget{eq:series-length}{}{
-\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(r - s)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
 }\label{eq:series-length}\end{equation}
@@
 \(s = 11\) rounds for CoD SnD.\footnote{\(\phi\) and other symbols are
-  selected so as to avoid reserve symbols, like \(p\) for usage in other
-  contexts, without risking confusion. Upper-case symbol, e.g.~\(\Phi\),
-  are consistently used in this paper to represent proportions, while
-  lower-case symbols corresponding to proportions represent
-  probabilities. ``Hats'', e.g.~\(\hat{\Phi}\), are used to convey
-  expectations, while ``bare'' symbols mirroring hat-ed symbols convey
-  observational data.}
+  selected so as to reserve symbols like \(p\) for usage in other
+  contexts without causing confusion for the reader. Upper-case symbol,
+  e.g.~\(\Phi\), are consistently used in this paper to represent
+  proportions, while lower-case symbols corresponding to proportions
+  represent probabilities. ``Hats'', e.g.~\(\hat{\Phi}\), are used to
+  convey expectations, while ``bare'' symbols mirroring hat-ed symbols
+  convey observational data.}
 
@@
 
-using \(m\) from Equation \ref{eq:m}. The Bernoulli round loss
-probability for a series lasting \(r\) rounds, \(p^{\ell|kr}_0\)
-(i.e.~\(\ell = 1 - w, w \in [0, 1]\)), can be formulated symmetrically.
+using \(m\) from Equation \ref{eq:m}.
 
-As shown by MS, we should expect the proportion of rounds wins
-immediately following a streak of \(k\) rounds wins for a series lasting
-\(r\) rounds, \(\hat{P}^{w|kr}_{MS}\), to be strictly less than
-\(p^{w|r}\).\footnote{See Appendix E.1 of MS for details on the proof
-  that follows.}\footnote{Here, I choose symbols, e.g.~\(\pi\), \(x\),
-  etc. that mostly do not conflict with syntax in other places. The
-  exceptions are \(k\) and \(r\), which are used to represent streak
-  length and number of trials globally.}
+As shown by MS with their Theorem 1, we should expect the proportion of
+rounds wins immediately following a streak of \(k\) rounds wins for a
+series lasting \(r\) rounds, \(\hat{P}^{w|kr}_{MS}\), to be strictly
+less than \(p^{w|r}\).\footnote{See Appendix E.1 of MS for details on
+  the proof that follows.} Unfortunately, there does not exist a closed
+form representation for the expectation for \(\hat{P}^{w|kr}_{MS}\) for
+\(k > 1\). Nonetheless, one may recursively build a collection of
+dictionaries to compute the expectation analytically, or, more
+conveniently, one may run simulations to estimate the expected
+value.\footnote{I've adapted the code from Vafa (2017), which implements
+  MS's framework (2018).}
 
-\begin{quote}
-Theorem 1: \emph{Let}
-\(\mathbf{X} = \{X_i\}^{r}_{i=1}, r \geq 3\)\emph{, be a sequence of
-independent Bernoulli trials, each with probability of success}
-\(0 < \pi < 1\)\emph{. Let} \(\hat{\Pi}_k(\mathbf{X})\) \emph{be the
-proportion of successes on the subset of trials} \(I_k(\mathbf{X})\)
-\emph{that immediately follow} \(k\) consecutive successes, that is,
-\(\hat{\Pi}_k(\mathbf{X}) := \sum_{i \in I_k(\mathbf{X})} X_i | I_k(\mathbf{X}) |. \hat{\Pi}_k\)
-\emph{is a biased estimate of}
-\(\mathbb{P}(X_t = 1 | \prod_{j=t-k}^{t-1} X_j = 1) \equiv \pi\)
-\emph{for all} \(k\) \emph{such that} \(1 \leq k \leq r - 2\)\emph{. In
-particular,}
-\(E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset] < \pi.\)
-\end{quote}
-
-MS notes that there does not exists a closed form representation for
-\(E[\hat{\Pi}_k(\mathbf{X}) | I_k(\mathbf{X}) \neq \emptyset]\),
-henceforth \(E^\Pi\), for \(k \> 1\). One may recursively build a
-collection of dictionaries to quantify \(E^\Pi\) analytically, or, more
-reasonably for large values of \(n\), one may run simulations to
-estimate the expected value. Indeed, Figure 1 uses simulation to
-estimate \(E^\Pi\) as a function of the total number of trials \(r\),
-given \(\pi\) and \(k\).\footnote{I've adapted the code from Vafa
-  (2017), which implements MS's framework (2018).}\footnote{Note that
-  \(\pi\) and \(\hat{\Pi}_k(\mathbf{X})\) are analogues for
-  \(p_0^{w|r}\) and \(\hat{P}^{w|kr}_{MS}\) in my notation for CoD SnD.}
-
-\begin{figure}
-\centering
-\includegraphics{images/pwkr_ms.png}
-\caption{The expected value of the proportion of successes on trials, $E^\Pi$, that immediately follow $k$ consecutive successes for Bernoulli trial success $\pi = 0.5$ and streak lengths $k \in [2, 3, 4]$, as a function of the total number of trials $r$.}
-\end{figure}
-
-My context is fundamentally different from that of GVT and MS, both of
-whom focus on longitudinal data in controlled settings. GVT also
-performs statistical tests on shots from players in live games,
-i.e.~``observational'' data, but they note that their findings are
-likely affected player shot selection in the face of defensive strategy
-by the opposing team. The number of trials is fixed in their
-experimental designs, but in CoD SnD, the number of rounds played is
-determined as a function of the max number of possible rounds (\(s\))
-and whether or not the team wins the series, as shown in Equation
-\ref{eq:pwr}. The Bernoulli trial success probability, i.e.~a round win
-in CoD SnD, is not independent of the opponent. Consequently, a
-statistical test of the difference in \(\hat{P}^{w|kr}\) and
-\(\hat{P}^{\ell|kr}\), as performed by GVT and MS to evaluate their
-respective hypothesis regarding post-streak success rates is not
-appropriate.
+Although it would be convenient to emulate the hypothesis testing for
+difference of proportions performed by MS (and GVT), my context is
+fundamentally different from that of MS, who focus on longitudinal data
+in controlled settings.\footnote{GVT also performs statistical tests on
+  shots from players in live games, i.e.~``observational'' data, but
+  they note that their findings are likely affected player shot
+  selection in the face of defensive strategy by the opposing team.} The
+number of trials is fixed in their experimental designs, but in CoD SnD,
+the number of rounds played is determined as a function of the max
+number of possible rounds (\(s\)) and whether or not the team wins the
+series, as shown in Equation \ref{eq:pwr}. The Bernoulli trial success
+probability, i.e.~a round win in CoD SnD, is not independent of the
+opponent. Consequently, a statistical test of the difference in
+\(\hat{P}^{w|kr}\) and \(\hat{P}^{\ell|kr}\), as performed by MS to
+evaluate their hypothesis regarding post-streak success rates is not
+completely appropriate, although useful as a reference.
 
@@
 
-If there are \(\sigma\) observed successes in a sample of \(r\) trials
-and we expect that there should be \(r * \omega_0\), the probability of
-getting this expected number of successes is
+If there are \(r_+\) observed successes in a sample of \(r\) trials and
+we expect that there should be \(r * \omega_0\), the probability of
+arriving at this expected number of successes is
 
 \begin{equation}\protect\hypertarget{eq:binom}{}{
-\Pr(\sigma) = {\binom {r}{\sigma}} \omega^{\sigma}(1-\omega)^{r-\sigma}.
+\Pr(r_+) = {\binom {r}{r_+}} \omega^{r_+}(1-\omega)^{r-\sigma}.
 }\label{eq:binom}\end{equation}
@@
 \(\omega_0\) and the observed probability
-\(p^{w|kr} = N^{w|kr} \times P^{w|kr}\), where \(N^{w|kr}\) is the
-observed number of instances where a teams wins the round immediately
-following a \(k\)-round winning streak in a series lasting \(r\) rounds,
-for the observed \(\omega\), we can evaluate whether the observed
-probability is not significantly different from the notional
-probability. If we reject this hypothesis, then we might consider team
-momentum, represented by post-streak success, plausible.
+\(p^{w|kr} = N^{w|kr} \times P^{w|kr}\), for the observed \(\omega\),
+where \(N^{w|kr}\) is the observed number of instances where a teams
+wins the round immediately following a \(k\)-round winning streak in a
+series lasting \(r\) rounds, we can evaluate the null hypothesis that
+the observed probability is equal to the notional probability. If we
+reject this null hypothesis, then we might consider team momentum,
+represented by post-streak success, plausible.
 
-Returning to the streak-selection adjustment framework proposed by MS,
-one can perform the same binomial test, swapping out \(p^{w|kr}_0\) with
-\(p^{w|kr}_{MS}\). Of course, given the caveats mentioned before, the
-results should be heeded with caution.
+One can perform the same binomial test for the MS probability adjusting
+for streak-selection bias, \(p^{w|kr}_{MS}\). Given the caveats
+mentioned before, the results should be heeded with caution.
+
+Stepping back from the one-sided perspective of a single team's
+probability of winning and their streakiness, I can attempt to detect
+the ``hot hand'' more broadly with the Wald-Wolfowitz runs test, a
+common tool used in the field of quality control. Under the null
+hypothesis, the number of runs in a sequence of \(r\) trials is a random
+variable with the following mean \(\mu\) and variance \(\sigma^2\).
+
+\begin{equation}\protect\hypertarget{eq:ww}{}{
+\mu = \frac{2r_+r_-}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
+}\label{eq:ww}\end{equation}
 
@@
 
+\hypertarget{discussion}{%
+\section{Discussion}\label{discussion}}
+
+For the sake of brevity, I did not delve into win rates and streaks
+split by offensive or defensive role. For example, it would be
+interesting to look at whether the round win rate is higher after a
+streaks of three round wins when the team starts the streak winning as
+the offensive team. This would mean that, in the round immediately
+following the streak, the streaking team would be playing defense, where
+teams are slightly more likely to win on average. On the other hand,
+streaks of three starting with an offensive round win---theoretically,
+given \(\phi_O\) = 47.7\% the expected frequency is
+\(\phi_O^2 \times (1 - \phi_O) \approx 0.119\)---are likely to occur
+less frequently than such streaks starting with a defensive
+win---\(\phi_O \times (1 - \phi_O)^2 \approx 0.130\)---so I would want
+to account for sample size differences.
+
+Regarding future work, I've reached out to the Twitter user
+``R11stats'', who privately tracks in-round player
+engagements.\footnote{\url{https://twitter.com/R11stats}} R11stats
+expressed intent on making the data public, which would allow for
+research into player-specific momentum.
+
+\hypertarget{acknowledgements}{%
+\section*{Acknowledgements}\label{acknowledgements}}
+\addcontentsline{toc}{section}{Acknowledgements}
+
+I would like to thank my brother Andrew for giving me feedback on early
+iterations of this paper, and for requiring me to mention him.
+
 \hypertarget{references}{%

### 2022-08-21 scripts/1-scrape-cod.R
data as csvs

@@ -2,8 +2,8 @@
 ## Data from https://twitter.com/IOUTurtle
 library(tidyverse)
 library(googlesheets4)
-library(magrittr)
 library(qs)
+library(readr)
 
 dir_data <- 'data'
 dir.create(dir_data, showWarnings = FALSE)
@@ -244,6 +244,8 @@ cod_rounds <- cod_series |>
     map = sprintf('%s - %s', map, game)
   ) |> 
   relocate(series_id, .after = 'game')
-filename <- 'cod_rounds.qs'
+
+filename <- 'cod_rounds.csv'
+## multiple directories in case knitting doesn't handle subdirectories well
 sprintf('%s/%s', c('data', 'paper', 'presentation'), filename) |> 
-  walk(~qs::qsave(cod_rounds, .x))
+  walk(~write_csv(cod_rounds, .x))

### 2022-08-21 scripts/1-scrape-valorant.R

@@ -337,7 +337,7 @@ val_rounds <- bind_rows(
     more_weird_val_series_outcomes |> distinct(series_id),
     by = 'series_id'
   )
-qs::qsave(val_rounds, 'data/valorant_rounds.qs')
+write_csv(val_rounds, 'data/valorant_rounds.csv')
 
 # val_rounds |> 
 #   group_by(team, series_id) |> 

### 2022-08-21 paper/paper.Rmd
adding breakdown by round i

@@
   - name: Tony ElHabr
-    affiliations:
-      - name: Georgia Institute of Technology
     email: anthonyelhabr@gmail.com
@@
 library(dplyr)
-library(qs)
 library(tidyr)
@@
 
-cod_rounds <- qs::qread('data/cod_rounds.qs')
+cod_rounds <- read_csv('data/cod_rounds.csv')
 ```
@@
 
-## Description of Call of Duty Search and Destroy
+## Game Description
 
@@
 
-The empirical offensive round win percentage across all rounds is $\phi_O$ = 47.8%.[^8] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+The empirical offensive round win percentage across all rounds is $\tau_O$ = 47.8%.[^8] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
-Offensive round win rate is not quite constant, although never veers more than 10% from this global average.
+Offensive round win rate is not quite constant, although never veers more than 10% from this global average.[^9]
 
 [^8]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
+
+[^9]: At tournaments, higher-seeded ("better") teams choose whether they want to start on offense or defense in either the SnD series played as the second game or the fifth game in the best-of-five format used in tournaments, and their opponent is assigned to play offense in the first round of the SnD slot (second or fifth game) not chosen.
+[@codrules] (Other game variants like Hardpoint are played as the first, third, and fourth games in the matchup.) Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game, although this choice is not universal.
+With online qualifiers, teams all play each other twice throughout the season.
+Each team gets to play the higher-seeded role once in their matchups, despite their win-loss records.
 
@@
   ) |>
-  gt::as_latex()
+  gt::as_latex() |> 
+  cat()
 ```
@@
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^9] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^10] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^9]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^10]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 [-@gilovich1985], henceforth GVT, do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^10].
+However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^11].
 Specifically, MS say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
@@
 
-[^10]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
+[^11]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
 provides a novel structural candidate explanation for the persistence of gambler's fallacy beliefs", per MS.
@@
 playing either offense or defense for many consecutive rounds).
-On the other hand, teams in CoD SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^11] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+On the other hand, teams in CoD SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^12] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
 Bernoulli trials.
 
-[^11]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
+[^12]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
 
@@
 
-The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^12] is
-
-[^12]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
+The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^13] is
+
+[^13]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
 
@@
 ```
-$s = 11$ rounds for CoD SnD.[^13]
-
-[^13]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
+$s = 11$ rounds for CoD SnD.[^14]
+
+[^14]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
 Upper-case symbol, e.g.
@@
 
-As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^14] Unfortunately, there does not exist a closed form representation for the expectation for $\hat{P}^{w|kr}_{MS}$ for $k > 1$.
-Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value.[^15]
-
-[^14]: See Appendix E.1 of MS for details on the proof that follows.
-
-[^15]: I've adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
-
-Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^16] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series, as shown in Equation \ref{eq:pwr}.
+As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^15] Unfortunately, there does not exist a closed form representation for the expectation for $\hat{P}^{w|kr}_{MS}$ for $k > 1$.
+Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value.[^16]
+
+[^15]: See Appendix E.1 of MS for details on the proof that follows.
+
+[^16]: I've adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^17] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series, as shown in Equation \ref{eq:pwr}.
 The Bernoulli trial success probability, i.e.
@@
 
-[^16]: GVT also performs statistical tests on shots from players in live games, i.e.
+[^17]: GVT also performs statistical tests on shots from players in live games, i.e.
 "observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
@@
 using $m$ from Equation \ref{eq:m}.
-We can perform a binomial test to test the null hypothesis $H_0 : \omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^17]
-
-[^17]: $\omega$ and other symbols are chosen so as to not conflict with symbols already used elsewhere for in other equations, either generic or for CoD SnD specifically.
+We can perform a binomial test to test the null hypothesis $H_0 : \omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^18]
+
+[^18]: $\omega$ and other symbols are chosen so as to not conflict with symbols already used elsewhere for in other equations, either generic or for CoD SnD specifically.
 
@@
 
-Stepping back from the one-sided perspective of a single team's probability of winning and their streakiness, I can attempt to detect the "hot hand" more broadly with the Wald-Wolfowitz runs test, a common tool used in the field of quality control.
+Stepping back from the one-sided perspective of a single team's probability of winning and their streakiness, one can attempt to detect the "hot hand" more broadly with the Wald-Wolfowitz runs test, a common tool used in the field of quality control.
 Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable with the following mean $\mu$ and variance $\sigma^2$.
@@
 ```
+One might subset observed series sequences to those that violate the run test null hypothesis and perform a proportions test where the null is that the observe rate of such series is equal to the frequency that we should expect, given a choice for the constant round win probability $\phi$.
+If the
+
 # Results
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^18] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^19] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^18]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+[^19]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 
-summarize_cod_win_prop_after_k_wins <- function(k, ...) {
-  probs_nx_k <- crossing(
-    n_rounds = 7L:11L,
-    win_series = c(TRUE, FALSE),
-    win_round = c(TRUE, FALSE)
-  ) |> 
+compute_probs_nx_k <- function(df, k) {
+  df |> 
     mutate(
@@
     )
+}
+
+summarize_cod_win_prop_after_k_wins <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    win_series = c(TRUE, FALSE),
+    win_round = c(TRUE, FALSE)
+  ) |> 
+    compute_probs_nx_k(k)
 
@@
 
-summarize_cod_win_prop_after_k_wins_i_rounds <- function(k) {
-  probs_nx_k <- crossing(
-    n_rounds = 7L:11L,
-    round = 3L:11L,
-    win_series = c(TRUE, FALSE),
-    win_round = c(TRUE, FALSE)
-  ) |> 
-    filter(round >= (!!k + 1L)) |> 
-    mutate(
-      is_valid = case_when(
-        win_series ~ TRUE,
-        (n_rounds - !!k - 6L) >= 0L ~ TRUE,
-        TRUE ~ FALSE
-      )
-    ) |> 
-    filter(is_valid) |> 
-    select(-is_valid) |> 
-    mutate(
-      naive_prop = ifelse(win_series, 6L / n_rounds, (n_rounds - 6L) / n_rounds),
-      notional_prop = (ifelse(win_series, 6L, n_rounds - 6L) - k) / (n_rounds - k),
-      across(c(naive_prop, notional_prop), ~ifelse(win_round, .x, 1 - .x)),
-      ms_prop = map2_dbl(
-        n_rounds, naive_prop, 
-        ~simulate_post_streak_prob(n = ..1, k = !!k, p = ..2)
-      ),
-      across(
-        ms_prop,
-        ~ifelse(win_round, .x, naive_prop + (naive_prop - .x))
-      )
-    )
-
-  postprocess_round_streaks(
-    k = k,
-    probs_nx_k = probs_nx_k,
-    round
-  )
-}
-
 cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
@@
 cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value < 0.05)
-
-tibble(win_streak = 1L) |>
-  mutate(
-    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
-  ) |>
-  unnest(data) |> 
-  filter(win_round, notional_p_value < 0.05)
-
-cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 1L:3L) |>
-  mutate(
-    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
-  ) |>
-  unnest(data)
-cod_round_win_prop_after_k_wins_i_rounds |> 
-  filter(notional_prop < prop, notional_p_value < 0.05) |> 
-  filter(n_rounds == round) |> 
-  filter(win_streak == 1) |> 
-  group_by(n_rounds, round) |> 
-  mutate(
-    total = sum(n),
-    prop = n / total
-  )
+# bonferroni correction?
+cod_round_win_prop_after_k_wins |> 
+  mutate(
+    n = n(),
+    p2 = notional_p_value |> p.adjust(),
+    p3 = ms_p_value |> p.adjust()
+  ) |> 
+  filter(win_streak == 3, win_round)
 ```
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^19] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively.
-
-[^19]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
-
-```{=tex}
-\begin{longtable}{rrrrrr}
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^20] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively.
+
+[^20]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+
+```{=tex}
+\begin{longtable}{rlrrrr}
 \caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, given the length of the series ($r$ rounds) and the series winner.
@@
 ```
-We observe that, with the exception of $\hat{P}^{w|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^20], all binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
+We observe that, with the exception of $\hat{P}^{w|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^21], all binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
 As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
 
-[^20]: This implies that the opponent, th eventual series winner, goes on to win the series 6-4 after going down 0-4.
+[^21]: This implies that the opponent, th eventual series winner, goes on to win the series 6-4 after going down 0-4.
 This is the only scenario in which one team wins four rounds consecutively but loses a best-of-11 series in 10 rounds.
@@
 
+```{r}
+#| label: cod_round_win_prop_after_k_wins_i_rounds
+summarize_cod_win_prop_after_k_wins_i_rounds <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    round = 3L:11L,
+    win_series = c(TRUE, FALSE),
+    win_round = c(TRUE, FALSE)
+  ) |> 
+    filter(round >= (!!k + 1L)) |> 
+    compute_probs_nx_k(k)
+
+  postprocess_round_streaks(
+    k = k,
+    probs_nx_k = probs_nx_k,
+    round
+  )
+}
+
+cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 1L:3L) |>
+  mutate(
+    data = map(win_streak, summarize_cod_win_prop_after_k_wins_i_rounds)
+  ) |>
+  unnest(data) |> 
+  select(-starts_with('ms')) |> 
+  group_by(win_streak, n_rounds, round) |> 
+  mutate(
+    total = sum(n),
+    prop = n / total
+  ) |> 
+  ungroup() |> 
+  mutate(
+    notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value |> round(2)
+  )
+
+## 5-3?
+cod_round_win_prop_after_k_wins_i_rounds |> 
+  filter(win_streak == 2) |> 
+  filter(n_rounds == 11, round == 11)
+```
+
+```{r}
+#| label: cod_round_win_prop_after_k_wins_i_rounds-table
+# cod_round_win_prop_after_k_wins_i_rounds |> 
+#   filter(win_streak == 3) |> 
+#   mutate(
+#     n = n(),
+#     p2 = notional_p_value |> p.adjust()
+#   ) |> 
+#   filter(!win_round) |> 
+#   # filter(notional_p_value < 0.05) |> 
+#   filter(n_rounds <= (round + 2)) |> 
+#   filter(n_rounds >= 9)
+
+cod_round_win_prop_after_k_wins_i_rounds |> 
+  mutate(
+    p2 = notional_p_value |> p.adjust()
+  ) |> 
+  filter(win_streak == 3) |> 
+  filter(win_round) |> 
+  # filter(notional_p_value < 0.05) |> 
+  filter(n_rounds <= (round + 2)) |> 
+  filter(n_rounds >= 9) |> 
+  # filter(n_rounds == round) |> 
+  # filter(notional_prop < prop) |> 
+  mutate(
+    across(
+      matches('p_value'), 
+      ~case_when(
+        .x <= 0.01 ~ '<=0.01', 
+        TRUE ~ sprintf('%.2f', .x)
+      )
+    ),
+    prop_lab = scales::percent(prop, accuracy = 0.1),
+    notional_lab = sprintf('%.1f%% (%s)', round(100 * notional_prop, 1), notional_p_value)
+  ) |>
+  arrange(n_rounds, round, win_series, win_round) |> 
+  transmute(
+    n_rounds,
+    round,
+    across(win_series, ~ifelse(.x, 'yes', 'no')),
+    total,
+    prop_lab,
+    notional_lab,
+    prop_is_gt = ifelse(prop > notional_prop, 'yes', 'no')
+  ) |> 
+  gt::gt() |> 
+  gt::cols_label(
+    n_rounds = 'r',
+    round = 'i',
+    win_series = 'Win series?',
+    total = 'N',
+    prop_lab = 'O',
+    notional_lab = 'a',
+    prop_is_gt = 'b'
+  ) |> 
+  gt::as_latex() |> 
+  cat()
+
+```
+
+Now let us explicitly consider the round, $i$.
+As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{w|kri}_0$, is statistically different than the observed $P^{w|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^22] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases (as well in a strong majority of cases not shown).
+
+[^22]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
+
+```{=tex}
+\begin{longtable}{rrlrrrl}
+\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count and proportion of round wins immediately following the streak, $N^{w|kri}$ and $P^{w|kri}$ respectively.
+Additionally, the notional proportion, $\hat{P}^{w|kri}_0$, and the $p$-value of a binomial test comparing the underlying notional $p^{w|kri}_0$ to the probability implied by the observed proportion $p^{w|kri} = N^{w|kri} \times P^{w|kri}$.
+Table restricted to $r \in [9, 10, 11]$ and $r - 2 \leq i \leq r$ for brevity.}
+\label{tbl:cod-pw3ri-pl3ri} \\
+\toprule
+$r$ & $i$ & \text{Win series?} & $N^{w|kri}$ & $P^{w|kri}$ & $\hat{P}^{w|kri}_0$ ($p$-value) & $\hat{P}^{w|kri}_0 > P^{w|kri}$ \\
+
+9 & 7 & yes & 36 & 41.7\% & 50.0\% (0.41) & no \\ 
+9 & 8 & yes & 40 & 45.0\% & 50.0\% (0.64) & no \\ 
+9 & 9 & yes & 37 & 89.2\% & 50.0\% (<=0.01) & yes \\ 
+10 & 8 & no & 37 & 2.7\% & 14.3\% (0.06) & no \\ 
+10 & 8 & yes & 37 & 24.3\% & 42.9\% (0.03) & no \\ 
+10 & 9 & no & 32 & 6.2\% & 14.3\% (0.31) & no \\ 
+10 & 9 & yes & 32 & 12.5\% & 42.9\% (<=0.01) & no \\ 
+10 & 10 & yes & 29 & 72.4\% & 42.9\% (<=0.01) & yes \\ 
+11 & 9 & no & 32 & 15.6\% & 25.0\% (0.31) & no \\ 
+11 & 9 & yes & 32 & 31.2\% & 37.5\% (0.58) & no \\ 
+11 & 10 & no & 36 & 13.9\% & 25.0\% (0.18) & no \\ 
+11 & 10 & yes & 36 & 13.9\% & 37.5\% (<=0.01) & no \\ 
+11 & 11 & yes & 32 & 53.1\% & 37.5\% (0.10) & yes \\
+
+\bottomrule
+\end{longtable}
+```
 # Discussion
@@
 This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round win---theoretically, given $\phi_O$ = 47.7% the expected frequency is $\phi_O^2 \times (1 - \phi_O) \approx 0.119$---are likely to occur less frequently than such streaks starting with a defensive win---$\phi_O \times (1 - \phi_O)^2 \approx 0.130$---so I would want to account for sample size differences.
-
-Regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^21] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
-
-[^21]: <https://twitter.com/R11stats>
+On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx 0.119$---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx 0.130$---so I would want to account for sample size differences.
+
+Further regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^23] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+
+[^23]: <https://twitter.com/R11stats>
 
@@
 
-I would like to thank my brother Andrew for giving me feedback on early iterations of this paper, and for requiring me to mention him.
+I would like to thank my brother Andrew for giving me feedback on early iterations of this paper.
 

### 2022-08-21 paper/paper.tex
adding breakdown by round i

@@
 
-\hypertarget{description-of-call-of-duty-search-and-destroy}{%
-\subsection{Description of Call of Duty Search and
-Destroy}\label{description-of-call-of-duty-search-and-destroy}}
+\hypertarget{game-description}{%
+\subsection{Game Description}\label{game-description}}
 
@@
 The empirical offensive round win percentage across all rounds is
-\(\phi_O\) = 47.8\%.\footnote{Offensive round win percentage has been
+\(\tau_O\) = 47.8\%.\footnote{Offensive round win percentage has been
   nearly constant across the three games during the CDL era: 1. 47.2\%
@@
 team prior to an upcoming round). Offensive round win rate is not quite
-constant, although never veers more than 10\% from this global average.
+constant, although never veers more than 10\% from this global
+average.\footnote{At tournaments, higher-seeded (``better'') teams
+  choose whether they want to start on offense or defense in either the
+  SnD series played as the second game or the fifth game in the
+  best-of-five format used in tournaments, and their opponent is
+  assigned to play offense in the first round of the SnD slot (second or
+  fifth game) not chosen. ({``Competitive Settings \textbar{} Call of
+  Duty League,''} n.d.) (Other game variants like Hardpoint are played
+  as the first, third, and fourth games in the matchup.) Anecdotally,
+  the higher-seeded teams tend to choose to play defense in the first
+  round of the SnD series played as the second game, although this
+  choice is not universal. With online qualifiers, teams all play each
+  other twice throughout the season. Each team gets to play the
+  higher-seeded role once in their matchups, despite their win-loss
+  records.}
 
@@
 \begin{equation}\protect\hypertarget{eq:binom}{}{
-\Pr(r_+) = {\binom {r}{r_+}} \omega^{r_+}(1-\omega)^{r-\sigma}.
+\Pr(r_+) = {\binom {r}{r_+}} \omega^{r_+}(1-\omega)^{r-r+}.
 }\label{eq:binom}\end{equation}
@@
 Stepping back from the one-sided perspective of a single team's
-probability of winning and their streakiness, I can attempt to detect
+probability of winning and their streakiness, one can attempt to detect
 the ``hot hand'' more broadly with the Wald-Wolfowitz runs test, a
@@
 }\label{eq:ww}\end{equation}
+
+One might subset observed series sequences to those that violate the run
+test null hypothesis and perform a proportions test where the null is
+that the observe rate of such series is equal to the frequency that we
+should expect, given a choice for the constant round win probability
+\(\phi\). If the
 
@@
 
+Now let us explicitly consider the round, \(i\). As shown in Table
+\ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round \(i\)
+immediately following a streak of \(k\) round wins in a series lasting
+\(r\) rounds, \(\hat{P}{w|kri}_0\), is statistically different than the
+observed \(P^{w|kri}\) in several cases, notably when \(r = i\) for each
+of \(r \in [9, 10, 11]\).\footnote{The null can also be rejected for
+  \(r \in [7, 8]\), although these are not shown, and the sample sizes
+  are smaller.} Interestingly, the observed rate is greater than the
+expected rate in each case where we can reject the null hypothesis,
+whereas the observed rate is less than the expected rate in all other
+cases (as well in a strong majority of cases not shown).
+
+\begin{longtable}{rrrrrr}
+\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count and proportion of round wins immediately following the streak, $N^{w|kri}$ and $P^{w|kri}$ respectively.
+Additionally, the notional proportion, $\hat{P}^{w|kri}_0$, and the $p$-value of a binomial test comparing the underlying notional $p^{w|kri}_0$ to the probability implied by the observed proportion $p^{w|kri} = N^{w|kri} \times P^{w|kri}$.
+Table restricted to $r \in [9, 10, 11]$ and $r - 2 \leq i \leq r$ for brevity.}
+\label{tbl:cod-pw3ri-pl3ri} \\
+\toprule
+$r$ & $i$ & \text{Win series?} & $N^{w|kri}$ & $P^{w|kri}$ & $\hat{P}^{w|kri}_0$ ($p$-value) & $\hat{P}^{w|kri}_0 > P^{w|kri}$ \\
+
+9 & 7 & yes & 36 & 41.7\% & 50.0\% (0.41) & no \\ 
+9 & 8 & yes & 40 & 45.0\% & 50.0\% (0.64) & no \\ 
+9 & 9 & yes & 37 & 89.2\% & 50.0\% (<=0.01) & yes \\ 
+10 & 8 & no & 37 & 2.7\% & 14.3\% (0.06) & no \\ 
+10 & 8 & yes & 37 & 24.3\% & 42.9\% (0.03) & no \\ 
+10 & 9 & no & 32 & 6.2\% & 14.3\% (0.31) & no \\ 
+10 & 9 & yes & 32 & 12.5\% & 42.9\% (<=0.01) & no \\ 
+10 & 10 & yes & 29 & 72.4\% & 42.9\% (<=0.01) & yes \\ 
+11 & 9 & no & 32 & 15.6\% & 25.0\% (0.31) & no \\ 
+11 & 9 & yes & 32 & 31.2\% & 37.5\% (0.58) & no \\ 
+11 & 10 & no & 36 & 13.9\% & 25.0\% (0.18) & no \\ 
+11 & 10 & yes & 36 & 13.9\% & 37.5\% (<=0.01) & no \\ 
+11 & 11 & yes & 32 & 53.1\% & 37.5\% (0.10) & yes \\
+
+\bottomrule
+\end{longtable}
+
 \hypertarget{discussion}{%
@@
 streaks of three starting with an offensive round win---theoretically,
-given \(\phi_O\) = 47.7\% the expected frequency is
-\(\phi_O^2 \times (1 - \phi_O) \approx 0.119\)---are likely to occur
+given \(\tau_O\) = 47.7\% the expected frequency is
+\(\tau_O^2 \times (1 - \tau_O) \approx 0.119\)---are likely to occur
 less frequently than such streaks starting with a defensive
-win---\(\phi_O \times (1 - \phi_O)^2 \approx 0.130\)---so I would want
+win---\(\tau_O \times (1 - \tau_O)^2 \approx 0.130\)---so I would want
 to account for sample size differences.
 
-Regarding future work, I've reached out to the Twitter user
+Further regarding future work, I've reached out to the Twitter user
 ``R11stats'', who privately tracks in-round player
@@
 I would like to thank my brother Andrew for giving me feedback on early
-iterations of this paper, and for requiring me to mention him.
+iterations of this paper.
 
@@
 \url{https://doi.org/10.3233/JSA-200422}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-codrules}{}}%
+{``Competitive Settings \textbar{} Call of Duty League.''} n.d.
+\url{https://callofdutyleague.com/en-us/competitive-settings?tab=map-veto}.
 

### 2022-08-21 paper/paper.Rmd
knitted i table

@@
 ```{=tex}
-\begin{longtable}{rlrrrr}
+\begin{longtable}{rcrrrr}
 \caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, given the length of the series ($r$ rounds) and the series winner.
@@
 
+cod_round_win_prop_after_k_wins_i_rounds |> 
+  filter(win_streak == 3, n_rounds == round) |> 
+  filter(!win_series)
+
 ## 5-3?
@@
   filter(win_streak == 3) |> 
-  filter(win_round) |> 
-  # filter(notional_p_value < 0.05) |> 
-  filter(n_rounds <= (round + 2)) |> 
+  filter(!win_round) |> 
+  # filter(n_rounds <= (round + 2)) |> 
+  filter(n_rounds == round) |> 
   filter(n_rounds >= 9) |> 
-  # filter(n_rounds == round) |> 
-  # filter(notional_prop < prop) |> 
   mutate(
@@
 Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{w|kri}_0$, is statistically different than the observed $P^{w|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^22] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases (as well in a strong majority of cases not shown).
+As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{w|kri}_0$, is statistically different than the observed $P^{w|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^22] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
+Since
 
@@
 ```{=tex}
-\begin{longtable}{rrlrrrl}
+\begin{longtable}{rrcrrrc}
 \caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count and proportion of round wins immediately following the streak, $N^{w|kri}$ and $P^{w|kri}$ respectively.
@@
 \toprule
-$r$ & $i$ & \text{Win series?} & $N^{w|kri}$ & $P^{w|kri}$ & $\hat{P}^{w|kri}_0$ ($p$-value) & $\hat{P}^{w|kri}_0 > P^{w|kri}$ \\
-
+$r$ & $i$ & \text{Win series?} & $N^{w|kri}$ & $P^{w|kri}$ & $\hat{P}^{w|kri}_0$ ($p$-value) & $\hat{P}^{w|kri}_0 < P^{w|kri}$ \\ 
+\midrule
 9 & 7 & yes & 36 & 41.7\% & 50.0\% (0.41) & no \\ 
 9 & 8 & yes & 40 & 45.0\% & 50.0\% (0.64) & no \\ 
-9 & 9 & yes & 37 & 89.2\% & 50.0\% (<=0.01) & yes \\ 
+9 & 9 & yes & 37 & 89.2\% & 50.0\% (\textless=0.01) & yes \\ 
 10 & 8 & no & 37 & 2.7\% & 14.3\% (0.06) & no \\ 
@@
 10 & 9 & no & 32 & 6.2\% & 14.3\% (0.31) & no \\ 
-10 & 9 & yes & 32 & 12.5\% & 42.9\% (<=0.01) & no \\ 
-10 & 10 & yes & 29 & 72.4\% & 42.9\% (<=0.01) & yes \\ 
+10 & 9 & yes & 32 & 12.5\% & 42.9\% (\textless=0.01) & no \\ 
+10 & 10 & yes & 29 & 72.4\% & 42.9\% (\textless=0.01) & yes \\ 
 11 & 9 & no & 32 & 15.6\% & 25.0\% (0.31) & no \\ 
@@
 11 & 10 & no & 36 & 13.9\% & 25.0\% (0.18) & no \\ 
-11 & 10 & yes & 36 & 13.9\% & 37.5\% (<=0.01) & no \\ 
+11 & 10 & yes & 36 & 13.9\% & 37.5\% (\textless=0.01) & no \\ 
 11 & 11 & yes & 32 & 53.1\% & 37.5\% (0.10) & yes \\ 
-
 \bottomrule
@@
 This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx 0.119$---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx 0.130$---so I would want to account for sample size differences.
+On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx$ 13.0%---so I would want to account for sample size differences.
 

### 2022-08-21 paper/paper.tex
knitted i table

@@
 
-\begin{longtable}{rrrrrr}
+\begin{longtable}{rcrrrr}
 \caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, given the length of the series ($r$ rounds) and the series winner.
@@
 
-\begin{longtable}{rrrrrr}
+\begin{longtable}{rrcrrrc}
 \caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count and proportion of round wins immediately following the streak, $N^{w|kri}$ and $P^{w|kri}$ respectively.

### 2022-08-21 scripts/1-scrape-cod.R
data saving again

@@ -245,7 +245,8 @@ cod_rounds <- cod_series |>
   ) |> 
   relocate(series_id, .after = 'game')
 
-filename <- 'cod_rounds.csv'
 ## multiple directories in case knitting doesn't handle subdirectories well
-sprintf('%s/%s', c('data', 'paper', 'presentation'), filename) |> 
-  walk(~write_csv(cod_rounds, .x))
+# filename <- 'cod_rounds.csv'
+# sprintf('%s/%s', c('data', 'paper', 'presentation'), filename) |> 
+#   walk(~write_csv(cod_rounds, .x, na = ''))
+write_csv(cod_rounds, 'data/cod_rounds.csv', na = '')

### 2022-08-21 paper/paper.Rmd
re-reading, added all tables, by p-value adj, no p-values in tables

@@
 Second, I examine post-streak round win probability, given the series outcome.
-I find no evidence that post-streak win rate is significantly different than expected for combinations of streak length, series length, and series winner, suggesting that the perception of momentum at the team level is deceiving.
+I find no evidence that post-streak win rate is significantly different than expected for combinations of streak length, series length, and series winner, suggesting that the perception of momentum at the team level is just that, perception.
 bibliography: references.bib  
@@
 A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
+Further, it is analogous to a trial in statistical analysis of Bernoulli events.
 
@@
 
-[^7]: Data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>
+[^7]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Processed data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
 
@@
 Most assume a constant probability $\phi$ of a given team winning a game in the series, regardless of the series state.
-Mosteller [-@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that matchups should not modeled with $\phi = 0.5$.
-Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\phi \approx 0.65$.
-in each case: (1) solving for $p$ from the empirical average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
-maximum likelihood), and (3) minimizing the chi-square goodness of fit statistic for $\phi$.
+Mosteller [-@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that games should not be modeled with a constant (null) $\phi_0 = 0.5$.
+Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\phi \approx 0.65$ in each case: (1) solving for $p$ from the empirical average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
+maximum likelihood), and (3) minimizing the chi-square goodness of fit statistic $\chi^2$ for $\phi$.
 
 Chance [-@chance2020] re-examines the constant probability notion in Major League Baseball's (MLB) World Series (1923--2018), the National Basketball Association's (NBA) Finals (1951--2018), and the National Hockey League's (NHL) Stanley Cup (1939--2018).
-Chance finds strong evidence against the null hypothesis of $\phi = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.
+Chance finds strong evidence against the null hypothesis of $\phi_0 = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.
 Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^10] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and "hot hand fallacy" (positive recency).
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^10] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily in esports.
-Work has been done to examine in-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
-However, research on round-level trends is sparse, perhaps because games like Counter-Strike and Valorant both have economic aspects that can create clear advantages on side in a given round, given how prior rounds played out.
-
-Additionally, both Counter-Strike and Valorant have overtime rules and blocked offensive/defensive roles (i.e.
-playing either offense or defense for many consecutive rounds).
-On the other hand, teams in CoD SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^12] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+Other research has borrowed a common approach from the field of quality control, looking at unlikely sequences of events with the Wald-Wolfowitz runs test [@peel2015], [@steeger2021].
+Peel and Clauset find no evidence for unlikely sequences of scoring events in the NHL, College Football (CFB), and National Football League (NFL), but do in the NBA.
+As a check on their entropy approach to momentum identification, Steeger et al.
+found three NHL teams who sequence of wins in the 2018-2019 regular season violated the Wald-Wolfowitz null hypothesis, although these teams did not match the teams identified with their primary approach.
+
+## My contribution
+
+Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily, if at all, in esports.
+Work has been done to examine intra-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
+However, considering Counter-Strike and Valorant specifically, research on round-level trends seems non-existant, perhaps for one of many reasons:
+
+1.
+Both have economic aspects that can create clear advantages for one side in a given round, given how prior rounds played out.
+CoD has no such equivalent, except for perhaps "kill streaks", which infrequently play a role.
+2.
+Teams play either offense or defense for many consecutive rounds.
+(The former has a 14-14-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^12] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
 Bernoulli trials.
+3.  Both Counter-Strike and Valorant have overtime rules---team must win by two rounds---which can make end-of-series sequences difficult to model. CoD SnD does not have overtime rules.
 
@@
 
+To my knowledge, there is no existing public statistical research on CoD SnD format, beyond descriptive analysis on social media.
+While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation on a common concept like the hot-hand phenomenon in a new field---particularly one that is less subjected to factors that may be difficult to control for, e.g.
+weather---should hopefully be useful as a precedent or supplement for future researchers.
+
 # Methodology
 
-## Distribution of rounds played {#sec:method-rounds-played}
+## Distribution of rounds played
 
@@
 
-## Momentum {#sec:method-momentum}
+## Momentum
+
+### MS post-streak probability
 
@@
 \begin{equation}\protect\hypertarget{eq:pwr}{}{
-p_0(\text{win} | r) = p^{w|r}_0 = \{
-\begin{array}{rl}
+p_0(\text{win} | r) = p^{+|r}_0 = \{
+\begin{array}{cl}
 \frac{m}{r}, & \text{team wins series} \\
@@
 
-As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{w|kr}_{MS}$, to be strictly less than $p^{w|r}$.[^15] Unfortunately, there does not exist a closed form representation for the expectation for $\hat{P}^{w|kr}_{MS}$ for $k > 1$.
-Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value.[^16]
-
-[^15]: See Appendix E.1 of MS for details on the proof that follows.
-
-[^16]: I've adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
-
-Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^17] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series, as shown in Equation \ref{eq:pwr}.
+As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|kr}_{MS}$, to be strictly less than $p^{+|r}$.[^15] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|kr}_{MS}$ for $k > 1$.
+Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value, as I choose to do.[^16]
+
+[^15]: See Appendix E.1 of MS for the proof.
+
+[^16]: I have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^17] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
 The Bernoulli trial success probability, i.e.
 a round win in CoD SnD, is not independent of the opponent.
-Consequently, a statistical test of the difference in $\hat{P}^{w|kr}$ and $\hat{P}^{\ell|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rates is not completely appropriate, although useful as a reference.
+Consequently, a statistical test of the difference in $\hat{P}^{+|kr}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rates, is not completely appropriate, although useful as a reference.
 
@@
 
-One might consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{w|kr}_0$.
-The Bernoulli round win probability underlying $\hat{P}^{w|kr}_0$ is
+### "Notional" post-streak probability
+
+One might consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|kr}_0$.
+The Bernoulli round win probability underlying $\hat{P}^{+|kr}_0$ is
 
@@
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-p_0(\text{win} | k, r) = p^{w|kr}_0 =\{
-\begin{array}{rl}
-\frac{m - k}{i - k}, & \text{team wins series} \\
-\frac{s - m - k}{i - k}, & \text{team loses series}
+p_0(\text{win} | k, r) = p^{+|kr}_0 =\{
+\begin{array}{cl}
+\frac{m - k}{r - k}, & \text{team wins series} \\
+\frac{s - m - k}{r - k}, & \text{team loses series}
 \end{array}
@@
 using $m$ from Equation \ref{eq:m}.
-We can perform a binomial test to test the null hypothesis $H_0 : \omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^18]
+
+We can perform a binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^18] If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
 
 [^18]: $\omega$ and other symbols are chosen so as to not conflict with symbols already used elsewhere for in other equations, either generic or for CoD SnD specifically.
-
-If there are $r_+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
 
@@
 \begin{equation}\protect\hypertarget{eq:binom}{}{
-\Pr(r_+) = {\binom {r}{r_+}} \omega^{r_+}(1-\omega)^{r-r+}.
+\Pr(r^w) = {\binom {r}{r^+}} \omega^{r^+}(1-\omega)^{r-r^+}.
 }\label{eq:binom}\end{equation}
 ```
-Plugging in the notional probability $p^{w|kr}_0$ for the null $\omega_0$ and the observed probability $p^{w|kr} = N^{w|kr} \times P^{w|kr}$, for the observed $\omega$, where $N^{w|kr}$ is the observed number of instances where a teams wins the round immediately following a $k$-round winning streak in a series lasting $r$ rounds, we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
-If we reject this null hypothesis, then we might consider team momentum, represented by post-streak success, plausible.
-
-One can perform the same binomial test for the MS probability adjusting for streak-selection bias, $p^{w|kr}_{MS}$. Given the caveats mentioned before, the results should be heeded with caution.
-
-Stepping back from the one-sided perspective of a single team's probability of winning and their streakiness, one can attempt to detect the "hot hand" more broadly with the Wald-Wolfowitz runs test, a common tool used in the field of quality control.
-Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable with the following mean $\mu$ and variance $\sigma^2$.
+Plugging in the notional proportion $\hat{p}^{+|kr}_0$ for the null $\omega_0$ and the observed proportion $P^{+|kr}$ for $\omega$ (treating proportions as probabilities), we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
+If we can reject this null hypothesis, then we might consider team momentum, represented by post-streak success, plausible.
+
+One can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|kr}_{MS}$. FOOTY: Given the caveats mentioned before, the results should be heeded with caution.
+
+We can further decompose Equation \ref{eq:pwkr} by the round $i$ ($i \leq r$) in which the streak of length $k$ carries into.
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:pwkri}{}{
+p_0(\text{win} | k, r, i) = p^{+|kri}_0 =\{
+\begin{array}{cl}
+\frac{m - k}{r - k}, & \text{team wins series}, i \neq r \\
+1, & \text{team wins series}, i = r \\
+\frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r \\
+0, & \text{team loses series}, i = r
+\end{array}
+}
+\label{eq:pwkri}
+\end{equation}
+```
+Again, one might apply a binomial test to evaluate the hypothesis that the expected proportions, both $\hat{P}^{+|kri}_0$ and $\hat{P}^{+|kri}_{MS}$, are equal to the observed proportion $P^{+|kr}$.
+
+### Wald-Wolfowitz runs test
+
+Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with the Wald-Wolfowitz runs test.
+Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable, which can take on values $r^+$ and $r^-$ for success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$.
 
@@
 \begin{equation}\protect\hypertarget{eq:ww}{}{
-\mu = \frac{2r_+r_-}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
+\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
 }\label{eq:ww}\end{equation}
 ```
-One might subset observed series sequences to those that violate the run test null hypothesis and perform a proportions test where the null is that the observe rate of such series is equal to the frequency that we should expect, given a choice for the constant round win probability $\phi$.
-If the
+One might subset observed series sequences to those that violate the run test null hypothesis and perform a test of proportions, where the null is that the observed rate of such series is equal to the frequency that we should expect, given a choice for the constant round win probability $\phi$.
+If we can reject the null, then we can argue in favor of the hot hand.
 
@@
 
-## Distribution of rounds played {#sec:results-rounds-played}
+## Distribution of rounds played
 
@@
 
-## Momentum {#sec:results-momentum}
+## Momentum
 
@@
 cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value < 0.05)
-# bonferroni correction?
-cod_round_win_prop_after_k_wins |> 
-  mutate(
-    n = n(),
-    p2 = notional_p_value |> p.adjust(),
-    p3 = ms_p_value |> p.adjust()
-  ) |> 
-  filter(win_streak == 3, win_round)
 ```
@@
 cod_round_win_prop_after_k_wins |> 
-  filter(win_streak == 2L) |> 
-  mutate(
-    across(
-      matches('p_value'), 
-      ~case_when(
-        .x <= 0.01 ~ '<=0.01', 
-        TRUE ~ sprintf('%.2f', .x)
-      )
-    ),
+  mutate(
+    orig_notional_p_value = notional_p_value,
+    orig_ms_p_value = ms_p_value
+  ) |> 
+  # group_by(win_streak) |> 
+  mutate(
+    across(c(notional_p_value, ms_p_value), ~p.adjust(.x, method = 'BY'))
+  ) |> 
+  # ungroup() |>
+  filter(win_streak == 3L) |> 
+  # filter(ms_p_value < 0.05)
+  mutate(
     prop_lab = scales::percent(prop, accuracy = 0.1),
-    notional_lab = sprintf('%.1f%% (%s)', round(100 * notional_prop, 1), notional_p_value),
-    ms_lab = sprintf('%.1f%% (%s)', round(100 * ms_prop, 1), ms_p_value)
+    notional_lab = sprintf('%.1f%%', 100 * notional_prop),
+    ms_lab = sprintf('%.1f%%', 100 * ms_prop)
   ) |>
   arrange(n_rounds, win_series, win_round) |> 
+  filter(win_round) |> 
   transmute(
@@
     across(win_series, ~ifelse(.x, 'yes', 'no')),
-    win_round,
+    n,
     total,
@@
   ) |> 
-  group_split(win_round) |> 
-  walk(
-    function(df) {
-      message(sprintf('win_round=%s, win_series=%s', df$win_round[[1]], df$win_series[[1]]))
-      df <- df |> 
-        select(
-          -c(win_round)
-        ) |> 
   gt::gt() |> 
@@
     win_series = 'Win series?',
+    n = 'r+',
     total = 'N',
@@
   cat()
-    }
-  )
-
-```
-
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^20] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively.
+```
+
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^20] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{+|kr}_0$ and $\hat{P}^{+|kr}_{MS}$ respectively.
 
@@
 ```{=tex}
-\begin{longtable}{rcrrrr}
-\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, given the length of the series ($r$ rounds) and the series winner.
-Additionally, the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively, and the $p$-values of binomial tests comparing the underlying notional and MS round win probabilities, $p^{w|kr}_0$ and $p^{w|kr}_{MS}$, to the probability implied by the observed proportion $p^{w|kr} = N^{w|kr} \times P^{w|kr}$.}
+\begin{longtable}{rcrrrrr}
+\caption{Given the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|kr}$, and proportion of round wins, $P^{+|kr}$, among $N^{kr}$ instances where a team could win after the streak $k=3$ ($P^{+|kr} = \frac{r^{+|kr}}{N^{kr}}$).
+Additionally, the notional and MS expected proportions, $\hat{P}^{+|kr}_0$ and $\hat{P}^{+|kr}_{MS}$ respectively.}
 \label{tbl:cod-pw3r-pl3r} \\
+
 \toprule
-$r$ & \text{Win series?} & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ ($p$-value) \\ 
+$r$ & \text{Win series?} & $r^{+|kr}$ & $N^{kr}$ & $P^{+|kr}$ & $\hat{P}^{+|kr}_0$ & $\hat{P}^{+|kr}_{MS}$ \\ 
 \midrule
-7 & yes & 209 & 74.6\% & 75.0\% (0.94) & 75.7\% (0.69) \\ 
-8 & yes & 209 & 62.2\% & 60.0\% (0.53) & 61.9\% (0.94) \\ 
-9 & yes & 193 & 51.8\% & 50.0\% (0.67) & 52.7\% (0.83) \\ 
-10 & no & 60 & 13.3\% & 14.3\% (1.00) & 26.7\% (0.02) \\ 
-10 & yes & 151 & 43.7\% & 42.9\% (0.87) & 44.7\% (0.87) \\ 
-11 & no & 129 & 24.0\% & 25.0\% (0.84) & 30.8\% (0.11) \\ 
-11 & yes & 150 & 40.0\% & 37.5\% (0.56) & 38.8\% (0.80) \\
+
+7 & yes & 156 & 209 & 74.6\% & 75.0\% & 75.7\% \\ 
+8 & yes & 130 & 209 & 62.2\% & 60.0\% & 61.9\% \\ 
+9 & yes & 100 & 193 & 51.8\% & 50.0\% & 52.7\% \\ 
+10 & no & 8 & 60 & 13.3\% & 14.3\% & 26.7\% \\ 
+10 & yes & 66 & 151 & 43.7\% & 42.9\% & 44.7\% \\ 
+11 & no & 31 & 129 & 24.0\% & 25.0\% & 30.8\% \\ 
+11 & yes & 60 & 150 & 40.0\% & 37.5\% & 38.8\% \\
 
@@
 ```
-We observe that, with the exception of $\hat{P}^{w|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^21], all binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
-As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
-
-[^21]: This implies that the opponent, th eventual series winner, goes on to win the series 6-4 after going down 0-4.
+With the exception of $\hat{P}^{+|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^21], all un-adjusted binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
+Adjusting the $p$-values with the Benjamini & Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^22]
+
+[^21]: This implies that the opponent, the eventual series winner, goes on to win the series 6-4 after going down 0-4.
 This is the only scenario in which one team wins four rounds consecutively but loses a best-of-11 series in 10 rounds.
 
-When performing the same tests for streaks of two, four, and five, there is no case in which I can reject the binomial null hypothesis for the expected notional probability $p^{w|kr}_0$.
-The null hypothesis can be rejected for expected MS probability $p^{w|kr}_{MS}$ when $k = 4, r = [7, 8, 10]$ and $k = 5, r = [7, 8]$.
-Nonetheless, the usefulness of $p^{w|kr}_{MS}$ is questionable, as described before, and the sample sizes are smaller for these conditions (all under 20 instances, with the exception of $k = 4, r = [7, 8]$ with 70 and 39 observations respectively).
+[^22]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
+
+When performing the same tests for streaks of two, four, and five, there is no case in which I can reject the binomial null hypothesis for the expected notional probability $p^{+|kr}_0$.
+The null hypothesis can only be rejected for the expected MS probability $p^{+|kr}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^23]
+
+[^23]: At 36, the sample size for \$k = 5, r = 7\$ is not as large as most other combinations of \$k\$ and \$r\$.
 
@@
   ) |> 
-    filter(round >= (!!k + 1L)) |> 
+    filter(round >= (!!k + 1L), n_rounds > round) |> 
     compute_probs_nx_k(k)
@@
 
-cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 1L:3L) |>
+init_cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 3L) |>
   mutate(
@@
   unnest(data) |> 
-  select(-starts_with('ms')) |> 
-  group_by(win_streak, n_rounds, round) |> 
+  select(-starts_with('ms'))
+
+cod_round_win_prop_after_k_wins_i_rounds <- init_cod_round_win_prop_after_k_wins_i_rounds |>
+  group_by(win_streak, win_round, n_rounds, round) |> 
   mutate(
@@
 
+# ## example of why we needed to recalculate prop... prop and notional_prop should sum to 1, grouped by win_streak and win_round
+# cod_round_win_prop_after_k_wins_i_rounds |> 
+#   filter(win_streak == 3, n_rounds == 11, round == 10)
+# 
+# ## 5-3?
+# cod_round_win_prop_after_k_wins_i_rounds |> 
+#   filter(win_streak == 2) |> 
+#   filter(n_rounds == 11, round == 11)
+```
+
+```{r}
+#| label: cod_round_win_prop_after_k_wins_i_rounds-table
+
 cod_round_win_prop_after_k_wins_i_rounds |> 
-  filter(win_streak == 3, n_rounds == round) |> 
-  filter(!win_series)
-
-## 5-3?
-cod_round_win_prop_after_k_wins_i_rounds |> 
-  filter(win_streak == 2) |> 
-  filter(n_rounds == 11, round == 11)
-```
-
-```{r}
-#| label: cod_round_win_prop_after_k_wins_i_rounds-table
-# cod_round_win_prop_after_k_wins_i_rounds |> 
-#   filter(win_streak == 3) |> 
-#   mutate(
-#     n = n(),
-#     p2 = notional_p_value |> p.adjust()
-#   ) |> 
-#   filter(!win_round) |> 
-#   # filter(notional_p_value < 0.05) |> 
-#   filter(n_rounds <= (round + 2)) |> 
-#   filter(n_rounds >= 9)
-
-cod_round_win_prop_after_k_wins_i_rounds |> 
-  mutate(
-    p2 = notional_p_value |> p.adjust()
-  ) |> 
-  filter(win_streak == 3) |> 
-  filter(!win_round) |> 
-  # filter(n_rounds <= (round + 2)) |> 
-  filter(n_rounds == round) |> 
-  filter(n_rounds >= 9) |> 
+  mutate(
+    across(notional_p_value, p.adjust)
+  ) |>
+  filter(
+    win_round,
+    # round >= (n_rounds - 3)
+    n_rounds >= 10,
+    win_streak == 3
+  ) |>  
+  filter(total >= 10) |> 
   mutate(
@@
     prop_lab = scales::percent(prop, accuracy = 0.1),
-    notional_lab = sprintf('%.1f%% (%s)', round(100 * notional_prop, 1), notional_p_value)
+    notional_lab = scales::percent(notional_prop, accuracy = 0.1)
   ) |>
@@
     across(win_series, ~ifelse(.x, 'yes', 'no')),
+    n,
     total,
     prop_lab,
-    notional_lab,
-    prop_is_gt = ifelse(prop > notional_prop, 'yes', 'no')
+    notional_lab
   ) |> 
@@
     win_series = 'Win series?',
+    n = 'r+',
     total = 'N',
     prop_lab = 'O',
-    notional_lab = 'a',
-    prop_is_gt = 'b'
+    notional_lab = 'a'
   ) |> 
@@
 Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{w|kri}_0$, is statistically different than the observed $P^{w|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^22] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
-Since
-
-[^22]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
+As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|kri}_0$, is statistically different than the observed $P^{+|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^24] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
+
+[^24]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
 
 ```{=tex}
-\begin{longtable}{rrcrrrc}
-\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count and proportion of round wins immediately following the streak, $N^{w|kri}$ and $P^{w|kri}$ respectively.
-Additionally, the notional proportion, $\hat{P}^{w|kri}_0$, and the $p$-value of a binomial test comparing the underlying notional $p^{w|kri}_0$ to the probability implied by the observed proportion $p^{w|kri} = N^{w|kri} \times P^{w|kri}$.
-Table restricted to $r \in [9, 10, 11]$ and $r - 2 \leq i \leq r$ for brevity.}
+\begin{longtable}{rrcrrrr}
+\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|kri}$, and proportion of round wins, $P^{+|kri}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|kri} = \frac{r^{+|kri}}{N^{kri}}$).
+Additionally, the notional proportion, $\hat{P}^{+|kri}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|kri}_0$ to the observed proportion $P^{+|kri}$.
+Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{kri} > 10$ for brevity.}
 \label{tbl:cod-pw3ri-pl3ri} \\
 \toprule
-$r$ & $i$ & \text{Win series?} & $N^{w|kri}$ & $P^{w|kri}$ & $\hat{P}^{w|kri}_0$ ($p$-value) & $\hat{P}^{w|kri}_0 < P^{w|kri}$ \\ 
+$r$ & $i$ & \text{Win series?} & $r^{+|kri}$ & $N^{kri}$ & $P^{+|kri}$ & $\hat{P}^{+|kri}_0$\\ 
 \midrule
-9 & 7 & yes & 36 & 41.7\% & 50.0\% (0.41) & no \\ 
-9 & 8 & yes & 40 & 45.0\% & 50.0\% (0.64) & no \\ 
-9 & 9 & yes & 37 & 89.2\% & 50.0\% (\textless=0.01) & yes \\ 
-10 & 8 & no & 37 & 2.7\% & 14.3\% (0.06) & no \\ 
-10 & 8 & yes & 37 & 24.3\% & 42.9\% (0.03) & no \\ 
-10 & 9 & no & 32 & 6.2\% & 14.3\% (0.31) & no \\ 
-10 & 9 & yes & 32 & 12.5\% & 42.9\% (\textless=0.01) & no \\ 
-10 & 10 & yes & 29 & 72.4\% & 42.9\% (\textless=0.01) & yes \\ 
-11 & 9 & no & 32 & 15.6\% & 25.0\% (0.31) & no \\ 
-11 & 9 & yes & 32 & 31.2\% & 37.5\% (0.58) & no \\ 
-11 & 10 & no & 36 & 13.9\% & 25.0\% (0.18) & no \\ 
-11 & 10 & yes & 36 & 13.9\% & 37.5\% (\textless=0.01) & no \\ 
-11 & 11 & yes & 32 & 53.1\% & 37.5\% (0.10) & yes \\ 
+
+10 & 7 & no & 2 & 13 & 15.4\% & 14.3\% \\ 
+10 & 7 & yes & 11 & 13 & 84.6\% & 42.9\% \\ 
+10 & 8 & no & 1 & 10 & 10.0\% & 14.3\% \\ 
+10 & 8 & yes & 9 & 10 & 90.0\% & 42.9\% \\ 
+11 & 5 & no & 9 & 13 & 69.2\% & 25.0\% \\ 
+11 & 5 & yes & 4 & 13 & 30.8\% & 37.5\% \\ 
+11 & 6 & no & 4 & 13 & 30.8\% & 25.0\% \\ 
+11 & 6 & yes & 9 & 13 & 69.2\% & 37.5\% \\ 
+11 & 7 & no & 3 & 10 & 30.0\% & 25.0\% \\ 
+11 & 7 & yes & 7 & 10 & 70.0\% & 37.5\% \\ 
+11 & 9 & no & 5 & 15 & 33.3\% & 25.0\% \\ 
+11 & 9 & yes & 10 & 15 & 66.7\% & 37.5\% \\ 
+11 & 10 & no & 5 & 10 & 50.0\% & 25.0\% \\ 
+11 & 10 & yes & 5 & 10 & 50.0\% & 37.5\% \\
+
+\bottomrule
+\end{longtable}
+```
+```{r}
+#| label: cod_round_arrangements
+library(randtests)
+simulate_cod_round_arrangements <- function(p = 0.5, n_sims = 10000, seed = 42) {
+  n_rounds_max <- 11
+  set.seed(seed)
+  w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE, prob = c(1 - p, p))
+  m <- matrix(w, nrow = n_sims, ncol = n_rounds_max)
+  # data.frame(x)
+  df <- as_tibble(m)
+  names(df) <- sprintf('%d', 1:n_rounds_max)
+  df$i <- 1:nrow(df)
+
+  sim_rounds <- tibble(
+    i = rep(1:n_sims, each = n_rounds_max),
+    r = rep(1:n_sims, times = n_rounds_max),
+    w = w
+  ) |> 
+    group_by(i) |> 
+    mutate(
+      cumu_w = cumsum(w),
+      cumu_l = cumsum(w == 0)
+    ) |> 
+    ungroup() |> 
+    mutate(
+      cumu_wl_max = ifelse(cumu_w > cumu_l, cumu_w, cumu_l)
+    ) |> 
+    filter(cumu_wl_max <= 6)
+
+  sim_rounds <- df |> 
+    pivot_longer(
+      -i,
+      names_to = 'r',
+      values_to = 'w'
+    ) |> 
+    mutate(
+      across(r, as.integer)
+    ) |> 
+    group_by(i) |> 
+    mutate(
+      cumu_w = cumsum(w),
+      cumu_l = cumsum(w == 0)
+    ) |> 
+    ungroup() |> 
+    mutate(
+      cumu_wl_max = ifelse(cumu_w > cumu_l, cumu_w, cumu_l)
+    ) |> 
+    filter(cumu_wl_max <= 6)
+
+  sim_rounds_to_drop <- anti_join(
+    sim_rounds |> 
+      filter(cumu_wl_max == 6L),
+    sim_rounds |> 
+      filter(cumu_wl_max == 6L) |> 
+      group_by(i) |> 
+      slice_min(r, n = 1) |> 
+      ungroup(), 
+    by = c('i', 'r', 'w', 'cumu_w', 'cumu_l', 'cumu_wl_max')
+  )
+
+  sim_rounds <- sim_rounds |> 
+    anti_join(
+      sim_rounds_to_drop, 
+      by = c('i', 'r', 'w', 'cumu_w', 'cumu_l', 'cumu_wl_max')
+    )
+
+  ## always from offensive perspective
+  pre_expected_records <- sim_rounds |> 
+    inner_join(
+      sim_rounds |> 
+        filter(cumu_wl_max == 6) |> 
+        mutate(
+          zeros_win = cumu_l == cumu_wl_max
+        ) |> 
+        select(i, zeros_win),
+      by = 'i'
+    ) |> 
+    mutate(
+      across(w, ~ifelse(zeros_win, abs(1 - .x), .x))
+    )
+
+  pre_expected_records |> 
+    group_by(i) |> 
+    summarize(
+      cumu_w = max(cumu_w),
+      cumu_l = max(cumu_l),
+      ws = paste0(w, collapse = '-')
+    ) |> 
+    ungroup() |> 
+    mutate(
+      wins = ifelse(cumu_w == 6, cumu_w, cumu_l),
+      losses = ifelse(cumu_w == 6, cumu_l, cumu_w),
+      n_rounds = wins + losses
+    ) |> 
+    count(n_rounds, ws, sort = TRUE) |> 
+    mutate(prop = n / sum(n))
+}
+
+cod_expected_round_arrangements_mle <- simulate_cod_round_arrangements(0.575)
+
+cod_actual_round_arrangements <- cod_rounds |> 
+  filter(win_series) |> 
+  mutate(across(win_round, as.integer)) |> 
+  group_by(year, event, series) |> 
+  summarize(
+    wins = max(cumu_w),
+    losses = max(cumu_l),
+    ws = paste0(win_round, collapse = '-')
+  ) |> 
+  ungroup() |> 
+  mutate(
+    n_rounds = wins + losses
+  ) |> 
+  count(n_rounds,  ws, sort = TRUE) |> 
+  mutate(prop = n / sum(n))
+
+perform_run_tests <- function(cod_expected_round_arrangements) {
+  suppressWarnings(
+    cod_run_tests <- cod_expected_round_arrangements |> 
+      select(n_rounds, ws) |> 
+      separate(ws, into = as.character(1:11), remove = FALSE) |> 
+      pivot_longer(
+        -c(n_rounds, ws),
+        names_to = 'round',
+        values_to = 'w',
+        values_drop_na = TRUE
+      ) |> 
+      mutate(
+        across(c(round, w), as.integer)
+      ) |> 
+      # filter(record != '6-0') |> 
+      select(-round) |> 
+      group_by(n_rounds, ws) |> 
+      summarize(
+        w = list(w)
+      ) |> 
+      ungroup() |> 
+      mutate(
+        p_value = map_dbl(w, ~randtests::runs.test(.x, threshold = 0.5)$p.value),
+        is_significant = p_value <= 0.05
+      ) |> 
+      select(n_rounds, ws, p_value, is_significant)
+  )
+
+  expected_total <- sum(cod_expected_round_arrangements$n)
+  actual_total <- sum(cod_actual_round_arrangements$n)
+  cod_round_arrangements <- cod_expected_round_arrangements |> 
+    rename(n_expected = n, prop_expected = prop) |>
+    mutate(
+      n_expected_adj = n_expected * (!!actual_total) / (!!expected_total)
+    ) |> 
+    left_join(
+      cod_actual_round_arrangements |> 
+        rename(n_actual = n, prop_actual = prop),
+      by = c('n_rounds', 'ws')
+    ) |> 
+    inner_join(
+      cod_run_tests,
+      by = c('n_rounds', 'ws')
+    ) |> 
+    mutate(
+      across(n_actual, replace_na, 0L),
+      across(prop_actual, replace_na, 0)
+    )
+}
+
+cod_round_arrangements_mle |> 
+  # mutate(
+  #   total_actual = sum(n_actual),
+  #   total_expected = sum(n_expected)
+  # ) |> 
+  filter(!is.na(p_value)) |> 
+  filter(is_significant) |> 
+  mutate(
+    total_actual = sum(n_actual),
+    total_expected_adj = sum(n_expected_adj)
+  ) |> 
+  mutate(
+    prop_p_value = vectorized_prop_test(n_actual, total_actual, round(n_expected_adj), round(total_expected_adj))$p.value,
+    orig_prop_p_value = prop_p_value,
+    across(prop_p_value, ~p.adjust(.x, method = 'BY') |> round(3))
+  )
+
+cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()
+cod_round_arrangements_mle |> 
+  filter(is_significant) |> 
+  filter(n_rounds < 11) |> 
+  transmute(
+    n_rounds,
+    ws,
+    n_actual,
+    across(prop_actual, ~sprintf('%.2f%%', 100 * .x)),
+    across(n_expected_adj, round, 2),
+    across(prop_expected, ~sprintf('%.2f%%', 100 * .x))
+  ) |> 
+  gt::gt() |> 
+  gt::cols_label(
+    n_rounds = 'r',
+    ws = 'Sequence',
+    n_actual = 'a',
+    prop_actual = 'b',
+    n_expected_adj = 'c',
+    prop_expected = 'd'
+  ) |> 
+  gt::as_latex() |> 
+  cat()
+```
+
+In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
+(In addition to these 13, there are 12 additional sequences for $r = 11$.) The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$.
+A test for difference between the actual and expected proportions of all sequences indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.
+
+```{=tex}
+\begin{longtable}{rlrrrr}
+
+\caption{Given the length of the series ($r$ rounds), the sequence of round wins by the series winner $^\zeta(r)$, where round wins $r^w$ and losses $r^-$ are indicated by 1 and 0 respectively, among sequences that reject the Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$.
+The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$.
+$\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
+\label{tbl:cod-runs} \\
+
+\toprule
+r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
+\midrule
+8 & 0-0-1-1-1-1-1-1 & 4 & 0.47\% & 7.67 & 0.90\% \\ 
+9 & 0-0-0-1-1-1-1-1-1 & 4 & 0.47\% & 3.75 & 0.44\% \\ 
+10 & 1-1-1-1-0-0-0-0-1-1 & 1 & 0.12\% & 2.39 & 0.28\% \\ 
+10 & 1-0-0-0-0-1-1-1-1-1 & 0 & 0.00\% & 2.04 & 0.24\% \\ 
+10 & 1-0-1-0-1-1-0-1-0-1 & 3 & 0.35\% & 2.04 & 0.24\% \\ 
+10 & 1-1-1-0-0-0-0-1-1-1 & 2 & 0.23\% & 2.04 & 0.24\% \\ 
+10 & 0-0-0-0-1-1-1-1-1-1 & 2 & 0.23\% & 1.79 & 0.21\% \\ 
+10 & 1-0-1-0-1-0-1-1-0-1 & 3 & 0.35\% & 1.70 & 0.20\% \\ 
+10 & 1-0-1-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.70 & 0.20\% \\ 
+10 & 1-1-0-0-0-0-1-1-1-1 & 1 & 0.12\% & 1.19 & 0.14\% \\ 
+10 & 1-0-1-0-1-0-1-0-1-1 & 3 & 0.35\% & 1.11 & 0.13\% \\ 
+10 & 1-1-0-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.11 & 0.13\% \\ 
+10 & 1-1-1-1-1-0-0-0-0-1 & 2 & 0.23\% & 1.02 & 0.12\% \\ 
 \bottomrule
@@
 
-Further regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^23] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
-
-[^23]: <https://twitter.com/R11stats>
+Further regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^25] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+
+[^25]: <https://twitter.com/R11stats>
 
@@
 
-I would like to thank my brother Andrew for giving me feedback on early iterations of this paper.
+Thank my brother Andrew for giving me feedback on drafts of this paper.
 

### 2022-08-21 paper/paper.tex
re-reading, added all tables, by p-value adj, no p-values in tables

--- 2022-08-21 paper/paper.tex
@@
 series winner, suggesting that the perception of momentum at the team
-level is deceiving.
+level is just that, perception.
 \end{abstract}
@@
 ``match'' in such leagues is analogous to a ``round'' of CoD SnD.
+Further, it is analogous to a trial in statistical analysis of Bernoulli
+events.
 
@@
   played online.} Data was collected in spreadsheets by community member
-``IOUTurtle''.\footnote{Data: \url{https://linktr.ee/CDLArchive}.
-  Author: \url{https://twitter.com/IOUTurtle}}
+``IOUTurtle''.\footnote{Raw data: \url{https://linktr.ee/CDLArchive}.
+  Author: \url{https://twitter.com/IOUTurtle}. Processed data can be
+  found at
+  \url{https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv}.}
 
@@
 dominated the National League in Major League Baseball's (MLB) World
-Series matchups, implying that matchups should not modeled with
-\(\phi = 0.5\). Mosteller proposed three approaches for identifying the
-optimal constant probability value of the stronger team in the World
-Series, finding \(\phi \approx 0.65\). in each case: (1) solving for
-\(p\) from the empirical average number of games won by the loser of the
-series, which he called the ``method of moments'' approach; (2)
-maximizing the likelihood that the sample would have been drawn from a
-population in which the probability of a team winning a game is constant
-across the series (i.e.~maximum likelihood), and (3) minimizing the
-chi-square goodness of fit statistic for \(\phi\).
+Series matchups, implying that games should not be modeled with a
+constant (null) \(\phi_0 = 0.5\). Mosteller proposed three approaches
+for identifying the optimal constant probability value of the stronger
+team in the World Series, finding \(\phi \approx 0.65\) in each case:
+(1) solving for \(p\) from the empirical average number of games won by
+the loser of the series, which he called the ``method of moments''
+approach; (2) maximizing the likelihood that the sample would have been
+drawn from a population in which the probability of a team winning a
+game is constant across the series (i.e.~maximum likelihood), and (3)
+minimizing the chi-square goodness of fit statistic \(\chi^2\) for
+\(\phi\).
 
@@
 Hockey League's (NHL) Stanley Cup (1939--2018). Chance finds strong
-evidence against the null hypothesis of \(\phi = 0.5\) in the MLB and
+evidence against the null hypothesis of \(\phi_0 = 0.5\) in the MLB and
 NHL championship series when applying Mosteller's first and second
@@
   not.} Two opposing fallacies are observed in the context of momentum:
-the ``gambler's fallacy'' (negative recency) and ``hot hand fallacy''
-(positive recency). Per Ayton et al. (2004), negative recency is ``the
-belief that, for random events, runs of a particular outcome \ldots{}
-will be balanced by a tendency for the opposite outcome'', while
-positive recency is the expectation of observing future results that
-match recent results.
+the ``gambler's fallacy'' (negative recency) and the ``hot hand
+fallacy'' (positive recency). Per Ayton et al. (2004), negative recency
+is ``the belief that, for random events, runs of a particular outcome
+\ldots{} will be balanced by a tendency for the opposite outcome'',
+while positive recency is the expectation of observing future results
+that match recent results.
 
@@
 
+Other research has borrowed a common approach from the field of quality
+control, looking at unlikely sequences of events with the Wald-Wolfowitz
+runs test (Peel and Clauset 2015), (Steeger, Dulin, and Gonzalez 2021).
+Peel and Clauset find no evidence for unlikely sequences of scoring
+events in the NHL, College Football (CFB), and National Football League
+(NFL), but do in the NBA. As a check on their entropy approach to
+momentum identification, Steeger et al.~found three NHL teams who
+sequence of wins in the 2018-2019 regular season violated the
+Wald-Wolfowitz null hypothesis, although these teams did not match the
+teams identified with their primary approach.
+
+\hypertarget{my-contribution}{%
+\subsection{My contribution}\label{my-contribution}}
+
 Despite the plethora of existing research on games played in a series
-and momentum in sports, these topics have yet to be investigated heavily
-in esports. Work has been done to examine in-round win probability in
-other FPS titles such as Counter-Strike (Xenopoulos, Freeman, and Silva
-2022) and Valorant (DeRover 2021), both of which are round-based like
-CoD SnD. However, research on round-level trends is sparse, perhaps
-because games like Counter-Strike and Valorant both have economic
-aspects that can create clear advantages on side in a given round, given
-how prior rounds played out.
+and momentum in sports, these topics have yet to be investigated
+heavily, if at all, in esports. Work has been done to examine
+intra-round win probability in other FPS titles such as Counter-Strike
+(Xenopoulos, Freeman, and Silva 2022) and Valorant (DeRover 2021), both
+of which are round-based like CoD SnD. However, considering
+Counter-Strike and Valorant specifically, research on round-level trends
+seems non-existant, perhaps for one of many reasons:
 
-Additionally, both Counter-Strike and Valorant have overtime rules and
-blocked offensive/defensive roles (i.e.~playing either offense or
-defense for many consecutive rounds). On the other hand, teams in CoD
-SnD rotate sides every round, analogous to a 1-1-1-1-1-1-1 format for
-home advantage in best-of-seven series for professional sports like the
-MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1 is not used today in these
-  leagues, but it was at least one in each league.} While theoretically
-one might be able to account for any kind of format, such as a 5-5-1,
-the rotation of team sides every round is convenient for convincing
-ourselves that rounds could reasonably be modeled as i.i.d. Bernoulli
-trials.
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Both have economic aspects that can create clear advantages for one
+  side in a given round, given how prior rounds played out. CoD has no
+  such equivalent, except for perhaps ``kill streaks'', which
+  infrequently play a role.
+\item
+  Teams play either offense or defense for many consecutive rounds. (The
+  former has a 14-14-1 format and the latter uses a 12-12-1 format.) On
+  the other hand, teams in CoD SnD rotate roles every round, analogous
+  to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series
+  for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
+    is not used today in these leagues, but it was at least one in each
+    league.} While theoretically one might be able to account for any
+  kind of format, such as a 5-5-1, the rotation of team sides every
+  round is convenient for convincing ourselves that rounds could
+  reasonably be modeled as i.i.d. Bernoulli trials.
+\item
+  Both Counter-Strike and Valorant have overtime rules---team must win
+  by two rounds---which can make end-of-series sequences difficult to
+  model. CoD SnD does not have overtime rules.
+\end{enumerate}
+
+To my knowledge, there is no existing public statistical research on CoD
+SnD format, beyond descriptive analysis on social media. While
+intra-round trends may be more directly applicable to teams looking for
+an advantage on their competition, broader investigation on a common
+concept like the hot-hand phenomenon in a new field---particularly one
+that is less subjected to factors that may be difficult to control for,
+e.g.~weather---should hopefully be useful as a precedent or supplement
+for future researchers.
 
@@
 
-\hypertarget{sec:method-rounds-played}{%
+\hypertarget{distribution-of-rounds-played}{%
 \subsection{Distribution of rounds
-played}\label{sec:method-rounds-played}}
+played}\label{distribution-of-rounds-played}}
 
@@
 
-\hypertarget{sec:method-momentum}{%
-\subsection{Momentum}\label{sec:method-momentum}}
+\hypertarget{momentum}{%
+\subsection{Momentum}\label{momentum}}
+
+\hypertarget{ms-post-streak-probability}{%
+\subsubsection{MS post-streak
+probability}\label{ms-post-streak-probability}}
 
@@
 rounds wins immediately following a streak of \(k\) rounds wins for a
-series lasting \(r\) rounds, \(\hat{P}^{w|kr}_{MS}\), to be strictly
-less than \(p^{w|r}\).\footnote{See Appendix E.1 of MS for details on
-  the proof that follows.} Unfortunately, there does not exist a closed
-form representation for the expectation for \(\hat{P}^{w|kr}_{MS}\) for
-\(k > 1\). Nonetheless, one may recursively build a collection of
-dictionaries to compute the expectation analytically, or, more
-conveniently, one may run simulations to estimate the expected
-value.\footnote{I've adapted the code from Vafa (2017), which implements
-  MS's framework (2018).}
+series lasting \(r\) rounds, \(\hat{P}^{+|kr}_{MS}\), to be strictly
+less than \(p^{+|r}\).\footnote{See Appendix E.1 of MS for the proof.}
+Unfortunately, there does not exist a closed form representation for the
+expected value of \(\hat{P}^{+|kr}_{MS}\) for \(k > 1\). Nonetheless,
+one may recursively build a collection of dictionaries to compute the
+expectation analytically, or, more conveniently, one may run simulations
+to estimate the expected value, as I choose to do.\footnote{I have
+  adapted the code from Vafa (2017), which implements MS's framework
+  (2018).}
 
@@
 number of possible rounds (\(s\)) and whether or not the team wins the
-series, as shown in Equation \ref{eq:pwr}. The Bernoulli trial success
-probability, i.e.~a round win in CoD SnD, is not independent of the
-opponent. Consequently, a statistical test of the difference in
-\(\hat{P}^{w|kr}\) and \(\hat{P}^{\ell|kr}\), as performed by MS to
-evaluate their hypothesis regarding post-streak success rates is not
-completely appropriate, although useful as a reference.
+series. The Bernoulli trial success probability, i.e.~a round win in CoD
+SnD, is not independent of the opponent. Consequently, a statistical
+test of the difference in \(\hat{P}^{+|kr}\) and \(\hat{P}^{-|kr}\), as
+performed by MS to evaluate their hypothesis regarding post-streak
+success rates, is not completely appropriate, although useful as a
+reference.
+
+\hypertarget{notional-post-streak-probability}{%
+\subsubsection{``Notional'' post-streak
+probability}\label{notional-post-streak-probability}}
 
@@
 given the length of the series (\(r\) rounds), the ``notional''
-proportion \(\hat{P}^{w|kr}_0\). The Bernoulli round win probability
-underlying \(\hat{P}^{w|kr}_0\) is
+proportion \(\hat{P}^{+|kr}_0\). The Bernoulli round win probability
+underlying \(\hat{P}^{+|kr}_0\) is
 
 \begin{equation}\protect\hypertarget{eq:pwkr}{}{
-p_0(\text{win} | k, r) = p^{w|kr}_0 =\{
-\begin{array}{rl}
-\frac{m - k}{i - k}, & \text{team wins series} \\
-\frac{s - m - k}{i - k}, & \text{team loses series}
+p_0(\text{win} | k, r) = p^{+|kr}_0 =\{
+\begin{array}{cl}
+\frac{m - k}{r - k}, & \text{team wins series} \\
+\frac{s - m - k}{r - k}, & \text{team loses series}
 \end{array}
@@
 
-using \(m\) from Equation \ref{eq:m}. We can perform a binomial test to
-test the null hypothesis \(H_0 : \omega = \omega_0\) for the observed
-probability of success \(\omega\) and a user-specified \(\omega_0\),
-where \(0 \leq \omega_0 \leq 1\).\footnote{\(\omega\) and other symbols
-  are chosen so as to not conflict with symbols already used elsewhere
-  for in other equations, either generic or for CoD SnD specifically.}
+using \(m\) from Equation \ref{eq:m}.
 
-If there are \(r_+\) observed successes in a sample of \(r\) trials and
-we expect that there should be \(r * \omega_0\), the probability of
+We can perform a binomial test to evaluate the null hypothesis
+\(\omega = \omega_0\) for the observed probability of success \(\omega\)
+and a user-specified \(\omega_0\), where
+\(0 \leq \omega_0 \leq 1\).\footnote{\(\omega\) and other symbols are
+  chosen so as to not conflict with symbols already used elsewhere for
+  in other equations, either generic or for CoD SnD specifically.} If
+there are \(r^+\) observed successes in a sample of \(r\) trials and we
+expect that there should be \(r * \omega_0\), the probability of
 arriving at this expected number of successes is
@@
 \begin{equation}\protect\hypertarget{eq:binom}{}{
-\Pr(r_+) = {\binom {r}{r_+}} \omega^{r_+}(1-\omega)^{r-r+}.
+\Pr(r^w) = {\binom {r}{r^+}} \omega^{r^+}(1-\omega)^{r-r^+}.
 }\label{eq:binom}\end{equation}
 
-Plugging in the notional probability \(p^{w|kr}_0\) for the null
-\(\omega_0\) and the observed probability
-\(p^{w|kr} = N^{w|kr} \times P^{w|kr}\), for the observed \(\omega\),
-where \(N^{w|kr}\) is the observed number of instances where a teams
-wins the round immediately following a \(k\)-round winning streak in a
-series lasting \(r\) rounds, we can evaluate the null hypothesis that
-the observed probability is equal to the notional probability. If we
-reject this null hypothesis, then we might consider team momentum,
-represented by post-streak success, plausible.
+Plugging in the notional proportion \(\hat{p}^{+|kr}_0\) for the null
+\(\omega_0\) and the observed proportion \(P^{+|kr}\) for \(\omega\)
+(treating proportions as probabilities), we can evaluate the null
+hypothesis that the observed probability is equal to the notional
+probability. If we can reject this null hypothesis, then we might
+consider team momentum, represented by post-streak success, plausible.
 
-One can perform the same binomial test for the MS probability adjusting
-for streak-selection bias, \(p^{w|kr}_{MS}\). Given the caveats
-mentioned before, the results should be heeded with caution.
+One can perform the same binomial test for the MS's
+streak-selection-adjusted proportion, \(\hat{P}^{+|kr}_{MS}\). FOOTY:
+Given the caveats mentioned before, the results should be heeded with
+caution.
 
-Stepping back from the one-sided perspective of a single team's
-probability of winning and their streakiness, one can attempt to detect
-the ``hot hand'' more broadly with the Wald-Wolfowitz runs test, a
-common tool used in the field of quality control. Under the null
-hypothesis, the number of runs in a sequence of \(r\) trials is a random
-variable with the following mean \(\mu\) and variance \(\sigma^2\).
+We can further decompose Equation \ref{eq:pwkr} by the round \(i\)
+(\(i \leq r\)) in which the streak of length \(k\) carries into.
+
+\begin{equation}\protect\hypertarget{eq:pwkri}{}{
+p_0(\text{win} | k, r, i) = p^{+|kri}_0 =\{
+\begin{array}{cl}
+\frac{m - k}{r - k}, & \text{team wins series}, i \neq r \\
+1, & \text{team wins series}, i = r \\
+\frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r \\
+0, & \text{team loses series}, i = r
+\end{array}
+}
+\label{eq:pwkri}
+\end{equation}
+
+Again, one might apply a binomial test to evaluate the hypothesis that
+the expected proportions, both \(\hat{P}^{+|kri}_0\) and
+\(\hat{P}^{+|kri}_{MS}\), are equal to the observed proportion
+\(P^{+|kr}\).
+
+\hypertarget{wald-wolfowitz-runs-test}{%
+\subsubsection{Wald-Wolfowitz runs
+test}\label{wald-wolfowitz-runs-test}}
+
+Stepping back from the one-sided perspective of a single team's round
+win probability when streaking, one can attempt to detect the hot hand
+phenomenon with the Wald-Wolfowitz runs test. Under the null hypothesis,
+the number of runs in a sequence of \(r\) trials is a random variable,
+which can take on values \(r^+\) and \(r^-\) for success and failure
+respectively, with the following mean \(\mu\) and variance \(\sigma^2\).
 
 \begin{equation}\protect\hypertarget{eq:ww}{}{
-\mu = \frac{2r_+r_-}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
+\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
 }\label{eq:ww}\end{equation}
@@
 One might subset observed series sequences to those that violate the run
-test null hypothesis and perform a proportions test where the null is
-that the observe rate of such series is equal to the frequency that we
-should expect, given a choice for the constant round win probability
-\(\phi\). If the
+test null hypothesis and perform a test of proportions, where the null
+is that the observed rate of such series is equal to the frequency that
+we should expect, given a choice for the constant round win probability
+\(\phi\). If we can reject the null, then we can argue in favor of the
+hot hand.
 
@@
 
-\hypertarget{sec:results-rounds-played}{%
+\hypertarget{distribution-of-rounds-played-1}{%
 \subsection{Distribution of rounds
-played}\label{sec:results-rounds-played}}
+played}\label{distribution-of-rounds-played-1}}
 
@@
 
-\hypertarget{sec:results-momentum}{%
-\subsection{Momentum}\label{sec:results-momentum}}
+\hypertarget{momentum-1}{%
+\subsection{Momentum}\label{momentum-1}}
 
@@
 outcome (\(r\) rounds and winner) with the notional and MS expected
-proportions, \(\hat{P}^{w|kr}_0\) and \(\hat{P}^{w|kr}_{MS}\)
+proportions, \(\hat{P}^{+|kr}_0\) and \(\hat{P}^{+|kr}_{MS}\)
 respectively.
 
-\begin{longtable}{rrrrrr}
-\caption{Observed count and proportion of round wins immediately following round win streak of $k=3$, $N^{w|kr}$ and $P^{w|kr}$ respectively, given the length of the series ($r$ rounds) and the series winner.
-Additionally, the notional and MS expected proportions, $\hat{P}^{w|kr}_0$ and $\hat{P}^{w|kr}_{MS}$ respectively, and the $p$-values of binomial tests comparing the underlying notional and MS round win probabilities, $p^{w|kr}_0$ and $p^{w|kr}_{MS}$, to the probability implied by the observed proportion $p^{w|kr} = N^{w|kr} \times P^{w|kr}$.}
+\begin{longtable}{rcrrrrr}
+\caption{Given the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|kr}$, and proportion of round wins, $P^{+|kr}$, among $N^{kr}$ instances where a team could win after the streak $k=3$ ($P^{+|kr} = \frac{r^{+|kr}}{N^{kr}}$).
+Additionally, the notional and MS expected proportions, $\hat{P}^{+|kr}_0$ and $\hat{P}^{+|kr}_{MS}$ respectively.}
 \label{tbl:cod-pw3r-pl3r} \\
+
 \toprule
-$r$ & \text{Win series?} & $N^{w|kr}$ & $P^{w|kr}$ & $\hat{P}^{w|kr}_0$ ($p$-value) & $\hat{P}^{w|kr}_{MS}$ ($p$-value) \\ 
+$r$ & \text{Win series?} & $r^{+|kr}$ & $N^{kr}$ & $P^{+|kr}$ & $\hat{P}^{+|kr}_0$ & $\hat{P}^{+|kr}_{MS}$ \\ 
 \midrule
-7 & yes & 209 & 74.6\% & 75.0\% (0.94) & 75.7\% (0.69) \\ 
-8 & yes & 209 & 62.2\% & 60.0\% (0.53) & 61.9\% (0.94) \\ 
-9 & yes & 193 & 51.8\% & 50.0\% (0.67) & 52.7\% (0.83) \\ 
-10 & no & 60 & 13.3\% & 14.3\% (1.00) & 26.7\% (0.02) \\ 
-10 & yes & 151 & 43.7\% & 42.9\% (0.87) & 44.7\% (0.87) \\ 
-11 & no & 129 & 24.0\% & 25.0\% (0.84) & 30.8\% (0.11) \\ 
-11 & yes & 150 & 40.0\% & 37.5\% (0.56) & 38.8\% (0.80) \\
+
+7 & yes & 156 & 209 & 74.6\% & 75.0\% & 75.7\% \\ 
+8 & yes & 130 & 209 & 62.2\% & 60.0\% & 61.9\% \\ 
+9 & yes & 100 & 193 & 51.8\% & 50.0\% & 52.7\% \\ 
+10 & no & 8 & 60 & 13.3\% & 14.3\% & 26.7\% \\ 
+10 & yes & 66 & 151 & 43.7\% & 42.9\% & 44.7\% \\ 
+11 & no & 31 & 129 & 24.0\% & 25.0\% & 30.8\% \\ 
+11 & yes & 60 & 150 & 40.0\% & 37.5\% & 38.8\% \\
 
@@
 
-We observe that, with the exception of \(\hat{P}^{w|kr}_{MS}\) when
-\(r = 10\) and the eventual series loser is the team that wins after a
-streak of three round wins\footnote{This implies that the opponent, th
-  eventual series winner, goes on to win the series 6-4 after going down
-  0-4. This is the only scenario in which one team wins four rounds
-  consecutively but loses a best-of-11 series in 10 rounds.}, all
-binomial test \(p\)-values are greater than the typical
-\(\alpha = 0.05\) threshold, implying that we cannot reject the null
-hypothesis that the expected notional and MS post-streak round win rates
-are different than the observed proportion. As noted before, the MS
-expectations may be unreliable for CoD SnD, so one is inclined to prefer
-the results of the notional binomial tests.
+With the exception of \(\hat{P}^{+|kr}_{MS}\) when \(r = 10\) and the
+eventual series loser is the team that wins after a streak of three
+round wins\footnote{This implies that the opponent, the eventual series
+  winner, goes on to win the series 6-4 after going down 0-4. This is
+  the only scenario in which one team wins four rounds consecutively but
+  loses a best-of-11 series in 10 rounds.}, all un-adjusted binomial
+test \(p\)-values are greater than the typical \(\alpha = 0.05\)
+threshold, implying that we cannot reject the null hypothesis that the
+expected notional and MS post-streak round win rates are different than
+the observed proportion. Adjusting the \(p\)-values with the Benjamini
+\& Yekutieli (BY) correction (2001), the null hypothesis cannot be
+rejected for any case.\footnote{As noted before, the MS expectations may
+  be unreliable for CoD SnD, so one is inclined to prefer the results of
+  the notional binomial tests.}
 
@@
 is no case in which I can reject the binomial null hypothesis for the
-expected notional probability \(p^{w|kr}_0\). The null hypothesis can be
-rejected for expected MS probability \(p^{w|kr}_{MS}\) when
-\(k = 4, r = [7, 8, 10]\) and \(k = 5, r = [7, 8]\). Nonetheless, the
-usefulness of \(p^{w|kr}_{MS}\) is questionable, as described before,
-and the sample sizes are smaller for these conditions (all under 20
-instances, with the exception of \(k = 4, r = [7, 8]\) with 70 and 39
-observations respectively).
+expected notional probability \(p^{+|kr}_0\). The null hypothesis can
+only be rejected for the expected MS probability \(p^{+|kr}_{MS}\) when
+\(k = 5, r = 7\) after applying the BY p-value correction.\footnote{At
+  36, the sample size for \$k = 5, r = 7\$ is not as large as most other
+  combinations of \$k\$ and \$r\$.}
 
@@
 immediately following a streak of \(k\) round wins in a series lasting
-\(r\) rounds, \(\hat{P}{w|kri}_0\), is statistically different than the
-observed \(P^{w|kri}\) in several cases, notably when \(r = i\) for each
+\(r\) rounds, \(\hat{P}{+|kri}_0\), is statistically different than the
+observed \(P^{+|kri}\) in several cases, notably when \(r = i\) for each
 of \(r \in [9, 10, 11]\).\footnote{The null can also be rejected for
@@
 whereas the observed rate is less than the expected rate in all other
-cases (as well in a strong majority of cases not shown).
+cases, as well in a strong majority of cases not shown.
 
-\begin{longtable}{rrrrrr}
-\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count and proportion of round wins immediately following the streak, $N^{w|kri}$ and $P^{w|kri}$ respectively.
-Additionally, the notional proportion, $\hat{P}^{w|kri}_0$, and the $p$-value of a binomial test comparing the underlying notional $p^{w|kri}_0$ to the probability implied by the observed proportion $p^{w|kri} = N^{w|kri} \times P^{w|kri}$.
-Table restricted to $r \in [9, 10, 11]$ and $r - 2 \leq i \leq r$ for brevity.}
+\begin{longtable}{rrcrrrr}
+\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|kri}$, and proportion of round wins, $P^{+|kri}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|kri} = \frac{r^{+|kri}}{N^{kri}}$).
+Additionally, the notional proportion, $\hat{P}^{+|kri}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|kri}_0$ to the observed proportion $P^{+|kri}$.
+Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{kri} > 10$ for brevity.}
 \label{tbl:cod-pw3ri-pl3ri} \\
 \toprule
-$r$ & $i$ & \text{Win series?} & $N^{w|kri}$ & $P^{w|kri}$ & $\hat{P}^{w|kri}_0$ ($p$-value) & $\hat{P}^{w|kri}_0 > P^{w|kri}$ \\
+$r$ & $i$ & \text{Win series?} & $r^{+|kri}$ & $N^{kri}$ & $P^{+|kri}$ & $\hat{P}^{+|kri}_0$\\ 
+\midrule
 
-9 & 7 & yes & 36 & 41.7\% & 50.0\% (0.41) & no \\ 
-9 & 8 & yes & 40 & 45.0\% & 50.0\% (0.64) & no \\ 
-9 & 9 & yes & 37 & 89.2\% & 50.0\% (<=0.01) & yes \\ 
-10 & 8 & no & 37 & 2.7\% & 14.3\% (0.06) & no \\ 
-10 & 8 & yes & 37 & 24.3\% & 42.9\% (0.03) & no \\ 
-10 & 9 & no & 32 & 6.2\% & 14.3\% (0.31) & no \\ 
-10 & 9 & yes & 32 & 12.5\% & 42.9\% (<=0.01) & no \\ 
-10 & 10 & yes & 29 & 72.4\% & 42.9\% (<=0.01) & yes \\ 
-11 & 9 & no & 32 & 15.6\% & 25.0\% (0.31) & no \\ 
-11 & 9 & yes & 32 & 31.2\% & 37.5\% (0.58) & no \\ 
-11 & 10 & no & 36 & 13.9\% & 25.0\% (0.18) & no \\ 
-11 & 10 & yes & 36 & 13.9\% & 37.5\% (<=0.01) & no \\ 
-11 & 11 & yes & 32 & 53.1\% & 37.5\% (0.10) & yes \\
+10 & 7 & no & 2 & 13 & 15.4\% & 14.3\% \\ 
+10 & 7 & yes & 11 & 13 & 84.6\% & 42.9\% \\ 
+10 & 8 & no & 1 & 10 & 10.0\% & 14.3\% \\ 
+10 & 8 & yes & 9 & 10 & 90.0\% & 42.9\% \\ 
+11 & 5 & no & 9 & 13 & 69.2\% & 25.0\% \\ 
+11 & 5 & yes & 4 & 13 & 30.8\% & 37.5\% \\ 
+11 & 6 & no & 4 & 13 & 30.8\% & 25.0\% \\ 
+11 & 6 & yes & 9 & 13 & 69.2\% & 37.5\% \\ 
+11 & 7 & no & 3 & 10 & 30.0\% & 25.0\% \\ 
+11 & 7 & yes & 7 & 10 & 70.0\% & 37.5\% \\ 
+11 & 9 & no & 5 & 15 & 33.3\% & 25.0\% \\ 
+11 & 9 & yes & 10 & 15 & 66.7\% & 37.5\% \\ 
+11 & 10 & no & 5 & 10 & 50.0\% & 25.0\% \\ 
+11 & 10 & yes & 5 & 10 & 50.0\% & 37.5\% \\
 
+\bottomrule
+\end{longtable}
+
+In Table \ref{tbl:cod-runs}, the observed and expected count of
+sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
+shown for sequences, \(\zeta(r)\), for which one can reject the
+Wald-Wolfowitz null hypothesis at a confidence level of
+\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). (In addition to these 13,
+there are 12 additional sequences for \(r = 11\).) The relative
+frequency of the expected proportions are based on 10,000 simulations
+using the constant round probability \(\phi_2 = 0.575\). A test for
+difference between the actual and expected proportions of all sequences
+indicates that the null hypothesis---that the two proportions are
+equal---cannot be rejected for any of the 25 significant sequences.
+
+\begin{longtable}{rlrrrr}
+
+\caption{Given the length of the series ($r$ rounds), the sequence of round wins by the series winner $^\zeta(r)$, where round wins $r^w$ and losses $r^-$ are indicated by 1 and 0 respectively, among sequences that reject the Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$.
+The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$.
+$\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
+\label{tbl:cod-runs} \\
+
+\toprule
+r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
+\midrule
+8 & 0-0-1-1-1-1-1-1 & 4 & 0.47\% & 7.67 & 0.90\% \\ 
+9 & 0-0-0-1-1-1-1-1-1 & 4 & 0.47\% & 3.75 & 0.44\% \\ 
+10 & 1-1-1-1-0-0-0-0-1-1 & 1 & 0.12\% & 2.39 & 0.28\% \\ 
+10 & 1-0-0-0-0-1-1-1-1-1 & 0 & 0.00\% & 2.04 & 0.24\% \\ 
+10 & 1-0-1-0-1-1-0-1-0-1 & 3 & 0.35\% & 2.04 & 0.24\% \\ 
+10 & 1-1-1-0-0-0-0-1-1-1 & 2 & 0.23\% & 2.04 & 0.24\% \\ 
+10 & 0-0-0-0-1-1-1-1-1-1 & 2 & 0.23\% & 1.79 & 0.21\% \\ 
+10 & 1-0-1-0-1-0-1-1-0-1 & 3 & 0.35\% & 1.70 & 0.20\% \\ 
+10 & 1-0-1-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.70 & 0.20\% \\ 
+10 & 1-1-0-0-0-0-1-1-1-1 & 1 & 0.12\% & 1.19 & 0.14\% \\ 
+10 & 1-0-1-0-1-0-1-0-1-1 & 3 & 0.35\% & 1.11 & 0.13\% \\ 
+10 & 1-1-0-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.11 & 0.13\% \\ 
+10 & 1-1-1-1-1-0-0-0-0-1 & 2 & 0.23\% & 1.02 & 0.12\% \\ 
 \bottomrule
@@
 given \(\tau_O\) = 47.7\% the expected frequency is
-\(\tau_O^2 \times (1 - \tau_O) \approx 0.119\)---are likely to occur
+\(\tau_O^2 \times (1 - \tau_O) \approx\) 11.9\%---are likely to occur
 less frequently than such streaks starting with a defensive
-win---\(\tau_O \times (1 - \tau_O)^2 \approx 0.130\)---so I would want
+win---\(\tau_O \times (1 - \tau_O)^2 \approx\) 13.0\%---so I would want
 to account for sample size differences.
@@
 
-I would like to thank my brother Andrew for giving me feedback on early
-iterations of this paper.
+Thank my brother Andrew for giving me feedback on drafts of this paper.
 
@@
 \& Cognition} 32 (8): 13691378.
+
+\leavevmode\vadjust pre{\hypertarget{ref-benjamini2001}{}}%
+Benjamini, Yoav, and Daniel Yekutieli. 2001. {``The Control of the False
+Discovery Rate in Multiple Testing Under Dependency.''} \emph{Annals of
+Statistics}, 11651188.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-peel2015}{}}%
+Peel, Leto, and Aaron Clauset. 2015. {``Predicting Sports Scoring
+Dynamics with Restoration and Anti-Persistence.''} In, 339348. IEEE.
+
 \leavevmode\vadjust pre{\hypertarget{ref-steeger2021}{}}%

### 2022-08-21 paper/paper.Rmd
icing up son

@@
 ---
-title: "They're Clutching up! Team Momentum in Round-Based Esports"
+title: "They're Icing up! Team Momentum in Round-Based Esports"
 authors:
@@
 ```
+Anecdotally, observers swear by the existence of momentum in CoD SnD series, to the extent that vernacular has been developed to describe such phenomenon.
+People say that teams "ice up" when the team wins several consecutive rounds to come back to win a series, often culminating with a series-clinching round win.[^10] Further, viewers have come to embrace the "5-3" phenomenon, where teams win three consecutive rounds after facing a 5-3 deficit to win 6-5.
+There is even a term for the rare 0-5 comeback---a "full sail".
+
+[^10]: This vernacular is not specific to CoD SnD in specific, and is not only used in the contexts of streaks.
+
 # Literature review
@@
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^10] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^11] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^10]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^11]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 [-@gilovich1985], henceforth GVT, do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^11].
+However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^12].
 Specifically, MS say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
@@
 
-[^11]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
+[^12]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
 provides a novel structural candidate explanation for the persistence of gambler's fallacy beliefs", per MS.
@@
 Teams play either offense or defense for many consecutive rounds.
-(The former has a 14-14-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^12] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+(The former has a 14-14-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^13] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
 Bernoulli trials.
@@
 
-[^12]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
+[^13]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
 
@@
 
-The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^13] is
-
-[^13]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
+The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^14] is
+
+[^14]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
 
@@
 ```
-$s = 11$ rounds for CoD SnD.[^14]
-
-[^14]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
+$s = 11$ rounds for CoD SnD.[^15]
+
+[^15]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
 Upper-case symbol, e.g.
@@
 
-As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|kr}_{MS}$, to be strictly less than $p^{+|r}$.[^15] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|kr}_{MS}$ for $k > 1$.
-Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value, as I choose to do.[^16]
-
-[^15]: See Appendix E.1 of MS for the proof.
-
-[^16]: I have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
-
-Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^17] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
+As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|kr}_{MS}$, to be strictly less than $p^{+|r}$.[^16] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|kr}_{MS}$ for $k > 1$.
+Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value, as I choose to do.[^17]
+
+[^16]: See Appendix E.1 of MS for the proof.
+
+[^17]: I have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^18] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
 The Bernoulli trial success probability, i.e.
@@
 
-[^17]: GVT also performs statistical tests on shots from players in live games, i.e.
+[^18]: GVT also performs statistical tests on shots from players in live games, i.e.
 "observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
@@
 
-We can perform a binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^18] If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
-
-[^18]: $\omega$ and other symbols are chosen so as to not conflict with symbols already used elsewhere for in other equations, either generic or for CoD SnD specifically.
+We can perform a binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^19] If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
+
+[^19]: $\omega$ and other symbols are chosen so as to not conflict with symbols already used elsewhere for in other equations, either generic or for CoD SnD specifically.
 
@@
 Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with the Wald-Wolfowitz runs test.
-Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable, which can take on values $r^+$ and $r^-$ for success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$.
+Under the null hypothesis, the number of runs in a sequence of $r$ trials, $\zeta(r)$, is a random variable that can take on values $r^+$ and $r^-$ for success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$.
 
@@
 ```
-One might subset observed series sequences to those that violate the run test null hypothesis and perform a test of proportions, where the null is that the observed rate of such series is equal to the frequency that we should expect, given a choice for the constant round win probability $\phi$.
-If we can reject the null, then we can argue in favor of the hot hand.
+To incorporate my findings regarding constant round win probability, I can specify that $\Pr(r^+) = \phi$ (and, conversely, that $\Pr(r^-) = 1 - \phi$).
+
+One can subset the observed series sequences to those that violate the run test null hypothesis and perform a test of proportions, where the null is that the observed rate $\psi^+$ of such series is equal to the frequency rate $\psi_0$.
+The test statistic $Z$
+
+```{=tex}
+\begin{equation}\protect\hypertarget{eq:prop}{}{
+Z = \frac{\psi^+ - \psi^+_0}{\sqrt{\psi^+_d (1 - \psi^+_d) ( \frac{1}{N^+} + \frac{1}{\hat{N}^+})}}
+}\label{eq:prop}\end{equation}
+```
+where $\psi^+_d = \frac{r^+ - \hat{r}^+}{N^+ - \hat{N}^+}$. If we can reject the null hypothesis for many sequences, then there is implicit evidence in favor of the hot hand.
 
@@
 Chance's [-@chance2020] work is closely related to mine, and, in fact, provides a guide for this investigation.
-Afterwards, I investigate post-streak win rates and the context of momentum, leveraging MS's [-@miller2018] framework for streak selection bias.
+Afterwards, I investigate post-streak win rates and the context of momentum.
 
@@
 
-Using Equation \ref{eq:chi-squ}, I find that $\chi^2 = 16.0$ (p-value of 0.0068) for the naive constant round win probability $\phi_0 = 0.5$.
-Thus, I can comfortably reject the constant probability null hypothesis for $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
+Using Equation \ref{eq:chi-squ}, I find that $\chi^2 = 16.0$ ($p$-value of 0.0068) for the naive constant round win probability $\phi_0 = 0.5$.
+Thus, I can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
 
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^19] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^20] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^19]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+[^20]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^20] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{+|kr}_0$ and $\hat{P}^{+|kr}_{MS}$ respectively.
-
-[^20]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^21] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{+|kr}_0$ and $\hat{P}^{+|kr}_{MS}$ respectively.
+
+[^21]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
 
@@
 ```
-With the exception of $\hat{P}^{+|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^21], all un-adjusted binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
-Adjusting the $p$-values with the Benjamini & Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^22]
-
-[^21]: This implies that the opponent, the eventual series winner, goes on to win the series 6-4 after going down 0-4.
+With the exception of $\hat{P}^{+|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^22], all un-adjusted binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
+Adjusting the $p$-values with the Benjamini & Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^23]
+
+[^22]: This implies that the opponent, the eventual series winner, goes on to win the series 6-4 after going down 0-4.
 This is the only scenario in which one team wins four rounds consecutively but loses a best-of-11 series in 10 rounds.
 
-[^22]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
+[^23]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
 
 When performing the same tests for streaks of two, four, and five, there is no case in which I can reject the binomial null hypothesis for the expected notional probability $p^{+|kr}_0$.
-The null hypothesis can only be rejected for the expected MS probability $p^{+|kr}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^23]
-
-[^23]: At 36, the sample size for \$k = 5, r = 7\$ is not as large as most other combinations of \$k\$ and \$r\$.
+The null hypothesis can only be rejected for the expected MS probability $p^{+|kr}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^24]
+
+[^24]: At 36, the sample size for \$k = 5, r = 7\$ is not as large as most other combinations of \$k\$ and \$r\$.
 
@@
 Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|kri}_0$, is statistically different than the observed $P^{+|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^24] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
-
-[^24]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
+As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|kri}_0$, is statistically different than the observed $P^{+|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
+
+[^25]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
 
@@
 
-Further regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^25] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
-
-[^25]: <https://twitter.com/R11stats>
+Further regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+
+[^26]: <https://twitter.com/R11stats>
 

### 2022-08-21 paper/paper.tex
icing up son

@@
 
-\title{They're Clutching up! Team Momentum in Round-Based Esports}
+\title{They're Icing up! Team Momentum in Round-Based Esports}
 
@@
 \end{longtable}
+
+Anecdotally, observers swear by the existence of momentum in CoD SnD
+series, to the extent that vernacular has been developed to describe
+such phenomenon. People say that teams ``ice up'' when the team wins
+several consecutive rounds to come back to win a series, often
+culminating with a series-clinching round win.\footnote{This vernacular
+  is not specific to CoD SnD in specific, and is not only used in the
+  contexts of streaks.} Further, viewers have come to embrace the
+``5-3'' phenomenon, where teams win three consecutive rounds after
+facing a 5-3 deficit to win 6-5. There is even a term for the rare 0-5
+comeback---a ``full sail''.
 
@@
 phenomenon with the Wald-Wolfowitz runs test. Under the null hypothesis,
-the number of runs in a sequence of \(r\) trials is a random variable,
-which can take on values \(r^+\) and \(r^-\) for success and failure
-respectively, with the following mean \(\mu\) and variance \(\sigma^2\).
+the number of runs in a sequence of \(r\) trials, \(\zeta(r)\), is a
+random variable that can take on values \(r^+\) and \(r^-\) for success
+and failure respectively, with the following mean \(\mu\) and variance
+\(\sigma^2\).
 
@@
 
-One might subset observed series sequences to those that violate the run
-test null hypothesis and perform a test of proportions, where the null
-is that the observed rate of such series is equal to the frequency that
-we should expect, given a choice for the constant round win probability
-\(\phi\). If we can reject the null, then we can argue in favor of the
-hot hand.
+To incorporate my findings regarding constant round win probability, I
+can specify that \(\Pr(r^+) = \phi\) (and, conversely, that
+\(\Pr(r^-) = 1 - \phi\)).
+
+One can subset the observed series sequences to those that violate the
+run test null hypothesis and perform a test of proportions, where the
+null is that the observed rate \(\psi^+\) of such series is equal to the
+frequency rate \(\psi_0\). The test statistic \(Z\)
+
+\begin{equation}\protect\hypertarget{eq:prop}{}{
+Z = \frac{\psi^+ - \psi^+_0}{\sqrt{\psi^+_d (1 - \psi^+_d) ( \frac{1}{N^+} + \frac{1}{\hat{N}^+})}}
+}\label{eq:prop}\end{equation}
+
+where \(\psi^+_d = \frac{r^+ - \hat{r}^+}{N^+ - \hat{N}^+}\). If we can
+reject the null hypothesis for many sequences, then there is implicit
+evidence in favor of the hot hand.
 
@@
 investigation. Afterwards, I investigate post-streak win rates and the
-context of momentum, leveraging MS's (2018) framework for streak
-selection bias.
+context of momentum.
 
@@
 
-Using Equation \ref{eq:chi-squ}, I find that \(\chi^2 = 16.0\) (p-value
-of 0.0068) for the naive constant round win probability
+Using Equation \ref{eq:chi-squ}, I find that \(\chi^2 = 16.0\)
+(\(p\)-value of 0.0068) for the naive constant round win probability
 \(\phi_0 = 0.5\). Thus, I can comfortably reject the constant
-probability null hypothesis for \(\phi_0 = 0.5\), even at a confidence
-level of \(\alpha = 0.01\).
+probability hypothesis for the null \(\phi_0 = 0.5\), even at a
+confidence level of \(\alpha = 0.01\).
 

### 2022-08-21 paper/paper.Rmd
feedback thru old p6

@@
 ---
-title: "They're Icing up! Team Momentum in Round-Based Esports"
+title: "The Hot Hand in Call of Duty Search and Destroy"
 authors:
@@
     url: https://tonyelhabr.rbind.io
+  - name: Andrew ElHabr
+    email: andrewelhabr@gatech.edu
+    affiliation: Georgia Institute of Technology
+    department: School of Industrial and Systems Engineering (ISyE)
+    location: Atlanta, Georgia, USA
 abstract: |
-  My research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).
-First, I find evidence supprting the hypothesis that round win probability can be modeled as a constant across the series, although not at the naive 50%.
-Second, I examine post-streak round win probability, given the series outcome.
-I find no evidence that post-streak win rate is significantly different than expected for combinations of streak length, series length, and series winner, suggesting that the perception of momentum at the team level is just that, perception.
+  Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).
+First, we find evidence supprting the hypothesis that round win probability can be modeled as a constant across the series, although not at the naive 50%.
+Second, we examine post-streak round win probability, given the series outcome.
+We find no evidence that post-streak win rate is significantly different than expected for combinations of streak length, series length, and series winner, suggesting that the perception of momentum at the team level is just that, perception.
 bibliography: references.bib
+keywords:
+  - esports
+  - Call of Duty
+  - hot hand
+  - runs test
 output:
@@
   nrow()
+
+cod_win_series_prop <- cod_rounds |> 
+  distinct(series_id, win_series, n_rounds) |> 
+  count(n_rounds) |> 
+  mutate(prop = n / sum(n)) |> 
+  arrange(n_rounds)
 ```
@@
 
-## Game Description
+## Call of Duty Search and Destroy
 
@@
 
-In professional CoD SnD, a team take turns playing offense and defense every round. They must win six rounds to win the series.[^2] A round can end in one of five ways:
+In professional CoD SnD, the two teams take turns playing offense and defense every round. They must win six rounds to win the series.[^2] A round can end in one of five ways:
 
@@
 
-I adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
+We adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
 A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
@@
 
+SnD is not the only game type played in competitive CoD.
+Teams play in a head-to-head, best-of-five (first-to-three wins) format, where SnD is always played as the second and fifth game mode (if a fifth variant is needed).
+The best-of-five across game types could also be called a "series", but since we analyze only the SnD game types, we refer to SnD games as series (of rounds).
+
+Anecdotally, most observers swear by the existence of momentum in CoD SnD series, to the extent that vernacular has been developed to describe such phenomenon.
+People say that teams "ice up" when the team wins several consecutive rounds to come back to win a series, often culminating with a series-clinching round win.[^5] Further, viewers have come to embrace the "5-3" phenomenon, where teams win three consecutive rounds after facing a 5-3 deficit to win 6-5.
+There is even a term for the rare 0-5 comeback---a "full sail".
+
+[^5]: This vernacular is not specific to CoD SnD in specific, and is not only used in the contexts of streaks.
+
 ## Data
@@
 CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), operating since 2020.
-The CDL has completed three year-long "seasons" as of August 2022.[^5]
-
-[^5]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
+The CDL has completed three year-long "seasons" as of August 2022.[^6]
+
+[^6]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
 Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
@@
 
-The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^6] Data was collected in spreadsheets by community member "IOUTurtle".[^7]
-
-[^6]: 288 of the series occur in major tournaments, which are considered to be more "competitive" than the qualifiers since they are played in person (COVID-permitting), whereas the qualifiers are played online.
-
-[^7]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Processed data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
-
-The empirical offensive round win percentage across all rounds is $\tau_O$ = 47.8%.[^8] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^7] Data was collected in spreadsheets by community member "IOUTurtle".[^8]
+
+[^7]: 288 of the series occur in major tournaments, which are considered to be more "competitive" than the qualifiers since they are played in person (COVID-permitting), whereas the qualifiers are played online.
+
+[^8]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Processed data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
+
+The observed offensive round win percentage across all rounds is $\tau_O$ = 47.8%.[^9] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
-Offensive round win rate is not quite constant, although never veers more than 10% from this global average.[^9]
-
-[^8]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
-
-[^9]: At tournaments, higher-seeded ("better") teams choose whether they want to start on offense or defense in either the SnD series played as the second game or the fifth game in the best-of-five format used in tournaments, and their opponent is assigned to play offense in the first round of the SnD slot (second or fifth game) not chosen.
-[@codrules] (Other game variants like Hardpoint are played as the first, third, and fourth games in the matchup.) Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game, although this choice is not universal.
-With online qualifiers, teams all play each other twice throughout the season.
-Each team gets to play the higher-seeded role once in their matchups, despite their win-loss records.
+Offensive round win rate is not quite constant, although never veers more than 10% from this overall average.
+
+[^9]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
 
@@
 \begin{longtable}{crrrrrr}
-\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins}\label{tbl:cod-o-win-prop-by-series-state} \\
+\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins.
+Numbers in parentheses are sample sizes.}\label{tbl:cod-o-win-prop-by-series-state} \\
 \toprule
@@
 ```
-Anecdotally, observers swear by the existence of momentum in CoD SnD series, to the extent that vernacular has been developed to describe such phenomenon.
-People say that teams "ice up" when the team wins several consecutive rounds to come back to win a series, often culminating with a series-clinching round win.[^10] Further, viewers have come to embrace the "5-3" phenomenon, where teams win three consecutive rounds after facing a 5-3 deficit to win 6-5.
-There is even a term for the rare 0-5 comeback---a "full sail".
-
-[^10]: This vernacular is not specific to CoD SnD in specific, and is not only used in the contexts of streaks.
+On the extremes, 6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7 of series.
+
+At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series played as the second game or the fifth game, and their opponent is assigned to play offense in the first round of the SnD slot not chosen.[^10][^11] [@codrules] With online qualifiers, teams all play each other twice throughout the season.
+Each team gets to play the higher-seeded role once in their matchups, despite their win-loss records.
+Overall, we might say that bias due to stronger teams playing defense (slightly advantageous) more often is very minimal.
+
+[^10]: "Hardpoint" has been played as the first and fourth games in a matchup; the variant for the third game was Domination in the 2020 season, and Control in the 2021 and 2022 seasons.
+
+[^11]: Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game, although this choice is not consistent across teams, or with the same team over time.
 
@@
 Mosteller [-@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that games should not be modeled with a constant (null) $\phi_0 = 0.5$.
-Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\phi \approx 0.65$ in each case: (1) solving for $p$ from the empirical average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
+Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\phi \approx 0.65$ in each case: (1) solving for $\phi$ from the observed average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
 maximum likelihood), and (3) minimizing the chi-square goodness of fit statistic $\chi^2$ for $\phi$.
@@
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^11] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^12] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^11]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^12]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 [-@gilovich1985], henceforth GVT, do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo [-@miller2018], henceforth MS, refuted the conclusions of GVT, proving a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy[^12].
+However, Miller and Sanjurjo [-@miller2018], henceforth MS, provide a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy.
 Specifically, MS say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
 conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success".
-When applying streak selection bias to GVT.'s data, MS come to the opposite conclusions as GVT.
-
-[^12]: Streak selection bias, "in conjunction with a quasi-Bayesian model of decision making under sample size neglect...
-provides a novel structural candidate explanation for the persistence of gambler's fallacy beliefs", per MS.
+When applying streak selection bias to GVT's data, MS come to the opposite conclusions as GVT.
 
@@
 
-## My contribution
+## Our contribution
 
@@
 
-[^13]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least one in each league.
-
-To my knowledge, there is no existing public statistical research on CoD SnD format, beyond descriptive analysis on social media.
+[^13]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each league.
+
+To our knowledge, there is no existing public statistical research on CoD SnD format, beyond descriptive analysis on social media.
 While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation on a common concept like the hot-hand phenomenon in a new field---particularly one that is less subjected to factors that may be difficult to control for, e.g.
-weather---should hopefully be useful as a precedent or supplement for future researchers.
+weather---should be useful as a precedent or supplement for future researchers.
 
@@
 
-The formula for the expected proportion of series a best-of-$s$ format ending in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$, for a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^14] is
-
-[^14]: If $\phi > 0.5$, then one might say that this team is the better team (known in hindsight).
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:m}{}{
+In a best-of-$s$ format, assuming a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^14], the probability that a series ends in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$ is
+
+[^14]: If $\phi > 0.5$, we can say that this is the stronger team.
+
+```{=tex}
+\begin{equation}\label{eq:m}
 m = \frac{s + 1}{2}
-}\label{eq:m}\end{equation}
-```
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:series-length}{}{
+\end{equation}
+```
+```{=tex}
+\begin{equation}\label{eq:series-length}
 \hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
-}\label{eq:series-length}\end{equation}
-```
-$s = 11$ rounds for CoD SnD.[^15]
+\end{equation}
+```
+$s = 11$ rounds for CoD SnD.[^15] For example, assuming $\phi = 0.5$, the probability of a series ending in 9 rounds in CoD is
 
@@
 Upper-case symbol, e.g.
-$\Phi$, are consistently used in this paper to represent proportions, while lower-case symbols corresponding to proportions represent probabilities.
+$\Phi$, are consistently used in this paper to represent proportions, while lower-case symbols are used to represent Bernoulli trials success probability.
 "Hats", e.g.
-$\hat{\Phi}$, are used to convey expectations, while "bare" symbols mirroring hat-ed symbols convey observational data.
-
-To evaluate the constant round win probability null hypothesis---that is, that the expected and observed round win rates, $\hat{\Phi}(r)$ and $\Phi(r)$ respectively, are equal to one another---we can compute the chi-square goodness of fit statistic, $\chi^2$,
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:chi-squ}{}{
-\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}.
-}\label{eq:chi-squ}\end{equation}
-```
-$r \in R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
+$\hat{\Phi}$, are used to convey expectations, while bare symbols symbols convey observational data.
+
+$$
+\hat{\Phi}(9) = \frac{(9 - 1)!}{(6 - 1)!(11 - 9)!}(0.5^{6}(1 - 0.5)^{9 - 6} + 0.5^{9 - 6}(1 - 0.5)^6) = 56 (0.5^9 + 0.5^9) = 0.21875.
+$$
+
+To evaluate the constant round win probability null hypothesis---that is, that the expected and observed round win rates, $\hat{\Phi}(r)$ and $\Phi(r)$ respectively, are equal to one another---we can compute the chi-square goodness of fit statistic
+
+```{=tex}
+\begin{equation}\label{eq:chi-squ}
+\chi^2 = \sum^{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}.
+\end{equation}
+```
+in which $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
 
@@
 ```{=tex}
-\begin{equation}\protect\hypertarget{eq:pwr}{}{
-p_0(\text{win} | r) = p^{+|r}_0 = \{
-\begin{array}{cl}
-\frac{m}{r}, & \text{team wins series} \\
-\frac{r - m}{r}, & \text{team loses series}
-\end{array}
-}
-\label{eq:pwr}
+\begin{equation}\label{eq:pwr}
+p_0(\text{win} | r) = p^{+|r}_0 = \begin{cases} 
+\frac{m}{r} & \text{team wins series} \\ 
+\frac{r - m}{r} & \text{team loses series}  
+\end{cases}
 \end{equation}
@@
 
-As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|kr}_{MS}$, to be strictly less than $p^{+|r}$.[^16] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|kr}_{MS}$ for $k > 1$.
-Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value, as I choose to do.[^17]
+As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.[^16] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|k,r}_{MS}$ for $k > 1$.
+Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value, as We choose to do.[^17]
 
@@
 
-[^17]: I have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
-
-Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), my context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^18] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
+[^17]: We have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^18] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
 The Bernoulli trial success probability, i.e.
 a round win in CoD SnD, is not independent of the opponent.
-Consequently, a statistical test of the difference in $\hat{P}^{+|kr}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rates, is not completely appropriate, although useful as a reference.
+Consequently, a statistical test of the difference in $\hat{P}^{+|k,r}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rates, is not completely appropriate, although useful as a reference.
 
@@
 
-One might consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|kr}_0$.
-The Bernoulli round win probability underlying $\hat{P}^{+|kr}_0$ is
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:pwkr}{}{
-p_0(\text{win} | k, r) = p^{+|kr}_0 =\{
-\begin{array}{cl}
-\frac{m - k}{r - k}, & \text{team wins series} \\
-\frac{s - m - k}{r - k}, & \text{team loses series}
-\end{array}
-}
-\label{eq:pwkr}
+One can consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|k,r}_0$.
+The Bernoulli round win probability underlying $\hat{P}^{+|k,r}_0$ is
+
+```{=tex}
+\begin{equation}\label{eq:pwkr}
+p_0(\text{win} | k, r) = p^{+|k,r}_0 = \begin{cases}
+\frac{m - k}{r - k} & \text{team wins series} \\
+\frac{s - m - k}{r - k} & \text{team loses series}
+\end{cases}
 \end{equation}
@@
 ```{=tex}
-\begin{equation}\protect\hypertarget{eq:binom}{}{
+\begin{equation}\label{eq:binom}
 \Pr(r^w) = {\binom {r}{r^+}} \omega^{r^+}(1-\omega)^{r-r^+}.
-}\label{eq:binom}\end{equation}
-```
-Plugging in the notional proportion $\hat{p}^{+|kr}_0$ for the null $\omega_0$ and the observed proportion $P^{+|kr}$ for $\omega$ (treating proportions as probabilities), we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
-If we can reject this null hypothesis, then we might consider team momentum, represented by post-streak success, plausible.
-
-One can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|kr}_{MS}$. FOOTY: Given the caveats mentioned before, the results should be heeded with caution.
+\end{equation}
+```
+Treating the notional proportion $p^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
+If we can reject this null hypothesis, then we can consider team momentum, represented by post-streak success, plausible.
+
+One can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|k,r}_{MS}$. FOOTY: Given the caveats mentioned before, the results should be heeded with caution.
 
@@
 \begin{equation}\protect\hypertarget{eq:pwkri}{}{
-p_0(\text{win} | k, r, i) = p^{+|kri}_0 =\{
+p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 =\{
 \begin{array}{cl}
@@
 ```
-Again, one might apply a binomial test to evaluate the hypothesis that the expected proportions, both $\hat{P}^{+|kri}_0$ and $\hat{P}^{+|kri}_{MS}$, are equal to the observed proportion $P^{+|kr}$.
+Again, one might apply a binomial test to evaluate the hypothesis that the expected proportions, both $\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$, are equal to the observed proportion $P^{+|k,r}$.
 
@@
 ```
-To incorporate my findings regarding constant round win probability, I can specify that $\Pr(r^+) = \phi$ (and, conversely, that $\Pr(r^-) = 1 - \phi$).
+To incorporate our findings regarding constant round win probability, We can specify that $\Pr(r^+) = \phi$ (and, conversely, that $\Pr(r^-) = 1 - \phi$).
 
@@
 
-First, I investigate the constant probability assumption and the distribution of rounds played in a series.
+First, We investigate the constant probability assumption and the distribution of rounds played in a series.
 Chance's [-@chance2020] work is closely related to mine, and, in fact, provides a guide for this investigation.
-Afterwards, I investigate post-streak win rates and the context of momentum.
+Afterwards, We investigate post-streak win rates within the context of momentum.
 
@@
 
-Using Equation \ref{eq:chi-squ}, I find that $\chi^2 = 16.0$ ($p$-value of 0.0068) for the naive constant round win probability $\phi_0 = 0.5$.
-Thus, I can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
+Using Equation \ref{eq:chi-squ}, We find that $\chi^2 = 16.0$ ($p$-value of 0.0068) for the naive constant round win probability $\phi_0 = 0.5$.
+Thus, We can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
 
@@
 \begin{longtable}{rrrr}
-\caption{The expected proportion of series lasting $r$ rounds ($\hat{\Phi}_0(r)$) in a best-of-11 format, wehre $r \in R = [6, 7, 8, 9, 10, 11]$ under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-The observed frequencies for CoD SnD are shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^R N(r)$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
+\caption{The expected proportion of series lasting $r$ rounds ($\hat{\Phi}_0(r)$) in a best-of-11 format, where $r \in R = [6, 7, 8, 9, 10, 11]$ under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
+The observed frequencies for CoD SnD are shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
 \toprule
-$r$ & $\hat{\Phi}_0(r)$ & $\Phi(r)$ & $N(r)$ \\ 
+$r$ & $N(r)$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ \\ 
 \midrule
-6 & $3.1\%$ & $4.7\%$ & 40 \\ 
-7 & $9.4\%$ & $11.9\%$ & 101 \\ 
-8 & $16.4\%$ & $16.5\%$ & 141 \\ 
-9 & $21.9\%$ & $21.7\%$ & 185 \\ 
-10 & $24.6\%$ & $21.5\%$ & 183 \\ 
-11 & $24.6\%$ & $23.7\%$ & 202 \\ 
+6 & 40 & $4.7\%$ & $3.1\%$ \\ 
+7 & 101 & $11.9\%$ & $9.4\%$ \\ 
+8 & 141 & $16.5\%$ & $16.4\%$ \\ 
+9 & 185 & $21.7\%$ & $21.9\%$ \\ 
+10 & 183 & $21.5\%$ & $24.6\%$ \\ 
+11 & 202 & $23.7\%$ & $24.6\%$ \\ 
 \bottomrule
@@
 
-## This adjustment is something that is not done in the paper. I do it here to reduce
+## This adjustment is something that is not done in the paper. We do it here to reduce
 ##   the magnitude of the exponents.
@@
 
-Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that I find when applying the three methods suggested by Mosteller [-@mosteller1952].
-Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which I cannot reject the constant probability null hypothesis.
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that We find when applying the three methods suggested by Mosteller [-@mosteller1952].
+Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which We cannot reject the constant probability null hypothesis.
 
@@
 \endhead
-0. Naive & 0.5000 & 16.0 (\textless=0.01) \\
+0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
 1. Method of moments & 0.5725 & 3.6 (0.6) \\
@@
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^20] I observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^20] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
@@
 \toprule()
-$r$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 & $\Phi(r)$ \\
+$r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
 \midrule()
 \endhead
-6 & 3.1\% & 4.2\% & 4.7\% \\
-7 & 9.4\% & 11.2\% & 11.9\% \\
-8 & 16.4\% & 17.8\% & 16.5\% \\
-9 & 21.9\% & 21.8\% & 21.7\% \\
-10 & 24.6\% & 23.0\% & 21.5\% \\
-11 & 24.6\% & 22.0\% & 23.7\% \\
+6 & 4.7\% & 3.1\% & 4.2\% \\
+7 & 11.9\% & 9.4\% & 11.2\% \\
+8 & 16.5\% & 16.4\% & 17.8\% \\
+9 & 21.7\% & 21.9\% & 21.8\% \\
+10 & 21.5\% & 24.6\% & 23.0\% \\
+11 & 23.7\% & 24.6\% & 22.0\% \\
 \bottomrule()
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], I focus on streaks of three round wins.[^21] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{+|kr}_0$ and $\hat{P}^{+|kr}_{MS}$ respectively.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], We focus on streaks of three round wins.[^21] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively.
 
@@
 \begin{longtable}{rcrrrrr}
-\caption{Given the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|kr}$, and proportion of round wins, $P^{+|kr}$, among $N^{kr}$ instances where a team could win after the streak $k=3$ ($P^{+|kr} = \frac{r^{+|kr}}{N^{kr}}$).
-Additionally, the notional and MS expected proportions, $\hat{P}^{+|kr}_0$ and $\hat{P}^{+|kr}_{MS}$ respectively.}
+\caption{Given the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r}$, and proportion of round wins, $P^{+|k,r}$, among $N^{kr}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r} = \frac{r^{+|k,r}}{N^{kr}}$).
+Additionally, the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively.}
 \label{tbl:cod-pw3r-pl3r} \\
@@
 \toprule
-$r$ & \text{Win series?} & $r^{+|kr}$ & $N^{kr}$ & $P^{+|kr}$ & $\hat{P}^{+|kr}_0$ & $\hat{P}^{+|kr}_{MS}$ \\ 
+$r$ & \text{Win series?} & $r^{+|k,r}$ & $N^{kr}$ & $P^{+|k,r}$ & $\hat{P}^{+|k,r}_0$ & $\hat{P}^{+|k,r}_{MS}$ \\ 
 \midrule
@@
 ```
-With the exception of $\hat{P}^{+|kr}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^22], all un-adjusted binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
+With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^22], all un-adjusted binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
 Adjusting the $p$-values with the Benjamini & Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^23]
@@
 
-When performing the same tests for streaks of two, four, and five, there is no case in which I can reject the binomial null hypothesis for the expected notional probability $p^{+|kr}_0$.
-The null hypothesis can only be rejected for the expected MS probability $p^{+|kr}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^24]
+When performing the same tests for streaks of two, four, and five, there is no case in which We can reject the binomial null hypothesis for the expected notional probability $p^{+|k,r}_0$.
+The null hypothesis can only be rejected for the expected MS probability $p^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^24]
 
@@
 Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|kri}_0$, is statistically different than the observed $P^{+|kri}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
+As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
 
@@
 \begin{longtable}{rrcrrrr}
-\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|kri}$, and proportion of round wins, $P^{+|kri}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|kri} = \frac{r^{+|kri}}{N^{kri}}$).
-Additionally, the notional proportion, $\hat{P}^{+|kri}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|kri}_0$ to the observed proportion $P^{+|kri}$.
+\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r,i}$, and proportion of round wins, $P^{+|k,r,i}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r,i} = \frac{r^{+|k,r,i}}{N^{kri}}$).
+Additionally, the notional proportion, $\hat{P}^{+|k,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k,r,i}_0$ to the observed proportion $P^{+|k,r,i}$.
 Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{kri} > 10$ for brevity.}
@@
 \toprule
-$r$ & $i$ & \text{Win series?} & $r^{+|kri}$ & $N^{kri}$ & $P^{+|kri}$ & $\hat{P}^{+|kri}_0$\\ 
+$r$ & $i$ & \text{Win series?} & $r^{+|k,r,i}$ & $N^{kri}$ & $P^{+|k,r,i}$ & $\hat{P}^{+|k,r,i}_0$\\ 
 \midrule
@@
 
-For the sake of brevity, I did not delve into win rates and streaks split by offensive or defensive role.
+For the sake of brevity, We did not delve into win rates and streaks split by offensive or defensive role.
 For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak winning as the offensive team.
 This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx$ 13.0%---so I would want to account for sample size differences.
-
-Further regarding future work, I've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx$ 13.0%---so We would want to account for sample size differences.
+
+Further regarding future work, We've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
 
@@
 
-Thank my brother Andrew for giving me feedback on drafts of this paper.
+Thank our brother Andrew for giving me feedback on drafts of this paper.
 

### 2022-08-21 paper/paper.tex
feedback thru old p6

@@
 
-\title{They're Icing up! Team Momentum in Round-Based Esports}
+\title{The Hot Hand in Call of Duty Search and Destroy}
 
@@
   \texttt{\href{mailto:anthonyelhabr@gmail.com}{\nolinkurl{anthonyelhabr@gmail.com}}} \\
+   \And
+    Andrew ElHabr
+   \\
+    School of Industrial and Systems Engineering (ISyE) \\
+    Georgia Institute of Technology \\
+  Atlanta, Georgia, USA \\
+  \texttt{\href{mailto:andrewelhabr@gatech.edu}{\nolinkurl{andrewelhabr@gatech.edu}}} \\
   }
@@
 \begin{abstract}
-My research investigates patterns in round win percentages in
+Our research investigates patterns in round win percentages in
 professional Search and Destroy (SnD) matches of the popular
-first-person shooter game Call of Duty (CoD). First, I find evidence
+first-person shooter game Call of Duty (CoD). First, we find evidence
 supprting the hypothesis that round win probability can be modeled as a
-constant across the series, although not at the naive 50\%. Second, I
-examine post-streak round win probability, given the series outcome. I
+constant across the series, although not at the naive 50\%. Second, we
+examine post-streak round win probability, given the series outcome. We
 find no evidence that post-streak win rate is significantly different
@@
 
+\keywords{
+    esports
+   \and
+    Call of Duty
+   \and
+    hot hand
+   \and
+    runs test
+  }
+
 \hypertarget{introduction}{%
@@
 
-\hypertarget{game-description}{%
-\subsection{Game Description}\label{game-description}}
+\hypertarget{call-of-duty-search-and-destroy}{%
+\subsection{Call of Duty Search and
+Destroy}\label{call-of-duty-search-and-destroy}}
 
@@
 
-In professional CoD SnD, a team take turns playing offense and defense
-every round. They must win six rounds to win the series.\footnote{A
-  maximum of 11 even rounds can be played. There is no ``sudden death''
-  or ``win by two'' rule like there are for SnD equivalent in
-  professional Counter-Strike and Valorant matches.} A round can end in
-one of five ways:
+In professional CoD SnD, the two teams take turns playing offense and
+defense every round. They must win six rounds to win the
+series.\footnote{A maximum of 11 even rounds can be played. There is no
+  ``sudden death'' or ``win by two'' rule like there are for SnD
+  equivalent in professional Counter-Strike and Valorant matches.} A
+round can end in one of five ways:
 
@@
 
-I adopt the terminology ``series'' to refer to what CoD SnD players
+We adopt the terminology ``series'' to refer to what CoD SnD players
 typically call a ``match'', so as to emulate the terminology of playoff
@@
 events.
+
+SnD is not the only game type played in competitive CoD. Teams play in a
+head-to-head, best-of-five (first-to-three wins) format, where SnD is
+always played as the second and fifth game mode (if a fifth variant is
+needed). The best-of-five across game types could also be called a
+``series'', but since we analyze only the SnD game types, we refer to
+SnD games as series (of rounds).
+
+Anecdotally, most observers swear by the existence of momentum in CoD
+SnD series, to the extent that vernacular has been developed to describe
+such phenomenon. People say that teams ``ice up'' when the team wins
+several consecutive rounds to come back to win a series, often
+culminating with a series-clinching round win.\footnote{This vernacular
+  is not specific to CoD SnD in specific, and is not only used in the
+  contexts of streaks.} Further, viewers have come to embrace the
+``5-3'' phenomenon, where teams win three consecutive rounds after
+facing a 5-3 deficit to win 6-5. There is even a term for the rare 0-5
+comeback---a ``full sail''.
 
@@
 
-The empirical offensive round win percentage across all rounds is
+The observed offensive round win percentage across all rounds is
 \(\tau_O\) = 47.8\%.\footnote{Offensive round win percentage has been
@@
 team prior to an upcoming round). Offensive round win rate is not quite
-constant, although never veers more than 10\% from this global
-average.\footnote{At tournaments, higher-seeded (``better'') teams
-  choose whether they want to start on offense or defense in either the
-  SnD series played as the second game or the fifth game in the
-  best-of-five format used in tournaments, and their opponent is
-  assigned to play offense in the first round of the SnD slot (second or
-  fifth game) not chosen. ({``Competitive Settings \textbar{} Call of
-  Duty League,''} n.d.) (Other game variants like Hardpoint are played
-  as the first, third, and fourth games in the matchup.) Anecdotally,
-  the higher-seeded teams tend to choose to play defense in the first
-  round of the SnD series played as the second game, although this
-  choice is not universal. With online qualifiers, teams all play each
-  other twice throughout the season. Each team gets to play the
-  higher-seeded role once in their matchups, despite their win-loss
-  records.}
+constant, although never veers more than 10\% from this overall average.
 
 \begin{longtable}{crrrrrr}
-\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins}\label{tbl:cod-o-win-prop-by-series-state} \\
+\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins.
+Numbers in parentheses are sample sizes.}\label{tbl:cod-o-win-prop-by-series-state} \\
 \toprule
@@
 
-Anecdotally, observers swear by the existence of momentum in CoD SnD
-series, to the extent that vernacular has been developed to describe
-such phenomenon. People say that teams ``ice up'' when the team wins
-several consecutive rounds to come back to win a series, often
-culminating with a series-clinching round win.\footnote{This vernacular
-  is not specific to CoD SnD in specific, and is not only used in the
-  contexts of streaks.} Further, viewers have come to embrace the
-``5-3'' phenomenon, where teams win three consecutive rounds after
-facing a 5-3 deficit to win 6-5. There is even a term for the rare 0-5
-comeback---a ``full sail''.
+On the extremes, 6-0 sweeps make up 4.7\% of all series, while 6-5
+series make up 23.7 of series.
+
+At tournaments, higher-seeded (``better'') teams choose whether they
+want to start on offense in the SnD series played as the second game or
+the fifth game, and their opponent is assigned to play offense in the
+first round of the SnD slot not chosen.\footnote{``Hardpoint'' has been
+  played as the first and fourth games in a matchup; the variant for the
+  third game was Domination in the 2020 season, and Control in the 2021
+  and 2022 seasons.}\footnote{Anecdotally, the higher-seeded teams tend
+  to choose to play defense in the first round of the SnD series played
+  as the second game, although this choice is not consistent across
+  teams, or with the same team over time.} ({``Competitive Settings
+\textbar{} Call of Duty League,''} n.d.) With online qualifiers, teams
+all play each other twice throughout the season. Each team gets to play
+the higher-seeded role once in their matchups, despite their win-loss
+records. Overall, we might say that bias due to stronger teams playing
+defense (slightly advantageous) more often is very minimal.
 
@@
 team in the World Series, finding \(\phi \approx 0.65\) in each case:
-(1) solving for \(p\) from the empirical average number of games won by
-the loser of the series, which he called the ``method of moments''
+(1) solving for \(\phi\) from the observed average number of games won
+by the loser of the series, which he called the ``method of moments''
 approach; (2) maximizing the likelihood that the sample would have been
@@
 henceforth GVT, do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo (2018), henceforth MS, refuted the
-conclusions of GVT, proving a framework for quantifying streak selection
-bias, which effectively works in the manner posited by the gambler's
-fallacy\footnote{Streak selection bias, ``in conjunction with a
-  quasi-Bayesian model of decision making under sample size
-  neglect\ldots{} provides a novel structural candidate explanation for
-  the persistence of gambler's fallacy beliefs'', per MS.}.
-Specifically, MS say that a ``bias exists in a common measure of the
-conditional dependence of present outcomes on streaks of past outcomes
-in sequential data'' implying that, under i.i.d. conditions, ``the
-proportion of successes among the outcomes that immediately follow a
-streak of consecutive successes is expected to be strictly less than the
-underlying (conditional) probability of success''. When applying streak
-selection bias to GVT.'s data, MS come to the opposite conclusions as
-GVT.
+However, Miller and Sanjurjo (2018), henceforth MS, provide a framework
+for quantifying streak selection bias, which effectively works in the
+manner posited by the gambler's fallacy. Specifically, MS say that a
+``bias exists in a common measure of the conditional dependence of
+present outcomes on streaks of past outcomes in sequential data''
+implying that, under i.i.d. conditions, ``the proportion of successes
+among the outcomes that immediately follow a streak of consecutive
+successes is expected to be strictly less than the underlying
+(conditional) probability of success''. When applying streak selection
+bias to GVT's data, MS come to the opposite conclusions as GVT.
 
@@
 
-\hypertarget{my-contribution}{%
-\subsection{My contribution}\label{my-contribution}}
+\hypertarget{our-contribution}{%
+\subsection{Our contribution}\label{our-contribution}}
 
@@
   for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
-    is not used today in these leagues, but it was at least one in each
+    is not used today in these leagues, but it was at least once in each
     league.} While theoretically one might be able to account for any
@@
 
-To my knowledge, there is no existing public statistical research on CoD
-SnD format, beyond descriptive analysis on social media. While
+To our knowledge, there is no existing public statistical research on
+CoD SnD format, beyond descriptive analysis on social media. While
 intra-round trends may be more directly applicable to teams looking for
@@
 that is less subjected to factors that may be difficult to control for,
-e.g.~weather---should hopefully be useful as a precedent or supplement
-for future researchers.
+e.g.~weather---should be useful as a precedent or supplement for future
+researchers.
 
@@
 
-The formula for the expected proportion of series a best-of-\(s\) format
-ending in \(r\) rounds (\(r \leq s\)), \(\hat{\Phi}(r)\), for a constant
-round win probability \(\phi\) (\(0 \leq \phi \leq 1\)) for one
-team\footnote{If \(\phi > 0.5\), then one might say that this team is
-  the better team (known in hindsight).} is
+In a best-of-\(s\) format, assuming a constant round win probability
+\(\phi\) (\(0 \leq \phi \leq 1\)) for one team\footnote{If
+  \(\phi > 0.5\), we can say that this is the stronger team.}, the
+probability that a series ends in \(r\) rounds (\(r \leq s\)),
+\(\hat{\Phi}(r)\) is
 
-\begin{equation}\protect\hypertarget{eq:m}{}{
+\begin{equation}\label{eq:m}
 m = \frac{s + 1}{2}
-}\label{eq:m}\end{equation}
+\end{equation}
 
-\begin{equation}\protect\hypertarget{eq:series-length}{}{
+\begin{equation}\label{eq:series-length}
 \hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
-}\label{eq:series-length}\end{equation}
+\end{equation}
 
@@
   e.g.~\(\Phi\), are consistently used in this paper to represent
-  proportions, while lower-case symbols corresponding to proportions
-  represent probabilities. ``Hats'', e.g.~\(\hat{\Phi}\), are used to
-  convey expectations, while ``bare'' symbols mirroring hat-ed symbols
-  convey observational data.}
+  proportions, while lower-case symbols are used to represent Bernoulli
+  trials success probability. ``Hats'', e.g.~\(\hat{\Phi}\), are used to
+  convey expectations, while bare symbols symbols convey observational
+  data.} For example, assuming \(\phi = 0.5\), the probability of a
+series ending in 9 rounds in CoD is
+
+\[
+\hat{\Phi}(9) = \frac{(9 - 1)!}{(6 - 1)!(11 - 9)!}(0.5^{6}(1 - 0.5)^{9 - 6} + 0.5^{9 - 6}(1 - 0.5)^6) = 56 (0.5^9 + 0.5^9) = 0.21875.
+\]
 
@@
 and \(\Phi(r)\) respectively, are equal to one another---we can compute
-the chi-square goodness of fit statistic, \(\chi^2\),
+the chi-square goodness of fit statistic
 
-\begin{equation}\protect\hypertarget{eq:chi-squ}{}{
-\chi^2 = \sum^R \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}.
-}\label{eq:chi-squ}\end{equation}
+\begin{equation}\label{eq:chi-squ}
+\chi^2 = \sum^{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}.
+\end{equation}
 
-\(r \in R = [6, 7, 8, 9, 10, 11]\) for CoD SnD.
+in which \(R = [6, 7, 8, 9, 10, 11]\) for CoD SnD.
 
@@
 
-\begin{equation}\protect\hypertarget{eq:pwr}{}{
-p_0(\text{win} | r) = p^{+|r}_0 = \{
-\begin{array}{cl}
-\frac{m}{r}, & \text{team wins series} \\
-\frac{r - m}{r}, & \text{team loses series}
-\end{array}
-}
-\label{eq:pwr}
+\begin{equation}\label{eq:pwr}
+p_0(\text{win} | r) = p^{+|r}_0 = \begin{cases} 
+\frac{m}{r} & \text{team wins series} \\ 
+\frac{r - m}{r} & \text{team loses series}  
+\end{cases}
 \end{equation}
@@
 rounds wins immediately following a streak of \(k\) rounds wins for a
-series lasting \(r\) rounds, \(\hat{P}^{+|kr}_{MS}\), to be strictly
+series lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly
 less than \(p^{+|r}\).\footnote{See Appendix E.1 of MS for the proof.}
 Unfortunately, there does not exist a closed form representation for the
-expected value of \(\hat{P}^{+|kr}_{MS}\) for \(k > 1\). Nonetheless,
+expected value of \(\hat{P}^{+|k,r}_{MS}\) for \(k > 1\). Nonetheless,
 one may recursively build a collection of dictionaries to compute the
 expectation analytically, or, more conveniently, one may run simulations
-to estimate the expected value, as I choose to do.\footnote{I have
+to estimate the expected value, as We choose to do.\footnote{We have
   adapted the code from Vafa (2017), which implements MS's framework
@@
 Although it would be convenient to emulate the hypothesis testing for
-difference of proportions performed by MS (and GVT), my context is
+difference of proportions performed by MS (and GVT), our context is
 fundamentally different from that of MS, who focus on longitudinal data
@@
 SnD, is not independent of the opponent. Consequently, a statistical
-test of the difference in \(\hat{P}^{+|kr}\) and \(\hat{P}^{-|kr}\), as
+test of the difference in \(\hat{P}^{+|k,r}\) and \(\hat{P}^{-|kr}\), as
 performed by MS to evaluate their hypothesis regarding post-streak
@@
 
-One might consider another form of the expected proportion of rounds won
+One can consider another form of the expected proportion of rounds won
 immediately after a streak of \(k\) round wins in a best-of-\(s\) series
 given the length of the series (\(r\) rounds), the ``notional''
-proportion \(\hat{P}^{+|kr}_0\). The Bernoulli round win probability
-underlying \(\hat{P}^{+|kr}_0\) is
+proportion \(\hat{P}^{+|k,r}_0\). The Bernoulli round win probability
+underlying \(\hat{P}^{+|k,r}_0\) is
 
-\begin{equation}\protect\hypertarget{eq:pwkr}{}{
-p_0(\text{win} | k, r) = p^{+|kr}_0 =\{
-\begin{array}{cl}
-\frac{m - k}{r - k}, & \text{team wins series} \\
-\frac{s - m - k}{r - k}, & \text{team loses series}
-\end{array}
-}
-\label{eq:pwkr}
+\begin{equation}\label{eq:pwkr}
+p_0(\text{win} | k, r) = p^{+|k,r}_0 = \begin{cases}
+\frac{m - k}{r - k} & \text{team wins series} \\
+\frac{s - m - k}{r - k} & \text{team loses series}
+\end{cases}
 \end{equation}
@@
 
-\begin{equation}\protect\hypertarget{eq:binom}{}{
+\begin{equation}\label{eq:binom}
 \Pr(r^w) = {\binom {r}{r^+}} \omega^{r^+}(1-\omega)^{r-r^+}.
-}\label{eq:binom}\end{equation}
+\end{equation}
 
-Plugging in the notional proportion \(\hat{p}^{+|kr}_0\) for the null
-\(\omega_0\) and the observed proportion \(P^{+|kr}\) for \(\omega\)
-(treating proportions as probabilities), we can evaluate the null
-hypothesis that the observed probability is equal to the notional
-probability. If we can reject this null hypothesis, then we might
-consider team momentum, represented by post-streak success, plausible.
+Treating the notional proportion \(p^{+|k,r}_0\) as the null
+\(\omega_0\) and plugging in the observed proportion \(P^{+|k,r}\) for
+\(\omega\) in Equation \ref{eq:binom} (treating proportions as
+probabilities), we can evaluate the null hypothesis that the observed
+probability is equal to the notional probability. If we can reject this
+null hypothesis, then we can consider team momentum, represented by
+post-streak success, plausible.
 
 One can perform the same binomial test for the MS's
-streak-selection-adjusted proportion, \(\hat{P}^{+|kr}_{MS}\). FOOTY:
+streak-selection-adjusted proportion, \(\hat{P}^{+|k,r}_{MS}\). FOOTY:
 Given the caveats mentioned before, the results should be heeded with
@@
 Again, one might apply a binomial test to evaluate the hypothesis that
-the expected proportions, both \(\hat{P}^{+|kri}_0\) and
-\(\hat{P}^{+|kri}_{MS}\), are equal to the observed proportion
-\(P^{+|kr}\).
+the expected proportions, both \(\hat{P}^{+|k,r,i}_0\) and
+\(\hat{P}^{+|k,r,i}_{MS}\), are equal to the observed proportion
+\(P^{+|k,r}\).
 
@@
 
-To incorporate my findings regarding constant round win probability, I
+To incorporate our findings regarding constant round win probability, We
 can specify that \(\Pr(r^+) = \phi\) (and, conversely, that
@@
 
-First, I investigate the constant probability assumption and the
+First, We investigate the constant probability assumption and the
 distribution of rounds played in a series. Chance's (2020) work is
 closely related to mine, and, in fact, provides a guide for this
-investigation. Afterwards, I investigate post-streak win rates and the
-context of momentum.
+investigation. Afterwards, We investigate post-streak win rates within
+the context of momentum.
 
@@
 
-Using Equation \ref{eq:chi-squ}, I find that \(\chi^2 = 16.0\)
+Using Equation \ref{eq:chi-squ}, We find that \(\chi^2 = 16.0\)
 (\(p\)-value of 0.0068) for the naive constant round win probability
-\(\phi_0 = 0.5\). Thus, I can comfortably reject the constant
+\(\phi_0 = 0.5\). Thus, We can comfortably reject the constant
 probability hypothesis for the null \(\phi_0 = 0.5\), even at a
@@
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for
-the constant round win probability that I find when applying the three
+the constant round win probability that We find when applying the three
 methods suggested by Mosteller (1952). Each is approximately or equal to
 0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a
-\(\chi^2\) value for which I cannot reject the constant probability null
-hypothesis.
+\(\chi^2\) value for which We cannot reject the constant probability
+null hypothesis.
 
@@
   results would be nearly identical to those for the maximum likelihood
-  estimate of \(\phi\) (since they are all \(\approx 0.575\)).} I
+  estimate of \(\phi\) (since they are all \(\approx 0.575\)).} We
 observe that \(\hat{\Phi}_2(r)\) is larger than \(\hat{\Phi}_0(r)\) for
@@
 Given that people typically perceive streaks as beginning after the
-third success (or failure) at minimum (Carlson and Shu 2007), I focus on
-streaks of three round wins.\footnote{Three happens to also be a
+third success (or failure) at minimum (Carlson and Shu 2007), We focus
+on streaks of three round wins.\footnote{Three happens to also be a
   reasonable number for series that lasts at maximum 11 rounds.} Table
@@
 outcome (\(r\) rounds and winner) with the notional and MS expected
-proportions, \(\hat{P}^{+|kr}_0\) and \(\hat{P}^{+|kr}_{MS}\)
+proportions, \(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\)
 respectively.
@@
 
-With the exception of \(\hat{P}^{+|kr}_{MS}\) when \(r = 10\) and the
+With the exception of \(\hat{P}^{+|k,r}_{MS}\) when \(r = 10\) and the
 eventual series loser is the team that wins after a streak of three
@@
 When performing the same tests for streaks of two, four, and five, there
-is no case in which I can reject the binomial null hypothesis for the
-expected notional probability \(p^{+|kr}_0\). The null hypothesis can
-only be rejected for the expected MS probability \(p^{+|kr}_{MS}\) when
+is no case in which We can reject the binomial null hypothesis for the
+expected notional probability \(p^{+|k,r}_0\). The null hypothesis can
+only be rejected for the expected MS probability \(p^{+|k,r}_{MS}\) when
 \(k = 5, r = 7\) after applying the BY p-value correction.\footnote{At
@@
 immediately following a streak of \(k\) round wins in a series lasting
-\(r\) rounds, \(\hat{P}{+|kri}_0\), is statistically different than the
-observed \(P^{+|kri}\) in several cases, notably when \(r = i\) for each
-of \(r \in [9, 10, 11]\).\footnote{The null can also be rejected for
-  \(r \in [7, 8]\), although these are not shown, and the sample sizes
-  are smaller.} Interestingly, the observed rate is greater than the
-expected rate in each case where we can reject the null hypothesis,
-whereas the observed rate is less than the expected rate in all other
-cases, as well in a strong majority of cases not shown.
+\(r\) rounds, \(\hat{P}{+|k,r,i}_0\), is statistically different than
+the observed \(P^{+|k,r,i}\) in several cases, notably when \(r = i\)
+for each of \(r \in [9, 10, 11]\).\footnote{The null can also be
+  rejected for \(r \in [7, 8]\), although these are not shown, and the
+  sample sizes are smaller.} Interestingly, the observed rate is greater
+than the expected rate in each case where we can reject the null
+hypothesis, whereas the observed rate is less than the expected rate in
+all other cases, as well in a strong majority of cases not shown.
 
 \begin{longtable}{rrcrrrr}
-\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|kri}$, and proportion of round wins, $P^{+|kri}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|kri} = \frac{r^{+|kri}}{N^{kri}}$).
-Additionally, the notional proportion, $\hat{P}^{+|kri}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|kri}_0$ to the observed proportion $P^{+|kri}$.
+\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r,i}$, and proportion of round wins, $P^{+|k,r,i}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r,i} = \frac{r^{+|k,r,i}}{N^{kri}}$).
+Additionally, the notional proportion, $\hat{P}^{+|k,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k,r,i}_0$ to the observed proportion $P^{+|k,r,i}$.
 Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{kri} > 10$ for brevity.}
@@
 
-For the sake of brevity, I did not delve into win rates and streaks
+For the sake of brevity, We did not delve into win rates and streaks
 split by offensive or defensive role. For example, it would be
@@
 less frequently than such streaks starting with a defensive
-win---\(\tau_O \times (1 - \tau_O)^2 \approx\) 13.0\%---so I would want
+win---\(\tau_O \times (1 - \tau_O)^2 \approx\) 13.0\%---so We would want
 to account for sample size differences.
 
-Further regarding future work, I've reached out to the Twitter user
+Further regarding future work, We've reached out to the Twitter user
 ``R11stats'', who privately tracks in-round player

### 2022-08-21 paper/paper.Rmd
p7 feedback

@@
 
+### Post-streak probability
+
 ```{r}
@@
 
-[^21]: Three happens to also be a reasonable number for series that lasts at maximum 11 rounds.
+[^21]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
 
@@
 \begin{longtable}{rcrrrrr}
-\caption{Given the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r}$, and proportion of round wins, $P^{+|k,r}$, among $N^{kr}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r} = \frac{r^{+|k,r}}{N^{kr}}$).
-Additionally, the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively.}
+\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$).
+Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
 \label{tbl:cod-pw3r-pl3r} \\
@@
 \toprule
-$r$ & \text{Win series?} & $r^{+|k,r}$ & $N^{kr}$ & $P^{+|k,r}$ & $\hat{P}^{+|k,r}_0$ & $\hat{P}^{+|k,r}_{MS}$ \\ 
+$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=3k,r}_{MS}$ \\ 
 \midrule
@@
 \begin{longtable}{rrcrrrr}
-\caption{Given the round $i$, the round win streak $k$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k,r,i}$, and proportion of round wins, $P^{+|k,r,i}$, among $N^{kri}$ instances where a team could win after the streak $k=3$ ($P^{+|k,r,i} = \frac{r^{+|k,r,i}}{N^{kri}}$).
-Additionally, the notional proportion, $\hat{P}^{+|k,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k,r,i}_0$ to the observed proportion $P^{+|k,r,i}$.
-Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{kri} > 10$ for brevity.}
+\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak ($P^{+|k=3,r,i} = \frac{r^{+|k=3,r,i}}{N^{k=3,r,i}}$).
+Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k=3,r,i}_0$ to the observed proportion $P^{+|k=3,r,i}$.
+Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{k=3,r,i} \geq 10$ for brevity.}
 \label{tbl:cod-pw3ri-pl3ri} \\
 \toprule
-$r$ & $i$ & \text{Win series?} & $r^{+|k,r,i}$ & $N^{kri}$ & $P^{+|k,r,i}$ & $\hat{P}^{+|k,r,i}_0$\\ 
+$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
 \midrule
@@
 ```
+
+### Wald-Wolfowitz runs test
 
@@
 
-For the sake of brevity, We did not delve into win rates and streaks split by offensive or defensive role.
+For the sake of brevity, we did not delve into win rates and streaks split by offensive or defensive role.
 For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak winning as the offensive team.
@@
 
-# Acknowledgements {.unnumbered}
-
-Thank our brother Andrew for giving me feedback on drafts of this paper.
+Other talking points
+
+-   We probably should have expected no hot hand effect given the small "skill gap" in the CoD relative to other esports (andecdotal, but most professional esports player, including CoD players themselves, would say this).
 

### 2022-08-21 paper/paper.tex
p7 feedback

@@
 
+\hypertarget{post-streak-probability}{%
+\subsubsection{Post-streak probability}\label{post-streak-probability}}
+
 Given that people typically perceive streaks as beginning after the
@@
 on streaks of three round wins.\footnote{Three happens to also be a
-  reasonable number for series that lasts at maximum 11 rounds.} Table
+  reasonable number for series that last at maximum 11 rounds.} Table
 \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate
@@
 \end{longtable}
+
+\hypertarget{wald-wolfowitz-runs-test-1}{%
+\subsubsection{Wald-Wolfowitz runs
+test}\label{wald-wolfowitz-runs-test-1}}
 
@@
 
-For the sake of brevity, We did not delve into win rates and streaks
+For the sake of brevity, we did not delve into win rates and streaks
 split by offensive or defensive role. For example, it would be
@@
 
-\hypertarget{acknowledgements}{%
-\section*{Acknowledgements}\label{acknowledgements}}
-\addcontentsline{toc}{section}{Acknowledgements}
+Other talking points
 
-Thank our brother Andrew for giving me feedback on drafts of this paper.
+\begin{itemize}
+\tightlist
+\item
+  We probably should have expected no hot hand effect given the small
+  ``skill gap'' in the CoD relative to other esports (andecdotal, but
+  most professional esports player, including CoD players themselves,
+  would say this).
+\end{itemize}
 

### 2022-08-22 paper/paper.Rmd
one big self review

@@
 ---
-title: "The Hot Hand in Call of Duty Search and Destroy"
+title: "The Hot Hand Fallacy in Call of Duty"
 authors:
@@
   Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).
-First, we find evidence supprting the hypothesis that round win probability can be modeled as a constant across the series, although not at the naive 50%.
+First, we find evidence suppOrting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%.
 Second, we examine post-streak round win probability, given the series outcome.
-We find no evidence that post-streak win rate is significantly different than expected for combinations of streak length, series length, and series winner, suggesting that the perception of momentum at the team level is just that, perception.
+Given streak length, series length, and series winner, we find no evidence that post-streak win rate is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving.
+Wald-Wolfowitz run tests also fail to provide evidence for the hot hand phenomenon.
 bibliography: references.bib
@@
 Call of Duty (CoD), first released in 2003, is one of the most popular first-person shooter (FPS) video game franchises of all-time.
-The most popular mode in the competitive scene is "Search and Destroy" (SnD).[^1] SnD is a one-sided game mode in which one team, the offensive side, tries to destroy one of two designated bomb sites on the map.
+The most popular mode in the competitive scene is "Search and Destroy" (SnD), in which one team tries to destroy one of two designated bomb sites on the map, defended by the opposing team.[^1]
 
@@
 
-In professional CoD SnD, the two teams take turns playing offense and defense every round. They must win six rounds to win the series.[^2] A round can end in one of five ways:
-
-[^2]: A maximum of 11 even rounds can be played. There is no "sudden death" or "win by two" rule like there are for SnD equivalent in professional Counter-Strike and Valorant matches.
+In professional CoD SnD, the two teams[^2] take turns playing offense and defense every round.
+The first to six round wins (best-of-11 format) is declared the series winner.[^3] A round can end in one of four ways:
+
+[^2]: In the 2020 season, teams played with five players each; in the 2021 and 2022 seasons, teams played with four players each.
+
+[^3]: Each round has a two-minute time limit, not counting the potential extension granted if a bomb is planted.
 
 1.  One team eliminates all members of the other team prior to a bomb plant. (Eliminating team wins.)
-2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^3] (Offense wins.)
-3.  The defensive team defuses the bomb after a bomb plant.[^4] (Defense wins.)
-4.  The offensive team does not make a plant by the time the round timer ends. (Defense wins.)
-
-[^3]:
+2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^4] (Offense wins.)
+3.  The defense defuses the bomb after a bomb plant.[^5] (Defense wins.)
+4.  The offense does not make a plant by the time the round timer ends. (Defense wins.)
+
+[^4]:
     -   The bomb can be picked up by any member of the offensive team.
-    -   The bomb carrier is not obstructed at all by carrying the bomb (i.e. movement is the same, weapon usage is the same).
+    -   The bomb carrier is not obstructed by carrying the bomb (i.e. movement is the same, weapon usage is the same, etc.).
     -   The defense does not get any visual indication for who is carrying the bomb.
@@
     -   A bomb defuse takes seven seconds. The timer resets if the player "drops" the bomb.
-    -   The bomb takes 45 seconds to defuse after being planted.
-
-[^4]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
-
-We adopt the terminology "series" to refer to what CoD SnD players typically call a "match", so as to emulate the terminology of playoff series in professional leagues like the National Basketball Association, National Hockey League, and Major League Baseball.
-A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD.
-Further, it is analogous to a trial in statistical analysis of Bernoulli events.
+    -   Once the bomb is planted, the round timer is reset to 45 seconds.
+
+[^5]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+
+We adopt the terminology "series" to refer to a single best-of-11 matchup, so as to mirror the terminology of playoff series in professional leagues like the National Basketball Association (NBA), National Hockey League (NHL), and Major League Baseball (MLB).
+A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD for the purposes of this paper.[^6]
+
+[^6]: Further, these are analogous to a trial in statistical analysis of Bernoulli events.
 
 SnD is not the only game type played in competitive CoD.
-Teams play in a head-to-head, best-of-five (first-to-three wins) format, where SnD is always played as the second and fifth game mode (if a fifth variant is needed).
-The best-of-five across game types could also be called a "series", but since we analyze only the SnD game types, we refer to SnD games as series (of rounds).
-
-Anecdotally, most observers swear by the existence of momentum in CoD SnD series, to the extent that vernacular has been developed to describe such phenomenon.
-People say that teams "ice up" when the team wins several consecutive rounds to come back to win a series, often culminating with a series-clinching round win.[^5] Further, viewers have come to embrace the "5-3" phenomenon, where teams win three consecutive rounds after facing a 5-3 deficit to win 6-5.
-There is even a term for the rare 0-5 comeback---a "full sail".
-
-[^5]: This vernacular is not specific to CoD SnD in specific, and is not only used in the contexts of streaks.
+Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game "maps", as most players refer to them (if a fifth map is needed).
+The best-of-five matchup could also be called a "series", but since we analyze only the SnD game types, we refer to SnD games as series.
 
@@
 CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), operating since 2020.
-The CDL has completed three year-long "seasons" as of August 2022.[^6]
-
-[^6]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle (released coming in the late fall), where a new game is published every year under the same title.
+The CDL has completed three year-long "seasons" as of August 2022.[^7]
+
+[^7]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, with releases coming in the late fall.
+A new game under the same brand---Call of Duty---is published every year by a rotating set of developers.
 Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
@@
 
-The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^7] Data was collected in spreadsheets by community member "IOUTurtle".[^8]
-
-[^7]: 288 of the series occur in major tournaments, which are considered to be more "competitive" than the qualifiers since they are played in person (COVID-permitting), whereas the qualifiers are played online.
-
-[^8]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Processed data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
-
-The observed offensive round win percentage across all rounds is $\tau_O$ = 47.8%.[^9] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^8] Data has been collected in spreadsheets by community member "IOUTurtle".[^9]
+
+[^8]: 288 of the series occur in major tournaments, which are considered to be more "competitive" than the qualifiers since they are played in person (COVID-permitting), whereas the qualifiers are played online.
+
+[^9]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Processed data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
+
+6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7% of series.
+The observed offensive round win percentage across all rounds is $\tau_O$ = 47.8%.[^10] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
-Offensive round win rate is not quite constant, although never veers more than 10% from this overall average.
-
-[^9]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
+Offensive round win rate is not quite constant, although never veers more than 10% from $\tau_O$.
+
+[^10]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
 
@@
 ```
-On the extremes, 6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7 of series.
-
-At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series played as the second game or the fifth game, and their opponent is assigned to play offense in the first round of the SnD slot not chosen.[^10][^11] [@codrules] With online qualifiers, teams all play each other twice throughout the season.
-Each team gets to play the higher-seeded role once in their matchups, despite their win-loss records.
-Overall, we might say that bias due to stronger teams playing defense (slightly advantageous) more often is very minimal.
-
-[^10]: "Hardpoint" has been played as the first and fourth games in a matchup; the variant for the third game was Domination in the 2020 season, and Control in the 2021 and 2022 seasons.
-
-[^11]: Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game, although this choice is not consistent across teams, or with the same team over time.
+At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series played as the second or fifth map, and their opponent is assigned to start on offense in the SnD map not chosen.[^11][^12] Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers.
+Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team, despite their win-loss records.
+Overall, we can argue that potential bias due to stronger teams playing defense---or, if offense, if offense happens to be generally advantageous for a given map---is very minimal.
+
+[^11]: Hardpoint has been played as the first and fourth maps in a matchup. The variant for the third map was Domination in the 2020 season, and Control in the 2021 and 2022 seasons.
+
+[^12]: Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game, although this choice is not consistent across teams, or with the same team over time.
 
@@
 Most assume a constant probability $\phi$ of a given team winning a game in the series, regardless of the series state.
-Mosteller [-@mosteller1952] observed that the American League had dominated the National League in Major League Baseball's (MLB) World Series matchups, implying that games should not be modeled with a constant (null) $\phi_0 = 0.5$.
+Mosteller [-@mosteller1952] observed that the American League had dominated the National League in MLB World Series matchups through 1952, implying that games should not be modeled with a constant (i.e.
+the null) $\phi_0 = 0.5$.
 Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\phi \approx 0.65$ in each case: (1) solving for $\phi$ from the observed average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
-maximum likelihood), and (3) minimizing the chi-square goodness of fit statistic $\chi^2$ for $\phi$.
-
-Chance [-@chance2020] re-examines the constant probability notion in Major League Baseball's (MLB) World Series (1923--2018), the National Basketball Association's (NBA) Finals (1951--2018), and the National Hockey League's (NHL) Stanley Cup (1939--2018).
-Chance finds strong evidence against the null hypothesis of $\phi_0 = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.
-Chance goes on to outline a conditional probability framework (likelihood of winning a game given the series state) which can exactly explain the distribution of the number of games played.
-
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^12] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
+maximum likelihood), and (3) minimizing the chi-squared goodness of fit statistic $\chi^2$ as a function of $\phi$.
+
+Chance [-@chance2020] re-examines the constant probability notion in the MLB World Series (1923--2018), the NBA Finals (1951--2018), and the NHL Stanley Cup (1939--2018).
+Chance found strong evidence against the null hypothesis of $\phi_0 = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.
+
+Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^13] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^12]: We often use use "streaks" and momentum interchangeably, but as [@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^13]: We often use "streaks" and momentum interchangeably, but as Steeger et al. ([-@steeger2021]) note, momentum implies dependence between events, whereas streaking does not.
 
@@
 Gilovich et al.
-[-@gilovich1985], henceforth GVT, do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo [-@miller2018], henceforth MS, provide a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy.
+[-@gilovich1985], henceforth GVT, ido not find evidence for the hot hand phenomenon.
+However, Miller and Sanjurjo [-@miller2018], henceforth MS, provided a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy.
 Specifically, MS say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
 conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success".
-When applying streak selection bias to GVT's data, MS come to the opposite conclusions as GVT.
-
-Other research has borrowed a common approach from the field of quality control, looking at unlikely sequences of events with the Wald-Wolfowitz runs test [@peel2015], [@steeger2021].
-Peel and Clauset find no evidence for unlikely sequences of scoring events in the NHL, College Football (CFB), and National Football League (NFL), but do in the NBA.
+When applying streak selection bias to GVT's data, MS came to the opposite conclusions as GVT.
+
+Other research has borrowed a common approach from the field of quality control, looking at unlikely sequences of events with the Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.
+2021).
+Peel and Clauset found no evidence for unlikely sequences of scoring events in the NHL, College Football (CFB), and National Football League (NFL), but did in the NBA.
 As a check on their entropy approach to momentum identification, Steeger et al.
-found three NHL teams who sequence of wins in the 2018-2019 regular season violated the Wald-Wolfowitz null hypothesis, although these teams did not match the teams identified with their primary approach.
+found several NHL teams with sequence of wins in the 2018-2019 regular season violating the Wald-Wolfowitz null hypothesis.
 
@@
 Work has been done to examine intra-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
-However, considering Counter-Strike and Valorant specifically, research on round-level trends seems non-existant, perhaps for one of many reasons:
+However, considering Counter-Strike and Valorant specifically, research on round-level trends seems non-existent, perhaps for one of several reasons:
 
 1.
-Both have economic aspects that can create clear advantages for one side in a given round, given how prior rounds played out.
-CoD has no such equivalent, except for perhaps "kill streaks", which infrequently play a role.
+Both have economic aspects that can create clear advantages for one team in a round, given how prior rounds played out.
+CoD has no such equivalent, except for perhaps "kill streaks", which infrequently occur.
 2.
 Teams play either offense or defense for many consecutive rounds.
-(The former has a 14-14-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^13] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+(The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^14] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
 Bernoulli trials.
@@
 
-[^13]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each league.
-
-To our knowledge, there is no existing public statistical research on CoD SnD format, beyond descriptive analysis on social media.
-While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation on a common concept like the hot-hand phenomenon in a new field---particularly one that is less subjected to factors that may be difficult to control for, e.g.
+[^14]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each league.
+
+To our knowledge, there is no existing public statistical research on the CoD SnD format, beyond descriptive analysis on social media.
+While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation of a concept like the hot-hand fallacy in a different sport---particularly one that is less subjected to factors that may be difficult to control for, e.g.
 weather---should be useful as a precedent or supplement for future researchers.
@@
 
-In a best-of-$s$ format, assuming a constant round win probability $\phi$ ($0 \leq \phi \leq 1$) for one team[^14], the probability that a series ends in $r$ rounds ($r \leq s$), $\hat{\Phi}(r)$ is
-
-[^14]: If $\phi > 0.5$, we can say that this is the stronger team.
-
-```{=tex}
-\begin{equation}\label{eq:m}
-m = \frac{s + 1}{2}
-\end{equation}
-```
-```{=tex}
-\begin{equation}\label{eq:series-length}
-\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
-\end{equation}
-```
-$s = 11$ rounds for CoD SnD.[^15] For example, assuming $\phi = 0.5$, the probability of a series ending in 9 rounds in CoD is
-
-[^15]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
+In a best-of-$s$ format, assuming a constant round win probability $\phi$[^15] (where $0 \leq \phi \leq 1$) for one team[^16], the expected proportion of series ending in $r$ rounds ($r \leq s$) is given by Equation \ref{eq:series-length}.
+
+[^15]: If $\phi > 0.5$, we can say that this is the stronger team.
+
+[^16]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
 Upper-case symbol, e.g.
-$\Phi$, are consistently used in this paper to represent proportions, while lower-case symbols are used to represent Bernoulli trials success probability.
+$\Phi$, are consistently used in this paper to represent proportions, while lower-case symbols corresponding to upper-case symbols, e.g.
+$\phi$, are used to represent Bernoulli trial success rates.
 "Hats", e.g.
 $\hat{\Phi}$, are used to convey expectations, while bare symbols symbols convey observational data.
+
+```{=tex}
+\begin{equation}\label{eq:m}
+m = \frac{s + 1}{2}.
+\end{equation}
+```
+```{=tex}
+\begin{equation}\label{eq:series-length}
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m).
+\end{equation}
+```
+For example, assuming $\phi = 0.5$, the probability of a series ending in nine rounds in CoD SnD, where $s=11$, is
 
@@
 \begin{equation}\label{eq:chi-squ}
-\chi^2 = \sum^{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}.
+\chi^2 = \sum^{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
 \end{equation}
@@
 p_0(\text{win} | r) = p^{+|r}_0 = \begin{cases} 
-\frac{m}{r} & \text{team wins series} \\ 
-\frac{r - m}{r} & \text{team loses series}  
+\frac{m}{r} & \text{team wins series}, \\ 
+\frac{r - m}{r} & \text{team loses series},
 \end{cases}
@@
 
-As shown by MS with their Theorem 1, we should expect the proportion of rounds wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.[^16] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|k,r}_{MS}$ for $k > 1$.
-Nonetheless, one may recursively build a collection of dictionaries to compute the expectation analytically, or, more conveniently, one may run simulations to estimate the expected value, as We choose to do.[^17]
-
-[^16]: See Appendix E.1 of MS for the proof.
-
-[^17]: We have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
-
-Although it would be convenient to emulate the hypothesis testing for difference of proportions performed by MS (and GVT), our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^18] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
+As shown by MS with their Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.[^17] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|k,r}_{MS}$ for $k > 1$.
+Nonetheless, one may run simulations to estimate the expected value, as we choose to do.[^18]
+
+[^17]: See Appendix E.1 of MS for the proof.
+
+[^18]: We have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+Although one might be tempted to mirror the hypothesis testing for difference of proportions performed by MS (and GVT), our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^19] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
 The Bernoulli trial success probability, i.e.
-a round win in CoD SnD, is not independent of the opponent.
-Consequently, a statistical test of the difference in $\hat{P}^{+|k,r}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rates, is not completely appropriate, although useful as a reference.
-
-[^18]: GVT also performs statistical tests on shots from players in live games, i.e.
+the single round win rate in CoD SnD, is not independent of the opponent.
+Consequently, a statistical test of the difference in $\hat{P}^{+|k,r}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rate, is not completely appropriate, although useful as a reference.
+
+[^19]: GVT also perform statistical tests on shots from players in live games, i.e.
 "observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
@@
 p_0(\text{win} | k, r) = p^{+|k,r}_0 = \begin{cases}
-\frac{m - k}{r - k} & \text{team wins series} \\
-\frac{s - m - k}{r - k} & \text{team loses series}
+\frac{m - k}{r - k} & \text{team wins series}, \\
+\frac{s - m - k}{r - k} & \text{team loses series},
 \end{cases}
@@
 
-We can perform a binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$, where $0 \leq \omega_0 \leq 1$.[^19] If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
-
-[^19]: $\omega$ and other symbols are chosen so as to not conflict with symbols already used elsewhere for in other equations, either generic or for CoD SnD specifically.
+We can perform a binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$ (where $0 \leq \omega_0 \leq 1$).
+If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
 
@@
 ```
-Treating the notional proportion $p^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
+Treating the notional proportion $\hat{P}^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
 If we can reject this null hypothesis, then we can consider team momentum, represented by post-streak success, plausible.
 
-One can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|k,r}_{MS}$. FOOTY: Given the caveats mentioned before, the results should be heeded with caution.
-
-We can further decompose Equation \ref{eq:pwkr} by the round $i$ ($i \leq r$) in which the streak of length $k$ carries into.
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:pwkri}{}{
-p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 =\{
-\begin{array}{cl}
-\frac{m - k}{r - k}, & \text{team wins series}, i \neq r \\
-1, & \text{team wins series}, i = r \\
-\frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r \\
-0, & \text{team loses series}, i = r
-\end{array}
-}
-\label{eq:pwkri}
+One can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|k,r}_{MS}$.[^20]
+
+[^20]: Given the caveats mentioned before, these results should be heeded with caution.
+
+We can further decompose Equation \ref{eq:pwkr} by the round $i$ (where $i \leq r$) in which the streak of length $k$ carries into.
+
+```{=tex}
+\begin{equation}\label{eq:pwkri}
+p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
+\frac{m - k}{r - k}, & \text{team wins series}, i \neq r, \\
+1, & \text{team wins series}, i = r, \\
+\frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r, \\
+0, & \text{team loses series}, i = r.
+\end{cases}
 \end{equation}
 ```
-Again, one might apply a binomial test to evaluate the hypothesis that the expected proportions, both $\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$, are equal to the observed proportion $P^{+|k,r}$.
+Again, we caapply a binomial test to evaluate the hypothesis that the expected proportions, $\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately, are equal to the observed proportion $P^{+|k,r}$.
 
@@
 
-Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with the Wald-Wolfowitz runs test.
+Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with a Wald-Wolfowitz runs test.
 Under the null hypothesis, the number of runs in a sequence of $r$ trials, $\zeta(r)$, is a random variable that can take on values $r^+$ and $r^-$ for success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$.
@@
 ```{=tex}
-\begin{equation}\protect\hypertarget{eq:ww}{}{
+\begin{equation}\label{eq:ww}
 \mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
-}\label{eq:ww}\end{equation}
+\end{equation}
 ```
@@
 
-One can subset the observed series sequences to those that violate the run test null hypothesis and perform a test of proportions, where the null is that the observed rate $\psi^+$ of such series is equal to the frequency rate $\psi_0$.
-The test statistic $Z$
-
-```{=tex}
-\begin{equation}\protect\hypertarget{eq:prop}{}{
-Z = \frac{\psi^+ - \psi^+_0}{\sqrt{\psi^+_d (1 - \psi^+_d) ( \frac{1}{N^+} + \frac{1}{\hat{N}^+})}}
-}\label{eq:prop}\end{equation}
-```
-where $\psi^+_d = \frac{r^+ - \hat{r}^+}{N^+ - \hat{N}^+}$. If we can reject the null hypothesis for many sequences, then there is implicit evidence in favor of the hot hand.
+One can subset the observed series sequences to those that violate the null hypothesis for the run test and perform a test of equal proportions, where the null is that the observed rate of a sequence, $\psi$, is equal to the expected rate of the sequence, $\hat{psi}$.
+The test statistic is
+
+```{=tex}
+\begin{equation}\label{eq:prop}
+Z = \frac{\hat{\psi} - \psi}{\sqrt{\psi_d (1 - \psi_d) ( \frac{1}{\hat{N}} + \frac{1}{N})}}
+\end{equation}
+```
+where $N$ is the observed number of sequences, $\hat{N}$ is the expected number, and $\psi_d = \frac{\psi - \hat{psi}}{N - \hat{N}}$.
+If we can reject the null hypothesis for such sequences, then there is implicit evidence in favor of the hot hand.
 
@@
 
-First, We investigate the constant probability assumption and the distribution of rounds played in a series.
-Chance's [-@chance2020] work is closely related to mine, and, in fact, provides a guide for this investigation.
-Afterwards, We investigate post-streak win rates within the context of momentum.
+First, we investigate the constant probability assumption and the distribution of rounds played in a series.
+Chance's [-@chance2020] work is closely related to our, and, in fact, provides a guide for this investigation.
+Afterwards, We investigate post-streak win rates, referring to work from MS.
+We finish with a brief look at sequences of round wins violating the Wald-Wolfowitz runs test, and whether such observed sequences occur more frequently than expected.
 
@@
 
-Using Equation \ref{eq:chi-squ}, We find that $\chi^2 = 16.0$ ($p$-value of 0.0068) for the naive constant round win probability $\phi_0 = 0.5$.
-Thus, We can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
+Using Equation \ref{eq:chi-squ}, we find that $\chi^2 = 16.0$ ($p$-value of 0.0068) for $\phi_0 = 0.5$.
+Thus, we can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
 
@@
 
-Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected series lasting $r$ rounds, $\hat{\Phi}_0(r)$ (under the assumption $\phi_0 = 0.5$), for $s = 11$, along with the observed proportions, $\Phi(r)$, in CoD SnD.
+Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.
 
@@
 \begin{longtable}{rrrr}
-\caption{The expected proportion of series lasting $r$ rounds ($\hat{\Phi}_0(r)$) in a best-of-11 format, where $r \in R = [6, 7, 8, 9, 10, 11]$ under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-The observed frequencies for CoD SnD are shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
+\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
+Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
 \toprule
@@
 
-Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that We find when applying the three methods suggested by Mosteller [-@mosteller1952].
-Each is approximately or equal to 0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which We cannot reject the constant probability null hypothesis.
-
-```{=tex}
-\begin{longtable}[]{@{}lrr@{}}
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that we find when applying the three methods suggested by Mosteller [-@mosteller1952].
+Each is approximately equal to 0.575.
+When applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which we cannot reject the constant probability null hypothesis.
+
+```{=tex}
+\begin{longtable}{lrr}
 \caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
-\toprule()
-Method & $\phi$ & $\chi^2$ (p-value) \\
-\midrule()
-\endfirsthead
-\toprule()
-Method & $\phi(r)$ & $\chi^2$ (p-value) \\
-\midrule()
-\endhead
+\toprule
+Method & $\phi$ & $\chi^2$ ($p$-value) \\
+\midrule
 0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
@@
 3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
-\bottomrule()
+\bottomrule
 \end{longtable}
 ```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^20] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^21] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^20]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
-
-```{=tex}
-\begin{longtable}[]{@{}rrrr@{}}
-\caption{The observed proportion of series $\Phi(r)$ ending in $r$ rounds in CoD SnD's best-of-11 format, compared to the expected proportion $\hat{\Phi}_0(r)$ the naive assumption $\phi_0 = 0.5$ and the expected proportion $\hat{\Phi}_2(r)$ under the maximum likelihood estimate $\phi_2 = 0.575$ for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
+[^21]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+
+```{=tex}
+\begin{longtable}{rrrr}
+\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
@@
 ```
-Observing that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (especially in comparison to $\hat{\Phi}_0(r)$), along with the null hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results}, it is fair to conclude that the constant round win probability assumption can be valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
+Observing that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (especially in comparison to $\hat{\Phi}_0(r)$), along with the null hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results}, we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], We focus on streaks of three round wins.[^21] Table \ref{tbl:cod-pw3r-pl3r} compares the observed round win rate $P^{w,kr}$ following streaks of $k=3$ round wins given the series outcome ($r$ rounds and winner) with the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively.
-
-[^21]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^22] Table \ref{tbl:cod-pw3r-pl3r} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win rate, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
+
+[^22]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
 
@@
 \toprule
-$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=3k,r}_{MS}$ \\ 
+$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=k=3,r}_{MS}$ \\ 
 \midrule
@@
 ```
-With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins[^22], all un-adjusted binomial test $p$-values are greater than the typical $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
-Adjusting the $p$-values with the Benjamini & Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^23]
-
-[^22]: This implies that the opponent, the eventual series winner, goes on to win the series 6-4 after going down 0-4.
-This is the only scenario in which one team wins four rounds consecutively but loses a best-of-11 series in 10 rounds.
+With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
+However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^23]
 
@@
 
-When performing the same tests for streaks of two, four, and five, there is no case in which We can reject the binomial null hypothesis for the expected notional probability $p^{+|k,r}_0$.
-The null hypothesis can only be rejected for the expected MS probability $p^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^24]
-
-[^24]: At 36, the sample size for \$k = 5, r = 7\$ is not as large as most other combinations of \$k\$ and \$r\$.
+When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the binomial null hypothesis for the expected notional proportion $\hat{P}^{+|k,r}_0$ (even before the BY p-value correction).
+The null hypothesis can only be rejected for the expected MS proportion $\hat{P}^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^24]
+
+[^24]: At 36, the sample size for $k = 5, r = 7$ is not as large as most other combinations of $k$ and $r$.
 
@@
 \begin{longtable}{rrcrrrr}
-\caption{Given the round $i$, the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak ($P^{+|k=3,r,i} = \frac{r^{+|k=3,r,i}}{N^{k=3,r,i}}$).
-Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$, and the $p$-value of a binomial test comparing $\hat{P}^{+|k=3,r,i}_0$ to the observed proportion $P^{+|k=3,r,i}$.
-Table restricted to $r \in [10, 11]$ and $i < r$ and $N^{k=3,r,i} \geq 10$ for brevity.}
+\caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak.
+Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$.
+Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$ for brevity.}
 \label{tbl:cod-pw3ri-pl3ri} \\
@@
 In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
-(In addition to these 13, there are 12 additional sequences for $r = 11$.) The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$.
-A test for difference between the actual and expected proportions of all sequences indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.
+In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.
 
@@
 
-\caption{Given the length of the series ($r$ rounds), the sequence of round wins by the series winner $^\zeta(r)$, where round wins $r^w$ and losses $r^-$ are indicated by 1 and 0 respectively, among sequences that reject the Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$.
+\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins $r^+$ and losses $r^-$ are denoted by $+$ and $-$ respectively.
 The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$.
@@
 \midrule
-8 & 0-0-1-1-1-1-1-1 & 4 & 0.47\% & 7.67 & 0.90\% \\ 
-9 & 0-0-0-1-1-1-1-1-1 & 4 & 0.47\% & 3.75 & 0.44\% \\ 
-10 & 1-1-1-1-0-0-0-0-1-1 & 1 & 0.12\% & 2.39 & 0.28\% \\ 
-10 & 1-0-0-0-0-1-1-1-1-1 & 0 & 0.00\% & 2.04 & 0.24\% \\ 
-10 & 1-0-1-0-1-1-0-1-0-1 & 3 & 0.35\% & 2.04 & 0.24\% \\ 
-10 & 1-1-1-0-0-0-0-1-1-1 & 2 & 0.23\% & 2.04 & 0.24\% \\ 
-10 & 0-0-0-0-1-1-1-1-1-1 & 2 & 0.23\% & 1.79 & 0.21\% \\ 
-10 & 1-0-1-0-1-0-1-1-0-1 & 3 & 0.35\% & 1.70 & 0.20\% \\ 
-10 & 1-0-1-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.70 & 0.20\% \\ 
-10 & 1-1-0-0-0-0-1-1-1-1 & 1 & 0.12\% & 1.19 & 0.14\% \\ 
-10 & 1-0-1-0-1-0-1-0-1-1 & 3 & 0.35\% & 1.11 & 0.13\% \\ 
-10 & 1-1-0-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.11 & 0.13\% \\ 
-10 & 1-1-1-1-1-0-0-0-0-1 & 2 & 0.23\% & 1.02 & 0.12\% \\ 
+8 & --++++++ & 4 & 0.47\% & 7.67 & 0.90\% \\ 
+9 & ---++++++ & 4 & 0.47\% & 3.75 & 0.44\% \\ 
+10 & ++++----++ & 1 & 0.12\% & 2.39 & 0.28\% \\ 
+10 & +----+++++ & 0 & 0.00\% & 2.04 & 0.24\% \\ 
+10 & +-+-++-+-+ & 3 & 0.35\% & 2.04 & 0.24\% \\ 
+10 & +++----+++ & 2 & 0.23\% & 2.04 & 0.24\% \\ 
+10 & ----++++++ & 2 & 0.23\% & 1.79 & 0.21\% \\ 
+10 & +-+-+-++-+ & 3 & 0.35\% & 1.70 & 0.20\% \\ 
+10 & +-++-+-+-+ & 0 & 0.00\% & 1.70 & 0.20\% \\ 
+10 & ++----++++ & 1 & 0.12\% & 1.19 & 0.14\% \\ 
+10 & +-+-+-+-++ & 3 & 0.35\% & 1.11 & 0.13\% \\ 
+10 & ++-+-+-+-+ & 0 & 0.00\% & 1.11 & 0.13\% \\ 
+10 & +++++----+ & 2 & 0.23\% & 1.02 & 0.12\% \\ 
 \bottomrule
@@
 ```
+The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$.
+A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta r}$ and $\hat{P}^{\zeta r}$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.
+
 # Discussion
 
+Anecdotally, most observers swear by the existence of momentum in CoD SnD series, to the extent that vernacular has been developed to describe such phenomenon.
+Viewers have come to embrace the "5-3" phenomenon, where teams win three consecutive rounds after facing a 5-3 deficit to win 6-5.
+There is even a term for the rare 0-5 comeback---a "full sail".
+
+However, our results do not provide evidence for momentum on several fronts: (1) the evidence supporting the constant round probability; (2) the failure to reject the binomial null hypothesis for post-streak win rates; and (3) the failure to reject the equal proportions null hypothesis for streaky round sequences identified by the Wald-Wolfowitz runs test.
+
+Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in the CoD relative to other esports.
+(Most professional esports players who have played CoD, including CoD players themselves, would not hesitate to state this.) A small skill gap fosters randomness in outcomes, implying that a given team is less likely to enjoy streaks of success in SnD.
+
 For the sake of brevity, we did not delve into win rates and streaks split by offensive or defensive role.
-For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak winning as the offensive team.
-This would mean that, in the round immediately following the streak, the streaking team would be playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round win---theoretically, given $\tau_O$ = 47.7% the expected frequency is $\tau_O^2 \times (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O \times (1 - \tau_O)^2 \approx$ 13.0%---so We would want to account for sample size differences.
-
-Further regarding future work, We've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak as the offensive team.
+This would mean that, in the round immediately following the latest streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average.
+On the other hand, streaks of three starting with an offensive round win---theoretically, knowing that $\tau_O$ = 47.7%, the expected frequency is $\tau_O^2 (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O (1 - \tau_O)^2 \approx$ 13.0%---so we would want to account for sample size differences.
+
+In the future, we could have account for prior team strengths, both in general and on specific maps.
+Even if doing so does not change the results, we could gain additional insight into why we do not observe statistically significant streakiness.
+
+Further regarding future work, we've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
 
@@
 
--   We probably should have expected no hot hand effect given the small "skill gap" in the CoD relative to other esports (andecdotal, but most professional esports player, including CoD players themselves, would say this).
+-
 

### 2022-08-22 paper/paper.tex
one big self review

@@
 
-\title{The Hot Hand in Call of Duty Search and Destroy}
+\title{The Hot Hand Fallacy in Call of Duty}
 
@@
 first-person shooter game Call of Duty (CoD). First, we find evidence
-supprting the hypothesis that round win probability can be modeled as a
-constant across the series, although not at the naive 50\%. Second, we
-examine post-streak round win probability, given the series outcome. We
-find no evidence that post-streak win rate is significantly different
-than expected for combinations of streak length, series length, and
-series winner, suggesting that the perception of momentum at the team
-level is just that, perception.
+suppOrting the hypothesis that round win probability can be modeled as a
+constant across rounds in the series, although not at the naive 50\%.
+Second, we examine post-streak round win probability, given the series
+outcome. Given streak length, series length, and series winner, we find
+no evidence that post-streak win rate is significantly different than
+expected, suggesting that the perception of momentum at the team level
+is deceiving. Wald-Wolfowitz run tests also fail to provide evidence for
+the hot hand phenomenon.
 \end{abstract}
@@
 first-person shooter (FPS) video game franchises of all-time. The most
-popular mode in the competitive scene is ``Search and Destroy''
-(SnD).\footnote{SnD bears resemblance to ``Bomb Defusal'' in
-  Counter-Strike and ``Plant/Defuse'' in Valorant, two other FPS games
-  played in more popular professional leagues.} SnD is a one-sided game
-mode in which one team, the offensive side, tries to destroy one of two
-designated bomb sites on the map.
+popular mode in the competitive scene is ``Search and Destroy'' (SnD),
+in which one team tries to destroy one of two designated bomb sites on
+the map, defended by the opposing team.\footnote{SnD bears resemblance
+  to ``Bomb Defusal'' in Counter-Strike and ``Plant/Defuse'' in
+  Valorant, two other FPS games played in more popular professional
+  leagues.}
 
-In professional CoD SnD, the two teams take turns playing offense and
-defense every round. They must win six rounds to win the
-series.\footnote{A maximum of 11 even rounds can be played. There is no
-  ``sudden death'' or ``win by two'' rule like there are for SnD
-  equivalent in professional Counter-Strike and Valorant matches.} A
-round can end in one of five ways:
+In professional CoD SnD, the two teams\footnote{In the 2020 season,
+  teams played with five players each; in the 2021 and 2022 seasons,
+  teams played with four players each.} take turns playing offense and
+defense every round. The first to six round wins (best-of-11 format) is
+declared the series winner.\footnote{Each round has a two-minute time
+  limit, not counting the potential extension granted if a bomb is
+  planted.} A round can end in one of four ways:
 
@@
     \item
-      The bomb carrier is not obstructed at all by carrying the bomb
-      (i.e.~movement is the same, weapon usage is the same).
+      The bomb carrier is not obstructed by carrying the bomb
+      (i.e.~movement is the same, weapon usage is the same, etc.).
     \item
@@
     \item
-      The bomb takes 45 seconds to defuse after being planted.
+      Once the bomb is planted, the round timer is reset to 45 seconds.
     \end{itemize}} (Offense wins.)
 \item
-  The defensive team defuses the bomb after a bomb plant.\footnote{Often
-    the defensive team will try to eliminate all team members prior to
+  The defense defuses the bomb after a bomb plant.\footnote{Often the
+    defensive team will try to eliminate all team members prior to
     making the defuse, but in some cases, they may try to ``ninja''
@@
 \item
-  The offensive team does not make a plant by the time the round timer
-  ends. (Defense wins.)
+  The offense does not make a plant by the time the round timer ends.
+  (Defense wins.)
 \end{enumerate}
 
-We adopt the terminology ``series'' to refer to what CoD SnD players
-typically call a ``match'', so as to emulate the terminology of playoff
-series in professional leagues like the National Basketball Association,
-National Hockey League, and Major League Baseball. A ``game'' or a
-``match'' in such leagues is analogous to a ``round'' of CoD SnD.
-Further, it is analogous to a trial in statistical analysis of Bernoulli
-events.
+We adopt the terminology ``series'' to refer to a single best-of-11
+matchup, so as to mirror the terminology of playoff series in
+professional leagues like the National Basketball Association (NBA),
+National Hockey League (NHL), and Major League Baseball (MLB). A
+``game'' or a ``match'' in such leagues is analogous to a ``round'' of
+CoD SnD for the purposes of this paper.\footnote{Further, these are
+  analogous to a trial in statistical analysis of Bernoulli events.}
 
 SnD is not the only game type played in competitive CoD. Teams play in a
-head-to-head, best-of-five (first-to-three wins) format, where SnD is
-always played as the second and fifth game mode (if a fifth variant is
-needed). The best-of-five across game types could also be called a
+head-to-head, best-of-five format, where SnD is always played as the
+second and fifth game ``maps'', as most players refer to them (if a
+fifth map is needed). The best-of-five matchup could also be called a
 ``series'', but since we analyze only the SnD game types, we refer to
-SnD games as series (of rounds).
-
-Anecdotally, most observers swear by the existence of momentum in CoD
-SnD series, to the extent that vernacular has been developed to describe
-such phenomenon. People say that teams ``ice up'' when the team wins
-several consecutive rounds to come back to win a series, often
-culminating with a series-clinching round win.\footnote{This vernacular
-  is not specific to CoD SnD in specific, and is not only used in the
-  contexts of streaks.} Further, viewers have come to embrace the
-``5-3'' phenomenon, where teams win three consecutive rounds after
-facing a 5-3 deficit to win 6-5. There is even a term for the rare 0-5
-comeback---a ``full sail''.
+SnD games as series.
 
@@
 ``seasons'' as of August 2022.\footnote{CoD is fairly unique compared to
-  other esports in that it runs on an annual lifecycle (released coming
-  in the late fall), where a new game is published every year under the
-  same title. Each new game bears resemblance to past ones, often
-  introducing relatively small variations (``improvements'') to
-  graphics, game modes, and other facets of gameplay. During the CDL
-  era, the games released have been Modern Warfare (2020), Cold War
-  (2021) and Vanguard (2022).}
+  other esports in that it runs on an annual lifecycle, with releases
+  coming in the late fall. A new game under the same brand---Call of
+  Duty---is published every year by a rotating set of developers. Each
+  new game bears resemblance to past ones, often introducing relatively
+  small variations (``improvements'') to graphics, game modes, and other
+  facets of gameplay. During the CDL era, the games released have been
+  Modern Warfare (2020), Cold War (2021) and Vanguard (2022).}
 
@@
   are played in person (COVID-permitting), whereas the qualifiers are
-  played online.} Data was collected in spreadsheets by community member
-``IOUTurtle''.\footnote{Raw data: \url{https://linktr.ee/CDLArchive}.
-  Author: \url{https://twitter.com/IOUTurtle}. Processed data can be
-  found at
+  played online.} Data has been collected in spreadsheets by community
+member ``IOUTurtle''.\footnote{Raw data:
+  \url{https://linktr.ee/CDLArchive}. Author:
+  \url{https://twitter.com/IOUTurtle}. Processed data can be found at
   \url{https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv}.}
 
-The observed offensive round win percentage across all rounds is
-\(\tau_O\) = 47.8\%.\footnote{Offensive round win percentage has been
+6-0 sweeps make up 4.7\% of all series, while 6-5 series make up 23.7\%
+of series. The observed offensive round win percentage across all rounds
+is \(\tau_O\) = 47.8\%.\footnote{Offensive round win percentage has been
   nearly constant across the three games during the CDL era: 1. 47.2\%
@@
 team prior to an upcoming round). Offensive round win rate is not quite
-constant, although never veers more than 10\% from this overall average.
+constant, although never veers more than 10\% from \(\tau_O\).
 
@@
 
-On the extremes, 6-0 sweeps make up 4.7\% of all series, while 6-5
-series make up 23.7 of series.
-
 At tournaments, higher-seeded (``better'') teams choose whether they
-want to start on offense in the SnD series played as the second game or
-the fifth game, and their opponent is assigned to play offense in the
-first round of the SnD slot not chosen.\footnote{``Hardpoint'' has been
-  played as the first and fourth games in a matchup; the variant for the
-  third game was Domination in the 2020 season, and Control in the 2021
-  and 2022 seasons.}\footnote{Anecdotally, the higher-seeded teams tend
-  to choose to play defense in the first round of the SnD series played
-  as the second game, although this choice is not consistent across
-  teams, or with the same team over time.} ({``Competitive Settings
-\textbar{} Call of Duty League,''} n.d.) With online qualifiers, teams
-all play each other twice throughout the season. Each team gets to play
-the higher-seeded role once in their matchups, despite their win-loss
-records. Overall, we might say that bias due to stronger teams playing
-defense (slightly advantageous) more often is very minimal.
+want to start on offense in the SnD series played as the second or fifth
+map, and their opponent is assigned to start on offense in the SnD map
+not chosen.\footnote{Hardpoint has been played as the first and fourth
+  maps in a matchup. The variant for the third map was Domination in the
+  2020 season, and Control in the 2021 and 2022 seasons.}\footnote{Anecdotally,
+  the higher-seeded teams tend to choose to play defense in the first
+  round of the SnD series played as the second game, although this
+  choice is not consistent across teams, or with the same team over
+  time.} Outside of tournaments, teams all play each other twice
+throughout the season, constituting qualifiers. Each team gets to play
+the higher-seeded role once in their head-to-head matchups with a given
+team, despite their win-loss records. Overall, we can argue that
+potential bias due to stronger teams playing defense---or, if offense,
+if offense happens to be generally advantageous for a given map---is
+very minimal.
 
@@
 series state. Mosteller (1952) observed that the American League had
-dominated the National League in Major League Baseball's (MLB) World
-Series matchups, implying that games should not be modeled with a
-constant (null) \(\phi_0 = 0.5\). Mosteller proposed three approaches
-for identifying the optimal constant probability value of the stronger
-team in the World Series, finding \(\phi \approx 0.65\) in each case:
-(1) solving for \(\phi\) from the observed average number of games won
-by the loser of the series, which he called the ``method of moments''
+dominated the National League in MLB World Series matchups through 1952,
+implying that games should not be modeled with a constant (i.e.~the
+null) \(\phi_0 = 0.5\). Mosteller proposed three approaches for
+identifying the optimal constant probability value of the stronger team
+in the World Series, finding \(\phi \approx 0.65\) in each case: (1)
+solving for \(\phi\) from the observed average number of games won by
+the loser of the series, which he called the ``method of moments''
 approach; (2) maximizing the likelihood that the sample would have been
@@
 game is constant across the series (i.e.~maximum likelihood), and (3)
-minimizing the chi-square goodness of fit statistic \(\chi^2\) for
-\(\phi\).
+minimizing the chi-squared goodness of fit statistic \(\chi^2\) as a
+function of \(\phi\).
 
-Chance (2020) re-examines the constant probability notion in Major
-League Baseball's (MLB) World Series (1923--2018), the National
-Basketball Association's (NBA) Finals (1951--2018), and the National
-Hockey League's (NHL) Stanley Cup (1939--2018). Chance finds strong
-evidence against the null hypothesis of \(\phi_0 = 0.5\) in the MLB and
-NHL championship series when applying Mosteller's first and second
-methods. Chance goes on to outline a conditional probability framework
-(likelihood of winning a game given the series state) which can exactly
-explain the distribution of the number of games played.
+Chance (2020) re-examines the constant probability notion in the MLB
+World Series (1923--2018), the NBA Finals (1951--2018), and the NHL
+Stanley Cup (1939--2018). Chance found strong evidence against the null
+hypothesis of \(\phi_0 = 0.5\) in the MLB and NHL championship series
+when applying Mosteller's first and second methods.
 
@@
 hand-in-hand with a discussion of the nature of series
-outcomes.\footnote{We often use use ``streaks'' and momentum
-  interchangeably, but as (Steeger, Dulin, and Gonzalez 2021) note,
-  momentum implies dependence between events, whereas streaking does
-  not.} Two opposing fallacies are observed in the context of momentum:
-the ``gambler's fallacy'' (negative recency) and the ``hot hand
-fallacy'' (positive recency). Per Ayton et al. (2004), negative recency
-is ``the belief that, for random events, runs of a particular outcome
-\ldots{} will be balanced by a tendency for the opposite outcome'',
-while positive recency is the expectation of observing future results
-that match recent results.
+outcomes.\footnote{We often use ``streaks'' and momentum
+  interchangeably, but as Steeger et al.~((2021)) note, momentum implies
+  dependence between events, whereas streaking does not.} Two opposing
+fallacies are observed in the context of momentum: the ``gambler's
+fallacy'' (negative recency) and the ``hot hand fallacy'' (positive
+recency). Per Ayton et al. (2004), negative recency is ``the belief
+that, for random events, runs of a particular outcome \ldots{} will be
+balanced by a tendency for the opposite outcome'', while positive
+recency is the expectation of observing future results that match recent
+results.
 
@@
 observational and controlled settings. Gilovich et al. (1985),
-henceforth GVT, do not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo (2018), henceforth MS, provide a framework
+henceforth GVT, ido not find evidence for the hot hand phenomenon.
+However, Miller and Sanjurjo (2018), henceforth MS, provided a framework
 for quantifying streak selection bias, which effectively works in the
@@
 (conditional) probability of success''. When applying streak selection
-bias to GVT's data, MS come to the opposite conclusions as GVT.
+bias to GVT's data, MS came to the opposite conclusions as GVT.
 
@@
 control, looking at unlikely sequences of events with the Wald-Wolfowitz
-runs test (Peel and Clauset 2015), (Steeger, Dulin, and Gonzalez 2021).
-Peel and Clauset find no evidence for unlikely sequences of scoring
-events in the NHL, College Football (CFB), and National Football League
-(NFL), but do in the NBA. As a check on their entropy approach to
-momentum identification, Steeger et al.~found three NHL teams who
-sequence of wins in the 2018-2019 regular season violated the
-Wald-Wolfowitz null hypothesis, although these teams did not match the
-teams identified with their primary approach.
+runs test (Peel and Clauset 2015, Steeger et al.~2021). Peel and Clauset
+found no evidence for unlikely sequences of scoring events in the NHL,
+College Football (CFB), and National Football League (NFL), but did in
+the NBA. As a check on their entropy approach to momentum
+identification, Steeger et al.~found several NHL teams with sequence of
+wins in the 2018-2019 regular season violating the Wald-Wolfowitz null
+hypothesis.
 
@@
 Counter-Strike and Valorant specifically, research on round-level trends
-seems non-existant, perhaps for one of many reasons:
+seems non-existent, perhaps for one of several reasons:
 
@@
   Both have economic aspects that can create clear advantages for one
-  side in a given round, given how prior rounds played out. CoD has no
-  such equivalent, except for perhaps ``kill streaks'', which
-  infrequently play a role.
+  team in a round, given how prior rounds played out. CoD has no such
+  equivalent, except for perhaps ``kill streaks'', which infrequently
+  occur.
 \item
   Teams play either offense or defense for many consecutive rounds. (The
-  former has a 14-14-1 format and the latter uses a 12-12-1 format.) On
+  former has a 15-15-1 format and the latter uses a 12-12-1 format.) On
   the other hand, teams in CoD SnD rotate roles every round, analogous
@@
 To our knowledge, there is no existing public statistical research on
-CoD SnD format, beyond descriptive analysis on social media. While
+the CoD SnD format, beyond descriptive analysis on social media. While
 intra-round trends may be more directly applicable to teams looking for
-an advantage on their competition, broader investigation on a common
-concept like the hot-hand phenomenon in a new field---particularly one
-that is less subjected to factors that may be difficult to control for,
+an advantage on their competition, broader investigation of a concept
+like the hot-hand fallacy in a different sport---particularly one that
+is less subjected to factors that may be difficult to control for,
 e.g.~weather---should be useful as a precedent or supplement for future
@@
 In a best-of-\(s\) format, assuming a constant round win probability
-\(\phi\) (\(0 \leq \phi \leq 1\)) for one team\footnote{If
-  \(\phi > 0.5\), we can say that this is the stronger team.}, the
-probability that a series ends in \(r\) rounds (\(r \leq s\)),
-\(\hat{\Phi}(r)\) is
+\(\phi\)\footnote{If \(\phi > 0.5\), we can say that this is the
+  stronger team.} (where \(0 \leq \phi \leq 1\)) for one
+team\footnote{\(\phi\) and other symbols are selected so as to reserve
+  symbols like \(p\) for usage in other contexts without causing
+  confusion for the reader. Upper-case symbol, e.g.~\(\Phi\), are
+  consistently used in this paper to represent proportions, while
+  lower-case symbols corresponding to upper-case symbols, e.g.~\(\phi\),
+  are used to represent Bernoulli trial success rates. ``Hats'',
+  e.g.~\(\hat{\Phi}\), are used to convey expectations, while bare
+  symbols symbols convey observational data.}, the expected proportion
+of series ending in \(r\) rounds (\(r \leq s\)) is given by Equation
+\ref{eq:series-length}.
 
 \begin{equation}\label{eq:m}
-m = \frac{s + 1}{2}
+m = \frac{s + 1}{2}.
 \end{equation}
@@
 \begin{equation}\label{eq:series-length}
-\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m)
+\hat{\Phi}(r) = \frac{(r - 1)!}{(m - 1)!(s - r)!}(\phi^{m}(1 - \phi)^{r - m} + \phi^{r - m}(1 - \phi)^m).
 \end{equation}
 
-\(s = 11\) rounds for CoD SnD.\footnote{\(\phi\) and other symbols are
-  selected so as to reserve symbols like \(p\) for usage in other
-  contexts without causing confusion for the reader. Upper-case symbol,
-  e.g.~\(\Phi\), are consistently used in this paper to represent
-  proportions, while lower-case symbols are used to represent Bernoulli
-  trials success probability. ``Hats'', e.g.~\(\hat{\Phi}\), are used to
-  convey expectations, while bare symbols symbols convey observational
-  data.} For example, assuming \(\phi = 0.5\), the probability of a
-series ending in 9 rounds in CoD is
+For example, assuming \(\phi = 0.5\), the probability of a series ending
+in nine rounds in CoD SnD, where \(s=11\), is
 
@@
 As shown by MS with their Theorem 1, we should expect the proportion of
-rounds wins immediately following a streak of \(k\) rounds wins for a
+round wins immediately following a streak of \(k\) rounds wins for a
 series lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly
@@
 expected value of \(\hat{P}^{+|k,r}_{MS}\) for \(k > 1\). Nonetheless,
-one may recursively build a collection of dictionaries to compute the
-expectation analytically, or, more conveniently, one may run simulations
-to estimate the expected value, as We choose to do.\footnote{We have
-  adapted the code from Vafa (2017), which implements MS's framework
-  (2018).}
+one may run simulations to estimate the expected value, as we choose to
+do.\footnote{We have adapted the code from Vafa (2017), which implements
+  MS's framework (2018).}
 
-Although it would be convenient to emulate the hypothesis testing for
+Although one might be tempted to mirror the hypothesis testing for
 difference of proportions performed by MS (and GVT), our context is
 fundamentally different from that of MS, who focus on longitudinal data
-in controlled settings.\footnote{GVT also performs statistical tests on
+in controlled settings.\footnote{GVT also perform statistical tests on
   shots from players in live games, i.e.~``observational'' data, but
@@
 number of possible rounds (\(s\)) and whether or not the team wins the
-series. The Bernoulli trial success probability, i.e.~a round win in CoD
-SnD, is not independent of the opponent. Consequently, a statistical
-test of the difference in \(\hat{P}^{+|k,r}\) and \(\hat{P}^{-|kr}\), as
-performed by MS to evaluate their hypothesis regarding post-streak
-success rates, is not completely appropriate, although useful as a
-reference.
+series. The Bernoulli trial success probability, i.e.~the single round
+win rate in CoD SnD, is not independent of the opponent. Consequently, a
+statistical test of the difference in \(\hat{P}^{+|k,r}\) and
+\(\hat{P}^{-|kr}\), as performed by MS to evaluate their hypothesis
+regarding post-streak success rate, is not completely appropriate,
+although useful as a reference.
 
@@
 \(\omega = \omega_0\) for the observed probability of success \(\omega\)
-and a user-specified \(\omega_0\), where
-\(0 \leq \omega_0 \leq 1\).\footnote{\(\omega\) and other symbols are
-  chosen so as to not conflict with symbols already used elsewhere for
-  in other equations, either generic or for CoD SnD specifically.} If
+and a user-specified \(\omega_0\) (where \(0 \leq \omega_0 \leq 1\)). If
 there are \(r^+\) observed successes in a sample of \(r\) trials and we
@@
 
-Treating the notional proportion \(p^{+|k,r}_0\) as the null
+Treating the notional proportion \(\hat{P}^{+|k,r}_0\) as the null
 \(\omega_0\) and plugging in the observed proportion \(P^{+|k,r}\) for
@@
 One can perform the same binomial test for the MS's
-streak-selection-adjusted proportion, \(\hat{P}^{+|k,r}_{MS}\). FOOTY:
-Given the caveats mentioned before, the results should be heeded with
-caution.
+streak-selection-adjusted proportion,
+\(\hat{P}^{+|k,r}_{MS}\).\footnote{Given the caveats mentioned before,
+  these results should be heeded with caution.}
 
 We can further decompose Equation \ref{eq:pwkr} by the round \(i\)
-(\(i \leq r\)) in which the streak of length \(k\) carries into.
+(where \(i \leq r\)) in which the streak of length \(k\) carries into.
 
-\begin{equation}\protect\hypertarget{eq:pwkri}{}{
-p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 =\{
-\begin{array}{cl}
-\frac{m - k}{r - k}, & \text{team wins series}, i \neq r \\
-1, & \text{team wins series}, i = r \\
-\frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r \\
-0, & \text{team loses series}, i = r
-\end{array}
-}
-\label{eq:pwkri}
+\begin{equation}\label{eq:pwkri}
+p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
+\frac{m - k}{r - k}, & \text{team wins series}, i \neq r, \\
+1, & \text{team wins series}, i = r, \\
+\frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r, \\
+0, & \text{team loses series}, i = r.
+\end{cases}
 \end{equation}
 
-Again, one might apply a binomial test to evaluate the hypothesis that
-the expected proportions, both \(\hat{P}^{+|k,r,i}_0\) and
-\(\hat{P}^{+|k,r,i}_{MS}\), are equal to the observed proportion
-\(P^{+|k,r}\).
+Again, we caapply a binomial test to evaluate the hypothesis that the
+expected proportions, \(\hat{P}^{+|k,r,i}_0\) and
+\(\hat{P}^{+|k,r,i}_{MS}\) separately, are equal to the observed
+proportion \(P^{+|k,r}\).
 
@@
 win probability when streaking, one can attempt to detect the hot hand
-phenomenon with the Wald-Wolfowitz runs test. Under the null hypothesis,
+phenomenon with a Wald-Wolfowitz runs test. Under the null hypothesis,
 the number of runs in a sequence of \(r\) trials, \(\zeta(r)\), is a
@@
 
-\begin{equation}\protect\hypertarget{eq:ww}{}{
+\begin{equation}\label{eq:ww}
 \mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
-}\label{eq:ww}\end{equation}
+\end{equation}
 
@@
 One can subset the observed series sequences to those that violate the
-run test null hypothesis and perform a test of proportions, where the
-null is that the observed rate \(\psi^+\) of such series is equal to the
-frequency rate \(\psi_0\). The test statistic \(Z\)
+null hypothesis for the run test and perform a test of equal
+proportions, where the null is that the observed rate of a sequence,
+\(\psi\), is equal to the expected rate of the sequence, \(\hat{psi}\).
+The test statistic is
 
-\begin{equation}\protect\hypertarget{eq:prop}{}{
-Z = \frac{\psi^+ - \psi^+_0}{\sqrt{\psi^+_d (1 - \psi^+_d) ( \frac{1}{N^+} + \frac{1}{\hat{N}^+})}}
-}\label{eq:prop}\end{equation}
+\begin{equation}\label{eq:prop}
+Z = \frac{\hat{\psi} - \psi}{\sqrt{\psi_d (1 - \psi_d) ( \frac{1}{\hat{N}} + \frac{1}{N})}}
+\end{equation}
 
-where \(\psi^+_d = \frac{r^+ - \hat{r}^+}{N^+ - \hat{N}^+}\). If we can
-reject the null hypothesis for many sequences, then there is implicit
-evidence in favor of the hot hand.
+where \(N\) is the observed number of sequences, \(\hat{N}\) is the
+expected number, and \(\psi_d = \frac{\psi - \hat{psi}}{N - \hat{N}}\).
+If we can reject the null hypothesis for such sequences, then there is
+implicit evidence in favor of the hot hand.
 
@@
 
-First, We investigate the constant probability assumption and the
+First, we investigate the constant probability assumption and the
 distribution of rounds played in a series. Chance's (2020) work is
-closely related to mine, and, in fact, provides a guide for this
-investigation. Afterwards, We investigate post-streak win rates within
-the context of momentum.
+closely related to our, and, in fact, provides a guide for this
+investigation. Afterwards, We investigate post-streak win rates,
+referring to work from MS. We finish with a brief look at sequences of
+round wins violating the Wald-Wolfowitz runs test, and whether such
+observed sequences occur more frequently than expected.
 
@@
 
-Using Equation \ref{eq:chi-squ}, We find that \(\chi^2 = 16.0\)
-(\(p\)-value of 0.0068) for the naive constant round win probability
-\(\phi_0 = 0.5\). Thus, We can comfortably reject the constant
-probability hypothesis for the null \(\phi_0 = 0.5\), even at a
-confidence level of \(\alpha = 0.01\).
+Using Equation \ref{eq:chi-squ}, we find that \(\chi^2 = 16.0\)
+(\(p\)-value of 0.0068) for \(\phi_0 = 0.5\). Thus, we can comfortably
+reject the constant probability hypothesis for the null
+\(\phi_0 = 0.5\), even at a confidence level of \(\alpha = 0.01\).
 
 Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected
-series lasting \(r\) rounds, \(\hat{\Phi}_0(r)\) (under the assumption
-\(\phi_0 = 0.5\)), for \(s = 11\), along with the observed proportions,
-\(\Phi(r)\), in CoD SnD.
+series lasting \(r\) rounds, the expected proportion of series given
+\(\phi_0 = 0.5\), \(\hat{\Phi}_0(r)\), and the observed proportions,
+\(\Phi(r)\).
 
 \begin{longtable}{rrrr}
-\caption{The expected proportion of series lasting $r$ rounds ($\hat{\Phi}_0(r)$) in a best-of-11 format, where $r \in R = [6, 7, 8, 9, 10, 11]$ under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-The observed frequencies for CoD SnD are shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
+\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
+Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
 \toprule
@@
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for
-the constant round win probability that We find when applying the three
-methods suggested by Mosteller (1952). Each is approximately or equal to
-0.575, and, when applying Equation \ref{eq:chi-squ}, each results in a
-\(\chi^2\) value for which We cannot reject the constant probability
+the constant round win probability that we find when applying the three
+methods suggested by Mosteller (1952). Each is approximately equal to
+0.575. When applying Equation \ref{eq:chi-squ}, each results in a
+\(\chi^2\) value for which we cannot reject the constant probability
 null hypothesis.
 
-\begin{longtable}[]{@{}lrr@{}}
+\begin{longtable}{lrr}
 \caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
-\toprule()
-Method & $\phi$ & $\chi^2$ (p-value) \\
-\midrule()
-\endfirsthead
-\toprule()
-Method & $\phi(r)$ & $\chi^2$ (p-value) \\
-\midrule()
-\endhead
+\toprule
+Method & $\phi$ & $\chi^2$ ($p$-value) \\
+\midrule
 0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
@@
 3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
-\bottomrule()
+\bottomrule
 \end{longtable}
@@
 
-\begin{longtable}[]{@{}rrrr@{}}
-\caption{The observed proportion of series $\Phi(r)$ ending in $r$ rounds in CoD SnD's best-of-11 format, compared to the expected proportion $\hat{\Phi}_0(r)$ the naive assumption $\phi_0 = 0.5$ and the expected proportion $\hat{\Phi}_2(r)$ under the maximum likelihood estimate $\phi_2 = 0.575$ for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
+\begin{longtable}{rrrr}
+\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
 \toprule()
@@
 hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results},
-it is fair to conclude that the constant round win probability
-assumption can be valid in CoD SnD series with the appropriate choice of
-\(\phi\) (\(\approx 0.575\)).
+we can say that the constant round win probability assumption is valid
+in CoD SnD series with the appropriate choice of \(\phi\)
+(\(\approx 0.575\)).
 
@@
 Given that people typically perceive streaks as beginning after the
-third success (or failure) at minimum (Carlson and Shu 2007), We focus
+third success (or failure) at minimum (Carlson and Shu 2007), we focus
 on streaks of three round wins.\footnote{Three happens to also be a
   reasonable number for series that last at maximum 11 rounds.} Table
-\ref{tbl:cod-pw3r-pl3r} compares the observed round win rate
-\(P^{w,kr}\) following streaks of \(k=3\) round wins given the series
-outcome (\(r\) rounds and winner) with the notional and MS expected
+\ref{tbl:cod-pw3r-pl3r} compares the notional and MS expected
 proportions, \(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\)
-respectively.
+respectively, with the observed round win rate, \(P^{+|kr}\), following
+streaks of \(k=3\) round wins given the series outcome.
 
@@
 eventual series loser is the team that wins after a streak of three
-round wins\footnote{This implies that the opponent, the eventual series
-  winner, goes on to win the series 6-4 after going down 0-4. This is
-  the only scenario in which one team wins four rounds consecutively but
-  loses a best-of-11 series in 10 rounds.}, all un-adjusted binomial
-test \(p\)-values are greater than the typical \(\alpha = 0.05\)
-threshold, implying that we cannot reject the null hypothesis that the
-expected notional and MS post-streak round win rates are different than
-the observed proportion. Adjusting the \(p\)-values with the Benjamini
-\& Yekutieli (BY) correction (2001), the null hypothesis cannot be
-rejected for any case.\footnote{As noted before, the MS expectations may
-  be unreliable for CoD SnD, so one is inclined to prefer the results of
-  the notional binomial tests.}
+round wins, all un-adjusted binomial test \(p\)-values are greater than
+the \(\alpha = 0.05\) confidence level, implying that we cannot reject
+the null hypothesis that the expected notional and MS post-streak round
+win rates are different than the observed proportion. However, after
+adjusting the \(p\)-values with the Benjamini and Yekutieli (BY)
+correction (2001), the null hypothesis cannot be rejected for any
+case.\footnote{As noted before, the MS expectations may be unreliable
+  for CoD SnD, so one is inclined to prefer the results of the notional
+  binomial tests.}
 
 When performing the same tests for streaks of two, four, and five, there
-is no case in which We can reject the binomial null hypothesis for the
-expected notional probability \(p^{+|k,r}_0\). The null hypothesis can
-only be rejected for the expected MS probability \(p^{+|k,r}_{MS}\) when
-\(k = 5, r = 7\) after applying the BY p-value correction.\footnote{At
-  36, the sample size for \$k = 5, r = 7\$ is not as large as most other
-  combinations of \$k\$ and \$r\$.}
+is no case in which we can reject the binomial null hypothesis for the
+expected notional proportion \(\hat{P}^{+|k,r}_0\) (even before the BY
+p-value correction). The null hypothesis can only be rejected for the
+expected MS proportion \(\hat{P}^{+|k,r}_{MS}\) when \(k = 5, r = 7\)
+after applying the BY p-value correction.\footnote{At 36, the sample
+  size for \(k = 5, r = 7\) is not as large as most other combinations
+  of \(k\) and \(r\).}
 
@@
 Wald-Wolfowitz null hypothesis at a confidence level of
-\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). (In addition to these 13,
-there are 12 additional sequences for \(r = 11\).) The relative
-frequency of the expected proportions are based on 10,000 simulations
-using the constant round probability \(\phi_2 = 0.575\). A test for
-difference between the actual and expected proportions of all sequences
-indicates that the null hypothesis---that the two proportions are
-equal---cannot be rejected for any of the 25 significant sequences.
+\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
+sequences shown, there are 12 additional sequences for \(r = 11\).
 
@@
 \midrule
-8 & 0-0-1-1-1-1-1-1 & 4 & 0.47\% & 7.67 & 0.90\% \\ 
-9 & 0-0-0-1-1-1-1-1-1 & 4 & 0.47\% & 3.75 & 0.44\% \\ 
-10 & 1-1-1-1-0-0-0-0-1-1 & 1 & 0.12\% & 2.39 & 0.28\% \\ 
-10 & 1-0-0-0-0-1-1-1-1-1 & 0 & 0.00\% & 2.04 & 0.24\% \\ 
-10 & 1-0-1-0-1-1-0-1-0-1 & 3 & 0.35\% & 2.04 & 0.24\% \\ 
-10 & 1-1-1-0-0-0-0-1-1-1 & 2 & 0.23\% & 2.04 & 0.24\% \\ 
-10 & 0-0-0-0-1-1-1-1-1-1 & 2 & 0.23\% & 1.79 & 0.21\% \\ 
-10 & 1-0-1-0-1-0-1-1-0-1 & 3 & 0.35\% & 1.70 & 0.20\% \\ 
-10 & 1-0-1-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.70 & 0.20\% \\ 
-10 & 1-1-0-0-0-0-1-1-1-1 & 1 & 0.12\% & 1.19 & 0.14\% \\ 
-10 & 1-0-1-0-1-0-1-0-1-1 & 3 & 0.35\% & 1.11 & 0.13\% \\ 
-10 & 1-1-0-1-0-1-0-1-0-1 & 0 & 0.00\% & 1.11 & 0.13\% \\ 
-10 & 1-1-1-1-1-0-0-0-0-1 & 2 & 0.23\% & 1.02 & 0.12\% \\ 
+8 & --++++++ & 4 & 0.47\% & 7.67 & 0.90\% \\ 
+9 & ---++++++ & 4 & 0.47\% & 3.75 & 0.44\% \\ 
+10 & ++++----++ & 1 & 0.12\% & 2.39 & 0.28\% \\ 
+10 & +----+++++ & 0 & 0.00\% & 2.04 & 0.24\% \\ 
+10 & +-+-++-+-+ & 3 & 0.35\% & 2.04 & 0.24\% \\ 
+10 & +++----+++ & 2 & 0.23\% & 2.04 & 0.24\% \\ 
+10 & ----++++++ & 2 & 0.23\% & 1.79 & 0.21\% \\ 
+10 & +-+-+-++-+ & 3 & 0.35\% & 1.70 & 0.20\% \\ 
+10 & +-++-+-+-+ & 0 & 0.00\% & 1.70 & 0.20\% \\ 
+10 & ++----++++ & 1 & 0.12\% & 1.19 & 0.14\% \\ 
+10 & +-+-+-+-++ & 3 & 0.35\% & 1.11 & 0.13\% \\ 
+10 & ++-+-+-+-+ & 0 & 0.00\% & 1.11 & 0.13\% \\ 
+10 & +++++----+ & 2 & 0.23\% & 1.02 & 0.12\% \\ 
 \bottomrule
 \end{longtable}
+
+The relative frequency of the expected proportions are based on 10,000
+simulations using the constant round probability \(\phi_2 = 0.575\). A
+test for the difference between the observed and expected proportions of
+all sequences, \(P^{\zeta r}\) and \(\hat{P}^{\zeta r}\) respectively,
+indicates that the null hypothesis---that the two proportions are
+equal---cannot be rejected for any of the 25 significant sequences.
 
@@
 
+Anecdotally, most observers swear by the existence of momentum in CoD
+SnD series, to the extent that vernacular has been developed to describe
+such phenomenon. Viewers have come to embrace the ``5-3'' phenomenon,
+where teams win three consecutive rounds after facing a 5-3 deficit to
+win 6-5. There is even a term for the rare 0-5 comeback---a ``full
+sail''.
+
+However, our results do not provide evidence for momentum on several
+fronts: (1) the evidence supporting the constant round probability; (2)
+the failure to reject the binomial null hypothesis for post-streak win
+rates; and (3) the failure to reject the equal proportions null
+hypothesis for streaky round sequences identified by the Wald-Wolfowitz
+runs test.
+
+Perhaps it is not surprising that we did not find evidence in favor of
+the hot hand effect given the small ``skill gap'' in the CoD relative to
+other esports. (Most professional esports players who have played CoD,
+including CoD players themselves, would not hesitate to state this.) A
+small skill gap fosters randomness in outcomes, implying that a given
+team is less likely to enjoy streaks of success in SnD.
+
 For the sake of brevity, we did not delve into win rates and streaks
@@
 interesting to look at whether the round win rate is higher after a
-streaks of three round wins when the team starts the streak winning as
-the offensive team. This would mean that, in the round immediately
-following the streak, the streaking team would be playing defense, where
-teams are slightly more likely to win on average. On the other hand,
-streaks of three starting with an offensive round win---theoretically,
-given \(\tau_O\) = 47.7\% the expected frequency is
-\(\tau_O^2 \times (1 - \tau_O) \approx\) 11.9\%---are likely to occur
-less frequently than such streaks starting with a defensive
-win---\(\tau_O \times (1 - \tau_O)^2 \approx\) 13.0\%---so We would want
-to account for sample size differences.
+streaks of three round wins when the team starts the streak as the
+offensive team. This would mean that, in the round immediately following
+the latest streak win, the streaking team would be playing defense,
+where teams are slightly more likely to win on average. On the other
+hand, streaks of three starting with an offensive round
+win---theoretically, knowing that \(\tau_O\) = 47.7\%, the expected
+frequency is \(\tau_O^2 (1 - \tau_O) \approx\) 11.9\%---are likely to
+occur less frequently than such streaks starting with a defensive
+win---\(\tau_O (1 - \tau_O)^2 \approx\) 13.0\%---so we would want to
+account for sample size differences.
 
-Further regarding future work, We've reached out to the Twitter user
+In the future, we could have account for prior team strengths, both in
+general and on specific maps. Even if doing so does not change the
+results, we could gain additional insight into why we do not observe
+statistically significant streakiness.
+
+Further regarding future work, we've reached out to the Twitter user
 ``R11stats'', who privately tracks in-round player
@@
 \item
-  We probably should have expected no hot hand effect given the small
-  ``skill gap'' in the CoD relative to other esports (andecdotal, but
-  most professional esports player, including CoD players themselves,
-  would say this).
 \end{itemize}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-codrules}{}}%
-{``Competitive Settings \textbar{} Call of Duty League.''} n.d.
-\url{https://callofdutyleague.com/en-us/competitive-settings?tab=map-veto}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-derover2021}{}}%
@@
 \emph{Journal of the American Statistical Association} 47 (259): 355380.
-
-\leavevmode\vadjust pre{\hypertarget{ref-peel2015}{}}%
-Peel, Leto, and Aaron Clauset. 2015. {``Predicting Sports Scoring
-Dynamics with Restoration and Anti-Persistence.''} In, 339348. IEEE.
 

### 2022-08-23 paper/paper.Rmd
spaces between + and -, other writing clean up

@@
 #| label: setup-code
+library(readr)
 library(dplyr)
@@
 Both have economic aspects that can create clear advantages for one team in a round, given how prior rounds played out.
-CoD has no such equivalent, except for perhaps "kill streaks", which infrequently occur.
+CoD has no such equivalent, except for perhaps "score streaks", which infrequently occur.
 2.
@@
 Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with a Wald-Wolfowitz runs test.
-Under the null hypothesis, the number of runs in a sequence of $r$ trials, $\zeta(r)$, is a random variable that can take on values $r^+$ and $r^-$ for success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$.
+Under the null hypothesis, the number of runs in a sequence of $r$ trials, $\zeta(r)$, is a random variable that can take on values $r^+$ and $r^- = r - r^+$ for the number of success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$:
 
@@
 \begin{equation}\label{eq:ww}
-\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
+\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
 \end{equation}
@@
 
-One can subset the observed series sequences to those that violate the null hypothesis for the run test and perform a test of equal proportions, where the null is that the observed rate of a sequence, $\psi$, is equal to the expected rate of the sequence, $\hat{psi}$.
+One can subset the observed series sequences to those that violate the null hypothesis for the run test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P(\zeta) = P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$.
 The test statistic is
@@
 \begin{equation}\label{eq:prop}
-Z = \frac{\hat{\psi} - \psi}{\sqrt{\psi_d (1 - \psi_d) ( \frac{1}{\hat{N}} + \frac{1}{N})}}
+Z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
 \end{equation}
 ```
-where $N$ is the observed number of sequences, $\hat{N}$ is the expected number, and $\psi_d = \frac{\psi - \hat{psi}}{N - \hat{N}}$.
+where
+
+$$
+P^\zeta_{\delta} = \frac{P^\zeta - \hat{P}^\zeta}{N^\zeta - \hat{N}^\zeta}
+$$
+
+and where $N^\zeta$ is the observed number of sequences, $\hat{N}^\zeta$ is the expected number of sequences.
 If we can reject the null hypothesis for such sequences, then there is implicit evidence in favor of the hot hand.
@@
 First, we investigate the constant probability assumption and the distribution of rounds played in a series.
-Chance's [-@chance2020] work is closely related to our, and, in fact, provides a guide for this investigation.
+Chance's work is closely related to our, and, in fact, provides a guide for this investigation.
 Afterwards, We investigate post-streak win rates, referring to work from MS.
@@
 #| label: cod_round_win_prop_after_k_wins_i_rounds-table
-
 cod_round_win_prop_after_k_wins_i_rounds |> 
@@
 
+cod_expected_round_arrangements_naive <- simulate_cod_round_arrangements(0.5)
 cod_expected_round_arrangements_mle <- simulate_cod_round_arrangements(0.575)
@@
 
+cod_round_arrangements_naive <- cod_expected_round_arrangements_naive |> perform_run_tests()
 cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()
+
 cod_round_arrangements_mle |> 
@@
 
-\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins $r^+$ and losses $r^-$ are denoted by $+$ and $-$ respectively.
+\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively.
 The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$.
@@
 \midrule
-8 & --++++++ & 4 & 0.47\% & 7.67 & 0.90\% \\ 
-9 & ---++++++ & 4 & 0.47\% & 3.75 & 0.44\% \\ 
-10 & ++++----++ & 1 & 0.12\% & 2.39 & 0.28\% \\ 
-10 & +----+++++ & 0 & 0.00\% & 2.04 & 0.24\% \\ 
-10 & +-+-++-+-+ & 3 & 0.35\% & 2.04 & 0.24\% \\ 
-10 & +++----+++ & 2 & 0.23\% & 2.04 & 0.24\% \\ 
-10 & ----++++++ & 2 & 0.23\% & 1.79 & 0.21\% \\ 
-10 & +-+-+-++-+ & 3 & 0.35\% & 1.70 & 0.20\% \\ 
-10 & +-++-+-+-+ & 0 & 0.00\% & 1.70 & 0.20\% \\ 
-10 & ++----++++ & 1 & 0.12\% & 1.19 & 0.14\% \\ 
-10 & +-+-+-+-++ & 3 & 0.35\% & 1.11 & 0.13\% \\ 
-10 & ++-+-+-+-+ & 0 & 0.00\% & 1.11 & 0.13\% \\ 
-10 & +++++----+ & 2 & 0.23\% & 1.02 & 0.12\% \\ 
+8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
+9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
+10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
+10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
+10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
+10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
+10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
+10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
+10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
+10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
+10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
+10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
+10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\ 
 \bottomrule
@@
 
-In the future, we could have account for prior team strengths, both in general and on specific maps.
+In the future, we could account for the quality of the teams, both in general and on specific maps.
 Even if doing so does not change the results, we could gain additional insight into why we do not observe statistically significant streakiness.
 
-Further regarding future work, we've reached out to the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.
 
 [^26]: <https://twitter.com/R11stats>
-
-Other talking points
-
--
 

### 2022-08-23 paper/paper.tex
spaces between + and -, other writing clean up

@@
 the number of runs in a sequence of \(r\) trials, \(\zeta(r)\), is a
-random variable that can take on values \(r^+\) and \(r^-\) for success
-and failure respectively, with the following mean \(\mu\) and variance
-\(\sigma^2\).
+random variable that can take on values \(r^+\) and \(r^- = r - r^+\)
+for the number of success and failure respectively, with the following
+mean \(\mu\) and variance \(\sigma^2\):
 
 \begin{equation}\label{eq:ww}
-\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}
+\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
 \end{equation}
@@
 null hypothesis for the run test and perform a test of equal
-proportions, where the null is that the observed rate of a sequence,
-\(\psi\), is equal to the expected rate of the sequence, \(\hat{psi}\).
-The test statistic is
+proportions, where the null is that the observed proportion of a
+sequence relative to all possible sequences, \(P(\zeta) = P^\zeta\), is
+equal to the expected proportion of the sequence relative to all
+possible sequences, \(\hat{P}^\zeta\). The test statistic is
 
 \begin{equation}\label{eq:prop}
-Z = \frac{\hat{\psi} - \psi}{\sqrt{\psi_d (1 - \psi_d) ( \frac{1}{\hat{N}} + \frac{1}{N})}}
+Z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
 \end{equation}
 
-where \(N\) is the observed number of sequences, \(\hat{N}\) is the
-expected number, and \(\psi_d = \frac{\psi - \hat{psi}}{N - \hat{N}}\).
-If we can reject the null hypothesis for such sequences, then there is
-implicit evidence in favor of the hot hand.
+where
+
+\[
+P^\zeta_{\delta} = \frac{P^\zeta - \hat{P}^\zeta}{N^\zeta - \hat{N}^\zeta}
+\]
+
+and where \(N^\zeta\) is the observed number of sequences,
+\(\hat{N}^\zeta\) is the expected number of sequences. If we can reject
+the null hypothesis for such sequences, then there is implicit evidence
+in favor of the hot hand.
 
@@
 First, we investigate the constant probability assumption and the
-distribution of rounds played in a series. Chance's (2020) work is
-closely related to our, and, in fact, provides a guide for this
-investigation. Afterwards, We investigate post-streak win rates,
-referring to work from MS. We finish with a brief look at sequences of
-round wins violating the Wald-Wolfowitz runs test, and whether such
-observed sequences occur more frequently than expected.
+distribution of rounds played in a series. Chance's work is closely
+related to our, and, in fact, provides a guide for this investigation.
+Afterwards, We investigate post-streak win rates, referring to work from
+MS. We finish with a brief look at sequences of round wins violating the
+Wald-Wolfowitz runs test, and whether such observed sequences occur more
+frequently than expected.
 
@@
 
-In the future, we could have account for prior team strengths, both in
+In the future, we could account for the quality of the teams, both in
 general and on specific maps. Even if doing so does not change the
@@
 
-Further regarding future work, we've reached out to the Twitter user
+Further regarding future work, we have contacted the Twitter user
 ``R11stats'', who privately tracks in-round player
@@
 research into player-specific momentum.
-
-Other talking points
-
-\begin{itemize}
-\tightlist
-\item
-\end{itemize}
 

### 2022-08-23 paper/paper.Rmd
footnote about number of sequences

@@
 
+cod_round_arrangements_naive <- cod_expected_round_arrangements_naive |> perform_run_tests()
+cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()
+
+# bind_rows(
+#   cod_round_arrangements_naive |> 
+#     filter(is_significant) |> 
+#     transmute(ws, is_naive = TRUE),
+#   cod_round_arrangements_naive |> 
+#     filter(is_significant) |> 
+#     transmute(ws, is_naive = FALSE)
+# ) |> 
+#   count(ws) |> 
+#   filter(n == 1L)
+
 cod_round_arrangements_mle |> 
@@
   )
-
-cod_round_arrangements_naive <- cod_expected_round_arrangements_naive |> perform_run_tests()
-cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()
 
@@
 
-In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
+In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^26] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
 In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.
+
+[^26]: If we used $\phi = 0.5$, we would get the same exact seqeunces.
 
@@
 
-Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^26] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^27] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
 While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.
 
-[^26]: <https://twitter.com/R11stats>
+[^27]: <https://twitter.com/R11stats>
 

### 2022-08-23 paper/paper.tex
footnote about number of sequences

@@
   team in a round, given how prior rounds played out. CoD has no such
-  equivalent, except for perhaps ``kill streaks'', which infrequently
+  equivalent, except for perhaps ``score streaks'', which infrequently
   occur.
@@
 shown for sequences, \(\zeta(r)\), for which one can reject the
-Wald-Wolfowitz null hypothesis at a confidence level of
+Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial
+success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
+  get the same exact seqeunces.} at a confidence level of
 \(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
@@
 expressed intent on making the data public, which would allow for
-research into player-specific momentum.
+research into player-specific momentum. While it seems there is no
+team-level hot hand effect in CoD SnD, perhaps there is with
+eliminations performed by individual players.
 

### 2022-08-25 paper/paper.Rmd
longtable -> table, other small notation fixes

@@
 ---
-title: "The Hot Hand Fallacy in Call of Duty"
+title: "The Hot Hand Fallacy in Call of Duty Search and Destroy"
 authors:
@@
 6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7% of series.
-The observed offensive round win percentage across all rounds is $\tau_O$ = 47.8%.[^10] Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
+The observed offensive round win percentage across all rounds is $\bar{\tau}_O$ = 47.8%.[^10] Table \ref{tbl:o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
 the number of round wins by each team prior to an upcoming round).
-Offensive round win rate is not quite constant, although never veers more than 10% from $\tau_O$.
+Offensive round win rate is not quite constant, although never veers more than 10% from $\bar{\tau}_O$.
 
@@
 ```{=tex}
-\begin{longtable}{crrrrrr}
-\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins.
-Numbers in parentheses are sample sizes.}\label{tbl:cod-o-win-prop-by-series-state} \\
+\begin{table}
+
+\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses are sample sizes.}
+
+\centering
+\begin{tabular}{crrrrrr}
 \toprule
@@
 \midrule
-0 & 47.8\%
-(852) & 46.6\%
-(408) & 43.1\%
-(216) & 43.5\%
-(115) & 43.3\%
-(67) & 40.5\%
-(37) \\ 
-1 & 48.6\%
-(444) & 49.3\%
-(418) & 51.5\%
-(309) & 43.4\%
-(205) & 43.3\%
-(120) & 39.4\%
-(99) \\ 
-2 & 52.8\%
-(218) & 48.9\%
-(305) & 48.9\%
-(315) & 46.6\%
-(262) & 48.7\%
-(189) & 42.1\%
-(133) \\ 
-3 & 54.5\%
-(123) & 46.0\%
-(200) & 49.6\%
-(250) & 45.6\%
-(248) & 44.4\%
-(214) & 44.8\%
-(174) \\ 
-4 & 56.9\%
-(65) & 54.5\%
-(145) & 47.2\%
-(193) & 44.7\%
-(228) & 55.2\%
-(221) & 50.5\%
-(208) \\ 
-5 & 47.4\%
-(38) & 49.4\%
-(83) & 47.1\%
-(136) & 50.9\%
-(175) & 45.2\%
-(177) & 46.0\%
-(202) \\ 
+
+0 & 47.8\%(852) & 46.6\%(408) & 43.1\%(216) & 43.5\%(115) & 43.3\%(67)  & 40.5\%(37)  \\
+1 & 48.6\%(444) & 49.3\%(418) & 51.5\%(309) & 43.4\%(205) & 43.3\%(120) & 39.4\%(99)  \\
+2 & 52.8\%(218) & 48.9\%(305) & 48.9\%(315) & 46.6\%(262) & 48.7\%(189) & 42.1\%(133) \\
+3 & 54.5\%(123) & 46.0\%(200) & 49.6\%(250) & 45.6\%(248) & 44.4\%(214) & 44.8\%(174) \\
+4 & 56.9\%(65)  & 54.5\%(145) & 47.2\%(193) & 44.7\%(228) & 55.2\%(221) & 50.5\%(208) \\
+5 & 47.4\%(38)  & 49.4\%(83)  & 47.1\%(136) & 50.9\%(175) & 45.2\%(177) & 46.0\%(202) \\
+
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:o-win-prop-by-series-state}
+
+\end{table}
 ```
@@
 \begin{equation}\label{eq:chi-squ}
-\chi^2 = \sum^{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
+\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
 \end{equation}
@@
 
-Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.
+Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.
 
 ```{=tex}
-\begin{longtable}{rrrr}
+\begin{table}
 \caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
+Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}
+
+\centering
+\begin{tabular}{rrrr}
 \toprule
@@
 \midrule
+
 6 & 40 & $4.7\%$ & $3.1\%$ \\ 
@@
 11 & 202 & $23.7\%$ & $24.6\%$ \\
+
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:prob-series-lasts-r-rounds}
+
+\end{table}
 ```
@@
 ```{=tex}
-\begin{longtable}{lrr}
-\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
+\begin{table}
+
+\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}
+
+\centering
+\begin{tabular}{lrr}
 \toprule
@@
 \midrule
+
 0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
@@
 3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
+
 \bottomrule
-\end{longtable}
-```
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^21] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+\end{tabular}
+
+\label{tbl:mosteller-methods-results}
+
+\end{table}
+```
+Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^21] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
@@
 ```{=tex}
-\begin{longtable}{rrrr}
-\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
-\toprule()
+\begin{table}
+\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}
+
+\centering
+\begin{tabular}{rrrrrr}
+\toprule
 $r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
-\midrule()
-\endhead
+\midrule
+
 6 & 4.7\% & 3.1\% & 4.2\% \\
@@
 11 & 23.7\% & 24.6\% & 22.0\% \\
-\bottomrule()
-\end{longtable}
+
+\bottomrule
+\end{tabular}
+
+\label{tbl:alternative-constant-ps}
+
+\end{table}
 ```
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^22] Table \ref{tbl:cod-pw3r-pl3r} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win rate, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^22] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win rate, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
 
@@
 ```{=tex}
-\begin{longtable}{rcrrrrr}
+\begin{table}
+
 \caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$).
 Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
-\label{tbl:cod-pw3r-pl3r} \\
-
+
+\centering
+\begin{tabular}{rcrrrrr}
 \toprule
@@
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:pwkr}
+
+\end{table}
 ```
@@
 Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
+As shown in Table \ref{tbl:pw3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
 
@@
 ```{=tex}
-\begin{longtable}{rrcrrrr}
+\begin{table}
+
 \caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak.
@@
 Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$ for brevity.}
-\label{tbl:cod-pw3ri-pl3ri} \\
+
+\centering
+\begin{tabular}{rrcrrrr}
 \toprule
@@
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:pw3ri}
+
+\end{table}
 ```
@@
 
-In Table \ref{tbl:cod-runs}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^26] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
+In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^26] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
 In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.
@@
 ```{=tex}
-\begin{longtable}{rlrrrr}
+\begin{table}
 
@@
 $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
-\label{tbl:cod-runs} \\
-
+
+\centering
+\begin{tabular}{rlrrrr}
 \toprule
-r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
+$r$ & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
 \midrule
@@
 10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\
+
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:ww-sequences}
+\end{table}
 ```
@@
 This would mean that, in the round immediately following the latest streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round win---theoretically, knowing that $\tau_O$ = 47.7%, the expected frequency is $\tau_O^2 (1 - \tau_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\tau_O (1 - \tau_O)^2 \approx$ 13.0%---so we would want to account for sample size differences.
+On the other hand, streaks of three starting with an offensive round win---theoretically, knowing that $\bar{\tau}_O$ = 47.7%, the expected frequency is $\bar{\tau}_O^2 (1 - \bar{\tau}_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\bar{\tau}_O (1 - \bar{\tau}_O)^2 \approx$ 13.0%---so we would want to account for sample size differences.
 

### 2022-08-25 paper/paper.tex
longtable -> table, other small notation fixes

@@
 
-\title{The Hot Hand Fallacy in Call of Duty}
+\title{The Hot Hand Fallacy in Call of Duty Search and Destroy}
 
@@
   in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)}
-Table \ref{tbl:cod-o-win-prop-by-series-state} shows round win
-percentages by series ``state'' (i.e.~the number of round wins by each
-team prior to an upcoming round). Offensive round win rate is not quite
-constant, although never veers more than 10\% from \(\tau_O\).
+Table \ref{tbl:o-win-prop-by-series-state} shows round win percentages
+by series ``state'' (i.e.~the number of round wins by each team prior to
+an upcoming round). Offensive round win rate is not quite constant,
+although never veers more than 10\% from \(\tau_O\).
 
-\begin{longtable}{crrrrrr}
-\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins.
-Numbers in parentheses are sample sizes.}\label{tbl:cod-o-win-prop-by-series-state} \\
+\begin{table}
+
+\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses are sample sizes.}
+
+\centering
+\begin{tabular}{crrrrrr}
 \toprule
@@
 \midrule
-0 & 47.8\%
-(852) & 46.6\%
-(408) & 43.1\%
-(216) & 43.5\%
-(115) & 43.3\%
-(67) & 40.5\%
-(37) \\ 
-1 & 48.6\%
-(444) & 49.3\%
-(418) & 51.5\%
-(309) & 43.4\%
-(205) & 43.3\%
-(120) & 39.4\%
-(99) \\ 
-2 & 52.8\%
-(218) & 48.9\%
-(305) & 48.9\%
-(315) & 46.6\%
-(262) & 48.7\%
-(189) & 42.1\%
-(133) \\ 
-3 & 54.5\%
-(123) & 46.0\%
-(200) & 49.6\%
-(250) & 45.6\%
-(248) & 44.4\%
-(214) & 44.8\%
-(174) \\ 
-4 & 56.9\%
-(65) & 54.5\%
-(145) & 47.2\%
-(193) & 44.7\%
-(228) & 55.2\%
-(221) & 50.5\%
-(208) \\ 
-5 & 47.4\%
-(38) & 49.4\%
-(83) & 47.1\%
-(136) & 50.9\%
-(175) & 45.2\%
-(177) & 46.0\%
-(202) \\ 
+
+0 & 47.8\%(852) & 46.6\%(408) & 43.1\%(216) & 43.5\%(115) & 43.3\%(67)  & 40.5\%(37)  \\
+1 & 48.6\%(444) & 49.3\%(418) & 51.5\%(309) & 43.4\%(205) & 43.3\%(120) & 39.4\%(99)  \\
+2 & 52.8\%(218) & 48.9\%(305) & 48.9\%(315) & 46.6\%(262) & 48.7\%(189) & 42.1\%(133) \\
+3 & 54.5\%(123) & 46.0\%(200) & 49.6\%(250) & 45.6\%(248) & 44.4\%(214) & 44.8\%(174) \\
+4 & 56.9\%(65)  & 54.5\%(145) & 47.2\%(193) & 44.7\%(228) & 55.2\%(221) & 50.5\%(208) \\
+5 & 47.4\%(38)  & 49.4\%(83)  & 47.1\%(136) & 50.9\%(175) & 45.2\%(177) & 46.0\%(202) \\
+
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:o-win-prop-by-series-state}
+
+\end{table}
 
@@
 
-Table \ref{tbl:cod-prob-series-lasting-r-rounds} shows the expected
-series lasting \(r\) rounds, the expected proportion of series given
+Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series
+lasting \(r\) rounds, the expected proportion of series given
 \(\phi_0 = 0.5\), \(\hat{\Phi}_0(r)\), and the observed proportions,
@@
 
-\begin{longtable}{rrrr}
+\begin{table}
 \caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum^{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}\label{tbl:cod-prob-series-lasting-r-rounds} \\
+Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}
+
+\centering
+\begin{tabular}{rrrr}
 \toprule
@@
 11 & 202 & $23.7\%$ & $24.6\%$ \\
+
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:prob-series-lasts-r-rounds}
+
+\end{table}
 
@@
 
-\begin{longtable}{lrr}
-\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}\label{tbl:mosteller-methods-results} \\
+\begin{table}
+
+\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}
+
+\centering
+\begin{tabular}{lrr}
 \toprule
@@
 3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
+
 \bottomrule
-\end{longtable}
+\end{tabular}
 
-Table \ref{tbl:expected-series-lengths-alternative-ps} shows the new
-\(\hat{\Phi}(r)\) when re-applying Equation \ref{eq:series-length} for
-the maximum likelihood estimate \(\phi_2 = 0.575\), resulting in a new
-set of expected proportions of series lasting \(r\) rounds
+\label{tbl:mosteller-methods-results}
+
+\end{table}
+
+Table \ref{tbl:alternative-constant-ps} shows the new \(\hat{\Phi}(r)\)
+when re-applying Equation \ref{eq:series-length} for the maximum
+likelihood estimate \(\phi_2 = 0.575\), resulting in a new set of
+expected proportions of series lasting \(r\) rounds
 \(\hat{\Phi}_2(r)\).\footnote{The method of moments and minimum
@@
 
-\begin{longtable}{rrrr}
-\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}\label{tbl:expected-series-lengths-alternative-ps} \\
-\toprule()
+\begin{table}
+\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}
+
+\centering
+\begin{tabular}{rrrrrr}
+\toprule
 $r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
-\midrule()
-\endhead
+\midrule
+
 6 & 4.7\% & 3.1\% & 4.2\% \\
@@
 11 & 23.7\% & 24.6\% & 22.0\% \\
-\bottomrule()
-\end{longtable}
+
+\bottomrule
+\end{tabular}
+
+\label{tbl:alternative-constant-ps}
+
+\end{table}
 
@@
   reasonable number for series that last at maximum 11 rounds.} Table
-\ref{tbl:cod-pw3r-pl3r} compares the notional and MS expected
-proportions, \(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\)
-respectively, with the observed round win rate, \(P^{+|kr}\), following
-streaks of \(k=3\) round wins given the series outcome.
+\ref{tbl:pwkr} compares the notional and MS expected proportions,
+\(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\) respectively, with
+the observed round win rate, \(P^{+|kr}\), following streaks of \(k=3\)
+round wins given the series outcome.
 
-\begin{longtable}{rcrrrrr}
+\begin{table}
+
 \caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$).
 Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
-\label{tbl:cod-pw3r-pl3r} \\
 
+\centering
+\begin{tabular}{rcrrrrr}
 \toprule
@@
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:pwkr}
+
+\end{table}
 
@@
 Now let us explicitly consider the round, \(i\). As shown in Table
-\ref{tbl:cod-pw3ri-pl3ri}, the notional win rate in the round \(i\)
-immediately following a streak of \(k\) round wins in a series lasting
-\(r\) rounds, \(\hat{P}{+|k,r,i}_0\), is statistically different than
-the observed \(P^{+|k,r,i}\) in several cases, notably when \(r = i\)
-for each of \(r \in [9, 10, 11]\).\footnote{The null can also be
-  rejected for \(r \in [7, 8]\), although these are not shown, and the
-  sample sizes are smaller.} Interestingly, the observed rate is greater
-than the expected rate in each case where we can reject the null
-hypothesis, whereas the observed rate is less than the expected rate in
-all other cases, as well in a strong majority of cases not shown.
+\ref{tbl:pw3ri}, the notional win rate in the round \(i\) immediately
+following a streak of \(k\) round wins in a series lasting \(r\) rounds,
+\(\hat{P}{+|k,r,i}_0\), is statistically different than the observed
+\(P^{+|k,r,i}\) in several cases, notably when \(r = i\) for each of
+\(r \in [9, 10, 11]\).\footnote{The null can also be rejected for
+  \(r \in [7, 8]\), although these are not shown, and the sample sizes
+  are smaller.} Interestingly, the observed rate is greater than the
+expected rate in each case where we can reject the null hypothesis,
+whereas the observed rate is less than the expected rate in all other
+cases, as well in a strong majority of cases not shown.
 
-\begin{longtable}{rrcrrrr}
+\begin{table}
+
 \caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak.
@@
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:pw3ri}
+
+\end{table}
 
@@
 
-In Table \ref{tbl:cod-runs}, the observed and expected count of
+In Table \ref{tbl:ww-sequences}, the observed and expected count of
 sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
@@
 
-\begin{longtable}{rlrrrr}
+\begin{table}
 
@@
 $\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
-\label{tbl:cod-runs} \\
 
+\centering
+\begin{tabular}{rlrrrr}
 \toprule
-r & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
+$r$ & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
 \midrule
@@
 10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\
+
 \bottomrule
-\end{longtable}
+\end{tabular}
+
+\label{tbl:ww-sequences}
+\end{table}
 

### 2022-08-25 paper/paper.Rmd
remove gt code, rename constant vars, proof-read up until result section, rate -> proportion in prose

@@
   Our research investigates patterns in round win percentages in professional Search and Destroy (SnD) matches of the popular first-person shooter game Call of Duty (CoD).
-First, we find evidence suppOrting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%.
-Second, we examine post-streak round win probability, given the series outcome.
-Given streak length, series length, and series winner, we find no evidence that post-streak win rate is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving.
+First, we find evidence supporting the hypothesis that round win probability can be modeled as a constant across rounds in the series, although not at the naive 50%.
+Second, we examine the proportion of round wins immediately following a win streak.
+Given streak length, series length, and series winner, we find no evidence that post-streak win proportion is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving.
 Wald-Wolfowitz run tests also fail to provide evidence for the hot hand phenomenon.
@@
 library(purrr)
-library(gt)
-library(scales)
+library(stringr)
+
+## i annotate when i use these with ::
+library(broom)
+library(randtests)
+library(withr)
 
@@
 
-pull_cod_o_win_prop_by_game <- function(.game) {
-  cod_o_win_prop_by_game |> 
-    filter(game == .game) |> 
-    pull(prop) |> 
-    scales::percent(accuracy = 0.1)
-}
-
 cod_n_series_lan <- cod_rounds |> 
-  filter(event |> stringr::str_detect('C[Hh][Aa][Mm][Pp]|Major')) |> 
+  filter(event |> str_detect('C[Hh][Aa][Mm][Pp]|Major')) |> 
   distinct(series_id) |> 
@@
 Call of Duty (CoD), first released in 2003, is one of the most popular first-person shooter (FPS) video game franchises of all-time.
-The most popular mode in the competitive scene is "Search and Destroy" (SnD), in which one team tries to destroy one of two designated bomb sites on the map, defended by the opposing team.[^1]
+The most popular mode in the competitive scene is "Search and Destroy" (SnD), in which one team tries to destroy one of two designated bomb sites on the map.[^1]
 
@@
 In professional CoD SnD, the two teams[^2] take turns playing offense and defense every round.
-The first to six round wins (best-of-11 format) is declared the series winner.[^3] A round can end in one of four ways:
+The first to six round wins (best-of-11 round format) is declared the series winner.[^3] A round can end in one of four ways:
 
@@
 
-[^3]: Each round has a two-minute time limit, not counting the potential extension granted if a bomb is planted.
-
-1.  One team eliminates all members of the other team prior to a bomb plant. (Eliminating team wins.)
-2.  The offensive team eliminates all members of the defensive team after a bomb plant.[^4] (Offense wins.)
-3.  The defense defuses the bomb after a bomb plant.[^5] (Defense wins.)
-4.  The offense does not make a plant by the time the round timer ends. (Defense wins.)
-
-[^4]:
-    -   The bomb can be picked up by any member of the offensive team.
-    -   The bomb carrier is not obstructed by carrying the bomb (i.e. movement is the same, weapon usage is the same, etc.).
-    -   The defense does not get any visual indication for who is carrying the bomb.
+[^3]: A short list of rules that govern timing follows.
+
+    -   Each round has a 90 second time limit, not counting the potential extension granted if a bomb is planted
     -   A bomb plant takes five seconds. The timer resets if the player stops planting site prior to completing it.
     -   A bomb defuse takes seven seconds. The timer resets if the player "drops" the bomb.
-    -   Once the bomb is planted, the round timer is reset to 45 seconds.
-
-[^5]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
+    -   Once the bomb is planted, the round timer is set to 45 seconds.
+
+1.  One team eliminates all members of the other team prior to a bomb plant. (Eliminating team wins.)
+2.  The offensive team eliminates all members of the defensive team after a bomb plant. (Offense wins.)
+3.  The defense defuses the bomb after a bomb plant.[^4] (Defense wins.)
+4.  The offense does not make a plant by the time the round timer ends. (Defense wins.)
+
+[^4]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
 
 We adopt the terminology "series" to refer to a single best-of-11 matchup, so as to mirror the terminology of playoff series in professional leagues like the National Basketball Association (NBA), National Hockey League (NHL), and Major League Baseball (MLB).
-A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD for the purposes of this paper.[^6]
-
-[^6]: Further, these are analogous to a trial in statistical analysis of Bernoulli events.
-
-SnD is not the only game type played in competitive CoD.
-Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game "maps", as most players refer to them (if a fifth map is needed).
-The best-of-five matchup could also be called a "series", but since we analyze only the SnD game types, we refer to SnD games as series.
+A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD for the purposes of this paper.
+
+We note that SnD is not the only game mode played in competitive CoD.[^5] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes.
+The best-of-five matchup could also be called a "series", but since we analyze only the SnD games, we refer to the SnD games as series.
+
+[^5]: Hardpoint has been played as the first and fourth maps in a matchup. The variant for the third map was Domination in the 2020 season, and Control in the 2021 and 2022 seasons.
 
@@
 CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), operating since 2020.
-The CDL has completed three year-long "seasons" as of August 2022.[^7]
-
-[^7]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, with releases coming in the late fall.
+The CDL has completed three year-long "seasons" as of August 2022.[^6]
+
+[^6]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, with releases coming in the late fall.
 A new game under the same brand---Call of Duty---is published every year by a rotating set of developers.
@@
 
-The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^8] Data has been collected in spreadsheets by community member "IOUTurtle".[^9]
-
-[^8]: 288 of the series occur in major tournaments, which are considered to be more "competitive" than the qualifiers since they are played in person (COVID-permitting), whereas the qualifiers are played online.
-
-[^9]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Processed data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
+The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^7] Data has been collected in spreadsheets by community member "IOUTurtle".[^8]
+
+[^7]: 288 of the series occur in major tournaments, which are considered to be more competitive than the qualifiers since they are played in person (COVID-permitting), eliminating randomness due to online latency and ping.
+The qualifiers are played online.
+
+[^8]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Our clean data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
 
 6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7% of series.
-The observed offensive round win percentage across all rounds is $\bar{\tau}_O$ = 47.8%.[^10] Table \ref{tbl:o-win-prop-by-series-state} shows round win percentages by series "state" (i.e.
-the number of round wins by each team prior to an upcoming round).
-Offensive round win rate is not quite constant, although never veers more than 10% from $\bar{\tau}_O$.
-
-[^10]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
-
-```{r}
-#| label: cod_o_win_prop
-cod_round_and_series_win_prop_by_side <- cod_rounds |>
-  group_by(pre_cumu_w, pre_cumu_l, is_offense) |>
-  summarize(
-    n = n(),
-    across(c(win_round, win_series), sum)
-  ) |>
-  ungroup() |>
-  mutate(
-    win_round_prop = win_round / n,
-    win_series_prop = win_series / n
-  )
-
-cod_round_and_series_win_prop_by_side |>
-  filter(is_offense) |>
-  transmute(
-    pre_cumu_w,
-    pre_cumu_l,
-    lab = sprintf('%.1f%%\n(%s)', round(100 * win_round_prop, 1), n)
-  ) |>
-  pivot_wider(
-    names_from = pre_cumu_l,
-    values_from = lab
-  ) |>
-  arrange(pre_cumu_w) |>
-  gt::gt() |>
-  gt::cols_label(
-    pre_cumu_w = "Defense round wins",
-  ) |>
-  gt::tab_spanner(
-    label = "Offense round wins",
-    columns = `0`:`5`
-  ) |>
-  gt::as_latex() |> 
-  cat()
-```
+The observed offensive round win percentage across all rounds is $\bar{\tau}_O$ = 47.8%.[^9] Table \ref{tbl:o-win-prop-by-series-state} shows offensive round win percentages by series "state", i.e.
+the number of round wins by each team prior to an upcoming round.
+Offensive round win percentage is not quite constant, although never veers more than 10% from $\bar{\tau}_O$.
+
+[^9]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
 
@@
 
-\caption{Offensive round win rates for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses are sample sizes.}
+\caption{Offensive round win percentage for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses indicate sample sizes.}
 
@@
 ```
-At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series played as the second or fifth map, and their opponent is assigned to start on offense in the SnD map not chosen.[^11][^12] Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers.
+At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series, played as the second or fifth game mode of the best-of-five matchup.
+Their opponent is assigned to start on offense in the SnD slot not chosen.[^10] Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers.
 Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team, despite their win-loss records.
-Overall, we can argue that potential bias due to stronger teams playing defense---or, if offense, if offense happens to be generally advantageous for a given map---is very minimal.
-
-[^11]: Hardpoint has been played as the first and fourth maps in a matchup. The variant for the third map was Domination in the 2020 season, and Control in the 2021 and 2022 seasons.
-
-[^12]: Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game, although this choice is not consistent across teams, or with the same team over time.
+Overall, we can argue that potential bias due to stronger teams playing defense---or, offense, if offense happens to be generally advantageous for a given map---is very minimal.
+
+[^10]: Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game mode in the best-of-five matchup, although this choice is not consistent across teams, or even with the same team over time.
 
@@
 Most assume a constant probability $\phi$ of a given team winning a game in the series, regardless of the series state.
-Mosteller [-@mosteller1952] observed that the American League had dominated the National League in MLB World Series matchups through 1952, implying that games should not be modeled with a constant (i.e.
-the null) $\phi_0 = 0.5$.
-Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\phi \approx 0.65$ in each case: (1) solving for $\phi$ from the observed average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximizing the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
-maximum likelihood), and (3) minimizing the chi-squared goodness of fit statistic $\chi^2$ as a function of $\phi$.
-
-Chance [-@chance2020] re-examines the constant probability notion in the MLB World Series (1923--2018), the NBA Finals (1951--2018), and the NHL Stanley Cup (1939--2018).
+Mosteller [-@mosteller1952] observed that the American League had dominated the National League in MLB World Series matchups through 1952, implying that games should not be modeled with a constant $\phi_0 = 0.5$.
+Mosteller proposed three approaches for identifying the optimal constant probability value of the stronger team in the World Series, finding $\hat{\phi} \approx 0.65$ in each case: (1) solve for $\phi$ from the observed average number of games won by the loser of the series, which he called the "method of moments" approach; (2) maximize the likelihood that the sample would have been drawn from a population in which the probability of a team winning a game is constant across the series (i.e.
+maximum likelihood), and (3) minimize the chi-squared goodness of fit statistic $\chi^2$ as a function of $\phi$.
+
+Chance [-@chance2020] re-examined the constant probability notion in the MLB World Series (1923--2018), the NBA Finals (1951--2018), and the NHL Stanley Cup (1939--2018).
 Chance found strong evidence against the null hypothesis of $\phi_0 = 0.5$ in the MLB and NHL championship series when applying Mosteller's first and second methods.
 
-Momentum, one of most discussed topics in sports analytics, goes hand-in-hand with a discussion of the nature of series outcomes.[^13] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
+The concept of momentum goes hand-in-hand with a discussion of the nature of series outcomes.[^11] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^13]: We often use "streaks" and momentum interchangeably, but as Steeger et al. ([-@steeger2021]) note, momentum implies dependence between events, whereas streaking does not.
-
-Studying both player streaks and team streaks in basketball, in both observational and controlled settings.
-Gilovich et al.
-[-@gilovich1985], henceforth GVT, ido not find evidence for the hot hand phenomenon.
+[^11]: We often use "streaks" and momentum interchangeably, but as Steeger et al. ([-@steeger2021]) note, momentum implies dependence between events, whereas streaking does not.
+
+Studying both player streaks and team streaks in basketball, in both observational and controlled settings, Gilovich et al.
+[-@gilovich1985], henceforth GVT, did not find evidence for the hot hand phenomenon.
 However, Miller and Sanjurjo [-@miller2018], henceforth MS, provided a framework for quantifying streak selection bias, which effectively works in the manner posited by the gambler's fallacy.
-Specifically, MS say that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
+Specifically, MS stated that a "bias exists in a common measure of the conditional dependence of present outcomes on streaks of past outcomes in sequential data" implying that, under i.i.d.
 conditions, "the proportion of successes among the outcomes that immediately follow a streak of consecutive successes is expected to be strictly less than the underlying (conditional) probability of success".
@@
 
-Other research has borrowed a common approach from the field of quality control, looking at unlikely sequences of events with the Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.
+Other research has borrowed techniques from the field of quality control, such as identifying unlikely sequences of events with the Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.
 2021).
@@
 As a check on their entropy approach to momentum identification, Steeger et al.
-found several NHL teams with sequence of wins in the 2018-2019 regular season violating the Wald-Wolfowitz null hypothesis.
+found several NHL teams with sequence of wins in the 2018-2019 regular season that violated the Wald-Wolfowitz null hypothesis.
 
@@
 Despite the plethora of existing research on games played in a series and momentum in sports, these topics have yet to be investigated heavily, if at all, in esports.
-Work has been done to examine intra-round win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
+Work has been done to examine intra-round, second-by-second win probability in other FPS titles such as Counter-Strike [@xenopoulos2022] and Valorant [@derover2021], both of which are round-based like CoD SnD.
 However, considering Counter-Strike and Valorant specifically, research on round-level trends seems non-existent, perhaps for one of several reasons:
@@
 Teams play either offense or defense for many consecutive rounds.
-(The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^14] While theoretically one might be able to account for any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+(The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^12] While theoretically one might be able to account for inter-round win percentage relationships in any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
 Bernoulli trials.
-3.  Both Counter-Strike and Valorant have overtime rules---team must win by two rounds---which can make end-of-series sequences difficult to model. CoD SnD does not have overtime rules.
-
-[^14]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each league.
+3.  Both Counter-Strike and Valorant have overtime rules---team must win by two rounds---which can make end-of-series sequences difficult to model properly. CoD SnD does not have overtime rules.
+
+[^12]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each.
 
 To our knowledge, there is no existing public statistical research on the CoD SnD format, beyond descriptive analysis on social media.
-While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation of a concept like the hot-hand fallacy in a different sport---particularly one that is less subjected to factors that may be difficult to control for, e.g.
+While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation of a concept like the hot-hand fallacy in a sport where it has not yet been invetigated---particularly one that is less subjected to factors that may be difficult to control for, e.g.
 weather---should be useful as a precedent or supplement for future researchers.
@@
 
-In a best-of-$s$ format, assuming a constant round win probability $\phi$[^15] (where $0 \leq \phi \leq 1$) for one team[^16], the expected proportion of series ending in $r$ rounds ($r \leq s$) is given by Equation \ref{eq:series-length}.
-
-[^15]: If $\phi > 0.5$, we can say that this is the stronger team.
-
-[^16]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
+In a best-of-$s$ format, assuming a constant round win probability $\phi$[^13] (where $0 \leq \phi \leq 1$) for one team[^14], the expected proportion of series ending in $r$ rounds ($r \leq s$) is given by Equation \ref{eq:series-length}.
+
+[^13]: If $\phi > 0.5$, we can say that this is the stronger team.
+
+[^14]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
 Upper-case symbol, e.g.
@@
 
-To evaluate the constant round win probability null hypothesis---that is, that the expected and observed round win rates, $\hat{\Phi}(r)$ and $\Phi(r)$ respectively, are equal to one another---we can compute the chi-square goodness of fit statistic
+To evaluate the constant round win probability hypothesis, we can compute the test statistic
 
@@
 \begin{equation}\label{eq:chi-squ}
-\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
+\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
 \end{equation}
 ```
-in which $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
+in which $\hat{\Phi}(r)$ and $\Phi(r)$ represent the expected and observed round win proportions respectively, and $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
+The null hypothesis is that the test statistic is chi-squared distributed, where the number of degrees of freedom is $\vert R \vert -1 = 5$ for Cod SnD.
+We reject the null hypothesis if $\chi^2 > \chi^2_{1-\alpha,\vert R \vert -1}$, where $\chi^2_{1-\alpha,\vert R \vert -1}$ is the chi-square critical value with $\vert R \vert -1$ degree of freedom and siginficance level $\alpha$.
 
@@
 
-Let us now consider round win rate immediately following a streak of $k$ wins, given that the series lasts $r$ rounds.
+Let us now consider round win proportions immediately following a streak of $k$ wins, given that the series lasts $r$ rounds.
 Removing our knowledge of a streak, we might model the Bernoulli round win probability as
@@
 
-As shown by MS with their Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.[^17] Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|k,r}_{MS}$ for $k > 1$.
-Nonetheless, one may run simulations to estimate the expected value, as we choose to do.[^18]
-
-[^17]: See Appendix E.1 of MS for the proof.
-
-[^18]: We have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
-
-Although one might be tempted to mirror the hypothesis testing for difference of proportions performed by MS (and GVT), our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings.[^19] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
+As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.[^15]
+
+[^15]: Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|k,r}_{MS}$ for $k > 1$.
+Nonetheless, one may run simulations to estimate the expected value, as we choose to do.
+We have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
+
+Although one might be tempted to mirror the equal proportions hypothesis testing performed by MS, our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^16] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
 The Bernoulli trial success probability, i.e.
-the single round win rate in CoD SnD, is not independent of the opponent.
+single round win percentage in CoD SnD, is not independent of the opponent.
 Consequently, a statistical test of the difference in $\hat{P}^{+|k,r}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rate, is not completely appropriate, although useful as a reference.
 
-[^19]: GVT also perform statistical tests on shots from players in live games, i.e.
+[^16]: GVT also perform statistical tests on shots from players in live games, i.e.
 "observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
@@
 
-We can perform a binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$ (where $0 \leq \omega_0 \leq 1$).
+We can perform a two-tailed binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$ (where $0 \leq \omega_0 \leq 1$).
 If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
@@
 ```
-Treating the notional proportion $\hat{P}^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed probability is equal to the notional probability.
+Treating the notional proportion $\hat{P}^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed proportion of post-streak round wins is equal to the notional proportion, given streak length $k$ and series length $r$.
 If we can reject this null hypothesis, then we can consider team momentum, represented by post-streak success, plausible.
 
-One can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|k,r}_{MS}$.[^20]
-
-[^20]: Given the caveats mentioned before, these results should be heeded with caution.
+As a reference, we can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|k,r}_{MS}$.
+However, given the caveats mentioned before regarding applying MS's theorem to our setting, the results of such binomial tests should be heeded with caution.
 
@@
 ```
-Again, we caapply a binomial test to evaluate the hypothesis that the expected proportions, $\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately, are equal to the observed proportion $P^{+|k,r}$.
+Again, we can apply a binomial test to evaluate the hypothesis that the expected proportions, $\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately, are equal to the observed proportion $P^{+|k,r}$.
 
@@
 
-Stepping back from the one-sided perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon with a Wald-Wolfowitz runs test.
-Under the null hypothesis, the number of runs in a sequence of $r$ trials, $\zeta(r)$, is a random variable that can take on values $r^+$ and $r^- = r - r^+$ for the number of success and failure respectively, with the following mean $\mu$ and variance $\sigma^2$:
+Stepping back from the (one-sided) perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon more broadly with a Wald-Wolfowitz runs test.
+Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes ($r^- = r - r^+$ failures), with the following mean $\mu$ and variance $\sigma^2$:
 
@@
 
-One can subset the observed series sequences to those that violate the null hypothesis for the run test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P(\zeta) = P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$.
+One can subset the observed series sequences, $\zeta(r)$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P(\zeta) = P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$.
 The test statistic is
@@
 \begin{equation}\label{eq:prop}
-Z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
+z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
 \end{equation}
@@
 
-and where $N^\zeta$ is the observed number of sequences, $\hat{N}^\zeta$ is the expected number of sequences.
-If we can reject the null hypothesis for such sequences, then there is implicit evidence in favor of the hot hand.
+and where $N^\zeta$ and $\hat{N}^\zeta$ are the observed and expected number of sequences respectively.
+The null hypothesis is that $z$ is normally distributed.
+If $z > +z_{(1-\alpha)/2}$ or $z < -z_{(1-\alpha)/2}$ for critical values at a significance level $\alpha$, we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.
 
 # Results
-
-First, we investigate the constant probability assumption and the distribution of rounds played in a series.
-Chance's work is closely related to our, and, in fact, provides a guide for this investigation.
-Afterwards, We investigate post-streak win rates, referring to work from MS.
-We finish with a brief look at sequences of round wins violating the Wald-Wolfowitz runs test, and whether such observed sequences occur more frequently than expected.
 
@@
 #| label: cod_series_outcome_prop
-.max_round <- 11
-.cutoff <- 6
+MAX_COD_ROUND <- 11
+COD_WIN_THRESHOLD <- 6
 prob_of_series_lasting_r_rounds <- function(r, p = 0.5, s) {
@@
 cod_actual_round_streaks <- cod_rounds |> 
-  filter(round <= .max_round) |> 
+  filter(round <= MAX_COD_ROUND) |> 
   filter(win_series) |> 
@@
   expected_round_streaks <- tibble(
-    n_rounds = .cutoff:.max_round
-  ) |> 
-    mutate(
-      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_r_rounds(.x, s = .max_round, p = !!p)),
-      n_expected_series_streaks = map_dbl(n_rounds, ~expected_series_streaks_of_outcomes(.cutoff, .x - .cutoff))
+    n_rounds = COD_WIN_THRESHOLD:MAX_COD_ROUND
+  ) |> 
+    mutate(
+      series_prop = map_dbl(n_rounds, ~prob_of_series_lasting_r_rounds(.x, s = MAX_COD_ROUND, p = !!p)),
+      n_expected_series_streaks = map_dbl(n_rounds, ~expected_series_streaks_of_outcomes(COD_WIN_THRESHOLD, .x - COD_WIN_THRESHOLD))
     ) |> 
@@
 
-Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.
-
-```{=tex}
-\begin{table}
-\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}
-
-\centering
-\begin{tabular}{rrrr}
-\toprule
-$r$ & $N(r)$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ \\ 
-\midrule
-
-6 & 40 & $4.7\%$ & $3.1\%$ \\ 
-7 & 101 & $11.9\%$ & $9.4\%$ \\ 
-8 & 141 & $16.5\%$ & $16.4\%$ \\ 
-9 & 185 & $21.7\%$ & $21.9\%$ \\ 
-10 & 183 & $21.5\%$ & $24.6\%$ \\ 
-11 & 202 & $23.7\%$ & $24.6\%$ \\
-
-\bottomrule
-\end{tabular}
-
-\label{tbl:prob-series-lasts-r-rounds}
-
-\end{table}
-```
 ```{r}
@@
 generate_chi_label <- function(statistic, p.value) {
-  sprintf('%.1f (%s)', statistic, ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2))))
+  sprintf(
+    '%.1f (%s)', 
+    statistic, 
+    ifelse(p.value <= 0.01, '<=0.01', as.character(round(p.value, 2)))
+  )
 }
@@
 
+Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.
+
+```{=tex}
+\begin{table}
+\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
+Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}
+
+\centering
+\begin{tabular}{rrrr}
+\toprule
+$r$ & $N(r)$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ \\ 
+\midrule
+
+6 & 40 & $4.7\%$ & $3.1\%$ \\ 
+7 & 101 & $11.9\%$ & $9.4\%$ \\ 
+8 & 141 & $16.5\%$ & $16.4\%$ \\ 
+9 & 185 & $21.7\%$ & $21.9\%$ \\ 
+10 & 183 & $21.5\%$ & $24.6\%$ \\ 
+11 & 202 & $23.7\%$ & $24.6\%$ \\
+
+\bottomrule
+\end{tabular}
+
+\label{tbl:prob-series-lasts-r-rounds}
+
+\end{table}
+```
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that we find when applying the three methods suggested by Mosteller [-@mosteller1952].
@@
 When applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which we cannot reject the constant probability null hypothesis.
+Note that rejection of the null hypothesis is the baseline and failure to reject the null is the non-trivial result, contrary to most statistical analysis.
 
@@
 ```
-Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^21] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^17] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^21]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+[^17]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 ```
-Observing that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (especially in comparison to $\hat{\Phi}_0(r)$), along with the null hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results}, we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
+Observing that the null hypothesis acceptance shown in Table \ref{tbl:mosteller-methods-results}, along with the observation that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (in comparison to $\hat{\Phi}_0(r)$), we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
 
@@
 
-```{r}
-#| label: cod_round_win_prop_after_k_wins-table
-cod_round_win_prop_after_k_wins |> 
-  mutate(
-    orig_notional_p_value = notional_p_value,
-    orig_ms_p_value = ms_p_value
-  ) |> 
-  # group_by(win_streak) |> 
-  mutate(
-    across(c(notional_p_value, ms_p_value), ~p.adjust(.x, method = 'BY'))
-  ) |> 
-  # ungroup() |>
-  filter(win_streak == 3L) |> 
-  # filter(ms_p_value < 0.05)
-  mutate(
-    prop_lab = scales::percent(prop, accuracy = 0.1),
-    notional_lab = sprintf('%.1f%%', 100 * notional_prop),
-    ms_lab = sprintf('%.1f%%', 100 * ms_prop)
-  ) |>
-  arrange(n_rounds, win_series, win_round) |> 
-  filter(win_round) |> 
-  transmute(
-    n_rounds,
-    across(win_series, ~ifelse(.x, 'yes', 'no')),
-    n,
-    total,
-    prop_lab,
-    notional_lab,
-    ms_lab
-  ) |> 
-  gt::gt() |> 
-  gt::cols_label(
-    n_rounds = 'r',
-    win_series = 'Win series?',
-    n = 'r+',
-    total = 'N',
-    prop_lab = 'O',
-    notional_lab = 'a',
-    ms_lab = 'b'
-  ) |> 
-  gt::as_latex() |> 
-  cat()
-```
-
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^22] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win rate, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
-
-[^22]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^18] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
+
+[^18]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
 
@@
 ```
-With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win rates are different than the observed proportion.
-However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^23]
-
-[^23]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
+With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win proportions are different than the observed proportion.
+However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^19]
+
+[^19]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
 
 When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the binomial null hypothesis for the expected notional proportion $\hat{P}^{+|k,r}_0$ (even before the BY p-value correction).
-The null hypothesis can only be rejected for the expected MS proportion $\hat{P}^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^24]
-
-[^24]: At 36, the sample size for $k = 5, r = 7$ is not as large as most other combinations of $k$ and $r$.
+The null hypothesis can only be rejected for the expected MS proportion $\hat{P}^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^20]
+
+[^20]: At 36, the sample size for $k = 5, r = 7$ is not as large as most other combinations of $k$ and $r$.
 
@@
 
-```{r}
-#| label: cod_round_win_prop_after_k_wins_i_rounds-table
-cod_round_win_prop_after_k_wins_i_rounds |> 
-  mutate(
-    across(notional_p_value, p.adjust)
-  ) |>
-  filter(
-    win_round,
-    # round >= (n_rounds - 3)
-    n_rounds >= 10,
-    win_streak == 3
-  ) |>  
-  filter(total >= 10) |> 
-  mutate(
-    across(
-      matches('p_value'), 
-      ~case_when(
-        .x <= 0.01 ~ '<=0.01', 
-        TRUE ~ sprintf('%.2f', .x)
-      )
-    ),
-    prop_lab = scales::percent(prop, accuracy = 0.1),
-    notional_lab = scales::percent(notional_prop, accuracy = 0.1)
-  ) |>
-  arrange(n_rounds, round, win_series, win_round) |> 
-  transmute(
-    n_rounds,
-    round,
-    across(win_series, ~ifelse(.x, 'yes', 'no')),
-    n,
-    total,
-    prop_lab,
-    notional_lab
-  ) |> 
-  gt::gt() |> 
-  gt::cols_label(
-    n_rounds = 'r',
-    round = 'i',
-    win_series = 'Win series?',
-    n = 'r+',
-    total = 'N',
-    prop_lab = 'O',
-    notional_lab = 'a'
-  ) |> 
-  gt::as_latex() |> 
-  cat()
-
-```
-
 Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:pw3ri}, the notional win rate in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^25] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
-
-[^25]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
+As shown in Table \ref{tbl:pw3ri}, the notional win proportion in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^21] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
+
+[^21]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
 
@@
 #| label: cod_round_arrangements
-library(randtests)
+
 simulate_cod_round_arrangements <- function(p = 0.5, n_sims = 10000, seed = 42) {
-  n_rounds_max <- 11
-  set.seed(seed)
-  w <- sample(c(0, 1), size = n_rounds_max * n_sims, replace = TRUE, prob = c(1 - p, p))
+  withr::local_seed(seed)
+  w <- sample(c(0, 1), size = MAX_COD_ROUND * n_sims, replace = TRUE, prob = c(1 - p, p))
   m <- matrix(w, nrow = n_sims, ncol = n_rounds_max)
@@
       ) |> 
-      # filter(record != '6-0') |> 
       select(-round) |> 
@@
 
-# bind_rows(
-#   cod_round_arrangements_naive |> 
-#     filter(is_significant) |> 
-#     transmute(ws, is_naive = TRUE),
-#   cod_round_arrangements_naive |> 
-#     filter(is_significant) |> 
-#     transmute(ws, is_naive = FALSE)
-# ) |> 
-#   count(ws) |> 
-#   filter(n == 1L)
-
 cod_round_arrangements_mle |> 
-  # mutate(
-  #   total_actual = sum(n_actual),
-  #   total_expected = sum(n_expected)
-  # ) |> 
   filter(!is.na(p_value)) |> 
@@
   mutate(
-    prop_p_value = vectorized_prop_test(n_actual, total_actual, round(n_expected_adj), round(total_expected_adj))$p.value,
+    prop_p_value = vectorized_prop_test(
+      n_actual, 
+      total_actual, 
+      round(n_expected_adj), 
+      round(total_expected_adj)
+    )$p.value,
     orig_prop_p_value = prop_p_value,
@@
   )
-
-cod_round_arrangements_mle |> 
-  filter(is_significant) |> 
-  filter(n_rounds < 11) |> 
-  transmute(
-    n_rounds,
-    ws,
-    n_actual,
-    across(prop_actual, ~sprintf('%.2f%%', 100 * .x)),
-    across(n_expected_adj, round, 2),
-    across(prop_expected, ~sprintf('%.2f%%', 100 * .x))
-  ) |> 
-  gt::gt() |> 
-  gt::cols_label(
-    n_rounds = 'r',
-    ws = 'Sequence',
-    n_actual = 'a',
-    prop_actual = 'b',
-    n_expected_adj = 'c',
-    prop_expected = 'd'
-  ) |> 
-  gt::as_latex() |> 
-  cat()
 ```
@@
 
-In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^26] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
+In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^22] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
 In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.
 
-[^26]: If we used $\phi = 0.5$, we would get the same exact seqeunces.
+[^22]: If we used $\phi = 0.5$, we would get the same exact seqeunces.
 
@@
 
-However, our results do not provide evidence for momentum on several fronts: (1) the evidence supporting the constant round probability; (2) the failure to reject the binomial null hypothesis for post-streak win rates; and (3) the failure to reject the equal proportions null hypothesis for streaky round sequences identified by the Wald-Wolfowitz runs test.
+However, our results do not provide evidence for momentum on several fronts: (1) the evidence supporting the constant round probability; (2) the failure to reject the binomial null hypothesis for post-streak win proportions; and (3) the failure to reject the equal proportions null hypothesis for streaky round sequences identified by the Wald-Wolfowitz runs test.
 
@@
 
-For the sake of brevity, we did not delve into win rates and streaks split by offensive or defensive role.
-For example, it would be interesting to look at whether the round win rate is higher after a streaks of three round wins when the team starts the streak as the offensive team.
+For the sake of brevity, we did not account for offensive or defensive role when considering win proportions during streaks.
+For example, it would be interesting to look at whether the round win percentage is higher after a streaks of three round wins when the team starts the streak as the offensive team.
 This would mean that, in the round immediately following the latest streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average.
@@
 
-Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^27] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^23] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
 While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.
 
-[^27]: <https://twitter.com/R11stats>
+[^23]: <https://twitter.com/R11stats>
 

### 2022-08-25 paper/paper.tex
remove gt code, rename constant vars, proof-read up until result section, rate -> proportion in prose

@@
 first-person shooter game Call of Duty (CoD). First, we find evidence
-suppOrting the hypothesis that round win probability can be modeled as a
+supporting the hypothesis that round win probability can be modeled as a
 constant across rounds in the series, although not at the naive 50\%.
-Second, we examine post-streak round win probability, given the series
-outcome. Given streak length, series length, and series winner, we find
-no evidence that post-streak win rate is significantly different than
-expected, suggesting that the perception of momentum at the team level
-is deceiving. Wald-Wolfowitz run tests also fail to provide evidence for
-the hot hand phenomenon.
+Second, we examine the proportion of round wins immediately following a
+win streak. Given streak length, series length, and series winner, we
+find no evidence that post-streak win proportion is significantly
+different than expected, suggesting that the perception of momentum at
+the team level is deceiving. Wald-Wolfowitz run tests also fail to
+provide evidence for the hot hand phenomenon.
 \end{abstract}
@@
 in which one team tries to destroy one of two designated bomb sites on
-the map, defended by the opposing team.\footnote{SnD bears resemblance
-  to ``Bomb Defusal'' in Counter-Strike and ``Plant/Defuse'' in
-  Valorant, two other FPS games played in more popular professional
-  leagues.}
+the map.\footnote{SnD bears resemblance to ``Bomb Defusal'' in
+  Counter-Strike and ``Plant/Defuse'' in Valorant, two other FPS games
+  played in more popular professional leagues.}
 
@@
   teams played with four players each.} take turns playing offense and
-defense every round. The first to six round wins (best-of-11 format) is
-declared the series winner.\footnote{Each round has a two-minute time
-  limit, not counting the potential extension granted if a bomb is
-  planted.} A round can end in one of four ways:
+defense every round. The first to six round wins (best-of-11 round
+format) is declared the series winner.\footnote{A short list of rules
+  that govern timing follows.
+
+  \begin{itemize}
+  \tightlist
+  \item
+    Each round has a 90 second time limit, not counting the potential
+    extension granted if a bomb is planted
+  \item
+    A bomb plant takes five seconds. The timer resets if the player
+    stops planting site prior to completing it.
+  \item
+    A bomb defuse takes seven seconds. The timer resets if the player
+    ``drops'' the bomb.
+  \item
+    Once the bomb is planted, the round timer is set to 45 seconds.
+  \end{itemize}} A round can end in one of four ways:
 
@@
   The offensive team eliminates all members of the defensive team after
-  a bomb plant.\footnote{\begin{itemize}
-    \tightlist
-    \item
-      The bomb can be picked up by any member of the offensive team.
-    \item
-      The bomb carrier is not obstructed by carrying the bomb
-      (i.e.~movement is the same, weapon usage is the same, etc.).
-    \item
-      The defense does not get any visual indication for who is carrying
-      the bomb.
-    \item
-      A bomb plant takes five seconds. The timer resets if the player
-      stops planting site prior to completing it.
-    \item
-      A bomb defuse takes seven seconds. The timer resets if the player
-      ``drops'' the bomb.
-    \item
-      Once the bomb is planted, the round timer is reset to 45 seconds.
-    \end{itemize}} (Offense wins.)
+  a bomb plant. (Offense wins.)
 \item
@@
 ``game'' or a ``match'' in such leagues is analogous to a ``round'' of
-CoD SnD for the purposes of this paper.\footnote{Further, these are
-  analogous to a trial in statistical analysis of Bernoulli events.}
+CoD SnD for the purposes of this paper.
 
-SnD is not the only game type played in competitive CoD. Teams play in a
+We note that SnD is not the only game mode played in competitive
+CoD.\footnote{Hardpoint has been played as the first and fourth maps in
+  a matchup. The variant for the third map was Domination in the 2020
+  season, and Control in the 2021 and 2022 seasons.} Teams play in a
 head-to-head, best-of-five format, where SnD is always played as the
-second and fifth game ``maps'', as most players refer to them (if a
-fifth map is needed). The best-of-five matchup could also be called a
-``series'', but since we analyze only the SnD game types, we refer to
-SnD games as series.
+second and fifth game modes. The best-of-five matchup could also be
+called a ``series'', but since we analyze only the SnD games, we refer
+to the SnD games as series.
 
@@
 series.\footnote{288 of the series occur in major tournaments, which are
-  considered to be more ``competitive'' than the qualifiers since they
-  are played in person (COVID-permitting), whereas the qualifiers are
-  played online.} Data has been collected in spreadsheets by community
-member ``IOUTurtle''.\footnote{Raw data:
-  \url{https://linktr.ee/CDLArchive}. Author:
-  \url{https://twitter.com/IOUTurtle}. Processed data can be found at
+  considered to be more competitive than the qualifiers since they are
+  played in person (COVID-permitting), eliminating randomness due to
+  online latency and ping. The qualifiers are played online.} Data has
+been collected in spreadsheets by community member
+``IOUTurtle''.\footnote{Raw data: \url{https://linktr.ee/CDLArchive}.
+  Author: \url{https://twitter.com/IOUTurtle}. Our clean data can be
+  found at
   \url{https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv}.}
@@
 of series. The observed offensive round win percentage across all rounds
-is \(\tau_O\) = 47.8\%.\footnote{Offensive round win percentage has been
-  nearly constant across the three games during the CDL era: 1. 47.2\%
-  in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard (2022)}
-Table \ref{tbl:o-win-prop-by-series-state} shows round win percentages
-by series ``state'' (i.e.~the number of round wins by each team prior to
-an upcoming round). Offensive round win rate is not quite constant,
-although never veers more than 10\% from \(\tau_O\).
+is \(\bar{\tau}_O\) = 47.8\%.\footnote{Offensive round win percentage
+  has been nearly constant across the three games during the CDL era: 1.
+  47.2\% in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard
+  (2022)} Table \ref{tbl:o-win-prop-by-series-state} shows offensive
+round win percentages by series ``state'', i.e.~the number of round wins
+by each team prior to an upcoming round. Offensive round win percentage
+is not quite constant, although never veers more than 10\% from
+\(\bar{\tau}_O\).
 
@@
 At tournaments, higher-seeded (``better'') teams choose whether they
-want to start on offense in the SnD series played as the second or fifth
-map, and their opponent is assigned to start on offense in the SnD map
-not chosen.\footnote{Hardpoint has been played as the first and fourth
-  maps in a matchup. The variant for the third map was Domination in the
-  2020 season, and Control in the 2021 and 2022 seasons.}\footnote{Anecdotally,
+want to start on offense in the SnD series, played as the second or
+fifth game mode of the best-of-five matchup. Their opponent is assigned
+to start on offense in the SnD slot not chosen.\footnote{Anecdotally,
   the higher-seeded teams tend to choose to play defense in the first
-  round of the SnD series played as the second game, although this
-  choice is not consistent across teams, or with the same team over
-  time.} Outside of tournaments, teams all play each other twice
-throughout the season, constituting qualifiers. Each team gets to play
-the higher-seeded role once in their head-to-head matchups with a given
-team, despite their win-loss records. Overall, we can argue that
-potential bias due to stronger teams playing defense---or, if offense,
-if offense happens to be generally advantageous for a given map---is
-very minimal.
+  round of the SnD series played as the second game mode in the
+  best-of-five matchup, although this choice is not consistent across
+  teams, or even with the same team over time.} Outside of tournaments,
+teams all play each other twice throughout the season, constituting
+qualifiers. Each team gets to play the higher-seeded role once in their
+head-to-head matchups with a given team, despite their win-loss records.
+Overall, we can argue that potential bias due to stronger teams playing
+defense---or, offense, if offense happens to be generally advantageous
+for a given map---is very minimal.
 
@@
 dominated the National League in MLB World Series matchups through 1952,
-implying that games should not be modeled with a constant (i.e.~the
-null) \(\phi_0 = 0.5\). Mosteller proposed three approaches for
-identifying the optimal constant probability value of the stronger team
-in the World Series, finding \(\phi \approx 0.65\) in each case: (1)
-solving for \(\phi\) from the observed average number of games won by
-the loser of the series, which he called the ``method of moments''
-approach; (2) maximizing the likelihood that the sample would have been
-drawn from a population in which the probability of a team winning a
-game is constant across the series (i.e.~maximum likelihood), and (3)
-minimizing the chi-squared goodness of fit statistic \(\chi^2\) as a
-function of \(\phi\).
+implying that games should not be modeled with a constant
+\(\phi_0 = 0.5\). Mosteller proposed three approaches for identifying
+the optimal constant probability value of the stronger team in the World
+Series, finding \(\hat{\phi} \approx 0.65\) in each case: (1) solve for
+\(\phi\) from the observed average number of games won by the loser of
+the series, which he called the ``method of moments'' approach; (2)
+maximize the likelihood that the sample would have been drawn from a
+population in which the probability of a team winning a game is constant
+across the series (i.e.~maximum likelihood), and (3) minimize the
+chi-squared goodness of fit statistic \(\chi^2\) as a function of
+\(\phi\).
 
-Chance (2020) re-examines the constant probability notion in the MLB
+Chance (2020) re-examined the constant probability notion in the MLB
 World Series (1923--2018), the NBA Finals (1951--2018), and the NHL
@@
 
-Momentum, one of most discussed topics in sports analytics, goes
-hand-in-hand with a discussion of the nature of series
-outcomes.\footnote{We often use ``streaks'' and momentum
-  interchangeably, but as Steeger et al.~((2021)) note, momentum implies
-  dependence between events, whereas streaking does not.} Two opposing
-fallacies are observed in the context of momentum: the ``gambler's
-fallacy'' (negative recency) and the ``hot hand fallacy'' (positive
-recency). Per Ayton et al. (2004), negative recency is ``the belief
-that, for random events, runs of a particular outcome \ldots{} will be
-balanced by a tendency for the opposite outcome'', while positive
-recency is the expectation of observing future results that match recent
-results.
+The concept of momentum goes hand-in-hand with a discussion of the
+nature of series outcomes.\footnote{We often use ``streaks'' and
+  momentum interchangeably, but as Steeger et al.~((2021)) note,
+  momentum implies dependence between events, whereas streaking does
+  not.} Two opposing fallacies are observed in the context of momentum:
+the ``gambler's fallacy'' (negative recency) and the ``hot hand
+fallacy'' (positive recency). Per Ayton et al. (2004), negative recency
+is ``the belief that, for random events, runs of a particular outcome
+\ldots{} will be balanced by a tendency for the opposite outcome'',
+while positive recency is the expectation of observing future results
+that match recent results.
 
 Studying both player streaks and team streaks in basketball, in both
-observational and controlled settings. Gilovich et al. (1985),
-henceforth GVT, ido not find evidence for the hot hand phenomenon.
+observational and controlled settings, Gilovich et al. (1985),
+henceforth GVT, did not find evidence for the hot hand phenomenon.
 However, Miller and Sanjurjo (2018), henceforth MS, provided a framework
 for quantifying streak selection bias, which effectively works in the
-manner posited by the gambler's fallacy. Specifically, MS say that a
+manner posited by the gambler's fallacy. Specifically, MS stated that a
 ``bias exists in a common measure of the conditional dependence of
@@
 
-Other research has borrowed a common approach from the field of quality
-control, looking at unlikely sequences of events with the Wald-Wolfowitz
-runs test (Peel and Clauset 2015, Steeger et al.~2021). Peel and Clauset
-found no evidence for unlikely sequences of scoring events in the NHL,
-College Football (CFB), and National Football League (NFL), but did in
-the NBA. As a check on their entropy approach to momentum
-identification, Steeger et al.~found several NHL teams with sequence of
-wins in the 2018-2019 regular season violating the Wald-Wolfowitz null
-hypothesis.
+Other research has borrowed techniques from the field of quality
+control, such as identifying unlikely sequences of events with the
+Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.~2021).
+Peel and Clauset found no evidence for unlikely sequences of scoring
+events in the NHL, College Football (CFB), and National Football League
+(NFL), but did in the NBA. As a check on their entropy approach to
+momentum identification, Steeger et al.~found several NHL teams with
+sequence of wins in the 2018-2019 regular season that violated the
+Wald-Wolfowitz null hypothesis.
 
@@
 heavily, if at all, in esports. Work has been done to examine
-intra-round win probability in other FPS titles such as Counter-Strike
-(Xenopoulos, Freeman, and Silva 2022) and Valorant (DeRover 2021), both
-of which are round-based like CoD SnD. However, considering
-Counter-Strike and Valorant specifically, research on round-level trends
-seems non-existent, perhaps for one of several reasons:
+intra-round, second-by-second win probability in other FPS titles such
+as Counter-Strike (Xenopoulos, Freeman, and Silva 2022) and Valorant
+(DeRover 2021), both of which are round-based like CoD SnD. However,
+considering Counter-Strike and Valorant specifically, research on
+round-level trends seems non-existent, perhaps for one of several
+reasons:
 
@@
   for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
-    is not used today in these leagues, but it was at least once in each
-    league.} While theoretically one might be able to account for any
-  kind of format, such as a 5-5-1, the rotation of team sides every
-  round is convenient for convincing ourselves that rounds could
-  reasonably be modeled as i.i.d. Bernoulli trials.
+    is not used today in these leagues, but it was at least once in
+    each.} While theoretically one might be able to account for
+  inter-round win percentage relationships in any kind of format, such
+  as a 5-5-1, the rotation of team sides every round is convenient for
+  convincing ourselves that rounds could reasonably be modeled as i.i.d.
+  Bernoulli trials.
 \item
@@
   by two rounds---which can make end-of-series sequences difficult to
-  model. CoD SnD does not have overtime rules.
+  model properly. CoD SnD does not have overtime rules.
 \end{enumerate}
@@
 an advantage on their competition, broader investigation of a concept
-like the hot-hand fallacy in a different sport---particularly one that
-is less subjected to factors that may be difficult to control for,
-e.g.~weather---should be useful as a precedent or supplement for future
-researchers.
+like the hot-hand fallacy in a sport where it has not yet been
+invetigated---particularly one that is less subjected to factors that
+may be difficult to control for, e.g.~weather---should be useful as a
+precedent or supplement for future researchers.
 
@@
 
-To evaluate the constant round win probability null hypothesis---that
-is, that the expected and observed round win rates, \(\hat{\Phi}(r)\)
-and \(\Phi(r)\) respectively, are equal to one another---we can compute
-the chi-square goodness of fit statistic
+To evaluate the constant round win probability hypothesis, we can
+compute the test statistic
 
 \begin{equation}\label{eq:chi-squ}
-\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)},
+\chi^2 = \sum_{r \in R} \frac{(\Phi(r) - \hat{\Phi}(r))^2}{\hat{\Phi}(r)}
 \end{equation}
 
-in which \(R = [6, 7, 8, 9, 10, 11]\) for CoD SnD.
+in which \(\hat{\Phi}(r)\) and \(\Phi(r)\) represent the expected and
+observed round win proportions respectively, and
+\(R = [6, 7, 8, 9, 10, 11]\) for CoD SnD. The null hypothesis is that
+the test statistic is chi-squared distributed, where the number of
+degrees of freedom is \(\vert R \vert -1 = 5\) for Cod SnD. We reject
+the null hypothesis if \(\chi^2 > \chi^2_{1-\alpha,\vert R \vert -1}\),
+where \(\chi^2_{1-\alpha,\vert R \vert -1}\) is the chi-square critical
+value with \(\vert R \vert -1\) degree of freedom and siginficance level
+\(\alpha\).
 
@@
 
-Let us now consider round win rate immediately following a streak of
-\(k\) wins, given that the series lasts \(r\) rounds. Removing our
+Let us now consider round win proportions immediately following a streak
+of \(k\) wins, given that the series lasts \(r\) rounds. Removing our
 knowledge of a streak, we might model the Bernoulli round win
@@
 
-As shown by MS with their Theorem 1, we should expect the proportion of
-round wins immediately following a streak of \(k\) rounds wins for a
-series lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly
-less than \(p^{+|r}\).\footnote{See Appendix E.1 of MS for the proof.}
-Unfortunately, there does not exist a closed form representation for the
-expected value of \(\hat{P}^{+|k,r}_{MS}\) for \(k > 1\). Nonetheless,
-one may run simulations to estimate the expected value, as we choose to
-do.\footnote{We have adapted the code from Vafa (2017), which implements
-  MS's framework (2018).}
+As implied by MS's Theorem 1, we should expect the proportion of round
+wins immediately following a streak of \(k\) rounds wins for a series
+lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
+\(p^{+|r}\).\footnote{Unfortunately, there does not exist a closed form
+  representation for the expected value of \(\hat{P}^{+|k,r}_{MS}\) for
+  \(k > 1\). Nonetheless, one may run simulations to estimate the
+  expected value, as we choose to do. We have adapted the code from Vafa
+  (2017), which implements MS's framework (2018).}
 
-Although one might be tempted to mirror the hypothesis testing for
-difference of proportions performed by MS (and GVT), our context is
-fundamentally different from that of MS, who focus on longitudinal data
-in controlled settings.\footnote{GVT also perform statistical tests on
+Although one might be tempted to mirror the equal proportions hypothesis
+testing performed by MS, our context is fundamentally different from
+that of MS, who focus on longitudinal data in controlled settings,
+unaffected by opposition.\footnote{GVT also perform statistical tests on
   shots from players in live games, i.e.~``observational'' data, but
@@
 number of possible rounds (\(s\)) and whether or not the team wins the
-series. The Bernoulli trial success probability, i.e.~the single round
-win rate in CoD SnD, is not independent of the opponent. Consequently, a
-statistical test of the difference in \(\hat{P}^{+|k,r}\) and
+series. The Bernoulli trial success probability, i.e.~single round win
+percentage in CoD SnD, is not independent of the opponent. Consequently,
+a statistical test of the difference in \(\hat{P}^{+|k,r}\) and
 \(\hat{P}^{-|kr}\), as performed by MS to evaluate their hypothesis
@@
 
-We can perform a binomial test to evaluate the null hypothesis
-\(\omega = \omega_0\) for the observed probability of success \(\omega\)
-and a user-specified \(\omega_0\) (where \(0 \leq \omega_0 \leq 1\)). If
-there are \(r^+\) observed successes in a sample of \(r\) trials and we
-expect that there should be \(r * \omega_0\), the probability of
-arriving at this expected number of successes is
+We can perform a two-tailed binomial test to evaluate the null
+hypothesis \(\omega = \omega_0\) for the observed probability of success
+\(\omega\) and a user-specified \(\omega_0\) (where
+\(0 \leq \omega_0 \leq 1\)). If there are \(r^+\) observed successes in
+a sample of \(r\) trials and we expect that there should be
+\(r * \omega_0\), the probability of arriving at this expected number of
+successes is
 
@@
 probabilities), we can evaluate the null hypothesis that the observed
-probability is equal to the notional probability. If we can reject this
-null hypothesis, then we can consider team momentum, represented by
-post-streak success, plausible.
+proportion of post-streak round wins is equal to the notional
+proportion, given streak length \(k\) and series length \(r\). If we can
+reject this null hypothesis, then we can consider team momentum,
+represented by post-streak success, plausible.
 
-One can perform the same binomial test for the MS's
-streak-selection-adjusted proportion,
-\(\hat{P}^{+|k,r}_{MS}\).\footnote{Given the caveats mentioned before,
-  these results should be heeded with caution.}
+As a reference, we can perform the same binomial test for the MS's
+streak-selection-adjusted proportion, \(\hat{P}^{+|k,r}_{MS}\). However,
+given the caveats mentioned before regarding applying MS's theorem to
+our setting, the results of such binomial tests should be heeded with
+caution.
 
@@
 
-Again, we caapply a binomial test to evaluate the hypothesis that the
+Again, we can apply a binomial test to evaluate the hypothesis that the
 expected proportions, \(\hat{P}^{+|k,r,i}_0\) and
@@
 
-Stepping back from the one-sided perspective of a single team's round
+Stepping back from the (one-sided) perspective of a single team's round
 win probability when streaking, one can attempt to detect the hot hand
-phenomenon with a Wald-Wolfowitz runs test. Under the null hypothesis,
-the number of runs in a sequence of \(r\) trials, \(\zeta(r)\), is a
-random variable that can take on values \(r^+\) and \(r^- = r - r^+\)
-for the number of success and failure respectively, with the following
-mean \(\mu\) and variance \(\sigma^2\):
+phenomenon more broadly with a Wald-Wolfowitz runs test. Under the null
+hypothesis, the number of runs in a sequence of \(r\) trials is a random
+variable that can take on values \(+\) or \(-\) and arrive at \(r^+\)
+successes (\(r^- = r - r^+\) failures), with the following mean \(\mu\)
+and variance \(\sigma^2\):
 
@@
 
-One can subset the observed series sequences to those that violate the
-null hypothesis for the run test and perform a test of equal
-proportions, where the null is that the observed proportion of a
+One can subset the observed series sequences, \(\zeta(r)\), to those
+that violate the null hypothesis for the runs test and perform a test of
+equal proportions, where the null is that the observed proportion of a
 sequence relative to all possible sequences, \(P(\zeta) = P^\zeta\), is
@@
 
-and where \(N^\zeta\) is the observed number of sequences,
-\(\hat{N}^\zeta\) is the expected number of sequences. If we can reject
-the null hypothesis for such sequences, then there is implicit evidence
-in favor of the hot hand.
+and where \(N^\zeta\) and \(\hat{N}^\zeta\) are the observed and
+expected number of sequences respectively. The null hypothesis is that
+\(z\) is normally distributed. If \(z > +z_{(1-\alpha)/2}\) or
+\(z < -z_{(1-\alpha)/2}\) for critical values at a significance level
+\(\alpha\), we can reject the null hypothesis for such sequences and
+build an argument in support of the hot hand effect.
 
@@
 \section{Results}\label{results}}
-
-First, we investigate the constant probability assumption and the
-distribution of rounds played in a series. Chance's work is closely
-related to our, and, in fact, provides a guide for this investigation.
-Afterwards, We investigate post-streak win rates, referring to work from
-MS. We finish with a brief look at sequences of round wins violating the
-Wald-Wolfowitz runs test, and whether such observed sequences occur more
-frequently than expected.
 
@@
 \(\chi^2\) value for which we cannot reject the constant probability
-null hypothesis.
+null hypothesis. Note that rejection of the null hypothesis is the
+baseline and failure to reject the null is the non-trivial result,
+contrary to most statistical analysis.
 
@@
 
-Observing that \(\hat{\Phi}_2(r)\) reasonably matches \(\Phi(r)\)
-(especially in comparison to \(\hat{\Phi}_0(r)\)), along with the null
-hypothesis rejection shown in Table \ref{tbl:mosteller-methods-results},
-we can say that the constant round win probability assumption is valid
-in CoD SnD series with the appropriate choice of \(\phi\)
-(\(\approx 0.575\)).
+Observing that the null hypothesis acceptance shown in Table
+\ref{tbl:mosteller-methods-results}, along with the observation that
+\(\hat{\Phi}_2(r)\) reasonably matches \(\Phi(r)\) (in comparison to
+\(\hat{\Phi}_0(r)\)), we can say that the constant round win probability
+assumption is valid in CoD SnD series with the appropriate choice of
+\(\phi\) (\(\approx 0.575\)).
 
@@
 \(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\) respectively, with
-the observed round win rate, \(P^{+|kr}\), following streaks of \(k=3\)
-round wins given the series outcome.
+the observed round win proportion, \(P^{+|kr}\), following streaks of
+\(k=3\) round wins given the series outcome.
 
@@
 the null hypothesis that the expected notional and MS post-streak round
-win rates are different than the observed proportion. However, after
-adjusting the \(p\)-values with the Benjamini and Yekutieli (BY)
+win proportions are different than the observed proportion. However,
+after adjusting the \(p\)-values with the Benjamini and Yekutieli (BY)
 correction (2001), the null hypothesis cannot be rejected for any
@@
 Now let us explicitly consider the round, \(i\). As shown in Table
-\ref{tbl:pw3ri}, the notional win rate in the round \(i\) immediately
-following a streak of \(k\) round wins in a series lasting \(r\) rounds,
-\(\hat{P}{+|k,r,i}_0\), is statistically different than the observed
-\(P^{+|k,r,i}\) in several cases, notably when \(r = i\) for each of
-\(r \in [9, 10, 11]\).\footnote{The null can also be rejected for
-  \(r \in [7, 8]\), although these are not shown, and the sample sizes
-  are smaller.} Interestingly, the observed rate is greater than the
-expected rate in each case where we can reject the null hypothesis,
-whereas the observed rate is less than the expected rate in all other
-cases, as well in a strong majority of cases not shown.
+\ref{tbl:pw3ri}, the notional win proportion in the round \(i\)
+immediately following a streak of \(k\) round wins in a series lasting
+\(r\) rounds, \(\hat{P}{+|k,r,i}_0\), is statistically different than
+the observed \(P^{+|k,r,i}\) in several cases, notably when \(r = i\)
+for each of \(r \in [9, 10, 11]\).\footnote{The null can also be
+  rejected for \(r \in [7, 8]\), although these are not shown, and the
+  sample sizes are smaller.} Interestingly, the observed rate is greater
+than the expected rate in each case where we can reject the null
+hypothesis, whereas the observed rate is less than the expected rate in
+all other cases, as well in a strong majority of cases not shown.
 
@@
 the failure to reject the binomial null hypothesis for post-streak win
-rates; and (3) the failure to reject the equal proportions null
+proportions; and (3) the failure to reject the equal proportions null
 hypothesis for streaky round sequences identified by the Wald-Wolfowitz
@@
 
-For the sake of brevity, we did not delve into win rates and streaks
-split by offensive or defensive role. For example, it would be
-interesting to look at whether the round win rate is higher after a
-streaks of three round wins when the team starts the streak as the
-offensive team. This would mean that, in the round immediately following
-the latest streak win, the streaking team would be playing defense,
-where teams are slightly more likely to win on average. On the other
-hand, streaks of three starting with an offensive round
-win---theoretically, knowing that \(\tau_O\) = 47.7\%, the expected
-frequency is \(\tau_O^2 (1 - \tau_O) \approx\) 11.9\%---are likely to
-occur less frequently than such streaks starting with a defensive
-win---\(\tau_O (1 - \tau_O)^2 \approx\) 13.0\%---so we would want to
-account for sample size differences.
+For the sake of brevity, we did not account for offensive or defensive
+role when considering win proportions during streaks. For example, it
+would be interesting to look at whether the round win percentage is
+higher after a streaks of three round wins when the team starts the
+streak as the offensive team. This would mean that, in the round
+immediately following the latest streak win, the streaking team would be
+playing defense, where teams are slightly more likely to win on average.
+On the other hand, streaks of three starting with an offensive round
+win---theoretically, knowing that \(\bar{\tau}_O\) = 47.7\%, the
+expected frequency is \(\bar{\tau}_O^2 (1 - \bar{\tau}_O) \approx\)
+11.9\%---are likely to occur less frequently than such streaks starting
+with a defensive win---\(\bar{\tau}_O (1 - \bar{\tau}_O)^2 \approx\)
+13.0\%---so we would want to account for sample size differences.
 

### 2022-08-25 paper/paper.Rmd
anonymize

@@
 authors:
-  - name: Tony ElHabr
-    email: anthonyelhabr@gmail.com
-    url: https://tonyelhabr.rbind.io
-  - name: Andrew ElHabr
-    email: andrewelhabr@gatech.edu
-    affiliation: Georgia Institute of Technology
-    department: School of Industrial and Systems Engineering (ISyE)
-    location: Atlanta, Georgia, USA
+  - name: Person One
+    email: personone@domain.com
+  - name: Person Two
+    email: persontwo@domain.com
 abstract: |

### 2022-08-25 paper/paper.tex
anonymize

@@
 \author{
-    Tony ElHabr
+    Person One
    \\
@@
    \\
-  \texttt{\href{mailto:anthonyelhabr@gmail.com}{\nolinkurl{anthonyelhabr@gmail.com}}} \\
+  \texttt{\href{mailto:personone@domain.com}{\nolinkurl{personone@domain.com}}} \\
    \And
-    Andrew ElHabr
+    Person two
    \\
-    School of Industrial and Systems Engineering (ISyE) \\
-    Georgia Institute of Technology \\
-  Atlanta, Georgia, USA \\
-  \texttt{\href{mailto:andrewelhabr@gatech.edu}{\nolinkurl{andrewelhabr@gatech.edu}}} \\
+     \\
+   \\
+  \texttt{\href{mailto:persontwo@domain.com}{\nolinkurl{persontwo@domain.com}}} \\
   }

### 2022-08-25 paper/paper.Rmd
anonymize

@@
     email: personone@domain.com
-  - name: Person Two
+  - name: Person two
     email: persontwo@domain.com

### 2022-08-26 paper/paper.Rmd
thursday morning review

--- 2022-08-25 paper/paper.Rmd
@@
   arrange(n_rounds)
+
+cod_rounds |> 
+  filter(round == 1) |> 
+  count(game, team, is_offense) |> 
+  group_by(game, team) |> 
+  mutate(prop = n / sum(n)) |> 
+  ungroup() |>
+  filter(is_offense) %>% 
+  arrange(-prop)
 ```
@@
 2.  The offensive team eliminates all members of the defensive team after a bomb plant. (Offense wins.)
-3.  The defense defuses the bomb after a bomb plant.[^4] (Defense wins.)
+3.  The defense defuses the bomb after a bomb plant. (Defense wins.)
 4.  The offense does not make a plant by the time the round timer ends. (Defense wins.)
-
-[^4]: Often the defensive team will try to eliminate all team members prior to making the defuse, but in some cases, they may try to "ninja" defuse.
 
@@
 
-We note that SnD is not the only game mode played in competitive CoD.[^5] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes.
+We note that SnD is not the only game mode played in competitive CoD.[^4] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes.
 The best-of-five matchup could also be called a "series", but since we analyze only the SnD games, we refer to the SnD games as series.
 
-[^5]: Hardpoint has been played as the first and fourth maps in a matchup. The variant for the third map was Domination in the 2020 season, and Control in the 2021 and 2022 seasons.
+[^4]: Hardpoint has been played as the first and fourth game modes in a matchup. The third game mode was Domination in the 2020 season, and Control in the 2021 and 2022 seasons.
 
@@
 
-CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), operating since 2020.
-The CDL has completed three year-long "seasons" as of August 2022.[^6]
-
-[^6]: CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, with releases coming in the late fall.
+The data set consists of all SnD matches played in major tournaments and qualifiers during the past three years[^5], totaling 7,792 rounds across 852 series.[^6] Data has been collected in spreadsheets by community member "IOUTurtle".[^7]
+
+[^5]: CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), operating since 2020.
+The CDL has completed three year-long "seasons" as of August 2022.
+
+    CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, with releases coming in the late fall.
 A new game under the same brand---Call of Duty---is published every year by a rotating set of developers.
@@
 
-The data set consists of all SnD matches played in major tournaments and qualifiers during the CDL era, totaling 7,792 rounds across 852 series.[^7] Data has been collected in spreadsheets by community member "IOUTurtle".[^8]
-
-[^7]: 288 of the series occur in major tournaments, which are considered to be more competitive than the qualifiers since they are played in person (COVID-permitting), eliminating randomness due to online latency and ping.
+[^6]: 288 of the series occur in major tournaments, which are considered to be more competitive than the qualifiers since they are played in person (COVID-permitting), eliminating randomness due to online latency and ping.
 The qualifiers are played online.
 
-[^8]: Raw data: <https://linktr.ee/CDLArchive>. Author: <https://twitter.com/IOUTurtle>. Our clean data can be found at <https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv>.
-
-6-0 sweeps make up 4.7% of all series, while 6-5 series make up 23.7% of series.
-The observed offensive round win percentage across all rounds is $\bar{\tau}_O$ = 47.8%.[^9] Table \ref{tbl:o-win-prop-by-series-state} shows offensive round win percentages by series "state", i.e.
+[^7]: Raw data: <https://linktr.ee/CDLArchive>. Cleaned data: <https://github.com/%7Bauthor%7D/%7Brepo%7D/blob/master/data/%7Bfile%7D.csv>.
+
+Sweeps (6-0 series) make up 4.7% of all series, while 6-5 series make up 23.7% of series.
+The observed offensive round win percentage across all rounds is $\bar{\tau}$ = 47.8%.[^8] Table \ref{tbl:o-win-prop-by-series-state} shows offensive round win percentages by series "state", i.e.
 the number of round wins by each team prior to an upcoming round.
-Offensive round win percentage is not quite constant, although never veers more than 10% from $\bar{\tau}_O$.
-
-[^9]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
+Offensive round win percentage is not quite constant, although never veers more than 10% from $\bar{\tau}$.
+
+[^8]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
 
@@
 
-\caption{Offensive round win percentage for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses indicate sample sizes.}
+\caption{Offensive round win percentage (\%) for the upcoming round, given both the offensive and defensive team's prior number of round wins. Numbers in parentheses indicate sample sizes.}
 
@@
 
-0 & 47.8\%(852) & 46.6\%(408) & 43.1\%(216) & 43.5\%(115) & 43.3\%(67)  & 40.5\%(37)  \\
-1 & 48.6\%(444) & 49.3\%(418) & 51.5\%(309) & 43.4\%(205) & 43.3\%(120) & 39.4\%(99)  \\
-2 & 52.8\%(218) & 48.9\%(305) & 48.9\%(315) & 46.6\%(262) & 48.7\%(189) & 42.1\%(133) \\
-3 & 54.5\%(123) & 46.0\%(200) & 49.6\%(250) & 45.6\%(248) & 44.4\%(214) & 44.8\%(174) \\
-4 & 56.9\%(65)  & 54.5\%(145) & 47.2\%(193) & 44.7\%(228) & 55.2\%(221) & 50.5\%(208) \\
-5 & 47.4\%(38)  & 49.4\%(83)  & 47.1\%(136) & 50.9\%(175) & 45.2\%(177) & 46.0\%(202) \\
+0 & 47.8 (852) & 46.6 (408) & 43.1 (216) & 43.5 (115) & 43.3 (67)  & 40.5 (37)  \\
+1 & 48.6 (444) & 49.3 (418) & 51.5 (309) & 43.4 (205) & 43.3 (120) & 39.4 (99)  \\
+2 & 52.8 (218) & 48.9 (305) & 48.9 (315) & 46.6 (262) & 48.7 (189) & 42.1 (133) \\
+3 & 54.5 (123) & 46.0 (200) & 49.6 (250) & 45.6 (248) & 44.4 (214) & 44.8 (174) \\
+4 & 56.9 (65)  & 54.5 (145) & 47.2 (193) & 44.7 (228) & 55.2 (221) & 50.5 (208) \\
+5 & 47.4 (38)  & 49.4 (83)  & 47.1 (136) & 50.9 (175) & 45.2 (177) & 46.0 (202) \\
 
@@
 ```
-At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series, played as the second or fifth game mode of the best-of-five matchup.
-Their opponent is assigned to start on offense in the SnD slot not chosen.[^10] Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers.
+
+The professional competition format balances the frequency with which teams play offense or defense to start a series, to the extent possible.
+Thus, win percentages in certain states are subjected to minimal selection bias, i.e.
+bias due to better teams playing defense more frequently.[^9]
+
+[^9]: At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series, played as the second or fifth game mode of the best-of-five matchup.
+Their opponent is assigned to start on offense in the SnD slot not chosen.
+Anecdotally, the better team tends to choose to play defense in the first round of the SnD series played as the second game mode in the best-of-five matchup, although this choice is not consistent across teams, or even with the same team over time.
+
+    Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers.
 Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team, despite their win-loss records.
-Overall, we can argue that potential bias due to stronger teams playing defense---or, offense, if offense happens to be generally advantageous for a given map---is very minimal.
-
-[^10]: Anecdotally, the higher-seeded teams tend to choose to play defense in the first round of the SnD series played as the second game mode in the best-of-five matchup, although this choice is not consistent across teams, or even with the same team over time.
 
@@
 
-The concept of momentum goes hand-in-hand with a discussion of the nature of series outcomes.[^11] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
+The concept of momentum goes hand-in-hand with a discussion of the nature of series outcomes.[^10] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^11]: We often use "streaks" and momentum interchangeably, but as Steeger et al. ([-@steeger2021]) note, momentum implies dependence between events, whereas streaking does not.
+[^10]: We often use "streaks" and momentum interchangeably, but as Steeger et al. [-@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 2021).
-Peel and Clauset found no evidence for unlikely sequences of scoring events in the NHL, College Football (CFB), and National Football League (NFL), but did in the NBA.
+Peel and Clauset found no evidence for unlikely sequences of scoring events in the NHL, College Football, and National Football League, although did in the NBA.
 As a check on their entropy approach to momentum identification, Steeger et al.
-found several NHL teams with sequence of wins in the 2018-2019 regular season that violated the Wald-Wolfowitz null hypothesis.
+found several NHL teams with sequences of wins in the 2018-2019 regular season that violated the Wald-Wolfowitz null hypothesis.
 
@@
 Teams play either offense or defense for many consecutive rounds.
-(The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^12] While theoretically one might be able to account for inter-round win percentage relationships in any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
+(The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^11] While theoretically one might be able to account for inter-round win percentage relationships in any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
 Bernoulli trials.
-3.  Both Counter-Strike and Valorant have overtime rules---team must win by two rounds---which can make end-of-series sequences difficult to model properly. CoD SnD does not have overtime rules.
-
-[^12]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each.
+3.  Both Counter-Strike and Valorant have overtime rules---a team must win by two rounds---which can make end-of-series sequences difficult to model properly. CoD SnD does not have overtime rules.
+
+[^11]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each.
 
@@
 While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation of a concept like the hot-hand fallacy in a sport where it has not yet been invetigated---particularly one that is less subjected to factors that may be difficult to control for, e.g.
-weather---should be useful as a precedent or supplement for future researchers.
+weather---should be useful as an inspiration for future researchers.
 
@@
 
-In a best-of-$s$ format, assuming a constant round win probability $\phi$[^13] (where $0 \leq \phi \leq 1$) for one team[^14], the expected proportion of series ending in $r$ rounds ($r \leq s$) is given by Equation \ref{eq:series-length}.
-
-[^13]: If $\phi > 0.5$, we can say that this is the stronger team.
-
-[^14]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
+In a best-of-$s$ format, assuming a constant round win probability $\phi$ (where $0 \leq \phi \leq 1$)[^12] for one team[^13], the expected proportion of series ending in $r$ rounds ($r \leq s$) is given by Equation \ref{eq:series-length}.
+
+[^12]: If $\phi > 0.5$, we can say that this is the stronger team.
+
+[^13]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
 Upper-case symbol, e.g.
@@
 ```
-For example, assuming $\phi = 0.5$, the probability of a series ending in nine rounds in CoD SnD, where $s=11$, is
+For example, assuming $\phi = 0.5$, the probability of a series ending in exactly nine rounds in CoD SnD, where $s=11$ (implying $m=6$), is
 
@@
 The null hypothesis is that the test statistic is chi-squared distributed, where the number of degrees of freedom is $\vert R \vert -1 = 5$ for Cod SnD.
-We reject the null hypothesis if $\chi^2 > \chi^2_{1-\alpha,\vert R \vert -1}$, where $\chi^2_{1-\alpha,\vert R \vert -1}$ is the chi-square critical value with $\vert R \vert -1$ degree of freedom and siginficance level $\alpha$.
 
@@
 \begin{equation}\label{eq:pwr}
-p_0(\text{win} | r) = p^{+|r}_0 = \begin{cases} 
+p_0(\text{win} | r) = p^{+|r}_0 := \begin{cases} 
   \frac{m}{r} & \text{team wins series}, \\ 
@@
 ```
-using $m$ from Equation \ref{eq:m}.
-
-As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.[^15]
-
-[^15]: Unfortunately, there does not exist a closed form representation for the expected value of $\hat{P}^{+|k,r}_{MS}$ for $k > 1$.
-Nonetheless, one may run simulations to estimate the expected value, as we choose to do.
-We have adapted the code from Vafa [-@vafa2017], which implements MS's framework [-@miller2018].
-
-Although one might be tempted to mirror the equal proportions hypothesis testing performed by MS, our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^16] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
+for $r \in R$ and $m$ from Equation \ref{eq:m}.
+
+As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.
+Although one might be tempted to mirror the equal proportions hypothesis testing performed by MS, our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^14] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
 The Bernoulli trial success probability, i.e.
@@
 
-[^16]: GVT also perform statistical tests on shots from players in live games, i.e.
-"observational" data, but they note that their findings are likely affected player shot selection in the face of defensive strategy by the opposing team.
+[^14]: GVT also perform statistical tests on shots from players in live games, i.e.
+"observational" data, but they note that their findings are likely affected by player shot selection in the face of defensive strategy by the opposing team.
 
@@
 \begin{equation}\label{eq:pwkr}
-p_0(\text{win} | k, r) = p^{+|k,r}_0 = \begin{cases}
+p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
   \frac{m - k}{r - k} & \text{team wins series}, \\
@@
 ```
-using $m$ from Equation \ref{eq:m}.
+for $r \in R$ and $m$ from Equation \ref{eq:m}.
 
@@
 \begin{equation}\label{eq:binom}
-\Pr(r^w) = {\binom {r}{r^+}} \omega^{r^+}(1-\omega)^{r-r^+}.
+\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r-r^+}.
 \end{equation}
@@
 The null hypothesis is that $z$ is normally distributed.
-If $z > +z_{(1-\alpha)/2}$ or $z < -z_{(1-\alpha)/2}$ for critical values at a significance level $\alpha$, we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.
+If $z > +z_{(1-\alpha)/2}$ or $z < -z_{(1-\alpha)/2}$ at a significance level $\alpha$, we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.
 
@@
 ```
-Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^17] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
+Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^15] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
 $\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
 
-[^17]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+[^15]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^18] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
-
-[^18]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^16] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
+
+[^16]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
 
@@
 With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win proportions are different than the observed proportion.
-However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^19]
-
-[^19]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
+However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^17]
+
+[^17]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
 
 When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the binomial null hypothesis for the expected notional proportion $\hat{P}^{+|k,r}_0$ (even before the BY p-value correction).
-The null hypothesis can only be rejected for the expected MS proportion $\hat{P}^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^20]
-
-[^20]: At 36, the sample size for $k = 5, r = 7$ is not as large as most other combinations of $k$ and $r$.
+The null hypothesis can only be rejected for the expected MS proportion $\hat{P}^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^18]
+
+[^18]: At 36, the sample size for $k = 5, r = 7$ is not as large as most other combinations of $k$ and $r$.
 
@@
 Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:pw3ri}, the notional win proportion in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^21] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
-
-[^21]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
+As shown in Table \ref{tbl:pw3ri}, the notional win proportion in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^19] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
+
+[^19]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
 
@@
 #| label: cod_round_arrangements
-
 simulate_cod_round_arrangements <- function(p = 0.5, n_sims = 10000, seed = 42) {
@@
   w <- sample(c(0, 1), size = MAX_COD_ROUND * n_sims, replace = TRUE, prob = c(1 - p, p))
-  m <- matrix(w, nrow = n_sims, ncol = n_rounds_max)
-  # data.frame(x)
+  m <- matrix(w, nrow = n_sims, ncol = MAX_COD_ROUND)
   df <- as_tibble(m)
-  names(df) <- sprintf('%d', 1:n_rounds_max)
+  names(df) <- sprintf('%d', 1:MAX_COD_ROUND)
   df$i <- 1:nrow(df)
@@
   sim_rounds <- tibble(
-    i = rep(1:n_sims, each = n_rounds_max),
-    r = rep(1:n_sims, times = n_rounds_max),
+    i = rep(1:n_sims, each = MAX_COD_ROUND),
+    r = rep(1:n_sims, times = MAX_COD_ROUND),
     w = w
@@
     ) |> 
-    filter(cumu_wl_max <= 6)
+    filter(cumu_wl_max <= COD_WIN_THRESHOLD)
 
@@
     sim_rounds |> 
-      filter(cumu_wl_max == 6L),
+      filter(cumu_wl_max == COD_WIN_THRESHOLD),
     sim_rounds |> 
-      filter(cumu_wl_max == 6L) |> 
+      filter(cumu_wl_max == COD_WIN_THRESHOLD) |> 
       group_by(i) |> 
@@
       sim_rounds |> 
-        filter(cumu_wl_max == 6) |> 
+        filter(cumu_wl_max == COD_WIN_THRESHOLD) |> 
         mutate(
@@
       across(w, ~ifelse(zeros_win, abs(1 - .x), .x))
+      # across(w, ~ifelse(zeros_win, '-', '+'))
     )
@@
       cumu_l = max(cumu_l),
-      ws = paste0(w, collapse = '-')
+      ws = paste0(w, collapse = ' ')
     ) |> 
@@
     mutate(
-      wins = ifelse(cumu_w == 6, cumu_w, cumu_l),
-      losses = ifelse(cumu_w == 6, cumu_l, cumu_w),
+      wins = ifelse(cumu_w == COD_WIN_THRESHOLD, cumu_w, cumu_l),
+      losses = ifelse(cumu_w == COD_WIN_THRESHOLD, cumu_l, cumu_w),
       n_rounds = wins + losses
@@
 
-In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^22] at a confidence level of $\alpha = 0.05$, for $r \in [8, 9, 10]$.
+In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^20] at a confidence level of $\alpha = 0.05$, for $r \inf [8, 9, 10]$.
 In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.
 
-[^22]: If we used $\phi = 0.5$, we would get the same exact seqeunces.
+[^20]: If we used $\phi = 0.5$, we would get the same exact sequences.
 
@@
 
-For the sake of brevity, we did not account for offensive or defensive role when considering win proportions during streaks.
+For the sake of brevity, we did not account for offensive or defensive role when considering win proportions in the rounds immediately following streaks.
 For example, it would be interesting to look at whether the round win percentage is higher after a streaks of three round wins when the team starts the streak as the offensive team.
-This would mean that, in the round immediately following the latest streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round win---theoretically, knowing that $\bar{\tau}_O$ = 47.7%, the expected frequency is $\bar{\tau}_O^2 (1 - \bar{\tau}_O) \approx$ 11.9%---are likely to occur less frequently than such streaks starting with a defensive win---$\bar{\tau}_O (1 - \bar{\tau}_O)^2 \approx$ 13.0%---so we would want to account for sample size differences.
+This would mean that, in the round immediately following the last streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average.
+On the other hand, streaks of three starting with an offensive round win are less likely to occur than such streaks starting with a defensive win-$\bar{\tau}^2 (1 - \bar{\tau}) \approx$ 11.9% in the former case and $\bar{\tau} (1 - \bar{\tau})^2 \approx$ 13.0% in the latter case---so we would need to properly account for sample size differences.
 
@@
 
-Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.[^23] R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
+Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.
+R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
 While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.
-
-[^23]: <https://twitter.com/R11stats>
 

### 2022-08-26 paper/paper.tex
render Two
thursday morning review

@@
    \And
-    Person two
+    Person Two
    \\
@@
 
-\usepackage{longtable}
 \usepackage{amsmath}
@@
 \item
-  The defense defuses the bomb after a bomb plant.\footnote{Often the
-    defensive team will try to eliminate all team members prior to
-    making the defuse, but in some cases, they may try to ``ninja''
-    defuse.} (Defense wins.)
+  The defense defuses the bomb after a bomb plant. (Defense wins.)
 \item
@@
 We note that SnD is not the only game mode played in competitive
-CoD.\footnote{Hardpoint has been played as the first and fourth maps in
-  a matchup. The variant for the third map was Domination in the 2020
+CoD.\footnote{Hardpoint has been played as the first and fourth game
+  modes in a matchup. The third game mode was Domination in the 2020
   season, and Control in the 2021 and 2022 seasons.} Teams play in a
@@
 
-CoD has roughly gone through three eras of professional gaming: (1)
-Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World
-League (CWL), initiated in 2016; and (3) the 12-franchise CoD League
-(CDL), operating since 2020. The CDL has completed three year-long
-``seasons'' as of August 2022.\footnote{CoD is fairly unique compared to
-  other esports in that it runs on an annual lifecycle, with releases
-  coming in the late fall. A new game under the same brand---Call of
-  Duty---is published every year by a rotating set of developers. Each
-  new game bears resemblance to past ones, often introducing relatively
-  small variations (``improvements'') to graphics, game modes, and other
-  facets of gameplay. During the CDL era, the games released have been
-  Modern Warfare (2020), Cold War (2021) and Vanguard (2022).}
+The data set consists of all SnD matches played in major tournaments and
+qualifiers during the past three years\footnote{CoD has roughly gone
+  through three eras of professional gaming: (1) Major League Gaming
+  (MLG) tournaments prior to 2016; (2) the CoD World League (CWL),
+  initiated in 2016; and (3) the 12-franchise CoD League (CDL),
+  operating since 2020. The CDL has completed three year-long
+  ``seasons'' as of August 2022.
 
-The data set consists of all SnD matches played in major tournaments and
-qualifiers during the CDL era, totaling 7,792 rounds across 852
+  CoD is fairly unique compared to other esports in that it runs on an
+  annual lifecycle, with releases coming in the late fall. A new game
+  under the same brand---Call of Duty---is published every year by a
+  rotating set of developers. Each new game bears resemblance to past
+  ones, often introducing relatively small variations (``improvements'')
+  to graphics, game modes, and other facets of gameplay. During the CDL
+  era, the games released have been Modern Warfare (2020), Cold War
+  (2021) and Vanguard (2022).}, totaling 7,792 rounds across 852
 series.\footnote{288 of the series occur in major tournaments, which are
@@
 ``IOUTurtle''.\footnote{Raw data: \url{https://linktr.ee/CDLArchive}.
-  Author: \url{https://twitter.com/IOUTurtle}. Our clean data can be
-  found at
-  \url{https://github.com/tonyelhabr/fps_round_games/blob/master/data/cod_rounds.csv}.}
+  Cleaned data:
+  \url{https://github.com/\%7Bauthor\%7D/\%7Brepo\%7D/blob/master/data/\%7Bfile\%7D.csv}.}
 
-6-0 sweeps make up 4.7\% of all series, while 6-5 series make up 23.7\%
-of series. The observed offensive round win percentage across all rounds
-is \(\bar{\tau}_O\) = 47.8\%.\footnote{Offensive round win percentage
-  has been nearly constant across the three games during the CDL era: 1.
-  47.2\% in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\% in Vanguard
-  (2022)} Table \ref{tbl:o-win-prop-by-series-state} shows offensive
-round win percentages by series ``state'', i.e.~the number of round wins
-by each team prior to an upcoming round. Offensive round win percentage
-is not quite constant, although never veers more than 10\% from
-\(\bar{\tau}_O\).
+Sweeps (6-0 series) make up 4.7\% of all series, while 6-5 series make
+up 23.7\% of series. The observed offensive round win percentage across
+all rounds is \(\bar{\tau}\) = 47.8\%.\footnote{Offensive round win
+  percentage has been nearly constant across the three games during the
+  CDL era: 1. 47.2\% in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\%
+  in Vanguard (2022)} Table \ref{tbl:o-win-prop-by-series-state} shows
+offensive round win percentages by series ``state'', i.e.~the number of
+round wins by each team prior to an upcoming round. Offensive round win
+percentage is not quite constant, although never veers more than 10\%
+from \(\bar{\tau}\).
 
@@
 
-At tournaments, higher-seeded (``better'') teams choose whether they
-want to start on offense in the SnD series, played as the second or
-fifth game mode of the best-of-five matchup. Their opponent is assigned
-to start on offense in the SnD slot not chosen.\footnote{Anecdotally,
-  the higher-seeded teams tend to choose to play defense in the first
-  round of the SnD series played as the second game mode in the
+The professional competition format balances the frequency with which
+teams play offense or defense to start a series, to the extent possible.
+Thus, win percentages in certain states are subjected to minimal
+selection bias, i.e.~bias due to better teams playing defense more
+frequently.\footnote{At tournaments, higher-seeded (``better'') teams
+  choose whether they want to start on offense in the SnD series, played
+  as the second or fifth game mode of the best-of-five matchup. Their
+  opponent is assigned to start on offense in the SnD slot not chosen.
+  Anecdotally, the better team tends to choose to play defense in the
+  first round of the SnD series played as the second game mode in the
   best-of-five matchup, although this choice is not consistent across
-  teams, or even with the same team over time.} Outside of tournaments,
-teams all play each other twice throughout the season, constituting
-qualifiers. Each team gets to play the higher-seeded role once in their
-head-to-head matchups with a given team, despite their win-loss records.
-Overall, we can argue that potential bias due to stronger teams playing
-defense---or, offense, if offense happens to be generally advantageous
-for a given map---is very minimal.
+  teams, or even with the same team over time.
+
+  Outside of tournaments, teams all play each other twice throughout the
+  season, constituting qualifiers. Each team gets to play the
+  higher-seeded role once in their head-to-head matchups with a given
+  team, despite their win-loss records.}
 
@@
 nature of series outcomes.\footnote{We often use ``streaks'' and
-  momentum interchangeably, but as Steeger et al.~((2021)) note,
-  momentum implies dependence between events, whereas streaking does
-  not.} Two opposing fallacies are observed in the context of momentum:
-the ``gambler's fallacy'' (negative recency) and the ``hot hand
-fallacy'' (positive recency). Per Ayton et al. (2004), negative recency
-is ``the belief that, for random events, runs of a particular outcome
-\ldots{} will be balanced by a tendency for the opposite outcome'',
-while positive recency is the expectation of observing future results
-that match recent results.
+  momentum interchangeably, but as Steeger et al. (2021) note, momentum
+  implies dependence between events, whereas streaking does not.} Two
+opposing fallacies are observed in the context of momentum: the
+``gambler's fallacy'' (negative recency) and the ``hot hand fallacy''
+(positive recency). Per Ayton et al. (2004), negative recency is ``the
+belief that, for random events, runs of a particular outcome \ldots{}
+will be balanced by a tendency for the opposite outcome'', while
+positive recency is the expectation of observing future results that
+match recent results.
 
@@
 Peel and Clauset found no evidence for unlikely sequences of scoring
-events in the NHL, College Football (CFB), and National Football League
-(NFL), but did in the NBA. As a check on their entropy approach to
+events in the NHL, College Football, and National Football League,
+although did in the NBA. As a check on their entropy approach to
 momentum identification, Steeger et al.~found several NHL teams with
-sequence of wins in the 2018-2019 regular season that violated the
+sequences of wins in the 2018-2019 regular season that violated the
 Wald-Wolfowitz null hypothesis.
@@
 \item
-  Both Counter-Strike and Valorant have overtime rules---team must win
+  Both Counter-Strike and Valorant have overtime rules---a team must win
   by two rounds---which can make end-of-series sequences difficult to
@@
 invetigated---particularly one that is less subjected to factors that
-may be difficult to control for, e.g.~weather---should be useful as a
-precedent or supplement for future researchers.
+may be difficult to control for, e.g.~weather---should be useful as an
+inspiration for future researchers.
 
@@
 In a best-of-\(s\) format, assuming a constant round win probability
-\(\phi\)\footnote{If \(\phi > 0.5\), we can say that this is the
-  stronger team.} (where \(0 \leq \phi \leq 1\)) for one
-team\footnote{\(\phi\) and other symbols are selected so as to reserve
-  symbols like \(p\) for usage in other contexts without causing
-  confusion for the reader. Upper-case symbol, e.g.~\(\Phi\), are
-  consistently used in this paper to represent proportions, while
-  lower-case symbols corresponding to upper-case symbols, e.g.~\(\phi\),
-  are used to represent Bernoulli trial success rates. ``Hats'',
-  e.g.~\(\hat{\Phi}\), are used to convey expectations, while bare
-  symbols symbols convey observational data.}, the expected proportion
-of series ending in \(r\) rounds (\(r \leq s\)) is given by Equation
-\ref{eq:series-length}.
+\(\phi\) (where \(0 \leq \phi \leq 1\))\footnote{If \(\phi > 0.5\), we
+  can say that this is the stronger team.} for one team\footnote{\(\phi\)
+  and other symbols are selected so as to reserve symbols like \(p\) for
+  usage in other contexts without causing confusion for the reader.
+  Upper-case symbol, e.g.~\(\Phi\), are consistently used in this paper
+  to represent proportions, while lower-case symbols corresponding to
+  upper-case symbols, e.g.~\(\phi\), are used to represent Bernoulli
+  trial success rates. ``Hats'', e.g.~\(\hat{\Phi}\), are used to convey
+  expectations, while bare symbols symbols convey observational data.},
+the expected proportion of series ending in \(r\) rounds (\(r \leq s\))
+is given by Equation \ref{eq:series-length}.
 
@@
 For example, assuming \(\phi = 0.5\), the probability of a series ending
-in nine rounds in CoD SnD, where \(s=11\), is
+in exactly nine rounds in CoD SnD, where \(s=11\) (implying \(m=6\)), is
 
@@
 the test statistic is chi-squared distributed, where the number of
-degrees of freedom is \(\vert R \vert -1 = 5\) for Cod SnD. We reject
-the null hypothesis if \(\chi^2 > \chi^2_{1-\alpha,\vert R \vert -1}\),
-where \(\chi^2_{1-\alpha,\vert R \vert -1}\) is the chi-square critical
-value with \(\vert R \vert -1\) degree of freedom and siginficance level
-\(\alpha\).
+degrees of freedom is \(\vert R \vert -1 = 5\) for Cod SnD.
 
@@
 
-using \(m\) from Equation \ref{eq:m}.
+for \(r \in R\) and \(m\) from Equation \ref{eq:m}.
 
@@
 lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
-\(p^{+|r}\).\footnote{Unfortunately, there does not exist a closed form
-  representation for the expected value of \(\hat{P}^{+|k,r}_{MS}\) for
-  \(k > 1\). Nonetheless, one may run simulations to estimate the
-  expected value, as we choose to do. We have adapted the code from Vafa
-  (2017), which implements MS's framework (2018).}
-
-Although one might be tempted to mirror the equal proportions hypothesis
-testing performed by MS, our context is fundamentally different from
-that of MS, who focus on longitudinal data in controlled settings,
-unaffected by opposition.\footnote{GVT also perform statistical tests on
-  shots from players in live games, i.e.~``observational'' data, but
-  they note that their findings are likely affected player shot
-  selection in the face of defensive strategy by the opposing team.} The
-number of trials is fixed in their experimental designs, but in CoD SnD,
-the number of rounds played is determined as a function of the max
-number of possible rounds (\(s\)) and whether or not the team wins the
-series. The Bernoulli trial success probability, i.e.~single round win
-percentage in CoD SnD, is not independent of the opponent. Consequently,
-a statistical test of the difference in \(\hat{P}^{+|k,r}\) and
-\(\hat{P}^{-|kr}\), as performed by MS to evaluate their hypothesis
-regarding post-streak success rate, is not completely appropriate,
-although useful as a reference.
+\(p^{+|r}\). Although one might be tempted to mirror the equal
+proportions hypothesis testing performed by MS, our context is
+fundamentally different from that of MS, who focus on longitudinal data
+in controlled settings, unaffected by opposition.\footnote{GVT also
+  perform statistical tests on shots from players in live games,
+  i.e.~``observational'' data, but they note that their findings are
+  likely affected by player shot selection in the face of defensive
+  strategy by the opposing team.} The number of trials is fixed in their
+experimental designs, but in CoD SnD, the number of rounds played is
+determined as a function of the max number of possible rounds (\(s\))
+and whether or not the team wins the series. The Bernoulli trial success
+probability, i.e.~single round win percentage in CoD SnD, is not
+independent of the opponent. Consequently, a statistical test of the
+difference in \(\hat{P}^{+|k,r}\) and \(\hat{P}^{-|kr}\), as performed
+by MS to evaluate their hypothesis regarding post-streak success rate,
+is not completely appropriate, although useful as a reference.
 
@@
 \(z\) is normally distributed. If \(z > +z_{(1-\alpha)/2}\) or
-\(z < -z_{(1-\alpha)/2}\) for critical values at a significance level
-\(\alpha\), we can reject the null hypothesis for such sequences and
-build an argument in support of the hot hand effect.
+\(z < -z_{(1-\alpha)/2}\) at a significance level \(\alpha\), we can
+reject the null hypothesis for such sequences and build an argument in
+support of the hot hand effect.
 
@@
 success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
-  get the same exact seqeunces.} at a confidence level of
-\(\alpha = 0.05\), for \(r \in [8, 9, 10]\). In addition to the 13
+  get the same exact sequences.} at a confidence level of
+\(\alpha = 0.05\), for \(r \inf [8, 9, 10]\). In addition to the 13
 sequences shown, there are 12 additional sequences for \(r = 11\).
@@
 For the sake of brevity, we did not account for offensive or defensive
-role when considering win proportions during streaks. For example, it
-would be interesting to look at whether the round win percentage is
-higher after a streaks of three round wins when the team starts the
-streak as the offensive team. This would mean that, in the round
-immediately following the latest streak win, the streaking team would be
-playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round
-win---theoretically, knowing that \(\bar{\tau}_O\) = 47.7\%, the
-expected frequency is \(\bar{\tau}_O^2 (1 - \bar{\tau}_O) \approx\)
-11.9\%---are likely to occur less frequently than such streaks starting
-with a defensive win---\(\bar{\tau}_O (1 - \bar{\tau}_O)^2 \approx\)
-13.0\%---so we would want to account for sample size differences.
+role when considering win proportions in the rounds immediately
+following streaks. For example, it would be interesting to look at
+whether the round win percentage is higher after a streaks of three
+round wins when the team starts the streak as the offensive team. This
+would mean that, in the round immediately following the last streak win,
+the streaking team would be playing defense, where teams are slightly
+more likely to win on average. On the other hand, streaks of three
+starting with an offensive round win are less likely to occur than such
+streaks starting with a defensive
+win-\(\bar{\tau}^2 (1 - \bar{\tau}) \approx\) 11.9\% in the former case
+and \(\bar{\tau} (1 - \bar{\tau})^2 \approx\) 13.0\% in the latter
+case---so we would need to properly account for sample size differences.
 
@@
 Further regarding future work, we have contacted the Twitter user
-``R11stats'', who privately tracks in-round player
-engagements.\footnote{\url{https://twitter.com/R11stats}} R11stats
+``R11stats'', who privately tracks in-round player engagements. R11stats
 expressed intent on making the data public, which would allow for
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-vafa2017}{}}%
-Vafa, Keyon. 2017. {``Is the Hot Hand Fallacy a Fallacy?''}
-\url{https://keyonvafa.github.io/hot-hand/}.
-
 \leavevmode\vadjust pre{\hypertarget{ref-xenopoulos2022}{}}%

### 2022-08-29 paper/paper.Rmd
atl fixes

@@
 A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD for the purposes of this paper.
-
-We note that SnD is not the only game mode played in competitive CoD.[^4] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes.
+Note that SnD is not the only game mode played in competitive CoD.[^4] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes.
 The best-of-five matchup could also be called a "series", but since we analyze only the SnD games, we refer to the SnD games as series.
@@
 
-    Outside of tournaments, teams all play each other twice throughout the season, constituting qualifiers.
-Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team, despite their win-loss records.
+    Outside of tournaments, teams play each other twice throughout the season, constituting qualifiers.
+Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team.
+
+    This format has minimized the range of rates at which teams start series playing offense.
+The highest rate at which a team has started their series playing defense across all tournament and qualifier SnD series in a single season is 66% (31 of 47).
+The lowest is 38% (16 of 42).
 
@@
 The null hypothesis is that the test statistic is chi-squared distributed, where the number of degrees of freedom is $\vert R \vert -1 = 5$ for Cod SnD.
+TODO: Make a note about $\alpha$
 
@@
 As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.
-Although one might be tempted to mirror the equal proportions hypothesis testing performed by MS, our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^14] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
+However, we should not mirror the equal proportions hypothesis testing performed by MS.
+
+Our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^14] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
 The Bernoulli trial success probability, i.e.
@@
 [^14]: GVT also perform statistical tests on shots from players in live games, i.e.
-"observational" data, but they note that their findings are likely affected by player shot selection in the face of defensive strategy by the opposing team.
+"observational" data, but they note that their findings are likely affected by player shot selection in the face of tactics by the opposing team.
 
@@
 
-One can consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|k,r}_0$.
+One can consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the final length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|k,r}_0$.
 The Bernoulli round win probability underlying $\hat{P}^{+|k,r}_0$ is
@@
 p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
-  \frac{m - k}{r - k} & \text{team wins series}, \\
-  \frac{s - m - k}{r - k} & \text{team loses series},
+  \frac{m - k}{r - k} & \text{team wins series}, r > m; \\
+  1 & \text{team wins series}, r = m; \\
+  \frac{s - m - k}{r - k} & \text{team loses series}, r > m + k; \\
+  0 & \text{team loses series}, r = m + k,
 \end{cases}
@@
 ```
-for $r \in R$ and $m$ from Equation \ref{eq:m}.
+
+where $r \in R$ for $m$ from Equation \ref{eq:m}.
 
 We can perform a two-tailed binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$ (where $0 \leq \omega_0 \leq 1$).
-If there are $r^+$ observed successes in a sample of $r$ trials and we expect that there should be $r * \omega_0$, the probability of arriving at this expected number of successes is
+If there are $r^+$ observed successes in a sample of $r$ trials, the probability of arriving at this expected number of successes is
 
@@
 ```
+
+We should expect that there should be $r * \omega_0$ successes.
+
+TODO: Simplify this first sentence.
+
 Treating the notional proportion $\hat{P}^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed proportion of post-streak round wins is equal to the notional proportion, given streak length $k$ and series length $r$.
@@
 
-We can further decompose Equation \ref{eq:pwkr} by the round $i$ (where $i \leq r$) in which the streak of length $k$ carries into.
+We can further decompose Equation \ref{eq:pwkr} by the round $i$ (where $k < i \leq r$) in which the streak of length $k$ carries into.
 
@@
 p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
-  \frac{m - k}{r - k}, & \text{team wins series}, i \neq r, \\
-  1, & \text{team wins series}, i = r, \\
-  \frac{s - m - k}{r - k}, & \text{team loses series}, i \neq r, \\
-  0, & \text{team loses series}, i = r.
+  \frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
+  1 & \text{team wins series}, i = r; \\
+  \frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
+  0 & \text{team loses series}, i = r \text{ or } r = m + k.
 \end{cases}
@@
 ```
-Again, we can apply a binomial test to evaluate the hypothesis that the expected proportions, $\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately, are equal to the observed proportion $P^{+|k,r}$.
+Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion--$\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately--is equal to the observed proportion $P^{+|k,r,i}$.
 
@@
 
-Stepping back from the (one-sided) perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon more broadly with a Wald-Wolfowitz runs test.
+Stepping back from the perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon more broadly with a Wald-Wolfowitz runs test.
 Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes ($r^- = r - r^+$ failures), with the following mean $\mu$ and variance $\sigma^2$:
@@
 ```
-To incorporate our findings regarding constant round win probability, We can specify that $\Pr(r^+) = \phi$ (and, conversely, that $\Pr(r^-) = 1 - \phi$).
-
-One can subset the observed series sequences, $\zeta(r)$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P(\zeta) = P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$.
+To incorporate our findings regarding constant round win probability, we can specify that $\Pr(r^+) = \phi$.
+
+One can subset the observed series sequences, $\zeta(r)$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$.
 The test statistic is
@@
 The null hypothesis is that $z$ is normally distributed.
-If $z > +z_{(1-\alpha)/2}$ or $z < -z_{(1-\alpha)/2}$ at a significance level $\alpha$, we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.
+If we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.
 
@@
 
-Using Equation \ref{eq:chi-squ}, we find that $\chi^2 = 16.0$ ($p$-value of 0.0068) for $\phi_0 = 0.5$.
-Thus, we can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$, even at a confidence level of $\alpha = 0.01$.
+Using Equation \ref{eq:chi-squ}, we find that $\chi^2 = 16.0$ ($p$-value of <0.01) for $\phi_0 = 0.5$.
+Thus, we can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$ at a confidence level of $\alpha = 0.05$.
 
@@
 
-Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series lasting $r$ rounds, the expected proportion of series given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, and the observed proportions, $\Phi(r)$.
+Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion of series lasting $r$ rounds given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, as well as the observed proportions, $\Phi(r)$.
 
@@
 ```
-Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability that we find when applying the three methods suggested by Mosteller [-@mosteller1952].
-Each is approximately equal to 0.575.
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability assumptions, each approximately equal to 0.575.
 When applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which we cannot reject the constant probability null hypothesis.
-Note that rejection of the null hypothesis is the baseline and failure to reject the null is the non-trivial result, contrary to most statistical analysis.
 
@@
 ```
-Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^15] We observe that $\hat{\Phi}_2(r)$ is larger than $\hat{\Phi}_0(r)$ for $r \in [6, 7]$, more closely matching $\Phi(r)$.
-$\hat{\Phi}_2(r)$ is also closer to the observed $\Phi(r)$ for $r \in [9, 10]$, although not for $r \in [8, 11]$.
+Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^15] We observe that $\hat{\Phi}_2(r)$ more closely matches $\Phi(r)$ than $\hat{\Phi}_0(r)$.
 
@@
 ```
-Observing that the null hypothesis acceptance shown in Table \ref{tbl:mosteller-methods-results}, along with the observation that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ (in comparison to $\hat{\Phi}_0(r)$), we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
+Observing the null hypothesis acceptance shown in Table \ref{tbl:mosteller-methods-results}, along with the observation that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$, we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
 
@@
 
-Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.[^16] Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|kr}$, following streaks of $k=3$ round wins given the series outcome.
-
-[^16]: Three happens to also be a reasonable number for series that last at maximum 11 rounds.
+Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.
+Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|k,r}$, following streaks of $k=3$ round wins given the series outcome.
 
@@
 ```
-With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win proportions are different than the observed proportion.
-However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.[^17]
-
-[^17]: As noted before, the MS expectations may be unreliable for CoD SnD, so one is inclined to prefer the results of the notional binomial tests.
+With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and when the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win proportions are different than the observed proportion.
+tODO: Move to Methodology.
+However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.
 
 When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the binomial null hypothesis for the expected notional proportion $\hat{P}^{+|k,r}_0$ (even before the BY p-value correction).
-The null hypothesis can only be rejected for the expected MS proportion $\hat{P}^{+|k,r}_{MS}$ when $k = 5, r = 7$ after applying the BY p-value correction.[^18]
+The null hypothesis can only be rejected in one extreme case for the MS proportion $\hat{P}^{+|k,r}_{MS}$.
+the expected  when $k = 5, r = 7$ after applying the BY p-value correction.[^18]
 

### 2022-08-29 paper/paper.tex
atl fixes

@@
 ``game'' or a ``match'' in such leagues is analogous to a ``round'' of
-CoD SnD for the purposes of this paper.
-
-We note that SnD is not the only game mode played in competitive
-CoD.\footnote{Hardpoint has been played as the first and fourth game
-  modes in a matchup. The third game mode was Domination in the 2020
-  season, and Control in the 2021 and 2022 seasons.} Teams play in a
-head-to-head, best-of-five format, where SnD is always played as the
-second and fifth game modes. The best-of-five matchup could also be
-called a ``series'', but since we analyze only the SnD games, we refer
-to the SnD games as series.
+CoD SnD for the purposes of this paper. Note that SnD is not the only
+game mode played in competitive CoD.\footnote{Hardpoint has been played
+  as the first and fourth game modes in a matchup. The third game mode
+  was Domination in the 2020 season, and Control in the 2021 and 2022
+  seasons.} Teams play in a head-to-head, best-of-five format, where SnD
+is always played as the second and fifth game modes. The best-of-five
+matchup could also be called a ``series'', but since we analyze only the
+SnD games, we refer to the SnD games as series.
 
@@
 
-  Outside of tournaments, teams all play each other twice throughout the
+  Outside of tournaments, teams play each other twice throughout the
   season, constituting qualifiers. Each team gets to play the
   higher-seeded role once in their head-to-head matchups with a given
-  team, despite their win-loss records.}
+  team.
+
+  This format has minimized the range of rates at which teams start
+  series playing offense. The highest rate at which a team has started
+  their series playing defense across all tournament and qualifier SnD
+  series in a single season is 66\% (31 of 47). The lowest is 38\% (16
+  of 42).}
 
@@
 lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
-\(p^{+|r}\). Although one might be tempted to mirror the equal
-proportions hypothesis testing performed by MS, our context is
-fundamentally different from that of MS, who focus on longitudinal data
-in controlled settings, unaffected by opposition.\footnote{GVT also
-  perform statistical tests on shots from players in live games,
-  i.e.~``observational'' data, but they note that their findings are
-  likely affected by player shot selection in the face of defensive
-  strategy by the opposing team.} The number of trials is fixed in their
-experimental designs, but in CoD SnD, the number of rounds played is
-determined as a function of the max number of possible rounds (\(s\))
-and whether or not the team wins the series. The Bernoulli trial success
-probability, i.e.~single round win percentage in CoD SnD, is not
+\(p^{+|r}\). However, we should not mirror the equal proportions
+hypothesis testing performed by MS.
+
+Our context is fundamentally different from that of MS, who focus on
+longitudinal data in controlled settings, unaffected by
+opposition.\footnote{GVT also perform statistical tests on shots from
+  players in live games, i.e.~``observational'' data, but they note that
+  their findings are likely affected by player shot selection in the
+  face of tactics by the opposing team.} The number of trials is fixed
+in their experimental designs, but in CoD SnD, the number of rounds
+played is determined as a function of the max number of possible rounds
+(\(s\)) and whether or not the team wins the series. The Bernoulli trial
+success probability, i.e.~single round win percentage in CoD SnD, is not
 independent of the opponent. Consequently, a statistical test of the
@@
 immediately after a streak of \(k\) round wins in a best-of-\(s\) series
-given the length of the series (\(r\) rounds), the ``notional''
+given the final length of the series (\(r\) rounds), the ``notional''
 proportion \(\hat{P}^{+|k,r}_0\). The Bernoulli round win probability
@@
 
-for \(r \in R\) and \(m\) from Equation \ref{eq:m}.
+where \(r \in R\) for \(m\) from Equation \ref{eq:m}.
 
@@
 \(0 \leq \omega_0 \leq 1\)). If there are \(r^+\) observed successes in
-a sample of \(r\) trials and we expect that there should be
-\(r * \omega_0\), the probability of arriving at this expected number of
-successes is
+a sample of \(r\) trials, the probability of arriving at this expected
+number of successes is
 
@@
 \end{equation}
+
+We should expect that there should be \(r * \omega_0\) successes.
 
@@
 We can further decompose Equation \ref{eq:pwkr} by the round \(i\)
-(where \(i \leq r\)) in which the streak of length \(k\) carries into.
+(where \(k < i \leq r\)) in which the streak of length \(k\) carries
+into.
 
@@
 Again, we can apply a binomial test to evaluate the hypothesis that the
-expected proportions, \(\hat{P}^{+|k,r,i}_0\) and
-\(\hat{P}^{+|k,r,i}_{MS}\) separately, are equal to the observed
-proportion \(P^{+|k,r}\).
+expected proportion--\(\hat{P}^{+|k,r,i}_0\) and
+\(\hat{P}^{+|k,r,i}_{MS}\) separately--is equal to the observed
+proportion \(P^{+|k,r,i}\).
 
@@
 
-Stepping back from the (one-sided) perspective of a single team's round
-win probability when streaking, one can attempt to detect the hot hand
+Stepping back from the perspective of a single team's round win
+probability when streaking, one can attempt to detect the hot hand
 phenomenon more broadly with a Wald-Wolfowitz runs test. Under the null

### 2022-08-29 paper/paper.Rmd
everything but table 7 analysis

@@
 title: "The Hot Hand Fallacy in Call of Duty Search and Destroy"
+link-citations: true
 authors:
@@
 
-[^5]: CoD has roughly gone through three eras of professional gaming: (1) Major League Gaming (MLG) tournaments prior to 2016; (2) the CoD World League (CWL), initiated in 2016; and (3) the 12-franchise CoD League (CDL), operating since 2020.
+[^5]: Since the release of "Call of Duty: Modern Warfare" in fall 2019, professional CoD has been orchestrated by the 12-franchise CoD League (CDL).
 The CDL has completed three year-long "seasons" as of August 2022.
-
-    CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, with releases coming in the late fall.
-A new game under the same brand---Call of Duty---is published every year by a rotating set of developers.
-Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
-During the CDL era, the games released have been Modern Warfare (2020), Cold War (2021) and Vanguard (2022).
 
@@
 
+CoD is fairly unique compared to other esports in that it runs on an annual lifecycle, with releases coming in the late fall.
+A new game under the same brand---"Call of Duty"---is published every year by a rotating set of developers.
+Each new game bears resemblance to past ones, often introducing relatively small variations ("improvements") to graphics, game modes, and other facets of gameplay.
+During the CDL era, the games released have been "Modern Warfare" (2020 season), "Cold War" (2021 season) and "Vanguard" (2022 season).
+
 Sweeps (6-0 series) make up 4.7% of all series, while 6-5 series make up 23.7% of series.
-The observed offensive round win percentage across all rounds is $\bar{\tau}$ = 47.8%.[^8] Table \ref{tbl:o-win-prop-by-series-state} shows offensive round win percentages by series "state", i.e.
+The observed offensive round win percentage[^8] across all rounds is $\bar{\tau}$ = 47.8%.[^9] Table \ref{tbl:o-win-prop-by-series-state} shows offensive round win percentages by series "state", i.e.
 the number of round wins by each team prior to an upcoming round.
@@
 
-[^8]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 1. 47.2% in MW (2020) 2. 47.9% in Cold War (2021) 3. 48.1% in Vanguard (2022)
+[^8]: We use the terms "percentage", "probability", and "proportion" synonymously throughout this paper when discussing round win rates.
+For the most part, we restrict "percentage" usage to observed values and "probability" usage to expected values, and we use "proportion" to refer to either observed or expected values.
+
+[^9]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 47.2% in Modern Warfare; 47.9% in Cold War; and 48.1% in Vanguard
 
@@
 ```
-
 The professional competition format balances the frequency with which teams play offense or defense to start a series, to the extent possible.
 Thus, win percentages in certain states are subjected to minimal selection bias, i.e.
-bias due to better teams playing defense more frequently.[^9]
-
-[^9]: At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series, played as the second or fifth game mode of the best-of-five matchup.
+bias due to better teams playing defense more frequently.[^10]
+
+[^10]: At tournaments, higher-seeded ("better") teams choose whether they want to start on offense in the SnD series, played as the second or fifth game mode of the best-of-five matchup.
 Their opponent is assigned to start on offense in the SnD slot not chosen.
@@
 
-    Outside of tournaments, teams play each other twice throughout the season, constituting qualifiers.
-Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team.
+Outside of tournaments, teams play each other twice throughout the season, constituting qualifiers. Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team.
 
@@
 
-The concept of momentum goes hand-in-hand with a discussion of the nature of series outcomes.[^10] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
+The concept of momentum goes hand-in-hand with a discussion of the nature of series outcomes.[^11] Two opposing fallacies are observed in the context of momentum: the "gambler's fallacy" (negative recency) and the "hot hand fallacy" (positive recency).
 Per Ayton et al.
@@
 
-[^10]: We often use "streaks" and momentum interchangeably, but as Steeger et al. [-@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
+[^11]: We often use "streaks" and momentum interchangeably, but as Steeger et al. [-@steeger2021] note, momentum implies dependence between events, whereas streaking does not.
 
@@
 Teams play either offense or defense for many consecutive rounds.
-(The former has a 15-15-1 format and the latter uses a 12-12-1 format.) On the other hand, teams in CoD SnD rotate roles every round, analogous to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series for professional sports like the MLB, NBA, and NHL.[^11] While theoretically one might be able to account for inter-round win percentage relationships in any kind of format, such as a 5-5-1, the rotation of team sides every round is convenient for convincing ourselves that rounds could reasonably be modeled as i.i.d.
-Bernoulli trials.
+(Counter-Strike has a 15-15-1 format and Valorant has a 12-12-1 format.) On the other hand, teams in CoD SnD rotate attacking and defending roles every round, minimizing the effect of map asymmetry on streaks of wins.[^12]
 3.  Both Counter-Strike and Valorant have overtime rules---a team must win by two rounds---which can make end-of-series sequences difficult to model properly. CoD SnD does not have overtime rules.
 
-[^11]: 1-1-1-1-1-1-1 is not used today in these leagues, but it was at least once in each.
+[^12]: Professional CoD has a set of maps (at least three, depending on the season) on which teams choose to play SnD.
+Most are asymmetric, introducing slight advantages for the offense or defense that do not exist on other maps.
+Counter-Strike and Valorant also have their own sets of maps for their analogous SnD modes.
 
 To our knowledge, there is no existing public statistical research on the CoD SnD format, beyond descriptive analysis on social media.
-While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation of a concept like the hot-hand fallacy in a sport where it has not yet been invetigated---particularly one that is less subjected to factors that may be difficult to control for, e.g.
+While intra-round trends may be more directly applicable to teams looking for an advantage on their competition, broader investigation of a concept like the hot-hand fallacy in a sport where it has not yet been investigated---particularly one that is less subjected to factors that may be difficult to control for, e.g.
 weather---should be useful as an inspiration for future researchers.
@@
 
-In a best-of-$s$ format, assuming a constant round win probability $\phi$ (where $0 \leq \phi \leq 1$)[^12] for one team[^13], the expected proportion of series ending in $r$ rounds ($r \leq s$) is given by Equation \ref{eq:series-length}.
-
-[^12]: If $\phi > 0.5$, we can say that this is the stronger team.
-
-[^13]: $\phi$ and other symbols are selected so as to reserve symbols like $p$ for usage in other contexts without causing confusion for the reader.
-Upper-case symbol, e.g.
-$\Phi$, are consistently used in this paper to represent proportions, while lower-case symbols corresponding to upper-case symbols, e.g.
-$\phi$, are used to represent Bernoulli trial success rates.
-"Hats", e.g.
-$\hat{\Phi}$, are used to convey expectations, while bare symbols symbols convey observational data.
+In a best-of-$s$ format, assuming a constant round win probability $\phi$ (where $0 \leq \phi \leq 1$) for a given team, the expected proportion of series ending in $r$ rounds (where $r \leq s$) is given by Equation \ref{eq:series-length}.
 
@@
 ```
-in which $\hat{\Phi}(r)$ and $\Phi(r)$ represent the expected and observed round win proportions respectively, and $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
+where $\hat{\Phi}(r)$ and $\Phi(r)$ represent the expected and observed round win proportions respectively, and where $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
 The null hypothesis is that the test statistic is chi-squared distributed, where the number of degrees of freedom is $\vert R \vert -1 = 5$ for Cod SnD.
-TODO: Make a note about $\alpha$
+We use a significance level of $\alpha = 0.05$ for this test and all others in this paper.
 
@@
 Let us now consider round win proportions immediately following a streak of $k$ wins, given that the series lasts $r$ rounds.
-Removing our knowledge of a streak, we might model the Bernoulli round win probability as
+Removing our knowledge of a streak, we might expect the win proportion for a round to be
 
@@
 \begin{equation}\label{eq:pwr}
-p_0(\text{win} | r) = p^{+|r}_0 := \begin{cases} 
+\hat{P}_0(\text{win} | r) = \hat{P}^{+|r}_0 := \begin{cases} 
 \frac{m}{r} & \text{team wins series}, \\ 
@@
 
-As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series lasting $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than $p^{+|r}$.
-However, we should not mirror the equal proportions hypothesis testing performed by MS.
-
-Our context is fundamentally different from that of MS, who focus on longitudinal data in controlled settings, unaffected by opposition.[^14] The number of trials is fixed in their experimental designs, but in CoD SnD, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
-The Bernoulli trial success probability, i.e.
-single round win percentage in CoD SnD, is not independent of the opponent.
-Consequently, a statistical test of the difference in $\hat{P}^{+|k,r}$ and $\hat{P}^{-|kr}$, as performed by MS to evaluate their hypothesis regarding post-streak success rate, is not completely appropriate, although useful as a reference.
-
-[^14]: GVT also perform statistical tests on shots from players in live games, i.e.
-"observational" data, but they note that their findings are likely affected by player shot selection in the face of tactics by the opposing team.
+As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series ending in $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than the observed proportion of round wins given the series length, but not given knowledge of the potential existence of a streak, $P^{+|r}$, i.e.
+the analogue of the expected proportion in Equation \ref{eq:pwr} for the observed data.
+However, our context is fundamentally different from that of MS, who evaluate data in controlled settings, unaffected by opposition.[^13]
+
+[^13]: GVT also perform statistical tests on shots from players in live games, i.e.
+"observational" data, but they note that their findings are likely affected by player shot selection influenced by the opposing team's defensive strategy.
+This is similar to our setting.
+
+The number of trials is fixed in their experimental designs; in CoD SnD, however, the number of rounds played is determined as a function of the max number of possible rounds ($s$) and whether or not the team wins the series.
+The single round win percentage in CoD SnD---analogous to a player's shooting percentage in MS's analysis of basketball players---is not independent of the opponent.
+Consequently, the i.i.d.
+assumption of MS's theorem regarding post-streak success may or may not be valid.
+Nonetheless, we still leverage $\hat{P}^{+|k,r}_{MS}$ as a reference for our results.
 
@@
 
-One can consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series given the final length of the series ($r$ rounds), the "notional" proportion $\hat{P}^{+|k,r}_0$.
-The Bernoulli round win probability underlying $\hat{P}^{+|k,r}_0$ is
+Let us consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series ending in $r$ rounds: the "notional" proportion
 
@@
 \begin{equation}\label{eq:pwkr}
-p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
+\hat{P}_0(\text{win} | k, r) = \hat{P}^{+|k,r}_0 := \begin{cases}
 \frac{m - k}{r - k} & \text{team wins series}, r > m; \\
@@
 ```
-
-where $r \in R$ for $m$ from Equation \ref{eq:m}.
-
-We can perform a two-tailed binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed probability of success $\omega$ and a user-specified $\omega_0$ (where $0 \leq \omega_0 \leq 1$).
-If there are $r^+$ observed successes in a sample of $r$ trials, the probability of arriving at this expected number of successes is
+where $r \in R$ and $m$ from Equation \ref{eq:m}.
+
+We can perform a two-tailed binomial test to evaluate the null hypothesis $\omega = \omega_0$ for the observed proportion of successes, $\omega$, and a null proportion, $\omega_0$ (where $0 \leq \omega_0 \leq 1$).
+The probability of exactly $r^+$ successes (and $r^- = r - r^+$ failures) in a sample of $r$ trials is
 
@@
 \begin{equation}\label{eq:binom}
-\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r-r^+}.
+\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r^-},
 \end{equation}
 ```
-
-We should expect that there should be $r * \omega_0$ successes.
-
-TODO: Simplify this first sentence.
-
-Treating the notional proportion $\hat{P}^{+|k,r}_0$ as the null $\omega_0$ and plugging in the observed proportion $P^{+|k,r}$ for $\omega$ in Equation \ref{eq:binom} (treating proportions as probabilities), we can evaluate the null hypothesis that the observed proportion of post-streak round wins is equal to the notional proportion, given streak length $k$ and series length $r$.
-If we can reject this null hypothesis, then we can consider team momentum, represented by post-streak success, plausible.
-
-As a reference, we can perform the same binomial test for the MS's streak-selection-adjusted proportion, $\hat{P}^{+|k,r}_{MS}$.
-However, given the caveats mentioned before regarding applying MS's theorem to our setting, the results of such binomial tests should be heeded with caution.
+where $\omega = \frac{r^+}{r}$ is the observed proportion of successes.
+If we can reject the null hypothesis---treating $P^{+|k,r}$ and $\hat{P}^{+|k,r}_0$ as $\omega$ and $\omega_0$ respectively---then we might consider team momentum plausible.
+Since we perform this test for many combinations of $k$ and $r$, we adjust the $p$-values with the Benjamini and Yekutieli (BY) false discovery procedure [-@benjamini2001].
+
+As a reference, we can perform the same binomial test for MS's proportion, $\hat{P}^{+|k,r}_{MS}$, which adjusts for streak selection bias.
+However, given the caveats mentioned before regarding the application of MS's theorem to our setting, the results of such binomial tests should be heeded with caution.
 
@@
 \begin{equation}\label{eq:pwkri}
-p_0(\text{win} | k, r, i) = p^{+|k,r,i}_0 = \begin{cases}
+\hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
 \frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
@@
 \frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
-  0 & \text{team loses series}, i = r \text{ or } r = m + k.
+0 & \text{team loses series}, i = r.
 \end{cases}
@@
 ```
-Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion--$\hat{P}^{+|k,r,i}_0$ and $\hat{P}^{+|k,r,i}_{MS}$ separately--is equal to the observed proportion $P^{+|k,r,i}$.
+Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion, $\hat{P}^{+|k,r,i}_0$, is equal to the observed proportion, $P^{+|k,r,i}$.
 
@@
 
-Stepping back from the perspective of a single team's round win probability when streaking, one can attempt to detect the hot hand phenomenon more broadly with a Wald-Wolfowitz runs test.
-Under the null hypothesis, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes ($r^- = r - r^+$ failures), with the following mean $\mu$ and variance $\sigma^2$:
+We can attempt to detect the hot hand phenomenon more broadly by focusing on non-random sequences identified by the Wald-Wolfowitz runs test.
+Note that the probability of success and failure need not be equal; thus, we can incorporate our findings regarding constant round win probability, specifying that the probability of success is $\phi_2 = 0.575$.
+
+Under the null hypothesis for the Wald-Wolfowitz runs test, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes (and $r^-$ failures), with the following mean $\mu_r$ [^14] and variance $\sigma_r^2$:
+
+[^14]: We calculate $\mu$ and $\sigma^2$ for each number of rounds $r \in R$.
 
@@
 \begin{equation}\label{eq:ww}
-\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
+\mu_r = \frac{2r^{+}r^{-}}{r} + 1, \sigma_r^2 = \frac{(\mu_r-1)(\mu_r-2)}{r-1}.
 \end{equation}
 ```
-To incorporate our findings regarding constant round win probability, we can specify that $\Pr(r^+) = \phi$.
-
-One can subset the observed series sequences, $\zeta(r)$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null is that the observed proportion of a sequence relative to all possible sequences, $P^\zeta$, is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta$.
+The null hypothesis is that the test statistic,
+
+```{=tex}
+\begin{equation}\label{eq:wwz}
+z_r = \frac{r^* - \mu_r}{\sigma_r},
+\end{equation}
+```
+where $r^*$ is the number of runs, is normally distributed.
+
+We can subset the observed series sequences, $\zeta_j$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null hypothesis is that the observed proportion of a sequence relative to all possible sequences, $P^{\zeta}_j$ ( $\frac{N^\zeta_j}{\sum_j N^\zeta }$), is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta_j$.
 The test statistic is
@@
 \begin{equation}\label{eq:prop}
-z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
+z^\zeta_j = \frac{P^\zeta_j - \hat{P}^\zeta_j}{\sqrt{P^\zeta_{j,\delta} (1 - P^\zeta_{j,\delta}) (1 / N^\zeta_j + 1 / \hat{N}^\zeta_j)  } }
 \end{equation}
 ```
-where
-
-$$
-P^\zeta_{\delta} = \frac{P^\zeta - \hat{P}^\zeta}{N^\zeta - \hat{N}^\zeta}
-$$
-
-and where $N^\zeta$ and $\hat{N}^\zeta$ are the observed and expected number of sequences respectively.
-The null hypothesis is that $z$ is normally distributed.
-If we can reject the null hypothesis for such sequences and build an argument in support of the hot hand effect.
+where $N^\zeta_j$ and $\hat{N}^\zeta_j$ respectively represent the observed and expected number of occurrences of sequence $\zeta_j$, and where $P^\zeta_{j,\delta} = (P^\zeta_j - \hat{P}^\zeta_j) / ({N^\zeta_j - \hat{N}^\zeta_j})$.
+The null hypothesis is that the test statistic is normally distributed.
+If we can reject the null hypothesis for such sequences, we can build an argument in support of the hot hand effect.[^15]
+
+[^15]: As with the binomial tests for the notional and MS post-streak proportions, we adjust the $p$-values with the BY correction.
 
@@
 
-Using Equation \ref{eq:chi-squ}, we find that $\chi^2 = 16.0$ ($p$-value of <0.01) for $\phi_0 = 0.5$.
-Thus, we can comfortably reject the constant probability hypothesis for the null $\phi_0 = 0.5$ at a confidence level of $\alpha = 0.05$.
+Using Equation \ref{eq:chi-squ}, we find that $\chi^2 = 16.0$ ($p$-value of \<0.01) for $\phi_0 = 0.5$.
+Thus, we can comfortably reject the constant probability hypothesis for the naive $\phi_0 = 0.5$.
 
@@
 
-Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion of series lasting $r$ rounds given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, as well as the observed proportions, $\Phi(r)$.
+Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion of series ending in $r$ rounds given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, as well as the observed proportions, $\Phi(r)$.
 
@@
 \begin{table}
-\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}
+\caption{The observed frequencies of CoD SnD series ending in $r$ rounds shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).
+Additionally, the expected proportion, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.}
 
@@
 ```
-Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability assumptions, each approximately equal to 0.575.
+Table \ref{tbl:mosteller-methods-results} shows the alternate values for the constant round win probability assumption, each approximately equal to 0.575.
 When applying Equation \ref{eq:chi-squ}, each results in a $\chi^2$ value for which we cannot reject the constant probability null hypothesis.
@@
 
-\caption{Alternate estimates of the constant probability ($\phi$) for winning a given round in a CoD SnD, applying the three methods suggested by Mosteller (1952), in addition to the naive ($\phi_0 = 0.5$).}
+\caption{Alternate estimates of the constant round win probability ($\phi$) and their corresponding $\chi^2$ values, applying the three methods suggested by Mosteller to CoD SnD.
+Additionally, the naive constant round win probability $\phi_0$ and its $\chi^2$.}
 
@@
 
-0. Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
-1. Method of moments & 0.5725 & 3.6 (0.6) \\
-2. Maximum likelihood & 0.5750 & 3.5 (0.62) \\
-3. Minimum ($\chi^2$) & 0.5775 & 3.5 (0.62) \\
+$\phi_0$: Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
+$\phi_1$: Method of moments & 0.5725 & 3.6 (0.6) \\
+$\phi_2$: Maximum likelihood & 0.5750 & 3.5 (0.62) \\
+$\phi_3$: Minimum $\chi^2$ & 0.5775 & 3.5 (0.62) \\
 
@@
 ```
-Table \ref{tbl:alternative-constant-ps} shows the new $\hat{\Phi}(r)$ when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$, resulting in a new set of expected proportions of series lasting $r$ rounds $\hat{\Phi}_2(r)$.[^15] We observe that $\hat{\Phi}_2(r)$ more closely matches $\Phi(r)$ than $\hat{\Phi}_0(r)$.
-
-[^15]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+Table \ref{tbl:alternative-constant-ps} shows the expected proportions of series ending in $r$ rounds, $\hat{\Phi}_2(r)$, when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$.[^16] We observe that $\hat{\Phi}_2(r)$ more closely matches $\Phi(r)$ than $\hat{\Phi}_0(r)$.
+
+[^16]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 \begin{table}
-\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}
+
+\caption{The observed proportion of CoD SnD series ending in $r$ rounds, $\Phi(r)$, compared to the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$.
+Additionally, the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ is repeated from Table \ref{tbl:prob-series-lasts-r-rounds} for comparison.}
 
 \centering
-\begin{tabular}{rrrrrr}
+\begin{tabular}{rrrr}
 \toprule
@@
 ```
-Observing the null hypothesis acceptance shown in Table \ref{tbl:mosteller-methods-results}, along with the observation that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$, we can say that the constant round win probability assumption is valid in CoD SnD series with the appropriate choice of $\phi$ ($\approx 0.575$).
+The observation that $\hat{\Phi}_2(r)$ reasonably matches $\Phi(r)$ supports the implication from the failure to reject the null hypothesis for $\phi_2$ (shown in Table \ref{tbl:mosteller-methods-results}): the constant round win probability assumption can be valid for CoD SnD with the appropriate choice of $\phi$ ($\approx 0.575$).
 
@@
       notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value,
-      ms_p_value = vectorized_binom_test(n, total, p = ms_prop)$p.value
+      ms_p_value = vectorized_binom_test(n, total, p = ms_prop)$p.value,
+      notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY')
     )
@@
 
-cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
+init_cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
   mutate(
@@
   unnest(data)
-cod_round_win_prop_after_k_wins |> filter(win_round, notional_p_value < 0.05)
-cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value < 0.05)
+
+cod_round_win_prop_after_k_wins <- init_cod_round_win_prop_after_k_wins |> 
+  filter(win_round) |> 
+  mutate(
+    notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY'),
+    ms_p_value_adj = ms_p_value |> p.adjust(method = 'BY')
+  )
+
+cod_round_win_prop_after_k_wins |> filter(win_round, notional_p_value_adj < 0.05)
+cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value_adj < 0.05)
 ```
@@
 Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.
-Table \ref{tbl:pwkr} compares the notional and MS expected proportions, $\hat{P}^{+|k,r}_0$ and $\hat{P}^{+|k,r}_{MS}$ respectively, with the observed round win proportion, $P^{+|k,r}$, following streaks of $k=3$ round wins given the series outcome.
+Table \ref{tbl:pwkr} compares the observed round win proportion, $P^{+|k=3,r}$, with the notional proportion, $\hat{P}^{+|k=3,r}$, following streaks of $k=3$ round wins.
+The MS proportion, $\hat{P}^{+|k=3,r}_{MS}$, is also shown as a reference.
 
@@
 
-\caption{Given the round win streak $k=3$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ instances where a team could win after the streak ($P^{+|k=3,r} = \frac{r^{+|k=3,r}}{N^{k=3,r}}$).
-Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ respectively.}
+\caption{For streaks of $k=3$ round wins in CoD SnD series ending in $r$ rounds, the observed count of rounds wins, $r^{+|k=3,r}$, and proportion of round wins, $P^{+|k=3,r}$, among $N^{k=3,r}$ chances ($P^{+|k=3,r} = r^{+|k=3,r} / N^{k=3,r}$).
+Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$, respectively.
+}
 
@@
 ```
-With the exception of $\hat{P}^{+|k,r}_{MS}$ when $r = 10$ and when the eventual series loser is the team that wins after a streak of three round wins, all un-adjusted binomial test $p$-values are greater than the $\alpha = 0.05$ confidence level, implying that we cannot reject the null hypothesis that the expected notional and MS post-streak round win proportions are different than the observed proportion.
-tODO: Move to Methodology.
-However, after adjusting the $p$-values with the Benjamini and Yekutieli (BY) correction [-@benjamini2001], the null hypothesis cannot be rejected for any case.
-
-When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the binomial null hypothesis for the expected notional proportion $\hat{P}^{+|k,r}_0$ (even before the BY p-value correction).
-The null hypothesis can only be rejected in one extreme case for the MS proportion $\hat{P}^{+|k,r}_{MS}$.
-the expected  when $k = 5, r = 7$ after applying the BY p-value correction.[^18]
-
-[^18]: At 36, the sample size for $k = 5, r = 7$ is not as large as most other combinations of $k$ and $r$.
+All binomial test $p$-values for both $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ are found to be insignificant at the $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the notional and MS post-streak round win proportions are different than the observed proportion for streaks of three.[^17] When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the null hypothesis for $\hat{P}^{+|k,r}_0$.
+The null hypothesis can only be rejected in some extreme cases for $\hat{P}^{+|k,r}_{MS}$.[^18]
+
+[^17]: $p$-values are not shown for readability purposes.
+
+[^18]: These cases are: (1) $k = 4$, $r = 7$ ($N^{k,r} = 108$); (2) $k = 4$, $r = 10$ ($N^{k,r} = 45$); (3) $k = 5, r = 7$ ($N^{k,r} = 37$); (4) $k = 5, r = 8$ ($N^{k,r} = 4$).
+In each case, the team won the series.
 
@@
   mutate(
-    notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value |> round(2)
+    notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value
+  ) |> 
+  filter(win_round) |> 
+  mutate(
+    notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY')
   )
@@
 # ## example of why we needed to recalculate prop... prop and notional_prop should sum to 1, grouped by win_streak and win_round
-# cod_round_win_prop_after_k_wins_i_rounds |> 
-#   filter(win_streak == 3, n_rounds == 11, round == 10)
-# 
+init_cod_round_win_prop_after_k_wins_i_rounds |>
+  filter(win_streak == 3, n_rounds == 11, round == 10)
+
+cod_round_win_prop_after_k_wins_i_rounds |>
+  filter(win_streak == 3, n_rounds == 11, round == 10)
+
 # ## 5-3?
@@
 
-Now let us explicitly consider the round, $i$.
-As shown in Table \ref{tbl:pw3ri}, the notional win proportion in the round $i$ immediately following a streak of $k$ round wins in a series lasting $r$ rounds, $\hat{P}{+|k,r,i}_0$, is statistically different than the observed $P^{+|k,r,i}$ in several cases, notably when $r = i$ for each of $r \in [9, 10, 11]$.[^19] Interestingly, the observed rate is greater than the expected rate in each case where we can reject the null hypothesis, whereas the observed rate is less than the expected rate in all other cases, as well in a strong majority of cases not shown.
-
-[^19]: The null can also be rejected for $r \in [7, 8]$, although these are not shown, and the sample sizes are smaller.
+Table \ref{tbl:pw3ri} shows the observed and notional proportions of round wins immediately following streaks of three round wins when explicitly accounting for the round index, $i$.[^19]
+
+[^19]: We omit the MS proportions $\hat{P}^{+|k=3,r,i}_{MS}$ since sample sizes are small and results may or may not be valid due to the questionable i.i.d assumption.
 
@@
 
-\caption{Given the round win streak $k=3$, the index of the round immediately following the streak $i$, the length of the series ($r$ rounds), and the series winner, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ instances where a team could win after the streak.
+\caption{For streaks of $k=3$ round wins in CoD SnD series ending in $r$ rounds, the observed count of rounds wins, $r^{+|k=3,r,i}$, and proportion of round wins, $P^{+|k=3,r,i}$, among $N^{k=3,r,i}$ chances, given the index of the round, $i$, immediately following the streak.
 Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$.
-Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$ for brevity.}
+Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$.}
 
@@
       across(w, ~ifelse(zeros_win, abs(1 - .x), .x))
-      # across(w, ~ifelse(zeros_win, '-', '+'))
     )
@@
       cumu_l = max(cumu_l),
-      ws = paste0(w, collapse = ' ')
+      ws = paste0(w, collapse = '-')
     ) |> 
@@
       ) |> 
+      mutate(
+        p_value = map_dbl(w, ~randtests::runs.test(.x, threshold = 0.5, pvalue = 'normal')$p.value),
+        across(p_value, ~ifelse(n_rounds == 6, 0, .x)),
+        is_significant = p_value <= 0.05
+      ) |> 
       ungroup() |> 
-      mutate(
-        p_value = map_dbl(w, ~randtests::runs.test(.x, threshold = 0.5)$p.value),
-        is_significant = p_value <= 0.05
-      ) |> 
       select(n_rounds, ws, p_value, is_significant)
@@
 
-In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences, $N^{\zeta r}$ and $\hat{N}^{\zeta r}$ respectively, are shown for sequences, $\zeta(r)$, for which one can reject the Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial success $\phi = 0.575$,[^20] at a confidence level of $\alpha = 0.05$, for $r \inf [8, 9, 10]$.
-In addition to the 13 sequences shown, there are 12 additional sequences for $r = 11$.
-
-[^20]: If we used $\phi = 0.5$, we would get the same exact sequences.
+In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences respectively, are shown for sequence for which we can reject the Wald-Wolfowitz null hypothesis[^20] at a confidence level of $\alpha = 0.05$, for $r \in [6, 7, 8, 9, 10]$[^21].
+In addition to the 14 sequences shown, there are 12 additional sequences for $r = 11$.
+
+[^20]: Interestingly, we identify the same non-random sequences when using either $\phi = 0.575$ or $\phi = 0.5$.
+
+[^21]: Since the normal method is invalid for sequences with only successes or failures, we use the exact method to evaluate (and reject) the null hypothesis for the Wald Wolfowitz runs test for $r = 6$.
 
@@
 
-\caption{Sequences ($\zeta(r)$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively.
-The observed count, $N^{\zeta r}$, and proportion, $P^{\zeta r}$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta r}$, and proportion, $\hat{P}^{\zeta r}$.
-$\hat{N}^{\zeta r}$ is scaled to the observed number of series played, hence its non-integer value.}
+\caption{Sequences ($\zeta_j$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [6, 7, 8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively.
+The observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$.
+$\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.}
 
@@
 \toprule
-$r$ & $\zeta(r)$ & $N^{\zeta r}$ & $P^{\zeta r}$ & $\hat{N}^{\zeta r}$ & $\hat{P}^{\zeta r}$ \\ 
+$r$ & $\zeta_j$ & $N^{\zeta}_j$ & $P^{\zeta}_j$ & $\hat{N}^{\zeta}_j$ & $\hat{P}^{\zeta}_j$ \\ 
 \midrule
+6 & + + + + + + & 40 & 4.7\% & 32.9 & 3.86\% \\
 8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
@@
 ```
-The relative frequency of the expected proportions are based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$.
-A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta r}$ and $\hat{P}^{\zeta r}$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the 25 significant sequences.
+The expected proportion of occurrences of each sequence $\zeta_j$ is based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$.
+A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta}_j$ and $\hat{P}^{\zeta}_j$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the non-random sequences.
 
@@
 
-However, our results do not provide evidence for momentum on several fronts: (1) the evidence supporting the constant round probability; (2) the failure to reject the binomial null hypothesis for post-streak win proportions; and (3) the failure to reject the equal proportions null hypothesis for streaky round sequences identified by the Wald-Wolfowitz runs test.
+However, our results do not provide evidence for momentum on several fronts: (1) the evidence supporting the constant round probability hypothesis; (2) the failure to reject the binomial null hypothesis for post-streak win probabilities; and (3) the failure to reject the equal proportions null hypothesis for non-random sequences identified by the Wald-Wolfowitz runs test.
 
 Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in the CoD relative to other esports.
-(Most professional esports players who have played CoD, including CoD players themselves, would not hesitate to state this.) A small skill gap fosters randomness in outcomes, implying that a given team is less likely to enjoy streaks of success in SnD.
+(Most professional esports players who have played CoD, including CoD players themselves, would not hesitate to state this.) A small skill gap fosters randomness in outcomes, implying that a given team is less likely to go on streaks of consecutive round wins in SnD, compared to the counterfactual setting where the skill gap is "large" and better teams consistently defeat worse teams.
 
 For the sake of brevity, we did not account for offensive or defensive role when considering win proportions in the rounds immediately following streaks.
-For example, it would be interesting to look at whether the round win percentage is higher after a streaks of three round wins when the team starts the streak as the offensive team.
-This would mean that, in the round immediately following the last streak win, the streaking team would be playing defense, where teams are slightly more likely to win on average.
-On the other hand, streaks of three starting with an offensive round win are less likely to occur than such streaks starting with a defensive win-$\bar{\tau}^2 (1 - \bar{\tau}) \approx$ 11.9% in the former case and $\bar{\tau} (1 - \bar{\tau})^2 \approx$ 13.0% in the latter case---so we would need to properly account for sample size differences.
-
-In the future, we could account for the quality of the teams, both in general and on specific maps.
-Even if doing so does not change the results, we could gain additional insight into why we do not observe statistically significant streakiness.
-
-Further regarding future work, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.
-R11stats expressed intent on making the data public, which would allow for research into player-specific momentum.
-While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with eliminations performed by individual players.
+It would be interesting to look at whether the round win percentage is higher after streaks of round wins when the team starts the streak as the offensive team.
+Considering streaks of three, this would mean that the streaking team would be playing defense in the round immediately following the last streak win.
+Knowing that teams are more likely to win on defense---recall $\bar{\tau} = 47.8%$---we should expect that teams on such streaks are more likely to win the round than teams that go on streaks of three starting with a defensive round win.
+On the other hand, streaks of three starting with an offensive round win are less likely to occur than such streaks starting with a defensive win---$\bar{\tau}^2 (1 - \bar{\tau}) \approx$ 11.9% in the former case and $\bar{\tau} (1 - \bar{\tau})^2 \approx$ 13.0% in the latter case---so we would need to properly account for sample size differences.
+
+Another idea would be to account for the quality of the teams, both in general and on specific maps.
+Even if we still cannot prove that the hot hand effect exists when doing so, a null finding would be insightful in and of itself.
+
+Further, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.
+Data regarding individual eliminations during each SnD round would facilitate research into player-specific momentum.
+While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with individual players.
 

### 2022-08-29 paper/paper.tex
everything but table 7 analysis

@@
 format) is declared the series winner.\footnote{A short list of rules
-  that govern timing follows.
+  that govern timing follows.} A round can end in one of four ways:
 
@@
 \item
-    A bomb plant takes five seconds. The timer resets if the player
-    stops planting site prior to completing it.
+  A bomb plant takes five seconds. The timer resets if the player stops
+  planting site prior to completing it.
 \item
@@
   Once the bomb is planted, the round timer is set to 45 seconds.
-  \end{itemize}} A round can end in one of four ways:
+\end{itemize}
 
@@
 The data set consists of all SnD matches played in major tournaments and
-qualifiers during the past three years\footnote{CoD has roughly gone
-  through three eras of professional gaming: (1) Major League Gaming
-  (MLG) tournaments prior to 2016; (2) the CoD World League (CWL),
-  initiated in 2016; and (3) the 12-franchise CoD League (CDL),
-  operating since 2020. The CDL has completed three year-long
-  ``seasons'' as of August 2022.
+qualifiers during the past three years\footnote{Since the release of
+  ``Call of Duty: Modern Warfare'' in fall 2019, professional CoD has
+  been orchestrated by the 12-franchise CoD League (CDL). The CDL has
+  completed three year-long ``seasons'' as of August 2022.}, totaling
+7,792 rounds across 852 series.\footnote{288 of the series occur in
+  major tournaments, which are considered to be more competitive than
+  the qualifiers since they are played in person (COVID-permitting),
+  eliminating randomness due to online latency and ping. The qualifiers
+  are played online.} Data has been collected in spreadsheets by
+community member ``IOUTurtle''.\footnote{Raw data:
+  \url{https://linktr.ee/CDLArchive}. Cleaned data:
+  \url{https://github.com/\%7Bauthor\%7D/\%7Brepo\%7D/blob/master/data/\%7Bfile\%7D.csv}.}
 
@@
 annual lifecycle, with releases coming in the late fall. A new game
-  under the same brand---Call of Duty---is published every year by a
+under the same brand---``Call of Duty''---is published every year by a
 rotating set of developers. Each new game bears resemblance to past
@@
 to graphics, game modes, and other facets of gameplay. During the CDL
-  era, the games released have been Modern Warfare (2020), Cold War
-  (2021) and Vanguard (2022).}, totaling 7,792 rounds across 852
-series.\footnote{288 of the series occur in major tournaments, which are
-  considered to be more competitive than the qualifiers since they are
-  played in person (COVID-permitting), eliminating randomness due to
-  online latency and ping. The qualifiers are played online.} Data has
-been collected in spreadsheets by community member
-``IOUTurtle''.\footnote{Raw data: \url{https://linktr.ee/CDLArchive}.
-  Cleaned data:
-  \url{https://github.com/\%7Bauthor\%7D/\%7Brepo\%7D/blob/master/data/\%7Bfile\%7D.csv}.}
+era, the games released have been ``Modern Warfare'' (2020 season),
+``Cold War'' (2021 season) and ``Vanguard'' (2022 season).
 
 Sweeps (6-0 series) make up 4.7\% of all series, while 6-5 series make
-up 23.7\% of series. The observed offensive round win percentage across
-all rounds is \(\bar{\tau}\) = 47.8\%.\footnote{Offensive round win
-  percentage has been nearly constant across the three games during the
-  CDL era: 1. 47.2\% in MW (2020) 2. 47.9\% in Cold War (2021) 3. 48.1\%
-  in Vanguard (2022)} Table \ref{tbl:o-win-prop-by-series-state} shows
+up 23.7\% of series. The observed offensive round win
+percentage\footnote{We use the terms ``percentage'', ``probability'',
+  and ``proportion'' synonymously throughout this paper when discussing
+  round win rates. For the most part, we restrict ``percentage'' usage
+  to observed values and ``probability'' usage to expected values, and
+  we use ``proportion'' to refer to either observed or expected values.}
+across all rounds is \(\bar{\tau}\) = 47.8\%.\footnote{Offensive round
+  win percentage has been nearly constant across the three games during
+  the CDL era: 47.2\% in Modern Warfare; 47.9\% in Cold War; and 48.1\%
+  in Vanguard} Table \ref{tbl:o-win-prop-by-series-state} shows
 offensive round win percentages by series ``state'', i.e.~the number of
@@
   best-of-five matchup, although this choice is not consistent across
-  teams, or even with the same team over time.
+  teams, or even with the same team over time.}
 
@@
 
-  This format has minimized the range of rates at which teams start
-  series playing offense. The highest rate at which a team has started
-  their series playing defense across all tournament and qualifier SnD
-  series in a single season is 66\% (31 of 47). The lowest is 38\% (16
-  of 42).}
+This format has minimized the range of rates at which teams start series
+playing offense. The highest rate at which a team has started their
+series playing defense across all tournament and qualifier SnD series in
+a single season is 66\% (31 of 47). The lowest is 38\% (16 of 42).
 
@@
 \(\phi\) of a given team winning a game in the series, regardless of the
-series state. Mosteller (1952) observed that the American League had
-dominated the National League in MLB World Series matchups through 1952,
-implying that games should not be modeled with a constant
-\(\phi_0 = 0.5\). Mosteller proposed three approaches for identifying
-the optimal constant probability value of the stronger team in the World
-Series, finding \(\hat{\phi} \approx 0.65\) in each case: (1) solve for
-\(\phi\) from the observed average number of games won by the loser of
-the series, which he called the ``method of moments'' approach; (2)
-maximize the likelihood that the sample would have been drawn from a
-population in which the probability of a team winning a game is constant
-across the series (i.e.~maximum likelihood), and (3) minimize the
-chi-squared goodness of fit statistic \(\chi^2\) as a function of
-\(\phi\).
+series state. Mosteller (\protect\hyperlink{ref-mosteller1952}{1952})
+observed that the American League had dominated the National League in
+MLB World Series matchups through 1952, implying that games should not
+be modeled with a constant \(\phi_0 = 0.5\). Mosteller proposed three
+approaches for identifying the optimal constant probability value of the
+stronger team in the World Series, finding \(\hat{\phi} \approx 0.65\)
+in each case: (1) solve for \(\phi\) from the observed average number of
+games won by the loser of the series, which he called the ``method of
+moments'' approach; (2) maximize the likelihood that the sample would
+have been drawn from a population in which the probability of a team
+winning a game is constant across the series (i.e.~maximum likelihood),
+and (3) minimize the chi-squared goodness of fit statistic \(\chi^2\) as
+a function of \(\phi\).
 
-Chance (2020) re-examined the constant probability notion in the MLB
-World Series (1923--2018), the NBA Finals (1951--2018), and the NHL
-Stanley Cup (1939--2018). Chance found strong evidence against the null
-hypothesis of \(\phi_0 = 0.5\) in the MLB and NHL championship series
-when applying Mosteller's first and second methods.
+Chance (\protect\hyperlink{ref-chance2020}{2020}) re-examined the
+constant probability notion in the MLB World Series (1923--2018), the
+NBA Finals (1951--2018), and the NHL Stanley Cup (1939--2018). Chance
+found strong evidence against the null hypothesis of \(\phi_0 = 0.5\) in
+the MLB and NHL championship series when applying Mosteller's first and
+second methods.
 
@@
 nature of series outcomes.\footnote{We often use ``streaks'' and
-  momentum interchangeably, but as Steeger et al. (2021) note, momentum
-  implies dependence between events, whereas streaking does not.} Two
-opposing fallacies are observed in the context of momentum: the
-``gambler's fallacy'' (negative recency) and the ``hot hand fallacy''
-(positive recency). Per Ayton et al. (2004), negative recency is ``the
-belief that, for random events, runs of a particular outcome \ldots{}
-will be balanced by a tendency for the opposite outcome'', while
-positive recency is the expectation of observing future results that
-match recent results.
+  momentum interchangeably, but as Steeger et al.
+  (\protect\hyperlink{ref-steeger2021}{2021}) note, momentum implies
+  dependence between events, whereas streaking does not.} Two opposing
+fallacies are observed in the context of momentum: the ``gambler's
+fallacy'' (negative recency) and the ``hot hand fallacy'' (positive
+recency). Per Ayton et al. (\protect\hyperlink{ref-ayton2004}{2004}),
+negative recency is ``the belief that, for random events, runs of a
+particular outcome \ldots{} will be balanced by a tendency for the
+opposite outcome'', while positive recency is the expectation of
+observing future results that match recent results.
 
 Studying both player streaks and team streaks in basketball, in both
-observational and controlled settings, Gilovich et al. (1985),
-henceforth GVT, did not find evidence for the hot hand phenomenon.
-However, Miller and Sanjurjo (2018), henceforth MS, provided a framework
-for quantifying streak selection bias, which effectively works in the
-manner posited by the gambler's fallacy. Specifically, MS stated that a
-``bias exists in a common measure of the conditional dependence of
-present outcomes on streaks of past outcomes in sequential data''
+observational and controlled settings, Gilovich et al.
+(\protect\hyperlink{ref-gilovich1985}{1985}), henceforth GVT, did not
+find evidence for the hot hand phenomenon. However, Miller and Sanjurjo
+(\protect\hyperlink{ref-miller2018}{2018}), henceforth MS, provided a
+framework for quantifying streak selection bias, which effectively works
+in the manner posited by the gambler's fallacy. Specifically, MS stated
+that a ``bias exists in a common measure of the conditional dependence
+of present outcomes on streaks of past outcomes in sequential data''
 implying that, under i.i.d. conditions, ``the proportion of successes
@@
 intra-round, second-by-second win probability in other FPS titles such
-as Counter-Strike (Xenopoulos, Freeman, and Silva 2022) and Valorant
-(DeRover 2021), both of which are round-based like CoD SnD. However,
-considering Counter-Strike and Valorant specifically, research on
-round-level trends seems non-existent, perhaps for one of several
-reasons:
+as Counter-Strike (\protect\hyperlink{ref-xenopoulos2022}{Xenopoulos,
+Freeman, and Silva 2022}) and Valorant
+(\protect\hyperlink{ref-derover2021}{DeRover 2021}), both of which are
+round-based like CoD SnD. However, considering Counter-Strike and
+Valorant specifically, research on round-level trends seems
+non-existent, perhaps for one of several reasons:
 
@@
 \item
-  Teams play either offense or defense for many consecutive rounds. (The
-  former has a 15-15-1 format and the latter uses a 12-12-1 format.) On
-  the other hand, teams in CoD SnD rotate roles every round, analogous
-  to a 1-1-1-1-1-1-1 format for home advantage in best-of-seven series
-  for professional sports like the MLB, NBA, and NHL.\footnote{1-1-1-1-1-1-1
-    is not used today in these leagues, but it was at least once in
-    each.} While theoretically one might be able to account for
-  inter-round win percentage relationships in any kind of format, such
-  as a 5-5-1, the rotation of team sides every round is convenient for
-  convincing ourselves that rounds could reasonably be modeled as i.i.d.
-  Bernoulli trials.
+  Teams play either offense or defense for many consecutive rounds.
+  (Counter-Strike has a 15-15-1 format and Valorant has a 12-12-1
+  format.) On the other hand, teams in CoD SnD rotate attacking and
+  defending roles every round, minimizing the effect of map asymmetry on
+  streaks of wins.\footnote{Professional CoD has a set of maps (at least
+    three, depending on the season) on which teams choose to play SnD.
+    Most are asymmetric, introducing slight advantages for the offense
+    or defense that do not exist on other maps. Counter-Strike and
+    Valorant also have their own sets of maps for their analogous SnD
+    modes.}
 \item
@@
 like the hot-hand fallacy in a sport where it has not yet been
-invetigated---particularly one that is less subjected to factors that
+investigated---particularly one that is less subjected to factors that
 may be difficult to control for, e.g.~weather---should be useful as an
@@
 In a best-of-\(s\) format, assuming a constant round win probability
-\(\phi\) (where \(0 \leq \phi \leq 1\))\footnote{If \(\phi > 0.5\), we
-  can say that this is the stronger team.} for one team\footnote{\(\phi\)
-  and other symbols are selected so as to reserve symbols like \(p\) for
-  usage in other contexts without causing confusion for the reader.
-  Upper-case symbol, e.g.~\(\Phi\), are consistently used in this paper
-  to represent proportions, while lower-case symbols corresponding to
-  upper-case symbols, e.g.~\(\phi\), are used to represent Bernoulli
-  trial success rates. ``Hats'', e.g.~\(\hat{\Phi}\), are used to convey
-  expectations, while bare symbols symbols convey observational data.},
-the expected proportion of series ending in \(r\) rounds (\(r \leq s\))
-is given by Equation \ref{eq:series-length}.
+\(\phi\) (where \(0 \leq \phi \leq 1\)) for a given team, the expected
+proportion of series ending in \(r\) rounds (where \(r \leq s\)) is
+given by Equation \ref{eq:series-length}.
 
@@
 
-in which \(\hat{\Phi}(r)\) and \(\Phi(r)\) represent the expected and
-observed round win proportions respectively, and
+where \(\hat{\Phi}(r)\) and \(\Phi(r)\) represent the expected and
+observed round win proportions respectively, and where
 \(R = [6, 7, 8, 9, 10, 11]\) for CoD SnD. The null hypothesis is that
 the test statistic is chi-squared distributed, where the number of
-degrees of freedom is \(\vert R \vert -1 = 5\) for Cod SnD.
+degrees of freedom is \(\vert R \vert -1 = 5\) for Cod SnD. We use a
+significance level of \(\alpha = 0.05\) for this test and all others in
+this paper.
 
@@
 of \(k\) wins, given that the series lasts \(r\) rounds. Removing our
-knowledge of a streak, we might model the Bernoulli round win
-probability as
+knowledge of a streak, we might expect the win proportion for a round to
+be
 
 \begin{equation}\label{eq:pwr}
-p_0(\text{win} | r) = p^{+|r}_0 := \begin{cases} 
+\hat{P}_0(\text{win} | r) = \hat{P}^{+|r}_0 := \begin{cases} 
 \frac{m}{r} & \text{team wins series}, \\ 
@@
 wins immediately following a streak of \(k\) rounds wins for a series
-lasting \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less than
-\(p^{+|r}\). However, we should not mirror the equal proportions
-hypothesis testing performed by MS.
-
-Our context is fundamentally different from that of MS, who focus on
-longitudinal data in controlled settings, unaffected by
+ending in \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less
+than the observed proportion of round wins given the series length, but
+not given knowledge of the potential existence of a streak, \(P^{+|r}\),
+i.e.~the analogue of the expected proportion in Equation \ref{eq:pwr}
+for the observed data. However, our context is fundamentally different
+from that of MS, who evaluate data in controlled settings, unaffected by
 opposition.\footnote{GVT also perform statistical tests on shots from
   players in live games, i.e.~``observational'' data, but they note that
-  their findings are likely affected by player shot selection in the
-  face of tactics by the opposing team.} The number of trials is fixed
-in their experimental designs, but in CoD SnD, the number of rounds
-played is determined as a function of the max number of possible rounds
-(\(s\)) and whether or not the team wins the series. The Bernoulli trial
-success probability, i.e.~single round win percentage in CoD SnD, is not
-independent of the opponent. Consequently, a statistical test of the
-difference in \(\hat{P}^{+|k,r}\) and \(\hat{P}^{-|kr}\), as performed
-by MS to evaluate their hypothesis regarding post-streak success rate,
-is not completely appropriate, although useful as a reference.
+  their findings are likely affected by player shot selection influenced
+  by the opposing team's defensive strategy. This is similar to our
+  setting.}
+
+The number of trials is fixed in their experimental designs; in CoD SnD,
+however, the number of rounds played is determined as a function of the
+max number of possible rounds (\(s\)) and whether or not the team wins
+the series. The single round win percentage in CoD SnD---analogous to a
+player's shooting percentage in MS's analysis of basketball players---is
+not independent of the opponent. Consequently, the i.i.d. assumption of
+MS's theorem regarding post-streak success may or may not be valid.
+Nonetheless, we still leverage \(\hat{P}^{+|k,r}_{MS}\) as a reference
+for our results.
 
@@
 
-One can consider another form of the expected proportion of rounds won
+Let us consider another form of the expected proportion of rounds won
 immediately after a streak of \(k\) round wins in a best-of-\(s\) series
-given the final length of the series (\(r\) rounds), the ``notional''
-proportion \(\hat{P}^{+|k,r}_0\). The Bernoulli round win probability
-underlying \(\hat{P}^{+|k,r}_0\) is
+ending in \(r\) rounds: the ``notional'' proportion
 
 \begin{equation}\label{eq:pwkr}
-p_0(\text{win} | k, r) = p^{+|k,r}_0 := \begin{cases}
+\hat{P}_0(\text{win} | k, r) = \hat{P}^{+|k,r}_0 := \begin{cases}
 \frac{m - k}{r - k} & \text{team wins series}, r > m; \\
@@
 
-where \(r \in R\) for \(m\) from Equation \ref{eq:m}.
+where \(r \in R\) and \(m\) from Equation \ref{eq:m}.
 
 We can perform a two-tailed binomial test to evaluate the null
-hypothesis \(\omega = \omega_0\) for the observed probability of success
-\(\omega\) and a user-specified \(\omega_0\) (where
-\(0 \leq \omega_0 \leq 1\)). If there are \(r^+\) observed successes in
-a sample of \(r\) trials, the probability of arriving at this expected
-number of successes is
+hypothesis \(\omega = \omega_0\) for the observed proportion of
+successes, \(\omega\), and a null proportion, \(\omega_0\) (where
+\(0 \leq \omega_0 \leq 1\)). The probability of exactly \(r^+\)
+successes (and \(r^- = r - r^+\) failures) in a sample of \(r\) trials
+is
 
 \begin{equation}\label{eq:binom}
-\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r-r^+}.
+\binom {r}{r^+} \omega^{r^+}(1-\omega)^{r^-},
 \end{equation}
 
-We should expect that there should be \(r * \omega_0\) successes.
+where \(\omega = \frac{r^+}{r}\) is the observed proportion of
+successes. If we can reject the null hypothesis---treating \(P^{+|k,r}\)
+and \(\hat{P}^{+|k,r}_0\) as \(\omega\) and \(\omega_0\)
+respectively---then we might consider team momentum plausible. Since we
+perform this test for many combinations of \(k\) and \(r\), we adjust
+the \(p\)-values with the Benjamini and Yekutieli (BY) false discovery
+procedure (\protect\hyperlink{ref-benjamini2001}{2001}).
 
-Treating the notional proportion \(\hat{P}^{+|k,r}_0\) as the null
-\(\omega_0\) and plugging in the observed proportion \(P^{+|k,r}\) for
-\(\omega\) in Equation \ref{eq:binom} (treating proportions as
-probabilities), we can evaluate the null hypothesis that the observed
-proportion of post-streak round wins is equal to the notional
-proportion, given streak length \(k\) and series length \(r\). If we can
-reject this null hypothesis, then we can consider team momentum,
-represented by post-streak success, plausible.
-
-As a reference, we can perform the same binomial test for the MS's
-streak-selection-adjusted proportion, \(\hat{P}^{+|k,r}_{MS}\). However,
-given the caveats mentioned before regarding applying MS's theorem to
-our setting, the results of such binomial tests should be heeded with
-caution.
+As a reference, we can perform the same binomial test for MS's
+proportion, \(\hat{P}^{+|k,r}_{MS}\), which adjusts for streak selection
+bias. However, given the caveats mentioned before regarding the
+application of MS's theorem to our setting, the results of such binomial
+tests should be heeded with caution.
 
@@
 Again, we can apply a binomial test to evaluate the hypothesis that the
-expected proportion--\(\hat{P}^{+|k,r,i}_0\) and
-\(\hat{P}^{+|k,r,i}_{MS}\) separately--is equal to the observed
-proportion \(P^{+|k,r,i}\).
+expected proportion, \(\hat{P}^{+|k,r,i}_0\), is equal to the observed
+proportion, \(P^{+|k,r,i}\).
 
@@
 
-Stepping back from the perspective of a single team's round win
-probability when streaking, one can attempt to detect the hot hand
-phenomenon more broadly with a Wald-Wolfowitz runs test. Under the null
-hypothesis, the number of runs in a sequence of \(r\) trials is a random
-variable that can take on values \(+\) or \(-\) and arrive at \(r^+\)
-successes (\(r^- = r - r^+\) failures), with the following mean \(\mu\)
-and variance \(\sigma^2\):
+We can attempt to detect the hot hand phenomenon more broadly by
+focusing on non-random sequences identified by the Wald-Wolfowitz runs
+test. Note that the probability of success and failure need not be
+equal; thus, we can incorporate our findings regarding constant round
+win probability, specifying that the probability of success is
+\(\phi_2 = 0.575\).
+
+Under the null hypothesis for the Wald-Wolfowitz runs test, the number
+of runs in a sequence of \(r\) trials is a random variable that can take
+on values \(+\) or \(-\) and arrive at \(r^+\) successes (and \(r^-\)
+failures), with the following mean \(\mu_r\) \footnote{We calculate
+  \(\mu\) and \(\sigma^2\) for each number of rounds \(r \in R\).} and
+variance \(\sigma_r^2\):
 
 \begin{equation}\label{eq:ww}
-\mu = \frac{2r^{+}r^{-}}{r} + 1, \sigma^2 = \frac{(\mu-1)(\mu-2)}{r-1}.
+\mu_r = \frac{2r^{+}r^{-}}{r} + 1, \sigma_r^2 = \frac{(\mu_r-1)(\mu_r-2)}{r-1}.
 \end{equation}
 
-To incorporate our findings regarding constant round win probability, We
-can specify that \(\Pr(r^+) = \phi\) (and, conversely, that
-\(\Pr(r^-) = 1 - \phi\)).
+The null hypothesis is that the test statistic,
 
-One can subset the observed series sequences, \(\zeta(r)\), to those
-that violate the null hypothesis for the runs test and perform a test of
-equal proportions, where the null is that the observed proportion of a
-sequence relative to all possible sequences, \(P(\zeta) = P^\zeta\), is
-equal to the expected proportion of the sequence relative to all
-possible sequences, \(\hat{P}^\zeta\). The test statistic is
+\begin{equation}\label{eq:wwz}
+z_r = \frac{r^* - \mu_r}{\sigma_r},
+\end{equation}
+
+where \(r^*\) is the number of runs, is normally distributed.
+
+We can subset the observed series sequences, \(\zeta_j\), to those that
+violate the null hypothesis for the runs test and perform a test of
+equal proportions, where the null hypothesis is that the observed
+proportion of a sequence relative to all possible sequences,
+\(P^{\zeta}_j\) ( \(\frac{N^\zeta_j}{\sum_j N^\zeta }\)), is equal to
+the expected proportion of the sequence relative to all possible
+sequences, \(\hat{P}^\zeta_j\). The test statistic is
 
 \begin{equation}\label{eq:prop}
-z = \frac{P^\zeta - \hat{P}^\zeta}{\sqrt{P^\zeta_{\delta} (1 - P^\zeta_{\delta}) (1 / N^\zeta + 1 / \hat{N}^\zeta)  } }
+z^\zeta_j = \frac{P^\zeta_j - \hat{P}^\zeta_j}{\sqrt{P^\zeta_{j,\delta} (1 - P^\zeta_{j,\delta}) (1 / N^\zeta_j + 1 / \hat{N}^\zeta_j)  } }
 \end{equation}
 
+where \(N^\zeta_j\) and \(\hat{N}^\zeta_j\) respectively represent the
+observed and expected number of occurrences of sequence \(\zeta_j\), and
 where
-
-\[
-P^\zeta_{\delta} = \frac{P^\zeta - \hat{P}^\zeta}{N^\zeta - \hat{N}^\zeta}
-\]
-
-and where \(N^\zeta\) and \(\hat{N}^\zeta\) are the observed and
-expected number of sequences respectively. The null hypothesis is that
-\(z\) is normally distributed. If \(z > +z_{(1-\alpha)/2}\) or
-\(z < -z_{(1-\alpha)/2}\) at a significance level \(\alpha\), we can
-reject the null hypothesis for such sequences and build an argument in
-support of the hot hand effect.
+\(P^\zeta_{j,\delta} = (P^\zeta_j - \hat{P}^\zeta_j) / ({N^\zeta_j - \hat{N}^\zeta_j})\).
+The null hypothesis is that the test statistic is normally distributed.
+If we can reject the null hypothesis for such sequences, we can build an
+argument in support of the hot hand effect.\footnote{As with the
+  binomial tests for the notional and MS post-streak proportions, we
+  adjust the \(p\)-values with the BY correction.}
 
@@
 Using Equation \ref{eq:chi-squ}, we find that \(\chi^2 = 16.0\)
-(\(p\)-value of 0.0068) for \(\phi_0 = 0.5\). Thus, we can comfortably
-reject the constant probability hypothesis for the null
-\(\phi_0 = 0.5\), even at a confidence level of \(\alpha = 0.01\).
+(\(p\)-value of \textless0.01) for \(\phi_0 = 0.5\). Thus, we can
+comfortably reject the constant probability hypothesis for the naive
+\(\phi_0 = 0.5\).
 
-Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected series
-lasting \(r\) rounds, the expected proportion of series given
-\(\phi_0 = 0.5\), \(\hat{\Phi}_0(r)\), and the observed proportions,
-\(\Phi(r)\).
+Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion
+of series ending in \(r\) rounds given \(\phi_0 = 0.5\),
+\(\hat{\Phi}_0(r)\), as well as the observed proportions, \(\Phi(r)\).
 
 \begin{table}
-\caption{The expected proportion of CoD SnD series lasting $r$ rounds, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.
-Additionally, the observed frequencies for CoD SnD shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).}
+\caption{The observed frequencies of CoD SnD series ending in $r$ rounds shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).
+Additionally, the expected proportion, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.}
 
@@
 Table \ref{tbl:mosteller-methods-results} shows the alternate values for
-the constant round win probability that we find when applying the three
-methods suggested by Mosteller (1952). Each is approximately equal to
-0.575. When applying Equation \ref{eq:chi-squ}, each results in a
+the constant round win probability assumption, each approximately equal
+to 0.575. When applying Equation \ref{eq:chi-squ}, each results in a
 \(\chi^2\) value for which we cannot reject the constant probability
-null hypothesis. Note that rejection of the null hypothesis is the
-baseline and failure to reject the null is the non-trivial result,
-contrary to most statistical analysis.
+null hypothesis.
 
@@
 
-Table \ref{tbl:alternative-constant-ps} shows the new \(\hat{\Phi}(r)\)
-when re-applying Equation \ref{eq:series-length} for the maximum
-likelihood estimate \(\phi_2 = 0.575\), resulting in a new set of
-expected proportions of series lasting \(r\) rounds
-\(\hat{\Phi}_2(r)\).\footnote{The method of moments and minimum
+Table \ref{tbl:alternative-constant-ps} shows the expected proportions
+of series ending in \(r\) rounds, \(\hat{\Phi}_2(r)\), when re-applying
+Equation \ref{eq:series-length} for the maximum likelihood estimate
+\(\phi_2 = 0.575\).\footnote{The method of moments and minimum
   \(\chi^2\) estimates for \(\phi\) are omitted simply because the
@@
   estimate of \(\phi\) (since they are all \(\approx 0.575\)).} We
-observe that \(\hat{\Phi}_2(r)\) is larger than \(\hat{\Phi}_0(r)\) for
-\(r \in [6, 7]\), more closely matching \(\Phi(r)\). \(\hat{\Phi}_2(r)\)
-is also closer to the observed \(\Phi(r)\) for \(r \in [9, 10]\),
-although not for \(r \in [8, 11]\).
+observe that \(\hat{\Phi}_2(r)\) more closely matches \(\Phi(r)\) than
+\(\hat{\Phi}_0(r)\).
 
 \begin{table}
-\caption{The observed proportion of CoD SnD series, $\Phi(r)$, ending in $r$ rounds, compared to the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ and the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$, for constant round win probability.}
+
+\caption{The observed proportion of CoD SnD series ending in $r$ rounds, $\Phi(r)$, compared to the expected proportion, $\hat{\Phi}_2(r)$, under the maximum likelihood estimate, $\phi_2 = 0.575$.
+Additionally, the expected proportion, $\hat{\Phi}_0(r)$, under the naive assumption $\phi_0 = 0.5$ is repeated from Table \ref{tbl:prob-series-lasts-r-rounds} for comparison.}
 
 \centering
-\begin{tabular}{rrrrrr}
+\begin{tabular}{rrrr}
 \toprule
@@
 
-Observing that the null hypothesis acceptance shown in Table
-\ref{tbl:mosteller-methods-results}, along with the observation that
-\(\hat{\Phi}_2(r)\) reasonably matches \(\Phi(r)\) (in comparison to
-\(\hat{\Phi}_0(r)\)), we can say that the constant round win probability
-assumption is valid in CoD SnD series with the appropriate choice of
-\(\phi\) (\(\approx 0.575\)).
+The observation that \(\hat{\Phi}_2(r)\) reasonably matches \(\Phi(r)\)
+supports the implication from the failure to reject the null hypothesis
+for \(\phi_2\) (shown in Table \ref{tbl:mosteller-methods-results}): the
+constant round win probability assumption can be valid for CoD SnD with
+the appropriate choice of \(\phi\) (\(\approx 0.575\)).
 
@@
 Given that people typically perceive streaks as beginning after the
-third success (or failure) at minimum (Carlson and Shu 2007), we focus
-on streaks of three round wins.\footnote{Three happens to also be a
-  reasonable number for series that last at maximum 11 rounds.} Table
-\ref{tbl:pwkr} compares the notional and MS expected proportions,
-\(\hat{P}^{+|k,r}_0\) and \(\hat{P}^{+|k,r}_{MS}\) respectively, with
-the observed round win proportion, \(P^{+|kr}\), following streaks of
-\(k=3\) round wins given the series outcome.
+third success (or failure) at minimum
+(\protect\hyperlink{ref-carlson2007}{Carlson and Shu 2007}), we focus on
+streaks of three round wins. Table \ref{tbl:pwkr} compares the observed
+round win proportion, \(P^{+|k=3,r}\), with the notional proportion,
+\(\hat{P}^{+|k=3,r}\), following streaks of \(k=3\) round wins. The MS
+proportion, \(\hat{P}^{+|k=3,r}_{MS}\), is also shown as a reference.
 
@@
 
-With the exception of \(\hat{P}^{+|k,r}_{MS}\) when \(r = 10\) and the
-eventual series loser is the team that wins after a streak of three
-round wins, all un-adjusted binomial test \(p\)-values are greater than
-the \(\alpha = 0.05\) confidence level, implying that we cannot reject
-the null hypothesis that the expected notional and MS post-streak round
-win proportions are different than the observed proportion. However,
-after adjusting the \(p\)-values with the Benjamini and Yekutieli (BY)
-correction (2001), the null hypothesis cannot be rejected for any
-case.\footnote{As noted before, the MS expectations may be unreliable
-  for CoD SnD, so one is inclined to prefer the results of the notional
-  binomial tests.}
+All binomial test \(p\)-values for both \(\hat{P}^{+|k=3,r}_0\) and
+\(\hat{P}^{+|k=3,r}_{MS}\) are found to be insignificant at the
+\(\alpha = 0.05\) threshold, implying that we cannot reject the null
+hypothesis that the notional and MS post-streak round win proportions
+are different than the observed proportion for streaks of
+three.\footnote{\(p\)-values are not shown for readability purposes.}
+When performing the same tests for streaks of two, four, and five, there
+is no case in which we can reject the null hypothesis for
+\(\hat{P}^{+|k,r}_0\). The null hypothesis can only be rejected in some
+extreme cases for \(\hat{P}^{+|k,r}_{MS}\).\footnote{These cases are:
+  (1) \(k = 4\), \(r = 7\) (\(N^{k,r} = 108\)); (2) \(k = 4\),
+  \(r = 10\) (\(N^{k,r} = 45\)); (3) \(k = 5, r = 7\)
+  (\(N^{k,r} = 37\)); (4) \(k = 5, r = 8\) (\(N^{k,r} = 4\)). In each
+  case, the team won the series.}
 
-When performing the same tests for streaks of two, four, and five, there
-is no case in which we can reject the binomial null hypothesis for the
-expected notional proportion \(\hat{P}^{+|k,r}_0\) (even before the BY
-p-value correction). The null hypothesis can only be rejected for the
-expected MS proportion \(\hat{P}^{+|k,r}_{MS}\) when \(k = 5, r = 7\)
-after applying the BY p-value correction.\footnote{At 36, the sample
-  size for \(k = 5, r = 7\) is not as large as most other combinations
-  of \(k\) and \(r\).}
-
-Now let us explicitly consider the round, \(i\). As shown in Table
-\ref{tbl:pw3ri}, the notional win proportion in the round \(i\)
-immediately following a streak of \(k\) round wins in a series lasting
-\(r\) rounds, \(\hat{P}{+|k,r,i}_0\), is statistically different than
-the observed \(P^{+|k,r,i}\) in several cases, notably when \(r = i\)
-for each of \(r \in [9, 10, 11]\).\footnote{The null can also be
-  rejected for \(r \in [7, 8]\), although these are not shown, and the
-  sample sizes are smaller.} Interestingly, the observed rate is greater
-than the expected rate in each case where we can reject the null
-hypothesis, whereas the observed rate is less than the expected rate in
-all other cases, as well in a strong majority of cases not shown.
+Table \ref{tbl:pw3ri} shows the observed and notional proportions of
+round wins immediately following streaks of three round wins when
+explicitly accounting for the round index, \(i\).\footnote{We omit the
+  MS proportions \(\hat{P}^{+|k=3,r,i}_{MS}\) since sample sizes are
+  small and results may or may not be valid due to the questionable
+  i.i.d assumption.}
 
@@
 In Table \ref{tbl:ww-sequences}, the observed and expected count of
-sequences, \(N^{\zeta r}\) and \(\hat{N}^{\zeta r}\) respectively, are
-shown for sequences, \(\zeta(r)\), for which one can reject the
-Wald-Wolfowitz null hypothesis, given probability of Bernoulli trial
-success \(\phi = 0.575\),\footnote{If we used \(\phi = 0.5\), we would
-  get the same exact sequences.} at a confidence level of
-\(\alpha = 0.05\), for \(r \inf [8, 9, 10]\). In addition to the 13
-sequences shown, there are 12 additional sequences for \(r = 11\).
+sequences respectively, are shown for sequence for which we can reject
+the Wald-Wolfowitz null hypothesis\footnote{Interestingly, we identify
+  the same non-random sequences when using either \(\phi = 0.575\) or
+  \(\phi = 0.5\).} at a confidence level of \(\alpha = 0.05\), for
+\(r \in [6, 7, 8, 9, 10]\)\footnote{Since the normal method is invalid
+  for sequences with only successes or failures, we use the exact method
+  to evaluate (and reject) the null hypothesis for the Wald Wolfowitz
+  runs test for \(r = 6\).}. In addition to the 14 sequences shown,
+there are 12 additional sequences for \(r = 11\).
 
@@
 
-The relative frequency of the expected proportions are based on 10,000
-simulations using the constant round probability \(\phi_2 = 0.575\). A
-test for the difference between the observed and expected proportions of
-all sequences, \(P^{\zeta r}\) and \(\hat{P}^{\zeta r}\) respectively,
-indicates that the null hypothesis---that the two proportions are
-equal---cannot be rejected for any of the 25 significant sequences.
+The expected proportion of occurrences of each sequence \(\zeta_j\) is
+based on 10,000 simulations using the constant round probability
+\(\phi_2 = 0.575\). A test for the difference between the observed and
+expected proportions of all sequences, \(P^{\zeta}_j\) and
+\(\hat{P}^{\zeta}_j\) respectively, indicates that the null
+hypothesis---that the two proportions are equal---cannot be rejected for
+any of the non-random sequences.
 
@@
 However, our results do not provide evidence for momentum on several
-fronts: (1) the evidence supporting the constant round probability; (2)
-the failure to reject the binomial null hypothesis for post-streak win
-proportions; and (3) the failure to reject the equal proportions null
-hypothesis for streaky round sequences identified by the Wald-Wolfowitz
-runs test.
+fronts: (1) the evidence supporting the constant round probability
+hypothesis; (2) the failure to reject the binomial null hypothesis for
+post-streak win probabilities; and (3) the failure to reject the equal
+proportions null hypothesis for non-random sequences identified by the
+Wald-Wolfowitz runs test.
 
@@
 small skill gap fosters randomness in outcomes, implying that a given
-team is less likely to enjoy streaks of success in SnD.
+team is less likely to go on streaks of consecutive round wins in SnD,
+compared to the counterfactual setting where the skill gap is ``large''
+and better teams consistently defeat worse teams.
 
@@
 role when considering win proportions in the rounds immediately
-following streaks. For example, it would be interesting to look at
-whether the round win percentage is higher after a streaks of three
-round wins when the team starts the streak as the offensive team. This
-would mean that, in the round immediately following the last streak win,
-the streaking team would be playing defense, where teams are slightly
-more likely to win on average. On the other hand, streaks of three
-starting with an offensive round win are less likely to occur than such
-streaks starting with a defensive
-win-\(\bar{\tau}^2 (1 - \bar{\tau}) \approx\) 11.9\% in the former case
-and \(\bar{\tau} (1 - \bar{\tau})^2 \approx\) 13.0\% in the latter
+following streaks. It would be interesting to look at whether the round
+win percentage is higher after streaks of round wins when the team
+starts the streak as the offensive team. Considering streaks of three,
+this would mean that the streaking team would be playing defense in the
+round immediately following the last streak win. Knowing that teams are
+more likely to win on defense---recall \(\bar{\tau} = 47.8%
+\)---we should expect that teams on such streaks are more likely to win
+the round than teams that go on streaks of three starting with a
+defensive round win. On the other hand, streaks of three starting with
+an offensive round win are less likely to occur than such streaks
+starting with a defensive
+win---\(\bar{\tau}^2 (1 - \bar{\tau}) \approx\) 11.9\% in the former
+case and \(\bar{\tau} (1 - \bar{\tau})^2 \approx\) 13.0\% in the latter
 case---so we would need to properly account for sample size differences.
 
-In the future, we could account for the quality of the teams, both in
-general and on specific maps. Even if doing so does not change the
-results, we could gain additional insight into why we do not observe
-statistically significant streakiness.
+Another idea would be to account for the quality of the teams, both in
+general and on specific maps. Even if we still cannot prove that the hot
+hand effect exists when doing so, a null finding would be insightful in
+and of itself.
 
-Further regarding future work, we have contacted the Twitter user
-``R11stats'', who privately tracks in-round player engagements. R11stats
-expressed intent on making the data public, which would allow for
-research into player-specific momentum. While it seems there is no
-team-level hot hand effect in CoD SnD, perhaps there is with
-eliminations performed by individual players.
+Further, we have contacted the Twitter user ``R11stats'', who privately
+tracks in-round player engagements. Data regarding individual
+eliminations during each SnD round would facilitate research into
+player-specific momentum. While it seems there is no team-level hot hand
+effect in CoD SnD, perhaps there is with individual players.
 

### 2022-08-30 paper/paper.Rmd
table 7

@@
 \hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
-\frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
+\frac{m-k-1}{r-k-1} & i < r-1; \\
+\frac{1}{2} & i = r-1; \\
 1 & \text{team wins series}, i = r; \\
-\frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
-0 & \text{team loses series}, i = r.
+0 & \text{team loses series}, i = r. \\
 \end{cases}
@@
       ungroup() |> 
-      select(n_rounds, win_round, win_series, ..., n, total, prop) |> 
-      # filter(!win_round) |> 
+      select(n_rounds, win_round, win_series, round, n, total, prop) |> 
       arrange(n_rounds, win_round, ...) |> 
@@
     mutate(
-      notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value,
-      ms_p_value = vectorized_binom_test(n, total, p = ms_prop)$p.value,
-      notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY')
-    )
-}
-
-compute_probs_nx_k <- function(df, k) {
+      notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value
+    )
+}
+
+filter_valid_n_rounds_combos <- function(df, k) {
   df |> 
@@
     filter(is_valid) |> 
-    select(-is_valid) |> 
+    select(-is_valid)
+}
+
+summarize_cod_win_prop_after_k_wins <- function(k) {
+  probs_nx_k <- crossing(
+    n_rounds = 7L:11L,
+    win_series = c(TRUE, FALSE),
+    win_round = c(TRUE, FALSE)
+  ) |> 
+    filter_valid_n_rounds_combos(k) |> 
     mutate(
@@
     )
-}
-
-summarize_cod_win_prop_after_k_wins <- function(k) {
-  probs_nx_k <- crossing(
-    n_rounds = 7L:11L,
-    win_series = c(TRUE, FALSE),
-    win_round = c(TRUE, FALSE)
-  ) |> 
-    compute_probs_nx_k(k)
 
@@
     probs_nx_k = probs_nx_k
-  )
-}
-
-init_cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
+  ) |> 
+    mutate(
+      ms_p_value = vectorized_binom_test(n, total, p = ms_prop)$p.value
+    )
+}
+
+cod_round_win_prop_after_k_wins <- tibble(win_streak = 2L:5L) |>
   mutate(
@@
   ) |>
-  unnest(data)
-
-cod_round_win_prop_after_k_wins <- init_cod_round_win_prop_after_k_wins |> 
+  unnest(data) |> 
   filter(win_round) |> 
@@
     n_rounds = 7L:11L,
-    round = 3L:11L,
+    round = (!!k):11L,
     win_series = c(TRUE, FALSE),
@@
     filter(round >= (!!k + 1L), n_rounds > round) |> 
-    compute_probs_nx_k(k)
+    filter_valid_n_rounds_combos(k) |> 
+    mutate(
+      notional_prop = case_when(
+        round == (n_rounds - 1L) ~ 0.5,
+        round == n_rounds & win_series ~ 1,
+        round == n_rounds & !win_series ~ 0,
+        TRUE ~ (COD_WIN_THRESHOLD - !!k - 1) / (n_rounds - !!k - 1)
+      ),
+      across(notional_prop, ~ifelse(win_round, .x, 1 - .x))
+    )
 
@@
 
-init_cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 3L) |>
+cod_round_win_prop_after_k_wins_i_rounds <- tibble(win_streak = 2L:5L) |>
   mutate(
@@
   unnest(data) |>
-  select(-starts_with('ms'))
-
-cod_round_win_prop_after_k_wins_i_rounds <- init_cod_round_win_prop_after_k_wins_i_rounds |>
-  group_by(win_streak, win_round, n_rounds, round) |> 
-  mutate(
-    total = sum(n),
-    prop = n / total
-  ) |> 
-  ungroup() |> 
-  mutate(
-    notional_p_value = vectorized_binom_test(n, total, p = notional_prop)$p.value
-  ) |> 
   filter(win_round) |> 
+  group_by(win_streak) |> 
   mutate(
     notional_p_value_adj = notional_p_value |> p.adjust(method = 'BY')
-  )
-
-# ## example of why we needed to recalculate prop... prop and notional_prop should sum to 1, grouped by win_streak and win_round
-init_cod_round_win_prop_after_k_wins_i_rounds |>
-  filter(win_streak == 3, n_rounds == 11, round == 10)
+  ) |> 
+  ungroup()
 
 cod_round_win_prop_after_k_wins_i_rounds |> 
-  filter(win_streak == 3, n_rounds == 11, round == 10)
-
-# ## 5-3?
-# cod_round_win_prop_after_k_wins_i_rounds |> 
-#   filter(win_streak == 2) |> 
-#   filter(n_rounds == 11, round == 11)
-```
-
-Table \ref{tbl:pw3ri} shows the observed and notional proportions of round wins immediately following streaks of three round wins when explicitly accounting for the round index, $i$.[^19]
+  filter(notional_p_value < 0.05)
+cod_round_win_prop_after_k_wins_i_rounds |> 
+  filter(notional_p_value_adj < 0.05)
+```
+
+Table \ref{tbl:pw3ri} shows the observed and notional proportions of round wins---$P^{+|k=3,r,i}$ and $\hat{P}^{+|k=3,r,i}_0$ respectively---immediately following streaks of three round wins when explicitly accounting for the post-streak round index, $i$.[^19][^20] While some of the observed and notional proportions differ strongly, the BY-corrected $p$-values indicate that the null hypothesis cannot be rejected for any combination of $i$ and $r$ (including those not shown).[^21] The same is true for streaks of two, four, and five.
 
 [^19]: We omit the MS proportions $\hat{P}^{+|k=3,r,i}_{MS}$ since sample sizes are small and results may or may not be valid due to the questionable i.i.d assumption.
+
+[^20]: Some combinations of $r$ and $i$ are not shown in the table for brevity.
+
+[^21]: There are combinations for which we could reject the null hypothesis if we did apply the BY correction, such as for $r = 10$ and $i = 9$.
 
@@
 Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$.
-Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$.}
+Table restricted to $r \in [10, 11]$ and $r - 3 \leq i \leq r - 1$.}
 
@@
 
-10 & 7 & no & 2 & 13 & 15.4\% & 14.3\% \\ 
-10 & 7 & yes & 11 & 13 & 84.6\% & 42.9\% \\ 
-10 & 8 & no & 1 & 10 & 10.0\% & 14.3\% \\ 
-10 & 8 & yes & 9 & 10 & 90.0\% & 42.9\% \\ 
-11 & 5 & no & 9 & 13 & 69.2\% & 25.0\% \\ 
-11 & 5 & yes & 4 & 13 & 30.8\% & 37.5\% \\ 
-11 & 6 & no & 4 & 13 & 30.8\% & 25.0\% \\ 
-11 & 6 & yes & 9 & 13 & 69.2\% & 37.5\% \\ 
-11 & 7 & no & 3 & 10 & 30.0\% & 25.0\% \\ 
-11 & 7 & yes & 7 & 10 & 70.0\% & 37.5\% \\ 
-11 & 9 & no & 5 & 15 & 33.3\% & 25.0\% \\ 
-11 & 9 & yes & 10 & 15 & 66.7\% & 37.5\% \\ 
-11 & 10 & no & 5 & 10 & 50.0\% & 25.0\% \\ 
-11 & 10 & yes & 5 & 10 & 50.0\% & 37.5\% \\
+10 & 7 & no & 2 & 6 & 33.3\% & 33.3\% \\ 
+10 & 7 & yes & 11 & 27 & 40.7\% & 33.3\% \\ 
+10 & 8 & no & 1 & 13 & 7.7\% & 33.3\% \\ 
+10 & 8 & yes & 9 & 24 & 37.5\% & 33.3\% \\ 
+10 & 9 & no & 2 & 12 & 16.7\% & 50.0\% \\ 
+10 & 9 & yes & 4 & 20 & 20.0\% & 50.0\% \\ 
+11 & 8 & no & 2 & 17 & 11.8\% & 28.6\% \\ 
+11 & 8 & yes & 3 & 19 & 15.8\% & 28.6\% \\ 
+11 & 9 & no & 5 & 12 & 41.7\% & 28.6\% \\ 
+11 & 9 & yes & 10 & 20 & 50.0\% & 28.6\% \\ 
+11 & 10 & no & 5 & 14 & 35.7\% & 50.0\% \\ 
+11 & 10 & yes & 5 & 22 & 22.7\% & 50.0\% \\
 
@@
 
-In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences respectively, are shown for sequence for which we can reject the Wald-Wolfowitz null hypothesis[^20] at a confidence level of $\alpha = 0.05$, for $r \in [6, 7, 8, 9, 10]$[^21].
-In addition to the 14 sequences shown, there are 12 additional sequences for $r = 11$.
-
-[^20]: Interestingly, we identify the same non-random sequences when using either $\phi = 0.575$ or $\phi = 0.5$.
-
-[^21]: Since the normal method is invalid for sequences with only successes or failures, we use the exact method to evaluate (and reject) the null hypothesis for the Wald Wolfowitz runs test for $r = 6$.
+In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences respectively, are shown for sequence for which we can reject the Wald-Wolfowitz null hypothesis[^22] at a confidence level of $\alpha = 0.05$, for $r \in [6, 7, 8, 9, 10]$[^23].
+In addition to the 14 sequences shown, there are 12 additional sequences for $r = 11$.[^24]
+
+[^22]: Interestingly, we identify the same non-random sequences when using either $\phi = 0.575$ or $\phi = 0.5$.
+
+[^23]: Since the normal method is invalid for sequences with only successes or failures, we use the exact method to evaluate (and reject) the null hypothesis for the Wald Wolfowitz runs test for $r = 6$.
+
+[^24]: Non-random sequences for $r = 11$ excluded for brevity.
 
@@
 \caption{Sequences ($\zeta_j$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [6, 7, 8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively.
-The observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$.
+Additionally, the observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$.
 $\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.}
@@
 \midrule
-6 & + + + + + + & 40 & 4.7\% & 32.9 & 3.86\% \\
+6 & + + + + + + & 40 & 4.69\% & 32.9 & 3.86\% \\
 8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 

### 2022-08-30 paper/paper.tex
table 7

@@
 Table \ref{tbl:pw3ri} shows the observed and notional proportions of
-round wins immediately following streaks of three round wins when
-explicitly accounting for the round index, \(i\).\footnote{We omit the
-  MS proportions \(\hat{P}^{+|k=3,r,i}_{MS}\) since sample sizes are
-  small and results may or may not be valid due to the questionable
-  i.i.d assumption.}
+round wins---\(P^{+|k=3,r,i}\) and \(\hat{P}^{+|k=3,r,i}_0\)
+respectively---immediately following streaks of three round wins when
+explicitly accounting for the post-streak round index,
+\(i\).\footnote{We omit the MS proportions \(\hat{P}^{+|k=3,r,i}_{MS}\)
+  since sample sizes are small and results may or may not be valid due
+  to the questionable i.i.d assumption.}\footnote{Some combinations of
+  \(r\) and \(i\) are not shown in the table for brevity.} While some of
+the observed and notional proportions differ strongly, the BY-corrected
+\(p\)-values indicate that the null hypothesis cannot be rejected for
+any combination of \(i\) and \(r\) (including those not
+shown).\footnote{There are combinations for which we could reject the
+  null hypothesis if we did apply the BY correction, such as for
+  \(r = 10\) and \(i = 9\).} The same is true for streaks of two, four,
+and five.
 
@@
   runs test for \(r = 6\).}. In addition to the 14 sequences shown,
-there are 12 additional sequences for \(r = 11\).
+there are 12 additional sequences for \(r = 11\).\footnote{Non-random
+  sequences for \(r = 11\) excluded for brevity.}
 

### 2022-08-30 paper/paper.Rmd
final? with gt

@@
 Second, we examine the proportion of round wins immediately following a win streak.
-Given streak length, series length, and series winner, we find no evidence that post-streak win proportion is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving.
-Wald-Wolfowitz run tests also fail to provide evidence for the hot hand phenomenon.
+Given the round index, streak length, series length, and series winner, we find no evidence that post-streak win proportion is significantly different than expected, suggesting that the perception of momentum at the team level is deceiving.
+Finally, we find that sequences of round wins that are identified as non-random by the Wald-Wolfowitz run tests do not occur more or less frequently than expectated, further failing to provide evidence for the hot hand effect.
 bibliography: references.bib
@@
 
-[^1]: SnD bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in more popular professional leagues.
+[^1]: SnD bears resemblance to "Bomb Defusal" in Counter-Strike and "Plant/Defuse" in Valorant, two other FPS games played in popular professional leagues.
 
@@
     -   A bomb defuse takes seven seconds. The timer resets if the player "drops" the bomb.
--   Once the bomb is planted, the round timer is set to 45 seconds.
+    -   Once the bomb is planted, the round timer is set to 45 seconds, regardless of the prior round timer.
 
@@
 A "game" or a "match" in such leagues is analogous to a "round" of CoD SnD for the purposes of this paper.
+
 Note that SnD is not the only game mode played in competitive CoD.[^4] Teams play in a head-to-head, best-of-five format, where SnD is always played as the second and fifth game modes.
@@
 The CDL has completed three year-long "seasons" as of August 2022.
-
-[^6]: 288 of the series occur in major tournaments, which are considered to be more competitive than the qualifiers since they are played in person (COVID-permitting), eliminating randomness due to online latency and ping.
-The qualifiers are played online.
-
-[^7]: Raw data: <https://linktr.ee/CDLArchive>. Cleaned data: <https://github.com/%7Bauthor%7D/%7Brepo%7D/blob/master/data/%7Bfile%7D.csv>.
 
@@
 
+[^6]: 288 of the series occur in major tournaments, which are considered to be more competitive than the qualifiers since they are played in person (COVID-permitting), eliminating randomness due to online latency and ping.
+The qualifiers are played online.
+
+[^7]: Raw data: <https://linktr.ee/CDLArchive>. Cleaned data: <https://github.com/author/repo/blob/master/data/file.csv>.
+
 Sweeps (6-0 series) make up 4.7% of all series, while 6-5 series make up 23.7% of series.
@@
 
-[^9]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 47.2% in Modern Warfare; 47.9% in Cold War; and 48.1% in Vanguard
+[^9]: Offensive round win percentage has been nearly constant across the three games during the CDL era: 47.2% in the 2020 season; 47.9% in the 2021 season; and 48.1% in the 2022 season.
 
@@
 
-Outside of tournaments, teams play each other twice throughout the season, constituting qualifiers. Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team.
+    Outside of tournaments, teams play each other twice throughout the season, constituting qualifiers.
+Each team gets to play the higher-seeded role once in their head-to-head matchups with a given team.
 
     This format has minimized the range of rates at which teams start series playing offense.
-The highest rate at which a team has started their series playing defense across all tournament and qualifier SnD series in a single season is 66% (31 of 47).
-The lowest is 38% (16 of 42).
+The highest rate at which a team has started their series playing defense across all tournament and qualifier SnD series in a single season is 66% (31 of 47 series).
+The lowest is 38% (16 of 42 series).
 
@@
 
-Other research has borrowed techniques from the field of quality control, such as identifying unlikely sequences of events with the Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.
-2021).
-Peel and Clauset found no evidence for unlikely sequences of scoring events in the NHL, College Football, and National Football League, although did in the NBA.
+Other research has borrowed techniques from the field of quality control, such as identifying unlikely sequences of events with the Wald-Wolfowitz runs test.
+Peel and Clauset [-@peel2015] found no evidence for unlikely sequences of scoring events in the NHL, College Football, and National Football League, although did in the NBA.
 As a check on their entropy approach to momentum identification, Steeger et al.
-found several NHL teams with sequences of wins in the 2018-2019 regular season that violated the Wald-Wolfowitz null hypothesis.
+[-@steeger2021] found several NHL teams with sequences of wins in the 2018-2019 regular season that violated the Wald-Wolfowitz null hypothesis.
 
@@
 
-[^12]: Professional CoD has a set of maps (at least three, depending on the season) on which teams choose to play SnD.
+[^12]: Professional CoD has a set of maps (at least four, depending on the season) on which teams choose to play SnD.
 Most are asymmetric, introducing slight advantages for the offense or defense that do not exist on other maps.
@@
 
-As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series ending in $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than the observed proportion of round wins given the series length, but not given knowledge of the potential existence of a streak, $P^{+|r}$, i.e.
+As implied by MS's Theorem 1, we should expect the proportion of round wins immediately following a streak of $k$ rounds wins for a series ending in $r$ rounds, $\hat{P}^{+|k,r}_{MS}$, to be strictly less than the observed proportion of round wins given the series length, where knowledge of the potential existence of a streak is not given, $P^{+|r}$, i.e.
 the analogue of the expected proportion in Equation \ref{eq:pwr} for the observed data.
@@
 
-Let us consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series ending in $r$ rounds: the "notional" proportion
+Let us consider another form of the expected proportion of rounds won immediately after a streak of $k$ round wins in a best-of-$s$ series ending in $r$ rounds, the "notional" proportion.
+We define the notional proportion as
 
@@
 \hat{P}_0(\text{win} | k, r) = \hat{P}^{+|k,r}_0 := \begin{cases}
+1 & \text{team wins series}, r = m; \\
+0 & \text{team loses series}, r = m + k; \\
 \frac{m - k}{r - k} & \text{team wins series}, r > m; \\
-1 & \text{team wins series}, r = m; \\
-\frac{s - m - k}{r - k} & \text{team loses series}, r > m + k; \\
-0 & \text{team loses series}, r = m + k,
+\frac{s - m - k}{r - k} & \text{team loses series}, r > m + k,
 \end{cases}
@@
 ```
-where $r \in R$ and $m$ from Equation \ref{eq:m}.
+where $r \in R$ and $m$ from Equation \ref{eq:m}.[^14]
+
+[^14]: Note that some cases are invalid, such as $\text{team loses series}$, $r < m + k$.
+It is impossible for team to go on a streak of $k$ round wins and then lose the series in less than $m + k$ rounds.
 
@@
 
-We can further decompose Equation \ref{eq:pwkr} by the round $i$ (where $k < i \leq r$) in which the streak of length $k$ carries into.
+We can further decompose Equation \ref{eq:pwkr} by the round $i$ ( $k < i \leq r$) in which the streak of length $k$ carries into:
 
@@
 \hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
+1 & \text{team wins series}, i = r \text{ or } r = m; \\
+0 & \text{team loses series}, i = r \text{ or } r = m + k; \\
 \frac{m-k-1}{r-k-1} & i < r-1; \\
-\frac{1}{2} & i = r-1; \\
-1 & \text{team wins series}, i = r; \\
-0 & \text{team loses series}, i = r. \\
+\frac{1}{2} & i = r-1.
 \end{cases}
@@
 ```
-Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion, $\hat{P}^{+|k,r,i}_0$, is equal to the observed proportion, $P^{+|k,r,i}$.
+where $r \in R$ and $m$ from Equation \ref{eq:m}.[^15][^16] Again, we can apply a binomial test to evaluate the hypothesis that the expected proportion, $\hat{P}^{+|k,r,i}_0$, is equal to the observed proportion, $P^{+|k,r,i}$.
+
+[^15]: The case where $i = r - 1$ is the round prior to the known last round in the series.
+We know the result of the last round since we know which team won the series.
+The penultimate round is essentially treated as a toss-up, hence $\frac{1}{2}$.
+
+[^16]: As with Equation \ref{eq:pwkr}, there are cases that are impossible, such as $\text{team loses series}$, $r < m + k$.
 
@@
 We can attempt to detect the hot hand phenomenon more broadly by focusing on non-random sequences identified by the Wald-Wolfowitz runs test.
-Note that the probability of success and failure need not be equal; thus, we can incorporate our findings regarding constant round win probability, specifying that the probability of success is $\phi_2 = 0.575$.
-
-Under the null hypothesis for the Wald-Wolfowitz runs test, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes (and $r^-$ failures), with the following mean $\mu_r$ [^14] and variance $\sigma_r^2$:
-
-[^14]: We calculate $\mu$ and $\sigma^2$ for each number of rounds $r \in R$.
+Note that the probability of success and failure need not be equal; thus, we can incorporate our findings regarding constant round win probability.
+
+Under the null hypothesis for the Wald-Wolfowitz runs test, the number of runs in a sequence of $r$ trials is a random variable that can take on values $+$ or $-$ and arrive at $r^+$ successes (and $r^-$ failures), with the following mean $\mu_r$ [^17] and variance $\sigma_r^2$:
+
+[^17]: We calculate $\mu$ and $\sigma^2$ for each number of rounds $r \in R$.
 
@@
 
-We can subset the observed series sequences, $\zeta_j$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null hypothesis is that the observed proportion of a sequence relative to all possible sequences, $P^{\zeta}_j$ ( $\frac{N^\zeta_j}{\sum_j N^\zeta }$), is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta_j$.
+We can subset the observed series sequences, $\zeta_j$, to those that violate the null hypothesis for the runs test and perform a test of equal proportions, where the null hypothesis is that the observed proportion of a sequence relative to all possible sequences, $P^{\zeta}_j$ ( $N^\zeta_j / \sum_j N^\zeta_j$), is equal to the expected proportion of the sequence relative to all possible sequences, $\hat{P}^\zeta_j$.
 The test statistic is
@@
 ```
-where $N^\zeta_j$ and $\hat{N}^\zeta_j$ respectively represent the observed and expected number of occurrences of sequence $\zeta_j$, and where $P^\zeta_{j,\delta} = (P^\zeta_j - \hat{P}^\zeta_j) / ({N^\zeta_j - \hat{N}^\zeta_j})$.
+where $N^\zeta_j$ and $\hat{N}^\zeta_j$ respectively represent the observed and expected number of occurrences of a sequence $\zeta_j$, and where $P^\zeta_{j,\delta} = (P^\zeta_j - \hat{P}^\zeta_j) / ({N^\zeta_j - \hat{N}^\zeta_j})$.
 The null hypothesis is that the test statistic is normally distributed.
-If we can reject the null hypothesis for such sequences, we can build an argument in support of the hot hand effect.[^15]
-
-[^15]: As with the binomial tests for the notional and MS post-streak proportions, we adjust the $p$-values with the BY correction.
+If we can reject the null hypothesis for such sequences, we can build an argument in support of the hot hand effect.[^18]
+
+[^18]: As with the binomial tests for the post-streak proportions, we adjust the $p$-values with the BY correction.
 
@@
 
-Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion of series ending in $r$ rounds given $\phi_0 = 0.5$, $\hat{\Phi}_0(r)$, as well as the observed proportions, $\Phi(r)$.
+Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion of series ending in $r$ rounds given $\phi_0$, $\hat{\Phi}_0(r)$, as well as the observed proportions, $\Phi(r)$.
 
@@
 \caption{Alternate estimates of the constant round win probability ($\phi$) and their corresponding $\chi^2$ values, applying the three methods suggested by Mosteller to CoD SnD.
-Additionally, the naive constant round win probability $\phi_0$ and its $\chi^2$.}
+Additionally, the naive constant round win probability $\phi_0$ and its $\chi^2$.
+$chi^2$ test $p$-values shown in parentheses.}
 
@@
 \toprule
-Method & $\phi$ & $\chi^2$ ($p$-value) \\
+Method & $\phi$ & $\chi^2$ \\
 \midrule
@@
 $\phi_0$: Naive & 0.5000 & 16.0 ($\leq$ 0.01) \\
-$\phi_1$: Method of moments & 0.5725 & 3.6 (0.6) \\
+$\phi_1$: Method of moments & 0.5725 & 3.6 (0.60) \\
 $\phi_2$: Maximum likelihood & 0.5750 & 3.5 (0.62) \\
@@
 ```
-Table \ref{tbl:alternative-constant-ps} shows the expected proportions of series ending in $r$ rounds, $\hat{\Phi}_2(r)$, when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$.[^16] We observe that $\hat{\Phi}_2(r)$ more closely matches $\Phi(r)$ than $\hat{\Phi}_0(r)$.
-
-[^16]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
+Table \ref{tbl:alternative-constant-ps} shows the expected proportions of series ending in $r$ rounds, $\hat{\Phi}_2(r)$, when re-applying Equation \ref{eq:series-length} for the maximum likelihood estimate $\phi_2 = 0.575$.[^19] We observe that $\hat{\Phi}_2(r)$ more closely matches $\Phi(r)$ than $\hat{\Phi}_0(r)$.
+
+[^19]: The method of moments and minimum $\chi^2$ estimates for $\phi$ are omitted simply because the results would be nearly identical to those for the maximum likelihood estimate of $\phi$ (since they are all $\approx 0.575$).
 
@@
 \toprule
-$r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ = 0.5 & $\hat{\Phi}_2(r)$ = 0.575 \\
+$r$ & $\Phi(r)$ & $\hat{\Phi}_0(r)$ & $\hat{\Phi}_2(r)$ \\
 \midrule
@@
 cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value_adj < 0.05)
+
+cod_round_win_prop_after_k_wins |> 
+  filter(win_streak == 3L) |> 
+  mutate(
+    across(
+      matches('p_value'), 
+      ~case_when(
+        .x <= 0.01 ~ '<=0.01', 
+        TRUE ~ sprintf('%.2f', .x)
+      )
+    ),
+    prop_lab = sprintf('%.1f', 100 * prop),
+    notional_lab = sprintf('%.1f (%s)', 100 * notional_prop, notional_p_value_adj),
+    ms_lab = sprintf('%.1f (%s)', 100 * ms_prop, ms_p_value_adj)
+  ) |>
+  arrange(n_rounds, win_series, win_round) |> 
+  filter(win_round) |> 
+  transmute(
+    n_rounds,
+    across(win_series, ~ifelse(.x, 'yes', 'no')),
+    n,
+    total,
+    prop_lab,
+    notional_lab,
+    ms_lab
+  ) |> 
+  gt::gt() |> 
+  gt::cols_label(
+    n_rounds = 'r',
+    win_series = 'Win series?',
+    n = 'r+',
+    total = 'N',
+    prop_lab = 'O',
+    notional_lab = 'a',
+    ms_lab = 'b'
+  ) |> 
+  gt::as_latex() |> 
+  cat()
 ```
@@
 Given that people typically perceive streaks as beginning after the third success (or failure) at minimum [@carlson2007], we focus on streaks of three round wins.
-Table \ref{tbl:pwkr} compares the observed round win proportion, $P^{+|k=3,r}$, with the notional proportion, $\hat{P}^{+|k=3,r}$, following streaks of $k=3$ round wins.
+Table \ref{tbl:pwkr} compares the observed round win proportion, $P^{+|k=3,r}$, with the notional proportion, $\hat{P}^{+|k=3,r}_0$, following streaks of $k=3$ round wins.
 The MS proportion, $\hat{P}^{+|k=3,r}_{MS}$, is also shown as a reference.
@@
 Additionally, the notional and MS expected proportions, $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$, respectively.
-}
+BY-corrected binomial test $p$-values shown in parentheses.}
 
@@
 \toprule
-$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ & $\hat{P}^{+|k=3,r}_0$ & $\hat{P}^{+|=k=3,r}_{MS}$ \\ 
+$r$ & \text{Win series?} & $r^{+|k=3,r}$ & $N^{k=3,r}$ & $P^{+|k=3,r}$ \% & $\hat{P}^{+|k=3,r}_0$ \% & $\hat{P}^{+|=k=3,r}_{MS}$ \% \\ 
 \midrule
 
-7 & yes & 156 & 209 & 74.6\% & 75.0\% & 75.7\% \\ 
-8 & yes & 130 & 209 & 62.2\% & 60.0\% & 61.9\% \\ 
-9 & yes & 100 & 193 & 51.8\% & 50.0\% & 52.7\% \\ 
-10 & no & 8 & 60 & 13.3\% & 14.3\% & 26.7\% \\ 
-10 & yes & 66 & 151 & 43.7\% & 42.9\% & 44.7\% \\ 
-11 & no & 31 & 129 & 24.0\% & 25.0\% & 30.8\% \\ 
-11 & yes & 60 & 150 & 40.0\% & 37.5\% & 38.8\% \\
+7 & yes & 156 & 209 & 74.6 & 75.0 (1.00) & 75.7 (1.00) \\ 
+8 & yes & 130 & 209 & 62.2 & 60.0 (1.00) & 61.9 (1.00) \\ 
+9 & yes & 100 & 193 & 51.8 & 50.0 (1.00) & 52.7 (1.00) \\ 
+10 & no & 8 & 60 & 13.3 & 14.3 (1.00) & 26.7 (0.54) \\ 
+10 & yes & 66 & 151 & 43.7 & 42.9 (1.00) & 44.7 (1.00) \\ 
+11 & no & 31 & 129 & 24.0 & 25.0 (1.00) & 30.8 (1.00) \\ 
+11 & yes & 60 & 150 & 40.0 & 37.5 (1.00) & 38.8 (1.00) \\
 
@@
 ```
-All binomial test $p$-values for both $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ are found to be insignificant at the $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the notional and MS post-streak round win proportions are different than the observed proportion for streaks of three.[^17] When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the null hypothesis for $\hat{P}^{+|k,r}_0$.
-The null hypothesis can only be rejected in some extreme cases for $\hat{P}^{+|k,r}_{MS}$.[^18]
-
-[^17]: $p$-values are not shown for readability purposes.
-
-[^18]: These cases are: (1) $k = 4$, $r = 7$ ($N^{k,r} = 108$); (2) $k = 4$, $r = 10$ ($N^{k,r} = 45$); (3) $k = 5, r = 7$ ($N^{k,r} = 37$); (4) $k = 5, r = 8$ ($N^{k,r} = 4$).
+All binomial test $p$-values for both $\hat{P}^{+|k=3,r}_0$ and $\hat{P}^{+|k=3,r}_{MS}$ are found to be insignificant at the $\alpha = 0.05$ threshold, implying that we cannot reject the null hypothesis that the notional and MS post-streak round win proportions are different than the observed proportion for streaks of three.
+When performing the same tests for streaks of two, four, and five, there is no case in which we can reject the null hypothesis for $\hat{P}^{+|k,r}_0$.
+The null hypothesis can only be rejected in some extreme cases for $\hat{P}^{+|k,r}_{MS}$.[^20]
+
+[^20]: These cases are: (1) $k = 4$, $r = 7$ ($N^{k,r} = 108$); (2) $k = 4$, $r = 10$ ($N^{k,r} = 45$); (3) $k = 5, r = 7$ ($N^{k,r} = 37$); (4) $k = 5, r = 8$ ($N^{k,r} = 4$).
 In each case, the team won the series.
@@
 
+cod_round_win_prop_after_k_wins_i_rounds |> filter(notional_p_value < 0.05)
+cod_round_win_prop_after_k_wins_i_rounds |> filter(notional_p_value_adj < 0.05)
+
 cod_round_win_prop_after_k_wins_i_rounds |> 
-  filter(notional_p_value < 0.05)
-cod_round_win_prop_after_k_wins_i_rounds |> 
-  filter(notional_p_value_adj < 0.05)
-```
-
-Table \ref{tbl:pw3ri} shows the observed and notional proportions of round wins---$P^{+|k=3,r,i}$ and $\hat{P}^{+|k=3,r,i}_0$ respectively---immediately following streaks of three round wins when explicitly accounting for the post-streak round index, $i$.[^19][^20] While some of the observed and notional proportions differ strongly, the BY-corrected $p$-values indicate that the null hypothesis cannot be rejected for any combination of $i$ and $r$ (including those not shown).[^21] The same is true for streaks of two, four, and five.
-
-[^19]: We omit the MS proportions $\hat{P}^{+|k=3,r,i}_{MS}$ since sample sizes are small and results may or may not be valid due to the questionable i.i.d assumption.
-
-[^20]: Some combinations of $r$ and $i$ are not shown in the table for brevity.
-
-[^21]: There are combinations for which we could reject the null hypothesis if we did apply the BY correction, such as for $r = 10$ and $i = 9$.
+  filter(
+    n_rounds >= 7,
+    (round + 2) >= n_rounds,
+    win_streak == 3L
+  ) |> 
+  mutate(
+    across(
+      matches('p_value'), 
+      ~case_when(
+        .x <= 0.01 ~ '<=0.01', 
+        TRUE ~ sprintf('%.2f', .x)
+      )
+    ),
+    prop_lab = sprintf('%.1f', 100 * prop),
+    notional_lab = sprintf('%.1f (%s)', 100 * notional_prop, notional_p_value_adj)
+  ) |>
+  arrange(n_rounds, win_series, win_round) |> 
+  filter(win_round) |> 
+  transmute(
+    n_rounds,
+    round,
+    across(win_series, ~ifelse(.x, 'yes', 'no')),
+    n,
+    total,
+    prop_lab,
+    notional_lab
+  ) |> 
+  arrange(n_rounds, round, win_series) |> 
+  gt::gt() |> 
+  gt::cols_label(
+    n_rounds = 'r',
+    round = 'i',
+    win_series = 'Win series?',
+    n = 'r+',
+    total = 'N',
+    prop_lab = 'O',
+    notional_lab = 'a'
+  ) |> 
+  gt::as_latex() |> 
+  cat()
+```
+
+Table \ref{tbl:pw3ri} shows the observed and notional proportions of round wins---$P^{+|k=3,r,i}$ and $\hat{P}^{+|k=3,r,i}_0$ respectively---immediately following streaks of three round wins when explicitly accounting for the post-streak round index, $i$.[^21] While some of the observed and notional proportions differ strongly, the BY-corrected $p$-values indicate that the null hypothesis cannot be rejected for any combination of $i$ and $r$, including those not shown for brevity.[^22] The same is true for streaks of two, four, and five.
+
+[^21]: We omit the MS proportions $\hat{P}^{+|k=3,r,i}_{MS}$ since sample sizes are small and results may or may not be valid due to the questionable i.i.d assumption.
+
+[^22]: There are combinations for which we could reject the null hypothesis if we did not apply the BY correction, such as for $r = 10$ and $i = 9$.
 
@@
 Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$.
-Table restricted to $r \in [10, 11]$ and $r - 3 \leq i \leq r - 1$.}
+Table restricted to $r \in [7, 8, 9, 10, 11]$ and $r - 3 \leq i \leq r - 1$.
+BY-corrected $p$-values shown in parentheses.}
 
@@
 \toprule
-$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
+$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ \% & $\hat{P}^{+|k=3,r,i}_0$ \% \\ 
 \midrule
 
-10 & 7 & no & 2 & 6 & 33.3\% & 33.3\% \\ 
-10 & 7 & yes & 11 & 27 & 40.7\% & 33.3\% \\ 
-10 & 8 & no & 1 & 13 & 7.7\% & 33.3\% \\ 
-10 & 8 & yes & 9 & 24 & 37.5\% & 33.3\% \\ 
-10 & 9 & no & 2 & 12 & 16.7\% & 50.0\% \\ 
-10 & 9 & yes & 4 & 20 & 20.0\% & 50.0\% \\ 
-11 & 8 & no & 2 & 17 & 11.8\% & 28.6\% \\ 
-11 & 8 & yes & 3 & 19 & 15.8\% & 28.6\% \\ 
-11 & 9 & no & 5 & 12 & 41.7\% & 28.6\% \\ 
-11 & 9 & yes & 10 & 20 & 50.0\% & 28.6\% \\ 
-11 & 10 & no & 5 & 14 & 35.7\% & 50.0\% \\ 
-11 & 10 & yes & 5 & 22 & 22.7\% & 50.0\% \\
+7 & 5 & yes & 36 & 54 & 66.7 & 66.7 (1.00) \\ 
+7 & 6 & yes & 34 & 54 & 63.0 & 50.0 (1.00) \\ 
+8 & 6 & yes & 20 & 41 & 48.8 & 50.0 (1.00) \\ 
+8 & 7 & yes & 24 & 46 & 52.2 & 50.0 (1.00) \\ 
+9 & 7 & yes & 15 & 33 & 45.5 & 40.0 (1.00) \\ 
+9 & 8 & yes & 18 & 37 & 48.6 & 50.0 (1.00) \\ 
+10 & 8 & no & 1 & 13 & 7.7 & 33.3 (1.00) \\ 
+10 & 8 & yes & 9 & 24 & 37.5 & 33.3 (1.00) \\ 
+10 & 9 & no & 2 & 12 & 16.7 & 50.0 (1.00) \\ 
+10 & 9 & yes & 4 & 20 & 20.0 & 50.0 (1.00) \\ 
+11 & 9 & no & 5 & 12 & 41.7 & 28.6 (1.00) \\ 
+11 & 9 & yes & 10 & 20 & 50.0 & 28.6 (1.00) \\ 
+11 & 10 & no & 5 & 14 & 35.7 & 50.0 (1.00) \\ 
+11 & 10 & yes & 5 & 22 & 22.7 & 50.0 (1.00) \\
 
@@
     )$p.value,
-    orig_prop_p_value = prop_p_value,
-    across(prop_p_value, ~p.adjust(.x, method = 'BY') |> round(3))
-  )
+    across(prop_p_value, list(adj = ~p.adjust(.x, method = 'BY'))),
+    across(
+      matches('p_value'), 
+      ~case_when(
+        .x <= 0.01 ~ '<=0.01', 
+        TRUE ~ sprintf('%.2f', .x)
+      )
+    ),
+    across(ws, ~str_replace_all(.x, '-', ' ') |> str_replace_all(c('1' = '+', '0' = '-'))),
+    actual_lab = sprintf('%.2f', 100 * prop_actual),
+    expected_lab = sprintf('%.2f (%s)', 100 * prop_expected, prop_p_value)
+  ) |> 
+  select(
+    n_rounds, 
+    ws,
+    n_actual,
+    actual_lab,
+    n_expected,
+    expected_lab
+  ) |> 
+  arrange(n_rounds, ws) |> 
+  filter(n_rounds <= 10) |> 
+  gt::gt() |> 
+  gt::cols_label(
+    n_rounds = 'r',
+    ws = 'zeta',
+    n_actual = 'n1',
+    actual_lab = 'p1',
+    n_expected = 'n2',
+    expected_lab = 'p2'
+  ) |> 
+  gt::as_latex() |> 
+  cat()
 ```
@@
 
-In Table \ref{tbl:ww-sequences}, the observed and expected count of sequences respectively, are shown for sequence for which we can reject the Wald-Wolfowitz null hypothesis[^22] at a confidence level of $\alpha = 0.05$, for $r \in [6, 7, 8, 9, 10]$[^23].
-In addition to the 14 sequences shown, there are 12 additional sequences for $r = 11$.[^24]
-
-[^22]: Interestingly, we identify the same non-random sequences when using either $\phi = 0.575$ or $\phi = 0.5$.
-
-[^23]: Since the normal method is invalid for sequences with only successes or failures, we use the exact method to evaluate (and reject) the null hypothesis for the Wald Wolfowitz runs test for $r = 6$.
-
-[^24]: Non-random sequences for $r = 11$ excluded for brevity.
+In Table \ref{tbl:ww-sequences} the observed and expected count of sequences---$P^{\zeta}_j$ and $\hat{P}^{\zeta}_j$ respectively---are shown for sequences for which we can reject the Wald-Wolfowitz null hypothesis[^23] at a confidence level of $\alpha = 0.05$, for $r \in [6, 7, 8, 9, 10]$[^24].
+In addition to the 14 sequences shown, there are 12 additional sequences for $r = 11$, not shown for brevity.[^25]
+
+[^23]: Interestingly, we identify the same non-random sequences when using either $\phi = 0.575$ or $\phi = 0.5$.
+
+[^24]: Since the normal method is invalid for sequences with only successes or failures, we use the exact method to evaluate (and reject) the null hypothesis for the Wald-Wolfowitz runs test for $r = 6$.
+
+[^25]: If we had used the exact method for detecting non-random sequences with the Wald-Wolfowitz runs test, we would have identified 20 sequences total.
 
@@
 Additionally, the observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$.
-$\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.}
+$\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.
+BY-corrected equal proportions test $p$-values in parentheses.}
 
@@
 \toprule
-$r$ & $\zeta_j$ & $N^{\zeta}_j$ & $P^{\zeta}_j$ & $\hat{N}^{\zeta}_j$ & $\hat{P}^{\zeta}_j$ \\ 
+$r$ & $\zeta_j$ & $N^{\zeta}_j$ & $P^{\zeta}_j$ \% & $\hat{N}^{\zeta}_j$ & $\hat{P}^{\zeta}_j$ \% \\ 
 \midrule
-6 & + + + + + + & 40 & 4.69\% & 32.9 & 3.86\% \\
-8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
-9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
-10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
-10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
-10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
-10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
-10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
-10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
-10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
-10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
-10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
-10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
-10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\
+
+6 & + + + + + + & 40 & 4.69 & 386 & 3.86 (0.62) \\ 
+8 & - - + + + + + + & 4 & 0.47 & 90 & 0.90 (0.23) \\ 
+9 & - - - + + + + + + & 4 & 0.47 & 44 & 0.44 (1.00) \\ 
+10 & - - - - + + + + + + & 2 & 0.23 & 21 & 0.21 (1.00) \\ 
+10 & + - - - - + + + + + & 0 & 0.00 & 24 & 0.24 (0.23) \\ 
+10 & + - + - + - + - + + & 3 & 0.35 & 13 & 0.13 (0.62) \\ 
+10 & + - + - + - + + - + & 3 & 0.35 & 20 & 0.20 (1.00) \\ 
+10 & + - + - + + - + - + & 3 & 0.35 & 24 & 0.24 (1.00) \\ 
+10 & + - + + - + - + - + & 0 & 0.00 & 20 & 0.20 (0.23) \\ 
+10 & + + - - - - + + + + & 1 & 0.12 & 14 & 0.14 (1.00) \\ 
+10 & + + - + - + - + - + & 0 & 0.00 & 13 & 0.13 (0.48) \\ 
+10 & + + + - - - - + + + & 2 & 0.23 & 24 & 0.24 (1.00) \\ 
+10 & + + + + - - - - + + & 1 & 0.12 & 28 & 0.28 (0.61) \\ 
+10 & + + + + + - - - - + & 2 & 0.23 & 12 & 0.12 (1.00) \\
 
@@
 The expected proportion of occurrences of each sequence $\zeta_j$ is based on 10,000 simulations using the constant round probability $\phi_2 = 0.575$.
-A test for the difference between the observed and expected proportions of all sequences, $P^{\zeta}_j$ and $\hat{P}^{\zeta}_j$ respectively, indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the non-random sequences.
+A test for the difference between the observed and expected proportions of all sequences indicates that the null hypothesis---that the two proportions are equal---cannot be rejected for any of the non-random sequences.
 
@@
 
-Anecdotally, most observers swear by the existence of momentum in CoD SnD series, to the extent that vernacular has been developed to describe such phenomenon.
+Anecdotally, most observers swear by the existence of momentum in CoD SnD series, to the extent that vernacular has been developed to describe such perception.
 Viewers have come to embrace the "5-3" phenomenon, where teams win three consecutive rounds after facing a 5-3 deficit to win 6-5.
@@
 
-However, our results do not provide evidence for momentum on several fronts: (1) the evidence supporting the constant round probability hypothesis; (2) the failure to reject the binomial null hypothesis for post-streak win probabilities; and (3) the failure to reject the equal proportions null hypothesis for non-random sequences identified by the Wald-Wolfowitz runs test.
-
-Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in the CoD relative to other esports.
-(Most professional esports players who have played CoD, including CoD players themselves, would not hesitate to state this.) A small skill gap fosters randomness in outcomes, implying that a given team is less likely to go on streaks of consecutive round wins in SnD, compared to the counterfactual setting where the skill gap is "large" and better teams consistently defeat worse teams.
+However, our results do not provide evidence for momentum on several fronts: (1) the evidence supporting the constant round probability hypothesis; (2) the failure to reject the binomial null hypothesis for post-streak win proportions; and (3) the failure to reject the equal proportions null hypothesis for sequences identified by the Wald-Wolfowitz runs test as non-random.
+
+Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in CoD relative to other esports that most CoD players themselves would describe, despite such a confession being potentially humiliating [@tacticalrab2022].
+A small skill gap fosters randomness in outcomes, implying that a given team is less likely to go on streaks of consecutive round wins in SnD, compared to the counterfactual setting where the skill gap is "large" and better teams consistently defeat worse teams.
 
@@
 Considering streaks of three, this would mean that the streaking team would be playing defense in the round immediately following the last streak win.
-Knowing that teams are more likely to win on defense---recall $\bar{\tau} = 47.8%$---we should expect that teams on such streaks are more likely to win the round than teams that go on streaks of three starting with a defensive round win.
+Knowing that teams are more likely to win on defense---note that $1 - \bar{\tau} = 52.2%$---we should expect that teams on such streaks are more likely to win the round than teams that go on streaks of three starting with a defensive round win.
 On the other hand, streaks of three starting with an offensive round win are less likely to occur than such streaks starting with a defensive win---$\bar{\tau}^2 (1 - \bar{\tau}) \approx$ 11.9% in the former case and $\bar{\tau} (1 - \bar{\tau})^2 \approx$ 13.0% in the latter case---so we would need to properly account for sample size differences.
 
-Another idea would be to account for the quality of the teams, both in general and on specific maps.
-Even if we still cannot prove that the hot hand effect exists when doing so, a null finding would be insightful in and of itself.
+Another idea would be to account for the quality of the teams. Even if we still cannot prove that the hot hand effect exists when doing so, a null finding would be insightful in and of itself.
 
 Further, we have contacted the Twitter user "R11stats", who privately tracks in-round player engagements.
-Data regarding individual eliminations during each SnD round would facilitate research into player-specific momentum.
+Data regarding individual eliminations during each SnD round would facilitate analysis of player-specific momentum.
 While it seems there is no team-level hot hand effect in CoD SnD, perhaps there is with individual players.

### 2022-08-30 paper/paper.tex
final? with gt

--- 2022-08-29 paper/paper.tex
@@
 Second, we examine the proportion of round wins immediately following a
-win streak. Given streak length, series length, and series winner, we
-find no evidence that post-streak win proportion is significantly
-different than expected, suggesting that the perception of momentum at
-the team level is deceiving. Wald-Wolfowitz run tests also fail to
-provide evidence for the hot hand phenomenon.
+win streak. Given the round index, streak length, series length, and
+series winner, we find no evidence that post-streak win proportion is
+significantly different than expected, suggesting that the perception of
+momentum at the team level is deceiving. Finally, we find that sequences
+of round wins that are identified as non-random by the Wald-Wolfowitz
+run tests do not occur more or less frequently than expectated, further
+failing to provide evidence for the hot hand effect.
 \end{abstract}
@@
   Counter-Strike and ``Plant/Defuse'' in Valorant, two other FPS games
-  played in more popular professional leagues.}
+  played in popular professional leagues.}
 
@@
 format) is declared the series winner.\footnote{A short list of rules
-  that govern timing follows.} A round can end in one of four ways:
+  that govern timing follows.
 
@@
   \item
-  A bomb plant takes five seconds. The timer resets if the player stops
-  planting site prior to completing it.
+    A bomb plant takes five seconds. The timer resets if the player
+    stops planting site prior to completing it.
   \item
@@
   \item
-  Once the bomb is planted, the round timer is set to 45 seconds.
-\end{itemize}
+    Once the bomb is planted, the round timer is set to 45 seconds,
+    regardless of the prior round timer.
+  \end{itemize}} A round can end in one of four ways:
 
@@
 ``game'' or a ``match'' in such leagues is analogous to a ``round'' of
-CoD SnD for the purposes of this paper. Note that SnD is not the only
-game mode played in competitive CoD.\footnote{Hardpoint has been played
-  as the first and fourth game modes in a matchup. The third game mode
-  was Domination in the 2020 season, and Control in the 2021 and 2022
-  seasons.} Teams play in a head-to-head, best-of-five format, where SnD
-is always played as the second and fifth game modes. The best-of-five
-matchup could also be called a ``series'', but since we analyze only the
-SnD games, we refer to the SnD games as series.
+CoD SnD for the purposes of this paper.
+
+Note that SnD is not the only game mode played in competitive
+CoD.\footnote{Hardpoint has been played as the first and fourth game
+  modes in a matchup. The third game mode was Domination in the 2020
+  season, and Control in the 2021 and 2022 seasons.} Teams play in a
+head-to-head, best-of-five format, where SnD is always played as the
+second and fifth game modes. The best-of-five matchup could also be
+called a ``series'', but since we analyze only the SnD games, we refer
+to the SnD games as series.
 
@@
   been orchestrated by the 12-franchise CoD League (CDL). The CDL has
-  completed three year-long ``seasons'' as of August 2022.}, totaling
-7,792 rounds across 852 series.\footnote{288 of the series occur in
-  major tournaments, which are considered to be more competitive than
-  the qualifiers since they are played in person (COVID-permitting),
-  eliminating randomness due to online latency and ping. The qualifiers
-  are played online.} Data has been collected in spreadsheets by
-community member ``IOUTurtle''.\footnote{Raw data:
-  \url{https://linktr.ee/CDLArchive}. Cleaned data:
-  \url{https://github.com/\%7Bauthor\%7D/\%7Brepo\%7D/blob/master/data/\%7Bfile\%7D.csv}.}
+  completed three year-long ``seasons'' as of August 2022.
 
@@
   era, the games released have been ``Modern Warfare'' (2020 season),
-``Cold War'' (2021 season) and ``Vanguard'' (2022 season).
+  ``Cold War'' (2021 season) and ``Vanguard'' (2022 season).}, totaling
+7,792 rounds across 852 series.\footnote{288 of the series occur in
+  major tournaments, which are considered to be more competitive than
+  the qualifiers since they are played in person (COVID-permitting),
+  eliminating randomness due to online latency and ping. The qualifiers
+  are played online.} Data has been collected in spreadsheets by
+community member ``IOUTurtle''.\footnote{Raw data:
+  \url{https://linktr.ee/CDLArchive}. Cleaned data:
+  \url{https://github.com/author/repo/blob/master/data/file.csv}.}
 
@@
   win percentage has been nearly constant across the three games during
-  the CDL era: 47.2\% in Modern Warfare; 47.9\% in Cold War; and 48.1\%
-  in Vanguard} Table \ref{tbl:o-win-prop-by-series-state} shows
-offensive round win percentages by series ``state'', i.e.~the number of
-round wins by each team prior to an upcoming round. Offensive round win
-percentage is not quite constant, although never veers more than 10\%
-from \(\bar{\tau}\).
+  the CDL era: 47.2\% in the 2020 season; 47.9\% in the 2021 season; and
+  48.1\% in the 2022 season.} Table \ref{tbl:o-win-prop-by-series-state}
+shows offensive round win percentages by series ``state'', i.e.~the
+number of round wins by each team prior to an upcoming round. Offensive
+round win percentage is not quite constant, although never veers more
+than 10\% from \(\bar{\tau}\).
 
@@
   best-of-five matchup, although this choice is not consistent across
-  teams, or even with the same team over time.}
+  teams, or even with the same team over time.
 
@@
 
-This format has minimized the range of rates at which teams start series
-playing offense. The highest rate at which a team has started their
-series playing defense across all tournament and qualifier SnD series in
-a single season is 66\% (31 of 47). The lowest is 38\% (16 of 42).
+  This format has minimized the range of rates at which teams start
+  series playing offense. The highest rate at which a team has started
+  their series playing defense across all tournament and qualifier SnD
+  series in a single season is 66\% (31 of 47 series). The lowest is
+  38\% (16 of 42 series).}
 
@@
 control, such as identifying unlikely sequences of events with the
-Wald-Wolfowitz runs test (Peel and Clauset 2015, Steeger et al.~2021).
-Peel and Clauset found no evidence for unlikely sequences of scoring
-events in the NHL, College Football, and National Football League,
-although did in the NBA. As a check on their entropy approach to
-momentum identification, Steeger et al.~found several NHL teams with
+Wald-Wolfowitz runs test. Peel and Clauset
+(\protect\hyperlink{ref-peel2015}{2015}) found no evidence for unlikely
+sequences of scoring events in the NHL, College Football, and National
+Football League, although did in the NBA. As a check on their entropy
+approach to momentum identification, Steeger et al.
+(\protect\hyperlink{ref-steeger2021}{2021}) found several NHL teams with
 sequences of wins in the 2018-2019 regular season that violated the
@@
   streaks of wins.\footnote{Professional CoD has a set of maps (at least
-    three, depending on the season) on which teams choose to play SnD.
+    four, depending on the season) on which teams choose to play SnD.
     Most are asymmetric, introducing slight advantages for the offense
@@
 ending in \(r\) rounds, \(\hat{P}^{+|k,r}_{MS}\), to be strictly less
-than the observed proportion of round wins given the series length, but
-not given knowledge of the potential existence of a streak, \(P^{+|r}\),
-i.e.~the analogue of the expected proportion in Equation \ref{eq:pwr}
-for the observed data. However, our context is fundamentally different
-from that of MS, who evaluate data in controlled settings, unaffected by
-opposition.\footnote{GVT also perform statistical tests on shots from
-  players in live games, i.e.~``observational'' data, but they note that
-  their findings are likely affected by player shot selection influenced
-  by the opposing team's defensive strategy. This is similar to our
-  setting.}
+than the observed proportion of round wins given the series length,
+where knowledge of the potential existence of a streak is not given,
+\(P^{+|r}\), i.e.~the analogue of the expected proportion in Equation
+\ref{eq:pwr} for the observed data. However, our context is
+fundamentally different from that of MS, who evaluate data in controlled
+settings, unaffected by opposition.\footnote{GVT also perform
+  statistical tests on shots from players in live games,
+  i.e.~``observational'' data, but they note that their findings are
+  likely affected by player shot selection influenced by the opposing
+  team's defensive strategy. This is similar to our setting.}
 
@@
 immediately after a streak of \(k\) round wins in a best-of-\(s\) series
-ending in \(r\) rounds: the ``notional'' proportion
+ending in \(r\) rounds, the ``notional'' proportion. We define the
+notional proportion as
 
@@
 
-where \(r \in R\) and \(m\) from Equation \ref{eq:m}.
+where \(r \in R\) and \(m\) from Equation \ref{eq:m}.\footnote{Note that
+  some cases are invalid, such as \(\text{team loses series}\),
+  \(r < m + k\). It is impossible for team to go on a streak of \(k\)
+  round wins and then lose the series in less than \(m + k\) rounds.}
 
@@
 
-We can further decompose Equation \ref{eq:pwkr} by the round \(i\)
-(where \(k < i \leq r\)) in which the streak of length \(k\) carries
-into.
+We can further decompose Equation \ref{eq:pwkr} by the round \(i\) (
+\(k < i \leq r\)) in which the streak of length \(k\) carries into:
 
@@
 \hat{P}_0(\text{win} | k, r, i) = \hat{P}^{+|k,r,i}_0 := \begin{cases}
-\frac{m - k}{r - k} & \text{team wins series}, i \neq r; \\
-1 & \text{team wins series}, i = r; \\
-\frac{s - m - k}{r - k} & \text{team loses series}, i \neq r, r > m + k; \\
-0 & \text{team loses series}, i = r.
+1 & \text{team wins series}, i = r \text{ or } r = m; \\
+0 & \text{team loses series}, i = r \text{ or } r = m + k; \\
+\frac{m-k-1}{r-k-1} & i < r-1; \\
+\frac{1}{2} & i = r-1.
 \end{cases}
@@
 
-Again, we can apply a binomial test to evaluate the hypothesis that the
-expected proportion, \(\hat{P}^{+|k,r,i}_0\), is equal to the observed
-proportion, \(P^{+|k,r,i}\).
+where \(r \in R\) and \(m\) from Equation
+\ref{eq:m}.\footnote{The case where \(i = r - 1\) is the round prior to
+  the known last round in the series. We know the result of the last
+  round since we know which team won the series. The penultimate round
+  is essentially treated as a toss-up, hence \(\frac{1}{2}\).}\footnote{As
+  with Equation \ref{eq:pwkr}, there are cases that are impossible, such
+  as \(\text{team loses series}\), \(r < m + k\).} Again, we can apply a
+binomial test to evaluate the hypothesis that the expected proportion,
+\(\hat{P}^{+|k,r,i}_0\), is equal to the observed proportion,
+\(P^{+|k,r,i}\).
 
@@
 equal; thus, we can incorporate our findings regarding constant round
-win probability, specifying that the probability of success is
-\(\phi_2 = 0.575\).
+win probability.
 
@@
 proportion of a sequence relative to all possible sequences,
-\(P^{\zeta}_j\) ( \(\frac{N^\zeta_j}{\sum_j N^\zeta }\)), is equal to
-the expected proportion of the sequence relative to all possible
-sequences, \(\hat{P}^\zeta_j\). The test statistic is
+\(P^{\zeta}_j\) ( \(N^\zeta_j / \sum_j N^\zeta_j\)), is equal to the
+expected proportion of the sequence relative to all possible sequences,
+\(\hat{P}^\zeta_j\). The test statistic is
 
@@
 where \(N^\zeta_j\) and \(\hat{N}^\zeta_j\) respectively represent the
-observed and expected number of occurrences of sequence \(\zeta_j\), and
-where
+observed and expected number of occurrences of a sequence \(\zeta_j\),
+and where
 \(P^\zeta_{j,\delta} = (P^\zeta_j - \hat{P}^\zeta_j) / ({N^\zeta_j - \hat{N}^\zeta_j})\).
@@
 argument in support of the hot hand effect.\footnote{As with the
-  binomial tests for the notional and MS post-streak proportions, we
-  adjust the \(p\)-values with the BY correction.}
+  binomial tests for the post-streak proportions, we adjust the
+  \(p\)-values with the BY correction.}
 
@@
 Table \ref{tbl:prob-series-lasts-r-rounds} shows the expected proportion
-of series ending in \(r\) rounds given \(\phi_0 = 0.5\),
-\(\hat{\Phi}_0(r)\), as well as the observed proportions, \(\Phi(r)\).
+of series ending in \(r\) rounds given \(\phi_0\), \(\hat{\Phi}_0(r)\),
+as well as the observed proportions, \(\Phi(r)\).
 
@@
 round win proportion, \(P^{+|k=3,r}\), with the notional proportion,
-\(\hat{P}^{+|k=3,r}\), following streaks of \(k=3\) round wins. The MS
+\(\hat{P}^{+|k=3,r}_0\), following streaks of \(k=3\) round wins. The MS
 proportion, \(\hat{P}^{+|k=3,r}_{MS}\), is also shown as a reference.
@@
 hypothesis that the notional and MS post-streak round win proportions
-are different than the observed proportion for streaks of
-three.\footnote{\(p\)-values are not shown for readability purposes.}
-When performing the same tests for streaks of two, four, and five, there
-is no case in which we can reject the null hypothesis for
+are different than the observed proportion for streaks of three. When
+performing the same tests for streaks of two, four, and five, there is
+no case in which we can reject the null hypothesis for
 \(\hat{P}^{+|k,r}_0\). The null hypothesis can only be rejected in some
@@
 Table \ref{tbl:pw3ri} shows the observed and notional proportions of
-round wins immediately following streaks of three round wins when
-explicitly accounting for the round index, \(i\).\footnote{We omit the
-  MS proportions \(\hat{P}^{+|k=3,r,i}_{MS}\) since sample sizes are
-  small and results may or may not be valid due to the questionable
-  i.i.d assumption.}
+round wins---\(P^{+|k=3,r,i}\) and \(\hat{P}^{+|k=3,r,i}_0\)
+respectively---immediately following streaks of three round wins when
+explicitly accounting for the post-streak round index, \(i\).\footnote{We
+  omit the MS proportions \(\hat{P}^{+|k=3,r,i}_{MS}\) since sample
+  sizes are small and results may or may not be valid due to the
+  questionable i.i.d assumption.} While some of the observed and
+notional proportions differ strongly, the BY-corrected \(p\)-values
+indicate that the null hypothesis cannot be rejected for any combination
+of \(i\) and \(r\), including those not shown for brevity.\footnote{There
+  are combinations for which we could reject the null hypothesis if we
+  did not apply the BY correction, such as for \(r = 10\) and \(i = 9\).}
+The same is true for streaks of two, four, and five.
 
@@
 Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$.
-Table restricted to $r \in [10, 11]$, $i < r$, and $N^{k=3,r,i} \geq 10$.}
+Table restricted to $r \in [7, 8, 9, 10, 11]$ and $r - 3 \leq i \leq r - 1$.
+BY-corrected $p$-values shown in parentheses.}
 
@@
 \toprule
-$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ & $\hat{P}^{+|k=3,r,i}_0$\\ 
+$r$ & $i$ & \text{Win series?} & $r^{+|k=3,r,i}$ & $N^{k=3,r,i}$ & $P^{+|k=3,r,i}$ \% & $\hat{P}^{+|k=3,r,i}_0$ \% \\ 
 \midrule
 
-10 & 7 & no & 2 & 13 & 15.4\% & 14.3\% \\ 
-10 & 7 & yes & 11 & 13 & 84.6\% & 42.9\% \\ 
-10 & 8 & no & 1 & 10 & 10.0\% & 14.3\% \\ 
-10 & 8 & yes & 9 & 10 & 90.0\% & 42.9\% \\ 
-11 & 5 & no & 9 & 13 & 69.2\% & 25.0\% \\ 
-11 & 5 & yes & 4 & 13 & 30.8\% & 37.5\% \\ 
-11 & 6 & no & 4 & 13 & 30.8\% & 25.0\% \\ 
-11 & 6 & yes & 9 & 13 & 69.2\% & 37.5\% \\ 
-11 & 7 & no & 3 & 10 & 30.0\% & 25.0\% \\ 
-11 & 7 & yes & 7 & 10 & 70.0\% & 37.5\% \\ 
-11 & 9 & no & 5 & 15 & 33.3\% & 25.0\% \\ 
-11 & 9 & yes & 10 & 15 & 66.7\% & 37.5\% \\ 
-11 & 10 & no & 5 & 10 & 50.0\% & 25.0\% \\ 
-11 & 10 & yes & 5 & 10 & 50.0\% & 37.5\% \\
+7 & 5 & yes & 36 & 54 & 66.7 & 66.7 (1.00) \\ 
+7 & 6 & yes & 34 & 54 & 63.0 & 50.0 (1.00) \\ 
+8 & 6 & yes & 20 & 41 & 48.8 & 50.0 (1.00) \\ 
+8 & 7 & yes & 24 & 46 & 52.2 & 50.0 (1.00) \\ 
+9 & 7 & yes & 15 & 33 & 45.5 & 40.0 (1.00) \\ 
+9 & 8 & yes & 18 & 37 & 48.6 & 50.0 (1.00) \\ 
+10 & 8 & no & 1 & 13 & 7.7 & 33.3 (1.00) \\ 
+10 & 8 & yes & 9 & 24 & 37.5 & 33.3 (1.00) \\ 
+10 & 9 & no & 2 & 12 & 16.7 & 50.0 (1.00) \\ 
+10 & 9 & yes & 4 & 20 & 20.0 & 50.0 (1.00) \\ 
+11 & 9 & no & 5 & 12 & 41.7 & 28.6 (1.00) \\ 
+11 & 9 & yes & 10 & 20 & 50.0 & 28.6 (1.00) \\ 
+11 & 10 & no & 5 & 14 & 35.7 & 50.0 (1.00) \\ 
+11 & 10 & yes & 5 & 22 & 22.7 & 50.0 (1.00) \\
 
@@
 
-In Table \ref{tbl:ww-sequences}, the observed and expected count of
-sequences respectively, are shown for sequence for which we can reject
-the Wald-Wolfowitz null hypothesis\footnote{Interestingly, we identify
-  the same non-random sequences when using either \(\phi = 0.575\) or
-  \(\phi = 0.5\).} at a confidence level of \(\alpha = 0.05\), for
+In Table \ref{tbl:ww-sequences} the observed and expected count of
+sequences---\(P^{\zeta}_j\) and \(\hat{P}^{\zeta}_j\) respectively---are
+shown for sequences for which we can reject the Wald-Wolfowitz null
+hypothesis\footnote{Interestingly, we identify the same non-random
+  sequences when using either \(\phi = 0.575\) or \(\phi = 0.5\).} at a
+confidence level of \(\alpha = 0.05\), for
 \(r \in [6, 7, 8, 9, 10]\)\footnote{Since the normal method is invalid
   for sequences with only successes or failures, we use the exact method
-  to evaluate (and reject) the null hypothesis for the Wald Wolfowitz
+  to evaluate (and reject) the null hypothesis for the Wald-Wolfowitz
   runs test for \(r = 6\).}. In addition to the 14 sequences shown,
-there are 12 additional sequences for \(r = 11\).
+there are 12 additional sequences for \(r = 11\), not shown for
+brevity.\footnote{If we had used the exact method for detecting
+  non-random sequences with the Wald-Wolfowitz runs test, we would have
+  identified 20 sequences total.}
 
@@
 \caption{Sequences ($\zeta_j$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [6, 7, 8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively.
-The observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$.
-$\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.}
+Additionally, the observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$.
+$\hat{N}^{\zeta}_j$ is scaled to the observed number of series played, hence its non-integer value.
+BY-corrected equal proportions test $p$-values in parentheses.}
 
@@
 \toprule
-$r$ & $\zeta_j$ & $N^{\zeta}_j$ & $P^{\zeta}_j$ & $\hat{N}^{\zeta}_j$ & $\hat{P}^{\zeta}_j$ \\ 
+$r$ & $\zeta_j$ & $N^{\zeta}_j$ & $P^{\zeta}_j$ \% & $\hat{N}^{\zeta}_j$ & $\hat{P}^{\zeta}_j$ \% \\ 
 \midrule
-6 & + + + + + + & 40 & 4.7\% & 32.9 & 3.86\% \\
-8 & - - + + + + + + & 4 & 0.47\% & 7.67 & 0.90\% \\ 
-9 & - - - + + + + + + & 4 & 0.47\% & 3.75 & 0.44\% \\ 
-10 & + + + + - - - - + + & 1 & 0.12\% & 2.39 & 0.28\% \\ 
-10 & + - - - - + + + + + & 0 & 0.00\% & 2.04 & 0.24\% \\ 
-10 & + - + - + + - + - + & 3 & 0.35\% & 2.04 & 0.24\% \\ 
-10 & + + + - - - - + + + & 2 & 0.23\% & 2.04 & 0.24\% \\ 
-10 & - - - - + + + + + + & 2 & 0.23\% & 1.79 & 0.21\% \\ 
-10 & + - + - + - + + - + & 3 & 0.35\% & 1.70 & 0.20\% \\ 
-10 & + - + + - + - + - + & 0 & 0.00\% & 1.70 & 0.20\% \\ 
-10 & + + - - - - + + + + & 1 & 0.12\% & 1.19 & 0.14\% \\ 
-10 & + - + - + - + - + + & 3 & 0.35\% & 1.11 & 0.13\% \\ 
-10 & + + - + - + - + - + & 0 & 0.00\% & 1.11 & 0.13\% \\ 
-10 & + + + + + - - - - + & 2 & 0.23\% & 1.02 & 0.12\% \\
+
+6 & + + + + + + & 40 & 4.69 & 386 & 3.86 (0.62) \\ 
+8 & - - + + + + + + & 4 & 0.47 & 90 & 0.90 (0.23) \\ 
+9 & - - - + + + + + + & 4 & 0.47 & 44 & 0.44 (1.00) \\ 
+10 & - - - - + + + + + + & 2 & 0.23 & 21 & 0.21 (1.00) \\ 
+10 & + - - - - + + + + + & 0 & 0.00 & 24 & 0.24 (0.23) \\ 
+10 & + - + - + - + - + + & 3 & 0.35 & 13 & 0.13 (0.62) \\ 
+10 & + - + - + - + + - + & 3 & 0.35 & 20 & 0.20 (1.00) \\ 
+10 & + - + - + + - + - + & 3 & 0.35 & 24 & 0.24 (1.00) \\ 
+10 & + - + + - + - + - + & 0 & 0.00 & 20 & 0.20 (0.23) \\ 
+10 & + + - - - - + + + + & 1 & 0.12 & 14 & 0.14 (1.00) \\ 
+10 & + + - + - + - + - + & 0 & 0.00 & 13 & 0.13 (0.48) \\ 
+10 & + + + - - - - + + + & 2 & 0.23 & 24 & 0.24 (1.00) \\ 
+10 & + + + + - - - - + + & 1 & 0.12 & 28 & 0.28 (0.61) \\ 
+10 & + + + + + - - - - + & 2 & 0.23 & 12 & 0.12 (1.00) \\
 
@@
 \(\phi_2 = 0.575\). A test for the difference between the observed and
-expected proportions of all sequences, \(P^{\zeta}_j\) and
-\(\hat{P}^{\zeta}_j\) respectively, indicates that the null
+expected proportions of all sequences indicates that the null
 hypothesis---that the two proportions are equal---cannot be rejected for
@@
 SnD series, to the extent that vernacular has been developed to describe
-such phenomenon. Viewers have come to embrace the ``5-3'' phenomenon,
+such perception. Viewers have come to embrace the ``5-3'' phenomenon,
 where teams win three consecutive rounds after facing a 5-3 deficit to
@@
 hypothesis; (2) the failure to reject the binomial null hypothesis for
-post-streak win probabilities; and (3) the failure to reject the equal
-proportions null hypothesis for non-random sequences identified by the
-Wald-Wolfowitz runs test.
+post-streak win proportions; and (3) the failure to reject the equal
+proportions null hypothesis for sequences identified by the
+Wald-Wolfowitz runs test as non-random.
 
 Perhaps it is not surprising that we did not find evidence in favor of
-the hot hand effect given the small ``skill gap'' in the CoD relative to
-other esports. (Most professional esports players who have played CoD,
-including CoD players themselves, would not hesitate to state this.) A
-small skill gap fosters randomness in outcomes, implying that a given
-team is less likely to go on streaks of consecutive round wins in SnD,
-compared to the counterfactual setting where the skill gap is ``large''
-and better teams consistently defeat worse teams.
+the hot hand effect given the small ``skill gap'' in CoD relative to
+other esports that most CoD players themselves would describe, despite
+such a confession being potentially humiliating
+(\protect\hyperlink{ref-tacticalrab2022}{TacticalRab 2022}). A small
+skill gap fosters randomness in outcomes, implying that a given team is
+less likely to go on streaks of consecutive round wins in SnD, compared
+to the counterfactual setting where the skill gap is ``large'' and
+better teams consistently defeat worse teams.
 
@@
 round immediately following the last streak win. Knowing that teams are
-more likely to win on defense---recall \(\bar{\tau} = 47.8%
+more likely to win on defense---note that \(1 - \bar{\tau} = 52.2%
 \)---we should expect that teams on such streaks are more likely to win
@@
 
-Another idea would be to account for the quality of the teams, both in
-general and on specific maps. Even if we still cannot prove that the hot
-hand effect exists when doing so, a null finding would be insightful in
-and of itself.
+Another idea would be to account for the quality of the teams. Even if
+we still cannot prove that the hot hand effect exists when doing so, a
+null finding would be insightful in and of itself.
 
@@
 tracks in-round player engagements. Data regarding individual
-eliminations during each SnD round would facilitate research into
+eliminations during each SnD round would facilitate analysis of
 player-specific momentum. While it seems there is no team-level hot hand
@@
 \emph{Journal of Quantitative Analysis in Sports} 17 (3): 155170.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tacticalrab2022}{}}%
+TacticalRab. 2022. {``Shotzzy FED UP of Vanguard, Scump Explains NO
+SKILL GAP in CDL?!''} January. \url{https://youtu.be/Iw1mb_U968s?t=300}.
 

### 2022-08-30 paper/paper.Rmd
rm gt

@@
 cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value_adj < 0.05)
-
-cod_round_win_prop_after_k_wins |> 
-  filter(win_streak == 3L) |> 
-  mutate(
-    across(
-      matches('p_value'), 
-      ~case_when(
-        .x <= 0.01 ~ '<=0.01', 
-        TRUE ~ sprintf('%.2f', .x)
-      )
-    ),
-    prop_lab = sprintf('%.1f', 100 * prop),
-    notional_lab = sprintf('%.1f (%s)', 100 * notional_prop, notional_p_value_adj),
-    ms_lab = sprintf('%.1f (%s)', 100 * ms_prop, ms_p_value_adj)
-  ) |>
-  arrange(n_rounds, win_series, win_round) |> 
-  filter(win_round) |> 
-  transmute(
-    n_rounds,
-    across(win_series, ~ifelse(.x, 'yes', 'no')),
-    n,
-    total,
-    prop_lab,
-    notional_lab,
-    ms_lab
-  ) |> 
-  gt::gt() |> 
-  gt::cols_label(
-    n_rounds = 'r',
-    win_series = 'Win series?',
-    n = 'r+',
-    total = 'N',
-    prop_lab = 'O',
-    notional_lab = 'a',
-    ms_lab = 'b'
-  ) |> 
-  gt::as_latex() |> 
-  cat()
 ```
@@
 cod_round_win_prop_after_k_wins_i_rounds |> filter(notional_p_value_adj < 0.05)
-
-cod_round_win_prop_after_k_wins_i_rounds |> 
-  filter(
-    n_rounds >= 7,
-    (round + 2) >= n_rounds,
-    win_streak == 3L
-  ) |> 
-  mutate(
-    across(
-      matches('p_value'), 
-      ~case_when(
-        .x <= 0.01 ~ '<=0.01', 
-        TRUE ~ sprintf('%.2f', .x)
-      )
-    ),
-    prop_lab = sprintf('%.1f', 100 * prop),
-    notional_lab = sprintf('%.1f (%s)', 100 * notional_prop, notional_p_value_adj)
-  ) |>
-  arrange(n_rounds, win_series, win_round) |> 
-  filter(win_round) |> 
-  transmute(
-    n_rounds,
-    round,
-    across(win_series, ~ifelse(.x, 'yes', 'no')),
-    n,
-    total,
-    prop_lab,
-    notional_lab
-  ) |> 
-  arrange(n_rounds, round, win_series) |> 
-  gt::gt() |> 
-  gt::cols_label(
-    n_rounds = 'r',
-    round = 'i',
-    win_series = 'Win series?',
-    n = 'r+',
-    total = 'N',
-    prop_lab = 'O',
-    notional_lab = 'a'
-  ) |> 
-  gt::as_latex() |> 
-  cat()
 ```
@@
 cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()
-
-cod_round_arrangements_mle |> 
-  filter(!is.na(p_value)) |> 
-  filter(is_significant) |> 
-  mutate(
-    total_actual = sum(n_actual),
-    total_expected_adj = sum(n_expected_adj)
-  ) |>
-  mutate(
-    prop_p_value = vectorized_prop_test(
-      n_actual, 
-      total_actual, 
-      round(n_expected_adj), 
-      round(total_expected_adj)
-    )$p.value,
-    across(prop_p_value, list(adj = ~p.adjust(.x, method = 'BY'))),
-    across(
-      matches('p_value'), 
-      ~case_when(
-        .x <= 0.01 ~ '<=0.01', 
-        TRUE ~ sprintf('%.2f', .x)
-      )
-    ),
-    across(ws, ~str_replace_all(.x, '-', ' ') |> str_replace_all(c('1' = '+', '0' = '-'))),
-    actual_lab = sprintf('%.2f', 100 * prop_actual),
-    expected_lab = sprintf('%.2f (%s)', 100 * prop_expected, prop_p_value)
-  ) |> 
-  select(
-    n_rounds, 
-    ws,
-    n_actual,
-    actual_lab,
-    n_expected,
-    expected_lab
-  ) |> 
-  arrange(n_rounds, ws) |> 
-  filter(n_rounds <= 10) |> 
-  gt::gt() |> 
-  gt::cols_label(
-    n_rounds = 'r',
-    ws = 'zeta',
-    n_actual = 'n1',
-    actual_lab = 'p1',
-    n_expected = 'n2',
-    expected_lab = 'p2'
-  ) |> 
-  gt::as_latex() |> 
-  cat()
 ```

### 2022-08-30 paper/paper.Rmd
braces instead of brackets

@@
 ```
-where $\hat{\Phi}(r)$ and $\Phi(r)$ represent the expected and observed round win proportions respectively, and where $R = [6, 7, 8, 9, 10, 11]$ for CoD SnD.
+where $\hat{\Phi}(r)$ and $\Phi(r)$ represent the expected and observed round win proportions respectively, and where $R = \{6, 7, 8, 9, 10, 11\}$ for CoD SnD.
 The null hypothesis is that the test statistic is chi-squared distributed, where the number of degrees of freedom is $\vert R \vert -1 = 5$ for Cod SnD.
@@
 \begin{table}
-\caption{The observed frequencies of CoD SnD series ending in $r$ rounds shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $r \in R = [6, 7, 8, 9, 10, 11]$).
+\caption{The observed frequencies of CoD SnD series ending in $r$ rounds shown as a count $N(r)$ and as a proportion $\Phi(r)$ of all series ($\sum_{r \in R} N(r)$, where $R = \{6, 7, 8, 9, 10, 11\}$).
 Additionally, the expected proportion, $\hat{\Phi}_0(r)$, under the assumption that each team has a constant round win probability $\phi_0 = 0.5$.}
@@
 Additionally, the notional proportion, $\hat{P}^{+|k=3,r,i}_0$.
-Table restricted to $r \in [7, 8, 9, 10, 11]$ and $r - 3 \leq i \leq r - 1$.
+Table restricted to $r \in \{7, 8, 9, 10, 11\}$ and $r - 3 \leq i \leq r - 1$.
 BY-corrected $p$-values shown in parentheses.}
@@
 
-\caption{Sequences ($\zeta_j$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in [6, 7, 8, 9, 10]$, where round wins and losses are denoted with $+$ and $-$ respectively.
+\caption{Sequences ($\zeta_j$) for which we can reject Wald-Wolfowitz null hypothesis for $r \in \{6, 7, 8, 9, 10\}$, where round wins and losses are denoted with $+$ and $-$ respectively.
 Additionally, the observed count, $N^{\zeta}_j$, and proportion, $P^{\zeta}_j$, of all possible sequences, as well as the expected count, $\hat{N}^{\zeta}_j$, and proportion, $\hat{P}^{\zeta}_j$.

### 2022-08-30 paper/paper.tex
braces instead of brackets

@@
 observed round win proportions respectively, and where
-\(R = [6, 7, 8, 9, 10, 11]\) for CoD SnD. The null hypothesis is that
+\(R = \{6, 7, 8, 9, 10, 11\}\) for CoD SnD. The null hypothesis is that
 the test statistic is chi-squared distributed, where the number of

### 2022-08-30 paper/paper.Rmd
discussion

@@
 
-Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in CoD relative to other esports that most CoD players themselves would describe, despite such a confession being potentially humiliating [@tacticalrab2022].
-A small skill gap fosters randomness in outcomes, implying that a given team is less likely to go on streaks of consecutive round wins in SnD, compared to the counterfactual setting where the skill gap is "large" and better teams consistently defeat worse teams.
+Perhaps it is not surprising that we did not find evidence in favor of the hot hand effect given the small "skill gap" in CoD relative to other esports, fostering more randomness in outcomes [@tacticalrab2022].
+More parity suggests that a given team is less likely to go on streaks of consecutive round wins in SnD compared to the counterfactual setting with a larger skill gap, where better teams more consistently defeat worse teams.
+On the other hand, one can argue that more parity does not necessarily imply that streaks of wins are more unlikely to occur, particularly when controlling for team ability.[^26]
+
+[^26]: Lopez et al.
+[-@lopez2018] found that, when accounting for team strength and temporal factors, game outcomes in the NHL and the MLB are more random than those in the NFL and the NBA, implying that the NHL and MLB are more competitive; and Chance found that no choice of a constant game probability could properly explain the distribution of games played in championships series for the NHL and the MLB.
+Together, their conclusions suggest that more parity does not necessarily preclude streaky outcomes.
 
@@
 Considering streaks of three, this would mean that the streaking team would be playing defense in the round immediately following the last streak win.
-Knowing that teams are more likely to win on defense---note that $1 - \bar{\tau} = 52.2%$---we should expect that teams on such streaks are more likely to win the round than teams that go on streaks of three starting with a defensive round win.
+Knowing that teams are more likely to win on defense---note that $1 - \bar{\tau}$ = 52.2%---we should expect that teams on such streaks are more likely to win the round than teams that go on streaks of three starting with a defensive round win.
 On the other hand, streaks of three starting with an offensive round win are less likely to occur than such streaks starting with a defensive win---$\bar{\tau}^2 (1 - \bar{\tau}) \approx$ 11.9% in the former case and $\bar{\tau} (1 - \bar{\tau})^2 \approx$ 13.0% in the latter case---so we would need to properly account for sample size differences.
-
-Another idea would be to account for the quality of the teams. Even if we still cannot prove that the hot hand effect exists when doing so, a null finding would be insightful in and of itself.
 

### 2022-08-30 paper/paper.tex
discussion

@@
 \usepackage{amsmath}
+\usepackage[bottom]{footmisc}
 \begin{document}
@@
 the hot hand effect given the small ``skill gap'' in CoD relative to
-other esports that most CoD players themselves would describe, despite
-such a confession being potentially humiliating
-(\protect\hyperlink{ref-tacticalrab2022}{TacticalRab 2022}). A small
-skill gap fosters randomness in outcomes, implying that a given team is
-less likely to go on streaks of consecutive round wins in SnD, compared
-to the counterfactual setting where the skill gap is ``large'' and
-better teams consistently defeat worse teams.
+other esports, fostering more randomness in outcomes
+(\protect\hyperlink{ref-tacticalrab2022}{TacticalRab 2022}). More parity
+suggests that a given team is less likely to go on streaks of
+consecutive round wins in SnD compared to the counterfactual setting
+with a larger skill gap, where better teams more consistently defeat
+worse teams. On the other hand, one can argue that more parity does not
+necessarily imply that streaks of wins are more unlikely to occur,
+particularly when controlling for team ability.\footnote{Lopez et al.
+  (\protect\hyperlink{ref-lopez2018}{2018}) found that, when accounting
+  for team strength and temporal factors, game outcomes in the NHL and
+  the MLB are more random than those in the NFL and the NBA, implying
+  that the NHL and MLB are more competitive; and Chance found that no
+  choice of a constant game probability could properly explain the
+  distribution of games played in championships series for the NHL and
+  the MLB. Together, their conclusions suggest that more parity does not
+  necessarily preclude streaky outcomes.}
 
@@
 round immediately following the last streak win. Knowing that teams are
-more likely to win on defense---note that \(1 - \bar{\tau} = 52.2%
-\)---we should expect that teams on such streaks are more likely to win
-the round than teams that go on streaks of three starting with a
+more likely to win on defense---note that \(1 - \bar{\tau}\) =
+52.2\%---we should expect that teams on such streaks are more likely to
+win the round than teams that go on streaks of three starting with a
 defensive round win. On the other hand, streaks of three starting with
@@
 case---so we would need to properly account for sample size differences.
-
-Another idea would be to account for the quality of the teams. Even if
-we still cannot prove that the hot hand effect exists when doing so, a
-null finding would be insightful in and of itself.
 
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-lopez2018}{}}%
+Lopez, Michael J., Gregory J. Matthews, and Benjamin S. Baumer. 2018.
+{``How Often Does the Best Team Win? A Unified Approach to Understanding
+Randomness in North American Sport.''} \emph{The Annals of Applied
+Statistics} 12 (4): 24832516.
+
 \leavevmode\vadjust pre{\hypertarget{ref-miller2018}{}}%

### 2022-10-12 scripts/1-scrape-cod-logs.R
remove presentation and plots

@@ -33,7 +33,7 @@ read_snd_logs_sheet <- function(year, overwrite = FALSE) {
     col_types = col_types
   )
   df <- raw |> janitor::clean_names()
-
+  
   qs::qsave(df, path)
   df
 }
@@ -57,7 +57,25 @@ cod_game_mapping <- c(
   '2020' = 'MW'
 )
 
-logs |> 
+team_mapping <- c(
+  'ATL' = 'FaZe',
+  'BOS' = 'Breach'
+  'DAL' = 'Empire',
+  'FLA' = 'Mutineers'
+  'LAG' = 'Guerrillas'
+  'LAT' = 'Thieves'
+  'LDN' = 'Royal Ravens'
+  'LON' = 'Royal Ravens',
+  'MIN' = 'Rokkr'
+  'NYSL' = 'Subliners'
+  'OC' = 'Optic'
+  'OPTX' = 'Optic'
+  'PAR' = 'Legion'
+  'SEA' = 'Surge'
+  'TOR' = 'Ultra'
+)
+
+log_ids <- logs |> 
   select(
     round,
     map,
@@ -67,26 +85,150 @@ logs |>
     map,
     offense_team,
     defense_team,
-    round_time_left,
-    bomb_timer_left,
-    activity,
-    weapon_or_bomb_site,
     offense_remaining,
     defense_remaining,
-    killer_player,
-    victim_player,
-    killer_team,
-    killer_off_def,
-    round_winner,
-    seconds_elapsed,
-    first_blood,
-    traded_out,
-    trade_kill,
-    initial_bomb_carrier_killed,
-    offense_players_remaining,
-    defense_players_remaining,
-    last_round_activity,
-    x1v_situation_entered_offense,
-    x1v_situation_entered_defense,
-    situation_length
+    round_time_left,
+    bomb_timer_left,
+    activity
+  )
+log_ids |> distinct()
+
+bind_rows(
+  logs |> 
+    transmute(
+      round,
+      map,
+      match_id,
+      map_id,
+      round,
+      map,
+      round_time_left,
+      bomb_timer_left,
+      activity,
+      is_offense = TRUE,
+      team = offense_team,
+      opponent = defense_team,
+      n_team_remaining = offense_remaining,
+      n_opp_remaining = defense_remaining,
+      weapon_or_bomb_site,
+      killer_player,
+      victim_player,
+      killer_team,
+      killer_off_def,
+      round_winner,
+      seconds_elapsed,
+      first_blood,
[…]

### 2022-10-12 paper/paper.Rmd
denonymize

@@
 authors:
-  - name: Person One
-    email: personone@domain.com
-  - name: Person Two
-    email: persontwo@domain.com
+  - name: Tony ElHabr
+    email: anthonyelhabr@gmail.com
+    url: https://tonyelhabr.rbind.io
+  - name: Andrew ElHabr
+    email: andrewelhabr@gatech.edu
+    affiliation: Georgia Institute of Technology
+    department: School of Industrial and Systems Engineering (ISyE)
+    location: Atlanta, Georgia, USA
 abstract: |
@@
 
-[^7]: Raw data: <https://linktr.ee/CDLArchive>. Cleaned data: <https://github.com/author/repo/blob/master/data/file.csv>.
+[^7]: Raw data: <https://linktr.ee/CDLArchive>. Cleaned data: <https://github.com/tonyelhabr/cod_snd/blob/master/data/cod_rounds.csv>.
 

### 2022-10-12 paper/paper.tex
denonymize

@@
 \author{
-    Person One
+    Tony ElHabr
    \\
@@
    \\
-  \texttt{\href{mailto:personone@domain.com}{\nolinkurl{personone@domain.com}}} \\
+  \texttt{\href{mailto:anthonyelhabr@gmail.com}{\nolinkurl{anthonyelhabr@gmail.com}}} \\
    \And
-    Person Two
+    Andrew ElHabr
    \\
-     \\
-   \\
-  \texttt{\href{mailto:persontwo@domain.com}{\nolinkurl{persontwo@domain.com}}} \\
+    School of Industrial and Systems Engineering (ISyE) \\
+    Georgia Institute of Technology \\
+  Atlanta, Georgia, USA \\
+  \texttt{\href{mailto:andrewelhabr@gatech.edu}{\nolinkurl{andrewelhabr@gatech.edu}}} \\
   }
@@
   \url{https://linktr.ee/CDLArchive}. Cleaned data:
-  \url{https://github.com/author/repo/blob/master/data/file.csv}.}
+  \url{https://github.com/tonyelhabr/cod_snd/blob/master/data/cod_rounds.csv}.}
 
